### 2016-11-16 tex/main.tex
Add base structure for the paper.

\documentclass{article}

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}

% Title
\title{A numerical study of fixation probabilities for strategies in the
Iterated Prisoner's Dilemma}
\author{Marc Harper and Vincent Knight}
\date{}

\begin{document}

\maketitle

\abstract{TBD}

\section{Introduction}\label{sec:introduction}

Main questions are:

\begin{enumerate}
    \item What strategies are good invaders?
    \item What strategies are good at resisting invasion?
    \item How do 1 and 2 change as a function of population size?
\end{enumerate}

Structure:

\begin{itemize}
    \item Overview of Moran processes;
    \item Review of the literature;
    \item Short discussion about the Axelrod library.
\end{itemize}

\section{Validation}\label{sec:validation}

Structure:

\begin{itemize}
    \item Compute fitness landscape for some strategy pairs;
    \item Verify against the data;
\end{itemize}

\section{Numerical results}\label{sec:numerical_results}

Structure:

\begin{itemize}
    \item General overview of the data obtained;
    \item Inclusion of most of the work in \texttt{Moran.ipynb}.
\end{itemize}

\section{Conclusion}\label{sec:conclusion}

\end{document}

### 2016-11-18 approximate_moran.py
Add an approx moran process.
Also including a nb to show how it works.

@@ -1,0 +1,59 @@
+import axelrod as axl
+import numpy as np
+
+class Pdf:
+    """A class for a probability distribution"""
+    def __init__(self, counter):
+        """Take as an instance of collections.counter"""
+        self.sample_space, self.counts = zip(*counter.items())
+        self.size = len(self.sample_space)
+        self.total = sum(self.counts)
+        self.probability = list([v / self.total  for v in self.counts])
+
+    def sample(self):
+        """Sample from the pdf"""
+        index = np.random.choice(a=range(self.size), p=self.probability)
+        # Numpy cannot sample from a list of n dimensional objects for n > 1, need to sample an index
+        return self.sample_space[index]
+
+    def __repr__(self):
+        return "Sample space: {} - Probabilities: {}".format(self.sample_space, self.probability)
+
+
+class ApproximateMoranProcess(axl.MoranProcess):
+    """
+    A class to approximate a Moran process based
+    on a distribution of potential Match outcomes.
+
+    Instead of playing the matches, the result is sampled
+    from a dictionary of play tuples to distribution of match outcomes
+    """
+    def __init__(self, players, cached_outcomes=None, mutation_rate=0.):
+        super(ApproximateMoranProcess, self).__init__(players, turns=0, noise=1, deterministic_cache=None, mutation_rate=0.)
+        self.cached_outcomes = cached_outcomes
+
+    def _play_next_round(self):
+        """
+        Plays the next round of the process. Every player is paired up
+        against every other player and the total scores are obtained from the
+        """
+        N = self.num_players
+        scores = [0] * N
+        for i in range(N):
+            for j in range(i + 1, N):
+                player_names = tuple([str(self.players[i]), str(self.players[j])])
+
+                try:
+                    match_scores = self.cached_outcomes[player_names].sample()
+                    scores[i] += match_scores[0]
+                    scores[j] += match_scores[1]
+                except KeyError:
+                    match_scores = self.cached_outcomes[player_names[::-1]].sample()
+                    scores[i] += match_scores[1]
+                    scores[j] += match_scores[0]
+                #print("------")
+                #print(self.players[i], scores[i], self.players[j], scores[j])
+        self.score_history.append(scores)
+        return scores
+
+

### 2016-11-20 approximate_moran.py
Add parallel match data generation script

@@ -1,14 +1,14 @@
 import axelrod as axl
 import numpy as np
 
-class Pdf:
+class Pdf(object):
     """A class for a probability distribution"""
     def __init__(self, counter):
         """Take as an instance of collections.counter"""
         self.sample_space, self.counts = zip(*counter.items())
         self.size = len(self.sample_space)
         self.total = sum(self.counts)
-        self.probability = list([v / self.total  for v in self.counts])
+        self.probability = list([v / self.total for v in self.counts])
 
     def sample(self):
         """Sample from the pdf"""
@@ -29,7 +29,7 @@ class ApproximateMoranProcess(axl.MoranProcess):
     from a dictionary of play tuples to distribution of match outcomes
     """
     def __init__(self, players, cached_outcomes=None, mutation_rate=0.):
-        super(ApproximateMoranProcess, self).__init__(players, turns=0, noise=1, deterministic_cache=None, mutation_rate=0.)
+        super(ApproximateMoranProcess, self).__init__(players, turns=0, noise=0, deterministic_cache=None, mutation_rate=0.)
         self.cached_outcomes = cached_outcomes
 
     def _play_next_round(self):
@@ -51,8 +51,6 @@ class ApproximateMoranProcess(axl.MoranProcess):
                     match_scores = self.cached_outcomes[player_names[::-1]].sample()
                     scores[i] += match_scores[1]
                     scores[j] += match_scores[0]
-                #print("------")
-                #print(self.players[i], scores[i], self.players[j], scores[j])
         self.score_history.append(scores)
         return scores
 

### 2016-11-20 generate_data.py

@@ -1,0 +1,138 @@
+from collections import defaultdict, Counter
+import csv
+import functools
+import multiprocessing
+import os
+
+import axelrod as axl
+#from approximate_moran import *
+
+def write_csv(outcomes, filename="outcomes.csv", append=False):
+    s = 'w'
+    if append:
+        s = 'a'
+    writer = csv.writer(open(filename, s))
+    for pair, counter in outcomes.items():
+        for scores, count in counter.items():
+            row = [pair[0], pair[1], scores[0], scores[1], count]
+            writer.writerow(row)
+
+def read_csv(filename="outcomes.csv"):
+    reader = csv.reader(open(filename))
+    outcomes = defaultdict(Counter)
+    for row in reader:
+        p1, p2, s1, s2, count = row
+        outcomes[(p1, p2)][(float(s1), float(s2))] = int(count)
+        if p1 != p2:
+            outcomes[(p2, p1)][(float(s2), float(s1))] = int(count)
+    return outcomes
+
+def generate_matchups(players):
+    # Want the triangular product
+    for i in range(len(players)):
+        for j in range(i, len(players)):
+            if i == j:
+                yield players[i].clone(), players[j]
+            else:
+                yield players[i], players[j]
+
+def generate_matchups_indices(num_players):
+    # Want the triangular product
+    for i in range(num_players):
+        for j in range(i, num_players):
+            yield i, j
+
+def sample_match_outcomes(players, turns, repetitions, noise=0):
+    """
+    Play all matches between pairs of players and return a dictionary mapping
+    player names to outcomes.
+    """
+    match_outcomes = dict()
+    matchups = list(generate_matchups(players))
+
+    for pairs in matchups:
+
+        match = axl.Match(pairs, turns=turns, noise=noise)
+        rs = repetitions
+        if not match._stochastic:
+            rs = 1
+        outcomes = []
+        for _ in range(rs):
+            match.play()
+            outcomes.append(match.final_score_per_turn())
+
+        counts = Counter(outcomes)
+
+        player_names = tuple(map(str, pairs))
+        match_outcomes[player_names] = counts
+
+    return match_outcomes
+
+def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
+    """
+    Write the winner of a Moran process to file
+    """
+    if seed:
+        axl.seed(seed)  # Seed the process
+
+    pairs = (players[i]().clone(), players[j]().clone())
[…]

### 2016-11-20 generate_data.py
Minor updates

@@ -78,8 +78,8 @@ def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
     pairs = (players[i]().clone(), players[j]().clone())
     match = axl.Match(pairs, turns=turns, noise=noise)
     rs = repetitions
-    if not match._stochastic:
-        rs = 1
+    if not match._stochastic and noise == 0:
+        print(noise)
     outcomes = []
     for _ in range(rs):
         match.play()
@@ -122,17 +122,21 @@ if __name__ == "__main__":
     #            and not s().classifier['long_run_time']
     #            and axl.obey_axelrod(s())]
 
-    players = [s for s in axl.all_strategies if axl.obey_axelrod(s())]
+    players = [s for s in axl.all_strategies if axl.obey_axelrod(s())
+               and not s().classifier['long_run_time']]
 
     print(len(list(map(str, players))))
 
-    os.remove("outcomes.csv")
+    try:
+        os.remove("outcomes.csv")
+    except FileNotFoundError:
+        pass
+
+    # sample_match_outcomes_parallel(turns=200, repetitions=100,
+    #                                filename="outcomes.csv", noise=0,
+    #                                processes=4)
 
     sample_match_outcomes_parallel(turns=200, repetitions=100,
-                                   filename="outcomes.csv", noise=0,
-                                   processes=4)
-
-    sample_match_outcomes_parallel(turns=200, repetitions=10,
                                    filename="outcomes_noise.csv", noise=0.05,
                                    processes=4)
 

### 2017-04-10 strategies.py
Move strategies.py to players.py and add fsms

@@ -1,121 +1,0 @@
-import axelrod as axl
-
-def selected_strategies():
-    strategies = [
-        axl.Adaptive,
-        axl.Aggravater,
-        axl.ALLCorALLD,
-        axl.Alternator,
-        axl.AlternatorHunter,
-        axl.AntiCycler,
-        axl.AntiTitForTat,
-        axl.APavlov2006,
-        axl.APavlov2011,
-        axl.Appeaser,
-        axl.AverageCopier,
-        axl.BackStabber,
-        axl.Bully,
-        axl.Calculator,
-        axl.Champion,
-        axl.Cooperator,
-        axl.ContriteTitForTat,
-        axl.CyclerCCCCCD,
-        axl.CyclerCCCD,
-        axl.CyclerCCD,
-        axl.CyclerDC,
-        axl.CyclerDDC,
-        axl.CycleHunter,
-        axl.Davis,
-        axl.Defector,
-        axl.DoubleCrosser,
-        axl.Eatherley,
-        axl.Feld,
-        axl.FirmButFair,
-        axl.FoolMeForever,
-        axl.FoolMeOnce,
-        axl.ForgetfulFoolMeOnce,
-        axl.ForgetfulGrudger,
-        axl.Forgiver,
-        axl.ForgivingTitForTat,
-        axl.Fortress3,
-        axl.Fortress4,
-        axl.PSOGambler,
-        axl.GTFT,
-        axl.GoByMajority,
-        axl.GoByMajority10,
-        axl.GoByMajority20,
-        axl.GoByMajority40,
-        axl.GoByMajority5,
-        axl.Handshake,
-        axl.HardGoByMajority,
-        axl.HardGoByMajority10,
-        axl.HardGoByMajority20,
-        axl.HardGoByMajority40,
-        axl.HardGoByMajority5,
-        axl.Golden,
-        axl.Grofman,
-        axl.Grudger,
-        axl.Grumpy,
-        axl.HardProber,
-        axl.HardTitFor2Tats,
-        axl.HardTitForTat,
-        axl.Inverse,
-        axl.InversePunisher,
-        axl.Joss,
-        axl.LimitedRetaliate,
-        axl.LimitedRetaliate2,
-        axl.LimitedRetaliate3,
-        axl.EvolvedLookerUp,
-        axl.MathConstantHunter,
-        axl.MetaHunter,
-        axl.NiceAverageCopier,
-        axl.Nydegger,
[…]

### 2017-04-10 moran.py
Add script to generate cache.
Also modify things so that it reads the players in properly.

@@ -176,8 +176,9 @@ if __name__ == "__main__":
     for k, v in match_outcomes.items():
         match_outcomes[k] = Pdf(v)
 
-    players = [s() for s in axl.all_strategies if axl.obey_axelrod(s())
-               and not s().classifier['long_run_time']]
+    # players are global
+    from players import selected_players
+    players = selected_players()
 
     main()
 

### 2017-04-10 generate_data.py
Add script to generate cache.
Also modify things so that it reads the players in properly.

@@ -1,0 +1,139 @@
+from collections import defaultdict, Counter
+import csv
+import functools
+import multiprocessing
+import os
+
+import axelrod as axl
+#from approximate_moran import *
+
+def write_csv(outcomes, filename="outcomes.csv", append=False):
+    s = 'w'
+    if append:
+        s = 'a'
+    writer = csv.writer(open(filename, s))
+    for pair, counter in outcomes.items():
+        for scores, count in counter.items():
+            row = [pair[0], pair[1], scores[0], scores[1], count]
+            writer.writerow(row)
+
+def read_csv(filename="outcomes.csv"):
+    reader = csv.reader(open(filename))
+    outcomes = defaultdict(Counter)
+    for row in reader:
+        p1, p2, s1, s2, count = row
+        outcomes[(p1, p2)][(float(s1), float(s2))] = int(count)
+        outcomes[(p2, p1)][(float(s2), float(s1))] = int(count)
+    return outcomes
+
+def generate_matchups(players):
+    # Want the triangular product
+    for i in range(len(players)):
+        for j in range(i, len(players)):
+            if i == j:
+                yield players[i].clone(), players[j]
+            else:
+                yield players[i], players[j]
+
+def generate_matchups_indices(num_players):
+    # Want the triangular product
+    for i in range(num_players):
+        for j in range(i, num_players):
+            yield i, j
+
+def sample_match_outcomes(players, turns, repetitions, noise=0):
+    """
+    Play all matches between pairs of players and return a dictionary mapping
+    player names to outcomes.
+    """
+    match_outcomes = dict()
+    matchups = list(generate_matchups(players))
+
+    for pairs in matchups:
+
+        match = axl.Match(pairs, turns=turns, noise=noise)
+        rs = repetitions
+        if not match._stochastic:
+            rs = 1
+        outcomes = []
+        for _ in range(rs):
+            match.play()
+            outcomes.append(match.final_score_per_turn())
+
+        counts = Counter(outcomes)
+
+        player_names = tuple(map(str, pairs))
+        match_outcomes[player_names] = counts
+
+    return match_outcomes
+
+def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
+    """
+    Write the winner of a Moran process to file
+    """
+    if seed:
+        axl.seed(seed)  # Seed the process
+
+    pairs = (players[i].clone(), players[j].clone())
+    match = axl.Match(pairs, turns=turns, noise=noise)
[…]

### 2017-04-10 generate_data.py
Add script to generate cache.
Also modify things so that it reads the players in properly.

@@ -1,0 +1,139 @@
+from collections import defaultdict, Counter
+import csv
+import functools
+import multiprocessing
+import os
+
+import axelrod as axl
+#from approximate_moran import *
+
+def write_csv(outcomes, filename="outcomes.csv", append=False):
+    s = 'w'
+    if append:
+        s = 'a'
+    writer = csv.writer(open(filename, s))
+    for pair, counter in outcomes.items():
+        for scores, count in counter.items():
+            row = [pair[0], pair[1], scores[0], scores[1], count]
+            writer.writerow(row)
+
+def read_csv(filename="outcomes.csv"):
+    reader = csv.reader(open(filename))
+    outcomes = defaultdict(Counter)
+    for row in reader:
+        p1, p2, s1, s2, count = row
+        outcomes[(p1, p2)][(float(s1), float(s2))] = int(count)
+        outcomes[(p2, p1)][(float(s2), float(s1))] = int(count)
+    return outcomes
+
+def generate_matchups(players):
+    # Want the triangular product
+    for i in range(len(players)):
+        for j in range(i, len(players)):
+            if i == j:
+                yield players[i].clone(), players[j]
+            else:
+                yield players[i], players[j]
+
+def generate_matchups_indices(num_players):
+    # Want the triangular product
+    for i in range(num_players):
+        for j in range(i, num_players):
+            yield i, j
+
+def sample_match_outcomes(players, turns, repetitions, noise=0):
+    """
+    Play all matches between pairs of players and return a dictionary mapping
+    player names to outcomes.
+    """
+    match_outcomes = dict()
+    matchups = list(generate_matchups(players))
+
+    for pairs in matchups:
+
+        match = axl.Match(pairs, turns=turns, noise=noise)
+        rs = repetitions
+        if not match._stochastic:
+            rs = 1
+        outcomes = []
+        for _ in range(rs):
+            match.play()
+            outcomes.append(match.final_score_per_turn())
+
+        counts = Counter(outcomes)
+
+        player_names = tuple(map(str, pairs))
+        match_outcomes[player_names] = counts
+
+    return match_outcomes
+
+def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
+    """
+    Write the winner of a Moran process to file
+    """
+    if seed:
+        axl.seed(seed)  # Seed the process
+
+    pairs = (players[i].clone(), players[j].clone())
+    match = axl.Match(pairs, turns=turns, noise=noise)
[…]

### 2017-04-10 tex/main.tex

@@
 \usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
+\usepackage{hyperref}
 
@@
 
+A key point here is that the relative fitness of a strategy depends on the population distribution.
+The original Moran process assumes a relative fitness of r of one strategy over the other, giving a fixation probability for the starting population $(i, N-i)$ (when $r != 1$)
+
+\[ \rho = \frac{1 - r^{-i}}{1 - r^{-N}}\]
+and $\rho = 1 / N$ if $r=1$ (the neutral fixation probability).
+
+This corresponds to a game matrix [[1, 1], [r, r]] (or [[r, r], [1, 1]]), which is of course not what we have -- it's a little complicated because our "fitness" is not the payout from the game matrix, rather the sum of the total scores of all the interactions each round.
+So ALLC and TFT are neutral wrt to each other because they will have the same score each round, giving an effective fitness landscape $f(i, N-i) = A [i, N-i]^T$ given by the matrix $A = [[1,1],[1,1]]$.
+This means that noise and the number of turns per Moran round are significant parameters.
+I think we should fix the turns at 200; some recent authors run the turns to infinity (to reach stationarity on the sub-"Markov process" on the states (C, C), (C, D), (D, C), (D, D)) but we can't analytically compute the stationary distribution for strategies that use more than one round of memory (and it's not really a Markov process for more than one round of memory anyway).
+Plus it's unrealistic, and ultimately just amounts to a transform of the game matrix.
+
+To see if one strategy is not neutral with respect to another, we want to empirically measure the fixation probability and compare to the neutral rate.
+To do this right we need a lot of counts, since we're estimating a binomial probability p with variance $p(1-p) / k$ and $p$ is close to $1 / N$.
+To get the variance small you need something like $k>1000$ observations ( we can work out the precise requirements).
+
+Note we're not estimating $r$ for each strategy (pair) since we're in a frequency dependent situation, so we need to look at the population states (1, N-1) and (N-1, 1) for every pair of strategies, i.e.
+we can't assume that we're in a $\rho \leftrightarrow 1-\rho$ symmetry.
+More precisely, $\rho_{(1, N-1)} != 1 - \rho_{(N-1, 1)}$ in general.
+However we can (for fun) compute $r$ from $\rho$ with Newton's method (it's not easily invertable for $N > 3$), or take a Bayesian approach on what the distribution of $\rho$ is and then compute a distribution for $r$ in the usual way.
+
+A nice addition would be, for an interesting combination of strategies, to measure the fixation value for all $(i, N-i)$ and compare to the above formula for the value of $r$ derived from the $(1, N-1)$ case.
+This would show how much we deviate from frequency independence.
+
+Beyond the raw data, we should try to estimate the strategies that are
+1) most resistant to invasion
+2) the best invaders
+3) "most neutral"
+
+as a function of N across the entire population of strategies.
+This can really open up if you want to say optimize a parameterized strategy to be most resistant to invasion (a topic of future work, perhaps) -- for example Random(p) for what p is best?
+
+The existing notebook attempts to get at 1 and 2 by looking at the distributions of fixation probabilities for each strategy -- that's what the box plots for each N try to visualize for particular N, and the "Player Rankings by Median vs.
+Population Size" for how the cooperative strategies become more successful as N increases.
+That plot is the main takeaway IMO, and reinforces the "evolution of cooperation" narrative that's so popular.
+We can tie back to Press and Dyson here -- yes, ZD strategies are good Head-to-Head and in small populations, but they aren't great when the population size gets bigger.
+How much bigger?
+Even at N=4 there is a dramatic decline for ZD-extort.
+Note that this goes against the claims of Stewart and Plotkin (they claimed that ZD strategies basically dominate the Moran process no matter how much memory you allow).
+This also matches our tournament results -- ZD strategies win matches but not tournaments.
+
+It would be great to see how the ensemble strategies (meta strategies) fare, if we don't mind burning the CPU cycles. I left them out of my initial analysis.
+
+Further Variants (possible additions or future papers):
+* Noise
+* Spatial structure
+* More than two types in the population
+* Modified Moran processes (e.g. Fermi selection with the strength of selection coefficient)
+* Altered game matrices
+
+Noise is especially interesting because a lot of the cooperative strategies are going to appear neutral to each other (since neither will cast a D unprovoked).
+A little bit of noise should shuffle the ranks around quite a bit, and show off the abilities of e.g.
+OmegaTFT.
+Might be worth including at least one of the "Player Rankings by Median vs.
+Population Size" plots for some value of noise (such as 0.05).
+
+More future work:
+* Mutation -- for mutation we no longer have fixation, rather a stationary distribution.
+This may require some more programming to compute efficiently (perhaps my stationary library).
+There's a lot of interesting work to do here.
+
+I think we'd want to include a few of the heatmaps in the final section of the notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
+Pushing N higher will make all the plots more interesting.
+How high we can get N?
+I'd really like to get it to N >= 12.
+
 Structure:
@@
     \item Overview of Moran processes;
-    \item Review of the literature;
+    \item Review of the literature (\cite{Lee2015, Nowak});
     \item Short discussion about the Axelrod library.
 \end{itemize}
+
+I'm happy to write this section. We can lift some references from one of my papers on the Moran process.
 
@@
 
+\bibliographystyle{plain}
+\bibliography{./bibliography.bib}
 \end{document}

### 2017-04-10 src/generate_cache.py
Suggest structure of repo in the README.md

@@ -122,8 +122,8 @@ if __name__ == "__main__":
     print(len(list(map(str, players))))
 
     try:
-        os.remove("outcomes.csv")
-        os.remove("outcomes_noise.csv")
+        os.remove("../data/outcomes.csv")
+        os.remove("../data/outcomes_noise.csv")
     except FileNotFoundError:
         pass
 
@@ -131,9 +131,9 @@ if __name__ == "__main__":
     turns = 200
 
     sample_match_outcomes_parallel(turns=turns, repetitions=repetitions,
-                                   filename="outcomes.csv", noise=0,
+                                   filename="../data/outcomes.csv", noise=0,
                                    processes=4)
 
     sample_match_outcomes_parallel(turns=turns, repetitions=repetitions,
-                                   filename="outcomes_noise.csv", noise=0.05,
+                                   filename="../data/outcomes_noise.csv", noise=0.05,
                                    processes=4)

### 2017-04-10 execute.sh
Reorganise python files.

@@ -1,6 +1,0 @@
-#!/bin/bash
-for i in `seq 2 5`;
-do
-    echo $i
-    python moran.py $i
-done

### 2017-04-10 tex/main.tex
Add section describing methodology.

@@
 \usepackage{hyperref}
+\usepackage{multicol}
+\usepackage{booktabs}
+\usepackage{xstring}
+\usepackage{subcaption}
+\usepackage{graphicx}
 
@@
 Iterated Prisoner's Dilemma}
-\author{Marc Harper and Vincent Knight}
+\author{Marc Harper \and Vincent Knight}
 \date{}
@@
 
-A key point here is that the relative fitness of a strategy depends on the population distribution.
-The original Moran process assumes a relative fitness of r of one strategy over the other, giving a fixation probability for the starting population $(i, N-i)$ (when $r != 1$)
+A key point here is that the relative fitness of a strategy depends on the
+population distribution. The original Moran process assumes a relative fitness
+of r of one strategy over the other, giving a fixation probability for the
+starting population $(i, N-i)$ (when $r != 1$)
 
@@
 
-This corresponds to a game matrix [[1, 1], [r, r]] (or [[r, r], [1, 1]]), which is of course not what we have -- it's a little complicated because our "fitness" is not the payout from the game matrix, rather the sum of the total scores of all the interactions each round.
-So ALLC and TFT are neutral wrt to each other because they will have the same score each round, giving an effective fitness landscape $f(i, N-i) = A [i, N-i]^T$ given by the matrix $A = [[1,1],[1,1]]$.
-This means that noise and the number of turns per Moran round are significant parameters.
-I think we should fix the turns at 200; some recent authors run the turns to infinity (to reach stationarity on the sub-"Markov process" on the states (C, C), (C, D), (D, C), (D, D)) but we can't analytically compute the stationary distribution for strategies that use more than one round of memory (and it's not really a Markov process for more than one round of memory anyway).
-Plus it's unrealistic, and ultimately just amounts to a transform of the game matrix.
+This corresponds to a game matrix [[1, 1], [r, r]] (or [[r, r], [1, 1]]), which
+is of course not what we have -- it's a little complicated because our "fitness"
+is not the payout from the game matrix, rather the sum of the total scores of
+all the interactions each round. So ALLC and TFT are neutral wrt to each other
+because they will have the same score each round, giving an effective fitness
+landscape $f(i, N-i) = A [i, N-i]^T$ given by the matrix $A = [[1,1],[1,1]]$.
+This means that noise and the number of turns per Moran round are significant
+parameters. I think we should fix the turns at 200; some recent authors run the
+turns to infinity (to reach stationarity on the sub-"Markov process" on the
+states (C, C), (C, D), (D, C), (D, D)) but we can't analytically compute the
+stationary distribution for strategies that use more than one round of memory
+(and it's not really a Markov process for more than one round of memory anyway).
+Plus it's unrealistic, and ultimately just amounts to a transform of the game
+matrix.
 
-To see if one strategy is not neutral with respect to another, we want to empirically measure the fixation probability and compare to the neutral rate.
-To do this right we need a lot of counts, since we're estimating a binomial probability p with variance $p(1-p) / k$ and $p$ is close to $1 / N$.
-To get the variance small you need something like $k>1000$ observations ( we can work out the precise requirements).
+To see if one strategy is not neutral with respect to another, we want to
+empirically measure the fixation probability and compare to the neutral rate. To
+do this right we need a lot of counts, since we're estimating a binomial
+probability p with variance $p(1-p) / k$ and $p$ is close to $1 / N$. To get the
+variance small you need something like $k>1000$ observations ( we can work out
+the precise requirements).
 
-Note we're not estimating $r$ for each strategy (pair) since we're in a frequency dependent situation, so we need to look at the population states (1, N-1) and (N-1, 1) for every pair of strategies, i.e.
-we can't assume that we're in a $\rho \leftrightarrow 1-\rho$ symmetry.
-More precisely, $\rho_{(1, N-1)} != 1 - \rho_{(N-1, 1)}$ in general.
-However we can (for fun) compute $r$ from $\rho$ with Newton's method (it's not easily invertable for $N > 3$), or take a Bayesian approach on what the distribution of $\rho$ is and then compute a distribution for $r$ in the usual way.
+Note we're not estimating $r$ for each strategy (pair) since we're in a
+frequency dependent situation, so we need to look at the population states (1,
+N-1) and (N-1, 1) for every pair of strategies, i.e. we can't assume that we're
+in a $\rho \leftrightarrow 1-\rho$ symmetry. More precisely, $\rho_{(1, N-1)} !=
+1 - \rho_{(N-1, 1)}$ in general. However we can (for fun) compute $r$ from
+$\rho$ with Newton's method (it's not easily invertable for $N > 3$), or take a
+Bayesian approach on what the distribution of $\rho$ is and then compute a
+distribution for $r$ in the usual way.
 
-A nice addition would be, for an interesting combination of strategies, to measure the fixation value for all $(i, N-i)$ and compare to the above formula for the value of $r$ derived from the $(1, N-1)$ case.
-This would show how much we deviate from frequency independence.
+A nice addition would be, for an interesting combination of strategies, to
+measure the fixation value for all $(i, N-i)$ and compare to the above formula
+for the value of $r$ derived from the $(1, N-1)$ case. This would show how much
+we deviate from frequency independence.
 
@@
 
-as a function of N across the entire population of strategies.
-This can really open up if you want to say optimize a parameterized strategy to be most resistant to invasion (a topic of future work, perhaps) -- for example Random(p) for what p is best?
+as a function of N across the entire population of strategies. This can really
+open up if you want to say optimize a parameterized strategy to be most
+resistant to invasion (a topic of future work, perhaps) -- for example Random(p)
+for what p is best?
 
-The existing notebook attempts to get at 1 and 2 by looking at the distributions of fixation probabilities for each strategy -- that's what the box plots for each N try to visualize for particular N, and the "Player Rankings by Median vs.
-Population Size" for how the cooperative strategies become more successful as N increases.
-That plot is the main takeaway IMO, and reinforces the "evolution of cooperation" narrative that's so popular.
-We can tie back to Press and Dyson here -- yes, ZD strategies are good Head-to-Head and in small populations, but they aren't great when the population size gets bigger.
-How much bigger?
-Even at N=4 there is a dramatic decline for ZD-extort.
-Note that this goes against the claims of Stewart and Plotkin (they claimed that ZD strategies basically dominate the Moran process no matter how much memory you allow).
-This also matches our tournament results -- ZD strategies win matches but not tournaments.
+The existing notebook attempts to get at 1 and 2 by looking at the distributions
+of fixation probabilities for each strategy -- that's what the box plots for
+each N try to visualize for particular N, and the "Player Rankings by Median vs.
+Population Size" for how the cooperative strategies become more successful as N
+increases. That plot is the main takeaway IMO, and reinforces the "evolution of
+cooperation" narrative that's so popular. We can tie back to Press and Dyson
+here -- yes, ZD strategies are good Head-to-Head and in small populations, but
+they aren't great when the population size gets bigger. How much bigger? Even at
+N=4 there is a dramatic decline for ZD-extort. Note that this goes against the
+claims of Stewart and Plotkin (they claimed that ZD strategies basically
+dominate the Moran process no matter how much memory you allow). This also
+matches our tournament results -- ZD strategies win matches but not tournaments.
 
-It would be great to see how the ensemble strategies (meta strategies) fare, if we don't mind burning the CPU cycles. I left them out of my initial analysis.
+It would be great to see how the ensemble strategies (meta strategies) fare, if
+we don't mind burning the CPU cycles. I left them out of my initial analysis.
 
-Further Variants (possible additions or future papers):
-* Noise
-* Spatial structure
-* More than two types in the population
-* Modified Moran processes (e.g. Fermi selection with the strength of selection coefficient)
-* Altered game matrices
+Further Variants (possible additions or future papers): * Noise * Spatial
+structure * More than two types in the population * Modified Moran processes
+(e.g. Fermi selection with the strength of selection coefficient) * Altered game
+matrices
 
-Noise is especially interesting because a lot of the cooperative strategies are going to appear neutral to each other (since neither will cast a D unprovoked).
-A little bit of noise should shuffle the ranks around quite a bit, and show off the abilities of e.g.
-OmegaTFT.
-Might be worth including at least one of the "Player Rankings by Median vs.
-Population Size" plots for some value of noise (such as 0.05).
+Noise is especially interesting because a lot of the cooperative strategies are
+going to appear neutral to each other (since neither will cast a D unprovoked).
+A little bit of noise should shuffle the ranks around quite a bit, and show off
+the abilities of e.g. OmegaTFT. Might be worth including at least one of the
+"Player Rankings by Median vs. Population Size" plots for some value of noise
+(such as 0.05).
 
-More future work:
-* Mutation -- for mutation we no longer have fixation, rather a stationary distribution.
-This may require some more programming to compute efficiently (perhaps my stationary library).
-There's a lot of interesting work to do here.
+More future work: * Mutation -- for mutation we no longer have fixation, rather
+a stationary distribution. This may require some more programming to compute
+efficiently (perhaps my stationary library). There's a lot of interesting work
+to do here.
 
-I think we'd want to include a few of the heatmaps in the final section of the notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
-Pushing N higher will make all the plots more interesting.
-How high we can get N?
-I'd really like to get it to N >= 12.
+Ip think we'd want to include a few of the heatmaps in the final section of the
+notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
+Pushing N higher will make all the plots more interesting. How high we can get
+N? I'd really like to get it to N >= 11.
 
@@
 
-I'm happy to write this section. We can lift some references from one of my papers on the Moran process.
+I'm happy to write this section. We can lift some references from one of my
+papers on the Moran process.
+
+\section{Methodology}\label{sec:methodology}
+
+To carry out this large numerical experiment 172 strategies are used from
+\cite{axelrodproject}. These include 169 default strategies in the library at
+the time (excluding strategies classified as having a long run time) as well as
+the following 3 finite state machine strategies:
+
+% TODO Include details about the 3 extra FSM strategies.
+
+Appendix~\ref{app:list_of_players} shows all the players in question. More
+information about each player can be obtained in the documentation for
+\cite{axelrodproject}. The memory depth of the used strategies is shown in
+Table~\ref{tbl:memory_depth_count}.
+
+\begin{table}[!hbtp]
+    \centering
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/memory_depth_count.tex}
+                \caption{Memory depth}
+                \label{tbl:memory_depth_count}
+        \end{subfigure}
+        \vspace{.5cm}
+
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/stochastic_count.tex}
+                \caption{Stochastic versus deterministic}
+                \label{tbl:stochastic_count}
+        \end{subfigure}
+        \caption{Summary of properties of used strategies}
+\end{table}
+
+All strategies are paired and these pairs are used in 1000 repetitions of a
+Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
+for even \(N\) between 2 and 14. The fixation probability is then estimated for
+each value of \(N\).
+
+Note that due to the high computational cost of these experiments, for any given
+interaction between two players within the Moran process the outcome is sampled
+from a pre computed cache of 10000 match outcomes. This is carried out using the
+approximate Moran process implemented in \cite{axelrodproject}.
+
+As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
+between two players that over the 10000 outcomes gives 6817 different scores.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.4\textwidth]{../img/players_with_most_scores.pdf}
+    \caption{All possible scores for the pair of strategies that have the most
+    different number of match outcomes}
+    \label{fig:players_with_most_scores}
+\end{figure}
 
@@
 \bibliography{./bibliography.bib}
+
+\appendix
+
+\section{List of players}\label{app:list_of_players}
+
+\begin{multicols}{3}
+	\begin{enumerate}
+		\input{../tbl/list_of_players.tex}
+	\end{enumerate}
+\end{multicols}
+
 \end{document}

### 2017-04-11 generate_data.py
Add an exception.
I'm hunting down a bug.

@@ -69,7 +69,7 @@ def sample_match_outcomes(players, turns, repetitions, noise=0):
 
 def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
     """
-    Write the winner of a Moran process to file
+    Write the outcome of a match to file.
     """
     if seed:
         axl.seed(seed)  # Seed the process
@@ -81,8 +81,11 @@ def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
         rs = 1
     outcomes = []
     for _ in range(rs):
-        match.play()
-        outcomes.append(match.final_score_per_turn())
+        try:
+            match.play()
+            outcomes.append(match.final_score_per_turn())
+        except KeyError:
+            print(turns, repetitions, noise, i, j, seed)
 
     counts = Counter(outcomes)
     player_names = tuple(map(str, pairs))
@@ -127,8 +130,8 @@ if __name__ == "__main__":
     except FileNotFoundError:
         pass
 
-    repetitions = 10000
-    turns = 200
+    repetitions = 200
+    turns = 50
 
     sample_match_outcomes_parallel(turns=turns, repetitions=repetitions,
                                    filename="outcomes.csv", noise=0,

### 2017-04-11 generate_data.py
Add an exception.
I'm hunting down a bug.

@@ -1,139 +1,0 @@
-from collections import defaultdict, Counter
-import csv
-import functools
-import multiprocessing
-import os
-
-import axelrod as axl
-#from approximate_moran import *
-
-def write_csv(outcomes, filename="outcomes.csv", append=False):
-    s = 'w'
-    if append:
-        s = 'a'
-    writer = csv.writer(open(filename, s))
-    for pair, counter in outcomes.items():
-        for scores, count in counter.items():
-            row = [pair[0], pair[1], scores[0], scores[1], count]
-            writer.writerow(row)
-
-def read_csv(filename="outcomes.csv"):
-    reader = csv.reader(open(filename))
-    outcomes = defaultdict(Counter)
-    for row in reader:
-        p1, p2, s1, s2, count = row
-        outcomes[(p1, p2)][(float(s1), float(s2))] = int(count)
-        outcomes[(p2, p1)][(float(s2), float(s1))] = int(count)
-    return outcomes
-
-def generate_matchups(players):
-    # Want the triangular product
-    for i in range(len(players)):
-        for j in range(i, len(players)):
-            if i == j:
-                yield players[i].clone(), players[j]
-            else:
-                yield players[i], players[j]
-
-def generate_matchups_indices(num_players):
-    # Want the triangular product
-    for i in range(num_players):
-        for j in range(i, num_players):
-            yield i, j
-
-def sample_match_outcomes(players, turns, repetitions, noise=0):
-    """
-    Play all matches between pairs of players and return a dictionary mapping
-    player names to outcomes.
-    """
-    match_outcomes = dict()
-    matchups = list(generate_matchups(players))
-
-    for pairs in matchups:
-
-        match = axl.Match(pairs, turns=turns, noise=noise)
-        rs = repetitions
-        if not match._stochastic:
-            rs = 1
-        outcomes = []
-        for _ in range(rs):
-            match.play()
-            outcomes.append(match.final_score_per_turn())
-
-        counts = Counter(outcomes)
-
-        player_names = tuple(map(str, pairs))
-        match_outcomes[player_names] = counts
-
-    return match_outcomes
-
-def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
-    """
-    Write the winner of a Moran process to file
-    """
-    if seed:
-        axl.seed(seed)  # Seed the process
-
-    pairs = (players[i].clone(), players[j].clone())
-    match = axl.Match(pairs, turns=turns, noise=noise)
[…]

### 2017-04-11 src/generate_cache.py

@@ -80,9 +80,13 @@ def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
     if not match._stochastic and noise == 0:
         rs = 1
     outcomes = []
+
     for _ in range(rs):
-        match.play()
-        outcomes.append(match.final_score_per_turn())
+        try:
+            match.play()
+            outcomes.append(match.final_score_per_turn())
+        except KeyError:
+            print(turns, repetitions, noise, i, j, seed)
 
     counts = Counter(outcomes)
     player_names = tuple(map(str, pairs))

### 2017-04-11 src/generate_cache.py
Revert "Add an exception."
This reverts commit c56751547744ff95578e2063aeb87a5b3eb8aa11.

@@ -80,13 +80,9 @@ def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
     if not match._stochastic and noise == 0:
         rs = 1
     outcomes = []
-
     for _ in range(rs):
-        try:
-            match.play()
-            outcomes.append(match.final_score_per_turn())
-        except KeyError:
-            print(turns, repetitions, noise, i, j, seed)
+        match.play()
+        outcomes.append(match.final_score_per_turn())
 
     counts = Counter(outcomes)
     player_names = tuple(map(str, pairs))

### 2017-04-11 src/generate_cache.py
Use the generator for indices.

@@ -28,12 +28,11 @@ def read_csv(filename="outcomes.csv"):
 
 def generate_matchups(players):
     # Want the triangular product
-    for i in range(len(players)):
-        for j in range(i, len(players)):
-            if i == j:
-                yield players[i].clone(), players[j]
-            else:
-                yield players[i], players[j]
+    for i, j in generate_matchups_indices(len(players)):
+        if i == j:
+            yield players[i].clone(), players[j]
+        else:
+            yield players[i], players[j]
 
 def generate_matchups_indices(num_players):
     # Want the triangular product

### 2017-04-11 tex/main.tex
Add an abstract.

@@
 
-\abstract{TBD}
+\abstract{The Iterated Prisoner's Dilemma is a well established framework for
+          the study of emergent behaviour. In this paper an extensive numerical
+          study of the evolutionary dynamics of this framework are presented.
+
+          Fixation probabilities for Moran processes are obtained for 172
+          different strategies. This is done in both a standard 200 turn
+          interaction and a noisy setting.
+
+          To the authors knowledge this is the largest
+          such study. It allows for insights about the behaviour and
+          performance of strategies with regard to their survival in an
+          evolutionary setting.
+          }  % TODO Add main conclusion/finding.
 

### 2017-04-11 tex/main.tex
Move to biblatex.
Add a validation section.
- Added a theoretic script (with tests)
- Modified Moran
- Written validation component in notebook.

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+
+\usepackage[backend=biber, firstinits=false, backref=false, url=true,
+            isbn=true, style=numeric]{biblatex}
+\addbibresource{bibliography.bib}
 
@@
        Iterated Prisoner's Dilemma}
-\author{Marc Harper \and Vincent Knight}
+\author{Marc Harper \and Vincent Knight} % TODO Authors?
 \date{}
@@
     \item Overview of Moran processes;
-    \item Review of the literature (\cite{Lee2015, Nowak});
+    \item Review of the literature (\cite{Lee2015, Nowak, Moran1957});
     \item Short discussion about the Axelrod library.
@@
 
-Structure:
+As described in \cite{Nowak} Consider the payoff matrix:
 
-\begin{itemize}
-    \item Compute fitness landscape for some strategy pairs;
-    \item Verify against the data;
-\end{itemize}
+\begin{equation}\label{equ:payoff_matrix}
+    M = \begin{pmatrix}
+        a, b\\
+        c, d
+        \end{pmatrix}
+\end{equation}
+
+The expected payoffs of \(i\) players of the first type in a population with \(N
+- i\) players of the second type are given by:
+
+\begin{equation}\label{equ:expected_payoff_one}
+    F_i = \frac{a(i - 1) + b(N - i)}{N - 1}
+\end{equation}
+
+\begin{equation}\label{equ:expected_payoff_two}
+    G_i = \frac{ci + d(N - i - 1)}{N - 1}
+\end{equation}
+
+With an intensity of selection \(\omega\) the fitness of both strategies is
+given by:
+
+\begin{equation}\label{equ:expected_payoff_one}
+    f_i = 1 - \omega + \omega F_i
+\end{equation}
+
+\begin{equation}\label{equ:expected_payoff_two}
+    g_i = 1 - \omega + \omega G_i
+\end{equation}
+
+The transitions within the birth death process that underpins the Moran process
+are then given by:
+
+\begin{align}
+	p_{i, i+1}&= \frac{if_i}{if_i+(N-i)g_i}\frac{N-i}{N}\label{equ:p_up}\\
+	p_{i, i-1}&= \frac{(N-i)g_i}{if_i+(N-i)g_i}\frac{i}{N}\label{equ:p_down}\\
+	p_{ii} &= 1 - p_{i, i+1} - p_{i, i-1}\label{equ:p_stay}
+\end{align}
+
+Using this it is a known result that the fixation probability of the first
+strategy in a population of \(i\) individuals of the first type (and \(N-i\)
+individuals of the second. We have:
+
+\begin{equation}\label{equ:fixation_probability}
+x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}\prod_{k=1}^{j}\gamma_j}
+\end{equation}
+
+where:
+
+\[
+\gamma_j = \frac{p_{j, j-1}}{p_{j, j+1}}
+\]
+
+Using this comparisons of \(x_{N/2}\) are shown in
+Figure~\ref{fig:comparison_deterministic}. Note that these are all deterministic
+strategies and show a perfect match up between the expected value of
+(\ref{equ:fixation_probability}) and the actual Moran process.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_1000_repetitions.pdf}
+        \caption{Alternator and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_1000_repetitions.pdf}
+        \caption{Alternator and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_1000_repetitions.pdf}
+        \caption{Alternator and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat_1000_repetitions.pdf}
+        \caption{Cooperator and Tit For Tat}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator_1000_repetitions.pdf}
+        \caption{Defector and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat_1000_repetitions.pdf}
+        \caption{Defector and Tit For Tat}
+    \end{subfigure}%
+    \caption{Comparison of theoretic and actual Moran Process fixation probabilities for \textbf{deterministic} strategies}
+    \label{fig:comparison_deterministic}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Cooperator_1000_repetitions.pdf}
+        \caption{Random and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Defector_1000_repetitions.pdf}
+        \caption{Random and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Tit_For_Tat_1000_repetitions.pdf}
+        \caption{Random and Tit For Tat}
+    \end{subfigure}%
+    % TODO Input more of these
+    \caption{Comparison of theoretic and actual Moran Process fixation probabilities for \textbf{stochastic} strategies}
+    \label{fig:comparison_stochastic}
+\end{figure}
+
+Figure~\ref{fig_comparison_stochastic} shows the fixation probabilities for
+stochastic strategies. These are no longer a good match which highlights the
+weakness of the analytical formulae the relies on the average payoffs. A
+detailed analysis of the 172 strategies considered will be shown in the next
+Section.
 
@@
 
-\bibliographystyle{plain}
-\bibliography{./bibliography.bib}
+\printbibliography
 

### 2017-04-11 src/moran.py

@@ -13,7 +13,7 @@ import axelrod as axl
 import pandas as pd
 
 from axelrod import ApproximateMoranProcess, Pdf
-from generate_data import read_csv
+from generate_cache import read_csv
 
 # For tests
 import collections

### 2017-04-11 src/theoretic.py

@@ -1,0 +1,135 @@
+"""
+Code to calculate analytic fixation probabilities
+"""
+import unittest
+import numpy as np
+import math
+
+def scores(strategy_pair, utilities):
+    """
+    Return the fitness scores:
+
+        [a, b]
+        [c, d]
+
+    for a pair of strategies, in a population of N individuals
+    with i individuals of the first type.
+    """
+    try:
+        s1, s2 = strategy_pair
+        m = np.array([[utilities[(s1, s1)][0], utilities[(s1, s2)][0]],
+                      [utilities[(s1, s2)][1], utilities[(s2, s2)][0]]])
+    except KeyError:
+        s2, s1 = strategy_pair
+        m = np.array([[utilities[(s2, s2)][0], utilities[(s1, s2)][1]],
+                      [utilities[(s1, s2)][0], utilities[(s1, s1)][0]]])
+    return m
+
+def fitness(strategy_pair, N, i, utilities):
+    """
+    Return the nowak fitness of a strategy pair in a population with
+    N total individuals and i individuals of the first type.
+    """
+    m = scores(strategy_pair, utilities)
+
+    f = (m[0, 0] * (i - 1) + m[0, 1] * (N - i)) / (N - 1)
+    g = (m[1, 0] * i + m[1, 1] * (N - i - 1)) / (N - 1)
+
+    return f, g
+
+def nowak_fitness(strategy_pair, N, i, utilities, selection_intensity=1):
+    """
+    Return the nowak fitness of a strategy pair in a population with
+    N total individuals and i individuals of the first type.
+    """
+    F, G = [1 + selection_intensity * (k - 1) for k in fitness(strategy_pair, N, i, utilities)]
+
+    return F, G
+
+def fermi_fitness(strategy_pair, N, i, utilities, selection_intensity=1):
+    """
+    Return the fermi fitness of a strategy pair in a population with
+    N total individuals and i individuals of the first type.
+    """
+    F, G = [math.exp(k) for k in fitness(strategy_pair, N, i, utilities)]
+
+    return F / (F + G), G / (F + G)
+
+def transition(strategy_pair, N, i, utilities, fitness_type="nowak",
+	       selection_intensity=1):
+    """
+    Return the 3 transition probabilities:
+
+    P[i, i - 1]
+    P[i, i]
+    P[i, i + 1]
+
+    Assuming:
+     - a given stratgy pair,
+     - a given total population size N
+     - and a state i (the number of individuals of the first type)
+    """
[…]

### 2017-04-11 generate_data.py
Remove unneeded script.

@@ -1,139 +1,0 @@
-from collections import defaultdict, Counter
-import csv
-import functools
-import multiprocessing
-import os
-
-import axelrod as axl
-#from approximate_moran import *
-
-def write_csv(outcomes, filename="outcomes.csv", append=False):
-    s = 'w'
-    if append:
-        s = 'a'
-    writer = csv.writer(open(filename, s))
-    for pair, counter in outcomes.items():
-        for scores, count in counter.items():
-            row = [pair[0], pair[1], scores[0], scores[1], count]
-            writer.writerow(row)
-
-def read_csv(filename="outcomes.csv"):
-    reader = csv.reader(open(filename))
-    outcomes = defaultdict(Counter)
-    for row in reader:
-        p1, p2, s1, s2, count = row
-        outcomes[(p1, p2)][(float(s1), float(s2))] = int(count)
-        outcomes[(p2, p1)][(float(s2), float(s1))] = int(count)
-    return outcomes
-
-def generate_matchups(players):
-    # Want the triangular product
-    for i in range(len(players)):
-        for j in range(i, len(players)):
-            if i == j:
-                yield players[i].clone(), players[j]
-            else:
-                yield players[i], players[j]
-
-def generate_matchups_indices(num_players):
-    # Want the triangular product
-    for i in range(num_players):
-        for j in range(i, num_players):
-            yield i, j
-
-def sample_match_outcomes(players, turns, repetitions, noise=0):
-    """
-    Play all matches between pairs of players and return a dictionary mapping
-    player names to outcomes.
-    """
-    match_outcomes = dict()
-    matchups = list(generate_matchups(players))
-
-    for pairs in matchups:
-
-        match = axl.Match(pairs, turns=turns, noise=noise)
-        rs = repetitions
-        if not match._stochastic:
-            rs = 1
-        outcomes = []
-        for _ in range(rs):
-            match.play()
-            outcomes.append(match.final_score_per_turn())
-
-        counts = Counter(outcomes)
-
-        player_names = tuple(map(str, pairs))
-        match_outcomes[player_names] = counts
-
-    return match_outcomes
-
-def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
-    """
-    Write the winner of a Moran process to file
-    """
-    if seed:
-        axl.seed(seed)  # Seed the process
-
-    pairs = (players[i].clone(), players[j].clone())
-    match = axl.Match(pairs, turns=turns, noise=noise)
[…]

### 2017-04-12 tex/main.tex
Move some of Marc's notes for further work.
Moving these to the conclusion.
Write introductory paragraph.
Highlighting the differences with a classic Moran process.

@@
           evolutionary setting.
-          }  % TODO Add main conclusion/finding.
+\end{abstract}  % TODO Add main conclusion/finding.
 
@@
 
-Main questions are:
+Since the formulation of the Moran Process in \cite{Moran1957}, this model of
+evolutionary population dynamics has been used to gain insights about the
+evolutionary stability of strategies in a number of settings. Similarly since
+the first Iterated Prisoner's Dilemma (IPD) tournament described in
+\cite{Axelrod1980a} the Prisoner's dilemma has been used to understand the
+evolution of cooperative behaviour in complex systems.
+
+The analytical models of a Moran process are based on the relative fitness
+between two strategies and take this to be a fixed value \(r\) \cite{Nowak}.
+This is a valid model for simple strategies of the Prisoner's Dilemma such as to
+\textit{always cooperate} or \textit{always defect}. This manuscript provides a
+detailed numerical analysis of \textbf{172} complex and adaptive strategies for
+the IPD\@. In this case the relative fitness of a strategy is dependent on the
+population distribution.
+
+This provides answers to the following questions:
 
@@
     \item What strategies are good at resisting invasion?
-    \item How do 1 and 2 change as a function of population size?
+    \item How does the population size affect these findings?
 \end{enumerate}
-
-A key point here is that the relative fitness of a strategy depends on the
-population distribution. The original Moran process assumes a relative fitness
-of r of one strategy over the other, giving a fixation probability for the
-starting population $(i, N-i)$ (when $r != 1$)
 
@@
 
-Beyond the raw data, we should try to estimate the strategies that are
-1) most resistant to invasion
-2) the best invaders
-3) "most neutral"
-
-as a function of N across the entire population of strategies. This can really
-open up if you want to say optimize a parameterized strategy to be most
-resistant to invasion (a topic of future work, perhaps) -- for example Random(p)
-for what p is best?
-
 The existing notebook attempts to get at 1 and 2 by looking at the distributions
@@
 we don't mind burning the CPU cycles. I left them out of my initial analysis.
-
-Further Variants (possible additions or future papers): * Noise * Spatial
-structure * More than two types in the population * Modified Moran processes
-(e.g. Fermi selection with the strength of selection coefficient) * Altered game
-matrices
-
-Noise is especially interesting because a lot of the cooperative strategies are
-going to appear neutral to each other (since neither will cast a D unprovoked).
-A little bit of noise should shuffle the ranks around quite a bit, and show off
-the abilities of e.g. OmegaTFT. Might be worth including at least one of the
-"Player Rankings by Median vs. Population Size" plots for some value of noise
-(such as 0.05).
 
@@
 
+Beyond the raw data, we should try to estimate the strategies that are
+1) most resistant to invasion
+2) the best invaders
+3) "most neutral"
+
+as a function of N across the entire population of strategies. This can really
+open up if you want to say optimize a parameterized strategy to be most
+resistant to invasion (a topic of future work, perhaps) -- for example Random(p)
+for what p is best?
+
+Further Variants (possible additions or future papers): * Noise * Spatial
+structure * More than two types in the population * Modified Moran processes
+(e.g. Fermi selection with the strength of selection coefficient) * Altered game
+matrices
+
+Noise is especially interesting because a lot of the cooperative strategies are
+going to appear neutral to each other (since neither will cast a D unprovoked).
+A little bit of noise should shuffle the ranks around quite a bit, and show off
+the abilities of e.g. OmegaTFT. Might be worth including at least one of the
+"Player Rankings by Median vs. Population Size" plots for some value of noise
+(such as 0.05).
+
 \printbibliography

### 2017-04-12 tex/main.tex
Make minor adjustment to abstract.

@@
 
-\abstract{The Iterated Prisoner's Dilemma is a well established framework for
+\begin{abstract}
+    The Iterated Prisoner's Dilemma is a well established framework for
           the study of emergent behaviour. In this paper an extensive numerical
@@
 
-I'm happy to write this section. We can lift some references from one of my
-papers on the Moran process.
+Some work has looked at evolutionary stability of strategies within the
+Prisoner's Dilemma \cite{Li2014} but this is not done in the more widely used
+setting of the Moran process but in terms of infinite population stability.
+
+In \cite{Baek2016} Moran processes are looked at in a theoretic framework for a
+small subset of strategies.
+
+In \cite{Lee2015} machine learning techniques are used to train a strategy
+capable of resisting invasion and also invade any memory one strategy.
 

### 2017-04-12 tex/main.tex
Adding discussion about noise and more imgs.

@@
 
-This provides answers to the following questions:
+Further deviations from the analytical model occur when interactions between
+players are subject to uncertainty. This is referred to as noise and has been
+considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}. Noise is
+also considered here.
+
+This work provides answers to the following questions:
 
@@
     \end{subfigure}%
-    % TODO Input more of these
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator_1000_repetitions.pdf}
+        \caption{All C or all D and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector_1000_repetitions.pdf}
+        \caption{All C or all D and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_0_5_1000_repetitions.pdf}
+        \caption{Calculator and Random}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD_1000_repetitions.pdf}
+        \caption{Calculator and All C or all D}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner_1000_repetitions.pdf}
+        \caption{Calculator and Arrogant Q learner}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat_1000_repetitions.pdf}
+        \caption{All C or all D and Tit For Tat}
+    \end{subfigure}%
     \caption{Comparison of theoretic and actual Moran Process fixation probabilities for \textbf{stochastic} strategies}
@@
 
-Figure~\ref{fig_comparison_stochastic} shows the fixation probabilities for
+Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
 stochastic strategies. These are no longer a good match which highlights the

### 2017-04-12 src/draw_validation_plots.py
Move validation plots to src.
These take a long time to run: not suitable for nbs.

@@ -1,0 +1,116 @@
+"""
+A script to draw the validation plots.
+"""
+import pandas as pd
+import axelrod as axl
+import matplotlib.pyplot as plt
+
+import generate_cache
+import theoretic
+
+import functools
+import multiprocessing
+
+
+def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
+                       cachefile=None):
+    """Run a Moran process and obtain the fixation probabilities"""
+    if cachefile is None:
+        cachefile = "../data/outcomes.csv"
+
+    cache = generate_cache.read_csv(cachefile)
+    for k, v in cache.items():
+        cache[k] = axl.Pdf(v)
+
+    players = []
+    for _ in range(i):
+        players.append(strategy_pair[0])
+    for _ in range(N - i):
+        players.append(strategy_pair[1])
+    mp = axl.ApproximateMoranProcess(players, cached_outcomes=cache)
+
+    win_count = 0
+    for seed in range(repetitions):
+        axl.seed(seed)
+        mp.reset()
+        mp.play()
+        if mp.winning_strategy_name == players[0].name:
+            win_count += 1
+
+    return win_count / repetitions
+
+
+def plot_theoretic_vs_simulated(max_N, repetitions, utilities, player1, player2):
+    """
+    Plot the theoretic value vs the simulated value
+    """
+    players = (player1, player2)
+    ns = range(2, max_N + 1, 2)
+    repetitions = repetitions
+
+    player_names = [p.__repr__() for p in players]
+    calculated = [theoretic.fixation(player_names, n, n // 2,
+                                     utilities=utilities)
+                 for n in ns]
+    simulated = [simulated_fixation(players,  n, n // 2,
+                                    repetitions=repetitions)
+                 for n in ns]
+    plt.figure()
+    plt.plot(ns, calculated, label="Theoretic $x_{N/2}$")
+    plt.scatter(ns, simulated, label="Simulated $x_{N/2}$")
+
+
+    plt.xlabel("Population size $N$")
+    plt.title("Fixation probability for {} against {}".format(*player_names))
+    plt.legend()
+    plt.ylim(0, 1)
+
+    filename = "img/{}_v_{}_{}_repetitions".format(*player_names, repetitions)
+    for substr in [".", ": ", ":", " "]:  # Clean up special characters
+        filename = filename.replace(substr, "_")
+    filename += ".pdf"
+    filename = "../" + filename
+
[…]

### 2017-04-12 tex/main.tex
Move Marc's notes to results section.
Fix abstract.
Draft the introduction section.
Have included an image of the Moran process.

@@
 \usepackage{amsmath}
+\usepackage{standalone}
+
+\usepackage{tikz}
+\usetikzlibrary{calc, shapes}
 
@@
 
-\[ \rho = \frac{1 - r^{-i}}{1 - r^{-N}}\]
-and $\rho = 1 / N$ if $r=1$ (the neutral fixation probability).
+Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
+process. The Moran process is a stochastic birth death process on a finite
+population in which the population size stays constant over time. Individuals
+are \textbf{selected} according to a given fitness landscape. Once selected, a
+given individual is reproduced and similarly another individual is chosen to be
+removed from the population. In some settings mutation is also considered but
+without mutation (the case considered in this work) this process will arrive at
+an absorbing state where the population is entirely made up of a single
+individual. The probability with which a given strategy is the survivor is call
+the absorption probability. A more detailed analytic description of this is
+given in Section~\ref{sec:validation}.
 
-This corresponds to a game matrix [[1, 1], [r, r]] (or [[r, r], [1, 1]]), which
-is of course not what we have -- it's a little complicated because our "fitness"
-is not the payout from the game matrix, rather the sum of the total scores of
-all the interactions each round. So ALLC and TFT are neutral wrt to each other
-because they will have the same score each round, giving an effective fitness
-landscape $f(i, N-i) = A [i, N-i]^T$ given by the matrix $A = [[1,1],[1,1]]$.
-This means that noise and the number of turns per Moran round are significant
-parameters. I think we should fix the turns at 200; some recent authors run the
-turns to infinity (to reach stationarity on the sub-"Markov process" on the
-states (C, C), (C, D), (D, C), (D, D)) but we can't analytically compute the
-stationary distribution for strategies that use more than one round of memory
-(and it's not really a Markov process for more than one round of memory anyway).
-Plus it's unrealistic, and ultimately just amounts to a transform of the game
-matrix.
+\begin{figure}[!hbtp]
+    \centering
+    \input{../img/moran_process.tex}
+    \label{fig:moran_process}
+    \caption{A diagrammatic representation of a Moran process}
+\end{figure}
 
-To see if one strategy is not neutral with respect to another, we want to
-empirically measure the fixation probability and compare to the neutral rate. To
-do this right we need a lot of counts, since we're estimating a binomial
-probability p with variance $p(1-p) / k$ and $p$ is close to $1 / N$. To get the
-variance small you need something like $k>1000$ observations ( we can work out
-the precise requirements).
+The Moran process was initially introduced in \cite{Moran1957} in a genetic
+setting. It has sine been used in a variety of settings including the
+understanding of the spread of cooperative behaviour. However, as stated before,
+these mainly consider non sophisticated strategies. Some work has looked at
+evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
+but this is not done in the more widely used setting of the Moran process but in
+terms of infinite population stability. In \cite{Baek2016} Moran processes are
+looked at in a theoretic framework for a small subset of strategies. In
+\cite{Lee2015} machine learning techniques are used to train a strategy capable
+of resisting invasion and also invade any memory one strategy.
+% TODO Is this OK? We should add more.
 
-Note we're not estimating $r$ for each strategy (pair) since we're in a
-frequency dependent situation, so we need to look at the population states (1,
-N-1) and (N-1, 1) for every pair of strategies, i.e. we can't assume that we're
-in a $\rho \leftrightarrow 1-\rho$ symmetry. More precisely, $\rho_{(1, N-1)} !=
-1 - \rho_{(N-1, 1)}$ in general. However we can (for fun) compute $r$ from
-$\rho$ with Newton's method (it's not easily invertable for $N > 3$), or take a
-Bayesian approach on what the distribution of $\rho$ is and then compute a
-distribution for $r$ in the usual way.
+The contribution of this work is a detailed and extensive analysis of absorption
+probabilities for 172 strategies. These strategies and the numerical simulations
+are from~\cite{axelrodproject} which is an open source research library written
+for the study of the IPD. The strategies and simulation frameworks are
+automatically tested in accordance to best practice. The large number of
+strategies are available thanks to the open source nature of the project with
+over 40 contributions made by different programmers.
 
-A nice addition would be, for an interesting combination of strategies, to
-measure the fixation value for all $(i, N-i)$ and compare to the above formula
-for the value of $r$ derived from the $(1, N-1)$ case. This would show how much
-we deviate from frequency independence.
-
-The existing notebook attempts to get at 1 and 2 by looking at the distributions
-of fixation probabilities for each strategy -- that's what the box plots for
-each N try to visualize for particular N, and the "Player Rankings by Median vs.
-Population Size" for how the cooperative strategies become more successful as N
-increases. That plot is the main takeaway IMO, and reinforces the "evolution of
-cooperation" narrative that's so popular. We can tie back to Press and Dyson
-here -- yes, ZD strategies are good Head-to-Head and in small populations, but
-they aren't great when the population size gets bigger. How much bigger? Even at
-N=4 there is a dramatic decline for ZD-extort. Note that this goes against the
-claims of Stewart and Plotkin (they claimed that ZD strategies basically
-dominate the Moran process no matter how much memory you allow). This also
-matches our tournament results -- ZD strategies win matches but not tournaments.
-
-It would be great to see how the ensemble strategies (meta strategies) fare, if
-we don't mind burning the CPU cycles. I left them out of my initial analysis.
-
-More future work: * Mutation -- for mutation we no longer have fixation, rather
-a stationary distribution. This may require some more programming to compute
-efficiently (perhaps my stationary library). There's a lot of interesting work
-to do here.
-
-Ip think we'd want to include a few of the heatmaps in the final section of the
-notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
-Pushing N higher will make all the plots more interesting. How high we can get
-N? I'd really like to get it to N >= 11.
-
-Structure:
-
-\begin{itemize}
-    \item Overview of Moran processes;
-    \item Review of the literature (\cite{Lee2015, Nowak, Moran1957});
-    \item Short discussion about the Axelrod library.
-\end{itemize}
-
-Some work has looked at evolutionary stability of strategies within the
-Prisoner's Dilemma \cite{Li2014} but this is not done in the more widely used
-setting of the Moran process but in terms of infinite population stability.
-
-In \cite{Baek2016} Moran processes are looked at in a theoretic framework for a
-small subset of strategies.
-
-In \cite{Lee2015} machine learning techniques are used to train a strategy
-capable of resisting invasion and also invade any memory one strategy.
+Section~\ref{sec:methodology} will explain the methodological approach used,
+Section~\ref{sec:validation} will validate the methodology by comparing
+simulated results to analytical results. The main results of this manuscript are
+presented in Section~\ref{sec:numerical_results} which will present a detailed
+analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
+conclude and offer future avenues for the work presented here.
 
@@
 interaction between two players within the Moran process the outcome is sampled
-from a pre computed cache of 10000 match outcomes. This is carried out using the
+from a pre computed cache of 1000 match outcomes. This is carried out using the
 approximate Moran process implemented in \cite{axelrodproject}.
@@
 As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
-between two players that over the 10000 outcomes gives 6817 different scores.
+between two players that over the 1000 outcomes gives 971 different scores.
 
@@
 \end{figure}
+
+% TODO Cite all relevant pieces of software: pandas, matplotlib, scipy, axelrod
+% etc...
+
+% TODO Introduce the next section.
 
@@
 
+% TODO Include more of these when finished.
 \begin{figure}[!hbtp]
@@
 
+\[ \rho = \frac{1 - r^{-i}}{1 - r^{-N}}\]
+and $\rho = 1 / N$ if $r=1$ (the neutral fixation probability).
+
+This corresponds to a game matrix [[1, 1], [r, r]] (or [[r, r], [1, 1]]), which
+is of course not what we have -- it's a little complicated because our "fitness"
+is not the payout from the game matrix, rather the sum of the total scores of
+all the interactions each round. So ALLC and TFT are neutral wrt to each other
+because they will have the same score each round, giving an effective fitness
+landscape $f(i, N-i) = A [i, N-i]^T$ given by the matrix $A = [[1,1],[1,1]]$.
+This means that noise and the number of turns per Moran round are significant
+parameters. I think we should fix the turns at 200; some recent authors run the
+turns to infinity (to reach stationarity on the sub-"Markov process" on the
+states (C, C), (C, D), (D, C), (D, D)) but we can't analytically compute the
+stationary distribution for strategies that use more than one round of memory
+(and it's not really a Markov process for more than one round of memory anyway).
+Plus it's unrealistic, and ultimately just amounts to a transform of the game
+matrix.
+
+To see if one strategy is not neutral with respect to another, we want to
+empirically measure the fixation probability and compare to the neutral rate. To
+do this right we need a lot of counts, since we're estimating a binomial
+probability p with variance $p(1-p) / k$ and $p$ is close to $1 / N$. To get the
+variance small you need something like $k>1000$ observations ( we can work out
+the precise requirements).
+
+Note we're not estimating $r$ for each strategy (pair) since we're in a
+frequency dependent situation, so we need to look at the population states (1,
+N-1) and (N-1, 1) for every pair of strategies, i.e. we can't assume that we're
+in a $\rho \leftrightarrow 1-\rho$ symmetry. More precisely, $\rho_{(1, N-1)} !=
+1 - \rho_{(N-1, 1)}$ in general. However we can (for fun) compute $r$ from
+$\rho$ with Newton's method (it's not easily invertable for $N > 3$), or take a
+Bayesian approach on what the distribution of $\rho$ is and then compute a
+distribution for $r$ in the usual way.
+
+A nice addition would be, for an interesting combination of strategies, to
+measure the fixation value for all $(i, N-i)$ and compare to the above formula
+for the value of $r$ derived from the $(1, N-1)$ case. This would show how much
+we deviate from frequency independence.
+
+The existing notebook attempts to get at 1 and 2 by looking at the distributions
+of fixation probabilities for each strategy -- that's what the box plots for
+each N try to visualize for particular N, and the "Player Rankings by Median vs.
+Population Size" for how the cooperative strategies become more successful as N
+increases. That plot is the main takeaway IMO, and reinforces the "evolution of
+cooperation" narrative that's so popular. We can tie back to Press and Dyson
+here -- yes, ZD strategies are good Head-to-Head and in small populations, but
+they aren't great when the population size gets bigger. How much bigger? Even at
+N=4 there is a dramatic decline for ZD-extort. Note that this goes against the
+claims of Stewart and Plotkin (they claimed that ZD strategies basically
+dominate the Moran process no matter how much memory you allow). This also
+matches our tournament results -- ZD strategies win matches but not tournaments.
+
+It would be great to see how the ensemble strategies (meta strategies) fare, if
+we don't mind burning the CPU cycles. I left them out of my initial analysis.
+
+More future work: * Mutation -- for mutation we no longer have fixation, rather
+a stationary distribution. This may require some more programming to compute
+efficiently (perhaps my stationary library). There's a lot of interesting work
+to do here.
+
+Ip think we'd want to include a few of the heatmaps in the final section of the
+notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
+Pushing N higher will make all the plots more interesting. How high we can get
+N? I'd really like to get it to N >= 11.
+
 Structure:

### 2017-04-13 src/draw_validation_plots.py
Add correct xticks to validation plots.

@@ -62,6 +62,7 @@ def plot_theoretic_vs_simulated(max_N, repetitions, utilities, player1, player2)
 
     plt.xlabel("Population size $N$")
     plt.title("Fixation probability for {} against {}".format(*player_names))
+    plt.xticks(ns)
     plt.legend()
     plt.ylim(0, 1)
 
@@ -88,7 +89,7 @@ if __name__ == "__main__":
                     (axl.Alternator(), axl.WinStayLoseShift()),
                     (axl.Calculator(), axl.ALLCorALLD()),
                     (axl.Calculator(), axl.ArrogantQLearner()),
-                    (axl.Calculator(), axl.Random())
+                    (axl.Calculator(), axl.Random()),
                     (axl.Cooperator(), axl.TitForTat()),
                     (axl.Defector(), axl.Cooperator()),
                     (axl.Defector(), axl.TitForTat()),

### 2017-04-13 src/moran.py
Minor refactor of the moran.py script.
- Correct the path
- Remove redundant loop
- Close unclosed file
- Refactor function calls

@@ -24,7 +24,7 @@ import unittest
 def output_players(players, outfilename="players.csv"):
     """Cache players to disk for later retrieval."""
     rows = [(i, str(player), player.classifier["stochastic"]) for (i, player) in enumerate(players)]
-    path = Path("results") / outfilename
+    path = Path("../data") / outfilename
     with path.open('w') as csvfile:
         writer = csv.writer(csvfile)
         writer.writerows(rows)
@@ -78,18 +78,16 @@ def write_winner(outfilename, names_inv,
         winner_name = mp.winning_strategy_name
         data[names_inv[winner_name]] += 1
 
-    path = Path("results")
+    path = Path("../data")
     path = path / outfilename
-    outputfile = csv.writer(path.open('a'))
-    rows = []
-    for winner, count in data.items():
-        rows.append([i, j, winner, count])
-    for row in rows:
-        outputfile.writerow(row)
+    with path.open('a') as f:
+        outputfile = csv.writer(f)
+        for winner, count in data.items():
+            outputfile.writerow([i, j, winner, count])
 
 
-def run_simulations(N=2, turns=100, repetitions=1000, noise=0,
-                    outfilename=None, processes=None, count=False, n=1):
+def run_simulations(N=2, repetitions=1000, outfilename=None,
+                    processes=None, count=False, n=1):
     """This function conducts many moran processes to empirically estimate
     fixation probabilities. For each pair of strategies, the population consists
     of n player of the first type and N-n players of the second type."""
@@ -99,7 +97,7 @@ def run_simulations(N=2, turns=100, repetitions=1000, noise=0,
     # Obtain current count of obtained values
     if count is True:
         try:
-            counts = obtain_current_count("results/" + outfilename)
+            counts = obtain_current_count("../data/" + outfilename)
         except OSError:
             # If file does not exist then don't count
             count = False
@@ -145,7 +143,7 @@ def main():
     N = int(sys.argv[1])  # Population size
 
     try:
-        n = sys.argv[2]
+        n = int(sys.argv[2])  # Initial population (n, N - n)
     except IndexError:
         n = 1
 
@@ -156,7 +154,7 @@ def main():
 
     repetitions = 1000
     # Make sure the data folder exists
-    path = Path("results")
+    path = Path("../data")
     path.mkdir(exist_ok=True)
 
     output_players(players)
@@ -170,7 +168,7 @@ if __name__ == "__main__":
     try:
[…]

### 2017-04-13 src/draw_validation_plots.py
Add some new images.

@@ -88,7 +88,7 @@ if __name__ == "__main__":
                     (axl.Alternator(), axl.WinStayLoseShift()),
                     (axl.Calculator(), axl.ALLCorALLD()),
                     (axl.Calculator(), axl.ArrogantQLearner()),
-                    (axl.Calculator(), axl.Random())
+                    (axl.Calculator(), axl.Random()),
                     (axl.Cooperator(), axl.TitForTat()),
                     (axl.Defector(), axl.Cooperator()),
                     (axl.Defector(), axl.TitForTat()),

### 2017-04-13 src/validate.py
Correct range for validation data.

@@ -101,6 +101,6 @@ if __name__ == "__main__":
 
 
     args = ((N, *players)
-            for N, players in itertools.product(range(1, max_N + 1, 2),
+            for N, players in itertools.product(range(2, max_N + 1, 2),
                                                 player_pairs))
     p.starmap(func, args)

### 2017-04-13 src/validate.py
Fix header

@@ -62,7 +62,7 @@ if __name__ == "__main__":
     outcomes_file = "../data/outcomes.csv"
     output_file = "../data/fixation_validation.csv"
     with open(output_file, "w") as f:
-        f.write("Repetitions, N, Player 1, Player 2, Theoretic, Simulated\n")
+        f.write("Repetitions,N,Player 1,Player 2,Theoretic,Simulated\n")
 
     player_pairs = [(axl.ALLCorALLD(), axl.Cooperator()),
                     (axl.ALLCorALLD(), axl.Defector()),
@@ -84,7 +84,7 @@ if __name__ == "__main__":
                     (axl.WinStayLoseShift(), axl.TitForTat())]
 
     max_N = 20
-    repetitions = 1000
+    repetitions = 20
 
     df = pd.read_csv(outcomes_file, header=None,
                      names=["Player 1", "Player 2",

### 2017-04-13 src/validate.py
Add Defector v WSLS to validate script

@@ -71,7 +71,7 @@ if __name__ == "__main__":
                     (axl.Alternator(), axl.Defector()),
                     (axl.Alternator(), axl.TitForTat()),
                     (axl.Alternator(), axl.WinStayLoseShift()),
-                    (axl.Alternator(), axl.WinStayLoseShift()),
+                    (axl.Defector(), axl.WinStayLoseShift()),
                     (axl.Calculator(), axl.ALLCorALLD()),
                     (axl.Calculator(), axl.ArrogantQLearner()),
                     (axl.Calculator(), axl.Random()),

### 2017-04-13 tex/main.tex

@@
 strategies and show a perfect match up between the expected value of
-(\ref{equ:fixation_probability}) and the actual Moran process.
+(\ref{equ:fixation_probability}) and the actual Moran process for almost all
+strategies pairs.
+% TODO Discuss why WSLS And TFT do not match.
 
-% TODO Include more of these when finished.
 \begin{figure}[!hbtp]
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator.pdf}
         \caption{Alternator and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector.pdf}
         \caption{Alternator and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat.pdf}
         \caption{Alternator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat.pdf}
         \caption{Cooperator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator.pdf}
         \caption{Defector and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat.pdf}
         \caption{Defector and Tit For Tat}
     \end{subfigure}%
-    \caption{Comparison of theoretic and actual Moran Process fixation probabilities for \textbf{deterministic} strategies}
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_C_v_Tit_For_Tat.pdf}
+        \caption{Win Stay Lose Shift and Tit For Tat}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift_C.pdf}
+        \caption{Alternator and Win Stay Lose Shift}
+    \end{subfigure}%
+    % TODO Add Defector v WSLS
+    \caption{Comparison of theoretic and actual Moran Process fixation
+             probabilities for \textbf{deterministic} strategies}
     \label{fig:comparison_deterministic}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Cooperator_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Cooperator.pdf}
         \caption{Random and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Defector_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Defector.pdf}
         \caption{Random and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Tit_For_Tat_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Tit_For_Tat.pdf}
         \caption{Random and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator.pdf}
         \caption{All C or all D and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector.pdf}
         \caption{All C or all D and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_0_5_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_0_5.pdf}
         \caption{Calculator and Random}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD.pdf}
         \caption{Calculator and All C or all D}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner.pdf}
         \caption{Calculator and Arrogant Q learner}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat_1000_repetitions.pdf}
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat.pdf}
         \caption{All C or all D and Tit For Tat}
     \end{subfigure}%
-    \caption{Comparison of theoretic and actual Moran Process fixation probabilities for \textbf{stochastic} strategies}
+    \caption{Comparison of theoretic and actual Moran Process
+             fixation probabilities for \textbf{stochastic} strategies}
     \label{fig:comparison_stochastic}

### 2017-04-13 src/validate.py
Correct name for strategy in validation.

@@ -35,7 +35,7 @@ def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
         axl.seed(seed)
         mp.reset()
         mp.play()
-        if mp.winning_strategy_name == players[0].name:
+        if mp.winning_strategy_name == str(players[0]):
             win_count += 1
 
     return win_count / repetitions

### 2017-04-13 src/validate.py
Set repetitions to 1000

@@ -84,7 +84,7 @@ if __name__ == "__main__":
                     (axl.WinStayLoseShift(), axl.TitForTat())]
 
     max_N = 20
-    repetitions = 20
+    repetitions = 1000
 
     df = pd.read_csv(outcomes_file, header=None,
                      names=["Player 1", "Player 2",

### 2017-04-13 tex/main.tex
Update with correct WSLS.

@@
 are from~\cite{axelrodproject} which is an open source research library written
-for the study of the IPD. The strategies and simulation frameworks are
+for the study of the IPD\@. The strategies and simulation frameworks are
 automatically tested in accordance to best practice. The large number of
@@
 the time (excluding strategies classified as having a long run time) as well as
-the following 3 finite state machine strategies:
+the following 3 finite state machine machine strategies \cite{Ashlock2006}:
 
 % TODO Include details about the 3 extra FSM strategies.
+% Possibly draw pictorial representations?
 
@@
 
-% TODO Cite all relevant pieces of software: pandas, matplotlib, scipy, axelrod
-% etc...
+A variety of software libraries have been used in this work:
 
-% TODO Introduce the next section.
+\begin{itemize}
+    \item The Axelrod library (IPD strategies and Moran processes)
+        \cite{axelrodproject}.
+    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
+    \item The pandas and numpy libraries (data manipulation)
+        \cite{mckinney2010data, walt2011numpy}
+\end{itemize}
+
+Section~\ref{sec:validation} will validate this approach against theoretic
+results.
 
@@
 strategies and show a perfect match up between the expected value of
-(\ref{equ:fixation_probability}) and the actual Moran process for almost all
+(\ref{equ:fixation_probability}) and the actual Moran process for all
 strategies pairs.
-% TODO Discuss why WSLS And TFT do not match.
 
@@
     \end{subfigure}%
-    % TODO Add Defector v WSLS
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift_C.pdf}
+        \caption{Defector and Win Stay Lose Shift}
+    \end{subfigure}%
     \caption{Comparison of theoretic and actual Moran Process fixation

### 2017-04-14 tex/main.tex
Re draw validation plots.
Also fix the name.

@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_C_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_v_Tit_For_Tat.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift_C.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift_C.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Cooperator.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Random_v_Cooperator.pdf}
         \caption{Random and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Defector.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Random_v_Defector.pdf}
         \caption{Random and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_0_5_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Random_v_Tit_For_Tat.pdf}
         \caption{Random and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_0_5.pdf}
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random.pdf}
         \caption{Calculator and Random}

### 2017-04-14 tex/main.tex
Redraw moran process diagram.
Use hashing to avoid counting on color.
Make minor stylistic tex changes.
Remove MH comment no longer relevant because N/2.

@@
 \usepackage{tikz}
-\usetikzlibrary{calc, shapes}
+\usetikzlibrary{calc, shapes, patterns}
 
@@
 an absorbing state where the population is entirely made up of a single
-individual. The probability with which a given strategy is the survivor is call
-the absorption probability. A more detailed analytic description of this is
-given in Section~\ref{sec:validation}.
+individual. The probability with which a given strategy is the survivor is
+called the absorption probability. A more detailed analytic description of this
+is given in Section~\ref{sec:validation}.
 
@@
     \input{../img/moran_process.tex}
+    \caption{A diagrammatic representation of a Moran process}
     \label{fig:moran_process}
-    \caption{A diagrammatic representation of a Moran process}
 \end{figure}
@@
     \item The pandas and numpy libraries (data manipulation)
-        \cite{mckinney2010data, walt2011numpy}
+        \cite{mckinney2010data, walt2011numpy}.
 \end{itemize}
@@
 \begin{equation}\label{equ:fixation_probability}
-x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}\prod_{k=1}^{j}\gamma_j}
+x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}
+      \prod_{k=1}^{j}\gamma_j}
 \end{equation}
@@
 stochastic strategies. These are no longer a good match which highlights the
-weakness of the analytical formulae the relies on the average payoffs. A
+weakness of the analytical formulae that relies on the average payoffs. A
 detailed analysis of the 172 strategies considered will be shown in the next
@@
 \section{Numerical results}\label{sec:numerical_results}
-
-\[ \rho = \frac{1 - r^{-i}}{1 - r^{-N}}\]
-and $\rho = 1 / N$ if $r=1$ (the neutral fixation probability).
-
-This corresponds to a game matrix [[1, 1], [r, r]] (or [[r, r], [1, 1]]), which
-is of course not what we have -- it's a little complicated because our "fitness"
-is not the payout from the game matrix, rather the sum of the total scores of
-all the interactions each round. So ALLC and TFT are neutral wrt to each other
-because they will have the same score each round, giving an effective fitness
-landscape $f(i, N-i) = A [i, N-i]^T$ given by the matrix $A = [[1,1],[1,1]]$.
-This means that noise and the number of turns per Moran round are significant
-parameters. I think we should fix the turns at 200; some recent authors run the
-turns to infinity (to reach stationarity on the sub-"Markov process" on the
-states (C, C), (C, D), (D, C), (D, D)) but we can't analytically compute the
-stationary distribution for strategies that use more than one round of memory
-(and it's not really a Markov process for more than one round of memory anyway).
-Plus it's unrealistic, and ultimately just amounts to a transform of the game
-matrix.
 
@@
 we deviate from frequency independence.
-
 The existing notebook attempts to get at 1 and 2 by looking at the distributions
@@
 
-Beyond the raw data, we should try to estimate the strategies that are
-1) most resistant to invasion
-2) the best invaders
-3) "most neutral"
-
-as a function of N across the entire population of strategies. This can really
-open up if you want to say optimize a parameterized strategy to be most
-resistant to invasion (a topic of future work, perhaps) -- for example Random(p)
-for what p is best?
-
 Further Variants (possible additions or future papers): * Noise * Spatial

### 2017-04-14 tex/main.tex
Move comments from MH to TODOs.

@@
 
-To see if one strategy is not neutral with respect to another, we want to
-empirically measure the fixation probability and compare to the neutral rate. To
-do this right we need a lot of counts, since we're estimating a binomial
-probability p with variance $p(1-p) / k$ and $p$ is close to $1 / N$. To get the
-variance small you need something like $k>1000$ observations ( we can work out
-the precise requirements).
+% TODO Compare fixation rates to neutral fixation 1/2 (because we're in the N/2)
+% case.
 
-Note we're not estimating $r$ for each strategy (pair) since we're in a
-frequency dependent situation, so we need to look at the population states (1,
-N-1) and (N-1, 1) for every pair of strategies, i.e. we can't assume that we're
-in a $\rho \leftrightarrow 1-\rho$ symmetry. More precisely, $\rho_{(1, N-1)} !=
-1 - \rho_{(N-1, 1)}$ in general. However we can (for fun) compute $r$ from
-$\rho$ with Newton's method (it's not easily invertable for $N > 3$), or take a
-Bayesian approach on what the distribution of $\rho$ is and then compute a
-distribution for $r$ in the usual way.
+% TODO Discuss effect of size on performance of strategies. Relate to Press and
+% Dyson work: "ZD strategies win matches but not tournaments".
 
-A nice addition would be, for an interesting combination of strategies, to
-measure the fixation value for all $(i, N-i)$ and compare to the above formula
-for the value of $r$ derived from the $(1, N-1)$ case. This would show how much
-we deviate from frequency independence.
-The existing notebook attempts to get at 1 and 2 by looking at the distributions
-of fixation probabilities for each strategy -- that's what the box plots for
-each N try to visualize for particular N, and the "Player Rankings by Median vs.
-Population Size" for how the cooperative strategies become more successful as N
-increases. That plot is the main takeaway IMO, and reinforces the "evolution of
-cooperation" narrative that's so popular. We can tie back to Press and Dyson
-here -- yes, ZD strategies are good Head-to-Head and in small populations, but
-they aren't great when the population size gets bigger. How much bigger? Even at
-N=4 there is a dramatic decline for ZD-extort. Note that this goes against the
-claims of Stewart and Plotkin (they claimed that ZD strategies basically
-dominate the Moran process no matter how much memory you allow). This also
-matches our tournament results -- ZD strategies win matches but not tournaments.
+% TODO Redo everything with Meta strategies? This was a comment by MH. I suggest
+% we leave this for this paper.
 
-It would be great to see how the ensemble strategies (meta strategies) fare, if
-we don't mind burning the CPU cycles. I left them out of my initial analysis.
+% TODO Include discussion about noise.
 
-More future work: * Mutation -- for mutation we no longer have fixation, rather
-a stationary distribution. This may require some more programming to compute
-efficiently (perhaps my stationary library). There's a lot of interesting work
-to do here.
-
-Ip think we'd want to include a few of the heatmaps in the final section of the
-notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
-Pushing N higher will make all the plots more interesting. How high we can get
-N? I'd really like to get it to N >= 11.
-
-Structure:
-
-\begin{itemize}
-    \item General overview of the data obtained;
-    \item Inclusion of most of the work in \texttt{Moran.ipynb}.
-\end{itemize}
+% TODO Discuss some particular interesting cases; strategies that perform well
+% in the overall tournament for v2.8.0 perhaps?
 
@@
 
-Further Variants (possible additions or future papers): * Noise * Spatial
-structure * More than two types in the population * Modified Moran processes
-(e.g. Fermi selection with the strength of selection coefficient) * Altered game
-matrices
+% TODO Write overall conclusion. (Perhaps: weakness of short memory
+% strategies?)
 
-Noise is especially interesting because a lot of the cooperative strategies are
-going to appear neutral to each other (since neither will cast a D unprovoked).
-A little bit of noise should shuffle the ranks around quite a bit, and show off
-the abilities of e.g. OmegaTFT. Might be worth including at least one of the
-"Player Rankings by Median vs. Population Size" plots for some value of noise
-(such as 0.05).
+Further work:
+
+\begin{itemize}
+    \item Spatial structure;
+    \item More than two types in the population;
+    \item Modified Moran processes (Fermi selection);
+    \item Mutation;
+\end{itemize}
+% TODO Write this section.
 

### 2017-04-14 src/clean_raw_moran.py
Add summary data file script.

@@ -1,0 +1,57 @@
+"""
+A script to clean the raw data
+
+NOTE this script consider P1 v P2 and the same match as P2 v P1 and calculates
+the fixation probabilities by considering both match ups. This holds if the
+Moran process data is generated using N / 2 individuals of the first type in a
+population of size N.
+"""
+import pandas as pd
+import csv
+
+
+# Read in the player representations
+with open("../data/players.csv", "r") as f:
+    reader = csv.reader(f)
+    index_to_players = {row[0]: row[1] for row in reader}
+
+# Read in the data
+data = []
+for N in range(2, 14 + 1, 2):
+    for noise, filename in enumerate(["../data/sims_{}.csv".format(N),
+                                 "../data/noise_sims_{0:02d}.csv".format(N)]):
+        noise = bool(noise)
+
+        with open(filename, "r") as f:
+            reader = csv.reader(f)
+            for row in reader:
+
+                index1, index2, indexwinner, winnercount = row
+
+                p1 = index_to_players[index1]
+                p2 = index_to_players[index2]
+                winner = index_to_players[indexwinner]
+
+                if index1 > index2:
+                    p1, p2 = p2, p1
+
+                data.append([noise, int(N), p1, p2, winner, int(winnercount)])
+
+full_data = pd.DataFrame(data, columns=["Noise", "N", "P1", "P2",
+                                        "Winner", "Winner count"])
+
+# Clean and write the data to file.
+with open("../data/sims_summary.csv", "w") as f:
+    writer = csv.writer(f)
+    writer.writerow(["P1", "P2", "N", "Noise",
+                     "Repetitions", "P1 fixation", "P2 fixation"])
+    for players_n_noise, df in full_data.groupby(["P1", "P2", "N", "Noise"]):
+
+        total = df["Winner count"].sum()
+
+        fixation_probabilities = []
+        for i in range(2):
+            count = float(df[df["Winner"] == players_n_noise[i]]["Winner count"].sum())
+            fixation_probabilities.append(count / total)
+
+        writer.writerow([*players_n_noise, total, *fixation_probabilities])

### 2017-04-15 tex/main.tex
Add acknowledgements of Raven.
Add some early analysis of rank vs N.

@@
 \usepackage{standalone}
+\usepackage{fancyvrb}
 
@@
 
-All strategies are paired and these pairs are used in 1000 repetitions of a
+All strategies are paired and these pairs are used in 2000 repetitions of a
 Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
@@
 
+Figures~\ref{fig:ranks_v_size_standard} and~\ref{fig:ranks_v_size_noisy} show
+the median rank of each strategy against population size in the standard and
+noisy settings. Note that these ranks are not necessarily integers as group ties
+are given the average rank.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
+    \caption{Median (inverse) rank of players against population size}
+    \label{fig:ranks_v_size_standard}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
+    \caption{Median (inverse) rank of players against population size with noise}
+    \label{fig:ranks_v_size_noisy}
+\end{figure}
+
+Tables~\ref{tbl:ranks_in_size_2_std},~\ref{tbl:ranks_in_size_14_std},~\ref{tbl:ranks_in_size_2_noisy}
+and~\ref{tbl:ranks_in_size_14_noisy} show the rankings across population size
+based for the top on bottom performers across the extreme population sizes.
+
+\begin{table}[!hbtp]
+    \centering
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/top_five_in_size_2_std.tex}
+            \label{tbl:top_five_in_size_2_std}
+        \end{subfigure}
+
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/bottom_five_in_size_2_std.tex}
+            \label{tbl:bottom_five_in_size_2_std}
+        \end{subfigure}%
+        \caption{Performance across population sizes of top and bottom
+        performing strategies in population size \(N=2\)}
+        \label{tbl:ranks_in_size_2_std}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/top_five_in_size_14_std.tex}
+            \label{tbl:top_five_in_size_14_std}
+        \end{subfigure}
+
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/bottom_five_in_size_14_std.tex}
+            \label{tbl:bottom_five_in_size_14_std}
+        \end{subfigure}%
+        \caption{Performance across population sizes of top and bottom
+        performing strategies in population size \(N=14\)}
+        \label{tbl:ranks_in_size_14_std}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/top_five_in_size_2_noisy.tex}
+            \label{tbl:top_five_in_size_2_noisy}
+        \end{subfigure}
+
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/bottom_five_in_size_2_noisy.tex}
+            \label{tbl:bottom_five_in_size_2_noisy}
+        \end{subfigure}%
+        \caption{Performance across population sizes of top and bottom
+        performing strategies in population size \(N=2\) (with noise)}
+        \label{tbl:ranks_in_size_2_noisy}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/top_five_in_size_14_noisy.tex}
+            \label{tbl:top_five_in_size_14_noisy}
+        \end{subfigure}
+
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/bottom_five_in_size_14_noisy.tex}
+            \label{tbl:bottom_five_in_size_14_noisy}
+        \end{subfigure}%
+        \caption{Performance across population sizes of top and bottom
+        performing strategies in population size \(N=14\) (with noise)}
+        \label{tbl:ranks_in_size_14_noisy}
+\end{table}
+
+Table~\ref{tbl:median_rank_v_memory_length} shows the performance based on
+memory length.
+
+\begin{table}[!hbtp]
+    \centering
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/median_rank_v_memory_length_std.tex}
+            \caption{Standard}
+            \label{tbl:top_five_in_size_14_noisy}
+        \end{subfigure}
+
+        \begin{subfigure}[t]{\textwidth}
+            \centering
+                \input{../tbl/median_rank_v_memory_length_noisy.tex}
+            \caption{Noisy}
+            \label{tbl:bottom_five_in_size_14_noisy}
+        \end{subfigure}%
+        \caption{Median rank by memory length}
+        \label{tbl:median_rank_v_memory_length}
+\end{table}
+
 % TODO Discuss effect of size on performance of strategies. Relate to Press and
 % Dyson work: "ZD strategies win matches but not tournaments".
+% TODO Include discussion about noise.
 
@@
 % we leave this for this paper.
-
-% TODO Include discussion about noise.
 
@@
 
+\section*{Acknowledgements}
+
+This work was performed using the computational facilities of the Advanced
+Research Computing @ Cardiff (ARCCA) Division, Cardiff University.
+
 \printbibliography

### 2017-04-16 tex/main.tex
Add a number of visualisations.
- Heatmaps
- Histograms

Also: tidy the nb.

@@
 
-% TODO Compare fixation rates to neutral fixation 1/2 (because we're in the N/2)
-% case.
+Figures~\ref{fig:fixation_heatmap_std} and~\ref{fig:fixation_heatmap_noise}
+shows the fixation rates of each player on the y axis against each player on the
+x axis.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_std.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_std.pdf}
+        \caption{\(N=4\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_std.pdf}
+        \caption{\(N=6\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_std.pdf}
+        \caption{\(N=8\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_std.pdf}
+        \caption{\(N=10\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_std.pdf}
+        \caption{\(N=12\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_std.pdf}
+        \caption{\(N=14\)}
+    \end{subfigure}%
+    \caption{Fixation probabilities of all strategies}
+    \label{fig:fixation_heatmap_std}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_noise.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_noise.pdf}
+        \caption{\(N=4\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_noise.pdf}
+        \caption{\(N=6\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_noise.pdf}
+        \caption{\(N=8\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_noise.pdf}
+        \caption{\(N=10\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_noise.pdf}
+        \caption{\(N=12\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_noise.pdf}
+        \caption{\(N=14\)}
+    \end{subfigure}%
+    \caption{Fixation probabilities of all strategies (with noise)}
+    \label{fig:fixation_heatmap_std}
+\end{figure}
+
+Figure~\ref{fig:histograms_all_fixation_rates_std}
+and~\ref{fig:histograms_all_fixation_rates_noise} show the distribution of the
+fixation rates for all strategies.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_std.pdf}
+    \caption{Distribution of fixation rates for all players}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_noise.pdf}
+    \caption{Distribution of fixation rates for all players (noise)}
+\end{figure}
+
+Figure~\ref{fig:histograms_median_fixation_rates_std}
+and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of the
+fixation rates for all strategies.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_std.pdf}
+    \caption{Distribution of median fixation rates for all players}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_noise.pdf}
+    \caption{Distribution of median fixation rates for all players (noise)}
+\end{figure}
 
@@
     \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
-    \caption{Median (inverse) rank of players against population size}
+    \caption{Median rank of players against population size}
     \label{fig:ranks_v_size_standard}
@@
     \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
-    \caption{Median (inverse) rank of players against population size with noise}
+    \caption{Median  rank of players against population size with noise}
     \label{fig:ranks_v_size_noisy}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_std.pdf}
+    \caption{Relationship between Median rank for population size}
+    \label{fig:relationship_ranks_v_size_standard}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_noisy.pdf}
+    \caption{Relationship between Median rank for population size with noise}
+    \label{fig:relationship_ranks_v_size_noise}
 \end{figure}

### 2017-04-16 src/clean_raw_moran.py

@@ -32,7 +32,7 @@ for N in range(2, 14 + 1, 2):
                 p2 = index_to_players[index2]
                 winner = index_to_players[indexwinner]
 
-                if index1 > index2:
+                if str(p1) > str(p2):
                     p1, p2 = p2, p1
 
                 data.append([noise, int(N), p1, p2, winner, int(winnercount)])

### 2017-04-19 tex/main.tex
Add a sentence I thought of during my walk.
I think the main idea I'm trying to get at here is that in P and D they
don't take in to account large populations: "mem 1 wins matches not
tournaments". In Nowak's work etc they don't take in to account memory
(at all): strategies are either All C or All D.
Add new Hilbe 2017 reference.
A paper stating that memory is important.

@@
 \cite{Lee2015} machine learning techniques are used to train a strategy capable
-of resisting invasion and also invade any memory one strategy.
+of resisting invasion and also invade any memory one strategy. Recent work
+\cite{Hilbe2017} has investigated the effect of memory length on strategy
+performance and the emergence of cooperation but this is not done in Moran
+process context and only considers specific cases of memory 2 strategies.
 % TODO Is this OK? We should add more.
@@
 strategies are available thanks to the open source nature of the project with
-over 40 contributions made by different programmers.
+over 40 contributions made by different programmers. Thus by considering Moran
+processes with population size greater than 2 we are taking in to account the
+effect of complex population dynamics. By considering sophisticated strategies
+we are taking in to effect the reputation of a strategy during each interaction.
 

### 2017-04-20 tex/main.tex
Add boxplot visualisation.
Also: improve the colormap for the median plots.

@@
     \end{subfigure}%
-    \caption{Fixation probabilities of all strategies}
+    \caption{Pairwise fixation probabilities of all strategies}
     \label{fig:fixation_heatmap_std}
@@
     \end{subfigure}%
-    \caption{Fixation probabilities of all strategies (with noise)}
+    \caption{Pairwise fixation probabilities of all strategies (with noise)}
     \label{fig:fixation_heatmap_std}
@@
 
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/fixation_boxplot_2_std.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_4_std.pdf}
+        %\caption{\(N=4\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_6_std.pdf}
+        %\caption{\(N=6\)}
+    %\end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/fixation_boxplot_8_std.pdf}
+        \caption{\(N=8\)}
+    \end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_10_std.pdf}
+        %\caption{\(N=10\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_12_std.pdf}
+        %\caption{\(N=12\)}
+    %\end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/fixation_boxplot_14_std.pdf}
+        \caption{\(N=14\)}
+    \end{subfigure}%
+    \caption{Fixation probabilities of all strategies}
+    \label{fig:fixation_boxplot_std}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/fixation_boxplot_2_noise.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_4_noise.pdf}
+        %\caption{\(N=4\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_6_noise.pdf}
+        %\caption{\(N=6\)}
+    %\end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/fixation_boxplot_8_noise.pdf}
+        \caption{\(N=8\)}
+    \end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_10_noise.pdf}
+        %\caption{\(N=10\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_12_noise.pdf}
+        %\caption{\(N=12\)}
+    %\end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/fixation_boxplot_14_noise.pdf}
+        \caption{\(N=14\)}
+    \end{subfigure}%
+    \caption{Fixation probabilities of all strategies (with noise)}
+    \label{fig:fixation_boxplot_std}
+\end{figure}
+
 Figure~\ref{fig:histograms_median_fixation_rates_std}
-and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of the
-fixation rates for all strategies.
+and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of
+the median fixation rates for all strategies.
 
@@
 \begin{figure}[!hbtp]
+
     \centering
-    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
+    \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_std.pdf}
+    \caption{Standard}
+    \label{fig:ranks_v_size_standard}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.5\textwidth}
+    \centering
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_noisy.pdf}
+    \caption{Noise}
+    \label{fig:ranks_v_size_noisy}
+    \end{subfigure}
     \caption{Median rank of players against population size}
-    \label{fig:ranks_v_size_standard}
-\end{figure}
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
-    \caption{Median  rank of players against population size with noise}
-    \label{fig:ranks_v_size_noisy}
 \end{figure}

### 2017-04-20 tex/main.tex
Add a table of linear regression coefficients.
This is neat (I think) as it shows numerically that the N=2 case has
very little to do with an actual population dynamic.

@@
 
+Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
+show the coefficients and \(R^2\) value of the linear model relating the rank in
+a particular sized population to the ranks in other populations sizes.
+% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
+% does show that the coefficient of the N=2 column is always low whereas the
+% coefficient of the N=14 column is high even in the N=4 row. So how well you do
+% in  a match (N=2) has got very little to do with an evolutionary process.
+
+\begin{table}[!hbtp]
+    \begin{subfigure}{.5\textwidth}
+        \centering
+        \input{"../tbl/linear_coeficients_std.tex"}
+        \caption{Linear model coefficients for ranks without noise}
+        \label{tbl:linear_coeficients_std}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.5\textwidth}
+        \centering
+        \input{"../tbl/linear_coeficients_noisy.tex"}
+        \caption{Linear model coefficients for ranks with noise}
+        \label{tbl:linear_coeficients_noisy}
+    \end{subfigure}
+    \caption{Linear coefficients}
+\end{table}
+
 Tables~\ref{tbl:ranks_in_size_2_std},~\ref{tbl:ranks_in_size_14_std},~\ref{tbl:ranks_in_size_2_noisy}

### 2017-04-20 src/validate.py
Add exact moran process to validation script.

@@ -15,7 +15,7 @@ import itertools
 
 def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
                        cachefile=None):
-    """Run a Moran process and obtain the fixation probabilities"""
+    """Run an approximate Moran process and obtain the fixation probabilities"""
     if cachefile is None:
         cachefile = "../data/outcomes.csv"
 
@@ -40,21 +40,44 @@ def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
 
     return win_count / repetitions
 
+def exact_fixation(strategy_pair, N, i=1, repetitions=10,
+                   turns=200):
+    """Run an exact Moran process and obtain the fixation probabilities"""
 
-def theoretic_vs_simulated(repetitions, utilities, filename,
-                           N, player1, player2):
+    players = []
+    for _ in range(i):
+        players.append(strategy_pair[0])
+    for _ in range(N - i):
+        players.append(strategy_pair[1])
+    mp = axl.MoranProcess(players, turns=turns)
+
+    win_count = 0
+    for seed in range(repetitions):
+        axl.seed(seed)
+        mp.reset()
+        mp.play()
+        if mp.winning_strategy_name == str(players[0]):
+            win_count += 1
+
+    return win_count / repetitions
+
+
+def theoretic_vs_simulated_vs_exact(repetitions, utilities, filename,
+                                    N, turns, player1, player2):
     """
     Return the theoretic values and the simulated values
     """
     players = (player1, player2)
-    repetitions = repetitions
 
-    player_names = [p.__repr__() for p in players]
-    t = theoretic.fixation(player_names, N, N // 2, utilities=utilities)
-    s = simulated_fixation(players,  N, N // 2, repetitions=repetitions)
+    for i in [1, N // 2, N - 1]:
+        player_names = [p.__repr__() for p in players]
+        t = theoretic.fixation(player_names, N, i, utilities=utilities)
+        s = simulated_fixation(players,  N, i, repetitions=repetitions)
+        e = exact_fixation(players,  N, i, turns=turns, repetitions=repetitions)
 
-    with open(filename, "a") as f:
-        f.write(",".join(map(str, [repetitions, N, *player_names, t, s])) + "\n")
+        with open(filename, "a") as f:
+            f.write(",".join(map(str,
[…]

### 2017-04-21 src/clean_raw_moran.py
Prepare to run 1, N-1 case.

@@ -18,8 +18,9 @@ with open("../data/players.csv", "r") as f:
 # Read in the data
 data = []
 for N in range(2, 14 + 1, 2):
-    for noise, filename in enumerate(["../data/sims_{}.csv".format(N),
-                                 "../data/noise_sims_{0:02d}.csv".format(N)]):
+    # Read N = 2 data
+    for noise, filename in enumerate(["../data/sims_n_over_2/sims_{}.csv".format(N),
+                                 "../data/sims_n_over_2/noise_sims_{0:02d}.csv".format(N)]):
         noise = bool(noise)
 
         with open(filename, "r") as f:
@@ -35,17 +36,17 @@ for N in range(2, 14 + 1, 2):
                 if str(p1) > str(p2):
                     p1, p2 = p2, p1
 
-                data.append([noise, int(N), p1, p2, winner, int(winnercount)])
+                data.append([noise, int(N), N // 2, p1, p2, winner, int(winnercount)])
 
-full_data = pd.DataFrame(data, columns=["Noise", "N", "P1", "P2",
+full_data = pd.DataFrame(data, columns=["Noise", "N", "i", "P1", "P2",
                                         "Winner", "Winner count"])
 
 # Clean and write the data to file.
 with open("../data/sims_summary.csv", "w") as f:
     writer = csv.writer(f)
-    writer.writerow(["P1", "P2", "N", "Noise",
+    writer.writerow(["P1", "P2", "N", "i", "Noise",
                      "Repetitions", "P1 fixation", "P2 fixation"])
-    for players_n_noise, df in full_data.groupby(["P1", "P2", "N", "Noise"]):
+    for players_n_noise, df in full_data.groupby(["P1", "P2", "N", "i", "Noise"]):
 
         total = df["Winner count"].sum()
 

### 2017-04-21 src/moran.py

@@ -152,7 +152,11 @@ def main():
     except IndexError:
         outfilename = None
 
-    repetitions = 1000
+    # If not in symmetric case run twice as many.
+    if n != N / 2:
+        repetitions = 2000
+    else:
+        repetitions = 1000
     # Make sure the data folder exists
     path = Path("../data")
     path.mkdir(exist_ok=True)

### 2017-04-21 src/validate.py
Remove exact from validation plot.
The run time is unreasonable.

@@ -40,44 +40,24 @@ def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
 
     return win_count / repetitions
 
-def exact_fixation(strategy_pair, N, i=1, repetitions=10,
-                   turns=200):
-    """Run an exact Moran process and obtain the fixation probabilities"""
 
-    players = []
-    for _ in range(i):
-        players.append(strategy_pair[0])
-    for _ in range(N - i):
-        players.append(strategy_pair[1])
-    mp = axl.MoranProcess(players, turns=turns)
-
-    win_count = 0
-    for seed in range(repetitions):
-        axl.seed(seed)
-        mp.reset()
-        mp.play()
-        if mp.winning_strategy_name == str(players[0]):
-            win_count += 1
-
-    return win_count / repetitions
-
-
-def theoretic_vs_simulated_vs_exact(repetitions, utilities, filename,
-                                    N, turns, player1, player2):
+def theoretic_vs_simulated(repetitions, utilities, filename,
+                           N, player1, player2):
     """
     Return the theoretic values and the simulated values
     """
     players = (player1, player2)
 
-    for i in [1, N // 2, N - 1]:
+    starting_pop = [1, N // 2, N - 1] if N != 2 else [1]
+
+    for i in starting_pop:
         player_names = [p.__repr__() for p in players]
         t = theoretic.fixation(player_names, N, i, utilities=utilities)
         s = simulated_fixation(players,  N, i, repetitions=repetitions)
-        e = exact_fixation(players,  N, i, turns=turns, repetitions=repetitions)
 
         with open(filename, "a") as f:
             f.write(",".join(map(str,
-                           [repetitions, N, i, *player_names, t, s, e])) + "\n")
+                           [repetitions, N, i, *player_names, t, s])) + "\n")
 
 
 if __name__ == "__main__":
@@ -85,7 +65,7 @@ if __name__ == "__main__":
     outcomes_file = "../data/outcomes.csv"
     output_file = "../data/fixation_validation.csv"
     with open(output_file, "w") as f:
-        f.write("Repetitions,N,i,Player 1,Player 2,Theoretic,Simulated,Exact\n")
+        f.write("Repetitions,N,i,Player 1,Player 2,Theoretic,Simulated\n")
 
     player_pairs = [(axl.ALLCorALLD(), axl.Cooperator()),
                     (axl.ALLCorALLD(), axl.Defector()),
[…]

### 2017-04-21 src/clean_raw_moran.py
Start refactoring for different initial population.

@@ -19,24 +19,27 @@ with open("../data/players.csv", "r") as f:
 data = []
 for N in range(2, 14 + 1, 2):
     # Read N = 2 data
-    for noise, filename in enumerate(["../data/sims_n_over_2/sims_{}.csv".format(N),
-                                 "../data/sims_n_over_2/noise_sims_{0:02d}.csv".format(N)]):
-        noise = bool(noise)
+    for filename in ["../data/sims_n_over_2/sims_{}.csv".format(N),
+                     "../data/sims_1/sims_{0:02d}.csv".format(N),
+                     "../data/sims_n_over_2/noise_sims_{0:02d}.csv".format(N)]:
 
-        with open(filename, "r") as f:
-            reader = csv.reader(f)
-            for row in reader:
+        noise = "noise" in filename
+        i = 1 if "1" in filename else N // 2
 
-                index1, index2, indexwinner, winnercount = row
+        try:
+            with open(filename, "r") as f:
+                reader = csv.reader(f)
+                for row in reader:
 
-                p1 = index_to_players[index1]
-                p2 = index_to_players[index2]
-                winner = index_to_players[indexwinner]
+                    index1, index2, indexwinner, winnercount = row
 
-                if str(p1) > str(p2):
-                    p1, p2 = p2, p1
+                    p1 = index_to_players[index1]
+                    p2 = index_to_players[index2]
+                    winner = index_to_players[indexwinner]
 
-                data.append([noise, int(N), N // 2, p1, p2, winner, int(winnercount)])
+                    data.append([noise, int(N), i, p1, p2, winner, int(winnercount)])
+        except FileNotFoundError:
+            pass
 
 full_data = pd.DataFrame(data, columns=["Noise", "N", "i", "P1", "P2",
                                         "Winner", "Winner count"])

### 2017-04-21 src/validate.py
Readjust to include invasion/resistance.

@@ -86,8 +86,8 @@ if __name__ == "__main__":
                     (axl.Random(), axl.TitForTat()),
                     (axl.WinStayLoseShift(), axl.TitForTat())]
 
-    max_N = 20
-    repetitions = 1000
+    max_N = 8
+    repetitions = 40
 
     df = pd.read_csv(outcomes_file, header=None,
                      names=["Player 1", "Player 2",

### 2017-04-21 tex/main.tex
Readjust to include invasion/resistance.

--- 2017-04-19 tex/main.tex
@@
 Using this comparisons of \(x_{N/2}\) are shown in
-Figure~\ref{fig:comparison_deterministic}. Note that these are all deterministic
-strategies and show a perfect match up between the expected value of
-(\ref{equ:fixation_probability}) and the actual Moran process for all
+Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
+values and the line shows the theoretic value. Note that these are all
+deterministic strategies and show a perfect match up between the expected value
+of (\ref{equ:fixation_probability}) and the actual Moran process for all
 strategies pairs.
@@
 
-Figures~\ref{fig:fixation_heatmap_std} and~\ref{fig:fixation_heatmap_noise}
-shows the fixation rates of each player on the y axis against each player on the
-x axis.
+Figures~\ref{fig:fixation_heatmap_1_std},~\ref{fig:fixation_heatmap_n_over_2_std}
+and~\ref{fig:fixation_heatmap_n_over_2_noise} shows the fixation rates of each
+player on the y axis against each player on the x axis.
 
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_std.pdf}
-        \caption{\(N=2\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
+        \caption{\((N,i)=(2, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_std.pdf}
-        \caption{\(N=4\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_1_std.pdf}
+        \caption{\((N,i)=(4, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_std.pdf}
-        \caption{\(N=6\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_1_std.pdf}
+        \caption{\((N,i)=(6, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_std.pdf}
-        \caption{\(N=8\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_1_std.pdf}
+        \caption{\((N,i)=(8, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_std.pdf}
-        \caption{\(N=10\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_1_std.pdf}
+        \caption{\((N,i)=(10, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_std.pdf}
-        \caption{\(N=12\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_1_std.pdf}
+        \caption{\((N,i)=(12, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_std.pdf}
-        \caption{\(N=14\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_1_std.pdf}
+        \caption{\((N,i)=(14, 1)\)}
     \end{subfigure}%
-    \caption{Fixation probabilities of all strategies}
-    \label{fig:fixation_heatmap_std}
+    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
+    \label{fig:fixation_heatmap_1_std}
 \end{figure}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_noise.pdf}
-        \caption{\(N=2\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
+        \caption{\((N,i)=(2, 1)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_noise.pdf}
-        \caption{\(N=4\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_std.pdf}
+        \caption{\((N,i)=(4, 2)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_noise.pdf}
-        \caption{\(N=6\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_std.pdf}
+        \caption{\((N,i)=(6, 3)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_noise.pdf}
-        \caption{\(N=8\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_std.pdf}
+        \caption{\((N,i)=(8, 4)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_noise.pdf}
-        \caption{\(N=10\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_std.pdf}
+        \caption{\((N,i)=(10, 5)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_noise.pdf}
-        \caption{\(N=12\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_std.pdf}
+        \caption{\((N,i)=(12, 6)\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_noise.pdf}
-        \caption{\(N=14\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_std.pdf}
+        \caption{\((N,i)=(14, 7)\)}
     \end{subfigure}%
-    \caption{Fixation probabilities of all strategies (with noise)}
-    \label{fig:fixation_heatmap_std}
-\end{figure}
-
-Figure~\ref{fig:histograms_all_fixation_rates_std}
-and~\ref{fig:histograms_all_fixation_rates_noise} show the distribution of the
-fixation rates for all strategies.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_std.pdf}
-    \caption{Distribution of fixation rates for all players}
+    \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
+    \label{fig:fixation_heatmap_n_over_2_std}
 \end{figure}
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../img/histograms_all_fixation_rates_noise.pdf}
-    \caption{Distribution of fixation rates for all players (noise)}
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_noise.pdf}
+        \caption{\((N,i)=(2, 1)\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_noise.pdf}
+        \caption{\((N,i)=(4, 2)\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_noise.pdf}
+        \caption{\((N,i)=(6, 3)\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_noise.pdf}
+        \caption{\((N,i)=(8, 4)\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_noise.pdf}
+        \caption{\((N,i)=(10, 5)\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_noise.pdf}
+        \caption{\((N,i)=(12, 6)\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_noise.pdf}
+        \caption{\((N,i)=(14, 7)\)}
+    \end{subfigure}%
+    \caption{Pairwise fixation probabilities of all strategies with noise}
+    \label{fig:fixation_heatmap_n_over_2_noise}
 \end{figure}
 
-Figure~\ref{fig:histograms_median_fixation_rates_std}
-and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of the
-fixation rates for all strategies.
+Figure~\ref{fig:invasion_boxplot_std} shows the fixation probabilities for each
+strategy when invading another strategy.
+Figure~\ref{fig:resistance_boxplot_std} shows the fixation probabilities for
+each strategy when resisting another strategy.
+Figure~\ref{fig:coexistance_boxplot_std} shows the fixation probabilities for
+each strategy when initially coexisting with another strategy.
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_std.pdf}
-    \caption{Distribution of median fixation rates for all players}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/invasion_boxplot_2_std.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/invasion_boxplot_4_std.pdf}
+        \caption{\(N=4\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/invasion_boxplot_6_std.pdf}
+        \caption{\(N=6\)}
+    \end{subfigure}%
+
+    % TODO be more selective here: just picking out the ones for which we
+    % currently have data
+    %\begin{subfigure}[htbp]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_8_std.pdf}
+        %\caption{\(N=8\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_10_std.pdf}
+        %\caption{\(N=10\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_12_std.pdf}
+        %\caption{\(N=12\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_14_std.pdf}
+        %\caption{\(N=14\)}
+    %\end{subfigure}%
+    \caption{Invasion fixation probabilities of all strategies}
+    \label{fig:invasion_boxplot_std}
 \end{figure}
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../img/histograms_median_fixation_rates_noise.pdf}
-    \caption{Distribution of median fixation rates for all players (noise)}
-\end{figure}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/resistance_boxplot_2_std.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
 
-Figures~\ref{fig:ranks_v_size_standard} and~\ref{fig:ranks_v_size_noisy} show
-the median rank of each strategy against population size in the standard and
-noisy settings. Note that these ranks are not necessarily integers as group ties
-are given the average rank.
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/resistance_boxplot_4_std.pdf}
+        \caption{\(N=4\)}
+    \end{subfigure}%
 
-\begin{figure}[!hbtp]
+    \begin{subfigure}[t]{\textwidth}
         \centering
-    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
-    \caption{Median rank of players against population size}
-    \label{fig:ranks_v_size_standard}
+        \includegraphics[width=\textwidth]{../img/resistance_boxplot_6_std.pdf}
+        \caption{\(N=6\)}
+    \end{subfigure}%
+
+    % TODO be more selective here: just picking out the ones for which we
+    % currently have data
+    %\begin{subfigure}[htbp]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_8_std.pdf}
+        %\caption{\(N=8\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_10_std.pdf}
+        %\caption{\(N=10\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_12_std.pdf}
+        %\caption{\(N=12\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_14_std.pdf}
+        %\caption{\(N=14\)}
+    %\end{subfigure}%
+    \caption{Resistance fixation probabilities of all strategies}
+    \label{fig:resistance_boxplot_std}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
-    \caption{Median  rank of players against population size with noise}
-    \label{fig:ranks_v_size_noisy}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_2_std.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_4_std.pdf}
+        %\caption{\(N=4\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_6_std.pdf}
+        %\caption{\(N=6\)}
+    %\end{subfigure}%
+
+    \begin{subfigure}[htbp]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_8_std.pdf}
+        \caption{\(N=8\)}
+    \end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_10_std.pdf}
+        %\caption{\(N=10\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_12_std.pdf}
+        %\caption{\(N=12\)}
+    %\end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_14_std.pdf}
+        \caption{\(N=14\)}
+    \end{subfigure}%
+    \caption{Coexistance fixation probabilities of all strategies}
+    \label{fig:coexistance_boxplot_std}
+\end{figure}
+
+Figures~\ref{fig:ranks_v_size_invasion},~\ref{fig:ranks_v_size_resistance}
+and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
+population size in the standard and noisy settings. Note that these ranks are
+not necessarily integers as group ties are given the average rank.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invasion.pdf}
+    \caption{Invasion}
+    \label{fig:ranks_v_size_invasion}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_std.pdf}
-    \caption{Relationship between Median rank for population size}
-    \label{fig:relationship_ranks_v_size_standard}
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resistance.pdf}
+    \caption{Resistance}
+    \label{fig:ranks_v_size_resistance}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_noisy.pdf}
-    \caption{Relationship between Median rank for population size with noise}
-    \label{fig:relationship_ranks_v_size_noise}
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_coexist.pdf}
+    \caption{Coexistance}
+    \label{fig:ranks_v_size_coexist}
 \end{figure}
 
-Tables~\ref{tbl:ranks_in_size_2_std},~\ref{tbl:ranks_in_size_14_std},~\ref{tbl:ranks_in_size_2_noisy}
-and~\ref{tbl:ranks_in_size_14_noisy} show the rankings across population size
-based for the top on bottom performers across the extreme population sizes.
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invasion.pdf}
+    \caption{Relationship between Median rank for population size for strategies
+    invading}
+    \label{fig:relationship_ranks_v_size_invasion}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resistance.pdf}
+    \caption{Relationship between Median rank for population size for strategies
+    resisting}
+    \label{fig:relationship_ranks_v_size_resistance}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_coexist.pdf}
+    \caption{Relationship between Median rank for population size for strategies
+    coexisting}
+    \label{fig:relationship_ranks_v_size_coexist}
+\end{figure}
+
+Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
+show the coefficients and \(R^2\) value of the linear model relating the rank in
+a particular sized population to the ranks in other populations sizes.
+% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
+% does show that the coefficient of the N=2 column is always low whereas the
+% coefficient of the N=14 column is high even in the N=4 row. So how well you do
+% in  a match (N=2) has got very little to do with an evolutionary process.
 
@@
     \centering
-        \begin{subfigure}[t]{\textwidth}
+    \begin{subfigure}{.5\textwidth}
         \centering
-                \input{../tbl/top_five_in_size_2_std.tex}
-            \label{tbl:top_five_in_size_2_std}
+        \input{"../tbl/linear_coeficients_invasion.tex"}
+        \caption{Linear model coefficients for ranks for invasion}
+        \label{tbl:linear_coeficients_invasion}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.5\textwidth}
+        \centering
+        \input{"../tbl/linear_coeficients_resistance.tex"}
+        \caption{Linear model coefficients for ranks for resistance}
+        \label{tbl:linear_coeficients_resistance}
     \end{subfigure}
 
-        \begin{subfigure}[t]{\textwidth}
+    \begin{subfigure}{.5\textwidth}
         \centering
-                \input{../tbl/bottom_five_in_size_2_std.tex}
-            \label{tbl:bottom_five_in_size_2_std}
-        \end{subfigure}%
-        \caption{Performance across population sizes of top and bottom
-        performing strategies in population size \(N=2\)}
-        \label{tbl:ranks_in_size_2_std}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/top_five_in_size_14_std.tex}
-            \label{tbl:top_five_in_size_14_std}
+        \input{"../tbl/linear_coeficients_coexist.tex"}
+        \caption{Linear model coefficients for ranks for coexistance}
+        \label{tbl:linear_coeficients_coexist}
     \end{subfigure}
-
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/bottom_five_in_size_14_std.tex}
-            \label{tbl:bottom_five_in_size_14_std}
-        \end{subfigure}%
-        \caption{Performance across population sizes of top and bottom
-        performing strategies in population size \(N=14\)}
-        \label{tbl:ranks_in_size_14_std}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/top_five_in_size_2_noisy.tex}
-            \label{tbl:top_five_in_size_2_noisy}
-        \end{subfigure}
-
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/bottom_five_in_size_2_noisy.tex}
-            \label{tbl:bottom_five_in_size_2_noisy}
-        \end{subfigure}%
-        \caption{Performance across population sizes of top and bottom
-        performing strategies in population size \(N=2\) (with noise)}
-        \label{tbl:ranks_in_size_2_noisy}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/top_five_in_size_14_noisy.tex}
-            \label{tbl:top_five_in_size_14_noisy}
-        \end{subfigure}
-
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/bottom_five_in_size_14_noisy.tex}
-            \label{tbl:bottom_five_in_size_14_noisy}
-        \end{subfigure}%
-        \caption{Performance across population sizes of top and bottom
-        performing strategies in population size \(N=14\) (with noise)}
-        \label{tbl:ranks_in_size_14_noisy}
-\end{table}
-
-Table~\ref{tbl:median_rank_v_memory_length} shows the performance based on
-memory length.
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/median_rank_v_memory_length_std.tex}
-            \caption{Standard}
-            \label{tbl:top_five_in_size_14_noisy}
-        \end{subfigure}
-
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/median_rank_v_memory_length_noisy.tex}
-            \caption{Noisy}
-            \label{tbl:bottom_five_in_size_14_noisy}
-        \end{subfigure}%
-        \caption{Median rank by memory length}
-        \label{tbl:median_rank_v_memory_length}
+    \caption{Linear coefficients}
 \end{table}

### 2017-04-21 src/clean_raw_moran.py

@@ -24,7 +24,7 @@ for N in range(2, 14 + 1, 2):
                      "../data/sims_n_over_2/noise_sims_{0:02d}.csv".format(N)]:
 
         noise = "noise" in filename
-        i = 1 if "1" in filename else N // 2
+        i = 1 if "sims_1/" in filename else N // 2
 
         try:
             with open(filename, "r") as f:

### 2017-04-23 tex/main.tex
Update results.

@@
 
-Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
-show the coefficients and \(R^2\) value of the linear model relating the rank in
-a particular sized population to the ranks in other populations sizes.
+Tables~\ref{tbl:linear_coeficients_invasion},~\ref{tbl:linear_coeficients_resistance}
+and~\ref{tbl:linear_coeficients_coexist} show the coefficients and \(R^2\) value
+of the linear model relating the rank in a particular sized population to the
+ranks in other populations sizes.
 % TODO Discuss these tables: show that none of the models are great (R^2) BUT it

### 2017-04-24 src/clean_raw_moran.py
Add code to numerically find relative fitness.
Also remove the Noisy data from the cleaning step.

@@ -6,56 +6,68 @@ the fixation probabilities by considering both match ups. This holds if the
 Moran process data is generated using N / 2 individuals of the first type in a
 population of size N.
 """
-import pandas as pd
 import csv
+import write_fitness
+import pandas as pd
 
 
-# Read in the player representations
-with open("../data/players.csv", "r") as f:
-    reader = csv.reader(f)
-    index_to_players = {row[0]: row[1] for row in reader}
+def read():
+    # Read in the player representations
+    with open("../data/players.csv", "r") as f:
+        reader = csv.reader(f)
+        index_to_players = {row[0]: row[1] for row in reader}
 
-# Read in the data
-data = []
-for N in range(2, 14 + 1, 2):
-    # Read N = 2 data
-    for filename in ["../data/sims_n_over_2/sims_{}.csv".format(N),
-                     "../data/sims_1/sims_{0:02d}.csv".format(N),
-                     "../data/sims_n_over_2/noise_sims_{0:02d}.csv".format(N)]:
+    # Read in the data
+    data = []
+    for N in range(2, 14 + 1, 2):
+        # Read N = 2 data
+        for filename in ["../data/sims_n_over_2/sims_{}.csv".format(N),
+                         "../data/sims_1/sims_{0:02d}.csv".format(N)]:
 
-        noise = "noise" in filename
-        i = 1 if "sims_1/" in filename else N // 2
+            noise = "noise" in filename
+            i = 1 if "sims_1/" in filename else N // 2
 
-        try:
-            with open(filename, "r") as f:
-                reader = csv.reader(f)
-                for row in reader:
+            try:
+                with open(filename, "r") as f:
+                    reader = csv.reader(f)
+                    for row in reader:
 
-                    index1, index2, indexwinner, winnercount = row
+                        index1, index2, indexwinner, winnercount = row
 
-                    p1 = index_to_players[index1]
-                    p2 = index_to_players[index2]
-                    winner = index_to_players[indexwinner]
+                        p1 = index_to_players[index1]
+                        p2 = index_to_players[index2]
+                        winner = index_to_players[indexwinner]
 
-                    data.append([noise, int(N), i, p1, p2, winner, int(winnercount)])
-        except FileNotFoundError:
-            pass
+                        data.append([noise, int(N), i, p1, p2, winner, int(winnercount)])
+            except FileNotFoundError:
+                pass
 
[…]

### 2017-04-24 src/write_fitness.py

@@ -1,0 +1,44 @@
+"""
+A script to write the relative fitness to file
+"""
+import pandas as pd
+import theoretic
+
+def read():
+    summary = pd.read_csv("../data/sims_summary.csv")
+
+    columns = [["player", "opponent", "N", "Noise", "$r_1$", "$r_{N/2}$"],
+               ["player", "opponent", "N", "Noise", "$r_{N-1}$"]]
+    dfs = [[], []]
+    for (player, N, opponent, Noise), df in summary.groupby(["P1", "N",
+                                                             "P2", "Noise"]):
+        try:
+            p = df[df["i"] == 1].iloc[0]["P1 fixation"]
+            r1 = theoretic.find_relative_fitness(N, 1, p)
+        except (IndexError, RuntimeError):
+            r1 = float("nan")
+
+        try:
+            p = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
+            rnover2 = theoretic.find_relative_fitness(N, N / 2, p)
+        except (IndexError, RuntimeError):
+            rnover2 = float("nan")
+
+        try:
+            p = df[df["i"] == df["N"] - 1].iloc[0]["P1 fixation"]
+            rminus1 = theoretic.find_relative_fitness(N, N - 1, p)
+        except (IndexError, RuntimeError):
+            rminus1 = float("nan")
+
+        dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, r1, rnover2]],
+                                   columns=columns[0]))
+        dfs[1].append(pd.DataFrame([[opponent, player, N, Noise, rminus1]],
+                                   columns=columns[1]))
+
+    dfs = [pd.concat(dfs[0]), pd.concat(dfs[1])]
+
+    return dfs[0].merge(dfs[1], on=["player", "N","opponent", "Noise"])
+
+if __name__ == "__main__":
+    fitness_df = read()
+    fitness_df.to_csv("../data/relative_fitness.csv")

### 2017-04-24 src/theoretic.py
Add code to numerically find relative fitness.
Also remove the Noisy data from the cleaning step.

@@ -4,6 +4,9 @@ Code to calculate analytic fixation probabilities
 import unittest
 import numpy as np
 import math
+import functools
+
+from scipy.optimize import newton
 
 def scores(strategy_pair, utilities):
     """
@@ -93,6 +96,40 @@ def fixation(strategy_pair, N, i, utilities,
     if i > 1:
         return (1 + s[i - 2]) / (1 + s[-1])
     return 1 / (1 + s[-1])
+
+
+def phi(N, i, r):
+    """
+    The fixation probability in a population with constant fitness r
+    """
+    return (1 - 1/(r ** i)) / (1 - 1/(r ** N))
+
+def phi_prime(N, i, r):
+    """
+    The derivative of `phi` (used for numerical root)
+    """
+    numerator = r ** (N - i - 1) * (-N * r ** i + N + i * r ** N - i)
+    denominator =(r ** (2 * N) - 2 * r ** N + 1)
+    return numerator / denominator
+
+def phi_prime2(N, i, r):
+    """
+    The second derivative of `phi` (used for numerical root)
+    """
+    numerator = r ** (N - i - 2) * (2 * N ** 2 * (r ** i - 1) + N * (r ** N - 1) * (N * (r ** i - 1) - 2 * i + r ** i - 1) - i * (i + 1) * (r ** N - 1) ** 2)
+    denominator = (r**N - 1)**3
+    return numerator / denominator
+
+@functools.lru_cache()
+def find_relative_fitness(N, i, p, initial_r=1.2):
+    """
+    Obtain constant fitness rate that corresponds to a given fixation
+    probability p.
+    """
+    f = lambda r: phi(N, i, r) - p
+    fprime = lambda r:phi_prime(N, i, r)
+    fprime2 = lambda r:phi_prime2(N, i, r)
+    return newton(f, x0=initial_r, fprime=fprime, fprime2=fprime2)
 
 #########
 # Tests #

### 2017-04-24 src/write_fitness.py
Write a final data set with all data.

@@ -7,32 +7,38 @@ import theoretic
 def read():
     summary = pd.read_csv("../data/sims_summary.csv")
 
-    columns = [["player", "opponent", "N", "Noise", "$r_1$", "$r_{N/2}$"],
-               ["player", "opponent", "N", "Noise", "$r_{N-1}$"]]
+    columns = [["player", "opponent", "N", "Noise", "$p_1$", "$p_{N/2}$",
+                "$r_1$", "$r_{N/2}$"],
+               ["player", "opponent", "N", "Noise", "$p_{N-1}$", "$r_{N-1}$"]]
     dfs = [[], []]
     for (player, N, opponent, Noise), df in summary.groupby(["P1", "N",
                                                              "P2", "Noise"]):
         try:
-            p = df[df["i"] == 1].iloc[0]["P1 fixation"]
-            r1 = theoretic.find_relative_fitness(N, 1, p)
+            p1 = df[df["i"] == 1].iloc[0]["P1 fixation"]
+            r1 = theoretic.find_relative_fitness(N, 1, p1)
         except (IndexError, RuntimeError):
+            p1 = float("nan")
             r1 = float("nan")
 
         try:
-            p = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
-            rnover2 = theoretic.find_relative_fitness(N, N / 2, p)
+            pnover2 = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
+            rnover2 = theoretic.find_relative_fitness(N, N / 2, pnover2)
         except (IndexError, RuntimeError):
+            pnover2 = float("nan")
             rnover2 = float("nan")
 
         try:
-            p = df[df["i"] == df["N"] - 1].iloc[0]["P1 fixation"]
-            rminus1 = theoretic.find_relative_fitness(N, N - 1, p)
+            pminus1 = df[df["i"] == df["N"] - 1].iloc[0]["P1 fixation"]
+            rminus1 = theoretic.find_relative_fitness(N, N - 1, pminus1)
         except (IndexError, RuntimeError):
+            pminus1 = float("nan")
             rminus1 = float("nan")
 
-        dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, r1, rnover2]],
+        dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, p1, pnover2,
+                                     r1, rnover2]],
                                    columns=columns[0]))
[…]

### 2017-04-24 tex/main.tex
Change title: numerical -> empirical
Add a `main.csv` data that makes all analysis easier.

--- 2017-04-21 tex/main.tex
@@
 % Title
-\title{A numerical study of fixation probabilities for strategies in the
+\title{An empirical study of fixation for strategies in the
        Iterated Prisoner's Dilemma}
@@
 players are subject to uncertainty. This is referred to as noise and has been
-considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}. Noise is
-also considered here.
+considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}.
 
@@
 
-Figures~\ref{fig:fixation_heatmap_1_std},~\ref{fig:fixation_heatmap_n_over_2_std}
-and~\ref{fig:fixation_heatmap_n_over_2_noise} shows the fixation rates of each
+Figures~\ref{fig:fixation_heatmap_invade}
+and~\ref{fig:fixation_heatmap_coexist} show the fixation rates of each
 player on the y axis against each player on the x axis.
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
         \caption{\((N,i)=(2, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_invade.pdf}
         \caption{\((N,i)=(4, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_invade.pdf}
         \caption{\((N,i)=(6, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_invade.pdf}
         \caption{\((N,i)=(8, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_invade.pdf}
         \caption{\((N,i)=(10, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
         \caption{\((N,i)=(12, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_invade.pdf}
         \caption{\((N,i)=(14, 1)\)}
@@
     \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
-    \label{fig:fixation_heatmap_1_std}
+    \label{fig:fixation_heatmap_invade}
 \end{figure}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_coexist.pdf}
         \caption{\((N,i)=(2, 1)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_coexist.pdf}
         \caption{\((N,i)=(4, 2)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_coexist.pdf}
         \caption{\((N,i)=(6, 3)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_coexist.pdf}
         \caption{\((N,i)=(8, 4)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_coexist.pdf}
         \caption{\((N,i)=(10, 5)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_coexist.pdf}
         \caption{\((N,i)=(12, 6)\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_std.pdf}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_coexist.pdf}
         \caption{\((N,i)=(14, 7)\)}
@@
     \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
-    \label{fig:fixation_heatmap_n_over_2_std}
+    \label{fig:fixation_heatmap_coexist}
 \end{figure}
 
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_1_noise.pdf}
-        \caption{\((N,i)=(2, 1)\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_2_noise.pdf}
-        \caption{\((N,i)=(4, 2)\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_3_noise.pdf}
-        \caption{\((N,i)=(6, 3)\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_4_noise.pdf}
-        \caption{\((N,i)=(8, 4)\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_5_noise.pdf}
-        \caption{\((N,i)=(10, 5)\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_6_noise.pdf}
-        \caption{\((N,i)=(12, 6)\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_7_noise.pdf}
-        \caption{\((N,i)=(14, 7)\)}
-    \end{subfigure}%
-    \caption{Pairwise fixation probabilities of all strategies with noise}
-    \label{fig:fixation_heatmap_n_over_2_noise}
-\end{figure}
-
-Figure~\ref{fig:invasion_boxplot_std} shows the fixation probabilities for each
+Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
 strategy when invading another strategy.
-Figure~\ref{fig:resistance_boxplot_std} shows the fixation probabilities for
+Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
 each strategy when resisting another strategy.
-Figure~\ref{fig:coexistance_boxplot_std} shows the fixation probabilities for
+Figure~\ref{fig:coexistance_boxplot_coexist} shows the fixation probabilities for
 each strategy when initially coexisting with another strategy.
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/invasion_boxplot_2_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
         \caption{\(N=2\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/invasion_boxplot_4_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_4_invade.pdf}
         \caption{\(N=4\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/invasion_boxplot_6_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_6_invade.pdf}
         \caption{\(N=6\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_8_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_8_invade.pdf}
         %\caption{\(N=8\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_10_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_10_invade.pdf}
         %\caption{\(N=10\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_12_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
         %\caption{\(N=12\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/invasion_boxplot_14_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_14_invade.pdf}
         %\caption{\(N=14\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/resistance_boxplot_2_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_2_resist.pdf}
         \caption{\(N=2\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/resistance_boxplot_4_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_4_resist.pdf}
         \caption{\(N=4\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/resistance_boxplot_6_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_6_resist.pdf}
         \caption{\(N=6\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_8_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_8_resist.pdf}
         %\caption{\(N=8\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_10_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_10_resist.pdf}
         %\caption{\(N=10\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_12_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
         %\caption{\(N=12\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/resistance_boxplot_14_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_14_resist.pdf}
         %\caption{\(N=14\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_2_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_2_coexist.pdf}
         \caption{\(N=2\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_4_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_4_coexist.pdf}
         %\caption{\(N=4\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_6_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_6_coexist.pdf}
         %\caption{\(N=6\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_8_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_8_coexist.pdf}
         \caption{\(N=8\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_10_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_10_coexist.pdf}
         %\caption{\(N=10\)}
@@
         %\centering
-        %\includegraphics[width=\textwidth]{../img/coexistance_boxplot_12_std.pdf}
+        %\includegraphics[width=\textwidth]{../img/boxplot_12_coexist.pdf}
         %\caption{\(N=12\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/coexistance_boxplot_14_std.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_14_coexist.pdf}
         \caption{\(N=14\)}
@@
 
-Figures~\ref{fig:ranks_v_size_invasion},~\ref{fig:ranks_v_size_resistance}
+Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
 and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
@@
     \centering
-    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invasion.pdf}
-    \caption{Invasion}
-    \label{fig:ranks_v_size_invasion}
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invade.pdf}
+    \caption{invade}
+    \label{fig:ranks_v_size_invade}
 \end{figure}
@@
     \centering
-    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resistance.pdf}
-    \caption{Resistance}
-    \label{fig:ranks_v_size_resistance}
+    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resist.pdf}
+    \caption{resist}
+    \label{fig:ranks_v_size_resist}
 \end{figure}
@@
     \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invasion.pdf}
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invade.pdf}
     \caption{Relationship between Median rank for population size for strategies
@@
     \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resistance.pdf}
+    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resist.pdf}
     \caption{Relationship between Median rank for population size for strategies
@@
 
-Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
-show the coefficients and \(R^2\) value of the linear model relating the rank in
-a particular sized population to the ranks in other populations sizes.
+Tables~\ref{tbl:linear_coeficients_invade},~\ref{tbl:linear_coeficients_resist}
+and~\ref{tbl:linear_coeficients_coexist} show the coefficients and \(R^2\) value
+of the linear model relating the rank in a particular sized population to the
+ranks in other populations sizes.
 % TODO Discuss these tables: show that none of the models are great (R^2) BUT it
@@
         \centering
-        \input{"../tbl/linear_coeficients_invasion.tex"}
+        \input{"../tbl/linear_coeficients_invade.tex"}
         \caption{Linear model coefficients for ranks for invasion}
-        \label{tbl:linear_coeficients_invasion}
+        \label{tbl:linear_coeficients_invade}
     \end{subfigure}%
@@
         \centering
-        \input{"../tbl/linear_coeficients_resistance.tex"}
+        \input{"../tbl/linear_coeficients_resist.tex"}
         \caption{Linear model coefficients for ranks for resistance}
-        \label{tbl:linear_coeficients_resistance}
+        \label{tbl:linear_coeficients_resist}
     \end{subfigure}
@@
 % Dyson work: "ZD strategies win matches but not tournaments".
-% TODO Include discussion about noise.
 

### 2017-04-24 src/write_fitness.py

@@ -1,5 +1,8 @@
 """
 A script to write the relative fitness to file
+
+TODO: Get rid of the intermediate step in `clean_raw_moran.py` and do it all in
+one go.
 """
 import pandas as pd
 import theoretic
@@ -15,24 +18,27 @@ def read():
                                                              "P2", "Noise"]):
         try:
             p1 = df[df["i"] == 1].iloc[0]["P1 fixation"]
-            r1 = theoretic.find_relative_fitness(N, 1, p1)
-        except (IndexError, RuntimeError):
+            pminus1 = df[df["i"] == 1].iloc[0]["P2 fixation"]
+            pnover2 = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
+        except IndexError:
             p1 = float("nan")
+            pminus1 = float("nan")
+            pnover2 = float("nan")
+
+        try:
+            r1 = theoretic.find_relative_fitness(N, 1, p1)
+        except RuntimeError:
             r1 = float("nan")
 
         try:
-            pnover2 = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
-            rnover2 = theoretic.find_relative_fitness(N, N / 2, pnover2)
-        except (IndexError, RuntimeError):
-            pnover2 = float("nan")
-            rnover2 = float("nan")
+            rminus1 = theoretic.find_relative_fitness(N, N - 1, pminus1)
+        except RuntimeError:
+            rminus1 = float("nan")
 
         try:
-            pminus1 = df[df["i"] == df["N"] - 1].iloc[0]["P1 fixation"]
-            rminus1 = theoretic.find_relative_fitness(N, N - 1, pminus1)
-        except (IndexError, RuntimeError):
-            pminus1 = float("nan")
-            rminus1 = float("nan")
+            rnover2 = theoretic.find_relative_fitness(N, N / 2, pnover2)
+        except RuntimeError:
+            rnover2 = float("nan")
 
         dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, p1, pnover2,
                                      r1, rnover2]],
@@ -47,4 +53,5 @@ def read():
 
 if __name__ == "__main__":
     fitness_df = read()
-    fitness_df.to_csv("../data/main.csv")
+    fitness_df = fitness_df[~fitness_df["Noise"]].drop("Noise", axis=1)
+    fitness_df.to_csv("../data/main.csv", index=False)

### 2017-04-24 src/clean_raw_moran.py
Add a `main.csv` data that makes all analysis easier.

@@ -68,6 +68,6 @@ if __name__ == "__main__":
     print("Writing summary data")
     write(full_data)
 
-    print("Computing relative fitness")
+    print("Writing final data file")
     fitness_df = write_fitness.read()
-    fitness_df.to_csv("../data/relative_fitness.csv")
+    fitness_df.to_csv("../data/main.csv")

### 2017-04-25 tex/main.tex
Add more data.

@@
 simulated results to analytical results. The main results of this manuscript are
-presented in Section~\ref{sec:numerical_results} which will present a detailed
+presented in Section~\ref{sec:empirical_results} which will present a detailed
 analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
@@
 
-\section{Numerical results}\label{sec:numerical_results}
+\section{Empirical results}\label{sec:empirical_results}
 
-Figures~\ref{fig:fixation_heatmap_invade}
-and~\ref{fig:fixation_heatmap_coexist} show the fixation rates of each
-player on the y axis against each player on the x axis.
+\subsection{Strong invaders}\label{sec:strong_invaders}
+
+Figures~\ref{fig:fixation_heatmap_invade} shows the pairwise fitness for
+strategies on the columns axis invading a population of strategies on the row
+axis.
 
@@
     \label{fig:fixation_heatmap_invade}
+\end{figure}
+
+Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
+strategy when invading another strategy.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/boxplot_4_invade.pdf}
+        \caption{\(N=4\)}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/boxplot_6_invade.pdf}
+        \caption{\(N=6\)}
+    \end{subfigure}%
+
+    % TODO be more selective here: just picking out the ones for which we
+    % currently have data
+    %\begin{subfigure}[htbp]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/boxplot_8_invade.pdf}
+        %\caption{\(N=8\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/boxplot_10_invade.pdf}
+        %\caption{\(N=10\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
+        %\caption{\(N=12\)}
+    %\end{subfigure}%
+
+    %\begin{subfigure}[t]{\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{../img/boxplot_14_invade.pdf}
+        %\caption{\(N=14\)}
+    %\end{subfigure}%
+    \caption{Invasion fixation probabilities of all strategies}
+    \label{fig:invasion_boxplot_std}
 \end{figure}
@@
 
-Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
-strategy when invading another strategy.
 Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
@@
 each strategy when initially coexisting with another strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
-        \caption{\(N=2\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_4_invade.pdf}
-        \caption{\(N=4\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_6_invade.pdf}
-        \caption{\(N=6\)}
-    \end{subfigure}%
-
-    % TODO be more selective here: just picking out the ones for which we
-    % currently have data
-    %\begin{subfigure}[htbp]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_8_invade.pdf}
-        %\caption{\(N=8\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_10_invade.pdf}
-        %\caption{\(N=10\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
-        %\caption{\(N=12\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_14_invade.pdf}
-        %\caption{\(N=14\)}
-    %\end{subfigure}%
-    \caption{Invasion fixation probabilities of all strategies}
-    \label{fig:invasion_boxplot_std}
-\end{figure}
 

### 2017-04-25 src/clean_raw_moran.py
Add more data.

@@ -1,10 +1,5 @@
 """
 A script to clean the raw data
-
-NOTE this script consider P1 v P2 and the same match as P2 v P1 and calculates
-the fixation probabilities by considering both match ups. This holds if the
-Moran process data is generated using N / 2 individuals of the first type in a
-population of size N.
 """
 import csv
 import write_fitness
@@ -19,7 +14,7 @@ def read():
 
     # Read in the data
     data = []
-    for N in range(2, 14 + 1, 2):
+    for N in range(2, 14 + 1):
         # Read N = 2 data
         for filename in ["../data/sims_n_over_2/sims_{}.csv".format(N),
                          "../data/sims_1/sims_{0:02d}.csv".format(N)]:
@@ -68,6 +63,7 @@ if __name__ == "__main__":
     print("Writing summary data")
     write(full_data)
 
-    print("Writing final data file")
+    print("Calculating fitness values")
     fitness_df = write_fitness.read()
-    fitness_df.to_csv("../data/main.csv")
+    print("Writing main data")
+    write_fitness.write(fitness_df)

### 2017-04-25 src/write_fitness.py

@@ -19,7 +19,10 @@ def read():
         try:
             p1 = df[df["i"] == 1].iloc[0]["P1 fixation"]
             pminus1 = df[df["i"] == 1].iloc[0]["P2 fixation"]
-            pnover2 = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
+            if N % 2 == 0:
+                pnover2 = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
+            else:
+                pnover2 = float("nan")
         except IndexError:
             p1 = float("nan")
             pminus1 = float("nan")
@@ -35,9 +38,12 @@ def read():
         except RuntimeError:
             rminus1 = float("nan")
 
-        try:
-            rnover2 = theoretic.find_relative_fitness(N, N / 2, pnover2)
-        except RuntimeError:
+        if N % 2 == 0:
+            try:
+                rnover2 = theoretic.find_relative_fitness(N, N / 2, pnover2)
+            except RuntimeError:
+                rnover2 = float("nan")
+        else:
             rnover2 = float("nan")
 
         dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, p1, pnover2,
@@ -51,7 +57,10 @@ def read():
 
     return dfs[0].merge(dfs[1], on=["player", "N","opponent", "Noise"])
 
+def write(df):
+    df = df[~df["Noise"]].drop("Noise", axis=1)
+    df.to_csv("../data/main.csv", index=False)
+
 if __name__ == "__main__":
     fitness_df = read()
-    fitness_df = fitness_df[~fitness_df["Noise"]].drop("Noise", axis=1)
-    fitness_df.to_csv("../data/main.csv", index=False)
+    write(fitness_df)

### 2017-04-26 tex/main.tex
Change a number of styles of plots and writing.
Modified the format from horizontal to vertical and I also used a
correlation matrix (which was essentially what I was doing before).

@@
 Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
-process. The Moran process is a stochastic birth death process on a finite
-population in which the population size stays constant over time. Individuals
-are \textbf{selected} according to a given fitness landscape. Once selected, a
-given individual is reproduced and similarly another individual is chosen to be
+process. This process is a stochastic birth death process on a finite population
+in which the population size stays constant over time. Individuals are
+\textbf{selected} according to a given fitness landscape. Once selected, a given
+individual is reproduced and similarly another individual is chosen to be
 removed from the population. In some settings mutation is also considered but
@@
 individual. The probability with which a given strategy is the survivor is
-called the absorption probability. A more detailed analytic description of this
+called the fixation probability. A more detailed analytic description of this
 is given in Section~\ref{sec:validation}.
@@
 The Moran process was initially introduced in \cite{Moran1957} in a genetic
-setting. It has sine been used in a variety of settings including the
+setting. It has since been used in a variety of settings including the
 understanding of the spread of cooperative behaviour. However, as stated before,
@@
 for the study of the IPD\@. The strategies and simulation frameworks are
-automatically tested in accordance to best practice. The large number of
-strategies are available thanks to the open source nature of the project with
-over 40 contributions made by different programmers. Thus by considering Moran
-processes with population size greater than 2 we are taking in to account the
-effect of complex population dynamics. By considering sophisticated strategies
-we are taking in to effect the reputation of a strategy during each interaction.
+automatically tested in accordance to best research software practice. The large
+number of strategies are available thanks to the open source nature of the
+project with over 40 contributions made by different programmers. Thus by
+considering Moran processes with population size greater than 2 we are taking in
+to account the effect of complex population dynamics. By considering
+sophisticated strategies we are taking in to effect the reputation of a strategy
+during each interaction.
 
@@
 information about each player can be obtained in the documentation for
-\cite{axelrodproject}. The memory depth of the used strategies is shown in
-Table~\ref{tbl:memory_depth_count}.
+\cite{axelrodproject}. There are \input{../tbl/num_stochastic.tex}stochastic and
+\input{../tbl/num_deterministic.tex}deterministic strategies. Their memory
+depth is shown in Table~\ref{tbl:memory_depth_count}.
 
 \begin{table}[!hbtp]
-    \centering
-        \begin{subfigure}[t]{\textwidth}
     \centering
@@
         \label{tbl:memory_depth_count}
-        \end{subfigure}
-        \vspace{.5cm}
-
-        \begin{subfigure}[t]{\textwidth}
-            \centering
-                \input{../tbl/stochastic_count.tex}
-                \caption{Stochastic versus deterministic}
-                \label{tbl:stochastic_count}
-        \end{subfigure}
-        \caption{Summary of properties of used strategies}
 \end{table}
 
-All strategies are paired and these pairs are used in 2000 repetitions of a
+All strategies are paired and these pairs are used in 1000 repetitions of a
 Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
@@
 each value of \(N\).
+% TODO The above is no longer true.
 
@@
 interaction between two players within the Moran process the outcome is sampled
-from a pre computed cache of 1000 match outcomes. This is carried out using the
-approximate Moran process implemented in \cite{axelrodproject}.
+from a pre computed cache of 1000 match outcomes. This is carried out using an
+software written for the purpose of this work. This has been
+implemented in \cite{axelrodproject} ensuring that it can be used to either
+reproduce the work or carry out further work.
 
-As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
-between two players that over the 1000 outcomes gives 971 different scores.
+Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
+the number of outcomes between all strategy pairs.
+Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
+stochastic matches have less than 786 unique outcomes whilst the maximum number
+is 971. This ensures that using a set of cached results from 1000 precomputed
+matches is sufficient for the analysis taking place here.
 
-\begin{figure}[!htbp]
+\begin{figure}[!hbtp]
     \centering
-    \includegraphics[width=.4\textwidth]{../img/players_with_most_scores.pdf}
-    \caption{All possible scores for the pair of strategies that have the most
-    different number of match outcomes}
-    \label{fig:players_with_most_scores}
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includegraphics[width=.9\textwidth]{../img/number_of_match_outcomes.pdf}
+        \caption{All matches}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includegraphics[width=.9\textwidth]{../img/number_of_stochastic_match_outcomes.pdf}
+        \caption{Stochastic matches}
+    \end{subfigure}%
+    \caption{The distribution of the number of unique outcomes used as the
+    cached results}
+    \label{fig:number_of_stochastic_match_outcomes}
 \end{figure}
 
-A variety of software libraries have been used in this work:
+\begin{table}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \input{../tbl/number_of_match_outcomes.tex}
+        \caption{All matches}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \input{../tbl/number_of_stochastic_match_outcomes.tex}
+        \caption{Stochastic matches}
+    \end{subfigure}%
+    \caption{Summary statistics for the number of different match outcomes used
+    as the cached results}
+    \label{tbl:number_of_stochastic_match_outcomes}
+\end{table}
 
-\begin{itemize}
-    \item The Axelrod library (IPD strategies and Moran processes)
-        \cite{axelrodproject}.
-    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
-    \item The pandas and numpy libraries (data manipulation)
-        \cite{mckinney2010data, walt2011numpy}.
-\end{itemize}
-
-Section~\ref{sec:validation} will validate this approach against theoretic
-results.
+Section~\ref{sec:validation} will validate the methodology used here against
+known theoretic results.
 
@@
 
-Using this comparisons of \(x_{N/2}\) are shown in
+Using this comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
 Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
@@
 weakness of the analytical formulae that relies on the average payoffs. A
-detailed analysis of the 172 strategies considered will be shown in the next
-Section.
+detailed analysis of the 172 strategies considered, using direct Moran processes
+will be shown in the next Section.
 
@@
 
+This section will outline the data analysis carried out:
+
+\begin{itemize}
+    \item Section~\ref{sec:two_individuals} will consider the specific case of
+        \(N=2\).
+    \item Section~\ref{sec:strong_invaders} will investigate the effect of
+        population size on the ability of a strategy to invade another
+        population. This will highlight how complex strategies with long
+        memories outperform simpler strategies.
+    \item Section~\ref{sec:strong_resistors} will similarly investigate the
+        ability to defend against an invasion.
+    \item Section~\ref{sec:population_size} will investigate the relationship
+        between performance for differing population sizes. This highlights the
+        importance of considering population dynamics over large populations.
+    \item Section~\ref{sec:fitness} will calculate the relative fitness of all
+        strategies.
+\end{itemize}
+
+\subsection{The special case of \(N=2\)}\label{sec:two_individuals}
+
+% TODO Move the case 2 graphics to here.
+
 \subsection{Strong invaders}\label{sec:strong_invaders}
 
-Figures~\ref{fig:fixation_heatmap_invade} shows the pairwise fitness for
-strategies on the columns axis invading a population of strategies on the row
-axis.
+In this section \(x_i\) will be investigated: the probability of 1 individual of
+a given type successfully becoming fixated in a population of \(N - 1\) other
+individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
+the players along the vertical axis when matched against the players on the
+horizontal axis. It can be seen that invasion is in general more challenging for
+\(N=7\) and \(N=11\) in comparison to \(N=2\).
+%TODO Change this to N=14
+This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
+showing the median fixation as well as the neutral fixation for each given
+scenario.
 
@@
         \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
-        \caption{\((N,i)=(2, 1)\)}
+        \caption{\(N=2\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_invade.pdf}
-        \caption{\((N,i)=(4, 1)\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
+        \caption{\(N=7\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_invade.pdf}
-        \caption{\((N,i)=(6, 1)\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_invade.pdf}
+        \caption{\(N=11\)}
+
+    %TODO Replace N=11 with N=14
     \end{subfigure}%
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_invade.pdf}
-        \caption{\((N,i)=(8, 1)\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_invade.pdf}
-        \caption{\((N,i)=(10, 1)\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
-        \caption{\((N,i)=(12, 1)\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_invade.pdf}
-        \caption{\((N,i)=(14, 1)\)}
-    \end{subfigure}%
     \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
     \label{fig:fixation_heatmap_invade}
-\end{figure}
-
-Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
-strategy when invading another strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
-        \caption{\(N=2\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_4_invade.pdf}
-        \caption{\(N=4\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_6_invade.pdf}
-        \caption{\(N=6\)}
-    \end{subfigure}%
-
-    % TODO be more selective here: just picking out the ones for which we
-    % currently have data
-    %\begin{subfigure}[htbp]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_8_invade.pdf}
-        %\caption{\(N=8\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_10_invade.pdf}
-        %\caption{\(N=10\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
-        %\caption{\(N=12\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_14_invade.pdf}
-        %\caption{\(N=14\)}
-    %\end{subfigure}%
-    \caption{Invasion fixation probabilities of all strategies}
-    \label{fig:invasion_boxplot_std}
 \end{figure}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_coexist.pdf}
-        \caption{\((N,i)=(2, 1)\)}
+        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
+        \caption{\(N=2\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_4_coexist.pdf}
-        \caption{\((N,i)=(4, 2)\)}
+        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
+        \caption{\(N=7\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_6_coexist.pdf}
-        \caption{\((N,i)=(6, 3)\)}
+        \includegraphics[width=\textwidth]{../img/boxplot_11_invade.pdf}
+        \caption{\(N=11\)}
     \end{subfigure}%
 
+    % TODO Replace N=11 with N=14 (when we have more data).
+    \caption{Median probabilities \(x_{1}\) of all strategies as well as the
+    neutral fixation probability}
+    \label{fig:fixation_boxplot_invade}
+\end{figure}
+
+For \(N\in\{2, 7, 11\}\) the top five strategies are given in
+% TODO Change N=11 to N=14
+Tables~\ref{tbl:top_five_invade}. It can be seen that for \(N=2\), as described
+in~\cite{Press2012}, zero determinant strategies perform well. There is a
+single strategy with infinite memory in the top five but this is in fact a meta
+strategy that plays with a team of memory one strategies picking out the top
+performer at each stage. The remaining strategy ``Feld" is the corresponding
+strategy submitted to the first tournament by Axelrod~\cite{Axelrod1980a}. All
+these strategies are stochastic.
+
+\begin{table}[!hbtp]
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{../tbl/summary_top_2_invade.tex}
+        \caption{\(N=2\)}
+    \end{subfigure}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{../tbl/summary_top_7_invade.tex}
+        \caption{\(N=7\)}
+    \end{subfigure}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{../tbl/summary_top_11_invade.tex}
+        \caption{\(N=11\)}
+    \end{subfigure}
+    %TODO Change N=11 to N=14
+    \caption{Properties of top five invaders}
+    \label{tbl:top_five_invade}
+\end{table}
+
+% TODO Write a little conclusion about invaders and introduce next section.
+
+\subsection{Strong resistors}\label{sec:strong_resistors}
+
+\begin{figure}[!hbtp]
+    \centering
     \begin{subfigure}[t]{.3\textwidth}
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_8_coexist.pdf}
-        \caption{\((N,i)=(8, 4)\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
+        \caption{\(N=2\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_10_coexist.pdf}
-        \caption{\((N,i)=(10, 5)\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
+        \caption{\(N=7\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_coexist.pdf}
-        \caption{\((N,i)=(12, 6)\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_resist.pdf}
+        \caption{\(N=11\)}
+
+    %TODO Replace N=11 with N=14
     \end{subfigure}%
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_coexist.pdf}
-        \caption{\((N,i)=(14, 7)\)}
-    \end{subfigure}%
-    \caption{Pairwise fixation probability \(x_{N/2}\) of all strategies}
-    \label{fig:fixation_heatmap_coexist}
-\end{figure}
-
-Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
-each strategy when resisting another strategy.
-Figure~\ref{fig:coexistance_boxplot_coexist} shows the fixation probabilities for
-each strategy when initially coexisting with another strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_2_resist.pdf}
-        \caption{\(N=2\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_4_resist.pdf}
-        \caption{\(N=4\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_6_resist.pdf}
-        \caption{\(N=6\)}
-    \end{subfigure}%
-
-    % TODO be more selective here: just picking out the ones for which we
-    % currently have data
-    %\begin{subfigure}[htbp]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_8_resist.pdf}
-        %\caption{\(N=8\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_10_resist.pdf}
-        %\caption{\(N=10\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
-        %\caption{\(N=12\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_14_resist.pdf}
-        %\caption{\(N=14\)}
-    %\end{subfigure}%
-    \caption{Resistance fixation probabilities of all strategies}
-    \label{fig:resistance_boxplot_std}
+    \caption{Pairwise fixation probability \(x_{N-1}\) of all strategies}
+    \label{fig:fixation_heatmap_resist}
 \end{figure}
@@
     \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
+        \caption{\(N=2\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
+        \caption{\(N=7\)}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../img/boxplot_11_resist.pdf}
+        \caption{\(N=11\)}
+    \end{subfigure}%
+
+    % TODO Replace N=11 with N=14 (when we have more data).
+    \caption{Median probabilities \(x_{N-1}\) of all strategies as well as the
+    neutral fixation probability}
+    \label{fig:fixation_boxplot_resist}
+\end{figure}
+
+\begin{table}[!hbtp]
     \begin{subfigure}[t]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_2_coexist.pdf}
-        \caption{\(N=2\)}
-    \end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_4_coexist.pdf}
-        %\caption{\(N=4\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_6_coexist.pdf}
-        %\caption{\(N=6\)}
-    %\end{subfigure}%
-
-    \begin{subfigure}[htbp]{\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_8_coexist.pdf}
-        \caption{\(N=8\)}
-    \end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_10_coexist.pdf}
-        %\caption{\(N=10\)}
-    %\end{subfigure}%
-
-    %\begin{subfigure}[t]{\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{../img/boxplot_12_coexist.pdf}
-        %\caption{\(N=12\)}
-    %\end{subfigure}%
-
+        \input{../tbl/summary_top_7_resist.tex}
+        \caption{\(N=7\)}
+    \end{subfigure}
     \begin{subfigure}[t]{\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_14_coexist.pdf}
-        \caption{\(N=14\)}
-    \end{subfigure}%
-    \caption{Coexistance fixation probabilities of all strategies}
-    \label{fig:coexistance_boxplot_std}
-\end{figure}
+        \input{../tbl/summary_top_11_resist.tex}
+        \caption{\(N=11\)}
+    \end{subfigure}
+    %TODO Change N=11 to N=14
+    \caption{Properties of top five strategies resistors}
+    \label{tbl:top_five_invade}
+\end{table}
+
+\subsection{The effect of population size}\label{sec:population_size}
 
@@
 and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
-population size in the standard and noisy settings. Note that these ranks are
+population size. Note that these ranks are
 not necessarily integers as group ties are given the average rank.
@@
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_invade.pdf}
-    \caption{Relationship between Median rank for population size for strategies
-    invading}
-    \label{fig:relationship_ranks_v_size_invasion}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_resist.pdf}
-    \caption{Relationship between Median rank for population size for strategies
-    resisting}
-    \label{fig:relationship_ranks_v_size_resistance}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{../img/relationship_between_median_ranks_coexist.pdf}
-    \caption{Relationship between Median rank for population size for strategies
-    coexisting}
-    \label{fig:relationship_ranks_v_size_coexist}
-\end{figure}
-
-Tables~\ref{tbl:linear_coeficients_invade},~\ref{tbl:linear_coeficients_resist}
-and~\ref{tbl:linear_coeficients_coexist} show the coefficients and \(R^2\) value
-of the linear model relating the rank in a particular sized population to the
-ranks in other populations sizes.
-% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
-% does show that the coefficient of the N=2 column is always low whereas the
-% coefficient of the N=14 column is high even in the N=4 row. So how well you do
-% in  a match (N=2) has got very little to do with an evolutionary process.
+Tables~\ref{tbl:correlation_coeficients_invade},~\ref{tbl:correlation_coeficients_resist}
+and~\ref{tbl:correlation_coeficients_coexist} show the correlation coefficients
+of the ranks in of strategies in differing population size. This is shown
+graphically in Figure~\ref{fig:correlation_coefficients}. It is immediate to
+note that how well a strategy performs in any Moran process for \(N>2\) has
+little to do with the performance for \(N=2\).
+% TODO This is a really good conclusion I think: it shows that when studying
+% population dynamics it is important to consider larger populations.
 
@@
     \centering
-    \begin{subfigure}{.5\textwidth}
+    \begin{subfigure}{\textwidth}
         \centering
-        \input{"../tbl/linear_coeficients_invade.tex"}
-        \caption{Linear model coefficients for ranks for invasion}
-        \label{tbl:linear_coeficients_invade}
+        \input{"../tbl/correlation_coeficients_invade.tex"}
+        \caption{Correlation coefficients for ranks for invasion}
+        \label{tbl:correlation_coeficients_invade}
     \end{subfigure}%
-    ~
-    \begin{subfigure}{.5\textwidth}
+
+    \begin{subfigure}{\textwidth}
         \centering
-        \input{"../tbl/linear_coeficients_resist.tex"}
-        \caption{Linear model coefficients for ranks for resistance}
-        \label{tbl:linear_coeficients_resist}
+        \input{"../tbl/correlation_coeficients_resist.tex"}
+        \caption{Correlation coefficients for ranks for resistance}
+        \label{tbl:correlation_coeficients_resist}
     \end{subfigure}
 
-    \begin{subfigure}{.5\textwidth}
+    \begin{subfigure}{\textwidth}
         \centering
-        \input{"../tbl/linear_coeficients_coexist.tex"}
-        \caption{Linear model coefficients for ranks for coexistance}
-        \label{tbl:linear_coeficients_coexist}
+        \input{"../tbl/correlation_coeficients_coexist.tex"}
+        \caption{Correlation coefficients for ranks for coexistance}
+        \label{tbl:correlation_coeficients_coexist}
     \end{subfigure}
-    \caption{Linear coefficients}
+    \caption{Correlation coefficients}
 \end{table}
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{subfigure}[t]{.3\textwidth}
+		\centering
+		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_invade.pdf}
+		\caption{Rank based on \(x_1\)}
+    \end{subfigure}
+    ~
+	\begin{subfigure}[t]{.3\textwidth}
+		\centering
+		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_resist.pdf}
+        \caption{Rank based on \(x_{N - 1}\)}
+    \end{subfigure}
+    ~
+	\begin{subfigure}[t]{.3\textwidth}
+		\centering
+		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_coexist.pdf}
+        \caption{Rank based on \(x_{N/2}\)}
+    \end{subfigure}
+    \caption{Correlation coefficients for ranks}
+    \label{fig:correlation_coefficients}
+\end{figure}
 
@@
 
+A variety of software libraries have been used in this work:
+
+\begin{itemize}
+    \item The Axelrod library (IPD strategies and Moran processes)
+        \cite{axelrodproject}.
+    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
+    \item The pandas and numpy libraries (data manipulation)
+        \cite{mckinney2010data, walt2011numpy}.
+\end{itemize}
+
 \printbibliography

### 2017-04-27 img/invasion_resistance.tex
More analysis and writing:
- Add discussion about numerical inversion;
- Add plots of relative fitness for validation strategy pairs
- Particular section for N=2

Various other changes.

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, shapes, patterns}

\begin{document}
\begin{tikzpicture}[scale=.9]
	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
        color=red!70, draw=red] {};
	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
        color=red!70, draw=red] {};
	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
        color=red!70, draw=red] {};
	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
        color=red!70, draw=red] {};
	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
\end{tikzpicture}
\end{document}

### 2017-04-27 tex/main.tex
More analysis and writing:
- Add discussion about numerical inversion;
- Add plots of relative fitness for validation strategy pairs
- Particular section for N=2

Various other changes.

@@
 \textit{always cooperate} or \textit{always defect}. This manuscript provides a
-detailed numerical analysis of \textbf{172} complex and adaptive strategies for
+detailed numerical analysis of \textbf{164} complex and adaptive strategies for
 the IPD\@. In this case the relative fitness of a strategy is dependent on the
@@
 The contribution of this work is a detailed and extensive analysis of absorption
-probabilities for 172 strategies. These strategies and the numerical simulations
+probabilities for 164 strategies. These strategies and the numerical simulations
 are from~\cite{axelrodproject} which is an open source research library written
@@
 
-To carry out this large numerical experiment 172 strategies are used from
-\cite{axelrodproject}. These include 169 default strategies in the library at
-the time (excluding strategies classified as having a long run time) as well as
+To carry out this large numerical experiment 164 strategies are used from
+\cite{axelrodproject}. These include 161 default strategies in the library at
+the time (excluding strategies classified as having a long run time and those
+that make use of the length of the game) as well as
 the following 3 finite state machine machine strategies \cite{Ashlock2006}:
@@
 Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
-stochastic matches have less than 786 unique outcomes whilst the maximum number
+stochastic matches have less than 788 unique outcomes whilst the maximum number
 is 971. This ensures that using a set of cached results from 1000 precomputed
@@
 weakness of the analytical formulae that relies on the average payoffs. A
-detailed analysis of the 172 strategies considered, using direct Moran processes
+detailed analysis of the 164 strategies considered, using direct Moran processes
 will be shown in the next Section.
@@
         importance of considering population dynamics over large populations.
-    \item Section~\ref{sec:fitness} will calculate the relative fitness of all
+    \item Section~\ref{sec:relative_fitness} will calculate the relative fitness of all
         strategies.
@@
 
-% TODO Move the case 2 graphics to here.
+The main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
+reflect a strategy's ability to invade or resist invasion.
+% TODO Perhaps mention that a lot of the research in to training fixation of
+% strategies assumes N=2? Is this true?
+For \(N=2\) these two cases coincide. Figure~\ref{fig:fixation_heatmap_2} shows
+all pairwise fixation probabilities for strategies on the vertical column when
+being matched against probabilities on the horizontal column. This is summarised
+in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2} It can be seen
+that, as described in in~\cite{Press2012}, zero determinant strategies perform
+well. The strategy with infinite memory \texttt{Collective} is a strategy with a
+handshake which implies that it will perform well against itself.. There is also
+one of the trained finite state machines in the top five.  The remaining
+strategy ``Feld" is the corresponding strategy submitted to the first tournament
+by Axelrod~\cite{Axelrod1980a}. All these strategies are stochastic.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.5\textwidth]{../img/fixation_heatmap_2_invade.pdf}
+    \caption{The pairwise fixation probabilities for \(N=2\)}
+    \label{fig:fixation_heatmap_2}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.5\textheight]{../img/boxplot_2_invade.pdf}
+    \caption{The median fixation probabilities for \(N=2\)}
+    \label{fig:boxplot_2}
+\end{figure}
+
+\begin{table}[!hbtp]
+    \centering
+    \input{../tbl/summary_top_2_invade.tex}
+    \caption{Summary of top five strategies for \(N=2\)}
+    \label{tbl:summary_top_2}
+\end{table}
+
+As will be demonstrated in Section~\ref{sec:population_size} \(N=2\)
+is a particular case. In the next sections we will pay close attention to
+strategies who are strong invaders/resistors and shown diagrammatically in
+Figure~\ref{fig:invasion_resistance}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \input{../img/invasion_resistance.tex}
+    \caption{A single individual will successfully invade the population with
+    probability \(x_1\). The group of Individuals will successfully resist with
+    probability \(x_{N-1}\)}
+    \label{fig:invasion_resistance}
+\end{figure}
 
@@
 horizontal axis. It can be seen that invasion is in general more challenging for
-\(N=7\) and \(N=11\) in comparison to \(N=2\).
+\(N=7\) and \(N=11\) in comparison to \(N=3\).
 %TODO Change this to N=14
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
-        \caption{\(N=2\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_invade.pdf}
+        \caption{\(N=3\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
-        \caption{\(N=2\)}
+        \includegraphics[width=\textwidth]{../img/boxplot_3_invade.pdf}
+        \caption{\(N=3\)}
     \end{subfigure}%
@@
 
-For \(N\in\{2, 7, 11\}\) the top five strategies are given in
+For \(N\in\{3, 7, 11\}\) the top five strategies are given in
 % TODO Change N=11 to N=14
-Tables~\ref{tbl:top_five_invade}. It can be seen that for \(N=2\), as described
-in~\cite{Press2012}, zero determinant strategies perform well. There is a
-single strategy with infinite memory in the top five but this is in fact a meta
-strategy that plays with a team of memory one strategies picking out the top
-performer at each stage. The remaining strategy ``Feld" is the corresponding
-strategy submitted to the first tournament by Axelrod~\cite{Axelrod1980a}. All
-these strategies are stochastic.
+Tables~\ref{tbl:top_five_invade}.
 
@@
         \centering
-        \input{../tbl/summary_top_2_invade.tex}
-        \caption{\(N=2\)}
+        \input{../tbl/summary_top_3_invade.tex}
+        \caption{\(N=3\)}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
-        \caption{\(N=2\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_resist.pdf}
+        \caption{\(N=3\)}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
+        \includegraphics[width=\textwidth]{../img/boxplot_3_resist.pdf}
         \caption{\(N=2\)}
@@
 \begin{table}[!hbtp]
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{../tbl/summary_top_3_resist.tex}
+        \caption{\(N=3\)}
+    \end{subfigure}
     \begin{subfigure}[t]{\textwidth}
@@
 
+\subsection{Relative fitness}\label{sec:relative_fitness}
+
+Under the assumption of a constant relative fitness \(r\) between two
+strategies~\cite{Nowak} the formula for \(x_i\) (for given \(N, r\) is:
+
+\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness}
+    x_i = x_i(r) = \frac{1-\frac{1}{r^{i}}}{1-\frac{1}{r^{N}}}
+\end{equation}
+
+Figure~\ref{fig:fixation_v_fitness_illustration} shows this function for
+\(N=10\) and \(i\in\{1, 5, 10\}\).
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=.6\textwidth]{../img/fixation_v_fitness_illustration.pdf}
+    \caption{\(x_i(r)\)}
+    \label{fig:fixation_v_fitness_illustration}
+\end{figure}
+
+The first and second derivative of
+(\ref{equ:fixation_probability_with_constant_relative_fitness}) is given by equations
+(\ref{equ:fixation_probability_with_constant_relative_fitness_prime}) and
+(\ref{equ:fixation_probability_with_constant_relative_fitness_prime2}).
+
+\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime}
+    \frac{dx_i}{dr} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime.tex}
+\end{equation}
+
+\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime2}
+    \frac{d^2x_i}{dr^2} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime2.tex}
+\end{equation}
+
+Using these, Halley's method \cite{Alefeld2012} can be used to efficiently
+numerically invert \(x_i(r)\) to obtain a theoretic relative fitness \(r\) that
+gives the calculated \(x_i(r)\) between two strategies for a given \(N, i\).
+% TODO Say more things: I still think this is a bit cylic. The formula we are
+% using assumes a constant relative fitness which we know does not exist.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_fitness.pdf}
+        \caption{Alternator and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_fitness.pdf}
+        \caption{Alternator and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_fitness.pdf}
+        \caption{Alternator and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat_fitness.pdf}
+        \caption{Cooperator and Tit For Tat}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator_fitness.pdf}
+        \caption{Defector and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat_fitness.pdf}
+        \caption{Defector and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
+        \caption{Win Stay Lose Shift and Tit For Tat}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
+        \caption{Alternator and Win Stay Lose Shift}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
+        \caption{Defector and Win Stay Lose Shift}
+    \end{subfigure}%
+    \caption{Estimated relative fitness
+             for \textbf{deterministic} strategies}
+    \label{fig:comparison_deterministic}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Random_v_Cooperator_fitness.pdf}
+        \caption{Random and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Random_v_Defector_fitness.pdf}
+        \caption{Random and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Random_v_Tit_For_Tat_fitness.pdf}
+        \caption{Random and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator_fitness.pdf}
+        \caption{All C or all D and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector_fitness.pdf}
+        \caption{All C or all D and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_fitness.pdf}
+        \caption{Calculator and Random}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD_fitness.pdf}
+        \caption{Calculator and All C or all D}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner_fitness.pdf}
+        \caption{Calculator and Arrogant Q learner}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\textwidth}
+        \centering
+        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat_fitness.pdf}
+        \caption{All C or all D and Tit For Tat}
+    \end{subfigure}%
+    \caption{Estimated relative fitness
+             for \textbf{stochastic} strategies}
+    \label{fig:comparison_stochastic}
+\end{figure}
+
 % TODO Discuss effect of size on performance of strategies. Relate to Press and
 % Dyson work: "ZD strategies win matches but not tournaments".
-
-% TODO Redo everything with Meta strategies? This was a comment by MH. I suggest
-% we leave this for this paper.
 

### 2017-04-28 tex/main.tex
Make possible to get p_1 when p_N/2 incomplete.

@@
 horizontal axis. It can be seen that invasion is in general more challenging for
-\(N=7\) and \(N=11\) in comparison to \(N=3\).
+\(N=7\) and \(N=12\) in comparison to \(N=3\).
 %TODO Change this to N=14
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_invade.pdf}
-        \caption{\(N=11\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
+        \caption{\(N=12\)}
 
-    %TODO Replace N=11 with N=14
+    %TODO Replace N=12 with N=14
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_11_invade.pdf}
-        \caption{\(N=11\)}
+        \includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
+        \caption{\(N=12\)}
     \end{subfigure}%
 
-    % TODO Replace N=11 with N=14 (when we have more data).
+    % TODO Replace N=12 with N=14 (when we have more data).
     \caption{Median probabilities \(x_{1}\) of all strategies as well as the
@@
 
-For \(N\in\{3, 7, 11\}\) the top five strategies are given in
-% TODO Change N=11 to N=14
+For \(N\in\{3, 7, 12\}\) the top five strategies are given in
+% TODO Change N=12 to N=14
 Tables~\ref{tbl:top_five_invade}.
@@
         \centering
-        \input{../tbl/summary_top_11_invade.tex}
-        \caption{\(N=11\)}
+        \input{../tbl/summary_top_12_invade.tex}
+        \caption{\(N=12\)}
     \end{subfigure}
-    %TODO Change N=11 to N=14
+    %TODO Change N=12 to N=14
     \caption{Properties of top five invaders}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_resist.pdf}
-        \caption{\(N=11\)}
+        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_resist.pdf}
+        \caption{\(N=12\)}
 
-    %TODO Replace N=11 with N=14
+    %TODO Replace N=12 with N=14
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_11_resist.pdf}
-        \caption{\(N=11\)}
+        \includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
+        \caption{\(N=12\)}
     \end{subfigure}%
 
-    % TODO Replace N=11 with N=14 (when we have more data).
+    % TODO Replace N=12 with N=14 (when we have more data).
     \caption{Median probabilities \(x_{N-1}\) of all strategies as well as the
@@
         \centering
-        \input{../tbl/summary_top_11_resist.tex}
-        \caption{\(N=11\)}
+        \input{../tbl/summary_top_12_resist.tex}
+        \caption{\(N=12\)}
     \end{subfigure}
-    %TODO Change N=11 to N=14
+    %TODO Change N=12 to N=14
     \caption{Properties of top five strategies resistors}
@@
     \end{subfigure}
-    \caption{Correlation coefficients}
+    \caption{Correlation coefficients of rankings by population size}
 \end{table}
@@
     \end{subfigure}
-    \caption{Correlation coefficients for ranks}
+    \caption{Heatmap of correlation coefficients of rankings by population size}
     \label{fig:correlation_coefficients}

### 2017-04-28 src/write_fitness.py
Make possible to get p_1 when p_N/2 incomplete.

@@ -6,9 +6,11 @@ one go.
 """
 import pandas as pd
 import theoretic
+import tempfile
 
-def read():
+def merged_df(N):
     summary = pd.read_csv("../data/sims_summary.csv")
+    summary = summary[summary["N"] == N]
 
     columns = [["player", "opponent", "N", "Noise", "$p_1$", "$p_{N/2}$",
                 "$r_1$", "$r_{N/2}$"],
@@ -19,14 +21,19 @@ def read():
         try:
             p1 = df[df["i"] == 1].iloc[0]["P1 fixation"]
             pminus1 = df[df["i"] == 1].iloc[0]["P2 fixation"]
+        except IndexError:
+            p1 = float("nan")
+            pminus1 = float("nan")
+
+
+        try:
             if N % 2 == 0:
                 pnover2 = df[df["i"] == df["N"] / 2].iloc[0]["P1 fixation"]
             else:
                 pnover2 = float("nan")
         except IndexError:
-            p1 = float("nan")
-            pminus1 = float("nan")
             pnover2 = float("nan")
+
 
         try:
             r1 = theoretic.find_relative_fitness(N, 1, p1)
@@ -56,6 +63,13 @@ def read():
     dfs = [pd.concat(dfs[0]), pd.concat(dfs[1])]
 
     return dfs[0].merge(dfs[1], on=["player", "N","opponent", "Noise"])
+
+def read():
+    dfs = []
+    for N in range(2, 14 + 1):
+        dfs.append(merged_df(N))
+
+    return pd.concat(dfs)
 
 def write(df):
     df = df[~df["Noise"]].drop("Noise", axis=1)

### 2017-04-28 tex/main.tex
Add some discussion and references.

@@
 process context and only considers specific cases of memory 2 strategies.
-% TODO Is this OK? We should add more.
+% TODO Add discussion about ZD strategies and discuss how this corresponds to
+% case of N = 2. Include pointing at \cite{Adami2013} which discusses how ZD
+% strategies are not fantastic in population dynamics.
+% Add \cite{Li2014}
 
@@
 being matched against probabilities on the horizontal column. This is summarised
-in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2} It can be seen
-that, as described in in~\cite{Press2012}, zero determinant strategies perform
-well. The strategy with infinite memory \texttt{Collective} is a strategy with a
-handshake which implies that it will perform well against itself.. There is also
-one of the trained finite state machines in the top five.  The remaining
-strategy ``Feld" is the corresponding strategy submitted to the first tournament
-by Axelrod~\cite{Axelrod1980a}. All these strategies are stochastic.
+in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2}.
+
+\begin{enumerate}
+    \item The top strategy is an extortionate Zero determinant
+        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
+    \item The Collective strategy has a simple handshake mechanism (a
+        cooperation followed by a defection on the first move). It then either
+        cooperates or defects for all rounds~\cite{Li2009}.  This strategy was
+        specifically designed for Evolutionary processes so it is perhaps also
+        not surprising that it does well here.
+    \item The finite state machine stragegy % TODO Perhaps refer to earlier
+        % discussion in the methodology section about these FSM strategies
+    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
+        first tournament~\cite{Axelrod1980a}: it punishes defections but
+        otherwise defects with a random probability that decays over time.
+    \item The final strategy in the top five is another extortionate Zero
+        determinant strategy~\cite{Press2012} with parameters \(l=p\).
+\end{enumerate}
 
 \begin{figure}[!hbtp]
+    \begin{subfigure}[t]{.4\textwidth}
         \centering
-    \includegraphics[width=.5\textwidth]{../img/fixation_heatmap_2_invade.pdf}
+        \includegraphics[width=\textwidth]{../img/fixation_heatmap_2_invade.pdf}
+        % TODO Remove this: I don't feel it is effective.
         \caption{The pairwise fixation probabilities for \(N=2\)}
         \label{fig:fixation_heatmap_2}
-\end{figure}
-
-\begin{figure}[!hbtp]
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.6\textwidth}
         \centering
-    \includegraphics[height=.5\textheight]{../img/boxplot_2_invade.pdf}
+        \includegraphics[height=.8\textheight]{../img/boxplot_2_invade.pdf}
         \caption{The median fixation probabilities for \(N=2\)}
         \label{fig:boxplot_2}
+    \end{subfigure}
 \end{figure}
@@
     \end{subfigure}%
+    %TODO Remove these? I don't feel they are effective
 
@@
 
-% TODO Write a little conclusion about invaders and introduce next section.
+It can be seen that apart from the Collective strategy, none of the strategies
+of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 12\}\). The new
+% TODO Change N=12 to N=14
+high performing strategies are:
+
+\begin{itemize}
+    \item Predator, a finite state machine described in~\cite{Ashlock2006}.
+    \item Prober 4, complex strategy with an initial 20 move sequence of
+        cooperations and defections~\cite{prison}. This initial sequence serves
+        as some kind of handshake.
+    \item Remorseful Prober, a strategy that will not immediately retaliate when
+        it recognises that the opponent is itself retaliating to a random
+        defection~\cite{Li2011}.
+    \item  Worse and worse 2: plays tit for tat for 20 moves and then defects
+        with with growing probability~\cite{prison}.
+    \item Tester: a strategy submitted to the second of Axelrod's tournaments
+        \cite{Axelrod1980b}.
+        % TODO Check if this list is still correct for N=14
+\end{itemize}
+
+As well as noting that the memory length and complexity of these strategies are
+quite complex it is interesting to note that none of them are akin to memory one
+strategies. Most are not stochastic.
+
+In the next section the performance in terms of \(x_{N-1}\) will be described:
+what strategies are particularly good at resisting an invasion.
 

### 2017-04-29 main.tex
Minor reorganisation of files.

--- 2017-04-28 tex/main.tex
@@
             isbn=true, style=numeric]{biblatex}
-\addbibresource{bibliography.bib}
+\addbibresource{./tex/bibliography.bib}
 
@@
     \centering
-    \input{../img/moran_process.tex}
+    \input{./tex/moran_process.tex}
     \caption{A diagrammatic representation of a Moran process}
@@
 information about each player can be obtained in the documentation for
-\cite{axelrodproject}. There are \input{../tbl/num_stochastic.tex}stochastic and
-\input{../tbl/num_deterministic.tex}deterministic strategies. Their memory
+\cite{axelrodproject}. There are \input{./tex/num_stochastic.tex}stochastic and
+\input{./tex/num_deterministic.tex}deterministic strategies. Their memory
 depth is shown in Table~\ref{tbl:memory_depth_count}.
@@
     \centering
-        \input{../tbl/memory_depth_count.tex}
+        \input{./tex/memory_depth_count.tex}
         \caption{Memory depth}
@@
         \centering
-        \includegraphics[width=.9\textwidth]{../img/number_of_match_outcomes.pdf}
+        \includegraphics[width=.9\textwidth]{./img/number_of_match_outcomes.pdf}
         \caption{All matches}
@@
         \centering
-        \includegraphics[width=.9\textwidth]{../img/number_of_stochastic_match_outcomes.pdf}
+        \includegraphics[width=.9\textwidth]{./img/number_of_stochastic_match_outcomes.pdf}
         \caption{Stochastic matches}
@@
         \centering
-        \input{../tbl/number_of_match_outcomes.tex}
+        \input{./tex/number_of_match_outcomes.tex}
         \caption{All matches}
@@
         \centering
-        \input{../tbl/number_of_stochastic_match_outcomes.tex}
+        \input{./tex/number_of_stochastic_match_outcomes.tex}
         \caption{Stochastic matches}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
         \caption{Alternator and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector.pdf}
         \caption{Alternator and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat.pdf}
         \caption{Alternator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat.pdf}
         \caption{Cooperator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator.pdf}
         \caption{Defector and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat.pdf}
         \caption{Defector and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_v_Cooperator.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator.pdf}
         \caption{Random and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_v_Defector.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector.pdf}
         \caption{Random and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat.pdf}
         \caption{Random and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Cooperator.pdf}
         \caption{All C or all D and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Defector.pdf}
         \caption{All C or all D and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Random.pdf}
         \caption{Calculator and Random}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD.pdf}
         \caption{Calculator and All C or all D}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner.pdf}
         \caption{Calculator and Arrogant Q learner}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Tit_For_Tat.pdf}
         \caption{All C or all D and Tit For Tat}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/fixation_heatmap_2_invade.pdf}
+        \includegraphics[width=\textwidth]{./img/fixation_heatmap_2_invade.pdf}
         % TODO Remove this: I don't feel it is effective.
@@
         \centering
-        \includegraphics[height=.8\textheight]{../img/boxplot_2_invade.pdf}
+        \includegraphics[height=.8\textheight]{./img/boxplot_2_invade.pdf}
         \caption{The median fixation probabilities for \(N=2\)}
@@
     \centering
-    \input{../tbl/summary_top_2_invade.tex}
+    \input{./tex/summary_top_2_invade.tex}
     \caption{Summary of top five strategies for \(N=2\)}
@@
     \centering
-    \input{../img/invasion_resistance.tex}
+    \input{./tex/invasion_resistance.tex}
     \caption{A single individual will successfully invade the population with
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_invade.pdf}
+        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_3_invade.pdf}
         \caption{\(N=3\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
+        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_7_invade.pdf}
         \caption{\(N=7\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_invade.pdf}
+        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_12_invade.pdf}
         \caption{\(N=12\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_3_invade.pdf}
+        \includegraphics[width=\textwidth]{./img/boxplot_3_invade.pdf}
         \caption{\(N=3\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
+        \includegraphics[width=\textwidth]{./img/boxplot_7_invade.pdf}
         \caption{\(N=7\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_12_invade.pdf}
+        \includegraphics[width=\textwidth]{./img/boxplot_12_invade.pdf}
         \caption{\(N=12\)}
@@
         \centering
-        \input{../tbl/summary_top_3_invade.tex}
+        \input{./tex/summary_top_3_invade.tex}
         \caption{\(N=3\)}
@@
         \centering
-        \input{../tbl/summary_top_7_invade.tex}
+        \input{./tex/summary_top_7_invade.tex}
         \caption{\(N=7\)}
@@
         \centering
-        \input{../tbl/summary_top_12_invade.tex}
+        \input{./tex/summary_top_12_invade.tex}
         \caption{\(N=12\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_resist.pdf}
+        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_3_resist.pdf}
         \caption{\(N=3\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
+        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_7_resist.pdf}
         \caption{\(N=7\)}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_12_resist.pdf}
+        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_12_resist.pdf}
         \caption{\(N=12\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_3_resist.pdf}
+        \includegraphics[width=\textwidth]{./img/boxplot_3_resist.pdf}
         \caption{\(N=2\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
+        \includegraphics[width=\textwidth]{./img/boxplot_7_resist.pdf}
         \caption{\(N=7\)}
@@
         \centering
-        \includegraphics[width=\textwidth]{../img/boxplot_12_resist.pdf}
+        \includegraphics[width=\textwidth]{./img/boxplot_12_resist.pdf}
         \caption{\(N=12\)}
@@
         \centering
-        \input{../tbl/summary_top_3_resist.tex}
+        \input{./tex/summary_top_3_resist.tex}
         \caption{\(N=3\)}
@@
         \centering
-        \input{../tbl/summary_top_7_resist.tex}
+        \input{./tex/summary_top_7_resist.tex}
         \caption{\(N=7\)}
@@
         \centering
-        \input{../tbl/summary_top_12_resist.tex}
+        \input{./tex/summary_top_12_resist.tex}
         \caption{\(N=12\)}
@@
     \centering
-    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_invade.pdf}
+    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_invade.pdf}
     \caption{invade}
@@
     \centering
-    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_resist.pdf}
+    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_resist.pdf}
     \caption{resist}
@@
     \centering
-    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_coexist.pdf}
+    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_coexist.pdf}
     \caption{Coexistance}
@@
         \centering
-        \input{"../tbl/correlation_coeficients_invade.tex"}
+        \input{"./tex/correlation_coeficients_invade.tex"}
         \caption{Correlation coefficients for ranks for invasion}
@@
         \centering
-        \input{"../tbl/correlation_coeficients_resist.tex"}
+        \input{"./tex/correlation_coeficients_resist.tex"}
         \caption{Correlation coefficients for ranks for resistance}
@@
         \centering
-        \input{"../tbl/correlation_coeficients_coexist.tex"}
+        \input{"./tex/correlation_coeficients_coexist.tex"}
         \caption{Correlation coefficients for ranks for coexistance}
@@
 		\centering
-		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_invade.pdf}
+		\includegraphics[width=.9\textwidth]{./img/correlation_heatmap_invade.pdf}
 		\caption{Rank based on \(x_1\)}
@@
 		\centering
-		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_resist.pdf}
+		\includegraphics[width=.9\textwidth]{./img/correlation_heatmap_resist.pdf}
         \caption{Rank based on \(x_{N - 1}\)}
@@
 		\centering
-		\includegraphics[width=.9\textwidth]{../img/correlation_heatmap_coexist.pdf}
+		\includegraphics[width=.9\textwidth]{./img/correlation_heatmap_coexist.pdf}
         \caption{Rank based on \(x_{N/2}\)}
@@
     \centering
-    \includegraphics[width=.6\textwidth]{../img/fixation_v_fitness_illustration.pdf}
+    \includegraphics[width=.6\textwidth]{./img/fixation_v_fitness_illustration.pdf}
     \caption{\(x_i(r)\)}
@@
 \begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime}
-    \frac{dx_i}{dr} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime.tex}
+    \frac{dx_i}{dr} = \input{./tex/fixation_probability_with_constant_relative_fitness_prime.tex}
 \end{equation}
@@
 \begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime2}
-    \frac{d^2x_i}{dr^2} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime2.tex}
+    \frac{d^2x_i}{dr^2} = \input{./tex/fixation_probability_with_constant_relative_fitness_prime2.tex}
 \end{equation}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator_fitness.pdf}
         \caption{Alternator and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector_fitness.pdf}
         \caption{Alternator and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat_fitness.pdf}
         \caption{Alternator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat_fitness.pdf}
         \caption{Cooperator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator_fitness.pdf}
         \caption{Defector and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat_fitness.pdf}
         \caption{Defector and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_v_Cooperator_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator_fitness.pdf}
         \caption{Random and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_v_Defector_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector_fitness.pdf}
         \caption{Random and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Random_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat_fitness.pdf}
         \caption{Random and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Cooperator_fitness.pdf}
         \caption{All C or all D and Cooperator}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Defector_fitness.pdf}
         \caption{All C or all D and Defector}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Random_fitness.pdf}
         \caption{Calculator and Random}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD_fitness.pdf}
         \caption{Calculator and All C or all D}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner_fitness.pdf}
         \caption{Calculator and Arrogant Q learner}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Tit_For_Tat_fitness.pdf}
         \caption{All C or all D and Tit For Tat}
@@
 	\begin{enumerate}
-		\input{../tbl/list_of_players.tex}
+		\input{./tex/list_of_players.tex}
 	\end{enumerate}

### 2017-04-29 tex/moran_process.tex
Minor reorganisation of files.

\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, shapes, patterns}

\begin{document}
\begin{tikzpicture}[scale=.9]
	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};

	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (B4) circle (.25cm);

	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (B4) circle (.25cm);
	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);

	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (A3) circle (.25cm);

	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (A3) circle (.25cm);
\end{tikzpicture}
\end{document}

### 2017-04-29 analyze.py

@@ -1,220 +1,0 @@
-
-from collections import defaultdict
-import csv
-import matplotlib.pyplot as plt
-import numpy as np
-from pathlib import Path
-
-
-def load_player_data():
-    """Loads the list of player names."""
-    names = []
-    path = Path("results") / "players.csv"
-    with path.open() as csvfile:
-        reader = csv.reader(csvfile)
-        for line in reader:
-            i, player_name, det = line
-            names.append(player_name)
-    return names
-
-def load_data(filename):
-    """Opens sim_*.csv files."""
-    with open(filename) as csvfile:
-        reader = csv.reader(csvfile)
-        for line in reader:
-            yield map(int, line)
-
-def combine_data(filename="sims_2.csv"):
-    """Aggregates data for all the matches in the simulation files."""
-    d = defaultdict(int)
-    count = defaultdict(int)
-    for line in load_data(filename):
-        i, j, w, c = line
-        count[(i, j)] += c
-        if i == w:
-            d[(i, j)] += c
-    results = dict()
-    for k, v in count.items():
-        results[k] = d[k] / float(count[k])
-    return results
-
-def sort_results(results, reverse=False, central_function=np.median,
-                 direction="invasion"):
-    N = max(k[1] for k in results.keys()) + 1
-    l = [[] for _ in range(N)]
-    for k, v in results.items():
-        i, j = k
-        if direction == "invasion":
-            l[i].append(v)
-        else:
-            l[j].append(v)
-
-    # Sort by median
-    centers = [(central_function(l[i]), i) for i in range(N)]
-    centers.sort(reverse=True)
-    domain = [y for (x, y) in centers]
-
-    names = load_player_data()
-    ranked_names = [names[y] for (x, y) in centers]
-
-    if reverse:
-        domain = list(reversed(domain))
-        ranked_names = list(reversed(ranked_names))
-    return domain, ranked_names
-
-def pairwise_heatmap(results, pop_size, direction="invasion"):
-    """Heatmap for the given population size for all players versus all other
-    players."""
-
-    domain, ranked_names = sort_results(results, reverse=True,
-                                        direction=direction)
-
-    player_names = load_player_data()
-    n = len(domain)
-    # print(n, len(domain))
-    xs = list(reversed(range(n)))
[…]

### 2017-04-29 tex/list_of_players.tex
Minor reorganisation of files.

\item Random Hunter
\item Cooperator
\item Adaptive
\item Random: 0.5
\item Contrite Tit For Tat
\item Cycle Hunter
\item Adaptive Tit For Tat: 0.5
\item Cooperator Hunter
\item Stochastic Cooperator
\item Remorseful Prober: 0.1
\item Cycler CCCCCD
\item Tricky Cooperator
\item Win-Shift Lose-Stay: D
\item Aggravater
\item Tricky Defector
\item $\pi$
\item Resurrection
\item Stochastic WSLS: 0.05
\item Win-Stay Lose-Shift: C
\item ALLCorALLD
\item Tullock: 11
\item Alternator
\item Retaliate: 0.1
\item Cycler CCCD
\item Worse and Worse
\item Alternator Hunter
\item Retaliate 2: 0.08
\item Worse and Worse 2
\item AntiCycler
\item Winner21
\item Cycler CCD
\item Suspicious Tit For Tat
\item Retaliate 3: 0.05
\item Willing
\item Worse and Worse 3
\item Anti Tit For Tat
\item Adaptive Pavlov 2006
\item Revised Downing: True
\item Cycler DC
\item ZD-Extort-2: 0.1111111111111111, 0.5
\item Adaptive Pavlov 2011
\item ZD-Extort-2 v2: 0.125, 0.5, 1
\item Ripoff
\item VeryBad
\item Cycler DDC
\item Appeaser
\item Cycler CCCDCD
\item Winner12
\item SelfSteem
\item Risky QLearner
\item ZD-Extort-4: 0.23529411764705882, 0.25, 1
\item Arrogant QLearner
\item Thumper
\item ZD-GEN-2: 0.125, 0.5, 3
\item Defector
\item ZD-GTFT-2: 0.25, 0.5
\item Average Copier
\item Davis: 10
\item ShortMem
\item Meta Hunter: 6 players
\item ThueMorseInverse
\item Tester
\item Better and Better
\item Spiteful Tit For Tat
\item Shubik
\item Defector Hunter
\item ThueMorse
\item ZD-SET-2: 0.25, 0.0, 2
\item $e$
\item Slow Tit For Two Tats
\item Desperate
\item Bully
\item SolutionB1
\item Meta Hunter Aggressive: 7 players
\item Calculator
\item Slow Tit For Two Tats 2
\item Tit For Tat
\item Tit For 2 Tats
\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 1, C
\item Doubler
\item Sneaky Tit For Tat
\item SolutionB5
\item Soft Grudger
\item EasyGo
\item CollectiveStrategy
\item Soft Joss: 0.9
\item Eatherley
\item Cautious QLearner
\item Two Tits For Tat
\item Firm But Fair
\item Hard Go By Majority
\item Handshake
\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 1, C
\item Fool Me Once
\item Prober 3
\item Eventual Cycle Hunter
\item Forgetful Grudger
\item Prober 4
\item Evolved ANN
\item Forgetful Fool Me Once: 0.05
\item Fool Me Forever
\item Hard Go By Majority: 10
\item Pun1
\item Evolved ANN 5
\item Fortress4
\item Hard Go By Majority: 20
\item Evolved ANN 5 Noise 05
\item PSO Gambler 2\_2\_2
\item Fortress3
\item Hard Go By Majority: 40
\item PSO Gambler 1\_1\_1
\item Evolved FSM 4
\item Forgiving Tit For Tat
\item Naive Prober: 0.1
\item GTFT: 0.33
\item Soft Go By Majority
\item Hard Go By Majority: 5
\item Nice Average Copier
\item Hard Prober
\item Forgiver
\item Opposite Grudger
\item General Soft Grudger: n=1,d=4,c=2
\item Evolved FSM 16
\item Hard Tit For 2 Tats
\item Soft Go By Majority: 10
\item Once Bitten
\item Hard Tit For Tat
\item EvolvedLookerUp2\_2\_2
\item Nydegger
\item Prober 2
\item Soft Go By Majority: 20
\item Hesitant QLearner
\item Evolved FSM 16 Noise 05
\item PSO Gambler 2\_2\_2 Noise 05
\item Omega TFT: 3, 8
\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 1, C
\item EvolvedLookerUp1\_1\_1
\item Soft Go By Majority: 40
\item Inverse
\item Hopeless
\item MEM2
\item Soft Go By Majority: 5
\item Inverse Punisher
\item Predator
\item Joss: 0.9
\item $\phi$
\item Gradual
\item Level Punisher
\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C')
\item Limited Retaliate: 0.1, 20
\item Grofman
\item Limited Retaliate 2: 0.08, 15
\item PSO Gambler Mem1
\item Negation
\item Punisher
\item Grudger
\item Prober
\item GrudgerAlternator
\item Limited Retaliate 3: 0.05, 20
\item Raider
\item Evolved HMM 5
\item Math Constant Hunter
\item Feld: 1.0, 0.5, 200
\item Grumpy: Nice, 10, -10

### 2017-04-29 src/test.sh

@@ -1,0 +1,4 @@
+echo "Testing moran.py"
+python -m unittest moran.py
+echo "Testing theoretic.py"
+python -m unittest theoretic.py

### 2017-04-29 test.sh

@@ -1,4 +1,0 @@
-echo "Testing approximate_moran.py"
-python -m unittest approximate_moran.py
-echo "Testing moran.py"
-python -m unittest moran.py

### 2017-04-29 main.tex
Add discussion to resistance section.

@@
 
-    Fixation probabilities for Moran processes are obtained for 172
-    different strategies. This is done in both a standard 200 turn
-    interaction and a noisy setting.
+    Fixation probabilities for Moran processes are obtained for 164
+    different strategies.
 
@@
     \item The Collective strategy has a simple handshake mechanism (a
-        cooperation followed by a defection on the first move). It then either
-        cooperates or defects for all rounds~\cite{Li2009}.  This strategy was
-        specifically designed for Evolutionary processes so it is perhaps also
-        not surprising that it does well here.
+        cooperation followed by a defection on the first move). As long as the
+        opponent plays the same handshake and does not defect in the future it
+        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
+        strategy was specifically designed for Evolutionary processes so it is
+        perhaps also not surprising that it does well here.
     \item The finite state machine stragegy % TODO Perhaps refer to earlier
@@
 
+Figures~\ref{fig:fixation_heatmap_resist} show \(x_{N-1}\)
+the players along the vertical axis when matched against the players on the
+horizontal axis. It can be seen that as the population size \(N\) increases the
+probability of resistance increases.
+This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
+showing the median fixation as well as the neutral fixation for each given
+scenario.
+
 \begin{figure}[!hbtp]
@@
 
+Table~\ref{tbl:top_five_resist} shows the top five strategies when ranked
+according to \(x_{N-1}\) for \(N\in\{3, 7, 12\}\).
+% TODO Change 12 to 14
+Once again none of the short memory strategies from
+Section~\ref{sec:two_individuals} perform well for high \(N\).
+
+Three strategies have both high \(x_1\) and high \(x_{N-1}\):
+
+\begin{itemize}
+    \item Collective;
+    \item Predator;
+    \item Prober 4
+\end{itemize}
+
+However, Remorseful Prober, Worse and Worse 2 and Tester no longer do as well.
+There are two strategies that are only top performers in \(x_{N-1}\):
+
+\begin{itemize}
+    \item Handshake: a slightly less aggressive version of the Collective
+        strategy \cite{robson1989}. As long as the initial sequence is played
+        then it cooperates. Thus it will do well in a population consisting of
+        many members of itself: just as the Collective strategy does. However it
+        is not aggressive enough to invade other populations.
+    \item Winner 21: a strategy that makes it's decision deterministically based
+        on 1 round of it's own strategy and 2 of the opponents strategy
+        \cite{Mathieu2015}.
+\end{itemize}
+% TODO Revise this if need be for N=14
+
+Interestingly none of these strategies are deterministic: this is explained by
+the need of strategies to have a steady hand when interacting with their own
+kind. In essence: acting stochastically increase the chance of friendly fire.
+
 \begin{table}[!hbtp]
@@
     %TODO Change N=12 to N=14
-    \caption{Properties of top five strategies resistors}
-    \label{tbl:top_five_invade}
+    \caption{Properties of top five resistors}
+    \label{tbl:top_five_resist}
 \end{table}
+
+It is evident through
+Sections~\ref{sec:two_individuals},~\ref{sec:strong_invaders}
+and~\ref{sec:strong_resistors} that performance of strategies not only depends
+on the initial population distribution but also that there seems to be a
+difference depending on whether or not \(N>2\). This will be explored further in
+the next section.
 

### 2017-04-29 main.tex
Add tables showing rank vs size.

@@
 
+% TODO Archive all data (Zenodo) and include details/reference here.
+
 This section will outline the data analysis carried out:
@@
 and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
-population size. Note that these ranks are
-not necessarily integers as group ties are given the average rank.
+population size. For all starting populations \(i\in\{1, N/2, N-1\}\) the ranks
+of strategies are relatively stable across the different values of \(N>2\)
+however for \(N=2\) there is a distinct difference. This confirms what has been
+discussed in previous sections.
+
+Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
+and~\ref{tbl:ranks_v_size_coexist} show the same information for the strategies
+that rated high for \(N=2\) and \(N=12\).
+% TODO Change to N=14?
 
@@
     \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_invade.pdf}
-    \caption{invade}
+    \caption{Ranks of all strategies according to \(x_1\) for different
+    population sizes}
     \label{fig:ranks_v_size_invade}
@@
 
+\begin{table}[!hbtp]
+    \centering
+    \scriptsize
+    \input{./tex/change_of_rank_invade.tex}
+    \caption{Ranks of some strategies according to \(x_1\) for different
+    population sizes}
+    \label{tbl:ranks_v_size_invade}
+\end{table}
+
 \begin{figure}[!hbtp]
@@
     \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_resist.pdf}
-    \caption{resist}
+    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
+    population sizes}
     \label{fig:ranks_v_size_resist}
@@
 
+\begin{table}[!hbtp]
+    \centering
+    \scriptsize
+    \input{./tex/change_of_rank_resist.tex}
+    \caption{Ranks of some strategies according to \(x_{N-1}\) for different
+    population sizes}
+    \label{tbl:ranks_v_size_resist}
+\end{table}
+
 \begin{figure}[!hbtp]
@@
     \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_coexist.pdf}
-    \caption{Coexistance}
+    \caption{Ranks of all strategies according to \(x_{N/2}\) for different
+    population sizes}
     \label{fig:ranks_v_size_coexist}
 \end{figure}
+
+\begin{table}[!hbtp]
+    \centering
+    \scriptsize
+    \input{./tex/change_of_rank_coexist.tex}
+    \caption{Ranks of some strategies according to \(x_{N/2}\) for different
+    population sizes}
+    \label{tbl:ranks_v_size_coexist}
+\end{table}
 
@@
 note that how well a strategy performs in any Moran process for \(N>2\) has
-little to do with the performance for \(N=2\).
-% TODO This is a really good conclusion I think: it shows that when studying
-% population dynamics it is important to consider larger populations.
+little to do with the performance for \(N=2\). This illustrates why the strong
+performance of zero determinant strategies predicted in \cite{Press2012} does
+not extend to larger populations. This was discussed theoretically in
+\cite{Adami2013} however not observed empirically at the scale presented here.
 
@@
 
-% TODO Discuss effect of size on performance of strategies. Relate to Press and
-% Dyson work: "ZD strategies win matches but not tournaments".
-
-% TODO Discuss some particular interesting cases; strategies that perform well
-% in the overall tournament for v2.8.0 perhaps?
-
 \section{Conclusion}\label{sec:conclusion}
 
-% TODO Write overall conclusion. (Perhaps: weakness of short memory
-% strategies?)
-
-Further work:
-
-\begin{itemize}
-    \item Spatial structure;
-    \item More than two types in the population;
-    \item Modified Moran processes (Fermi selection);
-    \item Mutation;
-\end{itemize}
-% TODO Write this section.
+A detailed empirical analysis of 164 strategies of the IPD within a pairwise
+Moran process has been carried out. All \(\binom{164}{2}=13,366\) possible
+ordered pairs of strategies have been placed in a Moran process with different
+starting values allowing the each strategy to attempt to invade the other.
+
+This is the largest such experiment carried out and has lead to many insights.
+
+When studying evolutionary processes it is vital to consider \(N>2\) as the
+special case for \(N=2\) cannot be used to extrapolate performance in bigger
+populations. This was shown both observationally in
+Sections~\ref{sec:strong_invaders} and~\ref{sec:strong_resistors} but also by
+considering the correlation of the ranks in different population sizes in
+Section~\ref{sec:population_size}.
+
+For \(N=2\), memory one strategies perform well, in particular as predicted by
+\cite{Press2012} zero determinant strategies rank highly. However, there are no
+memory one strategies in the top 5 performing strategies for \(N>3\). This is
+due to their lack of sophistication which allows them to recognise and adjust to
+their opponent.
+
+It is felt that these findings are important for the ongoing understanding of
+population dynamics and offer evidence for some of the shortcomings of short
+memory which has started to be recognised by the community~\cite{Hilbe2017}.
+
+All source code for this work has been written in a sustainable manner: it is
+open source, under version control and tested which ensures that all results can
+be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
+the processed data has also been properly archived.
+
+There are various areas for further work to build on this. Firstly, an analysis
+of the effect of noise would offer insights about the stability of the findings.
+It would also be possible to consider three or more types of strategy in the
+population and finally mutation would also offer an interesting dimension to
+explore.
 

### 2017-04-29 main.tex
Minor adjustments and run with new data.

@@
     evolutionary setting.
-\end{abstract}  % TODO Add main conclusion/finding.
+
+    Evidence is presented that shows that classical analysis of evolutionary
+    dynamics with 2 individuals is misleading. Furthermore, it is shown that
+    players with long memories and sophisticated behaviours outperform many
+    strategies that perform well in a 2 individual setting (such as zero
+    determinant strategies).
+
+\end{abstract}
 
@@
 All strategies are paired and these pairs are used in 1000 repetitions of a
-Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
-for even \(N\) between 2 and 14. The fixation probability is then estimated for
-each value of \(N\).
-% TODO The above is no longer true.
+Moran process assuming a starting population distribution of \(1, N-1 \),
+\((N/2, N/2)\) and \(N-1 , 1\). This is repeated for \(N\) between 2 and 14. The
+% TODO Change 14 to 12 if we do not use the 14 case.
+fixation probability is then estimated for each value of \(N\).
 
@@
 interaction between two players within the Moran process the outcome is sampled
-from a pre computed cache of 1000 match outcomes. This is carried out using an
+from a pre computed cache of 1000 match outcomes. This is carried out using
 software written for the purpose of this work. This has been
-implemented in \cite{axelrodproject} ensuring that it can be used to either
+implemented in~\cite{axelrodproject} ensuring that it can be used to either
 reproduce the work or carry out further work.
+% TODO Perhaps write some pseudo code for this?
 
@@
         perhaps also not surprising that it does well here.
-    \item The finite state machine stragegy % TODO Perhaps refer to earlier
+    \item The finite state machine strategy % TODO Perhaps refer to earlier
         % discussion in the methodology section about these FSM strategies
@@
 
+% TODO I do not understand the narrative for this and what it adds to the paper.
+
 Under the assumption of a constant relative fitness \(r\) between two

### 2017-05-04 main.tex
Add literature.
An introduction to the PD.
Two sentences about emergence of cooperation study
and two sentences about the ZD.

@@
 
+The Prisoner's Dilemma (PD)~\cite{Tucker1983} is a fundamental two person game 
+in Game theory. Each player can choose between cooperation (C) or defection 
+(D). The decisions are made simultaneously and independently. The payoffs of
+the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
+\end{pmatrix}$, where $T > R > P> S$ and $2R > T + S$. The PD is a one 
+round game, but is commonly studied in a manner where the prior outcomes 
+matter, the game then extends to its ’iterated’ form, the Iterated Prisoner's 
+Dilemma (IPD).
+
 Since the formulation of the Moran Process in \cite{Moran1957}, this model of
@@
 setting. It has since been used in a variety of settings including the
-understanding of the spread of cooperative behaviour. However, as stated before,
+understanding of the spread of cooperative behaviour. For instance, cancer 
+cells \cite{West2016}. Emergence of cooperative behaviour, also includes 
+studies in spatial topologies \cite{Nowak2017}. However, as stated before, 
 these mainly consider non sophisticated strategies. Some work has looked at
@@
 terms of infinite population stability. In \cite{Baek2016} Moran processes are
-looked at in a theoretic framework for a small subset of strategies. In
-\cite{Lee2015} machine learning techniques are used to train a strategy capable
-of resisting invasion and also invade any memory one strategy. Recent work
-\cite{Hilbe2017} has investigated the effect of memory length on strategy
-performance and the emergence of cooperation but this is not done in Moran
-process context and only considers specific cases of memory 2 strategies.
+looked at in a theoretic framework for a small subset of strategies. 
+The subset included memory one strategies, strategies that recall the events 
+of the previous round only. In \cite{Press2012}, a set of memory one 
+strategies, the zero determinant strategies, have been introduced. The ZD\@,
+strategies are highly praised and in \cite{Stewart26062012} argued that 
+generous ZD strategies are robust against invading strategies. However,
+in \cite{Lee2015} machine learning techniques are used to train a strategy 
+capable of resisting invasion and also able to invade any memory one strategy. 
+Recent work \cite{Hilbe2017} has investigated the effect of memory length on 
+strategy performance and the emergence of cooperation but this is not done in 
+Moran process context and only considers specific cases of memory 2 strategies.
 % TODO Add discussion about ZD strategies and discuss how this corresponds to
@@
 
-As described in \cite{Nowak} Consider the payoff matrix:
+As described in \cite{Nowak} consider the payoff matrix:
 
@@
 stochastic strategies. These are no longer a good match which highlights the
-weakness of the analytical formulae that relies on the average payoffs. A
+weakness of the analytical formula that relies on the average payoffs. A
 detailed analysis of the 164 strategies considered, using direct Moran processes

### 2017-05-04 main.tex
Vine corrections.
I have also included my name in the authors. Thank you once again
for the opportunity.

I decided to sign my name as 'Nikoleta E. Glynatsi` from now on

@@
        Iterated Prisoner's Dilemma}
-\author{Marc Harper \and Vincent Knight} % TODO Authors?
+\author{Marc Harper \and Vincent Knight \and Nikoleta E. Glynatsi} % TODO Authors?
 \date{}
@@
 
-The Prisoner's Dilemma (PD)~\cite{Tucker1983} is a fundamental two person game 
+The Prisoner's Dilemma (PD)~\cite{Flood1958} is a fundamental two person game 
 in Game theory. Each player can choose between cooperation (C) or defection 
@@
 round game, but is commonly studied in a manner where the prior outcomes 
-matter, the game then extends to its ’iterated’ form, the Iterated Prisoner's 
+matter, the game then extends to its `iterated'\ form, the Iterated Prisoner's 
 Dilemma (IPD).
@@
 of the previous round only. In \cite{Press2012}, a set of memory one 
-strategies, the zero determinant strategies, have been introduced. The ZD\@,
+strategies, the zero determinant strategies, were introduced. The ZD\@,
 strategies are highly praised and in \cite{Stewart26062012} argued that 
@@
 stochastic strategies. These are no longer a good match which highlights the
-weakness of the analytical formula that relies on the average payoffs. A
+weakness of the analytical formulae that relies on the average payoffs. A
 detailed analysis of the 164 strategies considered, using direct Moran processes

### 2017-05-08 main.tex

@@
 
-\usepackage[backend=biber, firstinits=false, backref=false, url=true,
-            isbn=true, style=numeric]{biblatex}
-\addbibresource{./tex/bibliography.bib}
+% \usepackage[backend=biber, firstinits=false, backref=false, url=true,
+%             isbn=true, style=numeric]{biblatex}
+% \addbibresource{./tex/bibliography.bib}
 
 % Title
-\title{An empirical study of fixation for strategies in the
-       Iterated Prisoner's Dilemma}
+\title{An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies}
 \author{Marc Harper \and Vincent Knight \and Nikoleta E. Glynatsi} % TODO Authors?
@@
     the study of emergent behaviour. In this paper an extensive numerical
-    study of the evolutionary dynamics of this framework are presented.
-
-    Fixation probabilities for Moran processes are obtained for 164
-    different strategies.
-
-    To the authors knowledge this is the largest
-    such study. It allows for insights about the behaviour and
-    performance of strategies with regard to their survival in an
-    evolutionary setting.
-
-    Evidence is presented that shows that classical analysis of evolutionary
-    dynamics with 2 individuals is misleading. Furthermore, it is shown that
-    players with long memories and sophisticated behaviours outperform many
-    strategies that perform well in a 2 individual setting (such as zero
-    determinant strategies).
-
+    study of the evolutionary dynamics of this framework are presented. Fixation
+    probabilities for Moran processes are obtained for 164
+    different strategies. We find that players with long memories and
+    sophisticated behaviours outperform many strategies that perform well
+    in a two player setting.
 \end{abstract}
@@
 
-The Prisoner's Dilemma (PD)~\cite{Flood1958} is a fundamental two person game 
-in Game theory. Each player can choose between cooperation (C) or defection 
-(D). The decisions are made simultaneously and independently. The payoffs of
+The Prisoner's Dilemma (PD)~\cite{Flood1958} is a fundamental two player game 
+used to model a large variety of strategic interactions. Each player can choose
+between cooperation (C) or defection (D). The decisions are made simultaneously
+and independently. The payoffs of
 the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
-\end{pmatrix}$, where $T > R > P> S$ and $2R > T + S$. The PD is a one 
+\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one 
 round game, but is commonly studied in a manner where the prior outcomes 
-matter, the game then extends to its `iterated'\ form, the Iterated Prisoner's 
+matter. This extended form is called the Iterated Prisoner's 
 Dilemma (IPD).
 
-Since the formulation of the Moran Process in \cite{Moran1957}, this model of
-evolutionary population dynamics has been used to gain insights about the
-evolutionary stability of strategies in a number of settings. Similarly since
-the first Iterated Prisoner's Dilemma (IPD) tournament described in
-\cite{Axelrod1980a} the Prisoner's dilemma has been used to understand the
-evolution of cooperative behaviour in complex systems.
-
-The analytical models of a Moran process are based on the relative fitness
-between two strategies and take this to be a fixed value \(r\) \cite{Nowak}.
-This is a valid model for simple strategies of the Prisoner's Dilemma such as to
-\textit{always cooperate} or \textit{always defect}. This manuscript provides a
-detailed numerical analysis of \textbf{164} complex and adaptive strategies for
-the IPD\@. In this case the relative fitness of a strategy is dependent on the
-population distribution.
-
-Further deviations from the analytical model occur when interactions between
-players are subject to uncertainty. This is referred to as noise and has been
-considered in the IPD setting in \cite{Bendor1993, Nowak1993, Wu1995}.
-
-This work provides answers to the following questions:
-
+The Moran Process \cite{Moran1957} is a model of
+evolutionary population dynamics that has been used to gain insights about the
+evolutionary stability and fixation of strategies in a number of settings.
+Similarly since the first Iterated Prisoner's Dilemma (IPD) tournament described in
+\cite{Axelrod1980a}, the Prisoner's dilemma has been used to understand the
+evolution of cooperative behaviour in complex systems. Several earlier
+works have studied iterated games in the context of the prisoner's dilemma
+\cite{Nowak} \cite{Stewart2012}.
+
+This manuscript provides a detailed numerical analysis of \textbf{164}
+complex and adaptive strategies for the IPD\@. This is made possible
+by the Axelrod library \cite{axelrodproject}, an effort to provide
+software for reproducible research for the IPD. The library now contains over 150
+parameterized strategies including classics like TitForTat and WinStayLoseShift,
+as well as recent variants such as OmegaTFT, zero determinant and other memory one strategies,
+strategies based on finite state machines, lookup tables, neural networks,
+and other machine learning based strategies, and a collection of novel strategies.
+The library can conduct matches, tournaments and population dynamics
+with variations including noise and spatial structure.
+
+We present fixation probabilities for all pairs of
+strategies in the library, identifying those are effective invaders and
+those resistant to invasion, for population sizes $N=2$ to $N=14$.
+
+In particular we address the following questions:
 \begin{enumerate}
@@
 
+While our results agree with some of the published literature, we find that:
+
+\begin{enumerate}
+ \item Zero determinant strategies are not particularly effective for $N > 2$
+ \item Long memory strategies are generally more effective than short memory strategies
+ \item Complex strategies can be effective
+\end{enumerate}
+
+\subsection{The Moran Process}
+
 Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
-process. This process is a stochastic birth death process on a finite population
+process, a stochastic birth death process on a finite population
 in which the population size stays constant over time. Individuals are
-\textbf{selected} according to a given fitness landscape. Once selected, a given
+\textbf{selected} according to a given fitness landscape. Once selected, the
 individual is reproduced and similarly another individual is chosen to be
@@
 without mutation (the case considered in this work) this process will arrive at
-an absorbing state where the population is entirely made up of a single
-individual. The probability with which a given strategy is the survivor is
+an absorbing state where the population is entirely made up of players of
+one strategy. The probability with which a given strategy is the survivor is
 called the fixation probability. A more detailed analytic description of this
@@
 
-The Moran process was initially introduced in \cite{Moran1957} in a genetic
-setting. It has since been used in a variety of settings including the
-understanding of the spread of cooperative behaviour. For instance, cancer 
-cells \cite{West2016}. Emergence of cooperative behaviour, also includes 
-studies in spatial topologies \cite{Nowak2017}. However, as stated before, 
-these mainly consider non sophisticated strategies. Some work has looked at
+The Moran process was initially introduced in \cite{Moran1957}. It has since been
+used in a variety of settings including the
+understanding of the spread of cooperative and non-cooperative behaviour
+such as cancer \cite{West2016} and the emergence of cooperative behaviour
+in spatial topologies \cite{Nowak2017}. However these works 
+mainly consider non-sophisticated strategies. Some work has looked at
 evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
-but this is not done in the more widely used setting of the Moran process but in
+but this is not done in the more widely-used setting of the Moran process, rather in
 terms of infinite population stability. In \cite{Baek2016} Moran processes are
-looked at in a theoretic framework for a small subset of strategies. 
+studied in a theoretical framework for a small subset of strategies. 
 The subset included memory one strategies, strategies that recall the events 
-of the previous round only. In \cite{Press2012}, a set of memory one 
-strategies, the zero determinant strategies, were introduced. The ZD\@,
-strategies are highly praised and in \cite{Stewart26062012} argued that 
+of the previous round only.
+
+Of particular interest are the zero determinant strategies introduced in \cite{Press2012}
+and highly-praised \cite{Stewart26062012} it was argued that 
 generous ZD strategies are robust against invading strategies. However,
-in \cite{Lee2015} machine learning techniques are used to train a strategy 
+in \cite{Lee2015} a strategy using machine learning techniques was
 capable of resisting invasion and also able to invade any memory one strategy. 
@@
 Moran process context and only considers specific cases of memory 2 strategies.
+In \cite{Adami2013} it was recognized that many zero determinant strategies do
+not fare well against themselves. This is a disadvantage for the Moran process
+where the best strategies cooperate well with other players using the same strategy.
+
 % TODO Add discussion about ZD strategies and discuss how this corresponds to
@@
 
+\subsection{The Axelrod Library}
+
 The contribution of this work is a detailed and extensive analysis of absorption
@@
 for the study of the IPD\@. The strategies and simulation frameworks are
-automatically tested in accordance to best research software practice. The large
+automatically tested to an extraordinarily high degree of coverage in accordance
+with best research software practices. The large
 number of strategies are available thanks to the open source nature of the
-project with over 40 contributions made by different programmers. Thus by
-considering Moran processes with population size greater than 2 we are taking in
-to account the effect of complex population dynamics. By considering
-sophisticated strategies we are taking in to effect the reputation of a strategy
-during each interaction.
+project with over 40 contributions made by different programmers and researchers.
 
@@
 Section~\ref{sec:validation} will validate the methodology by comparing
-simulated results to analytical results. The main results of this manuscript are
+simulated results to analytical results in some cases. The main results of this manuscript are
 presented in Section~\ref{sec:empirical_results} which will present a detailed
@@
 
-To carry out this large numerical experiment 164 strategies are used from
+To carry out this large numerical experiment, 164 strategies are used from
 \cite{axelrodproject}. These include 161 default strategies in the library at
@@
 % Possibly draw pictorial representations?
+% Remove the FSM strategies if they don't perform well.
 
@@
 \input{./tex/num_deterministic.tex}deterministic strategies. Their memory
-depth is shown in Table~\ref{tbl:memory_depth_count}.
+depth, defined by the number of rounds of history used by the strategy each round,
+is shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if
+the strategy uses the entire history of play (whatever its length). For example,
+a strategy that utilizes a handshaking mechanism where the opponents actions
+on the first few rounds of play determines the strategies subsequent behavior
+would have infinite memory depth.
 
@@
 
-All strategies are paired and these pairs are used in 1000 repetitions of a
-Moran process assuming a starting population distribution of \(1, N-1 \),
-\((N/2, N/2)\) and \(N-1 , 1\). This is repeated for \(N\) between 2 and 14. The
+Each strategy pair is run for 1000 runs of the Moran process to fixation
+with starting population distributions of $(1, N-1)$,
+$(N/2, N/2)$ and $(N-1 , 1)$, for \(N\) from 2 through 14. The
 % TODO Change 14 to 12 if we do not use the 14 case.
-fixation probability is then estimated for each value of \(N\).
-
-Note that due to the high computational cost of these experiments, for any given
-interaction between two players within the Moran process the outcome is sampled
-from a pre computed cache of 1000 match outcomes. This is carried out using
-software written for the purpose of this work. This has been
-implemented in~\cite{axelrodproject} ensuring that it can be used to either
-reproduce the work or carry out further work.
+fixation probability is then empirically computed for each combination of
+starting distribution and value of \(N\).
+
+Our software can carry out exact simulations of the Moran process. Since some of
+the strategies have a high computational cost or are stochastic, we sample
+from a large number of match outcomes for the pairs of players for use in computing
+fitnesses in the Moran process. This approach was verified to agree with unsampled
+calculations to a high degree of accuracy in specific cases.
 % TODO Perhaps write some pseudo code for this?
@@
 matches is sufficient for the analysis taking place here.
+% TODO is this true? the distribution also matters, not just the number of outcomes
 
@@
 
-Using this comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
+A neutral strategy will have fixation probability $x_i = i/N$. Alternatively,
+we can frame the outcomes in terms of relative fitness. For a strategy
+of relative fitness $r$ the fixation probability is well-known to be
+
+\[ x_i = \frac{1 - r^{-i}}{1 - r^{-N}} \]
+
+We can use this formula to compute a value $r_i$ that produces the observed
+value $x_i$, noting that for arbitrary strategies the value of this
+effective relative fitness is dependent on $i$ and $N$.
+
+Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
 Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
-values and the line shows the theoretic value. Note that these are all
+values and the line shows the theoretical value. Note that these are all
 deterministic strategies and show a perfect match up between the expected value
@@
 
-This section will outline the data analysis carried out:
+This section outlines the data analysis carried out:
 
 \begin{itemize}
-    \item Section~\ref{sec:two_individuals} will consider the specific case of
+    \item Section~\ref{sec:two_individuals} considers the specific case of
         \(N=2\).
-    \item Section~\ref{sec:strong_invaders} will investigate the effect of
+    \item Section~\ref{sec:strong_invaders} investigates the effect of
         population size on the ability of a strategy to invade another
@@
         memories outperform simpler strategies.
-    \item Section~\ref{sec:strong_resistors} will similarly investigate the
+    \item Section~\ref{sec:strong_resistors} similarly investigates the
         ability to defend against an invasion.
-    \item Section~\ref{sec:population_size} will investigate the relationship
-        between performance for differing population sizes. This highlights the
-        importance of considering population dynamics over large populations.
-    \item Section~\ref{sec:relative_fitness} will calculate the relative fitness of all
+    \item Section~\ref{sec:population_size} investigates the relationship
+        between performance for differing population sizes.
+    \item Section~\ref{sec:relative_fitness} calculates the relative fitness of all
         strategies.
@@
 
-The main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
-reflect a strategy's ability to invade or resist invasion.
-% TODO Perhaps mention that a lot of the research in to training fixation of
-% strategies assumes N=2? Is this true?
-For \(N=2\) these two cases coincide. Figure~\ref{fig:fixation_heatmap_2} shows
+When $N=2$ the Moran process is effectively a measure of the relative
+mean payoffs over all possible matches between two players. The strategy
+that scores higher than the other more often will fixate more often.
+
+Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
+reflect a strategy's ability to invade or resist invasion; for \(N=2\) these two cases
+coincide. Figure~\ref{fig:fixation_heatmap_2} shows
 all pairwise fixation probabilities for strategies on the vertical column when
@@
         cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
-        strategy was specifically designed for Evolutionary processes so it is
-        perhaps also not surprising that it does well here.
+        strategy was specifically designed for evolutionary processes.
     \item The finite state machine strategy % TODO Perhaps refer to earlier
@@
 
-As will be demonstrated in Section~\ref{sec:population_size} \(N=2\)
-is a particular case. In the next sections we will pay close attention to
+As will be demonstrated in Section~\ref{sec:population_size} the results for \(N=2\)
+differ from those of larger $N$. Hence our results do not concur with the literature
+which suggests that Zero Determinant strategies should be effective for larger population
+sizes, but we note that those analysis run each match to stationarity, while
+our matches run for a fixed number of rounds.
+
+In the next sections we pay close attention to
 strategies who are strong invaders/resistors and shown diagrammatically in
@@
 
-In this section \(x_i\) will be investigated: the probability of 1 individual of
-a given type successfully becoming fixated in a population of \(N - 1\) other
-individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
+In this section we focus on the ability of a mutant strategy to invade: the
+probability of 1 individual of a given type successfully becoming fixated in
+a population of \(N - 1\) other individuals, denoted by \(x_i\).
+Figures~\ref{fig:fixation_heatmap_invade} shows these values for
 the players along the vertical axis when matched against the players on the
-horizontal axis. It can be seen that invasion is in general more challenging for
-\(N=7\) and \(N=12\) in comparison to \(N=3\).
-%TODO Change this to N=14
-This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
+horizontal axis. For population size $N$, a neutral mutant has fixation
+probability $x_1 = 1 / N$. This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
 showing the median fixation as well as the neutral fixation for each given
@@
 
-It can be seen that apart from the Collective strategy, none of the strategies
+It can be seen that apart from the Collective Strategy, none of the strategies
 of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 12\}\). The new
@@
         cooperations and defections~\cite{prison}. This initial sequence serves
-        as some kind of handshake.
+        as approximate handshake.
     \item Remorseful Prober, a strategy that will not immediately retaliate when
-        it recognises that the opponent is itself retaliating to a random
+        it recognises that the opponent is retaliating to a random
         defection~\cite{Li2011}.
-    \item  Worse and worse 2: plays tit for tat for 20 moves and then defects
+    \item  Worse and Worse 2: plays Tit For Tat for 20 moves and then defects
         with with growing probability~\cite{prison}.
@@
 As well as noting that the memory length and complexity of these strategies are
-quite complex it is interesting to note that none of them are akin to memory one
-strategies. Most are not stochastic.
-
-In the next section the performance in terms of \(x_{N-1}\) will be described:
-what strategies are particularly good at resisting an invasion.
+much greater than one, it is interesting to note that none of them are akin to
+memory one strategies. Most are not stochastic.
 
 \subsection{Strong resistors}\label{sec:strong_resistors}
+
+In addition to identifying good invaders, we also identify strategies
+resistant to invasion by other strategies by examining the distribution
+of $x_{N-1}$ for each strategy. Note that this is equivalent to
+looking at $x_1$ for all opponents.
 
@@
 the players along the vertical axis when matched against the players on the
-horizontal axis. It can be seen that as the population size \(N\) increases the
-probability of resistance increases.
-This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
+horizontal axis. This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
 showing the median fixation as well as the neutral fixation for each given
@@
 \begin{itemize}
-    \item Collective;
-    \item Predator;
+    \item Collective
+    \item Predator
     \item Prober 4
@@
         is not aggressive enough to invade other populations.
-    \item Winner 21: a strategy that makes it's decision deterministically based
-        on 1 round of it's own strategy and 2 of the opponents strategy
+    \item Winner 21: a strategy that makes its decision deterministically based
+        on 1 round of its own strategy and 2 of the opponent's strategy
         \cite{Mathieu2015}.
@@
 
-Interestingly none of these strategies are deterministic: this is explained by
+Interestingly none of these strategies are stochastic: this is explained by
 the need of strategies to have a steady hand when interacting with their own
 kind. In essence: acting stochastically increase the chance of friendly fire.
+However we note that it is possible to design a strategy with a ``stochastic
+handshake'' \cite{Lee2015}.
 
@@
 
-\printbibliography
+% \printbibliography
 

### 2017-05-08 main.tex
Build with bibliography.

@@
 
-% \usepackage[backend=biber, firstinits=false, backref=false, url=true,
-%             isbn=true, style=numeric]{biblatex}
-% \addbibresource{./tex/bibliography.bib}
+\usepackage[backend=biber, firstinits=false, backref=false, url=true,
+            isbn=true, style=numeric]{biblatex}
+\addbibresource{./tex/bibliography.bib}
 
@@
 works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak} \cite{Stewart2012}.
-
-This manuscript provides a detailed numerical analysis of \textbf{164}
-complex and adaptive strategies for the IPD\@. This is made possible
-by the Axelrod library \cite{axelrodproject}, an effort to provide
-software for reproducible research for the IPD. The library now contains over 150
-parameterized strategies including classics like TitForTat and WinStayLoseShift,
-as well as recent variants such as OmegaTFT, zero determinant and other memory one strategies,
-strategies based on finite state machines, lookup tables, neural networks,
-and other machine learning based strategies, and a collection of novel strategies.
-The library can conduct matches, tournaments and population dynamics
-with variations including noise and spatial structure.
+\cite{Nowak, Stewart2012}.
+
+This manuscript provides a detailed numerical analysis of \textbf{164} complex
+and adaptive strategies for the IPD\@. This is made possible by the Axelrod
+library \cite{axelrodproject}, an effort to provide software for reproducible
+research for the IPD\@. The library now contains over 150 parameterized
+strategies including classics like TitForTat and WinStayLoseShift, as well as
+recent variants such as OmegaTFT, zero determinant and other memory one
+strategies, strategies based on finite state machines, lookup tables, neural
+networks, and other machine learning based strategies, and a collection of novel
+strategies. The library can conduct matches, tournaments and population
+dynamics with variations including noise and spatial structure.
 
@@
  \item Zero determinant strategies are not particularly effective for $N > 2$
- \item Long memory strategies are generally more effective than short memory strategies
+ \item Long memory strategies are generally more effective than short
+       memory strategies
  \item Complex strategies can be effective
@@
 Of particular interest are the zero determinant strategies introduced in \cite{Press2012}
-and highly-praised \cite{Stewart26062012} it was argued that 
+and highly-praised \cite{Stewart2012} it was argued that
 generous ZD strategies are robust against invading strategies. However,
@@
 
-% \printbibliography
+\printbibliography
 

### 2017-05-08 main.tex
Add abbreviations of player names.
In src/ there is now a python file that just contains a dictionary that
maps players/player names to abbreviations. All abbreviations are not
yet written.

@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT.pdf}
         \caption{Alternator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_TfT.pdf}
         \caption{Cooperator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_TfT.pdf}
         \caption{Defector and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WSLS.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_TfT.pdf}
         \caption{Random and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Tit_For_Tat.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_TfT.pdf}
         \caption{All C or all D and Tit For Tat}

### 2017-05-08 src/abbreviations.py

@@ -1,0 +1,12 @@
+"""
+A dictionary of player name abbreviations
+"""
+abbreviations = {"Tit For Tat": "TfT",
+                 "CollectiveStrategy": "CS",
+                 "Two Tits For Tat": "2TfT",
+                 "Tit For 2 Tats": "Tf2T",
+                 "Win-Stay Lose-Shift: C": "WSLS",
+                 "FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 1, C": "Trained FSM 1",
+                 "FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 1, C": "Trained FSM 2",
[…]

### 2017-05-08 main.tex
Remove table. 2.

@@
 
+Section~\ref{sec:methodology} will explain the methodological approach used,
+Section~\ref{sec:validation} will validate the methodology by comparing
+simulated results to analytical results in some cases. The main results of this
+manuscript are presented in Section~\ref{sec:empirical_results} which will
+present a detailed analysis of all the data generated. Finally,
+Section~\ref{sec:conclusion} will conclude and offer future avenues for the work
+presented here.
+
+\section{Methodology}\label{sec:methodology}
+
 \subsection{The Axelrod Library}
@@
 project with over 40 contributions made by different programmers and researchers.
-
-Section~\ref{sec:methodology} will explain the methodological approach used,
-Section~\ref{sec:validation} will validate the methodology by comparing
-simulated results to analytical results in some cases. The main results of this manuscript are
-presented in Section~\ref{sec:empirical_results} which will present a detailed
-analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
-conclude and offer future avenues for the work presented here.
-
-\section{Methodology}\label{sec:methodology}
 
@@
 the number of outcomes between all strategy pairs.
-Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
-stochastic matches have less than 788 unique outcomes whilst the maximum number
-is 971. This ensures that using a set of cached results from 1000 precomputed
-matches is sufficient for the analysis taking place here.
 % TODO is this true? the distribution also matters, not just the number of outcomes
+% TODO Good point, we could (if we wanted to) go down the line of checking
+% specific distributions etc or perhaps we just remove and point at the good
+% fits in the Validation section as a justification.
 
@@
 \end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \input{./tex/number_of_match_outcomes.tex}
-        \caption{All matches}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \input{./tex/number_of_stochastic_match_outcomes.tex}
-        \caption{Stochastic matches}
-    \end{subfigure}%
-    \caption{Summary statistics for the number of different match outcomes used
-    as the cached results}
-    \label{tbl:number_of_stochastic_match_outcomes}
-\end{table}
 

### 2017-05-08 main.tex
Further fix to abbreviations.

@@
 reflect a strategy's ability to invade or resist invasion; for \(N=2\) these two cases
-coincide. Figure~\ref{fig:fixation_heatmap_2} shows
-all pairwise fixation probabilities for strategies on the vertical column when
-being matched against probabilities on the horizontal column. This is summarised
-in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2}.
+coincide. Figure~\ref{fig:boxplot_2} shows
+all fixation probabilities for the strategies considered. This is summarised
+in Table~\ref{tbl:summary_top_2}.
 
@@
 \begin{figure}[!hbtp]
-    \begin{subfigure}[t]{.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/fixation_heatmap_2_invade.pdf}
-        % TODO Remove this: I don't feel it is effective.
-        \caption{The pairwise fixation probabilities for \(N=2\)}
-        \label{fig:fixation_heatmap_2}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.6\textwidth}
     \centering
     \includegraphics[height=.8\textheight]{./img/boxplot_2_invade.pdf}
-        \caption{The median fixation probabilities for \(N=2\)}
+    \caption{The fixation probabilities for \(N=2\)}
     \label{fig:boxplot_2}
-    \end{subfigure}
 \end{figure}
@@
 In the next sections we pay close attention to
-strategies who are strong invaders/resistors and shown diagrammatically in
-Figure~\ref{fig:invasion_resistance}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \input{./tex/invasion_resistance.tex}
-    \caption{A single individual will successfully invade the population with
-    probability \(x_1\). The group of Individuals will successfully resist with
-    probability \(x_{N-1}\)}
-    \label{fig:invasion_resistance}
-\end{figure}
+strategies who are strong invaders/resistors.
 
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT_fitness.pdf}
         \caption{Alternator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_TfT_fitness.pdf}
         \caption{Cooperator and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_TfT_fitness.pdf}
         \caption{Defector and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT_fitness.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT_fitness.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS_fitness.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Random_v_TfT_fitness.pdf}
         \caption{Random and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Tit_For_Tat_fitness.pdf}
+        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_TfT_fitness.pdf}
         \caption{All C or all D and Tit For Tat}

### 2017-05-08 src/abbreviations.py

@@ -1,12 +1,20 @@
 """
 A dictionary of player name abbreviations
 """
-abbreviations = {"Tit For Tat": "TfT",
-                 "CollectiveStrategy": "CS",
-                 "Two Tits For Tat": "2TfT",
-                 "Tit For 2 Tats": "Tf2T",
-                 "Win-Stay Lose-Shift: C": "WSLS",
-                 "FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 1, C": "Trained FSM 1",
-                 "FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 1, C": "Trained FSM 2",
[…]

### 2017-05-08 tex/fsm_two.tex
FSM graphs and process pseudocode
This closes #29 and #28.

The graph representation for the e finite state machines
as described in `players.py`.

Also for representing the process two pieces of pseudocode.
One for the data collection and one for the moran process.

The pseudocodes are in a tex file, not sure where you would like
them.

Update gitignore to ignore pdf of tex files.

Ashlock's fortress strategies for comparison are also included.n

\documentclass{standalone}

\usepackage{tikz}
\usepackage{standalone}
\usetikzlibrary{calc}

\begin{document}
    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};

	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};

    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};

    \coordinate[below of=0] (s);

    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);

    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);

    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);

    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);

    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/C$} (1);

    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);

    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);

    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);

    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);

    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);

    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);

    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);

    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);

    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);

    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);

    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);

    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);

    \end{tikzpicture}
\end{document}

### 2017-05-08 tex/fsm_one.tex
FSM graphs and process pseudocode
This closes #29 and #28.

The graph representation for the e finite state machines
as described in `players.py`.

Also for representing the process two pieces of pseudocode.
One for the data collection and one for the moran process.

The pseudocodes are in a tex file, not sure where you would like
them.

Update gitignore to ignore pdf of tex files.

Ashlock's fortress strategies for comparison are also included.n

Eating a letter

\documentclass{standalone}

\usepackage{tikz}
\usepackage{standalone}
\usetikzlibrary{calc}

\begin{document}
    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};

	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};

	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};

	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};

	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};

    \coordinate[left of=0] (s);

    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);

    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);

    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);

    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);

    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);

    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);

    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);

    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);

    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);

    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);

    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);

    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);

    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);

    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);

    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);

    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);

    \end{tikzpicture}
\end{document}

### 2017-05-08 tex/fsm_three.tex
FSM graphs and process pseudocode
This closes #29 and #28.

The graph representation for the e finite state machines
as described in `players.py`.

Also for representing the process two pieces of pseudocode.
One for the data collection and one for the moran process.

The pseudocodes are in a tex file, not sure where you would like
them.

Update gitignore to ignore pdf of tex files.

Ashlock's fortress strategies for comparison are also included.n

Eating a letter

\documentclass{standalone}

\usepackage{tikz}
\usepackage{standalone}
\usetikzlibrary{calc}

\begin{document}

    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];

    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$}; 
    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};  
    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};

    \coordinate[left of=0] (s);

    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);

    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);

    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);

    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);

    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
    \end{tikzpicture}

\end{document}

### 2017-05-08 main.tex
Modify ranking to consider mean not median.

@@
     \centering
-    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_invade.pdf}
+    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
     \caption{Ranks of all strategies according to \(x_1\) for different
@@
     \centering
-    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_resist.pdf}
+    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
     \caption{Ranks of all strategies according to \(x_{N-1}\) for different
@@
     \centering
-    \includegraphics[height=.9\textheight]{./img/median_rank_vs_population_size_coexist.pdf}
+    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_coexist.pdf}
     \caption{Ranks of all strategies according to \(x_{N/2}\) for different

### 2017-05-09 src/validate.py
Update validation script to run required data.

@@ -67,27 +67,19 @@ if __name__ == "__main__":
     with open(output_file, "w") as f:
         f.write("Repetitions,N,i,Player 1,Player 2,Theoretic,Simulated\n")
 
-    player_pairs = [(axl.ALLCorALLD(), axl.Cooperator()),
-                    (axl.ALLCorALLD(), axl.Defector()),
-                    (axl.ALLCorALLD(), axl.TitForTat()),
-                    (axl.Alternator(), axl.Cooperator()),
-                    (axl.Alternator(), axl.Defector()),
-                    (axl.Alternator(), axl.TitForTat()),
-                    (axl.Alternator(), axl.WinStayLoseShift()),
-                    (axl.Defector(), axl.WinStayLoseShift()),
-                    (axl.Calculator(), axl.ALLCorALLD()),
-                    (axl.Calculator(), axl.ArrogantQLearner()),
-                    (axl.Calculator(), axl.Random()),
-                    (axl.Cooperator(), axl.TitForTat()),
+    player_pairs = [(axl.Defector(), axl.Defector()),
+                    (axl.Defector(), axl.Alternator()),
                     (axl.Defector(), axl.Cooperator()),
                     (axl.Defector(), axl.TitForTat()),
-                    (axl.Random(), axl.Cooperator()),
-                    (axl.Random(), axl.Defector()),
-                    (axl.Random(), axl.TitForTat()),
-                    (axl.WinStayLoseShift(), axl.TitForTat())]
+                    (axl.Defector(), axl.WinStayLoseShift()),
+                    (axl.Random(), axl.Random()),
+                    (axl.Random(), axl.ZDExtort2()),
+                    (axl.Random(), axl.GTFT()),
+                    (axl.Random(), axl.WorseAndWorse2()),
+                    (axl.Random(), axl.PSOGambler2_2_2())]
 
-    max_N = 8
-    repetitions = 40
+    max_N = 20
+    repetitions = 1000
 
     df = pd.read_csv(outcomes_file, header=None,
                      names=["Player 1", "Player 2",

### 2017-05-09 src/validate.py
Add more data validation match ups.

@@ -75,8 +75,18 @@ if __name__ == "__main__":
                     (axl.Random(), axl.Random()),
                     (axl.Random(), axl.ZDExtort2()),
                     (axl.Random(), axl.GTFT()),
-                    (axl.Random(), axl.WorseAndWorse2()),
-                    (axl.Random(), axl.PSOGambler2_2_2())]
+                    (axl.Random(), axl.ALLCorALLD()),
+                    (axl.Random(), axl.PSOGambler2_2_2()),
+                    (axl.Cooperator(), axl.Random()),
+                    (axl.Cooperator(), axl.ZDExtort2()),
+                    (axl.Cooperator(), axl.GTFT()),
+                    (axl.Cooperator(), axl.ALLCorALLD()),
+                    (axl.Cooperator(), axl.PSOGambler2_2_2()),
+                    (axl.Alternator(), axl.Random()),
+                    (axl.Alternator(), axl.ZDExtort2()),
+                    (axl.Alternator(), axl.GTFT()),
+                    (axl.Alternator(), axl.ALLCorALLD()),
+                    (axl.Alternator(), axl.PSOGambler2_2_2())]
 
     max_N = 20
     repetitions = 1000

### 2017-05-09 main.tex

@@
 
-The Moran process was initially introduced in \cite{Moran1957}. It has since been
-used in a variety of settings including the
-understanding of the spread of cooperative and non-cooperative behaviour
-such as cancer \cite{West2016} and the emergence of cooperative behaviour
-in spatial topologies \cite{Nowak2017}. However these works
-mainly consider non-sophisticated strategies. Some work has looked at
-evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
-but this is not done in the more widely-used setting of the Moran process, rather in
-terms of infinite population stability. In \cite{Baek2016} Moran processes are
-studied in a theoretical framework for a small subset of strategies.
-The subset included memory one strategies, strategies that recall the events
-of the previous round only.
-
-Of particular interest are the zero determinant strategies introduced in \cite{Press2012}
-and highly-praised \cite{Stewart2012} it was argued that
-generous ZD strategies are robust against invading strategies. However,
-in \cite{Lee2015} a strategy using machine learning techniques was
-capable of resisting invasion and also able to invade any memory one strategy.
-Recent work \cite{Hilbe2017} has investigated the effect of memory length on
-strategy performance and the emergence of cooperation but this is not done in
-Moran process context and only considers specific cases of memory 2 strategies.
-In \cite{Adami2013} it was recognized that many zero determinant strategies do
-not fare well against themselves. This is a disadvantage for the Moran process
-where the best strategies cooperate well with other players using the same strategy.
-
-% TODO Add discussion about ZD strategies and discuss how this corresponds to
-% case of N = 2. Include pointing at \cite{Adami2013} which discusses how ZD
-% strategies are not fantastic in population dynamics.
-% Add \cite{Li2014}
-
-Section~\ref{sec:methodology} will explain the methodological approach used,
-Section~\ref{sec:validation} will validate the methodology by comparing
-simulated results to analytical results in some cases. The main results of this
-manuscript are presented in Section~\ref{sec:empirical_results} which will
-present a detailed analysis of all the data generated. Finally,
-Section~\ref{sec:conclusion} will conclude and offer future avenues for the work
-presented here.
-
-\section{Methodology}\label{sec:methodology}
-
-\subsection{The Axelrod Library}
+The Moran process was initially introduced in \cite{Moran1957}. It has since
+been used in a variety of settings including the understanding of the spread of
+cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
+emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
+However these works mainly consider non-sophisticated strategies. Some work has
+looked at evolutionary stability of strategies within the Prisoner's Dilemma
+\cite{Li2014} but this is not done in the more widely-used setting of the Moran
+process, rather in terms of infinite population stability. In \cite{Baek2016}
+Moran processes are studied in a theoretical framework for a small subset of
+strategies.  The subset included memory one strategies, strategies that recall
+the events of the previous round only.
+
+Of particular interest are the zero determinant strategies introduced in
+\cite{Press2012} and highly-praised \cite{Stewart2012} it was argued that
+generous ZD strategies are robust against invading strategies. However, in
+\cite{Lee2015} a strategy using machine learning techniques was capable of
+resisting invasion and also able to invade any memory one strategy.  Recent work
+\cite{Hilbe2017} has investigated the effect of memory length on strategy
+performance and the emergence of cooperation but this is not done in Moran
+process context and only considers specific cases of memory 2 strategies.  In
+\cite{Adami2013} it was recognized that many zero determinant strategies do not
+fare well against themselves. This is a disadvantage for the Moran process where
+the best strategies cooperate well with other players using the same strategy.
 
@@
 project with over 40 contributions made by different programmers and researchers.
+
+Section~\ref{sec:methodology} will explain the methodological approach used,
+Section~\ref{sec:validation} will validate the methodology by comparing
+simulated results to analytical results in some cases. The main results of this
+manuscript are presented in Section~\ref{sec:empirical_results} which will
+present a detailed analysis of all the data generated. Finally,
+Section~\ref{sec:conclusion} will conclude and offer future avenues for the work
+presented here.
+
+\section{Methodology}\label{sec:methodology}
 
@@
 \begin{enumerate}
-    \item The top strategy is an extortionate Zero determinant
-        strategy~\cite{Press2012} with parameters \(l=1\) and \(s=1/4\).
-    \item The Collective strategy has a simple handshake mechanism (a
-        cooperation followed by a defection on the first move). As long as the
-        opponent plays the same handshake and does not defect in the future it
-        cooperates. Otherwise it defects for all rounds~\cite{Li2009}.  This
-        strategy was specifically designed for evolutionary processes.
+    \item The top strategy is the Collective Strategy (CS) which has a simple
+        handshake mechanism (a cooperation followed by a defection on the first
+        move). As long as the opponent plays the same handshake and does not
+        defect in the future it cooperates. Otherwise it defects for all
+        rounds~\cite{Li2009}. This strategy was specifically designed for
+        evolutionary processes.
     \item The finite state machine strategy % TODO Perhaps refer to earlier
         % discussion in the methodology section about these FSM strategies
-    \item The Feld strategy is the corresponding strategy submitted to Axelrod's
-        first tournament~\cite{Axelrod1980a}: it punishes defections but
-        otherwise defects with a random probability that decays over time.
-    \item The final strategy in the top five is another extortionate Zero
-        determinant strategy~\cite{Press2012} with parameters \(l=p\).
+    \item The Defector: it always defects. As it has little potential
+        interaction with itself, recall that \(N=2\) is considered, its
+        aggressiveness is rewarded.
+    \item The Aggravater strategy which plays like Grudger (responding to any
+        defections with unconditional defections throughout) however starts by
+        playing 3 defections.
+    \item Predator, a finite state machine described in~\cite{Ashlock2006}.
 \end{enumerate}
@@
 
-As will be demonstrated in Section~\ref{sec:population_size} the results for \(N=2\)
-differ from those of larger $N$. Hence our results do not concur with the literature
-which suggests that Zero Determinant strategies should be effective for larger population
-sizes, but we note that those analysis run each match to stationarity, while
-our matches run for a fixed number of rounds.
+As will be demonstrated in Section~\ref{sec:population_size} the results for
+\(N=2\) differ from those of larger $N$. Hence our results do not concur with
+the literature which suggests that Zero Determinant strategies should be
+effective for larger population sizes, but we note that those analysis run each
+match to stationarity, while our matches run for a fixed number of rounds.
 
@@
 In this section we focus on the ability of a mutant strategy to invade: the
-probability of 1 individual of a given type successfully becoming fixated in
-a population of \(N - 1\) other individuals, denoted by \(x_i\).
-Figures~\ref{fig:fixation_heatmap_invade} shows these values for
-the players along the vertical axis when matched against the players on the
-horizontal axis. For population size $N$, a neutral mutant has fixation
-probability $x_1 = 1 / N$. This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
-showing the median fixation as well as the neutral fixation for each given
-scenario.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_3_invade.pdf}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_7_invade.pdf}
-        \caption{\(N=7\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_12_invade.pdf}
-        \caption{\(N=12\)}
-
-    %TODO Replace N=12 with N=14
-    \end{subfigure}%
-    %TODO Remove these? I don't feel they are effective
-
-    \caption{Pairwise fixation probability \(x_{1}\) of all strategies}
-    \label{fig:fixation_heatmap_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/boxplot_3_invade.pdf}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/boxplot_7_invade.pdf}
-        \caption{\(N=7\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/boxplot_12_invade.pdf}
-        \caption{\(N=12\)}
-    \end{subfigure}%
-
-    % TODO Replace N=12 with N=14 (when we have more data).
-    \caption{Median probabilities \(x_{1}\) of all strategies as well as the
-    neutral fixation probability}
-    \label{fig:fixation_boxplot_invade}
-\end{figure}
-
-For \(N\in\{3, 7, 12\}\) the top five strategies are given in
-% TODO Change N=12 to N=14
-Tables~\ref{tbl:top_five_invade}.
+probability of 1 individual of a given type successfully becoming fixated in a
+population of \(N - 1\) other individuals, denoted by \(x_i\). The fixation
+probabilities are shown in
+Figures~\ref{fig:boxplot_3_invade},~\ref{fig:boxplot_7_invade}
+and~\ref{fig:boxplot_14_invade} for \(N\in\{3, 7, 14\}\) showing the mean
+fixation as well as the neutral fixation for each given scenario.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.8\textheight]{./img/boxplot_3_invade.pdf}
+    \caption{The fixation probability \(x_1\) for \(N=3\)}
+    \label{fig:boxplot_3_invade}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.8\textheight]{./img/boxplot_7_invade.pdf}
+    \caption{The fixation probability \(x_1\) for \(N=7\)}
+    \label{fig:boxplot_7_invade}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.8\textheight]{./img/boxplot_14_invade.pdf}
+    \caption{The fixation probability \(x_1\) for \(N=14\)}
+    \label{fig:boxplot_14_invade}
+\end{figure}
+
+The top five strategies are given in Tables~\ref{tbl:top_five_invade}.
 
@@
         \centering
-        \input{./tex/summary_top_12_invade.tex}
-        \caption{\(N=12\)}
+        \input{./tex/summary_top_14_invade.tex}
+        \caption{\(N=14\)}
     \end{subfigure}
-    %TODO Change N=12 to N=14
     \caption{Properties of top five invaders}
@@
 
-It can be seen that apart from the Collective Strategy, none of the strategies
-of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 12\}\). The new
-% TODO Change N=12 to N=14
+It can be seen that apart from CS, none of the strategies
+of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
 high performing strategies are:
@@
 \begin{itemize}
-    \item Predator, a finite state machine described in~\cite{Ashlock2006}.
     \item Prober 4, complex strategy with an initial 20 move sequence of
@@
         as approximate handshake.
-    \item Remorseful Prober, a strategy that will not immediately retaliate when
-        it recognises that the opponent is retaliating to a random
-        defection~\cite{Li2011}.
-    \item  Worse and Worse 2: plays Tit For Tat for 20 moves and then defects
-        with with growing probability~\cite{prison}.
-    \item Tester: a strategy submitted to the second of Axelrod's tournaments
-        \cite{Axelrod1980b}.
-        % TODO Check if this list is still correct for N=14
+    \item Grudger (which only performs well for \(N=3\)), starts by cooperating
+        but will defect if at any point the opponent has defected.
+    \item MEM2, an infinite memory strategy that switches between TfT, Tf2T, and
+        Defector~\cite{Li2014}.
+    \item Fool Me Once, forgives one defection but defects forever once a second
+        defection takes place.
+    \item  PSO Gambler and Evolved Lookerup 2 2 2: are strategies that make use
+        of a lookup table mapping the first 2 moves of the opponent as well as
+        the last 2 moves of both players to an action. The PSO gambler is a
+        stochastic version which maps those states to probabilities of
+        cooperating. The lookerup was described in \cite{Knight2016}.
+	\item The evolved ANN strategies are neural networks that map a number of
+		attributes (first move, number of cooperations, last move etc\dots) to
+		an action. Both of these have been trained using an evolutionary
+		algorithm and the ANN 5 was trained to perform well in a noisy
+		tournament.
+	\item The Evolved FSM 16, is a 16 state finite machine strategy that has
+		been trained using an evolutionary algorithm.
 \end{itemize}
@@
 much greater than one, it is interesting to note that none of them are akin to
-memory one strategies. Most are not stochastic.
+memory one strategies. Only one is stochastic.
 
@@
 
-Figures~\ref{fig:fixation_heatmap_resist} show \(x_{N-1}\)
-the players along the vertical axis when matched against the players on the
-horizontal axis. This information is summarised in Figure~\ref{fig:fixation_boxplot_resist}
-showing the median fixation as well as the neutral fixation for each given
-scenario.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_3_resist.pdf}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_7_resist.pdf}
-        \caption{\(N=7\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/fixation_heatmap_12_resist.pdf}
-        \caption{\(N=12\)}
-
-    %TODO Replace N=12 with N=14
-    \end{subfigure}%
-    %TODO Remove these? I don't feel they are effective
-
-    \caption{Pairwise fixation probability \(x_{N-1}\) of all strategies}
-    \label{fig:fixation_heatmap_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/boxplot_3_resist.pdf}
-        \caption{\(N=2\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/boxplot_7_resist.pdf}
-        \caption{\(N=7\)}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/boxplot_12_resist.pdf}
-        \caption{\(N=12\)}
-    \end{subfigure}%
-
-    % TODO Replace N=12 with N=14 (when we have more data).
-    \caption{Median probabilities \(x_{N-1}\) of all strategies as well as the
-    neutral fixation probability}
-    \label{fig:fixation_boxplot_resist}
+The fixation
+probabilities are shown in
+Figures~\ref{fig:boxplot_3_resist},~\ref{fig:boxplot_7_invade}
+and~\ref{fig:boxplot_14_resist} for \(N\in\{3, 7, 14\}\) showing the mean
+fixation as well as the neutral fixation for each given scenario.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.8\textheight]{./img/boxplot_3_resist.pdf}
+    \caption{The fixation probability \(x_{N-1}\) for \(N=3\)}
+    \label{fig:boxplot_3_resist}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.8\textheight]{./img/boxplot_7_resist.pdf}
+    \caption{The fixation probability \(x_{N-1}\) for \(N=7\)}
+    \label{fig:boxplot_6_resist}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.8\textheight]{./img/boxplot_14_resist.pdf}
+    \caption{The fixation probability \(x_{N-1}\) for \(N=14\)}
+    \label{fig:boxplot_14_resist}
 \end{figure}
@@
 Table~\ref{tbl:top_five_resist} shows the top five strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 12\}\).
-% TODO Change 12 to 14
+according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
 Once again none of the short memory strategies from
@@
 
-Three strategies have both high \(x_1\) and high \(x_{N-1}\):
-
-\begin{itemize}
-    \item Collective
-    \item Predator
-    \item Prober 4
-\end{itemize}
-
-However, Remorseful Prober, Worse and Worse 2 and Tester no longer do as well.
-There are two strategies that are only top performers in \(x_{N-1}\):
+\begin{table}[!hbtp]
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{./tex/summary_top_3_resist.tex}
+        \caption{\(N=3\)}
+    \end{subfigure}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{./tex/summary_top_7_resist.tex}
+        \caption{\(N=7\)}
+    \end{subfigure}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        \input{./tex/summary_top_14_resist.tex}
+        \caption{\(N=14\)}
+    \end{subfigure}
+    \caption{Properties of top five resistors}
+    \label{tbl:top_five_resist}
+\end{table}
+
+There are 3 strategies that are only top performers in \(x_{N-1}\):
 
@@
         \cite{Mathieu2015}.
+	\item Predator: a finite state machine described in~\cite{Ashlock2006}
 \end{itemize}
-% TODO Revise this if need be for N=14
 
@@
 handshake'' \cite{Lee2015}.
-
-\begin{table}[!hbtp]
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \input{./tex/summary_top_3_resist.tex}
-        \caption{\(N=3\)}
-    \end{subfigure}
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \input{./tex/summary_top_7_resist.tex}
-        \caption{\(N=7\)}
-    \end{subfigure}
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        \input{./tex/summary_top_12_resist.tex}
-        \caption{\(N=12\)}
-    \end{subfigure}
-    %TODO Change N=12 to N=14
-    \caption{Properties of top five resistors}
-    \label{tbl:top_five_resist}
-\end{table}
 
@@
 and~\ref{tbl:ranks_v_size_coexist} show the same information for the strategies
-that rated high for \(N=2\) and \(N=12\).
-% TODO Change to N=14?
+that rated high for \(N=2\) and \(N=14\).
 
@@
 and~\ref{tbl:correlation_coeficients_coexist} show the correlation coefficients
-of the ranks in of strategies in differing population size. This is shown
+of the ranks of strategies in differing population size. This is shown
 graphically in Figure~\ref{fig:correlation_coefficients}. It is immediate to
@@
 
-For \(N=2\), memory one strategies perform well, in particular as predicted by
-\cite{Press2012} zero determinant strategies rank highly. However, there are no
-memory one strategies in the top 5 performing strategies for \(N>3\). This is
-due to their lack of sophistication which allows them to recognise and adjust to
-their opponent.
+Memory one strategies do not perform well, as predicted by \cite{Press2012}.
+However, there are no memory one strategies in the top 5 performing strategies
+for \(N>3\). This is due to their lack of sophistication which allows them to
+recognise and adjust to their opponent. Some very sophisticated strategies
+proves to be high performers for invasion: these are infinite memory strategies
+which have been trained using a number of reinforcement learning algorithms.
+Interestingly they have been trained to perform well in tournaments and not
+Moran processes which highlights the potentially for improvement.
 

### 2017-05-09 src/players.py
Update players.py

@@ -44,7 +44,7 @@ fsm_transitions = [
      (6, C, 6, D), (6, D, 6, D),
      (7, C, 7, D), (7, D, 5, C)]]
 
-fsm_players = [axl.FSMPlayer(transitions=transitions)
+fsm_players = [axl.FSMPlayer(transitions=transitions, initial_state=0, initial_action=C)
                for transitions in fsm_transitions]
 
 def selected_players(extra_players=fsm_players):

### 2017-05-09 src/generate_cache.py
Add temporary mod to run missing FSMs

@@ -5,7 +5,6 @@ import multiprocessing
 import os
 
 import axelrod as axl
-#from approximate_moran import *
 
 def write_csv(outcomes, filename="outcomes.csv", append=False):
     s = 'w'
@@ -38,7 +37,9 @@ def generate_matchups_indices(num_players):
     # Want the triangular product
     for i in range(num_players):
         for j in range(i, num_players):
-            yield i, j
+            # Add code to rerun last 3 players
+            if j in [num_players - i for i in range(3)]:
+                yield i, j
 
 def sample_match_outcomes(players, turns, repetitions, noise=0):
     """
@@ -68,7 +69,7 @@ def sample_match_outcomes(players, turns, repetitions, noise=0):
 
 def write_winner(filename, turns, repetitions, noise, i, j, seed=None):
     """
-    Write the winner of a Moran process to file
+    Write the scores of a match between two players to file
     """
     if seed:
         axl.seed(seed)  # Seed the process
@@ -121,18 +122,14 @@ if __name__ == "__main__":
     print(len(list(map(str, players))))
 
     try:
-        os.remove("../data/outcomes.csv")
-        os.remove("../data/outcomes_noise.csv")
+        os.remove("../data/missing_fsm_outcomes.csv")
     except FileNotFoundError:
         pass
 
     repetitions = 1000
     turns = 200
 
+    cpu_count = multiprocessing.cpu_count()
     sample_match_outcomes_parallel(turns=turns, repetitions=repetitions,
-                                   filename="../data/outcomes.csv", noise=0,
-                                   processes=4)
-
-    sample_match_outcomes_parallel(turns=turns, repetitions=repetitions,
-                                   filename="../data/outcomes_noise.csv", noise=0.05,
-                                   processes=4)
+                                   filename="../data/missing_fsm_outcomes.csv", noise=0,
+                                   processes=cpu_count)

### 2017-05-09 src/players.py

@@ -44,7 +44,9 @@ fsm_transitions = [
      (6, C, 6, D), (6, D, 6, D),
      (7, C, 7, D), (7, D, 5, C)]]
 
-fsm_players = [axl.FSMPlayer(transitions=transitions, initial_state=0, initial_action=C)
+fsm_players = [axl.FSMPlayer(transitions=transitions)
+               for transitions in fsm_transitions]
+fsm_players += [axl.FSMPlayer(transitions=transitions, initial_state=0, initial_action=C)
                for transitions in fsm_transitions]
 
 def selected_players(extra_players=fsm_players):

### 2017-05-09 src/validate.py
Write output using csv module

@@ -4,6 +4,7 @@ A script to draw the validation plots.
 import pandas as pd
 import axelrod as axl
 import matplotlib.pyplot as plt
+import csv
 
 import generate_cache
 import theoretic
@@ -51,13 +52,13 @@ def theoretic_vs_simulated(repetitions, utilities, filename,
     starting_pop = [1, N // 2, N - 1] if N != 2 else [1]
 
     for i in starting_pop:
-        player_names = [p.__repr__() for p in players]
+        player_names = [str(p) for p in players]
         t = theoretic.fixation(player_names, N, i, utilities=utilities)
         s = simulated_fixation(players,  N, i, repetitions=repetitions)
 
         with open(filename, "a") as f:
-            f.write(",".join(map(str,
-                           [repetitions, N, i, *player_names, t, s])) + "\n")
+            writer = csv.writer(f)
+            writer.writerow([repetitions, N, i, *player_names, t, s])
 
 
 if __name__ == "__main__":

### 2017-05-09 src/generate_cache.py
Re run full cache.

@@ -37,9 +37,7 @@ def generate_matchups_indices(num_players):
     # Want the triangular product
     for i in range(num_players):
         for j in range(i, num_players):
-            # Add code to rerun last 3 players
-            if j in [num_players - i for i in range(3)]:
-                yield i, j
+            yield i, j
 
 def sample_match_outcomes(players, turns, repetitions, noise=0):
     """

### 2017-05-09 main.tex
Change plots for validation.
Not sure if I'm a fan.

Also, add some abbreviations.

@@
 that make use of the length of the game) as well as
-the following 3 finite state machine machine strategies \cite{Ashlock2006}:
-
-% TODO Include details about the 3 extra FSM strategies.
+the following 6 finite state machine machine strategies \cite{Ashlock2006}:
+
+% TODO Include details about the 3/6 extra FSM strategies.
 % Possibly draw pictorial representations?
 % Remove the FSM strategies if they don't perform well.
+% TODO Decide if we include all 6 (so the same original 3 with the wrong initial
+% state) in the entire analysis.
 

### 2017-05-09 src/abbreviations.py

@@ -8,13 +8,24 @@ abbreviations = {str(player):player.name for player in players.selected_players(
 
 # Some manual overwrites:
 
+abbreviations["Contrite Tit For Tat"] = "CTfT"
+abbreviations["Forgiving Tit For Tat"] = "FTfT"
 abbreviations["Tit For Tat"] = "TfT"
+abbreviations["Hard Tit For 2 Tats"] = "HTf2T"
+abbreviations["Hard Tit For Tat"] = "HTfT"
 abbreviations["CollectiveStrategy"] = "CS"
 abbreviations["Two Tits For Tat"] = "2TfT"
 abbreviations["Tit For 2 Tats"] = "Tf2T"
-abbreviations["Win-Stay Lose-Shift: C"] = "WSLS"
+abbreviations["Win-Stay Lose-Shift: C"] = "WStLSh"
+abbreviations["Win-Shift Lose-Stay: D"] = "WShLSt"
+abbreviations["ZD-GTFT-2: 0.25, 0.5"] = "ZD-GTFT"
+abbreviations["ZD-GEN-2: 0.125, 0.5, 3"] = "ZD-GEN-2"
+abbreviations["ZD-SET-2: 0.25, 0.0, 2"] = "ZD-SET-2"
 abbreviations["ZD-Extort-4: 0.23529411764705882, 0.25, 1"] = "ZD-Extort-4"
 abbreviations["ZD-Extort-2: 0.1111111111111111, 0.5"] = "ZD-Extort-2"
[…]

### 2017-05-10 main.tex
Remove section on relative fitness.

@@
 
-\subsection{Relative fitness}\label{sec:relative_fitness}
-
-% TODO I do not understand the narrative for this and what it adds to the paper.
-
-Under the assumption of a constant relative fitness \(r\) between two
-strategies~\cite{Nowak} the formula for \(x_i\) (for given \(N, r\) is:
-
-\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness}
-    x_i = x_i(r) = \frac{1-\frac{1}{r^{i}}}{1-\frac{1}{r^{N}}}
-\end{equation}
-
-Figure~\ref{fig:fixation_v_fitness_illustration} shows this function for
-\(N=10\) and \(i\in\{1, 5, 10\}\).
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.6\textwidth]{./img/fixation_v_fitness_illustration.pdf}
-    \caption{\(x_i(r)\)}
-    \label{fig:fixation_v_fitness_illustration}
-\end{figure}
-
-The first and second derivative of
-(\ref{equ:fixation_probability_with_constant_relative_fitness}) is given by equations
-(\ref{equ:fixation_probability_with_constant_relative_fitness_prime}) and
-(\ref{equ:fixation_probability_with_constant_relative_fitness_prime2}).
-
-\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime}
-    \frac{dx_i}{dr} = \input{./tex/fixation_probability_with_constant_relative_fitness_prime.tex}
-\end{equation}
-
-\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime2}
-    \frac{d^2x_i}{dr^2} = \input{./tex/fixation_probability_with_constant_relative_fitness_prime2.tex}
-\end{equation}
-
-Using these, Halley's method \cite{Alefeld2012} can be used to efficiently
-numerically invert \(x_i(r)\) to obtain a theoretic relative fitness \(r\) that
-gives the calculated \(x_i(r)\) between two strategies for a given \(N, i\).
-% TODO Say more things: I still think this is a bit cylic. The formula we are
-% using assumes a constant relative fitness which we know does not exist.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator_fitness.pdf}
-        \caption{Alternator and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector_fitness.pdf}
-        \caption{Alternator and Defector}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT_fitness.pdf}
-        \caption{Alternator and Tit For Tat}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_TfT_fitness.pdf}
-        \caption{Cooperator and Tit For Tat}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator_fitness.pdf}
-        \caption{Defector and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_TfT_fitness.pdf}
-        \caption{Defector and Tit For Tat}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT_fitness.pdf}
-        \caption{Win Stay Lose Shift and Tit For Tat}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT_fitness.pdf}
-        \caption{Alternator and Win Stay Lose Shift}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS_fitness.pdf}
-        \caption{Defector and Win Stay Lose Shift}
-    \end{subfigure}%
-    \caption{Estimated relative fitness
-             for \textbf{deterministic} strategies}
-    \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator_fitness.pdf}
-        \caption{Random and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector_fitness.pdf}
-        \caption{Random and Defector}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_TfT_fitness.pdf}
-        \caption{Random and Tit For Tat}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Cooperator_fitness.pdf}
-        \caption{All C or all D and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Defector_fitness.pdf}
-        \caption{All C or all D and Defector}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Random_fitness.pdf}
-        \caption{Calculator and Random}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD_fitness.pdf}
-        \caption{Calculator and All C or all D}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner_fitness.pdf}
-        \caption{Calculator and Arrogant Q learner}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_TfT_fitness.pdf}
-        \caption{All C or all D and Tit For Tat}
-    \end{subfigure}%
-    \caption{Estimated relative fitness
-             for \textbf{stochastic} strategies}
-    \label{fig:comparison_stochastic}
-\end{figure}
-
 \section{Conclusion}\label{sec:conclusion}

### 2017-05-10 src/theoretic.py

@@ -97,40 +97,6 @@ def fixation(strategy_pair, N, i, utilities,
         return (1 + s[i - 2]) / (1 + s[-1])
     return 1 / (1 + s[-1])
 
-
-def phi(N, i, r):
-    """
-    The fixation probability in a population with constant fitness r
-    """
-    return (1 - 1/(r ** i)) / (1 - 1/(r ** N))
-
-def phi_prime(N, i, r):
-    """
-    The derivative of `phi` (used for numerical root)
-    """
-    numerator = r ** (N - i - 1) * (-N * r ** i + N + i * r ** N - i)
-    denominator =(r ** (2 * N) - 2 * r ** N + 1)
-    return numerator / denominator
-
-def phi_prime2(N, i, r):
-    """
-    The second derivative of `phi` (used for numerical root)
-    """
-    numerator = r ** (N - i - 2) * (2 * N ** 2 * (r ** i - 1) + N * (r ** N - 1) * (N * (r ** i - 1) - 2 * i + r ** i - 1) - i * (i + 1) * (r ** N - 1) ** 2)
-    denominator = (r**N - 1)**3
-    return numerator / denominator
-
-@functools.lru_cache()
-def find_relative_fitness(N, i, p, initial_r=1.2):
-    """
-    Obtain constant fitness rate that corresponds to a given fixation
-    probability p.
-    """
-    f = lambda r: phi(N, i, r) - p
-    fprime = lambda r:phi_prime(N, i, r)
-    fprime2 = lambda r:phi_prime2(N, i, r)
-    return newton(f, x0=initial_r, fprime=fprime, fprime2=fprime2)
-
 #########
 # Tests #
 #########

### 2017-05-10 src/write_fitness.py

@@ -5,16 +5,14 @@ TODO: Get rid of the intermediate step in `clean_raw_moran.py` and do it all in
 one go.
 """
 import pandas as pd
-import theoretic
 import tempfile
 
 def merged_df(N):
     summary = pd.read_csv("../data/sims_summary.csv")
     summary = summary[summary["N"] == N]
 
-    columns = [["player", "opponent", "N", "Noise", "$p_1$", "$p_{N/2}$",
-                "$r_1$", "$r_{N/2}$"],
-               ["player", "opponent", "N", "Noise", "$p_{N-1}$", "$r_{N-1}$"]]
+    columns = [["player", "opponent", "N", "Noise", "$p_1$", "$p_{N/2}$"],
+               ["player", "opponent", "N", "Noise", "$p_{N-1}$"]]
     dfs = [[], []]
     for (player, N, opponent, Noise), df in summary.groupby(["P1", "N",
                                                              "P2", "Noise"]):
@@ -34,30 +32,9 @@ def merged_df(N):
         except IndexError:
             pnover2 = float("nan")
 
-
-        try:
-            r1 = theoretic.find_relative_fitness(N, 1, p1)
-        except RuntimeError:
-            r1 = float("nan")
-
-        try:
-            rminus1 = theoretic.find_relative_fitness(N, N - 1, pminus1)
-        except RuntimeError:
-            rminus1 = float("nan")
-
-        if N % 2 == 0:
-            try:
-                rnover2 = theoretic.find_relative_fitness(N, N / 2, pnover2)
-            except RuntimeError:
-                rnover2 = float("nan")
-        else:
-            rnover2 = float("nan")
-
-        dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, p1, pnover2,
-                                     r1, rnover2]],
+        dfs[0].append(pd.DataFrame([[player, opponent, N, Noise, p1, pnover2]],
                                    columns=columns[0]))
-        dfs[1].append(pd.DataFrame([[opponent, player, N, Noise, pminus1,
-                                     rminus1]],
+        dfs[1].append(pd.DataFrame([[opponent, player, N, Noise, pminus1]],
                                    columns=columns[1]))
 
     dfs = [pd.concat(dfs[0]), pd.concat(dfs[1])]

### 2017-05-10 src/validate.py
Return to previous validation.

@@ -87,7 +87,26 @@ if __name__ == "__main__":
                     (axl.Alternator(), axl.ZDExtort2()),
                     (axl.Alternator(), axl.GTFT()),
                     (axl.Alternator(), axl.ALLCorALLD()),
-                    (axl.Alternator(), axl.PSOGambler2_2_2())]
+                    (axl.Alternator(), axl.PSOGambler2_2_2()),
+                    (axl.ALLCorALLD(), axl.Cooperator()),
+                    (axl.ALLCorALLD(), axl.Defector()),
+                    (axl.ALLCorALLD(), axl.TitForTat()),
+                    (axl.Alternator(), axl.Cooperator()),
+                    (axl.Alternator(), axl.Defector()),
+                    (axl.Alternator(), axl.TitForTat()),
+                    (axl.Alternator(), axl.WinStayLoseShift()),
+                    (axl.Defector(), axl.WinStayLoseShift()),
+                    (axl.Calculator(), axl.ALLCorALLD()),
+                    (axl.Calculator(), axl.ArrogantQLearner()),
+                    (axl.Calculator(), axl.Random()),
+                    (axl.Cooperator(), axl.TitForTat()),
+                    (axl.Defector(), axl.Cooperator()),
+                    (axl.Defector(), axl.TitForTat()),
+                    (axl.Random(), axl.Cooperator()),
+                    (axl.Random(), axl.Defector()),
+                    (axl.Random(), axl.TitForTat()),
+                    (axl.WinStayLoseShift(), axl.TitForTat())]
+
 
     max_N = 20
     repetitions = 1000

### 2017-05-10 main.tex
Adjust nb and rerun images.
Add tables for ZD strategies.

@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector.pdf}
-        \caption{Alternator and Defector}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_Alternator.pdf}
+        \caption{Defector and Alternator}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT.pdf}
+        \includegraphics[width=.8\textwidth]{./img/WStLSh_v_TfT.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WSLS.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WStLSh.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_WStLSh.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
 
+% TODO Add discussion about ZD strategies
+
+\begin{table}[!hbtp]
+    \centering
+    \scriptsize
+    \input{./tex/ZD_ranks_invade.tex}
+    \caption{Ranks of Zero determinant strategies according to \(x_{1}\) for different
+    population sizes}
+    \label{tbl:ZD_ranks_v_invade}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+    \scriptsize
+    \input{./tex/ZD_ranks_resist.tex}
+    \caption{Ranks of Zero determinant strategies according to \(x_{N-1}\) for different
+    population sizes}
+    \label{tbl:ZD_ranks_v_size_resist}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+    \scriptsize
+    \input{./tex/ZD_ranks_coexist.tex}
+    \caption{Ranks of Zero determinant strategies according to \(x_{N/2}\) for different
+    population sizes}
+    \label{tbl:ZD_ranks_v_size_coexist}
+\end{table}
+
 Tables~\ref{tbl:correlation_coeficients_invade},~\ref{tbl:correlation_coeficients_resist}

### 2017-05-11 src/preproces.py
Rename preprocessing script.

@@ -1,8 +1,5 @@
 """
-A script to write the relative fitness to file
-
-TODO: Get rid of the intermediate step in `clean_raw_moran.py` and do it all in
-one go.
+A script to write the final format of the data
 """
 import pandas as pd
 import tempfile

### 2017-05-11 main.tex
Add training section.

@@
 
-To carry out this large numerical experiment, 164 strategies are used from
-\cite{axelrodproject}. These include 161 default strategies in the library at
-the time (excluding strategies classified as having a long run time and those
-that make use of the length of the game) as well as
-the following 6 finite state machine machine strategies \cite{Ashlock2006}:
+To carry out this large numerical experiment, 164 strategies are used from the
+axelrod library: \cite{axelrodproject}.
 
-% TODO Include details about the 3/6 extra FSM strategies.
-% Possibly draw pictorial representations?
-% Remove the FSM strategies if they don't perform well.
-% TODO Decide if we include all 6 (so the same original 3 with the wrong initial
-% state) in the entire analysis.
-
+The axelrod library contains many machine learning based strategies trained
+with reinforcement learning algorithms. This work includes three additional
+strategies trained specifically to excel at the Moran process.
 Appendix~\ref{app:list_of_players} shows all the players in question. More
@@
 would have infinite memory depth.
+
+All of the
+strategies are trained with an evolutionary algorithm that perturbs strategy
+% TODO Add a generic text book reference
+parameters and optimizes an objective function, such as the mean total score
+against all other opponents or the mean fixation probability over a large
+number of Moran processes. The objective functions can include standard
+variations such as noisy matches, varying the number of rounds of play, and the
+other typical parameters used for the IPD. Variation is introduced via mutation
+and crossover of parameters, and the best performing strategies are carried to
+the next generation along with new variants. Similar methods appear in the
+literature \cite{Ashlock2006}.
+
+All of our training code is available in the
+Axelrod repository with documentation to train new strategies easily. Training
+% TODO Include link etc
+typically takes less than 200 iterations and can be completed within several
+hours on commodity hardware.  The three strategies trained specifically for
+this study are Trained FSM 1, 2, and 3 (TF1 - TF3), based on finite state
+machines of 16, 16, and 8 states respectively (see Figures \ref{}).
+% TODO Include images of FSMs
+These strategies were trained with the objective function of mean fixation
+probabilities for Moran processes starting at initial population states
+consisting of \(N/2\) individuals of the training candidates and \(N/2\)
+individuals of an opponent strategy, for all of the short run time strategies
+in the library (approximately 150 opponents at the time of training):
+
+\begin{itemize}
+	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per match
+	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per match
+	\item TF3 \(N=8\), 1\% noise, 100 repetitions per match
+\end{itemize}
+
+Each matchup of players was run to fixation for the specified number of
+repetitions to estimate the absorption probabilities. The trained algorithms
+were run for less than 50 generations.
+
+TF1 has an initial handshake of CCD and cooperates if the opponent matches.
+However if the opponent later defects, TF1 will respond in kind, so the
+handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
+achieve cooperation with TF1 after about 20 rounds of play.
+
+TF2 always starts
+with CD and will defect against opponents that start with DD. It plays CDD
+against itself and then cooperates thereafter. There is a longer complex
+handshake which eventually results in mutual cooperation with Firm but Fair,
+Fortress3, Fortress4, and Grofman (always) and Evolved HMM 5 and GTFT
+(depending on the random seed).
+
+TF3 cooperates and defects with
+various cycles depending on the opponent's actions. TF3 will mutually
+cooperate with any strategy and only tolerates a few defections before
+defecting for the rest of match. It is similar to but not exactly the same as
+Fool Me Once, a strategy that cooperates until the opponent has defected twice
+(not necessarily consecutively), and defects indefinitely thereafter. Though a
+product of training with a Moran objective, it was selected for inclusion
+because of the lack of an apparent handshake.
+
+For both TF1 and TF2 a handshake
+mechanism naturally emerges from the structure of the underlying finite state
+machine. This behavior is an outcome of the evolutionary process and is in no
+way hard-coded or included via an additional mechanism. Some of the existing
+strategies in the library were trained on earlier versions of the library
+(smaller total opponents used in training) based on neural networks, lookup
+tables and stochastic variants trained with a particle swarm algorithm, finite
+state machines and a stochastic variant mimicking hidden Markov models, and
+neural networks. These strategies were trained to win IPD tournaments using an
+objective function that computes the mean match payoffs against a collection of
+opponents. Detailed descriptions and the performance of these strategies in IPD
+tournaments will be described in another manuscript.
+% TODO Think of how to reference this upcoming manuscript
+% TODO Move the section below to the discussion for particular
+% cases and/or conclusion
+These strategies trained with the mean score
+objective are among the best invaders in the library but are not as resistant
+to invasion as the strategies trained using a Moran objective function (see
+Tables \ref{}). These strategies include trained finite state machine
+strategies, but they do not appear to have handshaking mechanisms. Therefore it
+is reasonable to conclude that the objective function is the cause of the
+emergence of handshaking mechanisms.
+The payoff maximizing strategies
+typically will not defect before the opponent's first defection, possibly
+because the training strategy collection contains a significant portion of
+strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
+for the remainder of the match if the opponent has more than a small number of
+cumulative defections. Paradoxically it is necessary to defect in order to
+achieve mutual cooperation with opponents using the same strategy but not with
+other opponents. A handshake requires at least one defection and there is
+selective pressure to defect as few times as possible to achieve the
+self-recognition mechanism. It is also unwise to defect on the first move as
+some strategies additionally retaliate first round defections. So the
+handshakes used by TF1 and TF2, and CS, are in some sense optimal.  These
+discoveries may have significant ramifications regarding the evolution of
+cooperation and forgiveness in biological organisms and social interactions
+between humans.
 

### 2017-05-11 src/abbreviations.py

@@ -23,9 +23,9 @@ abbreviations["ZD-GEN-2: 0.125, 0.5, 3"] = "ZD-GEN-2"
 abbreviations["ZD-SET-2: 0.25, 0.0, 2"] = "ZD-SET-2"
 abbreviations["ZD-Extort-4: 0.23529411764705882, 0.25, 1"] = "ZD-Extort-4"
 abbreviations["ZD-Extort-2: 0.1111111111111111, 0.5"] = "ZD-Extort-2"
-abbreviations["FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C"] =  "Trained FSM 1"
-abbreviations["FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, '
[…]

### 2017-05-11 src/players.py
Add a guess for the memory of TF{1,2,3}.

@@ -49,6 +49,10 @@ fsm_players = [axl.FSMPlayer(transitions=transitions)
 fsm_players += [axl.FSMPlayer(transitions=transitions, initial_state=0, initial_action=C)
                for transitions in fsm_transitions]
 
+fsm_players[0].classifier["memory_depth"] = float('inf')
+fsm_players[1].classifier["memory_depth"] = float('inf')
+fsm_players[2].classifier["memory_depth"] = 16
+
 def selected_players(extra_players=fsm_players):
     """
     Return a list of all players used in this paper

### 2017-05-11 main.tex
Adjust tex file to match new results.

@@
 this study are Trained FSM 1, 2, and 3 (TF1 - TF3), based on finite state
-machines of 16, 16, and 8 states respectively (see Figures \ref{}).
+machines of 8, 16, and 16 states respectively (see Figures \ref{}).
 % TODO Include images of FSMs
@@
 \begin{itemize}
-	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per match
+	\item TF1 \(N=8\), 1\% noise, 100 repetitions per match
 	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per match
-	\item TF3 \(N=8\), 1\% noise, 100 repetitions per match
+	\item TF3 \(N=12\), 0\% noise, 10000 repetitions per match
 \end{itemize}
@@
 
-TF1 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
-achieve cooperation with TF1 after about 20 rounds of play.
+TF1 cooperates and defects with
+various cycles depending on the opponent's actions. TF1 will mutually
+cooperate with any strategy and only tolerates a few defections before
+defecting for the rest of match. It is similar to but not exactly the same as
+Fool Me Once, a strategy that cooperates until the opponent has defected twice
+(not necessarily consecutively), and defects indefinitely thereafter. Though a
+product of training with a Moran objective, it was selected for inclusion
+because of the lack of an apparent handshake.
 
@@
 
-TF3 cooperates and defects with
-various cycles depending on the opponent's actions. TF3 will mutually
-cooperate with any strategy and only tolerates a few defections before
-defecting for the rest of match. It is similar to but not exactly the same as
-Fool Me Once, a strategy that cooperates until the opponent has defected twice
-(not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it was selected for inclusion
-because of the lack of an apparent handshake.
+TF3 has an initial handshake of CCD and cooperates if the opponent matches.
+However if the opponent later defects, TF3 will respond in kind, so the
+handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
+achieve cooperation with TF3 after about 20 rounds of play.
 
-For both TF1 and TF2 a handshake
+For both TF2 and TF3 a handshake
 mechanism naturally emerges from the structure of the underlying finite state
@@
 % TODO Think of how to reference this upcoming manuscript
-% TODO Move the section below to the discussion for particular
-% cases and/or conclusion
-These strategies trained with the mean score
-objective are among the best invaders in the library but are not as resistant
-to invasion as the strategies trained using a Moran objective function (see
-Tables \ref{}). These strategies include trained finite state machine
-strategies, but they do not appear to have handshaking mechanisms. Therefore it
-is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms.
-The payoff maximizing strategies
-typically will not defect before the opponent's first defection, possibly
-because the training strategy collection contains a significant portion of
-strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
-for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically it is necessary to defect in order to
-achieve mutual cooperation with opponents using the same strategy but not with
-other opponents. A handshake requires at least one defection and there is
-selective pressure to defect as few times as possible to achieve the
-self-recognition mechanism. It is also unwise to defect on the first move as
-some strategies additionally retaliate first round defections. So the
-handshakes used by TF1 and TF2, and CS, are in some sense optimal.  These
-discoveries may have significant ramifications regarding the evolution of
-cooperation and forgiveness in biological organisms and social interactions
-between humans.
 
@@
 $(N/2, N/2)$ and $(N-1 , 1)$, for \(N\) from 2 through 14. The
-% TODO Change 14 to 12 if we do not use the 14 case.
 fixation probability is then empirically computed for each combination of
@@
 Our software can carry out exact simulations of the Moran process. Since some of
-the strategies have a high computational cost or are stochastic, we sample
-from a large number of match outcomes for the pairs of players for use in computing
-fitnesses in the Moran process. This approach was verified to agree with unsampled
-calculations to a high degree of accuracy in specific cases.
+the strategies have a high computational cost or are stochastic, we sample from
+a large number of match outcomes for the pairs of players for use in computing
+fitnesses in the Moran process. This approach was verified to agree with
+unsampled calculations to a high degree of accuracy in specific cases.
 % TODO Perhaps write some pseudo code for this?
@@
 the number of outcomes between all strategy pairs.
-% TODO is this true? the distribution also matters, not just the number of outcomes
-% TODO Good point, we could (if we wanted to) go down the line of checking
-% specific distributions etc or perhaps we just remove and point at the good
-% fits in the Validation section as a justification.
 
@@
         between performance for differing population sizes.
-    \item Section~\ref{sec:relative_fitness} calculates the relative fitness of all
-        strategies.
 \end{itemize}
@@
 
-Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
-reflect a strategy's ability to invade or resist invasion; for \(N=2\) these two cases
-coincide. Figure~\ref{fig:boxplot_2} shows
-all fixation probabilities for the strategies considered. This is summarised
-in Table~\ref{tbl:summary_top_2}.
+Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\),
+these reflect a strategy's ability to invade or resist invasion; for \(N=2\)
+these two cases coincide. Figure~\ref{fig:boxplot_2} shows all fixation
+probabilities for the strategies considered. This is summarised in
+Table~\ref{tbl:summary_top_2}.
 
@@
         evolutionary processes.
-    \item The finite state machine strategy % TODO Perhaps refer to earlier
-        % discussion in the methodology section about these FSM strategies
     \item The Defector: it always defects. As it has little potential
@@
     \item Predator, a finite state machine described in~\cite{Ashlock2006}.
+    \item Handshake: a slightly less aggressive version of the Collective
+        strategy \cite{robson1989}. As long as the initial sequence is played
+        then it cooperates. Thus it will do well in a population consisting of
+        many members of itself: just as the Collective strategy does. However it
+        is not aggressive enough to invade other populations.
 \end{enumerate}
@@
 \begin{itemize}
-    \item Prober 4, complex strategy with an initial 20 move sequence of
-        cooperations and defections~\cite{prison}. This initial sequence serves
-        as approximate handshake.
     \item Grudger (which only performs well for \(N=3\)), starts by cooperating
@@
         Defector~\cite{Li2014}.
-    \item Fool Me Once, forgives one defection but defects forever once a second
-        defection takes place.
+    \item TF1, the finite state machine trained specifically for Moran processes
+        described in Section~\cite{sec:introduction}.
+    \item Prober 4, complex strategy with an initial 20 move sequence of
+        cooperations and defections~\cite{prison}. This initial sequence serves
+        as approximate handshake.
     \item  PSO Gambler and Evolved Lookerup 2 2 2: are strategies that make use
@@
 		tournament.
-	\item The Evolved FSM 16, is a 16 state finite machine strategy that has
-		been trained using an evolutionary algorithm.
+    \item The Evolved FSM 16 is a 16 state finite state machine trained to
+        perform well in tournaments.
 \end{itemize}
@@
 much greater than one, it is interesting to note that none of them are akin to
-memory one strategies. Only one is stochastic.
+memory one strategies. Only one is stochastic. The finite state machines trained
+specifically for Moran processes do not appear in the top 5: whereas strategies
+trained for tournament do. This is due to the nature of invasion: most of the
+opponents will initially be different strategies.
+
+The strategies trained with the mean score
+objective are among the best invaders in the library but are not as resistant
+to invasion as the strategies trained using a Moran objective function. These strategies include trained finite state machine
+strategies, but they do not appear to have handshaking mechanisms. Therefore it
+is reasonable to conclude that the objective function is the cause of the
+emergence of handshaking mechanisms.
+The payoff maximizing strategies
+typically will not defect before the opponent's first defection, possibly
+because the training strategy collection contains a significant portion of
+strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
+for the remainder of the match if the opponent has more than a small number of
+cumulative defections. Paradoxically it is necessary to defect in order to
+achieve mutual cooperation with opponents using the same strategy but not with
+other opponents. The importance of these handshakes will become apparent in the
+next Section.
 
@@
 
-There are 3 strategies that are only top performers in \(x_{N-1}\):
-
-\begin{itemize}
-    \item Handshake: a slightly less aggressive version of the Collective
-        strategy \cite{robson1989}. As long as the initial sequence is played
-        then it cooperates. Thus it will do well in a population consisting of
-        many members of itself: just as the Collective strategy does. However it
-        is not aggressive enough to invade other populations.
-    \item Winner 21: a strategy that makes its decision deterministically based
-        on 1 round of its own strategy and 2 of the opponent's strategy
-        \cite{Mathieu2015}.
-	\item Predator: a finite state machine described in~\cite{Ashlock2006}
-\end{itemize}
+There are are only two new strategies that appear in the top ranks for
+\(x_{N-1}\): TF2 and TF3. These two strategies are with from CS the strongest
+resistors. They all have handshakes, and whilst the handshake that CS has was
+programmed, the handshakes of TF2 and TF3 evolved through an evolutionary
+process. It is also worth noting that none of the highly trained strategies of
+Section~\ref{sec:strong_invaders} perform as well as resistors. This indicates
+the subtlety needed to recognise true opponents.
 
@@
 kind. In essence: acting stochastically increase the chance of friendly fire.
-However we note that it is possible to design a strategy with a ``stochastic
+However it is possible to design a strategy with a ``stochastic
 handshake'' \cite{Lee2015}.
+
+A handshake requires at least one defection and there is
+selective pressure to defect as few times as possible to achieve the
+self-recognition mechanism. It is also unwise to defect on the first move as
+some strategies additionally retaliate first round defections. So the
+handshakes used by TF2 and TF3, and CS, are in some sense optimal.  These
+discoveries may have significant ramifications regarding the evolution of
+cooperation and forgiveness in biological organisms such as antibacterial
+resistant bacteria and social interactions
+between humans.
 
@@
 
+% Discuss handshakes again. I think this is an important point.
+
 All source code for this work has been written in a sustainable manner: it is

### 2017-05-11 src/abbreviations.py

@@ -18,11 +18,6 @@ abbreviations["Two Tits For Tat"] = "2TfT"
 abbreviations["Tit For 2 Tats"] = "Tf2T"
 abbreviations["Win-Stay Lose-Shift: C"] = "WStLSh"
 abbreviations["Win-Shift Lose-Stay: D"] = "WShLSt"
-abbreviations["ZD-GTFT-2: 0.25, 0.5"] = "ZD-GTFT"
-abbreviations["ZD-GEN-2: 0.125, 0.5, 3"] = "ZD-GEN-2"
-abbreviations["ZD-SET-2: 0.25, 0.0, 2"] = "ZD-SET-2"
-abbreviations["ZD-Extort-4: 0.23529411764705882, 0.25, 1"] = "ZD-Extort-4"
-abbreviations["ZD-Extort-2: 0.1111111111111111, 0.5"] = "ZD-Extort-2"
 abbreviations["FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C"] =  "TF1"
[…]

### 2017-05-11 src/players.py

@@ -49,9 +49,9 @@ fsm_players = [axl.FSMPlayer(transitions=transitions)
 fsm_players += [axl.FSMPlayer(transitions=transitions, initial_state=0, initial_action=C)
                for transitions in fsm_transitions]
 
-fsm_players[0].classifier["memory_depth"] = float('inf')
-fsm_players[1].classifier["memory_depth"] = float('inf')
-fsm_players[2].classifier["memory_depth"] = 16
+fsm_players[3].classifier["memory_depth"] = float('inf')
+fsm_players[4].classifier["memory_depth"] = float('inf')
+fsm_players[5].classifier["memory_depth"] = 16
 
 def selected_players(extra_players=fsm_players):
     """

### 2017-05-12 main.tex
Add Owen C as author.
Write a first draft.
This has removed a number of things to make the paper a bit more
efficient. I have taken Marc's text about training strategies and moved
it around to fit better. It is also one of the main narratives of the
story now.

Note that I've removed "we" and "our" throughout.

@@
 % Title
-\title{An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies}
-\author{Marc Harper \and Vincent Knight \and Nikoleta E. Glynatsi} % TODO Authors?
+\title{An Empirical Study of Invasion and Resistance
+       for Iterated Prisoner's Dilemma Strategies}
+\author{Vincent Knight \and
+        Marc Harper \and
+        Nikoleta E. Glynatsi \and
+        Owen Campbell} % TODO Authors?
 \date{}
@@
     probabilities for Moran processes are obtained for 164
-    different strategies. We find that players with long memories and
+    different strategies. It is found that players with long memories and
     sophisticated behaviours outperform many strategies that perform well
@@
 
-The Prisoner's Dilemma (PD)~\cite{Flood1958} is a fundamental two player game
+The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
 used to model a large variety of strategic interactions. Each player can choose
@@
 matter. This extended form is called the Iterated Prisoner's
-Dilemma (IPD).
+Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
+number of strategies have been developed to take advantage of the history of
+play. Recently, some strategies referred to as Zero Determinant strategies
+\cite{Press2012} even manipulate players through extortion.
 
@@
 evolutionary population dynamics that has been used to gain insights about the
-evolutionary stability and fixation of strategies in a number of settings.
-Similarly since the first Iterated Prisoner's Dilemma (IPD) tournament described in
-\cite{Axelrod1980a}, the Prisoner's dilemma has been used to understand the
-evolution of cooperative behaviour in complex systems. Several earlier
+evolutionary stability in a number of settings (more details given in
+Section~\ref{sec:the_moran_process}).
+Several earlier
 works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak, Stewart2012}.
+\cite{Nowak, Stewart2012}, however these often make simplifying assumptions
+and/or do not consider sophisticated behaviour: only considering strategies that
+either cooperate or defect.
 
-This manuscript provides a detailed numerical analysis of \textbf{164} complex
-and adaptive strategies for the IPD\@. This is made possible by the Axelrod
-library \cite{axelrodproject}, an effort to provide software for reproducible
-research for the IPD\@. The library now contains over 150 parameterized
+This manuscript provides a detailed numerical analysis of
+\textbf{\input{./tex/num_strategies.tex}}complex and adaptive strategies for the
+IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
+effort to provide software for reproducible research for the IPD\@. The library
+now contains over \input{./tex/num_strategies_axelrod.tex}parameterized
 strategies including classics like TitForTat and WinStayLoseShift, as well as
-recent variants such as OmegaTFT, zero determinant and other memory one
+recent variants such as OmegaTFT, Zero determinant and other memory one
 strategies, strategies based on finite state machines, lookup tables, neural
 networks, and other machine learning based strategies, and a collection of novel
-strategies. The library can conduct matches, tournaments and population
+strategies. Not all strategies have been considered for this study: same use
+knowledge of the game such as the number of turns and others have a high
+computational run time. The large number of strategies are available thanks to
+the open source nature of the project with over 40 contributions made by
+different programmers and researchers \cite{Knight2016}. Three of the considered
+strategies are finite state machines trained specifically for Moran processes
+(described further in Section~\ref{sec:strategies}.
+
+The library can conduct matches, tournaments and population
 dynamics with variations including noise and spatial structure.
+The strategies and simulation frameworks are
+automatically tested to an extraordinarily high degree of coverage in accordance
+with best research software practices.
 
-We present fixation probabilities for all pairs of
-strategies in the library, identifying those are effective invaders and
+Fixation probabilities for all pairs of
+strategies are presented, identifying those that are effective invaders and
 those resistant to invasion, for population sizes $N=2$ to $N=14$.
 
-In particular we address the following questions:
+In particular the following questions are addressed:
 \begin{enumerate}
@@
 
-While our results agree with some of the published literature, we find that:
+While the results agree with some of the published literature, it is found that:
 
@@
  \item Zero determinant strategies are not particularly effective for $N > 2$
- \item Long memory strategies are generally more effective than short
-       memory strategies
- \item Complex strategies can be effective
+ \item Complex strategies can be effective, and in fact can naturally evolve
+     through evolutionary processes to outperform intelligently designed
+     strategies.
+ \item Strong resistors specifically evolve or have a handshake mechanism. This
+     has the potential to offer insight in to organisms such as antibacterial
+     resistant bacteria \cite{Davies2010}.
 \end{enumerate}
 
-\subsection{The Moran Process}
+\subsection{The Moran Process}\label{sec:the_moran_process}
 
 Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
-process, a stochastic birth death process on a finite population
-in which the population size stays constant over time. Individuals are
-\textbf{selected} according to a given fitness landscape. Once selected, the
-individual is reproduced and similarly another individual is chosen to be
-removed from the population. In some settings mutation is also considered but
-without mutation (the case considered in this work) this process will arrive at
-an absorbing state where the population is entirely made up of players of
-one strategy. The probability with which a given strategy is the survivor is
-called the fixation probability. A more detailed analytic description of this
-is given in Section~\ref{sec:validation}.
+process, a stochastic birth death process on a finite population in which the
+population size stays constant over time. Individuals are \textbf{selected}
+according to a given fitness landscape. Once selected, the individual is
+reproduced and similarly another individual is chosen to be removed from the
+population. In some settings mutation is also considered but without mutation
+(the case considered in this work) this process will arrive at an absorbing
+state where the population is entirely made up of players of one strategy. The
+probability with which a given strategy is the survivor is called the
+\textit{fixation probability}. A more detailed analytic description of this is
+given in Section~\ref{sec:validation}.
 
@@
 looked at evolutionary stability of strategies within the Prisoner's Dilemma
-\cite{Li2014} but this is not done in the more widely-used setting of the Moran
+\cite{Li2014} but this is not done in the more widely used setting of the Moran
 process, rather in terms of infinite population stability. In \cite{Baek2016}
@@
 
-Of particular interest are the zero determinant strategies introduced in
-\cite{Press2012} and highly-praised \cite{Stewart2012} it was argued that
-generous ZD strategies are robust against invading strategies. However, in
-\cite{Lee2015} a strategy using machine learning techniques was capable of
-resisting invasion and also able to invade any memory one strategy.  Recent work
-\cite{Hilbe2017} has investigated the effect of memory length on strategy
-performance and the emergence of cooperation but this is not done in Moran
-process context and only considers specific cases of memory 2 strategies.  In
-\cite{Adami2013} it was recognized that many zero determinant strategies do not
-fare well against themselves. This is a disadvantage for the Moran process where
-the best strategies cooperate well with other players using the same strategy.
+Of particular interest are the Zero determinant strategies introduced in
+\cite{Press2012} and praised in \cite{Stewart2012} it was argued that generous
+ZD strategies are robust against invading strategies. However, in \cite{Lee2015}
+a strategy using machine learning techniques was capable of resisting invasion
+and also able to invade any memory one strategy. Recent work \cite{Hilbe2017}
+has investigated the effect of memory length on strategy performance and the
+emergence of cooperation but this is not done in Moran process context and only
+considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
+recognised that many Zero determinant strategies do not fare well against
+themselves. This is a disadvantage for the Moran process where the best
+strategies cooperate well with other players using the same strategy.
 
-The contribution of this work is a detailed and extensive analysis of absorption
-probabilities for 164 strategies. These strategies and the numerical simulations
-are from~\cite{axelrodproject} which is an open source research library written
-for the study of the IPD\@. The strategies and simulation frameworks are
-automatically tested to an extraordinarily high degree of coverage in accordance
-with best research software practices. The large
-number of strategies are available thanks to the open source nature of the
-project with over 40 contributions made by different programmers and researchers.
+\subsection{Strategies considered}\label{sec:strategies}
 
-Section~\ref{sec:methodology} will explain the methodological approach used,
-Section~\ref{sec:validation} will validate the methodology by comparing
-simulated results to analytical results in some cases. The main results of this
-manuscript are presented in Section~\ref{sec:empirical_results} which will
-present a detailed analysis of all the data generated. Finally,
-Section~\ref{sec:conclusion} will conclude and offer future avenues for the work
-presented here.
+To carry out this large numerical experiment, \input{./tex/num_strategies}
+strategies, listed in Appendix~\ref{app:list_of_players} are used library. There
+are \input{./tex/num_stochastic.tex}stochastic and
+\input{./tex/num_deterministic.tex}deterministic strategies. Their memory depth,
+defined by the number of rounds of history used by the strategy each round, is
+shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
+strategy uses the entire history of play (whatever its length). For example, a
+strategy that utilizes a handshaking mechanism where the opponents actions on
+the first few rounds of play determines the strategies subsequent behavior would
+have infinite memory depth.
 
-\section{Methodology}\label{sec:methodology}
+A number of these strategies have been trained with reinforcement learning
+algorithms.
 
-To carry out this large numerical experiment, 164 strategies are used from the
-axelrod library: \cite{axelrodproject}.
+\begin{itemize}
+    \item Evolved ANN: a neural network based strategy;
+    \item Evolved LookerUp: a lookup table based strategy;
+    \item PSO Gambler: a stochastic version of the lookup table based strategy;
+    \item Evolved HMM: a hidden Markov model based strategy.
+\end{itemize}
 
-The axelrod library contains many machine learning based strategies trained
-with reinforcement learning algorithms. This work includes three additional
-strategies trained specifically to excel at the Moran process.
-Appendix~\ref{app:list_of_players} shows all the players in question. More
+A part from the PSO Gambler strategy, which was trained using a particle swarm
+optimisation algorithm, all these strategies are trained with an evolutionary
+algorithm that perturbs strategy parameters and optimizes the mean total score
+against all other opponents \cite{affenzeller2009genetic}. Variation is
+introduced via mutation and crossover of parameters, and the best performing
+strategies are carried to the next generation along with new variants. Similar
+methods appear in the literature \cite{Ashlock2006}.
+
+More
 information about each player can be obtained in the documentation for
-\cite{axelrodproject}. There are \input{./tex/num_stochastic.tex}stochastic and
-\input{./tex/num_deterministic.tex}deterministic strategies. Their memory
-depth, defined by the number of rounds of history used by the strategy each round,
-is shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if
-the strategy uses the entire history of play (whatever its length). For example,
-a strategy that utilizes a handshaking mechanism where the opponents actions
-on the first few rounds of play determines the strategies subsequent behavior
-would have infinite memory depth.
+\cite{axelrodproject} and a detailed description of the performance
+ of these strategies in IPD
+tournaments will be described in upcoming manuscript.
+% TODO Think of how to reference this upcoming manuscript
 
-All of the
-strategies are trained with an evolutionary algorithm that perturbs strategy
-% TODO Add a generic text book reference
-parameters and optimizes an objective function, such as the mean total score
-against all other opponents or the mean fixation probability over a large
-number of Moran processes. The objective functions can include standard
-variations such as noisy matches, varying the number of rounds of play, and the
-other typical parameters used for the IPD. Variation is introduced via mutation
-and crossover of parameters, and the best performing strategies are carried to
-the next generation along with new variants. Similar methods appear in the
-literature \cite{Ashlock2006}.
-
-All of our training code is available in the
+All of the training code is available in the
 Axelrod repository with documentation to train new strategies easily. Training
@@
 typically takes less than 200 iterations and can be completed within several
-hours on commodity hardware.  The three strategies trained specifically for
-this study are Trained FSM 1, 2, and 3 (TF1 - TF3), based on finite state
-machines of 8, 16, and 16 states respectively (see Figures \ref{}).
+hours on commodity hardware.
+
+There are three further strategies trained specifically for this study; Trained
+FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 8, 16,
+and 16 states respectively (see Figures \ref{}).
 % TODO Include images of FSMs
-These strategies were trained with the objective function of mean fixation
-probabilities for Moran processes starting at initial population states
-consisting of \(N/2\) individuals of the training candidates and \(N/2\)
-individuals of an opponent strategy, for all of the short run time strategies
-in the library (approximately 150 opponents at the time of training):
+As opposed to the previously described strategies, these strategies were trained
+with the objective function of \textbf{mean fixation probabilities for Moran
+processes} starting at initial population states consisting of \(N/2\)
+individuals of the training candidates and \(N/2\) individuals of an opponent
+strategy, taken from a selection of 150 opponents from the axelrod library:
 
@@
 repetitions to estimate the absorption probabilities. The trained algorithms
-were run for less than 50 generations.
+were run for less than 50 generations. Training data for this is available at
+\cite{data}.
 
@@
 (not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it was selected for inclusion
-because of the lack of an apparent handshake.
+product of training with a Moran objective. Interestingly it has no handshake
+mechanism, this could be due to the fact that it is trained in a noisy
+environment.
 
-TF2 always starts
-with CD and will defect against opponents that start with DD. It plays CDD
-against itself and then cooperates thereafter. There is a longer complex
-handshake which eventually results in mutual cooperation with Firm but Fair,
-Fortress3, Fortress4, and Grofman (always) and Evolved HMM 5 and GTFT
-(depending on the random seed).
+TF2 always starts with CD and will defect against opponents that start with
+DD\@. It plays CDD against itself and then cooperates thereafter. There is a
+longer complex handshake which eventually results in mutual cooperation with
+Firm but Fair, Fortress3, Fortress4, and Grofman (always) and Evolved HMM 5 and
+GTFT (depending on the random seed).
 
@@
 machine. This behavior is an outcome of the evolutionary process and is in no
-way hard-coded or included via an additional mechanism. Some of the existing
-strategies in the library were trained on earlier versions of the library
-(smaller total opponents used in training) based on neural networks, lookup
-tables and stochastic variants trained with a particle swarm algorithm, finite
-state machines and a stochastic variant mimicking hidden Markov models, and
-neural networks. These strategies were trained to win IPD tournaments using an
-objective function that computes the mean match payoffs against a collection of
-opponents. Detailed descriptions and the performance of these strategies in IPD
-tournaments will be described in another manuscript.
-% TODO Think of how to reference this upcoming manuscript
+way hard-coded or included via an additional mechanism.
 
@@
 
-Each strategy pair is run for 1000 runs of the Moran process to fixation
-with starting population distributions of $(1, N-1)$,
-$(N/2, N/2)$ and $(N-1 , 1)$, for \(N\) from 2 through 14. The
-fixation probability is then empirically computed for each combination of
-starting distribution and value of \(N\).
+\subsection{Data collection}\label{sec:data_collection}
 
-Our software can carry out exact simulations of the Moran process. Since some of
-the strategies have a high computational cost or are stochastic, we sample from
-a large number of match outcomes for the pairs of players for use in computing
-fitnesses in the Moran process. This approach was verified to agree with
-unsampled calculations to a high degree of accuracy in specific cases.
-% TODO Perhaps write some pseudo code for this?
+Each strategy pair is run for 1000 repetitions of the Moran process to fixation
+with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
+1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
+computed for each combination of starting distribution and value of \(N\).  The
+axelrod library can carry out exact simulations of the Moran process. Since some
+of the strategies have a high computational cost or are stochastic, samples are
+taken
+from a large number of match outcomes for the pairs of players for use in
+computing fitnesses in the Moran process. This approach was verified to agree
+with unsampled calculations to a high degree of accuracy in specific cases.
+This is described in Figure~\ref{alg:psuedocode}.
+% TODO Include pseudo code
 
-Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
-the number of outcomes between all strategy pairs.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{./img/number_of_match_outcomes.pdf}
-        \caption{All matches}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{./img/number_of_stochastic_match_outcomes.pdf}
-        \caption{Stochastic matches}
-    \end{subfigure}%
-    \caption{The distribution of the number of unique outcomes used as the
-    cached results}
-    \label{fig:number_of_stochastic_match_outcomes}
-\end{figure}
-
-Section~\ref{sec:validation} will validate the methodology used here against
-known theoretic results.
+Section~\ref{sec:validation} will further validate the methodology by comparing
+simulated results to analytical results in some cases. The main results of this
+manuscript are presented in Section~\ref{sec:empirical_results} which will
+present a detailed analysis of all the data generated. Finally,
+Section~\ref{sec:conclusion} will conclude and offer future avenues for the work
+presented here.
 
@@
 
-Using this it is a known result that the fixation probability of the first
-strategy in a population of \(i\) individuals of the first type (and \(N-i\)
-individuals of the second. We have:
+Using this it is a known result \cite{Nowak2017} that the fixation probability
+of the first strategy in a population of \(i\) individuals of the first type
+(and \(N-i\) individuals of the second::
 
@@
 
-A neutral strategy will have fixation probability $x_i = i/N$. Alternatively,
-we can frame the outcomes in terms of relative fitness. For a strategy
-of relative fitness $r$ the fixation probability is well-known to be
-
-\[ x_i = \frac{1 - r^{-i}}{1 - r^{-N}} \]
-
-We can use this formula to compute a value $r_i$ that produces the observed
-value $x_i$, noting that for arbitrary strategies the value of this
-effective relative fitness is dependent on $i$ and $N$.
+A neutral strategy will have fixation probability $x_i = i/N$.
 
@@
 stochastic strategies. These are no longer a good match which highlights the
-weakness of the analytical formulae that relies on the average payoffs. A
-detailed analysis of the 164 strategies considered, using direct Moran processes
-will be shown in the next Section.
+weakness of the analytical formulae that relies on the average payoffs
+(\ref{equ:payoff_matrix}).
+
+All data generated for this validation exercise can be found
+at \cite{data}.
+
+A detailed analysis of the 164 strategies considered,
+using direct Moran processes will be shown in the next Section.
 
 \section{Empirical results}\label{sec:empirical_results}
-
-% TODO Archive all data (Zenodo) and include details/reference here.
 
@@
     \item Section~\ref{sec:population_size} investigates the relationship
-        between performance for differing population sizes.
+        between performance for differing population sizes as well as
+        taking a close look at Zero determinant strategies \cite{Press2012}.
 \end{itemize}
@@
 
-Overall the main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\),
-these reflect a strategy's ability to invade or resist invasion; for \(N=2\)
-these two cases coincide. Figure~\ref{fig:boxplot_2} shows all fixation
+For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
+considered separately for larger \(N\) in sections~\ref{sec:strong_invaders} and
+~\ref{sec:strong_resistors}.  Figure~\ref{fig:boxplot_2} shows all fixation
 probabilities for the strategies considered. This is summarised in
@@
         defect in the future it cooperates. Otherwise it defects for all
-        rounds~\cite{Li2009}. This strategy was specifically designed for
-        evolutionary processes.
+        rounds. This strategy was specifically designed for
+        evolutionary processes \cite{Li2009}.
     \item The Defector: it always defects. As it has little potential
-        interaction with itself, recall that \(N=2\) is considered, its
+        interaction with itself (recall that \(N=2\)), its
         aggressiveness is rewarded.
@@
         playing 3 defections.
-    \item Predator, a finite state machine described in~\cite{Ashlock2006}.
+    \item Predator, a finite state machine described in \cite{Ashlock2006}.
     \item Handshake: a slightly less aggressive version of the Collective
@@
         many members of itself: just as the Collective strategy does. However it
-        is not aggressive enough to invade other populations.
+        is not aggressive enough to invade other populations (as can be seen in
+        Section~\ref{sec:strong_invaders}.
 \end{enumerate}
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_2_invade.pdf}
+    \includegraphics[height=.9\textheight]{./img/boxplot_2_invade.pdf}
     \caption{The fixation probabilities for \(N=2\)}
@@
 As will be demonstrated in Section~\ref{sec:population_size} the results for
-\(N=2\) differ from those of larger $N$. Hence our results do not concur with
+\(N=2\) differ from those of larger $N$. Hence these results do not concur with
 the literature which suggests that Zero Determinant strategies should be
-effective for larger population sizes, but we note that those analysis run each
-match to stationarity, while our matches run for a fixed number of rounds.
+effective for larger population sizes, but these analysis consider stationary
+behaviour, while this work runs for a fixed number of rounds. Note that the
+stationarity assumptions allows for the analysis to take place leading to the
+conclusions about zero determinant strategies however it is dependent on a
+specific structure of strategies. The analysis carried out here makes no
+assumptions about the structure of the strategies by using actual simulation
+interactions.
 
-In the next sections we pay close attention to
-strategies who are strong invaders/resistors.
+In the next sections close attention to
+strategies who are strong invaders/resistors is given.
 
@@
 
-In this section we focus on the ability of a mutant strategy to invade: the
+In this section the focus is on the ability of a mutant strategy to invade: the
 probability of 1 individual of a given type successfully becoming fixated in a
-population of \(N - 1\) other individuals, denoted by \(x_i\). The fixation
+population of \(N - 1\) other individuals, denoted by \(x_1\). The fixation
 probabilities are shown in
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_3_invade.pdf}
-    \caption{The fixation probability \(x_1\) for \(N=3\)}
+    \includegraphics[height=.9\textheight]{./img/boxplot_3_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
     \label{fig:boxplot_3_invade}
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_7_invade.pdf}
-    \caption{The fixation probability \(x_1\) for \(N=7\)}
+    \includegraphics[height=.9\textheight]{./img/boxplot_7_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
     \label{fig:boxplot_7_invade}
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_14_invade.pdf}
-    \caption{The fixation probability \(x_1\) for \(N=14\)}
+    \includegraphics[height=.9\textheight]{./img/boxplot_14_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
     \label{fig:boxplot_14_invade}
@@
     \item MEM2, an infinite memory strategy that switches between TfT, Tf2T, and
-        Defector~\cite{Li2014}.
+        Defector \cite{Li2014}.
     \item TF1, the finite state machine trained specifically for Moran processes
-        described in Section~\cite{sec:introduction}.
+        described in Section~\ref{sec:introduction}.
     \item Prober 4, complex strategy with an initial 20 move sequence of
-        cooperations and defections~\cite{prison}. This initial sequence serves
+        cooperations and defections \cite{prison}. This initial sequence serves
         as approximate handshake.
@@
 much greater than one, it is interesting to note that none of them are akin to
-memory one strategies. Only one is stochastic. The finite state machines trained
-specifically for Moran processes do not appear in the top 5: whereas strategies
-trained for tournament do. This is due to the nature of invasion: most of the
-opponents will initially be different strategies.
-
-The strategies trained with the mean score
-objective are among the best invaders in the library but are not as resistant
-to invasion as the strategies trained using a Moran objective function. These strategies include trained finite state machine
-strategies, but they do not appear to have handshaking mechanisms. Therefore it
-is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms.
-The payoff maximizing strategies
-typically will not defect before the opponent's first defection, possibly
-because the training strategy collection contains a significant portion of
-strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
-for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically it is necessary to defect in order to
-achieve mutual cooperation with opponents using the same strategy but not with
-other opponents. The importance of these handshakes will become apparent in the
-next Section.
+memory one strategies. Only one is stochastic although close inspection of the
+source code of PSO Gambler shows that it makes stochastic decisions with extreme
+probabilities: almost always acting as expected. Apart from TF1 in \(N=3\), the
+finite state machines trained specifically for Moran processes do not appear in
+the top 5: whereas strategies trained for tournament do. This is due to the
+nature of invasion: most of the opponents will initially be different
+strategies. The next section will consider the converse situation.
 
@@
 
-In addition to identifying good invaders, we also identify strategies
-resistant to invasion by other strategies by examining the distribution
-of $x_{N-1}$ for each strategy. Note that this is equivalent to
-looking at $x_1$ for all opponents.
+In addition to identifying good invaders, strategies resistant to invasion by
+other strategies are identified by examining the distribution of $x_{N-1}$ for
+each strategy. Note that this is equivalent to looking at $x_1$ for all
+opponents.
 
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_3_resist.pdf}
+    \includegraphics[height=.9\textheight]{./img/boxplot_3_resist.pdf}
     \caption{The fixation probability \(x_{N-1}\) for \(N=3\)}
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_7_resist.pdf}
+    \includegraphics[height=.9\textheight]{./img/boxplot_7_resist.pdf}
     \caption{The fixation probability \(x_{N-1}\) for \(N=7\)}
@@
     \centering
-    \includegraphics[height=.8\textheight]{./img/boxplot_14_resist.pdf}
+    \includegraphics[height=.9\textheight]{./img/boxplot_14_resist.pdf}
     \caption{The fixation probability \(x_{N-1}\) for \(N=14\)}
@@
 
-There are are only two new strategies that appear in the top ranks for
-\(x_{N-1}\): TF2 and TF3. These two strategies are with from CS the strongest
-resistors. They all have handshakes, and whilst the handshake that CS has was
-programmed, the handshakes of TF2 and TF3 evolved through an evolutionary
-process. It is also worth noting that none of the highly trained strategies of
-Section~\ref{sec:strong_invaders} perform as well as resistors. This indicates
-the subtlety needed to recognise true opponents.
-
 Interestingly none of these strategies are stochastic: this is explained by
@@
 handshake'' \cite{Lee2015}.
+
+There are are only two new strategies that appear in the top ranks for
+\(x_{N-1}\): TF2 and TF3. These two strategies are with CS the strongest
+resistors. They all have handshakes, and whilst the handshake that CS and
+Handshake (which ranks highly for the smaller values of \(N\)) have was
+programmed, the handshakes of TF2 and TF3 evolved through an evolutionary
+process.
+
+As described in Section~\ref{sec:strong_invaders} the strategies trained with
+the payoff maximizing objective are among the best invaders in the library
+however they are not as resistant to invasion as the strategies trained using a
+Moran objective function. These strategies include trained finite state machine
+strategies, but they do not appear to have handshaking mechanisms. Therefore it
+is reasonable to conclude that the objective function is the cause of the
+emergence of handshaking mechanisms.
+
+The payoff maximizing strategies typically will not defect before the opponent's
+first defection, possibly because the training strategy collection contains a
+significant portion of strategies such as Grudger and Fool Me Once that
+retaliate harshly by defecting for the remainder of the match if the opponent
+has more than a small number of cumulative defections. Paradoxically it is
+necessary to defect (as a signal) in order to achieve mutual cooperation with
+opponents using the same strategy but not with other opponents.
 
@@
 difference depending on whether or not \(N>2\). This will be explored further in
-the next section.
+the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also consider
+\(x_{N/2}\).
 
@@
 Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
-and~\ref{fig:ranks_v_size_coexist} show the median rank of each strategy against
-population size. For all starting populations \(i\in\{1, N/2, N-1\}\) the ranks
-of strategies are relatively stable across the different values of \(N>2\)
-however for \(N=2\) there is a distinct difference. This confirms what has been
-discussed in previous sections.
+and~\ref{fig:ranks_v_size_coexist} show the rank of each strategy based on mean
+fixation probabilities against population size.
+Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
+and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
+strategies:
 
-Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
-and~\ref{tbl:ranks_v_size_coexist} show the same information for the strategies
-that rated high for \(N=2\) and \(N=14\).
+\begin{itemize}
+    \item The strategies that ranked highly for \(N=2\);
+    \item The strategies that ranked highly for \(N=14\);
+    \item The Zero determinant strategies.
+\end{itemize}
+
+For all starting populations
+\(i\in\{1, N/2, N-1\}\) the ranks of strategies are relatively stable across the
+different values of \(N>2\) however for \(N=2\) there is a distinct difference.
+This highlights that there is little that can be inferred about the evolutionary
+performance of a strategy in a large population from its performance in a small
+population.
+
+This is confirmed by the performance of the Zero determinant strategies, whilst
+some do rank relatively highly for \(N=2\) (ZD-extort-4 has tank 16) this rank
+does not translate to larger populations.
 
@@
 
-% TODO Add discussion about ZD strategies
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \input{./tex/ZD_ranks_invade.tex}
-    \caption{Ranks of Zero determinant strategies according to \(x_{1}\) for different
-    population sizes}
-    \label{tbl:ZD_ranks_v_invade}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \input{./tex/ZD_ranks_resist.tex}
-    \caption{Ranks of Zero determinant strategies according to \(x_{N-1}\) for different
-    population sizes}
-    \label{tbl:ZD_ranks_v_size_resist}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \input{./tex/ZD_ranks_coexist.tex}
-    \caption{Ranks of Zero determinant strategies according to \(x_{N/2}\) for different
-    population sizes}
-    \label{tbl:ZD_ranks_v_size_coexist}
-\end{table}
-
-Tables~\ref{tbl:correlation_coeficients_invade},~\ref{tbl:correlation_coeficients_resist}
-and~\ref{tbl:correlation_coeficients_coexist} show the correlation coefficients
-of the ranks of strategies in differing population size. This is shown
-graphically in Figure~\ref{fig:correlation_coefficients}. It is immediate to
+Figure~\ref{fig:correlation_coeficients} show the correlation coefficients
+of the ranks of strategies in differing population size. It is immediate to
 note that how well a strategy performs in any Moran process for \(N>2\) has
 little to do with the performance for \(N=2\). This illustrates why the strong
-performance of zero determinant strategies predicted in \cite{Press2012} does
+performance of Zero determinant strategies predicted in \cite{Press2012} does
 not extend to larger populations. This was discussed theoretically in
 \cite{Adami2013} however not observed empirically at the scale presented here.
-
-\begin{table}[!hbtp]
-    \centering
-    \begin{subfigure}{\textwidth}
-        \centering
-        \input{"./tex/correlation_coeficients_invade.tex"}
-        \caption{Correlation coefficients for ranks for invasion}
-        \label{tbl:correlation_coeficients_invade}
-    \end{subfigure}%
-
-    \begin{subfigure}{\textwidth}
-        \centering
-        \input{"./tex/correlation_coeficients_resist.tex"}
-        \caption{Correlation coefficients for ranks for resistance}
-        \label{tbl:correlation_coeficients_resist}
-    \end{subfigure}
-
-    \begin{subfigure}{\textwidth}
-        \centering
-        \input{"./tex/correlation_coeficients_coexist.tex"}
-        \caption{Correlation coefficients for ranks for coexistance}
-        \label{tbl:correlation_coeficients_coexist}
-    \end{subfigure}
-    \caption{Correlation coefficients of rankings by population size}
-\end{table}
 
@@
 starting values allowing the each strategy to attempt to invade the other.
-
 This is the largest such experiment carried out and has lead to many insights.
@@
 Memory one strategies do not perform well, as predicted by \cite{Press2012}.
-However, there are no memory one strategies in the top 5 performing strategies
+There are no memory one strategies in the top 5 performing strategies
 for \(N>3\). This is due to their lack of sophistication which allows them to
@@
 
+One of the major findings discussed in Section~\ref{sec:strong_resistors}, is
+the ability of strategies with a handshake mechanism to resist invasion. This
+was not only identify for CS (an intelligently designed strategy) but also for
+two FSM strategies (TF2 and TF3) specifically trained through an evolutionary
+process. In these two cases, the handshake mechanism was a product of the
+evolutionary process. This has the potential to help with the understanding of
+organisms with a strong resistance to invasion such as anti antibacterial
+resistant bacteria \cite{Davies2010}. With the knowledge that a handshake being
+likely to exist, perhaps it can be mimicked.
+
 It is felt that these findings are important for the ongoing understanding of
 population dynamics and offer evidence for some of the shortcomings of short
-memory which has started to be recognised by the community~\cite{Hilbe2017}.
-
-% Discuss handshakes again. I think this is an important point.
+memory which has started to be recognised by the community \cite{Hilbe2017}.
 
@@
 be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
-the processed data has also been properly archived.
+% TODO Add reference to source code
+the processed data has also been properly archived and can be fond
+at \cite{data}.
 
@@
 \begin{itemize}
-    \item The Axelrod library (IPD strategies and Moran processes)
+    \item The axelrod library (IPD strategies and Moran processes)
         \cite{axelrodproject}.

### 2017-05-13 main.tex
Add fsm imgs, algs and fix naming confusion.
I had mixed up TF1 and TF3. This is now fixed throughout.

@@
 \usepackage{fancyvrb}
+\usepackage{algorithm,algorithmic}
 
@@
 There are three further strategies trained specifically for this study; Trained
-FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 8, 16,
-and 16 states respectively (see Figures \ref{}).
-% TODO Include images of FSMs
+FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
+and 8 states respectively (see Figures~\ref{fig:tf1},~\ref{fig:tf2}
+and~\ref{fig:tf3}).
+
+\begin{figure}[!hbtp]
+    \centering
+    \input{./tex/fsm_one.tex}
+    \caption{TF1: a 16 state finite state machine.}
+    \label{fig:tf1}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \input{./tex/fsm_two.tex}
+    \caption{TF2: a 16 state finite state machine.}
+    \label{fig:tf2}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \input{./tex/fsm_three.tex}
+    \caption{TF3: an 8 state finite state machine.}
+    \label{fig:tf3}
+\end{figure}
+
 As opposed to the previously described strategies, these strategies were trained
@@
 \begin{itemize}
-	\item TF1 \(N=8\), 1\% noise, 100 repetitions per match
+	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per match
 	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per match
-	\item TF3 \(N=12\), 0\% noise, 10000 repetitions per match
+	\item TF3 \(N=8\), 1\% noise, 100 repetitions per match
 \end{itemize}
@@
 
-TF1 cooperates and defects with
-various cycles depending on the opponent's actions. TF1 will mutually
+TF3 cooperates and defects with
+various cycles depending on the opponent's actions. TF3 will mutually
 cooperate with any strategy and only tolerates a few defections before
@@
 
-TF3 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF3 will respond in kind, so the
+TF1 has an initial handshake of CCD and cooperates if the opponent matches.
+However if the opponent later defects, TF1 will respond in kind, so the
 handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
-achieve cooperation with TF3 after about 20 rounds of play.
+achieve cooperation with TF1 after about 20 rounds of play.
 
-For both TF2 and TF3 a handshake
+For both TF1 and TF2 a handshake
 mechanism naturally emerges from the structure of the underlying finite state
@@
 with unsampled calculations to a high degree of accuracy in specific cases.
-This is described in Figure~\ref{alg:psuedocode}.
-% TODO Include pseudo code
+This is described in Algorithms~\ref{alg:data_collection}
+and~\ref{alg:moran_process}..
+
+\begin{algorithm}[!hbtp]
+        \caption{Data Collection}
+        \label{alg:data_collection}
+        \input{./tex/data_collection.tex}
+\end{algorithm}
+
+\begin{algorithm}[!hbtp]
+        \caption{Moran process}
+        \label{alg:moran_process}
+        \input{./tex/moran_process_simulation.tex}
+\end{algorithm}
 
@@
         Defector \cite{Li2014}.
-    \item TF1, the finite state machine trained specifically for Moran processes
+    \item TF3, the finite state machine trained specifically for Moran processes
         described in Section~\ref{sec:introduction}.
@@
 source code of PSO Gambler shows that it makes stochastic decisions with extreme
-probabilities: almost always acting as expected. Apart from TF1 in \(N=3\), the
+probabilities: almost always acting as expected. Apart from TF3 in \(N=3\), the
 finite state machines trained specifically for Moran processes do not appear in
@@
 There are are only two new strategies that appear in the top ranks for
-\(x_{N-1}\): TF2 and TF3. These two strategies are with CS the strongest
+\(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
 resistors. They all have handshakes, and whilst the handshake that CS and
 Handshake (which ranks highly for the smaller values of \(N\)) have was
-programmed, the handshakes of TF2 and TF3 evolved through an evolutionary
+programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
 process.
@@
 some strategies additionally retaliate first round defections. So the
-handshakes used by TF2 and TF3, and CS, are in some sense optimal. These
+handshakes used by TF1 and TF2, and CS, are in some sense optimal. These
 discoveries may have significant ramifications regarding the evolution of
@@
 was not only identify for CS (an intelligently designed strategy) but also for
-two FSM strategies (TF2 and TF3) specifically trained through an evolutionary
+two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
 process. In these two cases, the handshake mechanism was a product of the

### 2017-05-13 src/abbreviations.py

@@ -18,9 +18,9 @@ abbreviations["Two Tits For Tat"] = "2TfT"
 abbreviations["Tit For 2 Tats"] = "Tf2T"
 abbreviations["Win-Stay Lose-Shift: C"] = "WStLSh"
 abbreviations["Win-Shift Lose-Stay: D"] = "WShLSt"
-abbreviations["FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C"] =  "TF1"
+abbreviations["FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C"] = "TF1"
[…]

### 2017-05-14 main.tex
Fix broken fig ref.

@@
     \input{./tex/fsm_one.tex}
-    \caption{TF1: a 16 state finite state machine.}
+    \caption{TF1: a 16 state finite state machine with a handshake leading to
+    mutual cooperation at state 4.}
     \label{fig:tf1}
@@
     \input{./tex/fsm_two.tex}
-    \caption{TF2: a 16 state finite state machine.}
+    \caption{TF2: a 16 state finite state machine with a handshake leading to
+    mutual cooperation at state 16.}
     \label{fig:tf2}
@@
 
-Figure~\ref{fig:correlation_coeficients} show the correlation coefficients
+Figure~\ref{fig:correlation_coefficients} show the correlation coefficients
 of the ranks of strategies in differing population size. It is immediate to

### 2017-05-15 main.tex
A variety of edits for the paper

@@
        for Iterated Prisoner's Dilemma Strategies}
+\title{Evolving Invaders and Resistors for the Iterated Prisoner's Dilemma}
 \author{Vincent Knight \and
@@
     sophisticated behaviours outperform many strategies that perform well
-    in a two player setting.
+    in a two player setting. Moreover we introduce several strategies
+    trained with evolutionary algorithms to excel at the Moran process.
+    These strategies are excellent invaders and resistors of invasion.
 \end{abstract}
@@
 play. Recently, some strategies referred to as Zero Determinant strategies
-\cite{Press2012} even manipulate players through extortion.
+\cite{Press2012} can manipulate some players through extortionate mechanisms.
 
@@
 and/or do not consider sophisticated behaviour: only considering strategies that
-either cooperate or defect.
+either cooperate or defect, or are limited to classes of strategies
+such as memory-one strategies that only use the previous round of play.
 
@@
 networks, and other machine learning based strategies, and a collection of novel
-strategies. Not all strategies have been considered for this study: same use
-knowledge of the game such as the number of turns and others have a high
+strategies. Not all strategies have been considered for this study: excluded
+are those that make use of knowledge of the game such as the number of turns
+and others that have a high
 computational run time. The large number of strategies are available thanks to
@@
 
-The library can conduct matches, tournaments and population
+In addition to providing a large collection of strategies, the Axelrod library
+can conduct matches, tournaments and population
 dynamics with variations including noise and spatial structure.
@@
  \item Complex strategies can be effective, and in fact can naturally evolve
-     through evolutionary processes to outperform intelligently designed
-     strategies.
- \item Strong resistors specifically evolve or have a handshake mechanism. This
-     has the potential to offer insight in to organisms such as antibacterial
-     resistant bacteria \cite{Davies2010}.
+     through evolutionary processes to outperform designed strategies.
+ \item Strong resistors specifically evolve or have a handshake mechanism.
 \end{enumerate}
+
+These finding have the potential to offer insight in to organisms such as antibacterial
+resistant bacteria \cite{Davies2010} and human social behaviors.
 
@@
 \textit{fixation probability}. A more detailed analytic description of this is
-given in Section~\ref{sec:validation}.
+given in Section~\ref{sec:validation}. In our simulations offspring do not
+inherit any knowledge or history from parent replicants.
 
@@
 A part from the PSO Gambler strategy, which was trained using a particle swarm
-optimisation algorithm, all these strategies are trained with an evolutionary
+optimisation algorithm, these strategies are trained with an evolutionary
 algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. Variation is
+against all other opponents \cite{affenzeller2009genetic}. They were not
+trained specifically for the Moran process or to cooperate well with themselves
+(though they all do). Variation is
 introduced via mutation and crossover of parameters, and the best performing
@@
 
-More
-information about each player can be obtained in the documentation for
+More information about each player can be obtained in the documentation for
 \cite{axelrodproject} and a detailed description of the performance
- of these strategies in IPD
-tournaments will be described in upcoming manuscript.
+ of these strategies in IPD tournaments will be described in upcoming manuscript(s).
 % TODO Think of how to reference this upcoming manuscript
@@
 % TODO Include link etc
-typically takes less than 200 iterations and can be completed within several
+typically takes less than 100 generations and can be completed within several
 hours on commodity hardware.
@@
 \begin{itemize}
-	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per match
-	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per match
-	\item TF3 \(N=8\), 1\% noise, 100 repetitions per match
+	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per matchup
+	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per matchup
+	\item TF3 \(N=8\), 1\% noise, 100 repetitions per matchup
 \end{itemize}
@@
 (not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective. Interestingly it has no handshake
-mechanism, this could be due to the fact that it is trained in a noisy
-environment.
+product of training with a Moran objective. It differs from TF1 and TF2 
+by lacking a handshake mechanism.
 
@@
 handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
-achieve cooperation with TF1 after about 20 rounds of play.
+achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
+very similar to a strategy known as ``Collective Strategy'', which has a
+handshake of CD and cooperates with opponents that matched the handshake
+until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
+This strategy was specifically designed for evolutionary processes.
 
@@
 of the strategies have a high computational cost or are stochastic, samples are
-taken
-from a large number of match outcomes for the pairs of players for use in
+taken from a large number of match outcomes for the pairs of players for use in
 computing fitnesses in the Moran process. This approach was verified to agree
@@
 This is described in Algorithms~\ref{alg:data_collection}
-and~\ref{alg:moran_process}..
+and~\ref{alg:moran_process}.
 
@@
 \begin{equation}\label{equ:expected_payoff_one}
-    F_i = \frac{a(i - 1) + b(N - i)}{N - 1}
+    f_i = \frac{a(i - 1) + b(N - i)}{N - 1}
 \end{equation}
@@
 \begin{equation}\label{equ:expected_payoff_two}
-    G_i = \frac{ci + d(N - i - 1)}{N - 1}
+    g_i = \frac{ci + d(N - i - 1)}{N - 1}
 \end{equation}
 
-With an intensity of selection \(\omega\) the fitness of both strategies is
-given by:
-
-\begin{equation}\label{equ:expected_payoff_one}
-    f_i = 1 - \omega + \omega F_i
-\end{equation}
-
-\begin{equation}\label{equ:expected_payoff_two}
-    g_i = 1 - \omega + \omega G_i
-\end{equation}
+% With an intensity of selection \(\omega\) the fitness of both strategies is
+% given by:
+% 
+% \begin{equation}\label{equ:expected_payoff_one}
+%     f_i = 1 - \omega + \omega F_i
+% \end{equation}
+% 
+% \begin{equation}\label{equ:expected_payoff_two}
+%     g_i = 1 - \omega + \omega G_i
+% \end{equation}
 
@@
 of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategies pairs.
+strategies pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
+stochastic strategies. These are no longer a good match which highlights the
+weakness of the analytical formulae that relies on the average payoffs
+(\ref{equ:payoff_matrix}). Estimating all the transitions may give better agreement
+but is not necessary for our purposes. All data generated for this validation exercise can be found
+at \cite{data}.
 
@@
 \end{figure}
-
-Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies. These are no longer a good match which highlights the
-weakness of the analytical formulae that relies on the average payoffs
-(\ref{equ:payoff_matrix}).
-
-All data generated for this validation exercise can be found
-at \cite{data}.
-
-A detailed analysis of the 164 strategies considered,
-using direct Moran processes will be shown in the next Section.
 
@@
 
-When $N=2$ the Moran process is effectively a measure of the relative
+When $N=2$ the Moran process is effectively a measure of the distribution of relative
 mean payoffs over all possible matches between two players. The strategy
@@
     \item The top strategy is the Collective Strategy (CS) which has a simple
-        handshake mechanism (a cooperation followed by a defection on the first
-        move). As long as the opponent plays the same handshake and does not
-        defect in the future it cooperates. Otherwise it defects for all
-        rounds. This strategy was specifically designed for
-        evolutionary processes \cite{Li2009}.
+        handshake mechanism described above.
     \item The Defector: it always defects. As it has little potential
@@
     \input{./tex/summary_top_2_invade.tex}
-    \caption{Summary of top five strategies for \(N=2\)}
+    \caption{Summary of top five strategies for \(N=2\) (neutral fixation is $p=0.5$.}
     \label{tbl:summary_top_2}
@@
 assumptions about the structure of the strategies by using actual simulation
-interactions.
-
-In the next sections close attention to
-strategies who are strong invaders/resistors is given.
+interactions. \cite{Stewart...}
+
+% In the next sections close attention to
+% strategies who are strong invaders/resistors is given.
 
@@
 In this section the focus is on the ability of a mutant strategy to invade: the
-probability of 1 individual of a given type successfully becoming fixated in a
+probability of one individual of a given type successfully fixating in a
 population of \(N - 1\) other individuals, denoted by \(x_1\). The fixation
@@
 memory one strategies. Only one is stochastic although close inspection of the
-source code of PSO Gambler shows that it makes stochastic decisions with extreme
-probabilities: almost always acting as expected. Apart from TF3 in \(N=3\), the
-finite state machines trained specifically for Moran processes do not appear in
-the top 5: whereas strategies trained for tournament do. This is due to the
-nature of invasion: most of the opponents will initially be different
+source code of PSO Gambler shows that it makes stochastic decisions rarely, and
+is functionally very similar to its deterministic cousing EvolvedLookerUp. Apart
+from TF3 in \(N=3\), the finite state machines trained specifically for Moran
+processes do not appear in the top 5: whereas strategies trained for tournament do.
+This is due to the nature of invasion: most of the opponents will initially be different
 strategies. The next section will consider the converse situation.
@@
 
-The fixation
-probabilities are shown in
+The fixation probabilities are shown in
 Figures~\ref{fig:boxplot_3_resist},~\ref{fig:boxplot_7_invade}
@@
 the need of strategies to have a steady hand when interacting with their own
-kind. In essence: acting stochastically increase the chance of friendly fire.
-However it is possible to design a strategy with a ``stochastic
-handshake'' \cite{Lee2015}.
+kind. In essence: acting stochastically increases the chance of friendly fire.
+However it is possible to design a strategy with a stochastic or error-correcting
+handshake that is an excellent resistor even in noisy environments \cite{Lee2015}.
 
@@
 \(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
-resistors. They all have handshakes, and whilst the handshake that CS and
-Handshake (which ranks highly for the smaller values of \(N\)) have was
+resistors. They all have handshakes, and whilst the handshakes of CS and
+Handshake (which ranks highly for the smaller values of \(N\)) were
 programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
-process.
+process without any priming.
 
@@
 The payoff maximizing strategies typically will not defect before the opponent's
-first defection, possibly because the training strategy collection contains a
-significant portion of strategies such as Grudger and Fool Me Once that
-retaliate harshly by defecting for the remainder of the match if the opponent
-has more than a small number of cumulative defections. Paradoxically it is
-necessary to defect (as a signal) in order to achieve mutual cooperation with
-opponents using the same strategy but not with other opponents.
+first defection, possibly because the training strategy collection contains some
+strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
+for the remainder of the match if the opponent has more than a small number of
+cumulative defections. Paradoxically it is advantageous to defect (as a signal)
+in order to achieve mutual cooperation with opponents using the same strategy
+but not with other opponents. Nevertheless an evolutionary process is able to
+tunnel through the costs and risks associated to early defections to find more
+optimal solutions, so it is not surprising in hindsight that handshaking
+strategies emerge from the evolutionary training process.
 
@@
 some strategies additionally retaliate first round defections. So the
-handshakes used by TF1 and TF2, and CS, are in some sense optimal. These
+handshakes used by TF1, TF2, and CS are in some sense optimal. These
 discoveries may have significant ramifications regarding the evolution of
 cooperation and forgiveness in biological organisms such as antibacterial
-resistant bacteria and social interactions
-between humans.
+resistant bacteria and social interactions between humans.
 
@@
 
-This is confirmed by the performance of the Zero determinant strategies, whilst
-some do rank relatively highly for \(N=2\) (ZD-extort-4 has tank 16) this rank
+This is confirmed by the performance of the zero determinant strategies. While
+some do rank relatively highly for \(N=2\) (ZD-extort-4 has rank 16) this rank
 does not translate to larger populations.
@@
 
+\section{Discussion}
+
+Training strategies to excel
+at the Moran process led to the evolution of cooperation, but only with like
+individuals in the case of TF1 and TF2. This may have significant implications
+for human social interactions such as the evolution of ingroup/outgroup mechanisms
+and other sometimes costly rituals that reinforce group behavior.
+
+While TF1 and TF2 are competent invaders, the best invaders
+in the study do not appear to employ strict handshakes, and are generally
+cooperative strategies. TF3, which does not use a handshake, is a better invader
+than TF1 and TF2 but not as good of a resistor. Nevertheless it was the result
+of the same kind of training procceses and is a better combined invader-resistor
+than the invaders that were trained previously to maximize payout.
+
+The strategies trained to maximize payoff in head-to-head matches are generally
+cooperative and are effective invaders.
+Combined with the fact that handshaking strategies are stronger resisters,
+this suggests that while maximizing individual payoff can lead to the evolution
+of cooperation (through fixation), it is not necessarily evolutionarily stable
+in the long run. A strategy with a handshaking mechanism is still capable of
+invading and is more resistant to subsequent invasions. Moreover, the
+best resistor of the payoff maximally trained strategies is EvolvedLookerUp1_1_1,
+which always defects if the opponent defects in the first round, is effectively
+employing a one-shot handshake of C. These insights also suggest that a strategy
+aware of the population distribution could choose to become a handshaker at
+a critical threshold and use a different strategy for invasion when in the
+minority. However this information was not available to our strategies.
+
+We did not attempt other objective functions that may serve to select for both
+invasion and resistance better than training at a starting population of
+$(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
+improvement. Any handshake more sophisticated than C necessarily involves
+a defection. (A handshake consisting of a longer sequence of cooperations is
+effectively a grudger.) For TF3 or EvolvedLookerUp1_1_1 to become better resistors
+they need a longer, more strict handshake. But if this handshake involves
+a defection then likely the invasion ability is diminished for $N > 2$: the top
+invaders for larger $N$ are nice strategies that do not defect before their
+opponents. This is because good invaders still need to cooperate with themselves,
+and so in the absense of a handshake mechanism or knowledge of the population
+distribution, a strategy must be generally cooperative. Aggressive strategies
+are only effective invaders for the smallest $N$, dropping down dramatically
+as the population size increases.
+
+We did, however, attempt to evolve CS using FSM and lookup table based players,
+which resulted in some very similar strategies. In particular we evolved a
+lookup strategy that had a handshake of DC and played TFT with other players
+after a correct handshake and defecting otherwise, which is quite close in
+function to CS (full grudging is not possible with a lookup table).
+
+Finally we note that it may be possible to achieve similar results with smaller
+capacity finite state machine players.
+
 \section{Conclusion}\label{sec:conclusion}
@@
 
-When studying evolutionary processes it is vital to consider \(N>2\) as the
-special case for \(N=2\) cannot be used to extrapolate performance in bigger
+When studying evolutionary processes it is vital to consider \(N>2\) since
+results for \(N=2\) cannot be used to extrapolate performance in larger
 populations. This was shown both observationally in
@@
 
-Memory one strategies do not perform well, as predicted by \cite{Press2012}.
-There are no memory one strategies in the top 5 performing strategies
-for \(N>3\). This is due to their lack of sophistication which allows them to
-recognise and adjust to their opponent. Some very sophisticated strategies
-proves to be high performers for invasion: these are infinite memory strategies
+Memory one strategies do not perform well in general in this study. There are
+no memory one strategies in the top 5 performing strategies
+for \(N>3\). This is due at least partly to their lack of ability to
+recognise their opponents. More sophisticated strategies
+prove to be high performers for invasion: these are infinite memory strategies
 which have been trained using a number of reinforcement learning algorithms.
@@
 the ability of strategies with a handshake mechanism to resist invasion. This
-was not only identify for CS (an intelligently designed strategy) but also for
+was not only revealed for CS (a human designed strategy) but also for
 two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
@@
 
-It is felt that these findings are important for the ongoing understanding of
-population dynamics and offer evidence for some of the shortcomings of short
+These findings are important for the ongoing understanding of
+population dynamics and offer evidence for some of the shortcomings of low
 memory which has started to be recognised by the community \cite{Hilbe2017}.
@@
 
-There are various areas for further work to build on this. Firstly, an analysis
-of the effect of noise would offer insights about the stability of the findings.
-It would also be possible to consider three or more types of strategy in the
-population and finally mutation would also offer an interesting dimension to
-explore.
+% There are various areas for further work to build on this. Firstly, an analysis
+% of the effect of noise would offer insights about the stability of the findings.
+% It would also be possible to consider three or more types of strategy in the
+% population and finally mutation would also offer an interesting dimension to
+% explore.
 

### 2017-05-15 main.tex
Minor edits

@@
 Training strategies to excel
-at the Moran process led to the evolution of cooperation, but only with like
+at the Moran process leads to the evolution of cooperation, but only with like
 individuals in the case of TF1 and TF2. This may have significant implications
@@
 this suggests that while maximizing individual payoff can lead to the evolution
-of cooperation (through fixation), it is not necessarily evolutionarily stable
+of cooperation, these strategies are not the most evolutionarily stable
 in the long run. A strategy with a handshaking mechanism is still capable of
 invading and is more resistant to subsequent invasions. Moreover, the
-best resistor of the payoff maximally trained strategies is EvolvedLookerUp1_1_1,
+best resistor of the payoff maximally trained strategies (EvolvedLookerUp1_1_1),
 which always defects if the opponent defects in the first round, is effectively
@@
 effectively a grudger.) For TF3 or EvolvedLookerUp1_1_1 to become better resistors
-they need a longer, more strict handshake. But if this handshake involves
+they need a longer or more strict handshake. But if this handshake involves
 a defection then likely the invasion ability is diminished for $N > 2$: the top
@@
 lookup strategy that had a handshake of DC and played TFT with other players
-after a correct handshake and defecting otherwise, which is quite close in
+after a correct handshake while defecting otherwise, which is quite close in
 function to CS (full grudging is not possible with a lookup table).

### 2017-05-15 main.tex
Improve plots Addresses #34.
- Change color for neutral fixation in boxplots. Gone from blue to black.
- Remove grid lines in the rank plots. Still have the grey background
  but we can change that.
- Move the invasion and resistance rank plots to the corresponding
  sections.

@@
 probability of one individual of a given type successfully fixating in a
-population of \(N - 1\) other individuals, denoted by \(x_1\). The fixation
+population of \(N - 1\) other individuals, denoted by \(x_1\).
+The ranks of each strategy for all considered values of \(N\) according to mean
+\(x_1\) are shown in Figures~\ref{fig_ranks_v_size_invade}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
+    \caption{Ranks of all strategies according to \(x_1\) for different
+    population sizes}
+    \label{fig:ranks_v_size_invade}
+\end{figure}
+
+The fixation
 probabilities are shown in
@@
 other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy. Note that this is equivalent to looking at $x_1$ for all
-opponents.
+each strategy. The ranks of each strategy for all considered values of \(N\)
+according to mean \(x_{N-1}\) are shown in
+Figures~\ref{fig_ranks_v_size_resist}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
+    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
+    population sizes}
+    \label{fig:ranks_v_size_resist}
+\end{figure}
 
@@
 
-Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
-and~\ref{fig:ranks_v_size_coexist} show the rank of each strategy based on mean
-fixation probabilities against population size.
+To complement Figures~\ref{fig:ranks_v_size_invade}
+and~\ref{fig:ranks_v_size_resist} Figure~\ref{fig:ranks_v_size_coexist} shows
+the rank of each strategy based on \(x_{N/2}\).
 Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
@@
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
-    \caption{Ranks of all strategies according to \(x_1\) for different
-    population sizes}
-    \label{fig:ranks_v_size_invade}
-\end{figure}
-
 \begin{table}[!hbtp]
@@
 \end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
-    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
 

### 2017-05-15 main.tex
Improve tables Addresses #35
- Rewrite appendix with player information.
- Simplify the tables of top performing strategies.
- Present top 10% of strategies as opposed to top 5.
- Make TF* appear in bold.
- Include lines to separate strategies in rank tables and also display ints

@@
 To carry out this large numerical experiment, \input{./tex/num_strategies}
-strategies, listed in Appendix~\ref{app:list_of_players} are used library. There
-are \input{./tex/num_stochastic.tex}stochastic and
+strategies, listed (with their properties) in Appendix~\ref{app:list_of_players}
+are used library. There are \input{./tex/num_stochastic.tex}stochastic and
 \input{./tex/num_deterministic.tex}deterministic strategies. Their memory depth,
@@
 For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in sections~\ref{sec:strong_invaders} and
-~\ref{sec:strong_resistors}.  Figure~\ref{fig:boxplot_2} shows all fixation
+considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
+and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
 probabilities for the strategies considered. This is summarised in
@@
 \begin{table}[!hbtp]
+    \scriptsize
     \centering
     \input{./tex/summary_top_2_invade.tex}
-    \caption{Summary of top five strategies for \(N=2\) (neutral fixation is $p=0.5$.}
+    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\).}
     \label{tbl:summary_top_2}
@@
 \begin{figure}[!hbtp]
+    \scriptsize
     \centering
@@
 
-The top five strategies are given in Tables~\ref{tbl:top_five_invade}.
+The top strategies are given in Tables~\ref{tbl:top_five_invade}.
 
 \begin{table}[!hbtp]
-    \begin{subfigure}[t]{\textwidth}
+    \centering
+    \scriptsize
+    \begin{subfigure}[t]{.5\textwidth}
         \centering
@@
         \caption{\(N=3\)}
-    \end{subfigure}
-    \begin{subfigure}[t]{\textwidth}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.5\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}[t]{\textwidth}
+
+    \begin{subfigure}[t]{.3\textwidth}
         \centering
@@
     \end{subfigure}
-    \caption{Properties of top five invaders}
+    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
     \label{tbl:top_five_invade}
@@
 source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousing EvolvedLookerUp. Apart
+is functionally very similar to its deterministic cousin EvolvedLookerUp. Apart
 from TF3 in \(N=3\), the finite state machines trained specifically for Moran
-processes do not appear in the top 5: whereas strategies trained for tournament do.
+processes do not appear in the top 5: whereas strategies trained for tournaments do.
 This is due to the nature of invasion: most of the opponents will initially be different
@@
 
-Table~\ref{tbl:top_five_resist} shows the top five strategies when ranked
+Table~\ref{tbl:top_five_resist} shows the top strategies when ranked
 according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
@@
 \begin{table}[!hbtp]
-    \begin{subfigure}[t]{\textwidth}
+    \scriptsize
+    \centering
+    \begin{subfigure}[t]{.5\textwidth}
         \centering
@@
     \end{subfigure}
-    \caption{Properties of top five resistors}
+    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
     \label{tbl:top_five_resist}
@@
 % TODO Add reference to source code
-the processed data has also been properly archived and can be fond
+the processed data has also been properly archived and can be found
 at \cite{data}.
@@
 
-\begin{multicols}{3}
+\begin{multicols}{2}
 	\begin{enumerate}

### 2017-05-15 main.tex
Make minor adjustments.

@@
 source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin EvolvedLookerUp. Apart
+is functionally very similar to its deterministic cousin Evolved Looker Up. Apart
 from TF3 in \(N=3\), the finite state machines trained specifically for Moran
@@
 invading and is more resistant to subsequent invasions. Moreover, the
-best resistor of the payoff maximally trained strategies (EvolvedLookerUp1_1_1),
+best resistor of the payoff maximally trained strategies (Evolved Looker Up
+1\_1\_1),
 which always defects if the opponent defects in the first round, is effectively
@@
 a defection. (A handshake consisting of a longer sequence of cooperations is
-effectively a grudger.) For TF3 or EvolvedLookerUp1_1_1 to become better resistors
+effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
 they need a longer or more strict handshake. But if this handshake involves

### 2017-05-15 tex/list_of_players.tex
Minor adjustments and run with new data.
Rerun with data for N=11, i=1
Further fix to abbreviations.
Change plots for validation.
Not sure if I'm a fan.

Also, add some abbreviations.
Adjust nb and rerun images.
Rerun with final data.
Adjust tex file to match new results.
Add fsm imgs, algs and fix naming confusion.
I had mixed up TF1 and TF3. This is now fixed throughout.

@@
-\item Random Hunter
-\item Cooperator
-\item Adaptive
-\item Random: 0.5
-\item Contrite Tit For Tat
-\item Cycle Hunter
-\item Adaptive Tit For Tat: 0.5
-\item Cooperator Hunter
-\item Stochastic Cooperator
-\item Remorseful Prober: 0.1
-\item Cycler CCCCCD
-\item Tricky Cooperator
-\item Win-Shift Lose-Stay: D
-\item Aggravater
-\item Tricky Defector
-\item $\pi$
-\item Resurrection
-\item Stochastic WSLS: 0.05
-\item Win-Stay Lose-Shift: C
-\item ALLCorALLD
-\item Tullock: 11
-\item Alternator
-\item Retaliate: 0.1
-\item Cycler CCCD
-\item Worse and Worse
-\item Alternator Hunter
-\item Retaliate 2: 0.08
-\item Worse and Worse 2
-\item AntiCycler
-\item Winner21
-\item Cycler CCD
-\item Suspicious Tit For Tat
-\item Retaliate 3: 0.05
-\item Willing
-\item Worse and Worse 3
-\item Anti Tit For Tat
-\item Adaptive Pavlov 2006
-\item Revised Downing: True
-\item Cycler DC
-\item ZD-Extort-2: 0.1111111111111111, 0.5
-\item Adaptive Pavlov 2011
-\item ZD-Extort-2 v2: 0.125, 0.5, 1
-\item Ripoff
-\item VeryBad
-\item Cycler DDC
-\item Appeaser
-\item Cycler CCCDCD
-\item Winner12
-\item SelfSteem
-\item Risky QLearner
-\item ZD-Extort-4: 0.23529411764705882, 0.25, 1
-\item Arrogant QLearner
-\item Thumper
-\item ZD-GEN-2: 0.125, 0.5, 3
-\item Defector
-\item ZD-GTFT-2: 0.25, 0.5
-\item Average Copier
-\item Davis: 10
-\item ShortMem
-\item Meta Hunter: 6 players
-\item ThueMorseInverse
-\item Tester
-\item Better and Better
-\item Spiteful Tit For Tat
-\item Shubik
-\item Defector Hunter
-\item ThueMorse
-\item ZD-SET-2: 0.25, 0.0, 2
-\item $e$
-\item Slow Tit For Two Tats
-\item Desperate
-\item Bully
-\item SolutionB1
-\item Meta Hunter Aggressive: 7 players
-\item Calculator
-\item Slow Tit For Two Tats 2
-\item Tit For Tat
-\item Tit For 2 Tats
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 1, C
-\item Doubler
-\item Sneaky Tit For Tat
-\item SolutionB5
-\item Soft Grudger
-\item EasyGo
-\item CollectiveStrategy
-\item Soft Joss: 0.9
-\item Eatherley
-\item Cautious QLearner
-\item Two Tits For Tat
-\item Firm But Fair
-\item Hard Go By Majority
-\item Handshake
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 1, C
-\item Fool Me Once
-\item Prober 3
-\item Eventual Cycle Hunter
-\item Forgetful Grudger
-\item Prober 4
-\item Evolved ANN
-\item Forgetful Fool Me Once: 0.05
-\item Fool Me Forever
-\item Hard Go By Majority: 10
-\item Pun1
-\item Evolved ANN 5
-\item Fortress4
-\item Hard Go By Majority: 20
-\item Evolved ANN 5 Noise 05
-\item PSO Gambler 2\_2\_2
-\item Fortress3
-\item Hard Go By Majority: 40
-\item PSO Gambler 1\_1\_1
-\item Evolved FSM 4
-\item Forgiving Tit For Tat
-\item Naive Prober: 0.1
-\item GTFT: 0.33
-\item Soft Go By Majority
-\item Hard Go By Majority: 5
-\item Nice Average Copier
-\item Hard Prober
-\item Forgiver
-\item Opposite Grudger
-\item General Soft Grudger: n=1,d=4,c=2
-\item Evolved FSM 16
-\item Hard Tit For 2 Tats
-\item Soft Go By Majority: 10
-\item Once Bitten
-\item Hard Tit For Tat
-\item EvolvedLookerUp2\_2\_2
-\item Nydegger
-\item Prober 2
-\item Soft Go By Majority: 20
-\item Hesitant QLearner
-\item Evolved FSM 16 Noise 05
-\item PSO Gambler 2\_2\_2 Noise 05
-\item Omega TFT: 3, 8
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 1, C
-\item EvolvedLookerUp1\_1\_1
-\item Soft Go By Majority: 40
-\item Inverse
-\item Hopeless
-\item MEM2
-\item Soft Go By Majority: 5
-\item Inverse Punisher
-\item Predator
-\item Joss: 0.9
 \item $\phi$
-\item Gradual
-\item Level Punisher
-\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C')
-\item Limited Retaliate: 0.1, 20
-\item Grofman
-\item Limited Retaliate 2: 0.08, 15
-\item PSO Gambler Mem1
-\item Negation
-\item Punisher
-\item Grudger
-\item Prober
-\item GrudgerAlternator
-\item Limited Retaliate 3: 0.05, 20
-\item Raider
-\item Evolved HMM 5
-\item Math Constant Hunter
-\item Feld: 1.0, 0.5, 200
-\item Grumpy: Nice, 10, -10
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item $\pi$
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item $e$
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item ALLCorALLD
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Adaptive
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Adaptive Pavlov 2006
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Adaptive Pavlov 2011
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Adaptive Tit For Tat: 0.5
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Aggravater
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Alternator
+ - \textit{Deterministic} - \textit{Memory depth}: 1\item Alternator Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Anti Tit For Tat
+ - \textit{Deterministic} - \textit{Memory depth}: 1\item AntiCycler
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Appeaser
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Arrogant QLearner
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Average Copier
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Better and Better
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Bully
+ - \textit{Deterministic} - \textit{Memory depth}: 1\item Calculator
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Cautious QLearner
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item CollectiveStrategy
+(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Contrite Tit For Tat
+(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3\item Cooperator
+ - \textit{Deterministic} - \textit{Memory depth}: 0\item Cooperator Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Cycle Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Cycler CCCCCD
+ - \textit{Deterministic} - \textit{Memory depth}: 5\item Cycler CCCD
+ - \textit{Deterministic} - \textit{Memory depth}: 3\item Cycler CCCDCD
+ - \textit{Deterministic} - \textit{Memory depth}: 5\item Cycler CCD
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Cycler DC
+ - \textit{Deterministic} - \textit{Memory depth}: 1\item Cycler DDC
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Davis: 10
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Defector
+ - \textit{Deterministic} - \textit{Memory depth}: 0\item Defector Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Desperate
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Doubler
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item EasyGo
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Eatherley
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Eventual Cycle Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Evolved ANN
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Evolved ANN 5
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Evolved ANN 5 Noise 05
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Evolved FSM 16
+ - \textit{Deterministic} - \textit{Memory depth}: 16\item Evolved FSM 16 Noise 05
+ - \textit{Deterministic} - \textit{Memory depth}: 16\item Evolved FSM 4
+ - \textit{Deterministic} - \textit{Memory depth}: 4\item Evolved HMM 5
+ - \textit{Stochastic} - \textit{Memory depth}: 5\item EvolvedLookerUp1\_1\_1
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item EvolvedLookerUp2\_2\_2
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C
+(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: 16\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C
+(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C
+(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Feld: 1.0, 0.5, 200
+ - \textit{Stochastic} - \textit{Memory depth}: 200\item Firm But Fair
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Fool Me Forever
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Fool Me Once
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Forgetful Fool Me Once: 0.05
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Forgetful Grudger
+ - \textit{Deterministic} - \textit{Memory depth}: 10\item Forgiver
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Forgiving Tit For Tat
+(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Fortress3
+ - \textit{Deterministic} - \textit{Memory depth}: 3\item Fortress4
+ - \textit{Deterministic} - \textit{Memory depth}: 4\item GTFT: 0.33
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item General Soft Grudger: n=1,d=4,c=2
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Gradual
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C')
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Grofman
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Grudger
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item GrudgerAlternator
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Grumpy: Nice, 10, -10
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Handshake
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Hard Go By Majority
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Hard Go By Majority: 10
+ - \textit{Deterministic} - \textit{Memory depth}: 10\item Hard Go By Majority: 20
+ - \textit{Deterministic} - \textit{Memory depth}: 20\item Hard Go By Majority: 40
+ - \textit{Deterministic} - \textit{Memory depth}: 40\item Hard Go By Majority: 5
+ - \textit{Deterministic} - \textit{Memory depth}: 5\item Hard Prober
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Hard Tit For 2 Tats
+(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3\item Hard Tit For Tat
+(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3\item Hesitant QLearner
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Hopeless
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Inverse
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Inverse Punisher
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Joss: 0.9
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Level Punisher
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Limited Retaliate 2: 0.08, 15
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Limited Retaliate 3: 0.05, 20
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Limited Retaliate: 0.1, 20
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item MEM2
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Math Constant Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Meta Hunter Aggressive: 7 players
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Meta Hunter: 6 players
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Naive Prober: 0.1
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Negation
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Nice Average Copier
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Nydegger
+ - \textit{Deterministic} - \textit{Memory depth}: 3\item Omega TFT: 3, 8
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Once Bitten
+ - \textit{Deterministic} - \textit{Memory depth}: 12\item Opposite Grudger
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item PSO Gambler 1\_1\_1
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item PSO Gambler 2\_2\_2
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item PSO Gambler 2\_2\_2 Noise 05
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item PSO Gambler Mem1
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Predator
+ - \textit{Deterministic} - \textit{Memory depth}: 9\item Prober
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Prober 2
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Prober 3
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Prober 4
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Pun1
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Punisher
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Raider
+ - \textit{Deterministic} - \textit{Memory depth}: 3\item Random Hunter
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Random: 0.5
+ - \textit{Stochastic} - \textit{Memory depth}: 0\item Remorseful Prober: 0.1
+ - \textit{Stochastic} - \textit{Memory depth}: 2\item Resurrection
+ - \textit{Deterministic} - \textit{Memory depth}: 1\item Retaliate 2: 0.08
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Retaliate 3: 0.05
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Retaliate: 0.1
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Revised Downing: True
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Ripoff
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Risky QLearner
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item SelfSteem
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item ShortMem
+ - \textit{Deterministic} - \textit{Memory depth}: 10\item Shubik
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Slow Tit For Two Tats
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Slow Tit For Two Tats 2
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Sneaky Tit For Tat
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Soft Go By Majority
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Soft Go By Majority: 10
+ - \textit{Deterministic} - \textit{Memory depth}: 10\item Soft Go By Majority: 20
+ - \textit{Deterministic} - \textit{Memory depth}: 20\item Soft Go By Majority: 40
+ - \textit{Deterministic} - \textit{Memory depth}: 40\item Soft Go By Majority: 5
+ - \textit{Deterministic} - \textit{Memory depth}: 5\item Soft Grudger
+ - \textit{Deterministic} - \textit{Memory depth}: 6\item Soft Joss: 0.9
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item SolutionB1
+ - \textit{Deterministic} - \textit{Memory depth}: 3\item SolutionB5
+ - \textit{Deterministic} - \textit{Memory depth}: 5\item Spiteful Tit For Tat
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Stochastic Cooperator
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Stochastic WSLS: 0.05
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Suspicious Tit For Tat
+ - \textit{Deterministic} - \textit{Memory depth}: 1\item Tester
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item ThueMorse
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item ThueMorseInverse
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Thumper
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Tit For 2 Tats
+(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2\item Tit For Tat
+(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1\item Tricky Cooperator
+ - \textit{Deterministic} - \textit{Memory depth}: 10\item Tricky Defector
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Tullock: 11
+ - \textit{Stochastic} - \textit{Memory depth}: 11\item Two Tits For Tat
+(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2\item VeryBad
+ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item Willing
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item Win-Shift Lose-Stay: D
+(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1\item Win-Stay Lose-Shift: C
+(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1\item Winner12
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Winner21
+ - \textit{Deterministic} - \textit{Memory depth}: 2\item Worse and Worse
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Worse and Worse 2
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item Worse and Worse 3
+ - \textit{Stochastic} - \textit{Memory depth}: \(\infty\)\item ZD-Extort-2 v2: 0.125, 0.5, 1
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item ZD-Extort-2: 0.1111111111111111, 0.5
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item ZD-Extort-4: 0.23529411764705882, 0.25, 1
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item ZD-GEN-2: 0.125, 0.5, 3
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item ZD-GTFT-2: 0.25, 0.5
+ - \textit{Stochastic} - \textit{Memory depth}: 1\item ZD-SET-2: 0.25, 0.0, 2
+ - \textit{Stochastic} - \textit{Memory depth}: 1

### 2017-05-16 main.tex
Rerun all graphics.
Add explanation about validation for stochastic.
Discussed on #33

@@
 \begin{abstract}
-    The Iterated Prisoner's Dilemma is a well established framework for
-    the study of emergent behaviour. In this paper an extensive numerical
-    study of the evolutionary dynamics of this framework are presented. Fixation
-    probabilities for Moran processes are obtained for 164
-    different strategies. It is found that players with long memories and
-    sophisticated behaviours outperform many strategies that perform well
-    in a two player setting. Moreover we introduce several strategies
-    trained with evolutionary algorithms to excel at the Moran process.
-    These strategies are excellent invaders and resistors of invasion.
+    We present insights and empirical results from an extensive numerical
+    study of the evolutionary dynamics of the iterated prisoner's dilemma.
+    Fixation probabilities for Moran processes are obtained
+    for all pairs of 164 different strategies including classics such as TitForTat, zero
+    determinant strategies, and many more sophisticated strategies.
+    Players with long memories and sophisticated behaviours outperform
+    many strategies that perform well in a two player setting. Moreover we
+    introduce several strategies trained with evolutionary algorithms to
+    excel at the Moran process. These strategies are excellent invaders
+    and resistors of invasion and in some cases naturally evolve handshaking
+    mechanisms to resist invasion. The best invaders were those trained
+    to maximize total payoff while the best resistors invoke handshake machanisms.
+    This suggests that while maximizing individual payoff
+    can lead to the evolution of cooperation through invasion, the relatively
+    weak invasion resistance of payoff maximizing strategies are not as
+    evolutionarily stable as strategies employing handshake mechanisms.
 \end{abstract}
@@
 number of strategies have been developed to take advantage of the history of
-play. Recently, some strategies referred to as Zero Determinant strategies
+play. Recently, some strategies referred to as zero Determinant strategies
 \cite{Press2012} can manipulate some players through extortionate mechanisms.
@@
 works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak, Stewart2012}, however these often make simplifying assumptions
+\cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
 and/or do not consider sophisticated behaviour: only considering strategies that
@@
 
-This manuscript provides a detailed numerical analysis of
-\textbf{\input{./tex/num_strategies.tex}}complex and adaptive strategies for the
+This manuscript provides a detailed numerical analysis of agent-based simulations
+of \textbf{\input{./tex/num_strategies.tex}}complex and adaptive strategies for the
 IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
@@
 strategies including classics like TitForTat and WinStayLoseShift, as well as
-recent variants such as OmegaTFT, Zero determinant and other memory one
+recent variants such as OmegaTFT, zero determinant and other memory one
 strategies, strategies based on finite state machines, lookup tables, neural
@@
 computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 40 contributions made by
-different programmers and researchers \cite{Knight2016}. Three of the considered
+the open source nature of the project with over 40 contributors from around the
+world, made by programmers and researchers \cite{Knight2016}. Three of the considered
 strategies are finite state machines trained specifically for Moran processes
@@
 
-Fixation probabilities for all pairs of
-strategies are presented, identifying those that are effective invaders and
-those resistant to invasion, for population sizes $N=2$ to $N=14$.
+Using the Axelrod library and the many strategies it contains, we obtain
+fixation probabilities for all pairs of strategies, identifying
+those that are effective invaders and those resistant to invasion, for
+population sizes $N=2$ to $N=14$. Moreover we present a number of strategies
+that were created via reinforcement algorithms (evolutionary and particle
+swarm algorithms) that are among the best invaders and resistors of invasion
+known to date, and show that handshaking mechanims naturally arise from these
+processes as an invasion-resistance mechanism.
+
+Recent work has argued that agent-based
+simulations can provide insights in evolutionary game theory not available
+via direct mathematical analysis \cite{adami2016evolutionary}. The results
+and insighed contained in this paper would be difficult to derive analytically.
 
@@
  \item Strong resistors specifically evolve or have a handshake mechanism.
+ \item Strong invaders are generally cooperative strategies that do not defect
+ first but retaliate to varying degrees of intensity against strategies that defect.
+ \item Strategies evolved to maximize their total payout can be strong invaders
+ and achieve mutual cooperation with many other strategies.
 \end{enumerate}
@@
 state where the population is entirely made up of players of one strategy. The
-probability with which a given strategy is the survivor is called the
+probability with which a given strategy takes over a the population is called the
 \textit{fixation probability}. A more detailed analytic description of this is
@@
 Of particular interest are the Zero determinant strategies introduced in
-\cite{Press2012} and praised in \cite{Stewart2012} it was argued that generous
+\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
 ZD strategies are robust against invading strategies. However, in \cite{Lee2015}
@@
 has investigated the effect of memory length on strategy performance and the
-emergence of cooperation but this is not done in Moran process context and only
+emergence of cooperation but this is not done in a Moran process context and only
 considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
-recognised that many Zero determinant strategies do not fare well against
+recognised that many zero determinant strategies do not fare well against
 themselves. This is a disadvantage for the Moran process where the best
@@
 strategies, listed (with their properties) in Appendix~\ref{app:list_of_players}
-are used library. There are \input{./tex/num_stochastic.tex}stochastic and
+are used from the Axelrod library. There are 
+\input{./tex/num_stochastic.tex}stochastic and
 \input{./tex/num_deterministic.tex}deterministic strategies. Their memory depth,
@@
 A number of these strategies have been trained with reinforcement learning
-algorithms.
+algorithms prior to this study and not specifically for the Moran process.
 
@@
 algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. They were not
-trained specifically for the Moran process or to cooperate well with themselves
-(though they all do). Variation is
+against all other opponents \cite{affenzeller2009genetic}. They were trained to
+win IPD tournaments by maximizing their mean total payoffs against a variety
+of opponents. Variation is
 introduced via mutation and crossover of parameters, and the best performing
@@
 TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter. There is a
-longer complex handshake which eventually results in mutual cooperation with
-Firm but Fair, Fortress3, Fortress4, and Grofman (always) and Evolved HMM 5 and
-GTFT (depending on the random seed).
+DD\@. It plays CDD against itself and then cooperates thereafter. Cooperation
+can be rescued after a failed handshake by a complex sequence of plays
+which eventually results in mutual cooperation with Firm but Fair, Fortress3,
+Fortress4, and Grofman (always) and Evolved HMM 5 and GTFT (depending on the
+random seed). TF2 defects against all other players in the study, barring
+unusual cases arising from particular randomizations.
 
@@
 
-% With an intensity of selection \(\omega\) the fitness of both strategies is
-% given by:
-%
-% \begin{equation}\label{equ:expected_payoff_one}
-%     f_i = 1 - \omega + \omega F_i
-% \end{equation}
-%
-% \begin{equation}\label{equ:expected_payoff_two}
-%     g_i = 1 - \omega + \omega G_i
-% \end{equation}
-
 The transitions within the birth death process that underpins the Moran process
@@
 stochastic strategies. These are no longer a good match which highlights the
-weakness of the analytical formulae that relies on the average payoffs
-(\ref{equ:payoff_matrix}). Estimating all the transitions may give better agreement
-but is not necessary for our purposes. All data generated for this validation exercise can be found
+weakness of assuming a given interaction between two IPD strategies can be
+summarised with a set of utilities as shown in
+(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
+obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
+approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
+(\ref{equ:p_stay}). Obtaining these requires particular analysis for a given
+pair and can be quite a complex endeavour for stochastic strategies with long
+memory: this is not necessary for the purposes of this work.
+All data generated for this validation exercise can be found
 at \cite{data}.
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/WStLSh_v_TfT.pdf}
+        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WStLSh.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WSLS.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
         \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_WStLSh.pdf}
+        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
 mean payoffs over all possible matches between two players. The strategy
-that scores higher than the other more often will fixate more often.
-
-For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
+that scores higher than the other more often will fixate more often. For \(N=2\)
+the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
 considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
@@
         handshake mechanism described above.
-    \item The Defector: it always defects. As it has little potential
+    \item Defector: it always defects. As it has little potential
         interaction with itself (recall that \(N=2\)), its
         aggressiveness is rewarded.
-    \item The Aggravater strategy which plays like Grudger (responding to any
+    \item Aggravater, which plays like Grudger (responding to any
         defections with unconditional defections throughout) however starts by
@@
     \item Predator, a finite state machine described in \cite{Ashlock2006}.
-    \item Handshake: a slightly less aggressive version of the Collective
+    \item Handshake, a slightly less aggressive version of the Collective
         strategy \cite{robson1989}. As long as the initial sequence is played
         then it cooperates. Thus it will do well in a population consisting of
-        many members of itself: just as the Collective strategy does. However it
-        is not aggressive enough to invade other populations (as can be seen in
-        Section~\ref{sec:strong_invaders}.
+        many members of itself just as the Collective Strategy does. The
+        difference is that CS will defect after the handshake if the opponent
+        defects while handshake will not.
 \end{enumerate}
@@
 \begin{figure}[!hbtp]
-    \centering
-    \includegraphics[height=.9\textheight]{./img/boxplot_2_invade.pdf}
+    \begin{subfigure}{.5\textwidth}
+        \centering
+        \includegraphics[height=.7\textheight]{./img/boxplot_2_invade.pdf}
         \caption{The fixation probabilities for \(N=2\)}
         \label{fig:boxplot_2}
-\end{figure}
-
-\begin{table}[!hbtp]
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.5\textwidth}
         \scriptsize
@@
         \input{./tex/summary_top_2_invade.tex}
-    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\).}
+        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\)).}
         \label{tbl:summary_top_2}
-\end{table}
+    \end{subfigure}
+    \caption{Performance of strategies for \(N=2\)}
+\end{figure}
 
@@
 \(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that Zero Determinant strategies should be
+the literature which suggests that zero Determinant strategies should be
 effective for larger population sizes, but these analysis consider stationary
-behaviour, while this work runs for a fixed number of rounds. Note that the
-stationarity assumptions allows for the analysis to take place leading to the
-conclusions about zero determinant strategies however it is dependent on a
-specific structure of strategies. The analysis carried out here makes no
-assumptions about the structure of the strategies by using actual simulation
-interactions. \cite{Stewart...}
+behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
+The stationarity assumption allows for a deterministic payoff matrix 
+leading to the conclusions about zero determinant strategies in the space
+of memory-one strategies that do not generalize to this context.
 
@@
 
-\subsection{Strong invaders}\label{sec:strong_invaders}
+\subsection{Strong Invaders}\label{sec:strong_invaders}
 
@@
 The ranks of each strategy for all considered values of \(N\) according to mean
-\(x_1\) are shown in Figures~\ref{fig_ranks_v_size_invade}.
+\(x_1\) are shown in Figure~\ref{fig:ranks_v_size_invade}.
 
@@
 \begin{figure}[!hbtp]
-    \scriptsize
+    \centering
+    \begin{subfigure}{.3\textwidth}
         \centering
         \includegraphics[height=.9\textheight]{./img/boxplot_3_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
+        \caption{\(N=3\)}
         \label{fig:boxplot_3_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\textwidth}
         \centering
         \includegraphics[height=.9\textheight]{./img/boxplot_7_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
+        \caption{\(N=7\)}
         \label{fig:boxplot_7_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\textwidth}
         \centering
         \includegraphics[height=.9\textheight]{./img/boxplot_14_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
+        \caption{\(N=14\)}
         \label{fig:boxplot_14_invade}
-\end{figure}
-
-The top strategies are given in Tables~\ref{tbl:top_five_invade}.
+    \end{subfigure}
+    \caption{The fixation probabilities \(x_1\)}
+\end{figure}
+
+The top strategies are given in Tables~\ref{tbl:top_invade}.
 
@@
     \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_five_invade}
+    \label{tbl:top_invade}
 \end{table}
@@
         but will defect if at any point the opponent has defected.
-    \item MEM2, an infinite memory strategy that switches between TfT, Tf2T, and
+    \item MEM2, an infinite memory strategy that switches between TFT, TF2T, and
         Defector \cite{Li2014}.
@@
         described in Section~\ref{sec:introduction}.
-    \item Prober 4, complex strategy with an initial 20 move sequence of
+    \item Prober 4, a strategy which starts with a specific 20 move sequence of
         cooperations and defections \cite{prison}. This initial sequence serves
@@
         cooperating. The lookerup was described in \cite{Knight2016}.
-	\item The evolved ANN strategies are neural networks that map a number of
-		attributes (first move, number of cooperations, last move etc\dots) to
+    \item The Evolved ANN strategies are neural networks that map a number of
+	    attributes (first move, number of cooperations, last move, etc.) to
 	    an action. Both of these have been trained using an evolutionary
-		algorithm and the ANN 5 was trained to perform well in a noisy
-		tournament.
+	    algorithm.
     \item The Evolved FSM 16 is a 16 state finite state machine trained to
@@
 from TF3 in \(N=3\), the finite state machines trained specifically for Moran
-processes do not appear in the top 5: whereas strategies trained for tournaments do.
-This is due to the nature of invasion: most of the opponents will initially be different
-strategies. The next section will consider the converse situation.
+processes do not appear in the top 5 while strategies trained for tournaments do.
+This is due to the nature of invasion: most of the opponents will initially be of
+different types. The next section will consider the converse situation.
 
@@
 according to mean \(x_{N-1}\) are shown in
-Figures~\ref{fig_ranks_v_size_resist}.
+Figures~\ref{fig:ranks_v_size_resist}.
 
@@
     \centering
+    \begin{subfigure}{.3\textwidth}
+        \centering
         \includegraphics[height=.9\textheight]{./img/boxplot_3_resist.pdf}
-    \caption{The fixation probability \(x_{N-1}\) for \(N=3\)}
+        \caption{\(N=3\)}
         \label{fig:boxplot_3_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\textwidth}
         \centering
         \includegraphics[height=.9\textheight]{./img/boxplot_7_resist.pdf}
-    \caption{The fixation probability \(x_{N-1}\) for \(N=7\)}
-    \label{fig:boxplot_6_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
+        \caption{\(N=7\)}
+        \label{fig:boxplot_7_resist}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\textwidth}
         \centering
         \includegraphics[height=.9\textheight]{./img/boxplot_14_resist.pdf}
-    \caption{The fixation probability \(x_{N-1}\) for \(N=14\)}
+        \caption{\(N=14\)}
         \label{fig:boxplot_14_resist}
-\end{figure}
-
-Table~\ref{tbl:top_five_resist} shows the top strategies when ranked
+    \end{subfigure}
+    \caption{The fixation probabilities \(x_{N-1}\)}
+\end{figure}
+
+Table~\ref{tbl:top_resist} shows the top strategies when ranked
 according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
@@
     \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_five_resist}
+    \label{tbl:top_resist}
 \end{table}
@@
 the need of strategies to have a steady hand when interacting with their own
-kind. In essence: acting stochastically increases the chance of friendly fire.
+kind. Acting stochastically increases the chance of friendly fire.
 However it is possible to design a strategy with a stochastic or error-correcting
@@
 some strategies additionally retaliate first round defections. So the
-handshakes used by TF1, TF2, and CS are in some sense optimal. These
-discoveries may have significant ramifications regarding the evolution of
-cooperation and forgiveness in biological organisms such as antibacterial
-resistant bacteria and social interactions between humans.
+handshakes used by TF1, TF2, and CS are in some sense optimal.
 
@@
     \item The strategies that ranked highly for \(N=14\);
-    \item The Zero determinant strategies.
+    \item The zero determinant strategies.
 \end{itemize}
@@
     \input{./tex/change_of_rank_invade.tex}
-    \caption{Ranks of some strategies according to \(x_1\) for different
+    \caption{Invasion: Fixation ranks of some strategies according to \(x_1\) for different
     population sizes}
@@
     \input{./tex/change_of_rank_resist.tex}
-    \caption{Ranks of some strategies according to \(x_{N-1}\) for different
+    \caption{Resistance: Fixation ranks of some strategies according to \(x_{N-1}\) for different
     population sizes}
@@
     \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_coexist.pdf}
-    \caption{Ranks of all strategies according to \(x_{N/2}\) for different
+    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
     population sizes}
@@
 Figure~\ref{fig:correlation_coefficients} show the correlation coefficients
-of the ranks of strategies in differing population size. It is immediate to
-note that how well a strategy performs in any Moran process for \(N>2\) has
+of the ranks of strategies in differing population size. How well a strategy
+performs in any Moran process for \(N>2\) has
 little to do with the performance for \(N=2\). This illustrates why the strong
-performance of Zero determinant strategies predicted in \cite{Press2012} does
+performance of zero determinant strategies predicted in \cite{Press2012} does
 not extend to larger populations. This was discussed theoretically in
-\cite{Adami2013} however not observed empirically at the scale presented here.
+\cite{Adami2013} and observed empirically in these simulations.
 
@@
 a critical threshold and use a different strategy for invasion when in the
-minority. However this information was not available to our strategies.
+minority. Information about the population distribution was not available
+to our strategies.
 
@@
 process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. This has the potential to help with the understanding of
-organisms with a strong resistance to invasion such as anti antibacterial
-resistant bacteria \cite{Davies2010}. With the knowledge that a handshake being
-likely to exist, perhaps it can be mimicked.
+evolutionary process.
 
@@
 
-% There are various areas for further work to build on this. Firstly, an analysis
-% of the effect of noise would offer insights about the stability of the findings.
-% It would also be possible to consider three or more types of strategy in the
-% population and finally mutation would also offer an interesting dimension to
-% explore.
+There are many opportunities build on this work. In particular, an analysis
+of the effect of noise should offer insights regarding the stability of the findings,
+particularly for the handshaking strategies. They may be less dominant for
+larger amounts of noise since the handshaking mechanisms may become brittle.
+There are many other variations to explore including populations with more
+than one type, spatial structure, and mutation.
+
+% TODO: author contributions
 

### 2017-05-16 main.tex
Add a small discussion for longer ranking tables

@@
 and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
-probabilities for the strategies considered. This is summarised in
-Table~\ref{tbl:summary_top_2}.
+probabilities for the strategies considered. The top 16 (10\%) strategies are
+shown in
+Table~\ref{tbl:summary_top_2}. The top five ranking strategies are:
 
@@
 
+It is also noted that TF1, TF2 and TF3 all perform well, other finite state
+machines include Prober 3 and Prober 4 which are described in \cite{prison}.
+This is also the \(N\) for which a zero determinant strategy does appear in the
+top 10\% ranking strategies: ZD-extort-4. The performance of zero determinant
+strategies will be examined more closely in Section~\ref{sec:population_size}.
+
 \begin{figure}[!hbtp]
@@
 
-The top strategies are given in Tables~\ref{tbl:top_invade}.
+The top 16 strategies are given in Tables~\ref{tbl:top_invade}.
 
@@
 of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
-high performing strategies are:
+top performing strategies are:
 
@@
 
-As well as noting that the memory length and complexity of these strategies are
-much greater than one, it is interesting to note that none of them are akin to
-memory one strategies. Only one is stochastic although close inspection of the
+Only one of the above strategies is stochastic although close inspection of the
 source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin Evolved Looker Up. Apart
-from TF3 in \(N=3\), the finite state machines trained specifically for Moran
-processes do not appear in the top 5 while strategies trained for tournaments do.
-This is due to the nature of invasion: most of the opponents will initially be of
-different types. The next section will consider the converse situation.
+is functionally very similar to its deterministic cousin Evolved Looker Up.
+The PSO Gambler Mem1 strategy is a memory one strategy that has been trained to
+maximise it's utility and does perform well.
+Apart from TF3, the finite state machines trained specifically for
+Moran processes do not appear in the top 5: whereas strategies trained for
+tournaments do. This is due to the nature of invasion: most of the opponents
+will initially be different strategies. The next section will consider the
+converse situation.
 

### 2017-05-17 main.tex

--- 2017-05-15 main.tex
@@
         \label{tbl:summary_top_2}
-\end{table}
+    \end{subfigure}
+    \caption{Performance of strategies for \(N=2\)}
+\end{figure}
 

### 2017-05-17 main.tex
More updates

--- 2017-05-16 main.tex
@@
 \begin{abstract}
-    We present insights and empirical results from an extensive numerical
-    study of the evolutionary dynamics of the iterated prisoner's dilemma.
-    Fixation probabilities for Moran processes are obtained
-    for all pairs of 164 different strategies including classics such as TitForTat, zero
+    In this paper an extensive numerical
+    study of the evolutionary dynamics of the iterated prisoner's dilemma
+    are presented. Fixation probabilities for Moran processes are obtained
+    for 164 different strategies including classics such as TitForTat, zero
     determinant strategies, and many more sophisticated strategies.
@@
     and resistors of invasion and in some cases naturally evolve handshaking
-    mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake machanisms.
-    This suggests that while maximizing individual payoff
-    can lead to the evolution of cooperation through invasion, the relatively
-    weak invasion resistance of payoff maximizing strategies are not as
-    evolutionarily stable as strategies employing handshake mechanisms.
+    mechanisms to resist invasion.
 \end{abstract}
@@
 
+% With an intensity of selection \(\omega\) the fitness of both strategies is
+% given by:
+%
+% \begin{equation}\label{equ:expected_payoff_one}
+%     f_i = 1 - \omega + \omega F_i
+% \end{equation}
+%
+% \begin{equation}\label{equ:expected_payoff_two}
+%     g_i = 1 - \omega + \omega G_i
+% \end{equation}
+
 The transitions within the birth death process that underpins the Moran process
@@
 stochastic strategies. These are no longer a good match which highlights the
-weakness of assuming a given interaction between two IPD strategies can be
-summarised with a set of utilities as shown in
-(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
-obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
-approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
-(\ref{equ:p_stay}). Obtaining these requires particular analysis for a given
-pair and can be quite a complex endeavour for stochastic strategies with long
-memory: this is not necessary for the purposes of this work.
-All data generated for this validation exercise can be found
+weakness of the analytical formulae that relies on the average payoffs
+(\ref{equ:payoff_matrix}). Estimating all the transitions may give better agreement
+but is not necessary for our purposes. All data generated for this validation exercise can be found
 at \cite{data}.
@@
 The ranks of each strategy for all considered values of \(N\) according to mean
-\(x_1\) are shown in Figure~\ref{fig:ranks_v_size_invade}.
+\(x_1\) are shown in Figures~\ref{fig_ranks_v_size_invade}.
 
@@
 according to mean \(x_{N-1}\) are shown in
-Figures~\ref{fig:ranks_v_size_resist}.
+Figures~\ref{fig_ranks_v_size_resist}.
 
@@
 
-There are many opportunities build on this work. In particular, an analysis
-of the effect of noise should offer insights regarding the stability of the findings,
-particularly for the handshaking strategies. They may be less dominant for
-larger amounts of noise since the handshaking mechanisms may become brittle.
-There are many other variations to explore including populations with more
-than one type, spatial structure, and mutation.
-
-% TODO: author contributions
+% There are various areas for further work to build on this. Firstly, an analysis
+% of the effect of noise would offer insights about the stability of the findings.
+% It would also be possible to consider three or more types of strategy in the
+% population and finally mutation would also offer an interesting dimension to
+% explore.
 

### 2017-05-17 main.tex
Update abstract

@@
 \begin{abstract}
-    In this paper an extensive numerical
-    study of the evolutionary dynamics of the iterated prisoner's dilemma
-    are presented. Fixation probabilities for Moran processes are obtained
-    for 164 different strategies including classics such as TitForTat, zero
+    We present insights and empirical results from an extensive numerical
+    study of the evolutionary dynamics of the iterated prisoner's dilemma.
+    Fixation probabilities for Moran processes are obtained
+    for all pairs of 164 different strategies including classics such as TitForTat, zero
     determinant strategies, and many more sophisticated strategies.
@@
     and resistors of invasion and in some cases naturally evolve handshaking
-    mechanisms to resist invasion.
+    mechanisms to resist invasion. The best invaders were those trained
+    to maximize total payoff while the best resistors invoke handshake machanisms.
+    This suggests that while maximizing individual payoff
+    can lead to the evolution of cooperation through invasion, the relatively
+    weak invasion resistance of payoff maximizing strategies are not as
+    evolutionarily stable as strategies employing handshake mechanisms.
 \end{abstract}

### 2017-05-17 main.tex
Conclusion paragraph

@@
 
-% There are various areas for further work to build on this. Firstly, an analysis
-% of the effect of noise would offer insights about the stability of the findings.
-% It would also be possible to consider three or more types of strategy in the
-% population and finally mutation would also offer an interesting dimension to
-% explore.
+There are many opportunities build on this work. In particular, an analysis
+of the effect of noise should offer insights regarding the stability of the findings,
+particularly for the handshaking strategies. They may be less dominant for
+larger amounts of noise since the handshaking mechanisms may become brittle.
+There are many other variations to explore including populations with more
+than one type, spatial structure, and mutation.
 

### 2017-05-17 main.tex
Authors TODO
Make amendments suggested by Marc.

@@
 
+It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
+for which a zero determinant strategy does appear in the top 10\% ranking
+strategies: ZD-extort-4. The performance of zero determinant strategies will be
+examined more closely in Section~\ref{sec:population_size}.
+
 \begin{figure}[!hbtp]
@@
 
-As well as noting that the memory length and complexity of these strategies are
-much greater than one, it is interesting to note that none of them are akin to
-memory one strategies. Only one is stochastic although close inspection of the
+Only one of the above strategies is stochastic although close inspection of the
 source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin Evolved Looker Up. Apart
-from TF3 in \(N=3\), the finite state machines trained specifically for Moran
-processes do not appear in the top 5 while strategies trained for tournaments do.
-This is due to the nature of invasion: most of the opponents will initially be of
-different types. The next section will consider the converse situation.
+is functionally very similar to its deterministic cousin Evolved Looker Up.
+The PSO Gambler Mem1 strategy is a memory one strategy that has been trained to
+maximise its utility and does perform well.
+Apart from TF3, the finite state machines trained specifically for
+Moran processes do not appear in the top 5, while strategies trained for
+tournaments do. This is due to the nature of invasion: most of the opponents
+will initially be different strategies. The next section will consider the
+converse situation.
 
@@
 
+% TODO: author contributions
+
 \section*{Acknowledgements}

### 2017-05-17 main.tex
Rephrase sentence about the removed strategies.

--- 2017-05-17 main.tex
@@
 strategies. Not all strategies have been considered for this study: excluded
-are those that make use of knowledge of the game such as the number of turns
+are those that make use of knowledge of the number of turns in a match
 and others that have a high

### 2017-05-17 main.tex
Remove comments about antibacterial resistance.
Also remove %todo about contributions (it's currently in the README of
the repo and will/can be added to the paper depending on the journal?).

@@
 via direct mathematical analysis \cite{adami2016evolutionary}. The results
-and insighed contained in this paper would be difficult to derive analytically.
+and insights contained in this paper would be difficult to derive analytically.
 
@@
 \end{enumerate}
-
-These finding have the potential to offer insight in to organisms such as antibacterial
-resistant bacteria \cite{Davies2010} and human social behaviors.
 
@@
 
-% TODO: author contributions
-
 \section*{Acknowledgements}

### 2017-05-17 tex/list_of_players.tex
Set TF3 to have inf memory length.
Closes #25

@@
  - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C
-(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: 16\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C
+(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C
 (\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\)\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C

### 2017-05-17 src/players.py

@@ -51,7 +51,7 @@ fsm_players += [axl.FSMPlayer(transitions=transitions, initial_state=0, initial_
 
 fsm_players[3].classifier["memory_depth"] = float('inf')
 fsm_players[4].classifier["memory_depth"] = float('inf')
-fsm_players[5].classifier["memory_depth"] = 16
+fsm_players[5].classifier["memory_depth"] = float('inf')
 
 def selected_players(extra_players=fsm_players):
     """

### 2017-05-18 main.tex
Correct minor typos

@@
  first but retaliate to varying degrees of intensity against strategies that defect.
- \item Strategies evolved to maximize their total payout can be strong invaders
+ \item Strategies evolved to maximize their total payoff can be strong invaders
  and achieve mutual cooperation with many other strategies.
@@
 state where the population is entirely made up of players of one strategy. The
-probability with which a given strategy takes over a the population is called the
+probability with which a given strategy takes over a population is called the
 \textit{fixation probability}. A more detailed analytic description of this is
@@
 Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies, strategies that recall
+strategies. The subset included memory one strategies; strategies that recall
 the events of the previous round only.
@@
 \cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015}
+ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
 a strategy using machine learning techniques was capable of resisting invasion
@@
 To carry out this large numerical experiment, \input{./tex/num_strategies}
-strategies, listed (with their properties) in Appendix~\ref{app:list_of_players}
+strategies, listed (with their properties) in Appendix~\ref{app:list_of_players},
 are used from the Axelrod library. There are
@@
 strategy uses the entire history of play (whatever its length). For example, a
-strategy that utilizes a handshaking mechanism where the opponents actions on
+strategy that utilizes a handshaking mechanism where the opponent's actions on
 the first few rounds of play determines the strategies subsequent behavior would
@@
 
-A part from the PSO Gambler strategy, which was trained using a particle swarm
+Apart from the PSO Gambler strategy, which was trained using a particle swarm
 optimisation algorithm, these strategies are trained with an evolutionary
@@
 repetitions to estimate the absorption probabilities. The trained algorithms
-were run for less than 50 generations. Training data for this is available at
+were run for fewer than 50 generations. Training data for this is available at
 \cite{data}.
@@
 (not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective. It differs from TF1 and TF2
-by lacking a handshake mechanism.
+product of training with a Moran objective, it differs from TF1 and TF2
+in that it lacks a handshake mechanism.
 
@@
 values and the line shows the theoretical value. Note that these are all
-deterministic strategies and show a perfect match up between the expected value
+deterministic strategies and show a perfect match between the expected value
 of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategies pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
+strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
 stochastic strategies. These are no longer a good match which highlights the
@@
 the literature which suggests that zero Determinant strategies should be
-effective for larger population sizes, but these analysis consider stationary
+effective for larger population sizes, but these analyses consider stationary
 behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
@@
 
-Interestingly none of these strategies are stochastic: this is explained by
+Interestingly none of these strategies is stochastic: this is explained by
 the need of strategies to have a steady hand when interacting with their own
@@
 cooperative strategies. TF3, which does not use a handshake, is a better invader
-than TF1 and TF2 but not as good of a resistor. Nevertheless it was the result
+than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
 of the same kind of training procceses and is a better combined invader-resistor
@@
 distribution, a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping down dramatically
+are only effective invaders for the smallest $N$, dropping dramatically
 as the population size increases.
@@
 Interestingly they have been trained to perform well in tournaments and not
-Moran processes which highlights the potentially for improvement.
+Moran processes which highlights the potential for improvement.
 
@@
 
-There are many opportunities build on this work. In particular, an analysis
+There are many opportunities to build on this work. In particular, an analysis
 of the effect of noise should offer insights regarding the stability of the findings,

### 2017-05-19 main.tex
Minor corrections and typos.
Mainly keep 'Axelrod library' and 'zero determinant' consistent.
Dots in Figures captions.

@@
     mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake machanisms.
+    to maximize total payoff while the best resistors invoke handshake mechanism.
     This suggests that while maximizing individual payoff
@@
 number of strategies have been developed to take advantage of the history of
-play. Recently, some strategies referred to as zero Determinant strategies
+play. Recently, some strategies referred to as zero determinant (ZD) strategies
 \cite{Press2012} can manipulate some players through extortionate mechanisms.
@@
 strategies are finite state machines trained specifically for Moran processes
-(described further in Section~\ref{sec:strategies}.
+(described further in Section~\ref{sec:strategies}).
 
@@
     \input{./tex/moran_process.tex}
-    \caption{A diagrammatic representation of a Moran process}
+    \caption{A diagrammatic representation of a Moran process.}
     \label{fig:moran_process}
@@
 Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies; strategies that recall
+strategies. The subset included memory one strategies: strategies that recall
 the events of the previous round only.
 
-Of particular interest are the Zero determinant strategies introduced in
+Of particular interest are the zero determinant strategies introduced in
 \cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
@@
 individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the axelrod library:
+strategy, taken from a selection of 150 opponents from the Axelrod library:
 
@@
 computed for each combination of starting distribution and value of \(N\).  The
-axelrod library can carry out exact simulations of the Moran process. Since some
+Axelrod library can carry out exact simulations of the Moran process. Since some
 of the strategies have a high computational cost or are stochastic, samples are
@@
 of the first strategy in a population of \(i\) individuals of the first type
-(and \(N-i\) individuals of the second::
+and \(N-i\) individuals of the second:
 
@@
 approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
-(\ref{equ:p_stay}). Obtaining these requires particular analysis for a given
+(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
 pair and can be quite a complex endeavour for stochastic strategies with long
@@
     \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textbf{deterministic} strategies}
+             probabilities for \textbf{deterministic} strategies.}
     \label{fig:comparison_deterministic}
@@
     \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textbf{stochastic} strategies}
+             fixation probabilities for \textbf{stochastic} strategies.}
     \label{fig:comparison_stochastic}
@@
         between performance for differing population sizes as well as
-        taking a close look at Zero determinant strategies \cite{Press2012}.
+        taking a close look at zero determinant strategies \cite{Press2012}.
 \end{itemize}
@@
         \input{./tex/summary_top_2_invade.tex}
-        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\)).}
+        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
         \label{tbl:summary_top_2}
     \end{subfigure}
-    \caption{Performance of strategies for \(N=2\)}
+    \caption{Performance of strategies for \(N=2\).}
 \end{figure}
@@
 \(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that zero Determinant strategies should be
+the literature which suggests that zero determinant strategies should be
 effective for larger population sizes, but these analyses consider stationary
@@
     \caption{Ranks of all strategies according to \(x_1\) for different
-    population sizes}
+    population sizes.}
     \label{fig:ranks_v_size_invade}
@@
     \end{subfigure}
-    \caption{The fixation probabilities \(x_1\)}
+    \caption{The fixation probabilities \(x_1\).}
 \end{figure}
@@
         the last 2 moves of both players to an action. The PSO gambler is a
-        stochastic version which maps those states to probabilities of
-        cooperating. The lookerup was described in \cite{Knight2016}.
+        stochastic version of the Lookerup which maps those states to probabilities of cooperating. The Lookerup was described in \cite{Knight2016}.
     \item The Evolved ANN strategies are neural networks that map a number of
@@
     \caption{Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes}
+    population sizes.}
     \label{fig:ranks_v_size_resist}
@@
     \end{subfigure}
-    \caption{The fixation probabilities \(x_{N-1}\)}
+    \caption{The fixation probabilities \(x_{N-1}\).}
 \end{figure}
@@
 
-To complement Figures~\ref{fig:ranks_v_size_invade}
-and~\ref{fig:ranks_v_size_resist} Figure~\ref{fig:ranks_v_size_coexist} shows
+To complement Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
+and~\ref{fig:ranks_v_size_coexist} show
 the rank of each strategy based on \(x_{N/2}\).
@@
     \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes}
+    population sizes.}
     \label{fig:ranks_v_size_coexist}
@@
     \end{subfigure}
-    \caption{Heatmap of correlation coefficients of rankings by population size}
+    \caption{Heatmap of correlation coefficients of rankings by population size.}
     \label{fig:correlation_coefficients}
@@
 \begin{itemize}
-    \item The axelrod library (IPD strategies and Moran processes)
+    \item The Axelrod library (IPD strategies and Moran processes)
         \cite{axelrodproject}.

### 2017-05-19 main.tex
addressing vince's comments

@@
     mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake mechanism.
+    to maximize total payoff while the best resistors invoke handshake mechanisms.
     This suggests that while maximizing individual payoff
@@
 
-To complement Figures~\ref{fig:ranks_v_size_invade},~\ref{fig:ranks_v_size_resist}
-and~\ref{fig:ranks_v_size_coexist} show
+To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, \ref{fig:ranks_v_size_coexist} shows
 the rank of each strategy based on \(x_{N/2}\).

### 2017-05-19 main.tex

@@
 
-To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, \ref{fig:ranks_v_size_coexist} shows
-the rank of each strategy based on \(x_{N/2}\).
+To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, Figure~\ref{fig:ranks_v_size_coexists} shows the rank of each strategy based on \(x_{N/2}\).
 Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}

### 2017-05-26 main.tex
Add a sentence about the N/2 results.

--- 2017-05-19 main.tex
@@
 
-To complement Figures~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist}, \ref{fig:ranks_v_size_coexist} shows
+To complement Figures~\ref{fig:ranks_v_size_invade}
+and~\ref{fig:ranks_v_size_resist}, Figure~\ref{fig:ranks_v_size_coexist} shows
 the rank of each strategy based on \(x_{N/2}\).
@@
 \end{itemize}
+
+The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
+in particular TF1, TF2 and TF3 all rank in the top 8 strategies. This is to be
+expected since, as described in Section~\ref{sec:strategies} these strategies
+were trained in an initial population of \(N/2\) individuals.
 

### 2017-05-26 main.tex
Adjust wording.

@@
 The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 all rank in the top 8 strategies. This is to be
+in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
 expected since, as described in Section~\ref{sec:strategies} these strategies
-were trained in an initial population of \(N/2\) individuals.
+were trained in an initial population of \((N/2, N/2)\) individuals.
 

### 2017-06-07 main.tex
Fix action in tf2 diagram and add sentence.
Have added a sentence about 2 unreachable states.
Add sources to every strategy.
This used:

```python
import axelrod as axl
import re
import csv
assert axl.__version__ == '2.13.0' # Actually past 2.13

def get_bibtex_keys(player):
    """Get all bibtex keys for a player"""
    return list(set(re.findall(": \[(.*?)\]_", player.__doc__)))

with open("reference_keys.csv", "w") as f:
    writer = csv.writer(f)
    strategies_without_source = []
    for strategy in axl.strategies:
        player = strategy()
        keys = get_bibtex_keys(player)

@@
 random seed). TF2 defects against all other players in the study, barring
-unusual cases arising from particular randomizations.
+unusual cases arising from particular randomizations. Figure~\ref{fig:tf2} shows
+all 16 states of the strategy used for training although it is evident that
+states 6 and 7 are not reachable. They are nonetheless presented as they are
+outputs of the training algorithm.
 
@@
 However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
+handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
 achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
@@
     \item Prober 4, a strategy which starts with a specific 20 move sequence of
-        cooperations and defections \cite{prison}. This initial sequence serves
+        cooperations and defections \cite{Prison1998}. This initial sequence serves
         as approximate handshake.

### 2017-06-07 tex/list_of_players.tex
Add sources to every strategy.
This used:

```python
import axelrod as axl
import re
import csv
assert axl.__version__ == '2.13.0' # Actually past 2.13

def get_bibtex_keys(player):
    """Get all bibtex keys for a player"""
    return list(set(re.findall(": \[(.*?)\]_", player.__doc__)))

with open("reference_keys.csv", "w") as f:
    writer = csv.writer(f)
    strategies_without_source = []
    for strategy in axl.strategies:
        player = strategy()
        keys = get_bibtex_keys(player)

        if len(keys) == 0:
            if "Original" in player.__doc__:
                keys.append(

--- 2017-04-29 tex/list_of_players.tex
@@
-\item Random Hunter
-\item Cooperator
-\item Adaptive
-\item Random: 0.5
-\item Contrite Tit For Tat
-\item Cycle Hunter
-\item Adaptive Tit For Tat: 0.5
-\item Cooperator Hunter
-\item Stochastic Cooperator
-\item Remorseful Prober: 0.1
-\item Cycler CCCCCD
-\item Tricky Cooperator
-\item Win-Shift Lose-Stay: D
-\item Aggravater
-\item Tricky Defector
-\item $\pi$
-\item Resurrection
-\item Stochastic WSLS: 0.05
-\item Win-Stay Lose-Shift: C
-\item ALLCorALLD
-\item Tullock: 11
-\item Alternator
-\item Retaliate: 0.1
-\item Cycler CCCD
-\item Worse and Worse
-\item Alternator Hunter
-\item Retaliate 2: 0.08
-\item Worse and Worse 2
-\item AntiCycler
-\item Winner21
-\item Cycler CCD
-\item Suspicious Tit For Tat
-\item Retaliate 3: 0.05
-\item Willing
-\item Worse and Worse 3
-\item Anti Tit For Tat
-\item Adaptive Pavlov 2006
-\item Revised Downing: True
-\item Cycler DC
-\item ZD-Extort-2: 0.1111111111111111, 0.5
-\item Adaptive Pavlov 2011
-\item ZD-Extort-2 v2: 0.125, 0.5, 1
-\item Ripoff
-\item VeryBad
-\item Cycler DDC
-\item Appeaser
-\item Cycler CCCDCD
-\item Winner12
-\item SelfSteem
-\item Risky QLearner
-\item ZD-Extort-4: 0.23529411764705882, 0.25, 1
-\item Arrogant QLearner
-\item Thumper
-\item ZD-GEN-2: 0.125, 0.5, 3
-\item Defector
-\item ZD-GTFT-2: 0.25, 0.5
-\item Average Copier
-\item Davis: 10
-\item ShortMem
-\item Meta Hunter: 6 players
-\item ThueMorseInverse
-\item Tester
-\item Better and Better
-\item Spiteful Tit For Tat
-\item Shubik
-\item Defector Hunter
-\item ThueMorse
-\item ZD-SET-2: 0.25, 0.0, 2
-\item $e$
-\item Slow Tit For Two Tats
-\item Desperate
-\item Bully
-\item SolutionB1
-\item Meta Hunter Aggressive: 7 players
-\item Calculator
-\item Slow Tit For Two Tats 2
-\item Tit For Tat
-\item Tit For 2 Tats
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 1, C
-\item Doubler
-\item Sneaky Tit For Tat
-\item SolutionB5
-\item Soft Grudger
-\item EasyGo
-\item CollectiveStrategy
-\item Soft Joss: 0.9
-\item Eatherley
-\item Cautious QLearner
-\item Two Tits For Tat
-\item Firm But Fair
-\item Hard Go By Majority
-\item Handshake
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 1, C
-\item Fool Me Once
-\item Prober 3
-\item Eventual Cycle Hunter
-\item Forgetful Grudger
-\item Prober 4
-\item Evolved ANN
-\item Forgetful Fool Me Once: 0.05
-\item Fool Me Forever
-\item Hard Go By Majority: 10
-\item Pun1
-\item Evolved ANN 5
-\item Fortress4
-\item Hard Go By Majority: 20
-\item Evolved ANN 5 Noise 05
-\item PSO Gambler 2\_2\_2
-\item Fortress3
-\item Hard Go By Majority: 40
-\item PSO Gambler 1\_1\_1
-\item Evolved FSM 4
-\item Forgiving Tit For Tat
-\item Naive Prober: 0.1
-\item GTFT: 0.33
-\item Soft Go By Majority
-\item Hard Go By Majority: 5
-\item Nice Average Copier
-\item Hard Prober
-\item Forgiver
-\item Opposite Grudger
-\item General Soft Grudger: n=1,d=4,c=2
-\item Evolved FSM 16
-\item Hard Tit For 2 Tats
-\item Soft Go By Majority: 10
-\item Once Bitten
-\item Hard Tit For Tat
-\item EvolvedLookerUp2\_2\_2
-\item Nydegger
-\item Prober 2
-\item Soft Go By Majority: 20
-\item Hesitant QLearner
-\item Evolved FSM 16 Noise 05
-\item PSO Gambler 2\_2\_2 Noise 05
-\item Omega TFT: 3, 8
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 1, C
-\item EvolvedLookerUp1\_1\_1
-\item Soft Go By Majority: 40
-\item Inverse
-\item Hopeless
-\item MEM2
-\item Soft Go By Majority: 5
-\item Inverse Punisher
-\item Predator
-\item Joss: 0.9
-\item $\phi$
-\item Gradual
-\item Level Punisher
-\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C')
-\item Limited Retaliate: 0.1, 20
-\item Grofman
-\item Limited Retaliate 2: 0.08, 15
-\item PSO Gambler Mem1
-\item Negation
-\item Punisher
-\item Grudger
-\item Prober
-\item GrudgerAlternator
-\item Limited Retaliate 3: 0.05, 20
-\item Raider
-\item Evolved HMM 5
-\item Math Constant Hunter
-\item Feld: 1.0, 0.5, 200
-\item Grumpy: Nice, 10, -10
+\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
+\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
+\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
+\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
+\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
+\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
+\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
+\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
+\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
+\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
+\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
+\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
+\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
+\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
+\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
+\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
+\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{axelrodproject}
+\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
+\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
+\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
+\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980}
+\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
+\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
+\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}
+\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
+\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
+\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}
+\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
+\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
+\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
+\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
+\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
+\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
+\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980, Stewart2012}
+\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
+\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
+\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
+\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
+\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980}
+\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
+\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
+\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}
+\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2006}
+\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2014}
+\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980, Tzafestas2000}
+\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
+\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
+\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
+\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
+\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
+\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
+\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
+\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
+\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
+\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
+\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
+\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
+\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
+\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2015}
+\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Ashlock2015}
+\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
+\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
+\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
+\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
+\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
+\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980}
+\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980}
+\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
+\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
+\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
+\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
+\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
+\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
+\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
+\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
+\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
+\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
+\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}

### 2017-07-09 src/generate_cooperation_data.py
Write script to get cooperation heatmaps.

@@ -1,0 +1,75 @@
+"""
+Runs a spatial tournament on a bi partite graph and writes data with the mean
+cooperation rate of players of one cluster against all players
+"""
+
+import axelrod as axl
+import pandas as pd
+import numpy as np
+import multiprocessing
+import os
+import csv
+
+from players import selected_players
+players = selected_players()
+
+def obtain_cooperation_matrix(filename, number_of_turns=200):
+    data = []
+    with open(filename, "r") as f:
+        csv_reader = csv.reader(f)
+        for row in csv_reader:
+            data.append(row[2:4] + [int(a == "C") for a in row[4]])
+    df = pd.DataFrame(data, columns=["player", "opponent"] + ["Round {}".format(n) for n in range(number_of_turns)])
+    return np.array(df.groupby(["player", "opponent"]).mean())
+
+def main(index, players=players, processes=None, seed=1, turns=200, repetitions=10000,
+         noise=0):
+    """
+    index of the player in question
+    """
+    edges = [(index, j) for j, _ in enumerate(players)]
+    assert (index, index) in edges
+    assert len(edges) == len(players)
+
+    if processes is None:
+        processes = multiprocessing.cpu_count()
+
+    prefix = "{}_{}_{}_{}".format(seed, int(100 * noise), repetitions,
+                                  players[index])
+    interactions_filename = "../data/cooperation_{}_interactions.csv".format(prefix)
+    output_filename = "../data/cooperation_{}_array.gz".format(prefix)
+
+    # Deleting the file if it exists
+    try:
+        os.remove(interactions_filename)
+    except OSError:
+        pass
+
+    axl.seed(seed)  # Setting a seed
+    assert axl.__version__ == "2.9.0"
+    print("Axelrod version", axl.__version__)
+    print(len(players), "Players")
+    print("Seed", seed)
+    print("Repetitions", repetitions)
+    print("Noise", noise)
+    print("Player", players[index])
+
+    tournament = axl.SpatialTournament(players, edges=edges, turns=turns,
+                                       repetitions=repetitions, noise=noise)
+
+    tournament.play(filename=interactions_filename, processes=processes,
+                    build_results=False, progress_bar=False)
+
+    matrix = obtain_cooperation_matrix(interactions_filename)
+    np.savetxt(fname=output_filename, X=matrix, delimiter=",")
+
+if __name__ == "__main__":
+    import sys
+    args = sys.argv[1:]
+
[…]

### 2017-07-09 src/generate_cooperation_data.py
Fix problem with name being too long.

@@ -35,7 +35,7 @@ def main(index, players=players, processes=None, seed=1, turns=200, repetitions=
         processes = multiprocessing.cpu_count()
 
     prefix = "{}_{}_{}_{}".format(seed, int(100 * noise), repetitions,
-                                  players[index])
+                                  index)
     interactions_filename = "../data/cooperation_{}_interactions.csv".format(prefix)
     output_filename = "../data/cooperation_{}_array.gz".format(prefix)
 

### 2017-07-09 src/generate_cooperation_data.py
Use abbreviation in file name.

@@ -10,6 +10,7 @@ import multiprocessing
 import os
 import csv
 
+from abbreviations import abbreviations
 from players import selected_players
 players = selected_players()
 
@@ -35,7 +36,7 @@ def main(index, players=players, processes=None, seed=1, turns=200, repetitions=
         processes = multiprocessing.cpu_count()
 
     prefix = "{}_{}_{}_{}".format(seed, int(100 * noise), repetitions,
-                                  index)
+                                  abbreviations[str(players[index])])
     interactions_filename = "../data/cooperation_{}_interactions.csv".format(prefix)
     output_filename = "../data/cooperation_{}_array.gz".format(prefix)
 

### 2017-07-09 src/generate_cooperation_data.py
Fix heatmap script and include placeholders.

@@ -12,7 +12,9 @@ import csv
 
 from abbreviations import abbreviations
 from players import selected_players
-players = selected_players()
+players = [p for p in selected_players()
+			if ("length" not in p.classifier["makes_use_of"]) and
+                           ("Incorrect" not in abbreviations[str(p)])]
 
 def obtain_cooperation_matrix(filename, number_of_turns=200):
     data = []

### 2017-07-09 main.tex

@@
 process. In these two cases, the handshake mechanism was a product of the
-evolutionary process.
+evolutionary process. Figure~\ref{fig:cooperation_rates} shows the cooperation
+rate of TF1, TF2, TF3 and CS
+for each round of a match against all the opponents in this study. Whilst TF3
+does not have a strict handshake mechanism it is clear that all these strategies
+start a match by cooperating. It is then evident that TF3 cooperates more than
+the other strategies thus explaining the difference in performance. It is also
+clear that CS only cooperates with itself and Handshake: it is a very aggressive
+strategy.
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_TF1_array.pdf}
+        \caption{TF1}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_TF2_array.pdf}
+        \caption{TF2}
+    \end{subfigure}
+
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_TF3_array.pdf}
+        \caption{TF3}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_CS_array.pdf}
+        \caption{CS}
+    \end{subfigure}
+    \caption{Cooperation rate per round (over 20 repetitions).}
+    \label{fig:cooperation_rates}
+\end{figure}
+% TODO Update with 10k reps.
 

### 2017-07-10 main.tex
Various edits

@@
 The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
-used to model a large variety of strategic interactions. Each player can choose
-between cooperation (C) or defection (D). The decisions are made simultaneously
-and independently. The payoffs of
+used to model a variety of strategic interactions. Each player chooses
+simultaneously and independently
+between cooperation (C) or defection (D). The payoffs of
 the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
@@
 round game, but is commonly studied in a manner where the prior outcomes
-matter. This extended form is called the Iterated Prisoner's
+matter. This repeated form is called the Iterated Prisoner's
 Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
@@
 \cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
-and/or do not consider sophisticated behaviour: only considering strategies that
-either cooperate or defect, or are limited to classes of strategies
+or are limited to classes of strategies
 such as memory-one strategies that only use the previous round of play.
@@
 computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 40 contributors from around the
+the open source nature of the project with over 50 contributors from around the
 world, made by programmers and researchers \cite{Knight2016}. Three of the considered
@@
 swarm algorithms) that are among the best invaders and resistors of invasion
-known to date, and show that handshaking mechanims naturally arise from these
+known to date, and show that handshaking mechanisms naturally arise from these
 processes as an invasion-resistance mechanism.
@@
      through evolutionary processes to outperform designed strategies.
- \item Strong resistors specifically evolve or have a handshake mechanism.
+ \item The strongest resistors specifically evolve or have a handshake mechanism.
  \item Strong invaders are generally cooperative strategies that do not defect
@@
 emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider non-sophisticated strategies. Some work has
-looked at evolutionary stability of strategies within the Prisoner's Dilemma
+However these works mainly consider relatively simple strategies. Some work has
+looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
 \cite{Li2014} but this is not done in the more widely used setting of the Moran
@@
 
-To carry out this large numerical experiment, \input{./tex/num_strategies}
+To carry out this numerical experiment, \input{./tex/num_strategies}
 strategies, listed (with their properties) in Appendix~\ref{app:list_of_players},
@@
 product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism.
+in that it lacks a handshake mechanism. Figure~\ref{fig:tf3} shows
+all 8 states of the strategy produced by the training process (states 3 and 8
+are not reachable).
 
 TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter. Cooperation
+DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
+Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
 can be rescued after a failed handshake by a complex sequence of plays
-which eventually results in mutual cooperation with Firm but Fair, Fortress3,
-Fortress4, and Grofman (always) and Evolved HMM 5 and GTFT (depending on the
-random seed). TF2 defects against all other players in the study, barring
+which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
+GTFT, and a few others with low probability. TF2 defects against all other
+players in the study, barring
 unusual cases arising from particular randomizations. Figure~\ref{fig:tf2} shows
-all 16 states of the strategy used for training although it is evident that
-states 6 and 7 are not reachable. They are nonetheless presented as they are
-outputs of the training algorithm.
+all 16 states of the strategy (states 6 and 7 are not reachable).
 
@@
 \subsection{Data collection}\label{sec:data_collection}
+
+% Todo: verify 1000 repetitions
 
@@
         handshake mechanism described above.
-    \item Defector: it always defects. As it has little potential
-        interaction with itself (recall that \(N=2\)), its
-        aggressiveness is rewarded.
+    \item Defector: it always defects. Since it has no interactions with other
+        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
     \item Aggravater, which plays like Grudger (responding to any
@@
     \item Handshake, a slightly less aggressive version of the Collective
-        strategy \cite{robson1989}. As long as the initial sequence is played
+        Strategy \cite{robson1989}. As long as the initial sequence is played
         then it cooperates. Thus it will do well in a population consisting of
@@
     \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
-    \caption{Ranks of all strategies according to \(x_1\) for different
+    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
     population sizes.}
@@
     \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
-    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
+    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
     population sizes.}
@@
 is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms.
+emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
+handshake for high invasion resistance. TF3 is a better total payoff maximizer
+which makes it a better invader along with the strategies
+trained to maximize total payoff since successful fitness proportionate selection
+is necessary for invasion. Training with an objective with initial population
+mix other than $(N/2, N/2)$ may favor invasion or resistance.
 
@@
 performance of a strategy in a large population from its performance in a small
-population.
-
-This is confirmed by the performance of the zero determinant strategies. While
+population. This is confirmed by the performance of the zero determinant strategies: while
 some do rank relatively highly for \(N=2\) (ZD-extort-4 has rank 16) this rank
@@
 $(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
-improvement. Any handshake more sophisticated than C necessarily involves
-a defection. (A handshake consisting of a longer sequence of cooperations is
+improvement. Any handshake more sophisticated than always cooperate necessarily involves
+a defection. (A handshake consisting of a long sequence of cooperations is
 effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
@@
 invaders for larger $N$ are nice strategies that do not defect before their
-opponents. This is because good invaders still need to cooperate with themselves,
-and so in the absense of a handshake mechanism or knowledge of the population
-distribution, a strategy must be generally cooperative. Aggressive strategies
+opponents. This is because good invaders need to maximize match payoff to benefit
+from fitness proportionate selection,
+and so in the absence of a handshake mechanism, knowledge of the population
+distribution, or some identifying label on the opponent,
+a strategy must be generally cooperative. Aggressive strategies
 are only effective invaders for the smallest $N$, dropping dramatically
@@
 rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study. Whilst TF3
+for each round of a match against all the opponents in this study. While TF3
 does not have a strict handshake mechanism it is clear that all these strategies

### 2017-07-10 main.tex
Choose title.
Closes #46

@@
 % Title
-\title{An Empirical Study of Invasion and Resistance
-       for Iterated Prisoner's Dilemma Strategies}
-\title{Evolving Invaders and Resistors for the Iterated Prisoner's Dilemma}
+\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
+       Mechanisms: an empirical study of the Moran process for the iterated
+       Prisoner's dilemma using reinforcement learning}
 \author{Vincent Knight \and
@@
 emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
-handshake for high invasion resistance. TF3 is a better total payoff maximizer
+handshakes for high invasion resistance. TF3 is a better total payoff maximizer
 which makes it a better invader along with the strategies

### 2017-07-10 main.tex
Update cooperation heatmaps to 10k versions.
Closes #51

@@
         \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_TF1_array.pdf}
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF1_array.pdf}
         \caption{TF1}
@@
         \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_TF2_array.pdf}
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF2_array.pdf}
         \caption{TF2}
@@
         \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_TF3_array.pdf}
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF3_array.pdf}
         \caption{TF3}
@@
         \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_20_CS_array.pdf}
+        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_CS_array.pdf}
         \caption{CS}
     \end{subfigure}
-    \caption{Cooperation rate per round (over 20 repetitions).}
+    \caption{Cooperation rate per round (over 10000 repetitions).}
     \label{fig:cooperation_rates}
 \end{figure}
-% TODO Update with 10k reps.
 

### 2017-07-10 main.tex
Include pointer at Dojo.

@@
 
-All of the training code is available in the
-Axelrod repository with documentation to train new strategies easily. Training
-% TODO Include link etc
+All of the training code is archived at \cite{marc_harper_2017_824264}. This
+software is (similarly to the Axelrod library) available on github
+\url{https://github.com/Axelrod-Python/axelrod-dojo} with documentation to
+train new strategies easily. Training
 typically takes less than 100 generations and can be completed within several

### 2017-07-16 main.tex
Some additions and edits to the discussion and conclusion.

@@
 which always defects if the opponent defects in the first round, is effectively
-employing a one-shot handshake of C. These insights also suggest that a strategy
+employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
+which emerged from training memory one strategies for the Moran process,
+also effectively employs a handshake of always cooperating, as it defects
+for the remainder of the match if the opponent ever defects.
+
+The insights that payoff maximizers are better invaders and that handshakers
+are better resistors suggests that a strategy
 aware of the population distribution could choose to become a handshaker at
-a critical threshold and use a different strategy for invasion when in the
+a critical threshold and use a strategy better for invasion when in the
 minority. Information about the population distribution was not available
-to our strategies.
+to our strategies. Previous work has showed that strategies able to retain
+memory across matches can infer the population distribution and act in such
+a manner, resulting in a strategy effective at invasion and resistance
+\cite{Lee2015}.
 
@@
 improvement. Any handshake more sophisticated than always cooperate necessarily involves
-a defection. (A handshake consisting of a long sequence of cooperations is
+a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
 effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
@@
 a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping dramatically
+are only effective invaders for the smallest $N$, dropping dramatically in rank
 as the population size increases.
 
-We did, however, attempt to evolve CS using FSM and lookup table based players,
+We did, however, attempt to evolve CS using finite state machines and lookup table
+based players,
 which resulted in some very similar strategies. In particular we evolved a
@@
 after a correct handshake while defecting otherwise, which is quite close in
-function to CS (full grudging is not possible with a lookup table).
+function to CS (full grudging is not possible with a lookup table of limited
+depth).
 
@@
 starting values allowing the each strategy to attempt to invade the other.
-This is the largest such experiment carried out and has lead to many insights.
+This is the largest such experiment carried out and has led to many insights.
 
@@
 
-Memory one strategies do not perform well in general in this study. There are
-no memory one strategies in the top 5 performing strategies
-for \(N>3\). This is due at least partly to their lack of ability to
-recognise their opponents. More sophisticated strategies
-prove to be high performers for invasion: these are infinite memory strategies
-which have been trained using a number of reinforcement learning algorithms.
-Interestingly they have been trained to perform well in tournaments and not
-Moran processes which highlights the potential for improvement.
+Memory one strategies do not perform as well as longer memory strategies in general
+in this study. Several longer memory strategies were high performers for invasion,
+particularly the strategies which have been trained using a number of reinforcement
+learning algorithms. Interestingly they have been trained to perform well in
+tournaments and not Moran processes specifically. In some cases these strategies
+utilize all the history of play (the neural network strategies and the lookup
+table strategies, the latter using the first round and some number of trailing rounds).
+
+There are no memory one strategies in the top 5 performing strategies
+for \(N>3\). Training memory-one strategies specifically for the Moran process
+typically led to Grudger / Grim, a memory-one strategy with
+four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
+The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
+training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
+For comparison, training for maximum score difference between the player and the
+opponent resulted in a strategy nearly the same as Grudger, with four-vector
+$(0.9459, 0, 0, 0)$ (not included in the study).
 

### 2017-07-19 main.tex
Add affiliation and links to data.
Still need to reference ml paper once it's on the arxiv.

@@
 \usepackage{algorithm,algorithmic}
+\usepackage{authblk}
 
@@
        Mechanisms: an empirical study of the Moran process for the iterated
-       Prisoner's dilemma using reinforcement learning}
-\author{Vincent Knight \and
-        Marc Harper \and
-        Nikoleta E. Glynatsi \and
-        Owen Campbell} % TODO Authors?
+       Prisoner's dilemma}
+\author[1]{Vincent Knight}
+\author[2]{Marc Harper}
+\author[1]{Nikoleta E. Glynatsi}
+\author[3]{Owen Campbell}
+
+\affil[1]{Cardiff University, School of Mathematics, UK}
+\affil[2]{Google Inc., Mountain View, CA, USA}
+\affil[3]{Not affiliated}
+
 \date{}
@@
  of these strategies in IPD tournaments will be described in upcoming manuscript(s).
-% TODO Think of how to reference this upcoming manuscript
+% TODO Reference ml paper on arxiv.
 
@@
 \subsection{Data collection}\label{sec:data_collection}
-
-% Todo: verify 1000 repetitions
 
@@
 
-This section outlines the data analysis carried out:
+This section outlines the data analysis carried out, all data for this study is
+available at~\cite{data}:
 

### 2017-07-20 main.tex

--- 2017-07-16 main.tex
@@
        Mechanisms: an empirical study of the Moran process for the iterated
-       Prisoner's dilemma using reinforcement learning}
+       Prisoner's dilemma}
 \author{Vincent Knight \and

### 2017-07-21 main.tex

--- 2017-07-19 main.tex
@@
 \usetikzlibrary{calc, shapes, patterns}
-
-\usepackage[backend=biber, firstinits=false, backref=false, url=true,
-            isbn=true, style=numeric]{biblatex}
-\addbibresource{./tex/bibliography.bib}
 
@@
 \cite{axelrodproject} and a detailed description of the performance
- of these strategies in IPD tournaments will be described in upcoming manuscript(s).
-% TODO Reference ml paper on arxiv.
+of these strategies in IPD tournaments is described in~\cite{Harper2017}.
 
@@
 
-\printbibliography
+\bibliographystyle{plain}
+\bibliography{./tex/bibliography.bib}
 

### 2017-07-28 main.tex
Minor modification to the bibliography.
Resize everything so that it fits in IEEE sty

@@
-\documentclass{article}
+\documentclass[10pt,journal]{IEEEtran}
 
@@
 This manuscript provides a detailed numerical analysis of agent-based simulations
-of \textbf{\input{./tex/num_strategies.tex}}complex and adaptive strategies for the
+of \textbf{\input{tex/num_strategies.tex}}complex and adaptive strategies for the
 IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
 effort to provide software for reproducible research for the IPD\@. The library
-now contains over \input{./tex/num_strategies_axelrod.tex}parameterized
+now contains over \input{tex/num_strategies_axelrod.tex}parameterized
 strategies including classics like TitForTat and WinStayLoseShift, as well as
@@
     \centering
-    \input{./tex/moran_process.tex}
+    \scalebox{.5}{ \input{tex/moran_process.tex}}
     \caption{A diagrammatic representation of a Moran process.}
@@
 
-To carry out this numerical experiment, \input{./tex/num_strategies}
+To carry out this numerical experiment, \input{tex/num_strategies}
 strategies, listed (with their properties) in Appendix~\ref{app:list_of_players},
 are used from the Axelrod library. There are
-\input{./tex/num_stochastic.tex}stochastic and
-\input{./tex/num_deterministic.tex}deterministic strategies. Their memory depth,
+\input{tex/num_stochastic.tex}stochastic and
+\input{tex/num_deterministic.tex}deterministic strategies. Their memory depth,
 defined by the number of rounds of history used by the strategy each round, is
@@
     \centering
-    \input{./tex/fsm_one.tex}
+    \scalebox{.5}{\input{tex/fsm_one.tex}}
     \caption{TF1: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \input{./tex/fsm_two.tex}
+    \scalebox{.5}{\input{tex/fsm_two.tex}}
     \caption{TF2: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \input{./tex/fsm_three.tex}
+    \input{tex/fsm_three.tex}
     \caption{TF3: an 8 state finite state machine.}
@@
     \centering
-        \input{./tex/memory_depth_count.tex}
+        \scalebox{0.7}{\input{tex/memory_depth_count.tex}}
         \caption{Memory depth}
@@
         \label{alg:data_collection}
-        \input{./tex/data_collection.tex}
+        \input{tex/data_collection.tex}
 \end{algorithm}
@@
         \label{alg:moran_process}
-        \input{./tex/moran_process_simulation.tex}
+        \input{tex/moran_process_simulation.tex}
 \end{algorithm}
@@
     \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_Cooperator.pdf}
         \caption{Alternator and Cooperator}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Alternator.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_Alternator.pdf}
         \caption{Defector and Alternator}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_TfT.pdf}
         \caption{Alternator and Tit For Tat}
@@
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Cooperator_v_TfT.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Cooperator_v_TfT.pdf}
         \caption{Cooperator and Tit For Tat}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_Cooperator.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_Cooperator.pdf}
         \caption{Defector and Cooperator}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_TfT.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_TfT.pdf}
         \caption{Defector and Tit For Tat}
@@
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/WSLS_v_TfT.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WSLS.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_WSLS.pdf}
         \caption{Alternator and Win Stay Lose Shift}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_WSLS.pdf}
         \caption{Defector and Win Stay Lose Shift}
@@
     \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_Cooperator.pdf}
         \caption{Random and Cooperator}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Defector.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_Defector.pdf}
         \caption{Random and Defector}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_TfT.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_TfT.pdf}
         \caption{Random and Tit For Tat}
@@
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Cooperator.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
         \caption{All C or all D and Cooperator}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_Defector.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Defector.pdf}
         \caption{All C or all D and Defector}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Random.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Random.pdf}
         \caption{Calculator and Random}
@@
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Calculator_v_ALLCorALLD.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
         \caption{Calculator and All C or all D}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Calculator_v_Arrogant_QLearner.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
         \caption{Calculator and Arrogant Q learner}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/ALLCorALLD_v_TfT.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
         \caption{All C or all D and Tit For Tat}
@@
 \begin{figure}[!hbtp]
-    \begin{subfigure}{.5\textwidth}
-        \centering
-        \includegraphics[height=.7\textheight]{./img/boxplot_2_invade.pdf}
+    \begin{subfigure}{.5\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_2_invade.pdf}
         \caption{The fixation probabilities for \(N=2\)}
@@
     ~
-    \begin{subfigure}{.5\textwidth}
+    \begin{subfigure}{.5\columnwidth}
         \scriptsize
         \centering
-        \input{./tex/summary_top_2_invade.tex}
+        \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
         \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
@@
     \centering
-    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
+    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_invade.pdf}
     \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
@@
     \centering
-    \begin{subfigure}{.3\textwidth}
-        \centering
-        \includegraphics[height=.9\textheight]{./img/boxplot_3_invade.pdf}
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_3_invade.pdf}
         \caption{\(N=3\)}
@@
     ~
-    \begin{subfigure}{.3\textwidth}
-        \centering
-        \includegraphics[height=.9\textheight]{./img/boxplot_7_invade.pdf}
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_7_invade.pdf}
         \caption{\(N=7\)}
@@
     ~
-    \begin{subfigure}{.3\textwidth}
-        \centering
-        \includegraphics[height=.9\textheight]{./img/boxplot_14_invade.pdf}
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_14_invade.pdf}
         \caption{\(N=14\)}
@@
     \scriptsize
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \input{./tex/summary_top_3_invade.tex}
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \input{tex/summary_top_3_invade.tex}
         \caption{\(N=3\)}
     \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \input{./tex/summary_top_7_invade.tex}
+
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \input{tex/summary_top_7_invade.tex}
         \caption{\(N=7\)}
@@
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \input{./tex/summary_top_14_invade.tex}
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \input{tex/summary_top_14_invade.tex}
         \caption{\(N=14\)}
@@
     \centering
-    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
+    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_resist.pdf}
     \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
@@
     \centering
-    \begin{subfigure}{.3\textwidth}
-        \centering
-        \includegraphics[height=.9\textheight]{./img/boxplot_3_resist.pdf}
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_3_resist.pdf}
         \caption{\(N=3\)}
@@
     ~
-    \begin{subfigure}{.3\textwidth}
-        \centering
-        \includegraphics[height=.9\textheight]{./img/boxplot_7_resist.pdf}
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_7_resist.pdf}
         \caption{\(N=7\)}
@@
     ~
-    \begin{subfigure}{.3\textwidth}
-        \centering
-        \includegraphics[height=.9\textheight]{./img/boxplot_14_resist.pdf}
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_14_resist.pdf}
         \caption{\(N=14\)}
@@
     \centering
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \input{./tex/summary_top_3_resist.tex}
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \input{tex/summary_top_3_resist.tex}
         \caption{\(N=3\)}
     \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \input{./tex/summary_top_7_resist.tex}
+
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \input{tex/summary_top_7_resist.tex}
         \caption{\(N=7\)}
@@
 
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \input{./tex/summary_top_14_resist.tex}
+    \begin{subfigure}[t]{\columnwidth}
+        \centering
+        \input{tex/summary_top_14_resist.tex}
         \caption{\(N=14\)}
@@
     \scriptsize
-    \input{./tex/change_of_rank_invade.tex}
+    \scalebox{0.7}{\input{tex/change_of_rank_invade.tex}}
     \caption{Invasion: Fixation ranks of some strategies according to \(x_1\) for different
@@
     \scriptsize
-    \input{./tex/change_of_rank_resist.tex}
+    \scalebox{0.7}{\input{tex/change_of_rank_resist.tex}}
     \caption{Resistance: Fixation ranks of some strategies according to \(x_{N-1}\) for different
@@
     \centering
-    \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_coexist.pdf}
+    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_coexist.pdf}
     \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
@@
     \scriptsize
-    \input{./tex/change_of_rank_coexist.tex}
+    \input{tex/change_of_rank_coexist.tex}
     \caption{Ranks of some strategies according to \(x_{N/2}\) for different
@@
     \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{./img/correlation_heatmap_invade.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_invade.pdf}
         \caption{Rank based on \(x_1\)}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{./img/correlation_heatmap_resist.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_resist.pdf}
         \caption{Rank based on \(x_{N - 1}\)}
@@
     ~
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.9\textwidth]{./img/correlation_heatmap_coexist.pdf}
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_coexist.pdf}
         \caption{Rank based on \(x_{N/2}\)}
@@
     \centering
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF1_array.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF1_array.pdf}
         \caption{TF1}
@@
     ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF2_array.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF2_array.pdf}
         \caption{TF2}
@@
 
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF3_array.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF3_array.pdf}
         \caption{TF3}
@@
     ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_CS_array.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_CS_array.pdf}
         \caption{CS}
@@
 
+\newpage
 \bibliographystyle{plain}
-\bibliography{./tex/bibliography.bib}
+\bibliography{tex/bibliography.bib}
 
@@
 
-\begin{multicols}{2}
 \begin{enumerate}
-		\input{./tex/list_of_players.tex}
+    \input{tex/list_of_players.tex}
 \end{enumerate}
-\end{multicols}
 

### 2017-07-28 main.tex
Fix typos

--- 2017-07-20 main.tex
@@
 % Title
-\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
-       Mechanisms: an empirical study of the Moran process for the iterated
-       Prisoner's dilemma}
+\title{An Empirical Study of Invasion and Resistance
+       for Iterated Prisoner's Dilemma Strategies}
+\title{Evolving Invaders and Resistors for the Iterated Prisoner's Dilemma}
 \author{Vincent Knight \and
@@
     mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake mechanisms.
+    to maximize total payoff while the best resistors invoke handshake machanisms.
     This suggests that while maximizing individual payoff
@@
 The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
-used to model a variety of strategic interactions. Each player chooses
-simultaneously and independently
-between cooperation (C) or defection (D). The payoffs of
+used to model a large variety of strategic interactions. Each player can choose
+between cooperation (C) or defection (D). The decisions are made simultaneously
+and independently. The payoffs of
 the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
@@
 round game, but is commonly studied in a manner where the prior outcomes
-matter. This repeated form is called the Iterated Prisoner's
+matter. This extended form is called the Iterated Prisoner's
 Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
 number of strategies have been developed to take advantage of the history of
-play. Recently, some strategies referred to as zero determinant (ZD) strategies
+play. Recently, some strategies referred to as zero Determinant strategies
 \cite{Press2012} can manipulate some players through extortionate mechanisms.
@@
 \cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
-or are limited to classes of strategies
+and/or do not consider sophisticated behaviour: only considering strategies that
+either cooperate or defect, or are limited to classes of strategies
 such as memory-one strategies that only use the previous round of play.
@@
 and others that have a high
-computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 50 contributors from around the
+computational run time. The large number of strategies is available thanks to
+the open source nature of the project with over 40 contributors from around the
 world, made by programmers and researchers \cite{Knight2016}. Three of the considered
 strategies are finite state machines trained specifically for Moran processes
-(described further in Section~\ref{sec:strategies}).
+(described further in Section~\ref{sec:strategies}.
 
@@
 swarm algorithms) that are among the best invaders and resistors of invasion
-known to date, and show that handshaking mechanisms naturally arise from these
+known to date, and show that handshaking mechanims naturally arise from these
 processes as an invasion-resistance mechanism.
@@
      through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or have a handshake mechanism.
+ \item Strong resistors specifically evolve or have a handshake mechanism.
  \item Strong invaders are generally cooperative strategies that do not defect
  first but retaliate to varying degrees of intensity against strategies that defect.
- \item Strategies evolved to maximize their total payoff can be strong invaders
+ \item Strategies evolved to maximize their total payout can be strong invaders
  and achieve mutual cooperation with many other strategies.
@@
 state where the population is entirely made up of players of one strategy. The
-probability with which a given strategy takes over a population is called the
+probability with which a given strategy takes over a the population is called the
 \textit{fixation probability}. A more detailed analytic description of this is
@@
     \input{./tex/moran_process.tex}
-    \caption{A diagrammatic representation of a Moran process.}
+    \caption{A diagrammatic representation of a Moran process}
     \label{fig:moran_process}
@@
 emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider relatively simple strategies. Some work has
-looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
+However these works mainly consider non-sophisticated strategies. Some work has
+looked at evolutionary stability of strategies within the Prisoner's Dilemma
 \cite{Li2014} but this is not done in the more widely used setting of the Moran
@@
 Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies: strategies that recall
+strategies. The subset included memory one strategies, strategies that recall
 the events of the previous round only.
 
-Of particular interest are the zero determinant strategies introduced in
+Of particular interest are the Zero determinant strategies introduced in
 \cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
+ZD strategies are robust against invading strategies. However, in \cite{Lee2015}
 a strategy using machine learning techniques was capable of resisting invasion
@@
 
-To carry out this numerical experiment, \input{./tex/num_strategies}
-strategies, listed (with their properties) in Appendix~\ref{app:list_of_players},
+To carry out this large numerical experiment, \input{./tex/num_strategies}
+strategies, listed (with their properties) in Appendix~\ref{app:list_of_players}
 are used from the Axelrod library. There are
@@
 strategy uses the entire history of play (whatever its length). For example, a
-strategy that utilizes a handshaking mechanism where the opponent's actions on
+strategy that utilizes a handshaking mechanism where the opponents actions on
 the first few rounds of play determines the strategies subsequent behavior would
@@
 
-Apart from the PSO Gambler strategy, which was trained using a particle swarm
+A part from the PSO Gambler strategy, which was trained using a particle swarm
 optimisation algorithm, these strategies are trained with an evolutionary
@@
 
-All of the training code is archived at \cite{marc_harper_2017_824264}. This
-software is (similarly to the Axelrod library) available on github
-\url{https://github.com/Axelrod-Python/axelrod-dojo} with documentation to
-train new strategies easily. Training
+All of the training code is available in the
+Axelrod repository with documentation to train new strategies easily. Training
+% TODO Include link etc
 typically takes less than 100 generations and can be completed within several
@@
 individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the Axelrod library:
+strategy, taken from a selection of 150 opponents from the axelrod library:
 
@@
 repetitions to estimate the absorption probabilities. The trained algorithms
-were run for fewer than 50 generations. Training data for this is available at
+were run for less than 50 generations. Training data for this is available at
 \cite{data}.
@@
 (not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism. Figure~\ref{fig:tf3} shows
-all 8 states of the strategy produced by the training process (states 3 and 8
-are not reachable).
+product of training with a Moran objective. It differs from TF1 and TF2
+by lacking a handshake mechanism.
 
 TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
-Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
+DD\@. It plays CDD against itself and then cooperates thereafter. Cooperation
 can be rescued after a failed handshake by a complex sequence of plays
-which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
-GTFT, and a few others with low probability. TF2 defects against all other
-players in the study, barring
-unusual cases arising from particular randomizations. Figure~\ref{fig:tf2} shows
-all 16 states of the strategy (states 6 and 7 are not reachable).
+which eventually results in mutual cooperation with Firm but Fair, Fortress3,
+Fortress4, and Grofman (always) and Evolved HMM 5 and GTFT (depending on the
+random seed). TF2 defects against all other players in the study, barring
+unusual cases arising from particular randomizations.
 
@@
 However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
+handshake is not permanent. Only one player (Prober 4 \cite{prison}) manages to
 achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
@@
 
-% Todo: verify 1000 repetitions
-
 Each strategy pair is run for 1000 repetitions of the Moran process to fixation
@@
 computed for each combination of starting distribution and value of \(N\).  The
-Axelrod library can carry out exact simulations of the Moran process. Since some
+axelrod library can carry out exact simulations of the Moran process. Since some
 of the strategies have a high computational cost or are stochastic, samples are
@@
 of the first strategy in a population of \(i\) individuals of the first type
-and \(N-i\) individuals of the second:
+(and \(N-i\) individuals of the second::
 
@@
 values and the line shows the theoretical value. Note that these are all
-deterministic strategies and show a perfect match between the expected value
+deterministic strategies and show a perfect match up between the expected value
 of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
+strategies pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
 stochastic strategies. These are no longer a good match which highlights the
@@
 approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
-(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
+(\ref{equ:p_stay}). Obtaining these requires particular analysis for a given
 pair and can be quite a complex endeavour for stochastic strategies with long
@@
     \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textbf{deterministic} strategies.}
+             probabilities for \textbf{deterministic} strategies}
     \label{fig:comparison_deterministic}
@@
     \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textbf{stochastic} strategies.}
+             fixation probabilities for \textbf{stochastic} strategies}
     \label{fig:comparison_stochastic}
@@
         between performance for differing population sizes as well as
-        taking a close look at zero determinant strategies \cite{Press2012}.
+        taking a close look at Zero determinant strategies \cite{Press2012}.
 \end{itemize}
@@
         handshake mechanism described above.
-    \item Defector: it always defects. Since it has no interactions with other
-        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
+    \item Defector: it always defects. As it has little potential
+        interaction with itself (recall that \(N=2\)), its
+        aggressiveness is rewarded.
     \item Aggravater, which plays like Grudger (responding to any
@@
     \item Handshake, a slightly less aggressive version of the Collective
-        Strategy \cite{robson1989}. As long as the initial sequence is played
+        strategy \cite{robson1989}. As long as the initial sequence is played
         then it cooperates. Thus it will do well in a population consisting of
@@
         \input{./tex/summary_top_2_invade.tex}
-        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
+        \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\)).}
         \label{tbl:summary_top_2}
     \end{subfigure}
-    \caption{Performance of strategies for \(N=2\).}
+    \caption{Performance of strategies for \(N=2\)}
 \end{figure}
@@
 \(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that zero determinant strategies should be
-effective for larger population sizes, but these analyses consider stationary
+the literature which suggests that zero Determinant strategies should be
+effective for larger population sizes, but these analysis consider stationary
 behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
@@
     \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
-    population sizes.}
+    \caption{Ranks of all strategies according to \(x_1\) for different
+    population sizes}
     \label{fig:ranks_v_size_invade}
@@
     \end{subfigure}
-    \caption{The fixation probabilities \(x_1\).}
+    \caption{The fixation probabilities \(x_1\)}
 \end{figure}
@@
 It can be seen that apart from CS, none of the strategies
-of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
+of Table~\ref{tbl:summary_top_2} performs well for \(N\in\{3, 7, 14\}\). The new
 top performing strategies are:
@@
     \item Prober 4, a strategy which starts with a specific 20 move sequence of
-        cooperations and defections \cite{Prison1998}. This initial sequence serves
+        cooperations and defections \cite{prison}. This initial sequence serves
         as approximate handshake.
@@
         the last 2 moves of both players to an action. The PSO gambler is a
-        stochastic version of the Lookerup which maps those states to probabilities of cooperating. The Lookerup was described in \cite{Knight2016}.
+        stochastic version which maps those states to probabilities of
+        cooperating. The lookerup was described in \cite{Knight2016}.
     \item The Evolved ANN strategies are neural networks that map a number of
@@
     \includegraphics[height=.9\textheight]{./img/average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
+    \caption{Ranks of all strategies according to \(x_{N-1}\) for different
+    population sizes}
     \label{fig:ranks_v_size_resist}
@@
     \end{subfigure}
-    \caption{The fixation probabilities \(x_{N-1}\).}
+    \caption{The fixation probabilities \(x_{N-1}\)}
 \end{figure}
@@
 Once again none of the short memory strategies from
-Section~\ref{sec:two_individuals} perform well for high \(N\).
+Section~\ref{sec:two_individuals} performs well for high \(N\).
 
@@
 is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
-handshakes for high invasion resistance. TF3 is a better total payoff maximizer
-which makes it a better invader along with the strategies
-trained to maximize total payoff since successful fitness proportionate selection
-is necessary for invasion. Training with an objective with initial population
-mix other than $(N/2, N/2)$ may favor invasion or resistance.
+emergence of handshaking mechanisms.
 
@@
 but not with other opponents. Nevertheless an evolutionary process is able to
-tunnel through the costs and risks associated to early defections to find more
+tunnel through the costs and risks associated with early defections to find more
 optimal solutions, so it is not surprising in hindsight that handshaking
@@
 To complement Figures~\ref{fig:ranks_v_size_invade}
-and~\ref{fig:ranks_v_size_resist}, Figure~\ref{fig:ranks_v_size_coexist} shows
+and~\ref{fig:ranks_v_size_resist} Figure~\ref{fig:ranks_v_size_coexist} shows
 the rank of each strategy based on \(x_{N/2}\).
@@
 
-The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
-expected since, as described in Section~\ref{sec:strategies} these strategies
-were trained in an initial population of \((N/2, N/2)\) individuals.
-
 For all starting populations
@@
 performance of a strategy in a large population from its performance in a small
-population. This is confirmed by the performance of the zero determinant strategies: while
+population.
+
+This is confirmed by the performance of the zero determinant strategies. While
 some do rank relatively highly for \(N=2\) (ZD-extort-4 has rank 16) this rank
@@
     \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
+    population sizes}
     \label{fig:ranks_v_size_coexist}
@@
     \end{subfigure}
-    \caption{Heatmap of correlation coefficients of rankings by population size.}
+    \caption{Heatmap of correlation coefficients of rankings by population size}
     \label{fig:correlation_coefficients}
@@
 cooperative strategies. TF3, which does not use a handshake, is a better invader
-than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
+than TF1 and TF2 but not as good of a resistor. Nevertheless it was the result
 of the same kind of training procceses and is a better combined invader-resistor
@@
 cooperative and are effective invaders.
-Combined with the fact that handshaking strategies are stronger resisters,
+Combined with the fact that handshaking strategies are stronger resistors,
 this suggests that while maximizing individual payoff can lead to the evolution
@@
 which always defects if the opponent defects in the first round, is effectively
-employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
-which emerged from training memory one strategies for the Moran process,
-also effectively employs a handshake of always cooperating, as it defects
-for the remainder of the match if the opponent ever defects.
-
-The insights that payoff maximizers are better invaders and that handshakers
-are better resistors suggests that a strategy
+employing a one-shot handshake of C. These insights also suggest that a strategy
 aware of the population distribution could choose to become a handshaker at
-a critical threshold and use a strategy better for invasion when in the
+a critical threshold and use a different strategy for invasion when in the
 minority. Information about the population distribution was not available
-to our strategies. Previous work has showed that strategies able to retain
-memory across matches can infer the population distribution and act in such
-a manner, resulting in a strategy effective at invasion and resistance
-\cite{Lee2015}.
+to our strategies.
 
@@
 $(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
-improvement. Any handshake more sophisticated than always cooperate necessarily involves
-a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
+improvement. Any handshake more sophisticated than C necessarily involves
+a defection. (A handshake consisting of a longer sequence of cooperations is
 effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
@@
 invaders for larger $N$ are nice strategies that do not defect before their
-opponents. This is because good invaders need to maximize match payoff to benefit
-from fitness proportionate selection,
-and so in the absence of a handshake mechanism, knowledge of the population
-distribution, or some identifying label on the opponent,
-a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping dramatically in rank
+opponents. This is because good invaders still need to cooperate with themselves,
+and so in the absense of a handshake mechanism or knowledge of the population
+distribution, a strategy must be generally cooperative. Aggressive strategies
+are only effective invaders for the smallest $N$, dropping down dramatically
 as the population size increases.
 
-We did, however, attempt to evolve CS using finite state machines and lookup table
-based players,
+We did, however, attempt to evolve CS using FSM and lookup table based players,
 which resulted in some very similar strategies. In particular we evolved a
@@
 after a correct handshake while defecting otherwise, which is quite close in
-function to CS (full grudging is not possible with a lookup table of limited
-depth).
+function to CS (full grudging is not possible with a lookup table).
 
@@
 starting values allowing the each strategy to attempt to invade the other.
-This is the largest such experiment carried out and has led to many insights.
+This is the largest such experiment carried out and has lead to many insights.
 
@@
 
-Memory one strategies do not perform as well as longer memory strategies in general
-in this study. Several longer memory strategies were high performers for invasion,
-particularly the strategies which have been trained using a number of reinforcement
-learning algorithms. Interestingly they have been trained to perform well in
-tournaments and not Moran processes specifically. In some cases these strategies
-utilize all the history of play (the neural network strategies and the lookup
-table strategies, the latter using the first round and some number of trailing rounds).
-
-There are no memory one strategies in the top 5 performing strategies
-for \(N>3\). Training memory-one strategies specifically for the Moran process
-typically led to Grudger / Grim, a memory-one strategy with
-four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
-The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
-training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
-For comparison, training for maximum score difference between the player and the
-opponent resulted in a strategy nearly the same as Grudger, with four-vector
-$(0.9459, 0, 0, 0)$ (not included in the study).
+Memory one strategies do not perform well in general in this study. There are
+no memory one strategies in the top 5 performing strategies
+for \(N>3\). This is due at least partly to their lack of ability to
+recognise their opponents. More sophisticated strategies
+prove to be high performers for invasion: these are infinite memory strategies
+which have been trained using a number of reinforcement learning algorithms.
+Interestingly they have been trained to perform well in tournaments and not
+Moran processes which highlights the potentially for improvement.
 
@@
 process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. Figure~\ref{fig:cooperation_rates} shows the cooperation
-rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study. While TF3
-does not have a strict handshake mechanism it is clear that all these strategies
-start a match by cooperating. It is then evident that TF3 cooperates more than
-the other strategies thus explaining the difference in performance. It is also
-clear that CS only cooperates with itself and Handshake: it is a very aggressive
-strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF1_array.pdf}
-        \caption{TF1}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF2_array.pdf}
-        \caption{TF2}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_TF3_array.pdf}
-        \caption{TF3}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{./img/cooperation_0_0_10000_CS_array.pdf}
-        \caption{CS}
-    \end{subfigure}
-    \caption{Cooperation rate per round (over 10000 repetitions).}
-    \label{fig:cooperation_rates}
-\end{figure}
+evolutionary process.
 
@@
 
-There are many opportunities to build on this work. In particular, an analysis
+There are many opportunities build on this work. In particular, an analysis
 of the effect of noise should offer insights regarding the stability of the findings,

### 2017-07-28 main.tex

--- 2017-07-21 main.tex
@@
 and others that have a high
-computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 50 contributors from around the
+computational run time. The large number of strategies is available thanks to
+the open source nature of the project with over 40 contributors from around the
 world, made by programmers and researchers \cite{Knight2016}. Three of the considered
@@
 
+\newpage
 \bibliographystyle{plain}

### 2017-08-09 main.tex
Fix the details about the training.

@@
 and others that have a high
-computational run time. The large number of strategies is available thanks to
-the open source nature of the project with over 40 contributors from around the
+computational run time. The large number of strategies are available thanks to
+the open source nature of the project with over 50 contributors from around the
 world, made by programmers and researchers \cite{Knight2016}. Three of the considered
@@
 \begin{itemize}
-	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per matchup
-	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per matchup
-	\item TF3 \(N=8\), 1\% noise, 100 repetitions per matchup
+	\item TF1 \(N=12\), 0\% noise.
+	\item TF2 \(N=10\), 0\% noise.
+	\item TF3 \(N=8\), 1\% noise.
 \end{itemize}
 
-Each matchup of players was run to fixation for the specified number of
-repetitions to estimate the absorption probabilities. The trained algorithms
+Each matchup of players was run to fixation to estimate the absorption
+probabilities. The trained algorithms
 were run for fewer than 50 generations. Training data for this is available at
@@
 
-Each strategy pair is run for 1000 repetitions of the Moran process to fixation
+Each strategy pair is run
 with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
@@
 It can be seen that apart from CS, none of the strategies
-of Table~\ref{tbl:summary_top_2} performs well for \(N\in\{3, 7, 14\}\). The new
+of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
 top performing strategies are:
@@
 Once again none of the short memory strategies from
-Section~\ref{sec:two_individuals} performs well for high \(N\).
+Section~\ref{sec:two_individuals} perform well for high \(N\).
 
@@
 but not with other opponents. Nevertheless an evolutionary process is able to
-tunnel through the costs and risks associated with early defections to find more
+tunnel through the costs and risks associated to early defections to find more
 optimal solutions, so it is not surprising in hindsight that handshaking
@@
 cooperative and are effective invaders.
-Combined with the fact that handshaking strategies are stronger resistors,
+Combined with the fact that handshaking strategies are stronger resisters,
 this suggests that while maximizing individual payoff can lead to the evolution

### 2017-10-23 main.tex
Make note of a variety of TODOs

--- 2017-08-09 main.tex
@@
 and~\ref{fig:tf3}).
-
-\begin{figure}[!hbtp]
-    \centering
-    \input{./tex/fsm_one.tex}
+% TODO Describe what the diagram shows
+
+\begin{figure}[!hbtp]
+    \centering
+    \scalebox{.5}{\input{tex/fsm_one.tex}}
     \caption{TF1: a 16 state finite state machine with a handshake leading to
@@
 \begin{itemize}
-	\item TF1 \(N=12\), 0\% noise.
-	\item TF2 \(N=10\), 0\% noise.
-	\item TF3 \(N=8\), 1\% noise.
+	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per matchup
+	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per matchup
+	\item TF3 \(N=8\), 1\% noise, 100 repetitions per matchup
 \end{itemize}
 
-Each matchup of players was run to fixation to estimate the absorption
-probabilities. The trained algorithms
+Each matchup of players was run to fixation for the specified number of
+repetitions to estimate the absorption probabilities. The trained algorithms
 were run for fewer than 50 generations. Training data for this is available at
@@
 
-Each strategy pair is run
+Each strategy pair is run for 1000 repetitions of the Moran process to fixation
 with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
@@
 of the strategies have a high computational cost or are stochastic, samples are
+% TODO Add a bit more clarity that the cache is indeed stochastic (although not
+% when using deterministic strategies.
 taken from a large number of match outcomes for the pairs of players for use in
@@
 and~\ref{alg:moran_process}.
+% TODO Are we clear about selection procedure?
+% TODO Specify that kill off is uniformly random.
 
@@
         \label{alg:moran_process}
-        \input{./tex/moran_process_simulation.tex}
+        \input{tex/moran_process_simulation.tex}
+        % TODO Add description of number of turns in the IPD
 \end{algorithm}
@@
 Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
+% TODO Add description of lines shown.
 values and the line shows the theoretical value. Note that these are all
@@
 at \cite{data}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
+% TODO Include a statistical test (Bonferroni)
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_Cooperator.pdf}
         \caption{Alternator and Cooperator}
@@
     \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\textwidth}
-        \centering
-        \includegraphics[width=.8\textwidth]{./img/Random_v_Cooperator.pdf}
+    % TODO DEEMED Unreadable: reduce number of images.
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_Cooperator.pdf}
         \caption{Random and Cooperator}
@@
     \label{fig:comparison_stochastic}
+    % TODO DEEMED Unreadable: reduce number of images.
 \end{figure}
@@
     ~
-    \begin{subfigure}{.5\textwidth}
+    \begin{subfigure}{.5\columnwidth}
         \scriptsize
         \centering
-        \input{./tex/summary_top_2_invade.tex}
+        \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
         \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
+        % TODO Add more summary statistics to this measure
         \label{tbl:summary_top_2}
@@
     \caption{Performance of strategies for \(N=2\).}
+    % TODO Move the plot
+    % TODO Explain this more (see comment about error bars)
 \end{figure}
@@
     \label{fig:ranks_v_size_invade}
+    % TODO Move to online appendix
 \end{figure}
@@
     \caption{The fixation probabilities \(x_1\).}
+    % TODO Move to online appendix
 \end{figure}
@@
     \caption{The fixation probabilities \(x_{N-1}\).}
+    % TODO Move to online appendix
 \end{figure}
@@
     \label{fig:ranks_v_size_coexist}
+    % TODO Move to online appendix
 \end{figure}
@@
     \caption{Heatmap of correlation coefficients of rankings by population size.}
+    % TODO Increase font
     \label{fig:correlation_coefficients}
@@
     \caption{Cooperation rate per round (over 10000 repetitions).}
+    % TODO Make less bad. Perhaps remove names altogether.
+    % TODO Add better explanation of repetitions.
     \label{fig:cooperation_rates}
@@
 \bibliographystyle{plain}
-\bibliography{./tex/bibliography.bib}
+\bibliography{tex/bibliography.bib}
+% TODO Fix repeated item.
 
@@
 
+% TODO Reduce font
+% TODO Add number of states for FSMs
 \section{List of players}\label{app:list_of_players}
 
-\begin{multicols}{2}
 \begin{enumerate}
-		\input{./tex/list_of_players.tex}
+    \input{tex/list_of_players.tex}
 \end{enumerate}
-\end{multicols}
 

### 2017-10-23 main.tex
Make minor fixes.

@@
 \title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
-       Mechanisms: an empirical study of the Moran process for the iterated
-       Prisoner's dilemma}
+       Mechanisms: an Empirical Study of the Moran process for the Iterated
+       Prisoner's Dilemma}
+       % TODO Possibly change
 \author[1]{Vincent Knight}
@@
 number of strategies have been developed to take advantage of the history of
-play. Recently, some strategies referred to as zero determinant (ZD) strategies
+play. Recently, strategies referred to as zero determinant (ZD) strategies
 \cite{Press2012} can manipulate some players through extortionate mechanisms.
@@
      through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or have a handshake mechanism.
+ \item The strongest resistors specifically evolve or possess a handshake mechanism.
  \item Strong invaders are generally cooperative strategies that do not defect
@@
 emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider relatively simple strategies. Some work has
+However these works mainly consider relatively simple strategies. A few works 
 looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
@@
 All of the training code is archived at \cite{marc_harper_2017_824264}. This
-software is (similarly to the Axelrod library) available on github
-\url{https://github.com/Axelrod-Python/axelrod-dojo} with documentation to
+software is (similarly to the Axelrod library) available on 
+github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}} 
+with documentation to
 train new strategies easily. Training
@@
 Section~\ref{sec:validation} will further validate the methodology by comparing
-simulated results to analytical results in some cases. The main results of this
+simulated results to analytical results in a few selected cases. The main 
+results of this
 manuscript are presented in Section~\ref{sec:empirical_results} which will
@@
 
-Using this it is a known result \cite{Nowak2017} that the fixation probability
+Using this the fixation probability
 of the first strategy in a population of \(i\) individuals of the first type
-and \(N-i\) individuals of the second:
+and \(N-i\) individuals of the second, is given by \cite{Nowak2017}:
 
@@
 stochastic strategies. These are no longer a good match which highlights the
+% TODO Rephrase this sentence: possibly when doing the statistical test
 weakness of assuming a given interaction between two IPD strategies can be
@@
         difference is that CS will defect after the handshake if the opponent
-        defects while handshake will not.
+        defects while Handshake will not.
 \end{enumerate}
@@
 
-The top 16 strategies are given in Tables~\ref{tbl:top_invade}.
+The top 16 strategies are given in Table~\ref{tbl:top_invade}.
 
@@
 
-There are are only two new strategies that appear in the top ranks for
+There are only two new strategies that appear in the top ranks for
 \(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
@@
 difference depending on whether or not \(N>2\). This will be explored further in
-the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also consider
+the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also
+considering
 \(x_{N/2}\).
@@
     \scalebox{0.7}{\input{tex/change_of_rank_invade.tex}}
-    \caption{Invasion: Fixation ranks of some strategies according to \(x_1\) for different
+    \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
     population sizes}
@@
     \scalebox{0.7}{\input{tex/change_of_rank_resist.tex}}
-    \caption{Resistance: Fixation ranks of some strategies according to \(x_{N-1}\) for different
+    \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
     population sizes}
@@
     \input{tex/change_of_rank_coexist.tex}
-    \caption{Ranks of some strategies according to \(x_{N/2}\) for different
+    \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
     population sizes}
@@
 
-Figure~\ref{fig:correlation_coefficients} show the correlation coefficients
+Figure~\ref{fig:correlation_coefficients} shows the correlation coefficients
 of the ranks of strategies in differing population size. How well a strategy
@@
 than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
-of the same kind of training procceses and is a better combined invader-resistor
+of the same kind of training processes and is a better combined invader-resistor
 than the invaders that were trained previously to maximize payout.
@@
 ordered pairs of strategies have been placed in a Moran process with different
-starting values allowing the each strategy to attempt to invade the other.
+starting values allowing each strategy to attempt to invade the other.
 This is the largest such experiment carried out and has led to many insights.

### 2017-10-24 src/validate.py
Modify validation to carry out 1 sided t test.

@@ -13,6 +13,8 @@ import functools
 import multiprocessing
 import itertools
 
+from scipy import stats
+
 
 def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
                        cachefile=None):
@@ -31,15 +33,13 @@ def simulated_fixation(strategy_pair, N, i=1, repetitions=10,
         players.append(strategy_pair[1])
     mp = axl.ApproximateMoranProcess(players, cached_outcomes=cache)
 
-    win_count = 0
+    wins = []
     for seed in range(repetitions):
         axl.seed(seed)
         mp.reset()
         mp.play()
-        if mp.winning_strategy_name == str(players[0]):
-            win_count += 1
-
-    return win_count / repetitions
+        wins.append(int(mp.winning_strategy_name == str(players[0])))
+    return wins
 
 
 def theoretic_vs_simulated(repetitions, utilities, filename,
@@ -54,11 +54,15 @@ def theoretic_vs_simulated(repetitions, utilities, filename,
     for i in starting_pop:
         player_names = [str(p) for p in players]
         t = theoretic.fixation(player_names, N, i, utilities=utilities)
-        s = simulated_fixation(players,  N, i, repetitions=repetitions)
+        simulated_wins = simulated_fixation(players,  N, i, repetitions=repetitions)
+        s = sum(simulated_wins) / repetitions
+
+        test = stats.ttest_1samp(simulated_wins, t)
+        p = test.pvalue
 
         with open(filename, "a") as f:
             writer = csv.writer(f)
-            writer.writerow([repetitions, N, i, *player_names, t, s])
+            writer.writerow([repetitions, N, i, *player_names, t, s, p])
 
 
 if __name__ == "__main__":
@@ -66,7 +70,7 @@ if __name__ == "__main__":
     outcomes_file = "../data/outcomes.csv"
     output_file = "../data/fixation_validation.csv"
     with open(output_file, "w") as f:
-        f.write("Repetitions,N,i,Player 1,Player 2,Theoretic,Simulated\n")
+        f.write("Repetitions,N,i,Player 1,Player 2,Theoretic,Simulated,p Value\n")
 
     player_pairs = [(axl.Defector(), axl.Defector()),
                     (axl.Defector(), axl.Alternator()),

### 2017-10-24 main.tex
Reduce number of validation plots.
This is to improve the quality of these plots.
Have also added a sentence specifically describing which line is which.

@@
        Prisoner's Dilemma}
-       % TODO Possibly change
 \author[1]{Vincent Knight}
@@
 Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
-% TODO Add description of lines shown.
+Figure~\ref{fig:comparison_deterministic}. 
+The top most line on all figures (in red and using a circle) corresponds to
+\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
+\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
+\(X_{1}\).
+The points represent the simulated
 values and the line shows the theoretical value. Note that these are all
@@
 at \cite{data}.
-% TODO Include a statistical test (Bonferroni)
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Alternator_v_Cooperator.pdf}
+% TODO Include a statistical test (1 sided t test)
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/Alternator_v_Cooperator.pdf}
         \caption{Alternator and Cooperator}
@@
     ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Defector_v_Alternator.pdf}
-        \caption{Defector and Alternator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Alternator_v_TfT.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/Alternator_v_TfT.pdf}
         \caption{Alternator and Tit For Tat}
@@
 
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Cooperator_v_TfT.pdf}
-        \caption{Cooperator and Tit For Tat}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Defector_v_Cooperator.pdf}
-        \caption{Defector and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Defector_v_TfT.pdf}
-        \caption{Defector and Tit For Tat}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/WSLS_v_TfT.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/WSLS_v_TfT.pdf}
         \caption{Win Stay Lose Shift and Tit For Tat}
@@
     ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Alternator_v_WSLS.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
         \caption{Alternator and Win Stay Lose Shift}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Defector_v_WSLS.pdf}
-        \caption{Defector and Win Stay Lose Shift}
     \end{subfigure}%
@@
     \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Random_v_Cooperator.pdf}
-        \caption{Random and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Random_v_Defector.pdf}
-        \caption{Random and Defector}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Random_v_TfT.pdf}
-        \caption{Random and Tit For Tat}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
+
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
         \caption{All C or all D and Cooperator}
@@
     ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Defector.pdf}
-        \caption{All C or all D and Defector}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Random.pdf}
-        \caption{Calculator and Random}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
         \caption{Calculator and All C or all D}
     \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
+
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
         \caption{Calculator and Arrogant Q learner}
@@
     ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
+    \begin{subfigure}[t]{.5\columnwidth}
+        \centering
+        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
         \caption{All C or all D and Tit For Tat}

### 2017-10-24 tex/list_of_players.tex
Update grudger memory depth
Add state number to appendix for FSM players
Note that this is not necessarily the smallest number of states. That in
itself is a harder problem.

@@
 \item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
-\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16. \cite{axelrodproject}
-\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{axelrodproject}
+\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
+\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
+\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
 \item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
@@
 \item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\).
+\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
+\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
+\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
 \item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980}
@@
 \item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2006b}
-\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4. \cite{Ashlock2006b}
+\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006b}
+\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006b}
 \item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
@@
 \item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
-\item Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}
+\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980, Banks1990, Beaufils1997, Berg2015, Li2011}
 \item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
@@
 \item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9. \cite{Ashlock2006b}
+\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006b}
 \item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
@@
 \item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2006}
+\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
 \item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2014}
+\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
 \item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
@@
 \item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980}
-\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
+\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
 \item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
@@
 \item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
-\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Ashlock2015}
-\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{Ashlock2015}
+\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
+\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
 \item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
@@
 \item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Ashlock2008}
+\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
 \item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}

### 2017-10-24 main.tex
Add more summary statistics.
Have also moved the images out to make room.
Add state number to appendix for FSM players
Note that this is not necessarily the smallest number of states. That in
itself is a harder problem.
Increase font of correlation heatmaps.

@@
     \label{fig:comparison_deterministic}
-    % TODO DEEMED Unreadable: reduce number of images.
 \end{figure}
@@
     \label{fig:comparison_stochastic}
-    % TODO DEEMED Unreadable: reduce number of images.
 \end{figure}
@@
 probabilities for the strategies considered. The top 16 (10\%) strategies are
+% TODO Fix (have removed plot)
 shown in
@@
 
-\begin{figure}[!hbtp]
-    \begin{subfigure}{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_2_invade.pdf}
-        \caption{The fixation probabilities for \(N=2\)}
-        \label{fig:boxplot_2}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}{.5\columnwidth}
-        \scriptsize
+\begin{table}[!hbtp]
+    \tiny
     \centering
@@
     \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
-        % TODO Add more summary statistics to this measure
     \label{tbl:summary_top_2}
-    \end{subfigure}
-    \caption{Performance of strategies for \(N=2\).}
-    % TODO Move the plot
     % TODO Explain this more (see comment about error bars)
-\end{figure}
+\end{table}
 
@@
     \centering
-    \scriptsize
+    \tiny
     \begin{subfigure}[t]{\columnwidth}
@@
 \begin{table}[!hbtp]
-    \scriptsize
+    \tiny
     \centering
@@
         \centering
-        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_invade.pdf}
+        \includegraphics[width=\columnwidth]{img/correlation_heatmap_invade.pdf}
         \caption{Rank based on \(x_1\)}
@@
         \centering
-        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_resist.pdf}
+        \includegraphics[width=\columnwidth]{img/correlation_heatmap_resist.pdf}
         \caption{Rank based on \(x_{N - 1}\)}
@@
         \centering
-        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_coexist.pdf}
+        \includegraphics[width=\columnwidth]{img/correlation_heatmap_coexist.pdf}
         \caption{Rank based on \(x_{N/2}\)}
@@
     \caption{Heatmap of correlation coefficients of rankings by population size.}
-    % TODO Increase font
     \label{fig:correlation_coefficients}
@@
 
-% TODO Reduce font
-% TODO Add number of states for FSMs
 \section{List of players}\label{app:list_of_players}
 
+\footnotesize
 \begin{enumerate}

### 2017-10-24 main.tex
Create online materials with all plots.
This moves all the plots to a separate file. Have made font larger where
possible.

@@
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_invade}
-    % TODO Move to online appendix
-\end{figure}
-
 The fixation
@@
 fixation as well as the neutral fixation for each given scenario.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_3_invade.pdf}
-        \caption{\(N=3\)}
-        \label{fig:boxplot_3_invade}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_7_invade.pdf}
-        \caption{\(N=7\)}
-        \label{fig:boxplot_7_invade}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_14_invade.pdf}
-        \caption{\(N=14\)}
-        \label{fig:boxplot_14_invade}
-    \end{subfigure}
-    \caption{The fixation probabilities \(x_1\).}
-    % TODO Move to online appendix
-\end{figure}
 
@@
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
-
 The fixation probabilities are shown in
@@
 fixation as well as the neutral fixation for each given scenario.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_3_resist.pdf}
-        \caption{\(N=3\)}
-        \label{fig:boxplot_3_resist}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_7_resist.pdf}
-        \caption{\(N=7\)}
-        \label{fig:boxplot_7_resist}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{img/boxplot_14_resist.pdf}
-        \caption{\(N=14\)}
-        \label{fig:boxplot_14_resist}
-    \end{subfigure}
-    \caption{The fixation probabilities \(x_{N-1}\).}
-    % TODO Move to online appendix
-\end{figure}
 
@@
 \end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_coexist.pdf}
-    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_coexist}
-    % TODO Move to online appendix
-\end{figure}
 

### 2017-10-30 main.tex
Add p values of a t test.

@@
 Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Figure~\ref{fig:comparison_deterministic}. 
+Figure~\ref{fig:comparison_deterministic} for Alternator and WSLS.
 The top most line on all figures (in red and using a circle) corresponds to
@@
 The points represent the simulated
-values and the line shows the theoretical value. Note that these are all
-deterministic strategies and show a perfect match between the expected value
+values and the line shows the theoretical value. Note that these are 
+deterministic strategies and show a good match between the expected value
 of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies. These are no longer a good match which highlights the
-% TODO Rephrase this sentence: possibly when doing the statistical test
-weakness of assuming a given interaction between two IPD strategies can be
-summarised with a set of utilities as shown in
-(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
-obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
-approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
-(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
-pair and can be quite a complex endeavour for stochastic strategies with long
-memory: this is not necessary for the purposes of this work.
-All data generated for this validation exercise can be found
-at \cite{data}.
-% TODO Include a statistical test (1 sided t test)
+strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
+values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
+fact that the theoretic and simulated values are a good match.
+
+Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
+stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
+good match (confirmed with a \(t\)-test in
+Table~\ref{tab:comparison_stochastic}) which highlights the weakness of assuming
+a given interaction between two IPD strategies can be summarised with a set of
+utilities as shown in (\ref{equ:payoff_matrix}). For any given pair of
+strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
+opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
+and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
+given pair and can be quite a complex endeavour for stochastic strategies with
+long memory: this is not necessary for the purposes of this work.  All data
+generated for this validation exercise can be found at~\cite{data}.
 
@@
     \centering
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=.95\columnwidth]{img/Alternator_v_Cooperator.pdf}
-        \caption{Alternator and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=.95\columnwidth]{img/Alternator_v_TfT.pdf}
-        \caption{Alternator and Tit For Tat}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=.95\columnwidth]{img/WSLS_v_TfT.pdf}
-        \caption{Win Stay Lose Shift and Tit For Tat}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
     \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
-        \caption{Alternator and Win Stay Lose Shift}
-    \end{subfigure}%
     \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textbf{deterministic} strategies.}
+             probabilities for \textbf{deterministic} strategies: Alternator and
+             Cooperator.}
     \label{fig:comparison_deterministic}
@@
 
+\begin{table}[!hbtp]
+    \centering
+    \input{tex/t_test_results_alternator_v_wsls.tex}
+    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
+        value with the simulated value of the Moran Process fixation
+        probabilities for \textbf{deterministic} strategies: Alternator and
+    Cooperator.}
+    \label{tab:comparison_deterministic}
+\end{table}
+
 \begin{figure}[!hbtp]
     \centering
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
-        \caption{All C or all D and Cooperator}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=.95\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
-        \caption{Calculator and All C or all D}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
     \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
-        \caption{Calculator and Arrogant Q learner}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=.95\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
-        \caption{All C or all D and Tit For Tat}
-    \end{subfigure}%
     \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textbf{stochastic} strategies.}
+             fixation probabilities for \textbf{stochastic} strategies:
+             Calculator and Arrogant Q Learner.}
     \label{fig:comparison_stochastic}
 \end{figure}
+
+\begin{table}[!hbtp]
+    \centering
+    \input{tex/t_test_results_calculator_v_arrogant_q_learner.tex}
+    \caption{\(p\) values resulting from a \(t\) test comparing the theoretic
+        value with the simulated value of the Moran Process fixation
+        probabilities for \textbf{stochastic} strategies: Calculator and
+    Arrogant Q Learner.}
+    \label{tab:comparison_stochastic}
+\end{table}
 

### 2017-10-30 main.tex
Include better explanation of the Moran details

@@
 simulations can provide insights in evolutionary game theory not available
-via direct mathematical analysis \cite{adami2016evolutionary}. The results
+via direct mathematical analysis~\cite{adami2016evolutionary}. The results
 and insights contained in this paper would be difficult to derive analytically.
@@
 reproduced and similarly another individual is chosen to be removed from the
-population. In some settings mutation is also considered but without mutation
+population (a uniform random selection is used). In some settings mutation is 
+also considered but without mutation
 (the case considered in this work) this process will arrive at an absorbing
@@
 methods appear in the literature \cite{Ashlock2006}.
+There has also been some work on strategies using an evolutionary in real time: 
+in~\cite{Gaudesi2016}
+an evolutionary algorithm is used to build a model of the opponent and attempt
+to exploit any potential weakness. This sort of work is not considered here:
+strategies are instead pre trained.
 
@@
 FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively (see Figures~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}).
-% TODO Describe what the diagram shows
+and 8 states respectively. These are shown in Figures~\ref{fig:tf1},~\ref{fig:tf2}
+and~\ref{fig:tf3}), using the notation common in the literature where
+\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
+\(A_2\) as well as arrows corresponding to changes of state.
 
@@
     \centering
-    \scalebox{.5}{\input{tex/fsm_one.tex}}
+    \scalebox{.7}{\input{tex/fsm_one.tex}}
     \caption{TF1: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \scalebox{.5}{\input{tex/fsm_two.tex}}
+    \scalebox{.7}{\input{tex/fsm_two.tex}}
     \caption{TF2: a 16 state finite state machine with a handshake leading to
@@
 of the strategies have a high computational cost or are stochastic, samples are
-% TODO Add a bit more clarity that the cache is indeed stochastic (although not
-% when using deterministic strategies.
-taken from a large number of match outcomes for the pairs of players for use in
-computing fitnesses in the Moran process. This approach was verified to agree
-with unsampled calculations to a high degree of accuracy in specific cases.
-This is described in Algorithms~\ref{alg:data_collection}
-and~\ref{alg:moran_process}.
-% TODO Are we clear about selection procedure?
-% TODO Specify that kill off is uniformly random.
+taken from a large number of 200 turn match outcomes for the pairs of players
+for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
+matches is used). This approach was verified to agree with unsampled
+calculations to a high degree of accuracy in specific cases.  This is described
+in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.
 
@@
         \input{tex/moran_process_simulation.tex}
-        % TODO Add description of number of turns in the IPD
 \end{algorithm}

### 2017-10-31 main.tex
Add error bars to validation plots.

@@
 Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Figure~\ref{fig:comparison_deterministic} for Alternator and WSLS.
+Figure~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
+confidence interval computed using an asymptotic normal approximation is also
+included \cite{brown2001interval}).
 The top most line on all figures (in red and using a circle) corresponds to
@@
              probabilities for \textbf{deterministic} strategies: Alternator and
-             Cooperator.}
+         Cooperator. 5\% confidence intervals calculated using an asymptotic
+     normal approximation.}
     \label{fig:comparison_deterministic}
@@
              fixation probabilities for \textbf{stochastic} strategies:
-             Calculator and Arrogant Q Learner.}
+             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
+     normal approximation.}
     \label{fig:comparison_stochastic}
@@
     \end{subfigure}
-    \caption{Cooperation rate per round (over 10000 repetitions).}
-    % TODO Make less bad. Perhaps remove names altogether.
+    \caption{Cooperation rate per round (over 10000 repetitions). Rows
+        correspond to all the strategies considered in this work (ordered
+    alphabetically by name).}
     % TODO Add better explanation of repetitions.

### 2017-10-31 main.tex
Add better explanation of the cooperation rates.
Also remove the names from the plot.

--- 2017-10-30 main.tex
@@
        Prisoner's Dilemma}
+       % TODO Possibly change
 \author[1]{Vincent Knight}
@@
 Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Figure~\ref{fig:comparison_deterministic} for Alternator and WSLS.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(X_{1}\).
-The points represent the simulated
-values and the line shows the theoretical value. Note that these are 
-deterministic strategies and show a good match between the expected value
+Figure~\ref{fig:comparison_deterministic}. The points represent the simulated
+% TODO Add description of lines shown.
+values and the line shows the theoretical value. Note that these are all
+deterministic strategies and show a perfect match between the expected value
 of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
-values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
-fact that the theoretic and simulated values are a good match.
-
-Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
-good match (confirmed with a \(t\)-test in
-Table~\ref{tab:comparison_stochastic}) which highlights the weakness of assuming
-a given interaction between two IPD strategies can be summarised with a set of
-utilities as shown in (\ref{equ:payoff_matrix}). For any given pair of
-strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
-opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
-and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
-given pair and can be quite a complex endeavour for stochastic strategies with
-long memory: this is not necessary for the purposes of this work.  All data
-generated for this validation exercise can be found at~\cite{data}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
+strategy pairs. Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
+stochastic strategies. These are no longer a good match which highlights the
+% TODO Rephrase this sentence: possibly when doing the statistical test
+weakness of assuming a given interaction between two IPD strategies can be
+summarised with a set of utilities as shown in
+(\ref{equ:payoff_matrix}). For any given pair of strategies it is possible to
+obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as opposed to the
+approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down}) and
+(\ref{equ:p_stay})). Obtaining these requires particular analysis for a given
+pair and can be quite a complex endeavour for stochastic strategies with long
+memory: this is not necessary for the purposes of this work.
+All data generated for this validation exercise can be found
+at \cite{data}.
+% TODO Include a statistical test (Bonferroni)
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_Cooperator.pdf}
+        \caption{Alternator and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_Alternator.pdf}
+        \caption{Defector and Alternator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_TfT.pdf}
+        \caption{Alternator and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Cooperator_v_TfT.pdf}
+        \caption{Cooperator and Tit For Tat}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_Cooperator.pdf}
+        \caption{Defector and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_TfT.pdf}
+        \caption{Defector and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/WSLS_v_TfT.pdf}
+        \caption{Win Stay Lose Shift and Tit For Tat}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Alternator_v_WSLS.pdf}
+        \caption{Alternator and Win Stay Lose Shift}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Defector_v_WSLS.pdf}
+        \caption{Defector and Win Stay Lose Shift}
+    \end{subfigure}%
     \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textbf{deterministic} strategies: Alternator and
-             Cooperator.}
+             probabilities for \textbf{deterministic} strategies.}
     \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-    \input{tex/t_test_results_alternator_v_wsls.tex}
-    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textbf{deterministic} strategies: Alternator and
-    Cooperator.}
-    \label{tab:comparison_deterministic}
-\end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
+    % TODO DEEMED Unreadable: reduce number of images.
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_Cooperator.pdf}
+        \caption{Random and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_Defector.pdf}
+        \caption{Random and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Random_v_TfT.pdf}
+        \caption{Random and Tit For Tat}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Cooperator.pdf}
+        \caption{All C or all D and Cooperator}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_Defector.pdf}
+        \caption{All C or all D and Defector}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Random.pdf}
+        \caption{Calculator and Random}
+    \end{subfigure}%
+
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Calculator_v_ALLCorALLD.pdf}
+        \caption{Calculator and All C or all D}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
+        \caption{Calculator and Arrogant Q learner}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{.3\columnwidth}
+        \centering
+        \includegraphics[width=.8\columnwidth]{img/ALLCorALLD_v_TfT.pdf}
+        \caption{All C or all D and Tit For Tat}
+    \end{subfigure}%
     \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textbf{stochastic} strategies:
-             Calculator and Arrogant Q Learner.}
+             fixation probabilities for \textbf{stochastic} strategies.}
     \label{fig:comparison_stochastic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-    \input{tex/t_test_results_calculator_v_arrogant_q_learner.tex}
-    \caption{\(p\) values resulting from a \(t\) test comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textbf{stochastic} strategies: Calculator and
-    Arrogant Q Learner.}
-    \label{tab:comparison_stochastic}
-\end{table}
+    % TODO DEEMED Unreadable: reduce number of images.
+\end{figure}
 
@@
 probabilities for the strategies considered. The top 16 (10\%) strategies are
-% TODO Fix (have removed plot)
 shown in
@@
     \item Handshake, a slightly less aggressive version of the Collective
-        Strategy \cite{robson1989}. As long as the initial sequence is played
+        Strategy \cite{Robson1990}. As long as the initial sequence is played
         then it cooperates. Thus it will do well in a population consisting of
@@
 
-\begin{table}[!hbtp]
-    \tiny
+\begin{figure}[!hbtp]
+    \begin{subfigure}{.5\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_2_invade.pdf}
+        \caption{The fixation probabilities for \(N=2\)}
+        \label{fig:boxplot_2}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.5\columnwidth}
+        \scriptsize
         \centering
@@
         \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
+        % TODO Add more summary statistics to this measure
         \label{tbl:summary_top_2}
+    \end{subfigure}
+    \caption{Performance of strategies for \(N=2\).}
+    % TODO Move the plot
     % TODO Explain this more (see comment about error bars)
-\end{table}
+\end{figure}
 
@@
 
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_invade.pdf}
+    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different
+    population sizes.}
+    \label{fig:ranks_v_size_invade}
+    % TODO Move to online appendix
+\end{figure}
+
 The fixation
@@
 
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_3_invade.pdf}
+        \caption{\(N=3\)}
+        \label{fig:boxplot_3_invade}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_7_invade.pdf}
+        \caption{\(N=7\)}
+        \label{fig:boxplot_7_invade}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_14_invade.pdf}
+        \caption{\(N=14\)}
+        \label{fig:boxplot_14_invade}
+    \end{subfigure}
+    \caption{The fixation probabilities \(x_1\).}
+    % TODO Move to online appendix
+\end{figure}
+
 The top 16 strategies are given in Table~\ref{tbl:top_invade}.
@@
     \centering
-    \tiny
+    \scriptsize
     \begin{subfigure}[t]{\columnwidth}
@@
 
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_resist.pdf}
+    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
+    population sizes.}
+    \label{fig:ranks_v_size_resist}
+\end{figure}
+
 The fixation probabilities are shown in
@@
 
+\begin{figure}[!hbtp]
+    \centering
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_3_resist.pdf}
+        \caption{\(N=3\)}
+        \label{fig:boxplot_3_resist}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_7_resist.pdf}
+        \caption{\(N=7\)}
+        \label{fig:boxplot_7_resist}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}{.3\columnwidth}
+        \centering
+        \includegraphics[width=\columnwidth]{img/boxplot_14_resist.pdf}
+        \caption{\(N=14\)}
+        \label{fig:boxplot_14_resist}
+    \end{subfigure}
+    \caption{The fixation probabilities \(x_{N-1}\).}
+    % TODO Move to online appendix
+\end{figure}
+
 Table~\ref{tbl:top_resist} shows the top strategies when ranked
@@
 \begin{table}[!hbtp]
-    \tiny
+    \scriptsize
     \centering
@@
 
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{img/average_rank_vs_population_size_coexist.pdf}
+    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
+    population sizes.}
+    \label{fig:ranks_v_size_coexist}
+    % TODO Move to online appendix
+\end{figure}
+
 \begin{table}[!hbtp]
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/correlation_heatmap_invade.pdf}
+        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_invade.pdf}
         \caption{Rank based on \(x_1\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/correlation_heatmap_resist.pdf}
+        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_resist.pdf}
         \caption{Rank based on \(x_{N - 1}\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/correlation_heatmap_coexist.pdf}
+        \includegraphics[width=.9\columnwidth]{img/correlation_heatmap_coexist.pdf}
         \caption{Rank based on \(x_{N/2}\)}
@@
 
+% TODO Reduce font
+% TODO Add number of states for FSMs
 \section{List of players}\label{app:list_of_players}
 
-\footnotesize
 \begin{enumerate}

### 2017-10-31 main.tex

--- 2017-10-31 main.tex
@@
 rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study. While TF3
+for each round of a match against all the opponents in this study. 
+This corresponds to the fraction of cooperation played by that strategy observed
+in a given round (out of 200) where each matchup is repeated 10000 times to
+obtain the mean.
+
+While TF3
 does not have a strict handshake mechanism it is clear that all these strategies

### 2017-10-31 main.tex
Remove a number of references to figures.
This have been moved to the supplementary materials.

@@
 
-When $N=2$ the Moran process is effectively a measure of the distribution of relative
+When $N=2$ the Moran process is effectively a measure of the distribution of 
+relative
 mean payoffs over all possible matches between two players. The strategy
@@
 considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
-and~\ref{sec:strong_resistors}. Figure~\ref{fig:boxplot_2} shows all fixation
-probabilities for the strategies considered. The top 16 (10\%) strategies are
-% TODO Fix (have removed plot)
+and~\ref{sec:strong_resistors}. The top 16 (10\%) strategies are
 shown in
-Table~\ref{tbl:summary_top_2}. The top five ranking strategies are:
+Table~\ref{tbl:summary_top_2} and figures showing the performance of all
+strategies are available in the supplementary materials. 
+The top five ranking strategies are:
 
@@
     \label{tbl:summary_top_2}
-    % TODO Explain this more (see comment about error bars)
 \end{table}
@@
 population of \(N - 1\) other individuals, denoted by \(x_1\).
-The ranks of each strategy for all considered values of \(N\) according to mean
-\(x_1\) are shown in Figure~\ref{fig:ranks_v_size_invade}.
-
-The fixation
-probabilities are shown in
-Figures~\ref{fig:boxplot_3_invade},~\ref{fig:boxplot_7_invade}
-and~\ref{fig:boxplot_14_invade} for \(N\in\{3, 7, 14\}\) showing the mean
-fixation as well as the neutral fixation for each given scenario.
-
-The top 16 strategies are given in Table~\ref{tbl:top_invade}.
+
+The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
+figures showing the performance of all strategies is available in the
+supplementary materials.
 
@@
 other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy. The ranks of each strategy for all considered values of \(N\)
-according to mean \(x_{N-1}\) are shown in
-Figures~\ref{fig:ranks_v_size_resist}.
-
-The fixation probabilities are shown in
-Figures~\ref{fig:boxplot_3_resist},~\ref{fig:boxplot_7_invade}
-and~\ref{fig:boxplot_14_resist} for \(N\in\{3, 7, 14\}\) showing the mean
-fixation as well as the neutral fixation for each given scenario.
+each strategy.
 
 Table~\ref{tbl:top_resist} shows the top strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\).
+according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
+for all strategies are available in the supplementary materials.
 Once again none of the short memory strategies from
@@
 
-To complement Figures~\ref{fig:ranks_v_size_invade}
-and~\ref{fig:ranks_v_size_resist}, Figure~\ref{fig:ranks_v_size_coexist} shows
-the rank of each strategy based on \(x_{N/2}\).
 Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
-and~\ref{tbl:ranks_v_size_coexist} show the same information for a selection of
+and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
 strategies:
@@
     alphabetically by name).}
-    % TODO Add better explanation of repetitions.
     \label{fig:cooperation_rates}
@@
 be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
-% TODO Add reference to source code
 the processed data has also been properly archived and can be found
@@
 \bibliography{tex/bibliography.bib}
-% TODO Fix repeated item.
 

### 2017-10-31 main.tex
Minor rephrasing of a sentence.

@@
 good match (confirmed with a \(t\)-test in
-Table~\ref{tab:comparison_stochastic}) which highlights the weakness of assuming
+Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
 a given interaction between two IPD strategies can be summarised with a set of
-utilities as shown in (\ref{equ:payoff_matrix}). For any given pair of
+utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
 strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as

### 2017-10-31 response_to_reviewers.tex
Start work on response.

\documentclass[a4]{article}

\usepackage{hyperref}

\title{Response to reviews}

\begin{document}

\maketitle

\section{Comments from editor}

\begin{quote}
    Remember that it is possible to put material into an on-line appendix which
    is not page-limited if there are things you feel require more space to
    display.
\end{quote}

This is probably the most important change to the manuscript. We have moved most
of the figures to a supplementary materials document which not only allows for
them to be presented in a clearer way but also allows for all cases (variety of
population sizes) to be included.

\section{Comments from first referee}

\begin{quote}
   It's not easy to solve, so I can only point out the problems, and ask you to
   do what is possible to fix them. One possibility would be to put all figures
   in a downloadable Appendix, or some other online resource; and maybe remove
   some of the figures from the paper, in order to make more room for the
   others.
\end{quote}

Thank you for acknowledging the difficulty we're presented with. We feel that
having opted to put most of the figures in supplementary materials we arrive at
a more concise paper with much clearer plots (as they have more space).

We have also endeavoured to clear up the plots that have remained in the paper
(for example by removing cluttering labelling).

\begin{quote}
    font in the Appendix could be reduced (for example to the same size of the
    font in the references)
\end{quote}

This has been done.

\begin{quote}
    When you speak about evolutionary computation applied to the IPD, you could
    add some words about reference [21], that is otherwise only cited for GTFT.
    The basic idea of the publication was to create an EA able to adapt its
    behavior by building a model of the opponent 'online', during the game, and
    then exploiting the opponent's weaknesses. It's unpractical to use in your
    experiments (reported computational time is considerable, the technique is
    tailored for 1vs1 games as it can only model one opponent), but it could be
    interesting for the reader.
\end{quote}

Thank you for pointing this out, we have included these details in our
discussion.

\begin{quote}
- capitalization of words in the title is not consistent; why is "Emergence" with a capital "E", but "iterated" does not have a capital "I"?
\end{quote}

We have fixed this.

\begin{quote}
- page 1
	-- Recently, some strategies...can manipulate some... -> remove 'some'
\end{quote}

\begin{quote}
- page 2
	-- The strongest resistors specifically evolve or have -> possess
	-- Some work has looked -> A few works looked...
	-- http link should be put in a footnote, and using \url{} (if you are writing in Latex)
\end{quote}

\begin{quote}
- page 4
	-- ...to analytical results in some cases -> a few selected cases
\end{quote}

\begin{quote}
- page 5
	-- The difference is that CS will
defect after the handshake if the opponent defects while
handshake will not. -> last Handshake should be capitalized, to separate the player from the strategy
	-- Tables II -> Table II
\end{quote}

\begin{quote}
- page 8
	--  This will be explored
further in the next section, looking not only at x 1 and x N −1
but also consider x N/2 . -> considering...
\end{quote}

\begin{quote}
- page 10
	-- procceses -> processes
	-- TABLE VI: replace 'some' with 'a few selected'
\end{quote}

All of these have been addressed.

\begin{quote}
- page 3
	-- why did you present TF1, TF2, TF3 in reverse ordering?
\end{quote}

We were not too sure what happened here, looking at our version the ordering was
correct. We will specifically inspect the proofs upon submission.

\begin{quote}
	-- Using this it is a known results -> I could not understand what you mean here
\end{quote}

\begin{quote}
	-- These
are no longer a good match which highlights the weakness of
assuming a given interaction between two IPD strategies can be
summarised with a set of utilities as shown in (1). -> this phrase is also not clear
\end{quote}

We have addressed both of these comment by rephrasing.

\end{document}

### 2017-10-31 main.tex
Change cooperation rate diagrams.
The main points needed are the handshakes at the start and subsequent
behaviour (the full set of 200 turns make this unclear).

@@
 This corresponds to the fraction of cooperation played by that strategy observed
-in a given round (out of 200) where each matchup is repeated 10000 times to
+in a given round (out of the first 15) where each matchup is repeated 10000 times to
 obtain the mean.
@@
         correspond to all the strategies considered in this work (ordered
-    alphabetically by name).}
+    alphabetically by name). Columns correspond to round of an IPD match.}
     \label{fig:cooperation_rates}

### 2017-10-31 main.tex
Move description to caption.
Add discussion to end.

@@
 included \cite{brown2001interval}).
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(X_{1}\).
 The points represent the simulated
@@
          Cooperator. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.}
+     normal approximation.
+The top most line on all figures (in red and using a circle) corresponds to
+\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
+\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
+\(x_{1}\).}
     \label{fig:comparison_deterministic}
@@
              Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.}
+     normal approximation.
+The top most line on all figures (in red and using a circle) corresponds to
+\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
+\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
+\(x_{1}\).}
     \label{fig:comparison_stochastic}
@@
 
+One final point to recognise: the large set of strategies used here does not in
+itself constitute an authoritative set. Whilst it is not only large but very
+diverse, the results (and rankings) presented might change given a different set
+of strategies. A further piece of work could look at subgroups of strategies and
+how they fair against other subgroups. Note that because of the open nature of
+the work here (not only is the source code archived but so it the data) this and
+any other further analysis is possible to carry out.
+
 \section*{Acknowledgements}

### 2017-10-31 response_to_reviewers.tex
Finish response to reviewers.

@@
 
-\begin{quote}
+We would like to start our responses by stating that we feel that the reviews we
+have received are fair and detailed. It is clear that the reviewers are aiming
+to help us improve the manuscript and we are grateful for their time.
+
+We were particularly happy to note that the reviewers not only felt the work was
+of interest but made a point to note that our open scientific approach was
+noteworthy (publishing of source code and data).
+
+\begin{verbatim}
     Remember that it is possible to put material into an on-line appendix which
@@
     display.
-\end{quote}
+\end{verbatim}
 
@@
 
+We have referred to this throughout the text simply as `supplementary material',
+if there is a better way to do this we would be happy to change.
+
 \section{Comments from first referee}
 
-\begin{quote}
+\begin{verbatim}
    It's not easy to solve, so I can only point out the problems, and ask you to
@@
    others.
-\end{quote}
+\end{verbatim}
 
@@
 
-\begin{quote}
+\begin{verbatim}
     font in the Appendix could be reduced (for example to the same size of the
     font in the references)
-\end{quote}
+\end{verbatim}
 
@@
 
-\begin{quote}
+\begin{verbatim}
     When you speak about evolutionary computation applied to the IPD, you could
@@
     interesting for the reader.
-\end{quote}
+\end{verbatim}
 
@@
 
-\begin{quote}
+\begin{verbatim}
 - capitalization of words in the title is not consistent; why is "Emergence" with a capital "E", but "iterated" does not have a capital "I"?
-\end{quote}
+\end{verbatim}
 
@@
 
-\begin{quote}
+\begin{verbatim}
 - page 1
 	-- Recently, some strategies...can manipulate some... -> remove 'some'
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
+\begin{verbatim}
 - page 2
@@
 	-- http link should be put in a footnote, and using \url{} (if you are writing in Latex)
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
+\begin{verbatim}
 - page 4
 	-- ...to analytical results in some cases -> a few selected cases
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
+\begin{verbatim}
 - page 5
@@
 	-- Tables II -> Table II
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
+\begin{verbatim}
 - page 8
@@
 but also consider x N/2 . -> considering...
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
+\begin{verbatim}
 - page 10
@@
 	-- TABLE VI: replace 'some' with 'a few selected'
-\end{quote}
+\end{verbatim}
 
@@
 
-\begin{quote}
+\begin{verbatim}
 - page 3
 	-- why did you present TF1, TF2, TF3 in reverse ordering?
-\end{quote}
+\end{verbatim}
 
@@
 
-\begin{quote}
+\begin{verbatim}
 	-- Using this it is a known results -> I could not understand what you mean here
-\end{quote}
+\end{verbatim}
 
-\begin{quote}
+\begin{verbatim}
 	-- These
@@
 summarised with a set of utilities as shown in (1). -> this phrase is also not clear
-\end{quote}
+\end{verbatim}
 
@@
 
+\section{Comments from second referee}
+
+\begin{verbatim}
+
+    1. Title -- I don't think your title represents your paper well. It isn't
+    really about cooperation and it uses the Moran process rather than studying
+    it. I suggest:
+
+    A Comprehensive Empirical Study Of Iterated Prisoner's Dilemma Strategies
+    Using The Moran Process
+
+    Or, if you prefer to focus on results:
+
+    Iterated Prisoner's Dilemma Strategies With Handshakes Are More
+    Evolutionarily Stable
+
+    Whatever you decide on, make sure all words in the title are capitalized.
+
+\end{verbatim}
+
+Many thanks for the suggestion, having reflected on this and as this wasn't
+raised by any of the other reviewers we have decided to keep with the original
+title. We feel that the self recognition mechanisms serve as a way to reinforce
+cooperation which we would prefer to keep in the title. If you feel particularly
+strongly about this we would re consider.
+
+\begin{verbatim}
+    On page 3 you give noise values for TF1, TF2, and TF3. Some explanation of
+    this would be nice. Also, how did you choose TF1, TF2, and TF3? Were they
+    chosen randomly from many runs or were they chosen based on some selection
+    principle?
+\end{verbatim}
+
+The paragraphs just before `There are three further strategies trained
+specifically for this
+study' describe the training mechanism used to obtain TF1, TF2 and TF3.  Given
+that the Moran processes used are not in a noisy environment we did not feel the
+need to discuss this further (2/3 of the trained strategies were not trained in
+noise).
+
+\begin{verbatim}
+
+    3. Figures 2, 3, 4 -- hard to see arrow heads, make them larger
+
+    4. Figures 5 and 6 -- These are too small. It would be better to show fewer
+    examples at a readable size.
+
+    5. Figure 13 -- text labeling axes and scale is too small.
+
+    6. Figure 14 -- Heat map labels should be larger as well as the x-axis label
+    "Rounds." Given space restrictions, it is not possible to make the strategy
+    names larger, but on your other figures it is possible to enlarge the image
+    to read the strategy names and on these figures it is not. Maybe change the
+    file format or the resolution.
+
+    7. Typos
+
+    Section IIIB: "given in Tables II" should be "Table II"
+
+    Section IIIC: "There are are only two new strategies" -- cut repeated "are"
+
+    Section IIID: "Figure 13 show" should be "shows"
+
+    Section V: "allowing the each strategy" -- cut the word "the"
+\end{verbatim}
+
+We have hopefully addressed all these points satisfactorily: making images
+larger and more readable as well as picking up the typos. 
+In particular for the heatmap, we have enlarged the text and simply removed the
+name labels (they are not important). The main point being to see the initial
+play handshake, and to this end we have chosen to only display 15 rounds (as
+opposed to 200).
+Thank you for bringing this to our attention.
+
+\section{Comments from third reviewer}
+
+\begin{verbatim}
+    The first overarching comment is on the density and unreadability of the
+    figures. Displaying as much data as possible is laudable, but to my eyes the
+    condition "as possible" no longer holds.
+\end{verbatim}
+
+We agree and have (as detailed in previous comments) hopefully addressed this.
+
+\begin{verbatim}
+    Particular examples: Fig. 5 is unreadably small, and without extreme
+    magnification it is impossible to read the titles/axes/any words in the
+    subfigure graphics. Note that this *can* be remedied by repeating such
+    information outside of the graphics, and explicitly writing that "the red
+    lines are x_n-1, x-axis is N from 2 to 14, y-axis is fixation probability
+    from 0 to 1" in the caption would allow those graphs to be understood.
+\end{verbatim}
+
+These pointers have been added to the caption but also the number of these
+specific plots have been reduced which also hopes with clarity.
+
+\begin{verbatim}
+For this, tables may well be more readable in conjunction with the figures. Fig.
+2-4 are on the edge of being uninterpretable, and a transition table would also
+help with implementing the strategy.
+\end{verbatim}
+
+We have improved the size of Fig 2-4. We have however chosen to stick with
+diagrams as this is often the way they are represented in the literature (for
+example in Ashlock's papers). Note that we've added a description of the
+interpretation of the figures. If you feel strongly about a table we will
+reconsider.
+
+\begin{verbatim}
+    Fig. 13,14 have unreadable axes. Additionally, Fig.7,9,11 are not only
+    unreadable, but nowhere is it described what the error bars are (I am
+    presuming you treat "fixation probability against opponent X" as one data
+    point and are displaying stats over X, but other possibilities abound). Same
+    goes for Fig 14: what is the cooperation rate per round? Is it fraction of C
+    played by that strategy (as opposed to payoff R) observed in round n (out of
+    how many?), over 10k trials of one single head-to-head match?
+\end{verbatim}
+
+Fig 13,14 have improved axes but also are now improved due to the fact that only
+15 rounds are presented. As well as this, the requested explanations have all
+been included.
+
+\begin{verbatim}
+    Another general observation is with the strategy listing. The "memory
+    depth", in number of rounds of history necessary, is given. This is one
+    particular way of considering strategies, but in my opinion a far more
+    important measure is minimal number of states in a FSM representation. An
+    example is given where GRIM(Grudger) would need infinite memory *as number
+    of rounds input to a lookup table*, but clearly GRIM needs just one bit of
+    memory: whether the opponent has ever defected, which obviously maps to its
+    2^1 states. Allowing the FSM to specify what information it stores is much
+    more flexible. I strongly suggest including the state size as well.
+\end{verbatim}
+
+We have added the number of states in all FSM strategies to this listing. Note
+that we have not attempted to quantify the minimal state representation of all
+strategies (this in itself would be an impressive piece of work outside of the
+scope of this paper).
+
+\begin{verbatim}
+    Several base details of the experiments which I would need to understand,
+    particularly in Algorithm 2:
+    * rounds per game in the actual IPD played
+    I cannot locate this fundamental number, which matters (see DOI
+    10.1109/CIG.2015.7317950)
+    * results <- cache(match)
+    There is a discussion that stochastic strategies exist, and the
+    interpretation of Fig. 6 implies the result of a matchoff remains stochastic
+    (as opposed to taking expected score). Does this mean the cache is a
+    probabilistic function? This is unexpected and should be noted as well in
+    the algorithm.
+    * parent <- selected randomly in proportion to total match payoffs
+    Each individual is selected randomly in proportion to *its* total match
+    payoffs against every other individual? This could be clearer
+    * kill off <- random player from population
+    Is this uniformly at random? This should be specified
+\end{verbatim}
+
+This have all been addressed, in particular we have added to the brief explanation
+of the sampling that occurs from the cached results but made this very explicit.
+
+\begin{verbatim}
+I must take particular issue with the last paragraph of Section II. This makes
+two significant claims with implications for future work:
+1. Sampled fixation probabilities for deterministic strategies are a "perfect
+match" with the theoretical probabilities computed above (the latter is strongly
+appreciated)
+2. Such sampled fixation probabilities for stochastic strategies are "no longer
+a good match" with the theoretical probabilities computed using (presumably)
+expected payoff between the pairs
+
+I cannot accept either statement given the current manuscript, nor accept the
+manuscript without them. To claim 1., a cursory glance at Fig. 5(a,b,e) belie a
+perfect match. To claim 2., Fig. 6(a,b,f) look better than the three
+aforementioned graphs. The issue is, of course, that these probabilities are
+(each) binomially-distributed samples. Wherever there is sampling, and matching
+to theoretical is mentioned, I expect a statistical test. Here, I request
+confidence intervals computed using Bonferroni- (or equivalent) corrected
+binomial models be at least displayed in Fig. 5-6. Claim 2., which seems true,
+requires a corrected exact test against H0.
+\end{verbatim}
+
+We feel that the reviewer has made an excellent point. To make things clearer we
+have chosen to only show one pair of strategies for both types (deterministic
+and stochastic) and have:
+
+\begin{itemize}
+    \item Added simulated confidence bars obtained using an asymptotic normal
+        approximation.
+    \item Carried out a t test over all values in the plots which show the level
+        of significance of the differences (for stochastic) and similarities
+        (for deterministic) of the results.
+\end{itemize}
+
+We contemplated including similar plots/tables that show similar outcomes to the
+supplementary materials but felt that this was perhaps not necessary and would
+be an overflow of information.
+
+\begin{verbatim}
+Firstly, the extremely wide error bars (many are basically 0-1) imply, as we all
+know, that the relation "X beats Y at a particular type of IPD competition" is
+not even close to transitive. Computing the mean fixation probability *against a
+particular set of opponents* is highly sensitive to the composition of the
+competition, in the instant case "wide selection across the literature" with
+unknown weighting. There is no reason to accept the authors' choice, indeed any
+choice, as authoritative.
+
+I strongly suggest that particular subgroups of strategies (ZD, simple FSM,
+handshakers, etc.) be evaluated in block fashion against other subgroups. This
+would allow statements of the form "ZD-type strategies fail (relative to
+neutral) to invade [group] at N=? pairwise", which is alluded to in the paper,
+with the bonus of readable data for each claim. Please ensure statistical
+analysis for these are multiple-testing corrected.
+\end{verbatim}
+
+We acknowledge the point made here by the referee: it is a good one. We would
+suggest that as well as the large number of strategies they also represent quite
+a diverse selection. However the point made by the referee stands. We have
+included this point in our discussion. Note however that in terms of carrying
+out a subgroup analysis, we feel that this would not fall within the scope of
+this work. To do it properly would constitute a fundamental rewrite of all the
+results. This has been noted in the discussion, including the important point
+that by making our data available anyone could do this (and we hope to do so
+ourselves).
+
+\begin{verbatim}
+Secondly, with the results as computed globally, reporting the mean is
+insufficient for these wide ranges; for each of Fig. 7(b) and Tables II-III
+other generic descriptive stats are necessary.
+\end{verbatim}
+
+A number of further statistics have been reported.
+
+\begin{verbatim}
+Minor detail: references [11] and [13] are the same work. Formatting of the
+references in general is also worth checking again.
+\end{verbatim}
+
+This has been done.
+
 \end{document}

### 2017-10-31 main.tex
Fix a typo

@@
 how they fair against other subgroups. Note that because of the open nature of
-the work here (not only is the source code archived but so it the data) this and
+the work here (not only is the source code archived but so is the data) this and
 any other further analysis is possible to carry out.

### 2017-11-01 main.tex
Correct detail about repetitions of Moran process.

@@
 methods appear in the literature \cite{Ashlock2006}.
-There has also been some work on strategies using an evolutionary in real time: 
+There has also been some work on strategies using an evolutionary algorithm in real time: 
 in~\cite{Gaudesi2016}
 an evolutionary algorithm is used to build a model of the opponent and attempt
-to exploit any potential weakness. This sort of work is not considered here:
-strategies are instead pre trained.
+to exploit any potential weakness. In this work all strategies resulting from
+evolutionary algorithms are pre-trained.
 
@@
 until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
-This strategy was specifically designed for evolutionary processes.
+Collective Strategy was specifically designed for evolutionary processes.
 
@@
         \scalebox{0.7}{\input{tex/memory_depth_count.tex}}
-        \caption{Memory depth}
+        \caption{Memory depths}
         \label{tbl:memory_depth_count}
@@
 
-Each strategy pair is run for 1000 repetitions of the Moran process to fixation
+The Moran process is run for each strategy pair to fixation
 with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
@@
     \input{tex/t_test_results_calculator_v_arrogant_q_learner.tex}
-    \caption{\(p\) values resulting from a \(t\) test comparing the theoretic
+    \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
         value with the simulated value of the Moran Process fixation
@@
 
-When $N=2$ the Moran process is effectively a measure of the distribution of 
-relative
+When $N=2$ the fixation probabilities of the Moran process are effectively measures
+of the distribution of  relative
 mean payoffs over all possible matches between two players. The strategy
@@
 
-It can be seen that apart from CS, none of the strategies
+It can be seen that apart from CS, none of the strategies for \(N=2\)
 of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
@@
         as approximate handshake.
-    \item  PSO Gambler and Evolved Lookerup 2 2 2: are strategies that make use
+    \item  PSO Gambler and Evolved Lookerup 2 2 2: strategies that make use
         of a lookup table mapping the first 2 moves of the opponent as well as
-        the last 2 moves of both players to an action. The PSO gambler is a
-        stochastic version of the Lookerup which maps those states to probabilities of cooperating. The Lookerup was described in \cite{Knight2016}.
+        the last 2 moves of both players to an action.  PSO gambler is a
+        stochastic version of  Lookerup which maps those states to probabilities
+       of cooperating. Lookerup was described in \cite{Knight2016}.
     \item The Evolved ANN strategies are neural networks that map a number of
@@
 	    algorithm.
-    \item The Evolved FSM 16 is a 16 state finite state machine trained to
+    \item Evolved FSM 16 is a 16 state finite state machine trained to
         perform well in tournaments.
@@
 is functionally very similar to its deterministic cousin Evolved Looker Up.
-The PSO Gambler Mem1 strategy is a memory one strategy that has been trained to
+PSO Gambler Mem1 is a stochastic memory one strategy that has been trained to
 maximise its utility and does perform well.
@@
 for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically it is advantageous to defect (as a signal)
+cumulative defections. Paradoxically for handshaking strategies
+it is advantageous to defect (as a signal)
 in order to achieve mutual cooperation with opponents using the same strategy
@@
 self-recognition mechanism. It is also unwise to defect on the first move as
-some strategies additionally retaliate first round defections. So the
+some strategies additionally retaliate in response to first round defections. So the
 handshakes used by TF1, TF2, and CS are in some sense optimal.
@@
 population. This is confirmed by the performance of the zero determinant strategies: while
-some do rank relatively highly for \(N=2\) (ZD-extort-4 has rank 16) this rank
+some do rank relatively highly for \(N=2\) (ZD-Extort-4 has rank 16) this rank
 does not translate to larger populations.
@@
 individuals in the case of TF1 and TF2. This may have significant implications
-for human social interactions such as the evolution of ingroup/outgroup mechanisms
+for various biological and social phenomena such as
+human social interactions, particularly the evolution of ingroup/outgroup mechanisms
 and other sometimes costly rituals that reinforce group behavior.
@@
 One final point to recognise: the large set of strategies used here does not in
-itself constitute an authoritative set. Whilst it is not only large but very
+itself constitute an authoritative set. Whilst it is not only large but also very
 diverse, the results (and rankings) presented might change given a different set

### 2017-11-01 main.tex
Revert "Correct detail about repetitions of Moran process."
This reverts commit 641b44bb106766472f7d2cd9f426040a0886879a.

@@
 
-The Moran process is run for each strategy pair to fixation
+Each strategy pair is run for 1000 repetitions of the Moran process to fixation
 with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,

### 2017-11-01 response_to_reviewers.tex
Reorder TF* explanation.
Improve layout of response.

@@
 \usepackage{hyperref}
+\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
 
-\title{Response to reviews}
+\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
+       Mechanisms: an Empirical Study of the Moran process for the Iterated
+       Prisoner's Dilemma - Response to reviews}
 
@@
 We were particularly happy to note that the reviewers not only felt the work was
-of interest but made a point to note that our open scientific approach was
+of interest but made a point to say that our open scientific approach was
 noteworthy (publishing of source code and data).
@@
 
-We were not too sure what happened here, looking at our version the ordering was
-correct. We will specifically inspect the proofs upon submission.
+This was a slightly clumsy oversight and we have put them back in order.
 
 \begin{verbatim}
-	-- Using this it is a known results -> I could not understand what you mean here
+	-- Using this it is a known results -> 
+    I could not understand what you mean here
 \end{verbatim}
@@
 assuming a given interaction between two IPD strategies can be
-summarised with a set of utilities as shown in (1). -> this phrase is also not clear
+summarised with a set of utilities as shown in (1). -> 
+this phrase is also not clear
 \end{verbatim}

### 2017-11-01 response_to_reviewers.tex
Minor modification of review.

@@
 
-This was a slightly clumsy oversight and we have put them back in order.
+This was an oversight and we have put them back in order.
 
@@
 
-We have addressed both of these comment by rephrasing.
+We have addressed both of these comments by rephrasing.
 
@@
 larger and more readable as well as picking up the typos. 
-In particular for the heatmap, we have enlarged the text and simply removed the
+In particular for the heatmaps, we have enlarged the text and simply removed the
 name labels (they are not important). The main point being to see the initial
-play handshake, and to this end we have chosen to only display 15 rounds (as
+handshake, and to this end we have chosen to only display 15 rounds (as
 opposed to 200).
@@
 These pointers have been added to the caption but also the number of these
-specific plots have been reduced which also hopes with clarity.
+specific plots have been reduced which also helps with clarity.
 
@@
 \begin{itemize}
-    \item Added simulated confidence bars obtained using an asymptotic normal
+    \item Added simulated confidence intervals obtained using an asymptotic normal
         approximation.
@@
 
-We contemplated including similar plots/tables that show similar outcomes to the
+We contemplated adding similar plots/tables that show similar outcomes to the
 supplementary materials but felt that this was perhaps not necessary and would
@@
 We acknowledge the point made here by the referee: it is a good one. We would
-suggest that as well as the large number of strategies they also represent quite
-a diverse selection. However the point made by the referee stands. We have
-included this point in our discussion. Note however that in terms of carrying
+suggest that as well as the large number of strategies: they also represent quite
+a diverse selection. However the point made by the referee stands.
+
+We have
+added this to our discussion. Note however that in terms of carrying
 out a subgroup analysis, we feel that this would not fall within the scope of

### 2018-01-07 second_response_to_reviewers.tex
First draft of response to reviews.

\documentclass[a4]{article}

\usepackage{hyperref}
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}

\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an Empirical Study of the Moran process for the Iterated
       Prisoner's Dilemma - Response to reviews}

\begin{document}

\maketitle

\section{Comments from editor}

\begin{verbatim}
We have a problem with reviewers declining to re review the paper, which
forced us to invite first time reviewers for the revision.  The new reviewers
have a number of problems with the manuscript.  In particular you need to work
much harder to justify the relevance of your work to understanding iterated
games.
\end{verbatim}

We open our second response to the reviews by highlighting that in the original
review no comments were raised about the relevance of the work.
\textbf{Specifically all previous reviewers highlighted that the work was
noteworthy and worth publishing}.

Regarding the relevance of the work, comments from each reviewer were:

\begin{itemize}
    \item 
\begin{verbatim}
The paper is well written, the results seem solid and overall very interesting.
The main issues with this work, in my opinion, lie in the presentation:
\end{verbatim}
    \item

\begin{verbatim}
The analysis in the paper is well designed and clearly explained. It does an
excellent job of leveraging the work of many years and many different
researchers to create new and significant results. And, the paper serves as a
good model of how to make all code and data available, making the results easily
reproducible and expandable to other researchers curious about the behaviour of
additional strategies.
\end{verbatim}
    \item

\begin{verbatim}
The reported experiments fill an important hole in the understanding of IPD
evolution and are sorely needed. The authors also take pains to ensure the data
are publicly available, which is highly appreciated.
\end{verbatim}
\end{itemize}

Most requests were on the subject of
presentation of the results as well as requests for specific pieces of further
analysis. All of these were addressed.

This latest set of comments from the reviewers are mainly of two types:

\begin{enumerate}
    \item Further minor requests for presentation modifications (specifically
        the remaining reviewer from the first round only made requests of this
        type).
    \item Questions about the suitability/impact of the work.
\end{enumerate}

As we detail below we have addressed all requests of the first type. For the
requests of the second type, from the two new reviewers who are perhaps not
experts in the IPD, we have made some modifications to the manuscript but our
main responses are to answer the questions posed by the reviewers.

Specifically we describe how the Moran process is a well studied model of
evolutionary processes and that this paper is a major contribution to the
literature. It can be thought of as a tournament on Moran processes equivalent
to the seminal work by Robert Axelrod in the 1980s.

Robert Axelrod's work on the Prisoner's Dilemma tournaments (described in
the literature review) which has been cited more than 34,000 times considered
pair wise matches between strategies. Our work here provides a much more robust
type of tournament where strategies are pitted against one another in an actual
evolutionary process (as opposed to a single one of interaction).

\section{Comments from first referee}

\begin{verbatim}
   Figures are much improved! It was a good idea to move some of them to the
Supplementary Material. I still think the title is not representative of the
work -- you should reconsider at least changing the subtitle. You are not
studying the Moran process; you are studying Prisoner's Dilemma strategies.  I
\end{verbatim}

Thank you for agreeing to review the paper again.

We have changed the subtitle to be: `Empirical Study of strategies in the Moran
process for the Iterated Prisoner's

\begin{verbatim}
also still think the description on page 3 of how you found the TF1, TF2, and
TF3 strategies is confusing. It has a frustrating level of detail. You should
either have less detail or more detail. This is not a crucial point, however.
\end{verbatim}

The description of how we obtain the strategies is quite minimalistic.
The rest of the description in this section is specifically describing each
strategy (accompanied by the corresponding diagram). This description is quite
important as it highlights the handshake mechanism which is one of the main
findings of the work. We have considered changing this further but as this is
not a crucial point we would prefer to leave it as it is.

\section{Comments from second referee}

\begin{verbatim}

I couldn’t tell how each round is played. Does each individual play against only
one
other (randomly chosen) individual or against all N − 1 other individuals?

\end{verbatim}

Yes they play against all N - 1 other individuals. This is a standard Moran
process of this type and is described in
Algorithm 2. The mathematical equations (2) and (3) also ensures this to be the
case. Nonetheless we have added a sentence clarifying this:

``Individuals are \textbf{selected}
according to a given fitness landscape, in this work it is their total utility
against all other individuals in the population.''

\begin{verbatim}
    In the introduction the authors state "The results and insights contained in
    this paper
    would be difficult to derive analytically”. But in Section II the authors
    present several
    formulas (Eq. (2)–(7)) and analytically compare a couple of strategies. Why
    can’t
    these formulas be used to analytically compare any pair of strategies listed
    in the
    paper?
\end{verbatim}

This is the purpose of section II. The analytical results hold for deterministic
strategies however they do not for stochastic values where the average is just a
summary measure that is never truly obtained. This was raised by one of the
previous reviews which lead to the addition of Tables II and III to further show
the difference between the analytic result (which in this case is an
approximation) and the actual result.

After careful examination of how this section is written we do not see how it
can be improved and feel it is clear. Specifically this sentence: `This
demonstrates that assuming a given interaction between two
IPD strategies can be summarised with a set of utilities as
shown in (1) is not correct.'.

\begin{verbatim}
The authors should avoid jargon because it doesn’t help readability. For instance, in
Section III(c) the authors state “this is explained by the need of strategies to have a
steady hand when interacting with their own kind. Acting stochastically increases the
chance of friendly fire.”. What is a “steady hand” and what is “friendly fire” in an
IPD game?
\end{verbatim}

We have replaced this comments with more standard language.

\begin{verbatim}
Here are some of the questions I have after reading the
paper. (The first two points deal with the realism of the models; the last two with exploiting
the paper’s findings.)

- Suppose 10 people decide to play an IPD game. The authors only allowed pairs of
strategies in the population. If k individuals happen to pick the same strategy, what
is the likelihood the other 10 − k people will pick the same alternative strategy?
- The strategies evolved under a Moran process. Under a Moran process each round
one player must change his strategy 1 . Is there an example of a real-world social
dilemma or a human experiment where strategy changes resulted from a Moran pro-
cess or something similar? (This issue is particularly important because the authors
specifically trained some IPD strategies to excel at the Moran process.)
\end{verbatim}

We refer the reviewer to the many references included and the vast quantity of
literature on the Moran process. This is not a new model but a well understood
model of evolutionary processes with applications both to human and biological
interactions. It seems like the review mainly questions the Moran process itself
as opposed to our use of it.

\begin{verbatim}
Suppose the population is using either strategy A or strategy B. Mutation was
not
allowed in the authors’ simulation so no other strategies can be used. How
useful then
is it to know some other strategy C can successfully invade strategy B if
strategy C
isn’t available?
\end{verbatim}

This is more useful than the already published (and heavily cited) works in this
area that look at the score of A against B as opposed to the ability of A to
invade/defend B.

\begin{verbatim}
How useful is it knowing that strategy A can or cannot resist invasion by
strategy
B when players rarely know exactly what strategy their opponent is using? In
par-
ticular, before the game begins players won’t know what strategy others intend
to
use.
\end{verbatim}

This feels like a question about the entirety of the research field on the IPD.

We refer the referee to the vast quantity of literature in this field and in
particular highlight that one of the main goals of this area are to understand
properties of environment and strategies that enable for emergence of a given
type of behaviour. In the case of this work, we show that in evolutionary
environments, handshake mechanisms can emerge which contribute to the emergence
of cooperation.

We have added a sentence to the paper further explaining how this work offers a
more evolutionary robust version of Robert Axelrod's original tournament.

\section{Comments from third reviewer}

\begin{verbatim}
    I saw no significant contribution in the field of evolutionary computation
    itself. The whole paper would have been a great *experimental section* after
    some new idea or scheme.
\end{verbatim}

We have justified the contribution in many ways but agree that this paper is a
strong numerical experimental paper (as evidenced by the title) following the
novel idea of creating tournaments with Moran processes as ways to score pairs of
strategies.

\begin{verbatim}
Indeed, results appears sensible, when not obvious. Collective strategies
perform well, the usual suspects are hard to invade. However, generally
speaking, the main problem is that with IPD is extremely hard to infer
meaningful data from the mere statistical results, as it would be hard to draw
conclusions about the "best opening" looking at students playing chess. Indeed,
such an analysis makes perfect sense as soon as one restricts the domain to a
specific grandmaster, or a specific top-level tournament.
\end{verbatim}

A lot of the original and contemporary research in this area uses the IPD to
show why/how
cooperative behaviour may evolve. This has often been through large numerical
analyses such as these. However, none of them (as discussed in the literature
review) consider Moran processes on this scale. Furthermore, one of our main
conclusions/findings is that handshake mechanisms can also appear through
evolutionary processes and in particular that these can explain the emergence of
cooperation.

\begin{verbatim}
    The *Moran Processes* should be briefly introduced, let alone mentioned in
    the abstract before explaining how their *fixation probabilities* have been
    obtained.
\end{verbatim}

The Moran process is briefly introduced in section A. It is also described in
Fig 1, Algorithm 2 and also mathematically throughout equations (1) - (7).
Furthermore numerous background references are given.

\begin{verbatim}
The concept of *fixation probabilities* should be properly introduced, or, more
simply, authors can talk about *the probability with which a given strategy
takes over a population* without mentioning the specific term.
\end{verbatim}

We have added a description of this to the main text.

\begin{verbatim}
As a good journal paper could be read several years after being written, authors
should avoid relative expressions like "recent" or recently", and use absolute
timings, such as "in 2012" or "in the beginning of 2010s".
\end{verbatim}

We have modified this terminology.

\begin{verbatim}
    Population sizes range from 2 to 14. While 2 is an obvious choice, being the
    smallest possible *population*, the use of 14 is puzzling. Twice the days in
    a week?
\end{verbatim}

There needs to be an upper bound, 14 was chosen as the highest number reasonable
given the computational cost of running these models.

\begin{verbatim}
    *Moreover we present a number of strategies that were created via
    reinforcement algorithms* -> Which number?
\end{verbatim}

16. We have added this to the text.

\begin{verbatim}
*Zero determinant strategies are not particularly effective for N > 2* -> do you
mean that they *only* works good for N==2? Effective as invader, defenders or
both? Generally speaking, the whole text following *While the results agree with
some of the published literature, it is found that* is almost completely
unintelligible in such an early section of the paper.
\end{verbatim}

We have clarified the first bullet point (both invaders and defenders). We
disagree with the comment that this bullet point list is unintelligible (at
present at least 4 reviewers have read this summary of the findings and no one
has said that it is unintelligible). If this
is a sticking point for the referee we refer to the editor to decide how and if
these short sentences should be rewritten.

\begin{verbatim}
Use underscore, or dash, for multi word variable, eg. *player one* ->
*player_one*.
\end{verbatim}

We have modified the pseudo code to follow this suggestion.

\begin{verbatim}
uthors use a panmictic population, but the effect of population topologies would
have been interesting. Also mixed populations should be checked (eg. 50% TFT,
40% ETFT, 10% Grudger).
\end{verbatim}

Both these points are already mentioned in an area for possible future work.
Actually carrying out this analysis as part of this article is an unreasonable
request (the paper would end up being extremely large).

\begin{verbatim}
Algorithm 1 has a return at line 8, nullifying the previous three for loops.
Maybe *save* or *record* would be better?
\end{verbatim}

We have changed this to use yield.

\begin{verbatim}
*When studying evolutionary processes it is vital to consider N > 2 since
results for N = 2 cannot be used to extrapolate performance in larger
populations* sounds more like a truism than a conclusion.
\end{verbatim}

We agree. This paper presents the first empirical evidence and as discussed: in
the literature this is not well understood (results are often only considered
for N=2).

\begin{verbatim}
In EAs, the term *offspring* is usually preferred to *child*.
\end{verbatim}

We have modified this.

\begin{verbatim}
Do not use **bold** for emphasis.
\end{verbatim}

We have removed the bold.

\begin{verbatim}
Don't start a section with *Figure 1 shows a diagrammatic representation of the
Moran process*, rather, tell what a *Moran process* is, and then refer to figure
to better illustrate the idea.
\end{verbatim}

We have modified this.

\end{document}

### 2018-01-07 main.tex
Remove repetition details in training section.
Reorder TF* explanation.
First draft of response to reviews.

@@
 \title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
-       Mechanisms: an Empirical Study of the Moran process for the Iterated
-       Prisoner's Dilemma}
+       Mechanisms: Empirical Study of strategies in the Moran process for the
+       Iterated Prisoner's}
 \author[1]{Vincent Knight}
@@
 number of strategies have been developed to take advantage of the history of
-play. Recently, strategies referred to as zero determinant (ZD) strategies
+play. Strategies referred to as zero determinant (ZD) strategies
 \cite{Press2012} can manipulate some players through extortionate mechanisms.
@@
 
-Using the Axelrod library and the many strategies it contains, we obtain
-fixation probabilities for all pairs of strategies, identifying
-those that are effective invaders and those resistant to invasion, for
-population sizes $N=2$ to $N=14$. Moreover we present a number of strategies
-that were created via reinforcement algorithms (evolutionary and particle
-swarm algorithms) that are among the best invaders and resistors of invasion
-known to date, and show that handshaking mechanisms naturally arise from these
-processes as an invasion-resistance mechanism.
-
-Recent work has argued that agent-based
+Using the Axelrod library and the many strategies it contains, we obtain the
+probability with which a given strategy takes over a population (referred to as
+fixation probability) for all pairs of strategies, identifying those that are
+effective invaders and those resistant to invasion, for population sizes $N=2$
+to $N=14$. Moreover we present a number (16) of strategies that were created via
+reinforcement algorithms (evolutionary and particle swarm algorithms) that are
+among the best invaders and resistors of invasion known to date, and show that
+handshaking mechanisms naturally arise from these processes as an
+invasion-resistance mechanism.
+
+In 2016, work has argued that agent-based
 simulations can provide insights in evolutionary game theory not available
@@
 \begin{enumerate}
- \item Zero determinant strategies are not particularly effective for $N > 2$
+ \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
  \item Complex strategies can be effective, and in fact can naturally evolve
@@
 
-Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
-process, a stochastic birth death process on a finite population in which the
-population size stays constant over time. Individuals are \textbf{selected}
-according to a given fitness landscape. Once selected, the individual is
-reproduced and similarly another individual is chosen to be removed from the
-population (a uniform random selection is used). In some settings mutation is
-also considered but without mutation
-(the case considered in this work) this process will arrive at an absorbing
-state where the population is entirely made up of players of one strategy. The
-probability with which a given strategy takes over a population is called the
-\textit{fixation probability}. A more detailed analytic description of this is
-given in Section~\ref{sec:validation}. In our simulations offspring do not
-inherit any knowledge or history from parent replicants.
+A Moran process is a stochastic birth death process on a finite population in which the
+population size stays constant over time. Individuals are \textit{selected}
+according to a given fitness landscape, in this work it is their total utility
+against all other individuals in the population. Once selected, the individual
+is reproduced and similarly another individual is chosen to be removed from the
+population (a uniform random selection is used). This is shown diagrammatically
+in Figure~\ref{fig:moran_process}. In some settings mutation is
+also considered but without mutation (the case considered in this work) this
+process will arrive at an absorbing state where the population is entirely made
+up of players of one strategy. The probability with which a given strategy takes
+over a population is called the \textit{fixation probability}. A more detailed
+analytic description of this is given in Section~\ref{sec:validation}. In our
+simulations offspring do not inherit any knowledge or history from parent
+replicants.
 
@@
 a strategy using machine learning techniques was capable of resisting invasion
-and also able to invade any memory one strategy. Recent work \cite{Hilbe2017}
+and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
 has investigated the effect of memory length on strategy performance and the
@@
 strategies cooperate well with other players using the same strategy.
+
+This work uses pair wise Moran processes in a similar way to matches in the many
+IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
+This is a more robust tournament from an evolutionary point of view.
 
@@
 As opposed to the previously described strategies, these strategies were trained
-with the objective function of \textbf{mean fixation probabilities for Moran
+with the objective function of \textit{mean fixation probabilities for Moran
 processes} starting at initial population states consisting of \(N/2\)
@@
 \begin{itemize}
-	\item TF1 \(N=12\), 0\% noise, 10000 repetitions per matchup
-	\item TF2 \(N=10\), 0\% noise, 10000 repetitions per matchup
-	\item TF3 \(N=8\), 1\% noise, 100 repetitions per matchup
+	\item TF1 \(N=12\), 0\% noise.
+	\item TF2 \(N=10\), 0\% noise.
+	\item TF3 \(N=8\), 1\% noise.
 \end{itemize}
 
-Each matchup of players was run to fixation for the specified number of
-repetitions to estimate the absorption probabilities. The trained algorithms
+The trained algorithms
 were run for fewer than 50 generations. Training data for this is available at
 \cite{data}.
+
+TF1 has an initial handshake of CCD and cooperates if the opponent matches.
+However if the opponent later defects, TF1 will respond in kind, so the
+handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
+achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
+very similar to a strategy known as ``Collective Strategy'', which has a
+handshake of CD and cooperates with opponents that matched the handshake
+until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
+Collective Strategy was specifically designed for evolutionary processes.
+
+TF2 always starts with CD and will defect against opponents that start with
+DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
+Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
+can be rescued after a failed handshake by a complex sequence of plays
+which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
+GTFT, and a few others with low probability. TF2 defects against all other
+players in the study, barring
+unusual cases arising from particular randomizations. Figure~\ref{fig:tf2} shows
+all 16 states of the strategy (states 6 and 7 are not reachable).
 
@@
 are not reachable).
-
-TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
-Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
-can be rescued after a failed handshake by a complex sequence of plays
-which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
-GTFT, and a few others with low probability. TF2 defects against all other
-players in the study, barring
-unusual cases arising from particular randomizations. Figure~\ref{fig:tf2} shows
-all 16 states of the strategy (states 6 and 7 are not reachable).
-
-TF1 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
-achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
-very similar to a strategy known as ``Collective Strategy'', which has a
-handshake of CD and cooperates with opponents that matched the handshake
-until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
-Collective Strategy was specifically designed for evolutionary processes.
 
@@
     \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textbf{deterministic} strategies: Alternator and
+             probabilities for \textit{deterministic} strategies: Alternator and
          Cooperator. 5\% confidence intervals calculated using an asymptotic
@@
         value with the simulated value of the Moran Process fixation
-        probabilities for \textbf{deterministic} strategies: Alternator and
+        probabilities for \textit{deterministic} strategies: Alternator and
     Cooperator.}
@@
     \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textbf{stochastic} strategies:
+             fixation probabilities for \textit{stochastic} strategies:
              Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
@@
         value with the simulated value of the Moran Process fixation
-        probabilities for \textbf{stochastic} strategies: Calculator and
+        probabilities for \textit{stochastic} strategies: Calculator and
     Arrogant Q Learner.}
@@
 Interestingly none of these strategies is stochastic: this is explained by
-the need of strategies to have a steady hand when interacting with their own
-kind. Acting stochastically increases the chance of friendly fire.
+the need of strategies to act rationally interacting with their own
+kind. Acting stochastically increases the chance of reducing the score of individuals of the same type in a Moran process.
 However it is possible to design a strategy with a stochastic or error-correcting

### 2018-01-09 second_response_to_reviewers.tex
Include MH's comments/suggestions.

@@
 
-Specifically we describe how the Moran process is a well studied model of
+Specifically we describe how the Moran process is a well-studied model of
 evolutionary processes and that this paper is a major contribution to the
@@
 
-Robert Axelrod's work on the Prisoner's Dilemma tournaments (described in
-the literature review) which has been cited more than 34,000 times considered
-pair wise matches between strategies. Our work here provides a much more robust
-type of tournament where strategies are pitted against one another in an actual
-evolutionary process (as opposed to a single one of interaction).
+Robert Axelrod's work on the Prisoner's Dilemma tournaments (described in the
+literature review) which has been cited more than 34,000 times considered
+pair-wise matches between strategies. Our work here is much more
+computationally-intensive and accesses deeper questions of evolutionary
+stability.
+
+Furthermore, Moran processes for the IPD have been frequently studied from a
+theoretical point of view and our results extend that to strategies that are
+difficult (or impossible) to study analytically.
 
@@
 
-The description of how we obtain the strategies is quite minimalistic.
+The description of how we obtain the strategies is quite minimalistic and all
+training code is documented and available online (archived according to best
+practice).
 The rest of the description in this section is specifically describing each
@@
 Algorithm 2. The mathematical equations (2) and (3) also ensures this to be the
-case. Nonetheless we have added a sentence clarifying this:
+case. We have added a sentence clarifying this:
 
@@
 
-This is the purpose of section II. The analytical results hold for deterministic
-strategies however they do not for stochastic values where the average is just a
-summary measure that is never truly obtained. This was raised by one of the
-previous reviews which lead to the addition of Tables II and III to further show
-the difference between the analytic result (which in this case is an
-approximation) and the actual result.
+The purpose of this section (II) is to show that the simulations match the
+theory well in cases that are analytically accessible as a validation. This is
+in addition to the extensive test suite for the software which covers 100\% of
+the Axelrod library.
+
+As an example of a case where a theoretical result is more difficult to obtain,
+we note that when one or more of the strategies is stochastic then the utility
+function is also stochastic and would need to be analyzed statistically,
+assuming that the utility distribution could be analytically derived, which is
+unrealistic in many cases. Additionally long memory strategies are difficult to
+analyze theoretically, which is why they are often avoided in the literature,
+and why a number of misconceptions about them have persisted (including the
+strength of Zero determinant strategies, a point raised by the reviewers). 
+We approximate
+the utilities with a large number of simulations, a commonly used technique.
 
@@
 
-We refer the reviewer to the many references included and the vast quantity of
-literature on the Moran process. This is not a new model but a well understood
-model of evolutionary processes with applications both to human and biological
-interactions. It seems like the review mainly questions the Moran process itself
-as opposed to our use of it.
+This is the standard Moran process and the reviewer is asking about one of
+the many extensions of the standard process, e.g. to multi-strategy populations
+or other dynamics (such as a best-reply dynamic) which may allow players to
+dynamically choose new strategies each round. The standard is an evolutionary
+game where players have a fixed strategy throughout their lives with the
+biological analogy of bacteria with different genetically coded traits and also
+cancer, the latter of which is referenced in the introduction.
 
@@
 
-This is more useful than the already published (and heavily cited) works in this
-area that look at the score of A against B as opposed to the ability of A to
-invade/defend B.
+In biological situations it's often assumed that mutations are relatively rare
+so it makes sense to run a process to fixation rather than look at many
+variants at once in that context. In fact, the rate of mutation is typically
+set to 1 / N, a the population runs for O(N) iterations before converging to
+one of the absorbing states (and often far fewer), so there would typically be
+very few simultaneous mutations. There are other contexts where there would be
+more than two strategies at a time and they are interesting, but not the focus
+of this work.
+
+Additionally, if there is mutation then different techniques are needed. The
+Markov process no longer has absorbing states the stationary distribution has 
+to be studied instead. This is an interesting case but would be a
+work of similar length, and this work is the limiting case where mutation goes
+to zero.
 
@@
 
-We refer the referee to the vast quantity of literature in this field and in
+We refer the referee to the prior literature in this field and in
 particular highlight that one of the main goals of this area are to understand
@@
 type of behaviour. In the case of this work, we show that in evolutionary
-environments, handshake mechanisms can emerge which contribute to the emergence
+environments, handshake mechanisms can emerge which reinforces the emergence
 of cooperation.
@@
 We have added a sentence to the paper further explaining how this work offers a
-more evolutionary robust version of Robert Axelrod's original tournament.
+population based perspective.
 
@@
 conclusions/findings is that handshake mechanisms can also appear through
-evolutionary processes and in particular that these can explain the emergence of
+evolutionary processes.
+
+This is directly analogous to "the best opening" in chess. Moreover, our
+numerical results call into question several common assumptions in the
+literature, e.g. that it's enough to only consider memory-one strategies (it's
+demonstrably not the case), that ZD strategies are the best yet they don't win
+here, etc. This work specifically identifies fruitful and valuable new
+directions for future work.
+
+Finally, we show that "collective strategies" directly emerge from evolutionary
+processes and are reinforced by standard evolutionary mechanisms, which is a
+major theme of the paper and very relevant to the study of the evolution of
 cooperation.
@@
 
-There needs to be an upper bound, 14 was chosen as the highest number reasonable
-given the computational cost of running these models.
+There needs to be an upper bound, 14 was chosen as the highest number
+reasonable given the computational cost of running these models. Also, the
+lower values of N (greater than 2) are shown to already indicate the behaviour
+of higher values (see Figure 7).
 
@@
 has said that it is unintelligible). If this
-is a sticking point for the referee we refer to the editor to decide how and if
+is a sticking point for the referee we defer to the editor to decide how and if
 these short sentences should be rewritten.

### 2018-01-09 main.tex
Include MH's comments/suggestions.

@@
 population size stays constant over time. Individuals are \textit{selected}
-according to a given fitness landscape, in this work it is their total utility
-against all other individuals in the population. Once selected, the individual
+according to a given fitness landscape. The fitness landscape in this work is
+defined as the total utility against all other individuals in the population.
+Once selected, the individual
 is reproduced and similarly another individual is chosen to be removed from the
@@
 process will arrive at an absorbing state where the population is entirely made
-up of players of one strategy. The probability with which a given strategy takes
+up of players of one strategy. The probability with which a given strategy,
+starting from a single individual takes
 over a population is called the \textit{fixation probability}. A more detailed
@@
 
-This work uses pair wise Moran processes in a similar way to matches in the many
+This work uses pair-wise Moran processes in a similar way to matches in the many
 IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
-This is a more robust tournament from an evolutionary point of view.
+This work offers a population-based perspective which adds additional
+evolutionary components to the IPD, namely the evolutionary dynamics of invasion
+and resistance
 
@@
 
-Interestingly none of these strategies is stochastic: this is explained by
-the need of strategies to act rationally interacting with their own
-kind. Acting stochastically increases the chance of reducing the score of individuals of the same type in a Moran process.
-However it is possible to design a strategy with a stochastic or error-correcting
-handshake that is an excellent resistor even in noisy environments \cite{Lee2015}.
+Interestingly none of these strategies is stochastic: this is explained by the
+value of not provoking typically cooperative opponent strategies with
+speculative defections. This includes opponents using the same strategy.  Acting
+stochastically increases the chance of reducing the score of individuals of the
+same type in a Moran process.  However it is possible to design a strategy with
+a stochastic or error-correcting handshake that is an excellent resistor even in
+noisy environments \cite{Lee2015}.
 

### 2018-01-11 second_response_to_reviewers.tex
Add final edits from Marc.

@@
 In biological situations it's often assumed that mutations are relatively rare
-so it makes sense to run a process to fixation rather than look at many
-variants at once in that context. In fact, the rate of mutation is typically
-set to 1 / N, a the population runs for O(N) iterations before converging to
-one of the absorbing states (and often far fewer), so there would typically be
-very few simultaneous mutations. There are other contexts where there would be
+so it makes sense to run a process to fixation rather than look at many variants
+at once in that context. In fact, the rate of mutation is typically set to 1 /
+N, and the population runs for O(N) iterations before converging to one of the
+absorbing states (and often far fewer), so there would typically be very few
+simultaneous existing mutations. There are other contexts where there would be
 more than two strategies at a time and they are interesting, but not the focus

### 2018-01-11 main.tex
Add final edits from Marc.

@@
 IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
-This work offers a population-based perspective which adds additional
+A population-based perspective is given which adds additional
 evolutionary components to the IPD, namely the evolutionary dynamics of invasion
-and resistance
+and resistance.
 

### 2018-01-11 main.tex
Tweak the title.

@@
 \title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
-       Mechanisms: Empirical Study of strategies in the Moran process for the
+       Mechanisms: an Empirical Study of strategies in the Moran process for the
        Iterated Prisoner's}

### 2018-01-11 main.tex
Mark minor modifications.

@@
 
-Interestingly none of these strategies is stochastic: this is explained by the
+Interestingly none of these strategies are stochastic: this is explained by the
 value of not provoking typically cooperative opponent strategies with

### 2018-01-11 second_response_to_reviewers.tex
Tweak the title.

@@
 As we detail below we have addressed all requests of the first type. For the
-requests of the second type, from the two new reviewers who are perhaps not
-experts in the IPD, we have made some modifications to the manuscript but our
+requests of the second type, from the two new reviewers we have made some modifications to the manuscript but our
 main responses are to answer the questions posed by the reviewers.
@@
 
-We have changed the subtitle to be: `Empirical Study of strategies in the Moran
+We have changed the subtitle to be: `an Empirical Study of strategies in the Moran
 process for the Iterated Prisoner's

### 2018-01-11 main.tex
Add missing word to title!

@@
 \title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
-       Mechanisms: an Empirical Study of strategies in the Moran process for the
-       Iterated Prisoner's}
+       Mechanisms: an Empirical Study of Strategies in the Moran process for the
+       Iterated Prisoner's Dilemma}
 \author[1]{Vincent Knight}

### 2018-04-05 plos/main.tex
Use PLOS style guidelines
- Remove section headings
- Move all input files to main text;
- Move graphics files
- Add extra images to appendix

% Template for PLoS
% Version 3.4 January 2017
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended
% to minimize problems and delays during our production
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% Once your paper is accepted for publication,
% PLEASE REMOVE ALL TRACKED CHANGES in this file
% and leave only the final text of your manuscript.
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file.
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column.
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace}
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr}
\usepackage{graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\usepackage{algorithm,algorithmic}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{booktabs}
\usepackage{booktabs}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{pdflscape}
\usepackage{standalone}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{xstring}

\usetikzlibrary{calc, shapes, patterns}

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline
{Evolution reinforces cooperation with the emergence of self-recognition
 mechanisms: an empirical study of strategies in the Moran process for the
 iterated prisoner's dilemma }
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Vincent Knight\textsuperscript{1*\Yinyang},
Marc Harper\textsuperscript{2\Yinyang},
Nikoleta E. Glynatsi\textsuperscript{2\ddag},
Owen Campbell\textsuperscript{3\ddag},
\\
\bigskip
\textbf{1} Cardiff University, School of Mathematics, Cardiff, UK
\\
\textbf{2} Google Inc., Mountain View, CA, USA
\\
\textbf{3} Independent Researcher, Chester, UK
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
\ddag These authors also contributed equally to this work.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* knightva@cardiff.ac.uk

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
    We present insights and empirical results from an extensive numerical
    study of the evolutionary dynamics of the iterated prisoner's dilemma.
    Fixation probabilities for Moran processes are obtained
    for all pairs of 164 different strategies including classics such as TitForTat, zero
    determinant strategies, and many more sophisticated strategies.
    Players with long memories and sophisticated behaviours outperform
    many strategies that perform well in a two player setting. Moreover we
    introduce several strategies trained with evolutionary algorithms to
    excel at the Moran process. These strategies are excellent invaders
    and resistors of invasion and in some cases naturally evolve handshaking
    mechanisms to resist invasion. The best invaders were those trained
    to maximize total payoff while the best resistors invoke handshake mechanisms.
    This suggests that while maximizing individual payoff
    can lead to the evolution of cooperation through invasion, the relatively
    weak invasion resistance of payoff maximizing strategies are not as
    evolutionarily stable as strategies employing handshake mechanisms.
\linenumbers

\section*{Introduction}

The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
used to model a variety of strategic interactions. Each player chooses
simultaneously and independently
between cooperation (C) or defection (D). The payoffs of
the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one
round game, but is commonly studied in a manner where the prior outcomes
matter. This repeated form is called the Iterated Prisoner's
Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
number of strategies have been developed to take advantage of the history of
play. Strategies referred to as zero determinant (ZD) strategies
\cite{Press2012} can manipulate some players through extortionate mechanisms.

The Moran Process \cite{Moran1957} is a model of
evolutionary population dynamics that has been used to gain insights about the
evolutionary stability in a number of settings.
Several earlier
works have studied iterated games in the context of the prisoner's dilemma
\cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
or are limited to classes of strategies
such as memory-one strategies that only use the previous round of play.

This manuscript provides a detailed numerical analysis of agent-based simulations
of \textbf{164} complex and adaptive strategies for the
IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
effort to provide software for reproducible research for the IPD\@. The library
now contains over 186 parameterized
strategies including classics like TitForTat and WinStayLoseShift, as well as
recent variants such as OmegaTFT, zero determinant and other memory one
strategies, strategies based on finite state machines, lookup tables, neural
networks, and other machine learning based strategies, and a collection of novel
strategies. Not all strategies have been considered for this study: excluded
are those that make use of knowledge of the number of turns in a match
and others that have a high
computational run time. The large number of strategies are available thanks to
the open source nature of the project with over 50 contributors from around the
world, made by programmers and researchers \cite{Knight2016}. Three of the considered
strategies are finite state machines trained specifically for Moran processes
(described further in the Methods section).

In addition to providing a large collection of strategies, the Axelrod library
can conduct matches, tournaments and population
dynamics with variations including noise and spatial structure.
The strategies and simulation frameworks are
automatically tested to an extraordinarily high degree of coverage in accordance
with best research software practices.

Using the Axelrod library and the many strategies it contains, we obtain the
probability with which a given strategy takes over a population (referred to as
fixation probability) for all pairs of strategies, identifying those that are
effective invaders and those resistant to invasion, for population sizes $N=2$
to $N=14$. Moreover we present a number (16) of strategies that were created via
reinforcement algorithms (evolutionary and particle swarm algorithms) that are
among the best invaders and resistors of invasion known to date, and show that
handshaking mechanisms naturally arise from these processes as an
invasion-resistance mechanism.

In 2016, work has argued that agent-based
simulations can provide insights in evolutionary game theory not available
via direct mathematical analysis~\cite{adami2016evolutionary}. The results
and insights contained in this paper would be difficult to derive analytically.

In particular the following questions are addressed:
\begin{enumerate}
    \item What strategies are good invaders?
    \item What strategies are good at resisting invasion?
    \item How does the population size affect these findings?
\end{enumerate}

While the results agree with some of the published literature, it is found that:

\begin{enumerate}
 \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
 \item Complex strategies can be effective, and in fact can naturally evolve
     through evolutionary processes to outperform designed strategies.
 \item The strongest resistors specifically evolve or possess a handshake mechanism.
 \item Strong invaders are generally cooperative strategies that do not defect
 first but retaliate to varying degrees of intensity against strategies that defect.
 \item Strategies evolved to maximize their total payoff can be strong invaders
 and achieve mutual cooperation with many other strategies.
\end{enumerate}

\section*{Materials and methods}
\subsection*{The Moran Process}

A Moran process is a stochastic birth death process on a finite population in which the
population size stays constant over time. Individuals are \textit{selected}
according to a given fitness landscape. The fitness landscape in this work is
defined as the total utility against all other individuals in the population.
Once selected, the individual
is reproduced and similarly another individual is chosen to be removed from the
population (a uniform random selection is used). This is shown diagrammatically
in Fig~\ref{fig:moran_process}. In some settings mutation is
also considered but without mutation (the case considered in this work) this
process will arrive at an absorbing state where the population is entirely made
up of players of one strategy. The probability with which a given strategy,
starting from a single individual takes
over a population is called the \textit{fixation probability}. A more detailed
analytic description of this is given later. In our
simulations offspring do not inherit any knowledge or history from parent
replicants.

\begin{figure}[!hbtp]
    \centering
    \scalebox{.5}{

\begin{tikzpicture}[scale=.9]
	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
        color=blue!70, draw=blue] {};
	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};
	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
        color=red!70, draw=red] {};

	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (B4) circle (.25cm);

	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (B4) circle (.25cm);
	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);

	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (A3) circle (.25cm);

	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};

	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (A3) at ($(A3) + (4.5, 0)$) {};
	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
        pattern color=blue!70, draw=blue] {};
	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};
	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
        pattern color=red!70, draw=red] {};

	\draw [dotted, very thick] (A3) circle (.25cm);
\end{tikzpicture}

}
    \caption{A diagrammatic representation of a Moran process.}
    \label{fig:moran_process}
\end{figure}

The Moran process was initially introduced in \cite{Moran1957}. It has since
been used in a variety of settings including the understanding of the spread of
cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
However these works mainly consider relatively simple strategies. A few works
looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
\cite{Li2014} but this is not done in the more widely used setting of the Moran
process, rather in terms of infinite population stability. In \cite{Baek2016}
Moran processes are studied in a theoretical framework for a small subset of
strategies. The subset included memory one strategies: strategies that recall
the events of the previous round only.

Of particular interest are the zero determinant strategies introduced in
\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
a strategy using machine learning techniques was capable of resisting invasion
and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
has investigated the effect of memory length on strategy performance and the
emergence of cooperation but this is not done in a Moran process context and only
considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
recognised that many zero determinant strategies do not fare well against
themselves. This is a disadvantage for the Moran process where the best
strategies cooperate well with other players using the same strategy.

This work uses pair-wise Moran processes in a similar way to matches in the many
IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
A population-based perspective is given which adds additional
evolutionary components to the IPD, namely the evolutionary dynamics of invasion
and resistance.

\subsection*{Strategies considered}\label{sec:strategies}

To carry out this numerical experiment, 164
strategies, listed (with their properties) in the Appendix,
are used from the Axelrod library. There are
43 stochastic and
121 deterministic strategies. Their memory depth,
defined by the number of rounds of history used by the strategy each round, is
shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
strategy uses the entire history of play (whatever its length). For example, a
strategy that utilizes a handshaking mechanism where the opponent's actions on
the first few rounds of play determines the strategies subsequent behavior would
have infinite memory depth.

A number of these strategies have been trained with reinforcement learning
algorithms prior to this study and not specifically for the Moran process.

\begin{itemize}
    \item Evolved ANN: a neural network based strategy;
    \item Evolved LookerUp: a lookup table based strategy;
    \item PSO Gambler: a stochastic version of the lookup table based strategy;
    \item Evolved HMM: a hidden Markov model based strategy.
\end{itemize}

Apart from the PSO Gambler strategy, which was trained using a particle swarm
optimisation algorithm, these strategies are trained with an evolutionary
algorithm that perturbs strategy parameters and optimizes the mean total score
against all other opponents \cite{affenzeller2009genetic}. They were trained to
win IPD tournaments by maximizing their mean total payoffs against a variety
of opponents. Variation is
introduced via mutation and crossover of parameters, and the best performing
strategies are carried to the next generation along with new variants. Similar
methods appear in the literature \cite{Ashlock2006}.
There has also been some work on strategies using an evolutionary algorithm in real time:
in~\cite{Gaudesi2016}
an evolutionary algorithm is used to build a model of the opponent and attempt
to exploit any potential weakness. In this work all strategies resulting from
evolutionary algorithms are pre-trained.

More information about each player can be obtained in the documentation for
\cite{axelrodproject} and a detailed description of the performance
of these strategies in IPD tournaments is described in~\cite{Harper2017}.

All of the training code is archived at \cite{marc_harper_2017_824264}. This
software is (similarly to the Axelrod library) available on
github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
with documentation to
train new strategies easily. Training
typically takes less than 100 generations and can be completed within several
hours on commodity hardware.

There are three further strategies trained specifically for this study; Trained
FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
and~\ref{fig:tf3}), using the notation common in the literature where
\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
\(A_2\) as well as arrows corresponding to changes of state.

\begin{figure}[!hbtp]
    \centering
    \scalebox{.7}{
    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};

	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};

	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};

	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};

	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};

    \coordinate[left of=0] (s);

    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);

    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);

    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);

    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);

    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);

    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);

    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);

    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);

    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);

    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);

    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);

    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);

    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);

    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);

    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);

    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);

    \end{tikzpicture}
    }
    \caption{TF1: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 4.}
    \label{fig:tf1}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \scalebox{.7}{

    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};

	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};

    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};

    \coordinate[below of=0] (s);

    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);

    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);

    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);

    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);

    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/D$} (1);

    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);

    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);

    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);

    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);

    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);

    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);

    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);

    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);

    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);

    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);

    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);

    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);

    \end{tikzpicture}
    }
    \caption{TF2: a 16 state finite state machine with a handshake leading to
    mutual cooperation at state 16.}
    \label{fig:tf2}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{tikzpicture}

    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];

    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$}; 
    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};  
    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};

    \coordinate[left of=0] (s);

    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);

    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);

    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);

    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);

    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
    \end{tikzpicture}
    \caption{TF3: an 8 state finite state machine.}
    \label{fig:tf3}
\end{figure}

As opposed to the previously described strategies, these strategies were trained
with the objective function of \textit{mean fixation probabilities for Moran
processes} starting at initial population states consisting of \(N/2\)
individuals of the training candidates and \(N/2\) individuals of an opponent
strategy, taken from a selection of 150 opponents from the Axelrod library:

\begin{itemize}
	\item TF1 \(N=12\), 0\% noise.
	\item TF2 \(N=10\), 0\% noise.
	\item TF3 \(N=8\), 1\% noise.
\end{itemize}

The trained algorithms
were run for fewer than 50 generations. Training data for this is available at
\cite{data}.

TF1 has an initial handshake of CCD and cooperates if the opponent matches.
However if the opponent later defects, TF1 will respond in kind, so the
handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
very similar to a strategy known as ``Collective Strategy'', which has a
handshake of CD and cooperates with opponents that matched the handshake
until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
Collective Strategy was specifically designed for evolutionary processes.

TF2 always starts with CD and will defect against opponents that start with
DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
can be rescued after a failed handshake by a complex sequence of plays
which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
GTFT, and a few others with low probability. TF2 defects against all other
players in the study, barring
unusual cases arising from particular randomizations. Fig~\ref{fig:tf2} shows
all 16 states of the strategy (states 6 and 7 are not reachable).

TF3 cooperates and defects with
various cycles depending on the opponent's actions. TF3 will mutually
cooperate with any strategy and only tolerates a few defections before
defecting for the rest of match. It is similar to but not exactly the same as
Fool Me Once, a strategy that cooperates until the opponent has defected twice
(not necessarily consecutively), and defects indefinitely thereafter. Though a
product of training with a Moran objective, it differs from TF1 and TF2
in that it lacks a handshake mechanism. Fig~\ref{fig:tf3} shows
all 8 states of the strategy produced by the training process (states 3 and 8
are not reachable).

For both TF1 and TF2 a handshake
mechanism naturally emerges from the structure of the underlying finite state
machine. This behavior is an outcome of the evolutionary process and is in no
way hard-coded or included via an additional mechanism.

\begin{table}[!hbtp]
    \centering
        \scalebox{0.7}{
            \begin{tabular}{lrrrrrrrrrrrrrrrr}
            \toprule
            Memory Depth &   0   &   1   &   2   &   3   &   4   &   5   &   6   &   9   &   10  &   11  &   12  &   16  &   20  &   40  &   200 &  \(\infty\)   \\
            \midrule
            Count &     3 &    29 &    12 &     8 &     2 &     6 &     1 &     1 &     5 &     1 &     1 &     2 &     2 &     2 &     1 &    88 \\
            \bottomrule
            \end{tabular}
        }
        \caption{Memory depths}
        \label{tbl:memory_depth_count}
\end{table}

\subsection*{Data collection}

Each strategy pair is run for 1000 repetitions of the Moran process to fixation
with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
computed for each combination of starting distribution and value of \(N\).  The
Axelrod library can carry out exact simulations of the Moran process. Since some
of the strategies have a high computational cost or are stochastic, samples are
taken from a large number of 200 turn match outcomes for the pairs of players
for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
matches is used). This approach was verified to agree with unsampled
calculations to a high degree of accuracy in specific cases.  This is described
in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.

\begin{algorithm}[!hbtp]
        \caption{Data Collection}
        \label{alg:data_collection}
          \begin{algorithmic}[1]
            \FOR{player\_one \textbf{in} players\_list}
              \FOR{player\_two \textbf{in} (players\_list - player\_one)}
                \STATE pair $\gets$ (player\_one, player\_two)
                \FOR{starting\_population\_distributions \textbf{in} [$(1, N-1), (\frac{N}{2}, \frac{N}{2}), (N-1, 1)]$}
                \WHILE {repetitions $\leq 1000$}
                \STATE \textbf{simulate} moran process (pair, starting distribution)
                \ENDWHILE
                \STATE\textbf{yield} fixation probabilities
                \ENDFOR
              \ENDFOR
            \ENDFOR
          \end{algorithmic}
\end{algorithm}

\begin{algorithm}[!hbtp]
        \caption{Moran process}
        \label{alg:moran_process}
          \begin{algorithmic}[1]
          \STATE initial population $\gets$ (pair, starting distribution) \
          \STATE population $\gets$ initial population

            \WHILE {population not uniform}
              \FOR{player in population}
              \FOR{opponent in (population - player)}
                \STATE match $\gets$ (player, opponent) 
                \STATE results $\gets$ stochastic\_cache (200 round match)
                \ENDFOR
              \ENDFOR
              \STATE population $\gets$ sorted(results)
              \STATE parent $\gets$ selected randomly in proportion to its total match payoffs
              \STATE offspring $\gets$ parent
              \STATE kill off $\gets$ uniformly random player from population
              \STATE population $\gets$ offspring replaces kill off
            \ENDWHILE
          \end{algorithmic}
\end{algorithm}

The next section will further validate the methodology by comparing
simulated results to analytical results in a few selected cases. The main
results of this
manuscript are presented in which will
present a detailed analysis of all the data generated. Finally,
a discussion and conclusion will offer future avenues for the work
presented here.

\section*{Results}

\subsection*{Validation}

As described in \cite{Nowak} consider the payoff matrix:

\begin{equation}\label{equ:payoff_matrix}
    M = \begin{pmatrix}
        a, b\\
        c, d
        \end{pmatrix}
\end{equation}

The expected payoffs of \(i\) players of the first type in a population with \(N
- i\) players of the second type are given by:

\begin{equation}\label{equ:expected_payoff_one}
    f_i = \frac{a(i - 1) + b(N - i)}{N - 1}
\end{equation}

\begin{equation}\label{equ:expected_payoff_two}
    g_i = \frac{ci + d(N - i - 1)}{N - 1}
\end{equation}

The transitions within the birth death process that underpins the Moran process
are then given by:

\begin{align}
    p_{i, i+1}&= \frac{if_i}{if_i+(N-i)g_i}\frac{N-i}{N}\label{equ:p_up}\\
    p_{i, i-1}&= \frac{(N-i)g_i}{if_i+(N-i)g_i}\frac{i}{N}\label{equ:p_down}\\
    p_{ii} &= 1 - p_{i, i+1} - p_{i, i-1}\label{equ:p_stay}
\end{align}

Using this the fixation probability
of the first strategy in a population of \(i\) individuals of the first type
and \(N-i\) individuals of the second, is given by \cite{Nowak2017}:

\begin{equation}\label{equ:fixation_probability}
x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}
      \prod_{k=1}^{j}\gamma_j}
\end{equation}

where:

\[
\gamma_j = \frac{p_{j, j-1}}{p_{j, j+1}}
\]

A neutral strategy will have fixation probability $x_i = i/N$.

Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
confidence interval computed using an asymptotic normal approximation is also
included \cite{brown2001interval}).
The points represent the simulated
values and the line shows the theoretical value. Note that these are
deterministic strategies and show a good match between the expected value
of (\ref{equ:fixation_probability}) and the actual Moran process for all
strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
fact that the theoretic and simulated values are a good match.

Fig~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
good match (confirmed with a \(t\)-test in
Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
a given interaction between two IPD strategies can be summarised with a set of
utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
given pair and can be quite a complex endeavour for stochastic strategies with
long memory: this is not necessary for the purposes of this work.  All data
generated for this validation exercise can be found at~\cite{data}.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textit{deterministic} strategies: Alternator and
         Cooperator. 5\% confidence intervals calculated using an asymptotic
     normal approximation.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(x_{1}\).}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{table}[!hbtp]
    \centering

        \begin{tabular}{rrrr}
        \toprule
          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
        \midrule
          2 &          0.89942 &                0.89942 &                0.89942 \\
          4 &          0.16344 &                0.74768 &                0.85877 \\
          6 &          0.65406 &                0.84051 &                0.51992 \\
          8 &          0.92617 &                0.45748 &                0.38604 \\
         10 &          0.03505 &                0.37115 &                0.60635 \\
         12 &          0.96697 &                0.20790 &                0.18124 \\
         14 &          0.08126 &                0.63771 &                0.76246 \\
         16 &          0.59434 &                0.07697 &                0.42520 \\
         18 &          0.05339 &                0.47126 &                0.94814 \\
         20 &          0.30805 &                0.79795 &                0.82381 \\
        \bottomrule
        \end{tabular}

    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
        value with the simulated value of the Moran Process fixation
        probabilities for \textit{deterministic} strategies: Alternator and
    Cooperator.}
    \label{tab:comparison_deterministic}
\end{table}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
    \caption{Comparison of theoretic and actual Moran Process
             fixation probabilities for \textit{stochastic} strategies:
             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
     normal approximation.
The top most line on all figures (in red and using a circle) corresponds to
\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
\(x_{1}\).}
    \label{fig:comparison_stochastic}
\end{figure}

\begin{table}[!hbtp]
    \centering
        \begin{tabular}{rrrr}
        \toprule
          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
        \midrule
          2 &          0.05372 &                0.05372 &                0.05372 \\
          4 &          0.34188 &                0.00940 &                0.00005 \\
          6 &          0.16510 &                0.00000 &                0.00000 \\
          8 &          0.03451 &                0.00000 &                0.00000 \\
         10 &          0.00543 &                0.00000 &                0.00000 \\
         12 &          0.19646 &                0.00000 &                0.00000 \\
         14 &          0.00814 &                0.00000 &                0.00000 \\
         16 &          0.01038 &                0.00000 &                0.00000 \\
         18 &          0.39556 &                0.00000 &                0.00000 \\
         20 &          0.00030 &                0.00000 &                0.00000 \\
        \bottomrule
        \end{tabular}
    \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
        value with the simulated value of the Moran Process fixation
        probabilities for \textit{stochastic} strategies: Calculator and
    Arrogant Q Learner.}
    \label{tab:comparison_stochastic}
\end{table}

\subsection*{Empirical results}

This section outlines the data analysis carried out, all data for this study is
available at~\cite{data}.

\begin{itemize}
    \item First the specific case of
        \(N=2\) is considered.
    \item The effect of
        population size on the ability of a strategy to invade another
        population is investigated. This will highlight how complex strategies with long
        memories outperform simpler strategies.
    \item Then a similar investigation of the
        ability to defend against an invasion is given.
    \item Finally the relationship
        between performance for differing population sizes as well as
        taking a close look at zero determinant strategies \cite{Press2012} is
        analysed.
\end{itemize}

\subsubsection*{The special case of \(N=2\)}

When $N=2$ the fixation probabilities of the Moran process are effectively measures
of the distribution of  relative
mean payoffs over all possible matches between two players. The strategy
that scores higher than the other more often will fixate more often. For \(N=2\)
the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
considered separately for larger \(N\) in the following sections.
The top 16 (10\%) strategies are
shown in

Table~\ref{tbl:summary_top_2} and figures showing the performance of all
strategies are available in the appendix.
The top five ranking strategies are:

\begin{enumerate}
    \item The top strategy is the Collective Strategy (CS) which has a simple
        handshake mechanism described above.
    \item Defector: it always defects. Since it has no interactions with other
        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
    \item Aggravater, which plays like Grudger (responding to any
        defections with unconditional defections throughout) however starts by
        playing 3 defections.
    \item Predator, a finite state machine described in \cite{Ashlock2006}.
    \item Handshake, a slightly less aggressive version of the Collective
        Strategy \cite{Robson1990}. As long as the initial sequence is played
        then it cooperates. Thus it will do well in a population consisting of
        many members of itself just as the Collective Strategy does. The
        difference is that CS will defect after the handshake if the opponent
        defects while Handshake will not.
\end{enumerate}

It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
for which a zero determinant strategy does appear in the top 10\% ranking
strategies: ZD-extort-4. The performance of zero determinant strategies will be
examined more closely.

\begin{table}[!hbtp]
    \tiny
    \centering
    \scalebox{0.95}{
        \begin{tabular}{llrrrrrrr}
        \toprule
        {} &                  Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
        \midrule
        1  &                      CS &  0.497 &  0.5020 &  0.6651 &   0.572 &  0.9908 &  0.993 &  0.1800 \\
        2  &                Defector &  0.502 &  0.5020 &  0.6496 &   0.518 &  1.0000 &  1.000 &  0.1767 \\
        3  &              Aggravater &  0.502 &  0.5020 &  0.6328 &   0.518 &  0.9790 &  0.999 &  0.1660 \\
        4  &                Predator &  0.319 &  0.4980 &  0.6301 &   0.551 &  0.9870 &  0.993 &  0.1676 \\
        5  &               Handshake &  0.006 &  0.4503 &  0.6240 &   0.524 &  0.9908 &  0.993 &  0.1889 \\
        6  &                Prober 4 &  0.431 &  0.4620 &  0.6183 &   0.534 &  0.9579 &  0.958 &  0.1656 \\
        7  &                     \textbf{TF1} &  0.430 &  0.4980 &  0.6171 &   0.544 &  0.9240 &  0.981 &  0.1345 \\
        8  &                Prober 3 &  0.497 &  0.5011 &  0.6044 &   0.505 &  0.9930 &  0.993 &  0.1683 \\
        9  &                     \textbf{TF2} &  0.324 &  0.5020 &  0.6026 &   0.565 &  0.8362 &  0.887 &  0.1092 \\
        10 &                 Grudger &  0.497 &  0.5020 &  0.5996 &   0.502 &  0.9840 &  0.989 &  0.1695 \\
        11 &       Better and Better &  0.388 &  0.3951 &  0.5980 &   0.514 &  0.9300 &  0.934 &  0.1865 \\
        12 &                    MEM2 &  0.497 &  0.5001 &  0.5942 &   0.502 &  0.9840 &  0.987 &  0.1656 \\
        13 &  Meta Hunter Aggressive &  0.247 &  0.2943 &  0.5933 &   0.517 &  0.9498 &  0.981 &  0.2013 \\
        14 &                     \textbf{TF3} &  0.344 &  0.4971 &  0.5927 &   0.502 &  0.9790 &  0.982 &  0.1617 \\
        15 &            Fool Me Once &  0.494 &  0.4980 &  0.5892 &   0.502 &  0.9790 &  0.982 &  0.1625 \\
        16 &             ZD-Extort-4 &  0.497 &  0.5020 &  0.5867 &   0.584 &  0.6900 &  0.695 &  0.0724 \\
        \bottomrule
        \end{tabular}
    }
    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
    \label{tbl:summary_top_2}
\end{table}

As will be demonstrated the results for
\(N=2\) differ from those of larger $N$. Hence these results do not concur with
the literature which suggests that zero determinant strategies should be
effective for larger population sizes, but these analyses consider stationary
behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
The stationarity assumption allows for a deterministic payoff matrix
leading to the conclusions about zero determinant strategies in the space
of memory-one strategies that do not generalize to this context.

% In the next sections close attention to
% strategies who are strong invaders/resistors is given.

\subsubsection*{Strong Invaders}

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\).

The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
figures showing the performance of all strategies is available in the
appendix.

\begin{table}[!hbtp]
    \centering
    \tiny
    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=3\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=7\)}
    \end{subfigure}

    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
    \label{tbl:top_invade}
\end{table}

It can be seen that apart from CS, none of the strategies for \(N=2\)
of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
top performing strategies are:

\begin{itemize}
    \item Grudger (which only performs well for \(N=3\)), starts by cooperating
        but will defect if at any point the opponent has defected.
    \item MEM2, an infinite memory strategy that switches between TFT, TF2T, and
        Defector \cite{Li2014}.
    \item TF3, the finite state machine trained specifically for Moran processes
        described.
    \item Prober 4, a strategy which starts with a specific 20 move sequence of
        cooperations and defections \cite{Prison1998}. This initial sequence serves
        as approximate handshake.
    \item  PSO Gambler and Evolved Lookerup 2 2 2: strategies that make use
        of a lookup table mapping the first 2 moves of the opponent as well as
        the last 2 moves of both players to an action.  PSO gambler is a
        stochastic version of  Lookerup which maps those states to probabilities
       of cooperating. Lookerup was described in \cite{Knight2016}.
    \item The Evolved ANN strategies are neural networks that map a number of
	    attributes (first move, number of cooperations, last move, etc.) to
	    an action. Both of these have been trained using an evolutionary
	    algorithm.
    \item Evolved FSM 16 is a 16 state finite state machine trained to
        perform well in tournaments.
\end{itemize}

Only one of the above strategies is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousin Evolved Looker Up.
PSO Gambler Mem1 is a stochastic memory one strategy that has been trained to
maximise its utility and does perform well.
Apart from TF3, the finite state machines trained specifically for
Moran processes do not appear in the top 5, while strategies trained for
tournaments do. This is due to the nature of invasion: most of the opponents
will initially be different strategies. The next section will consider the
converse situation.

\subsubsection*{Strong resistors}

In addition to identifying good invaders, strategies resistant to invasion by
other strategies are identified by examining the distribution of $x_{N-1}$ for
each strategy.

Table~\ref{tbl:top_resist} shows the top strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
for all strategies are available in the supplementary materials.
Once again none of the short memory strategies previously discussed perform well for high \(N\).

\begin{table}[!hbtp]
    \tiny
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=3\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=7\)}
    \end{subfigure}

    \begin{subfigure}[t]{\columnwidth}
        \centering
        \begin{tabular}{llrrrrrrr}
        \toprule
        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
        \midrule
        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
        \bottomrule
        \end{tabular}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
    \label{tbl:top_resist}
\end{table}

Interestingly none of these strategies are stochastic: this is explained by the
value of not provoking typically cooperative opponent strategies with
speculative defections. This includes opponents using the same strategy.  Acting
stochastically increases the chance of reducing the score of individuals of the
same type in a Moran process.  However it is possible to design a strategy with
a stochastic or error-correcting handshake that is an excellent resistor even in
noisy environments \cite{Lee2015}.

There are only two new strategies that appear in the top ranks for
\(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
resistors. They all have handshakes, and whilst the handshakes of CS and
Handshake (which ranks highly for the smaller values of \(N\)) were
programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
process without any priming.

As described previously the strategies trained with
the payoff maximizing objective are among the best invaders in the library
however they are not as resistant to invasion as the strategies trained using a
Moran objective function. These strategies include trained finite state machine
strategies, but they do not appear to have handshaking mechanisms. Therefore it
is reasonable to conclude that the objective function is the cause of the
emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
handshakes for high invasion resistance. TF3 is a better total payoff maximizer
which makes it a better invader along with the strategies
trained to maximize total payoff since successful fitness proportionate selection
is necessary for invasion. Training with an objective with initial population
mix other than $(N/2, N/2)$ may favor invasion or resistance.

The payoff maximizing strategies typically will not defect before the opponent's
first defection, possibly because the training strategy collection contains some
strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
for the remainder of the match if the opponent has more than a small number of
cumulative defections. Paradoxically for handshaking strategies
it is advantageous to defect (as a signal)
in order to achieve mutual cooperation with opponents using the same strategy
but not with other opponents. Nevertheless an evolutionary process is able to
tunnel through the costs and risks associated with early defections to find more
optimal solutions, so it is not surprising in hindsight that handshaking
strategies emerge from the evolutionary training process.

A handshake requires at least one defection and there is
selective pressure to defect as few times as possible to achieve the
self-recognition mechanism. It is also unwise to defect on the first move as
some strategies additionally retaliate in response to first round defections. So the
handshakes used by TF1, TF2, and CS are in some sense optimal.

It is evident through
the work presented that performance of strategies not only depends
on the initial population distribution but also that there seems to be a
difference depending on whether or not \(N>2\). This will be explored further in
the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also
considering
\(x_{N/2}\).

\subsubsection*{The effect of population size}

Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
strategies:

\begin{itemize}
    \item The strategies that ranked highly for \(N=2\);
    \item The strategies that ranked highly for \(N=14\);
    \item The zero determinant strategies.
\end{itemize}

The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
expected since, as described previously these strategies
were trained in an initial population of \((N/2, N/2)\) individuals.

For all starting populations
\(i\in\{1, N/2, N-1\}\) the ranks of strategies are relatively stable across the
different values of \(N>2\) however for \(N=2\) there is a distinct difference.
This highlights that there is little that can be inferred about the evolutionary
performance of a strategy in a large population from its performance in a small
population. This is confirmed by the performance of the zero determinant strategies: while
some do rank relatively highly for \(N=2\) (ZD-Extort-4 has rank 16) this rank
does not translate to larger populations.

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \scalebox{0.7}{
        \begin{tabular}{lrrrrrrrrrrrrr}
        \toprule
                         Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
        \midrule
                           CS &    1 &    1 &    2 &   11 &    9 &   11 &   13 &   21 &   16 &   22 &   17 &   25 &   23 \\
                     Defector &    2 &   43 &   80 &   91 &   89 &   87 &   87 &  103 &   97 &  105 &   94 &  103 &  101 \\
                   Aggravater &    3 &   50 &   89 &   99 &  102 &  103 &  108 &  113 &  114 &  115 &  115 &  116 &  117 \\
                     Predator &    4 &    8 &   24 &   35 &   28 &   33 &   31 &   43 &   36 &   43 &   34 &   45 &   35 \\
                    Handshake &    5 &   17 &   40 &   46 &   43 &   46 &   46 &   49 &   48 &   49 &   47 &   50 &   49 \\
        \midrule
               Evolved FSM 16 &   31 &   11 &    6 &    2 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
            PSO Gambler 2\_2\_2 &   29 &   14 &   10 &    6 &    4 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
         EvolvedLookerUp2\_2\_2 &   33 &   18 &   11 &    9 &   10 &    6 &    6 &    5 &    3 &    5 &    3 &    3 &    3 \\
                  Evolved ANN &   20 &   10 &    8 &    7 &    8 &    5 &    3 &    3 &    4 &    3 &    4 &    4 &    4 \\
                Evolved ANN 5 &   21 &    9 &    7 &    8 &    7 &    4 &    5 &    4 &    5 &    4 &    5 &    5 &    5 \\
        \midrule
                          \textbf{TF1} &    7 &   13 &   33 &   38 &   30 &   39 &   42 &   46 &   42 &   46 &   41 &   46 &   46 \\
                          \textbf{TF2} &    9 &   19 &   29 &   33 &   19 &   28 &   29 &   38 &   27 &   34 &   26 &   32 &   30 \\
                          \textbf{TF3} &   14 &    4 &    5 &    5 &    6 &    9 &   11 &   11 &   12 &   14 &   13 &   13 &   16 \\
        \midrule
                  ZD-Extort-4 &   16 &   81 &  107 &  120 &  135 &  136 &  142 &  140 &  142 &  142 &  144 &  144 &  145 \\
               ZD-Extort-2 v2 &   41 &  105 &  126 &  140 &  152 &  152 &  153 &  152 &  153 &  153 &  153 &  152 &  153 \\
                  ZD-Extort-2 &   43 &  107 &  125 &  139 &  151 &  151 &  152 &  153 &  152 &  152 &  152 &  153 &  152 \\
                     ZD-SET-2 &  100 &  111 &  117 &  117 &  122 &  127 &  131 &  128 &  131 &  131 &  130 &  132 &  131 \\
                    ZD-GTFT-2 &  112 &   92 &   82 &   80 &   81 &   82 &   84 &   72 &   81 &   71 &   78 &   72 &   70 \\
                     ZD-GEN-2 &  113 &   96 &   87 &   83 &   85 &   88 &   90 &   82 &   87 &   82 &   86 &   83 &   91 \\
        \bottomrule
        \end{tabular}
    }
    \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
    population sizes}
    \label{tbl:ranks_v_size_invade}
\end{table}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \scalebox{0.7}{
        \begin{tabular}{lrrrrrrrrrrrrr}
        \toprule
                   Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
        \midrule
                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
               Defector &    2 &   29 &   55 &   79 &   94 &   97 &   98 &   98 &  102 &  101 &  103 &  100 &  102 \\
             Aggravater &    3 &   42 &   71 &   97 &  101 &  106 &  107 &  111 &  113 &  113 &  116 &  115 &  115 \\
               Predator &    4 &    2 &    3 &    3 &    3 &    4 &    4 &    4 &    4 &    4 &    4 &    4 &    4 \\
              Handshake &    5 &    4 &    5 &    5 &    5 &    5 &    5 &    6 &    6 &    6 &    6 &    6 &    6 \\
        \midrule
                    \textbf{TF1} &    7 &    3 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
                    \textbf{TF2} &   10 &    5 &    4 &    4 &    4 &    3 &    3 &    3 &    3 &    3 &    3 &    3 &    3 \\
               Prober 4 &    6 &    6 &    6 &    6 &    6 &    6 &    6 &    5 &    5 &    5 &    5 &    5 &    5 \\
        \midrule
                    \textbf{TF3} &   13 &    9 &   10 &   11 &   11 &   11 &   13 &   14 &   13 &   13 &   13 &   13 &   13 \\
        \midrule
            ZD-Extort-4 &   19 &   68 &   98 &  106 &  108 &  114 &  115 &  115 &  118 &  118 &  117 &  118 &  117 \\
         ZD-Extort-2 v2 &   49 &   98 &  111 &  121 &  123 &  124 &  124 &  130 &  130 &  132 &  134 &  132 &  134 \\
            ZD-Extort-2 &   50 &   97 &  112 &  123 &  124 &  125 &  123 &  126 &  131 &  131 &  132 &  133 &  133 \\
               ZD-SET-2 &  108 &  105 &  104 &  104 &  103 &  103 &  100 &  100 &  101 &   99 &   98 &   98 &   98 \\
              ZD-GTFT-2 &  112 &   95 &   88 &   84 &   75 &   72 &   71 &   73 &   71 &   71 &   67 &   68 &   68 \\
               ZD-GEN-2 &  114 &   96 &   89 &   86 &   77 &   75 &   72 &   74 &   72 &   72 &   68 &   69 &   69 \\
        \bottomrule
        \end{tabular}
    }
    \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
    population sizes}
    \label{tbl:ranks_v_size_resist}
\end{table}

\begin{table}[!hbtp]
    \centering
    \scriptsize
        \begin{tabular}{lrrrrrrr}
        \toprule
                   Size &      2 &      4 &      6 &      8 &     10 &     12 &     14 \\
        \midrule
                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    2 \\
               Defector &    2 &   78 &   99 &  106 &  110 &  113 &  120 \\
             Aggravater &    3 &   91 &  105 &  111 &  122 &  125 &  128 \\
               Predator &    4 &    2 &    4 &    4 &    4 &    4 &    4 \\
              Handshake &    5 &    6 &    5 &    6 &    6 &    6 &    6 \\
        \midrule
                    \textbf{TF2} &    9 &    4 &    3 &    2 &    2 &    2 &    1 \\
                    \textbf{TF1} &    7 &    3 &    2 &    3 &    3 &    3 &    3 \\
               Prober 4 &    6 &    5 &    6 &    5 &    5 &    5 &    5 \\
        \midrule
                    \textbf{TF3} &   14 &    8 &    8 &    8 &    8 &    8 &    8 \\
        \midrule
            ZD-Extort-4 &   16 &  102 &  117 &  129 &  141 &  143 &  145 \\
         ZD-Extort-2 v2 &   41 &  118 &  135 &  151 &  152 &  152 &  153 \\
            ZD-Extort-2 &   43 &  117 &  136 &  149 &  151 &  151 &  152 \\
               ZD-SET-2 &  100 &  110 &  110 &  108 &  106 &  106 &  108 \\
              ZD-GTFT-2 &  112 &   82 &   80 &   77 &   75 &   75 &   74 \\
               ZD-GEN-2 &  113 &   85 &   81 &   82 &   79 &   77 &   76 \\
        \bottomrule
        \end{tabular}
    \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
    population sizes}
    \label{tbl:ranks_v_size_coexist}
\end{table}

Fig~\ref{fig:correlation_coefficients} shows the correlation coefficients
of the ranks of strategies in differing population size. How well a strategy
performs in any Moran process for \(N>2\) has
little to do with the performance for \(N=2\). This illustrates why the strong
performance of zero determinant strategies predicted in \cite{Press2012} does
not extend to larger populations. This was discussed theoretically in
\cite{Adami2013} and observed empirically in these simulations.

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
        \caption{Rank based on \(x_1\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
        \caption{Rank based on \(x_{N - 1}\)}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{.3\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
        \caption{Rank based on \(x_{N/2}\)}
    \end{subfigure}
    \caption{Heatmap of correlation coefficients of rankings by population size.}
    \label{fig:correlation_coefficients}
\end{figure}

\section*{Discussion}

Training strategies to excel
at the Moran process leads to the evolution of cooperation, but only with like
individuals in the case of TF1 and TF2. This may have significant implications
for various biological and social phenomena such as
human social interactions, particularly the evolution of ingroup/outgroup mechanisms
and other sometimes costly rituals that reinforce group behavior.

While TF1 and TF2 are competent invaders, the best invaders
in the study do not appear to employ strict handshakes, and are generally
cooperative strategies. TF3, which does not use a handshake, is a better invader
than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
of the same kind of training processes and is a better combined invader-resistor
than the invaders that were trained previously to maximize payout.

The strategies trained to maximize payoff in head-to-head matches are generally
cooperative and are effective invaders.
Combined with the fact that handshaking strategies are stronger resistors,
this suggests that while maximizing individual payoff can lead to the evolution
of cooperation, these strategies are not the most evolutionarily stable
in the long run. A strategy with a handshaking mechanism is still capable of
invading and is more resistant to subsequent invasions. Moreover, the
best resistor of the payoff maximally trained strategies (Evolved Looker Up
1\_1\_1),
which always defects if the opponent defects in the first round, is effectively
employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
which emerged from training memory one strategies for the Moran process,
also effectively employs a handshake of always cooperating, as it defects
for the remainder of the match if the opponent ever defects.

The insights that payoff maximizers are better invaders and that handshakers
are better resistors suggests that a strategy
aware of the population distribution could choose to become a handshaker at
a critical threshold and use a strategy better for invasion when in the
minority. Information about the population distribution was not available
to our strategies. Previous work has showed that strategies able to retain
memory across matches can infer the population distribution and act in such
a manner, resulting in a strategy effective at invasion and resistance
\cite{Lee2015}.

We did not attempt other objective functions that may serve to select for both
invasion and resistance better than training at a starting population of
$(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
improvement. Any handshake more sophisticated than always cooperate necessarily involves
a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
they need a longer or more strict handshake. But if this handshake involves
a defection then likely the invasion ability is diminished for $N > 2$: the top
invaders for larger $N$ are nice strategies that do not defect before their
opponents. This is because good invaders need to maximize match payoff to benefit
from fitness proportionate selection,
and so in the absence of a handshake mechanism, knowledge of the population
distribution, or some identifying label on the opponent,
a strategy must be generally cooperative. Aggressive strategies
are only effective invaders for the smallest $N$, dropping dramatically in rank
as the population size increases.

We did, however, attempt to evolve CS using finite state machines and lookup table
based players,
which resulted in some very similar strategies. In particular we evolved a
lookup strategy that had a handshake of DC and played TFT with other players
after a correct handshake while defecting otherwise, which is quite close in
function to CS (full grudging is not possible with a lookup table of limited
depth).

Finally we note that it may be possible to achieve similar results with smaller
capacity finite state machine players.

\section*{Conclusion}

A detailed empirical analysis of 164 strategies of the IPD within a pairwise
Moran process has been carried out. All \(\binom{164}{2}=13,366\) possible
ordered pairs of strategies have been placed in a Moran process with different
starting values allowing each strategy to attempt to invade the other.
This is the largest such experiment carried out and has led to many insights.

When studying evolutionary processes it is vital to consider \(N>2\) since
results for \(N=2\) cannot be used to extrapolate performance in larger
populations. This was shown both observationally
 but also by
considering the correlation of the ranks in different population sizes.

Memory one strategies do not perform as well as longer memory strategies in general
in this study. Several longer memory strategies were high performers for invasion,
particularly the strategies which have been trained using a number of reinforcement
learning algorithms. Interestingly they have been trained to perform well in
tournaments and not Moran processes specifically. In some cases these strategies
utilize all the history of play (the neural network strategies and the lookup
table strategies, the latter using the first round and some number of trailing rounds).

There are no memory one strategies in the top 5 performing strategies
for \(N>3\). Training memory-one strategies specifically for the Moran process
typically led to Grudger / Grim, a memory-one strategy with
four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
For comparison, training for maximum score difference between the player and the
opponent resulted in a strategy nearly the same as Grudger, with four-vector
$(0.9459, 0, 0, 0)$ (not included in the study).

One of the major findings discussed, is
the ability of strategies with a handshake mechanism to resist invasion. This
was not only revealed for CS (a human designed strategy) but also for
two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
process. In these two cases, the handshake mechanism was a product of the
evolutionary process. Fig~\ref{fig:cooperation_rates} shows the cooperation
rate of TF1, TF2, TF3 and CS
for each round of a match against all the opponents in this study.
This corresponds to the fraction of cooperation played by that strategy observed
in a given round (out of the first 15) where each matchup is repeated 10000 times to
obtain the mean.

While TF3
does not have a strict handshake mechanism it is clear that all these strategies
start a match by cooperating. It is then evident that TF3 cooperates more than
the other strategies thus explaining the difference in performance. It is also
clear that CS only cooperates with itself and Handshake: it is a very aggressive
strategy.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
        \caption{TF1}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
        \caption{TF2}
    \end{subfigure}

    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
        \caption{TF3}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.5\columnwidth}
        \centering
        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
        \caption{CS}
    \end{subfigure}
    \caption{Cooperation rate per round (over 10000 repetitions). Rows
        correspond to all the strategies considered in this work (ordered
    alphabetically by name). Columns correspond to round of an IPD match.}
    \label{fig:cooperation_rates}
\end{figure}

These findings are important for the ongoing understanding of
population dynamics and offer evidence for some of the shortcomings of low
memory which has started to be recognised by the community \cite{Hilbe2017}.

All source code for this work has been written in a sustainable manner: it is
open source, under version control and tested which ensures that all results can
be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
the processed data has also been properly archived and can be found
at \cite{data}.

There are many opportunities to build on this work. In particular, an analysis
of the effect of noise should offer insights regarding the stability of the findings,
particularly for the handshaking strategies. They may be less dominant for
larger amounts of noise since the handshaking mechanisms may become brittle.
There are many other variations to explore including populations with more
than one type, spatial structure, and mutation.

One final point to recognise: the large set of strategies used here does not in
itself constitute an authoritative set. Whilst it is not only large but also very
diverse, the results (and rankings) presented might change given a different set
of strategies. A further piece of work could look at subgroups of strategies and
how they fair against other subgroups. Note that because of the open nature of
the work here (not only is the source code archived but so is the data) this and
any other further analysis is possible to carry out.

\section*{Acknowledgements}

This work was performed using the computational facilities of the Advanced
Research Computing @ Cardiff (ARCCA) Division, Cardiff University.

A variety of software libraries have been used in this work:

\begin{itemize}
    \item The Axelrod library (IPD strategies and Moran processes)
        \cite{axelrodproject}.
    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
    \item The pandas and numpy libraries (data manipulation)
        \cite{mckinney2010data, walt2011numpy}.
\end{itemize}

\nolinenumbers

\begin{thebibliography}{10}

\bibitem{Adami2013}
Christoph Adami and Arend Hintze.
\newblock {Evolutionary instability of zero-determinant strategies demonstrates
  that winning is not everything.}
\newblock {\em Nature communications}, 4(1):2193, 2013.

\bibitem{adami2016evolutionary}
Christoph Adami, Jory Schossau, and Arend Hintze.
\newblock {Evolutionary game theory using agent-based methods}.
\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.

\bibitem{affenzeller2009genetic}
Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
  Practical Applications}.
\newblock Numerical Insights. CRC Press, 2009.

\bibitem{Nowak2017}
Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
  Shing-Tung Yau, and Martin~A Nowak.
\newblock {Evolutionary dynamics on any population structure}.
\newblock 544:227--230, March 2017.

\bibitem{Ashlock2015}
Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
  Agents}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 7(1):53--65, 2015.

\bibitem{Ashlock2008}
Daniel Ashlock and Eun-Youn Kim.
\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
  dilemma strategies}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
  2008.

\bibitem{Ashlock2006}
Wendy Ashlock and Daniel Ashlock.
\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
  with different population sizes}.
\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
  pages 297--304. IEEE, 2006.

\bibitem{Ashlock2014}
Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
\newblock {The evolution of exploitation}.
\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
  Symposium on}, pages 135--142. IEEE, 2014.

\bibitem{Axelrod1980a}
Robert Axelrod.
\newblock {Effective choice in the prisoner's dilemma}.
\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.

\bibitem{Axelrod1980b}
Robert Axelrod.
\newblock {More Effective Choice in the Prisoner's Dilemma}.
\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.

\bibitem{Axelrod1984}
Robert Axelrod.
\newblock {\em The Evolution of Cooperation}.
\newblock Basic books. Basic Books, 1984.

\bibitem{Baek2016}
{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
  A}.
\newblock {Comparing reactive and memory- one strategies of direct
  reciprocity}.
\newblock {\em Nature Publishing Group}, pages 1--13, 2016.

\bibitem{Banks1990}
Jeffrey~S Banks and Rangarajan~K Sundaram.
\newblock {Repeated games, finite automata, and complexity}.
\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.

\bibitem{Beaufils1997}
Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
\newblock {Our meeting with gradual, a good strategy for the iterated
  prisoner’s dilemma}.
\newblock In {\em Proceedings of the Fifth International Workshop on the
  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.

\bibitem{brown2001interval}
Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
\newblock Interval estimation for a binomial proportion.
\newblock {\em Statistical science}, pages 101--117, 2001.

\bibitem{Andre2013}
Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
\newblock pages 1--6, 2013.

\bibitem{Eckhart2015}
Arnold Eckhart.
\newblock Coopsim v0.9.9 beta 6.
\newblock https://github.com/jecki/CoopSim/, 2015.

\bibitem{Flood1958}
Merrill~M Flood.
\newblock {Some Experimental Games}, 1958.

\bibitem{Frean1994}
Marcus~R Frean.
\newblock {The prisoner's dilemma without synchrony}.
\newblock {\em Proceedings of the Royal Society of London B: Biological
  Sciences}, 257(1348):75--79, 1994.

\bibitem{Gaudesi2016}
Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
  dilemma tournaments}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 8(3):288--300, 2016.

\bibitem{marc_harper_2017_824264}
Marc Harper, Vince Knight, and Martin Jones.
\newblock Axelrod-python/axelrod-dojo: v0.0.1.
\newblock https://doi.org/10.5281/zenodo.824264, July 2017.

\bibitem{Harper2017}
Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
  Glynatsi, and Owen Campbell.
\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
  Prisoner's Dilemma}.
\newblock arXiv:1707.06307, 2017.

\bibitem{Hilbe2017}
Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
  Nowak.
\newblock {Memory-n strategies of direct reciprocity}.
\newblock {\em Proceedings of the National Academy of Sciences}, page
  201621239, 2017.

\bibitem{Hilbe2013}
Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
\newblock {Adaptive dynamics of extortion and compliance}.
\newblock {\em PloS one}, 8(11):e77886, 2013.

\bibitem{hunter2007matplotlib}
John~D Hunter.
\newblock {Matplotlib: A 2D graphics environment}.
\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.

\bibitem{kendall2007iterated}
Graham Kendall, Xin Yao, and Siang~Y Chong.
\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
\newblock Advances in natural computation. World Scientific, 2007.

\bibitem{Knight2016}
Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
  Timothy Standen, Luis Visintini, and Karl Molden.
\newblock {An Open Framework for the Reproducible Study of the Iterated
  Prisoner ' s Dilemma}.
\newblock 2016.

\bibitem{data}
Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
  Self-Recognition Mechanisms: an empirical study of the Moran process for the
  iterated Prisoner's dilemma using reinforcement learning}.
\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.

\bibitem{Kraines1989}
David Kraines and Vivian Kraines.
\newblock {Pavlov and the prisoner's dilemma}.
\newblock {\em Theory and decision}, 26(1):47--79, 1989.

\bibitem{Kuhn2017}
Steven Kuhn.
\newblock Prisoner's dilemma.
\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
  edition, 2017.

\bibitem{Lee2015}
Christopher Lee, Marc Harper, and Dashiell Fryer.
\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
\newblock {\em Plos One}, 10(3):e0120625, 2015.

\bibitem{Li2011}
Jiawei Li, Philip Hingston, and Graham Kendall.
\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
  Dilemma Competitions}.
\newblock {\em IEEE Transactions on Computational Intelligence and AI in
  Games}, 3(4):348--360, 2011.

\bibitem{Li2009}
Jiawei Li and Graham Kendall.
\newblock {A strategy with novel evolutionary features for the iterated
  prisoner's dilemma.}
\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.

\bibitem{Li2014}
Jiawei Li and Graham Kendall.
\newblock {The effect of memory size on the evolutionary stability of
  strategies in iterated prisoner's dilemma}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
  2014.

\bibitem{Prison1998}
LIFL.
\newblock Prison.
\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.

\bibitem{Mathieu2015}
Philippe Mathieu and Jean-Paul Delahaye.
\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
  Abstract)}.
\newblock {\em 14th International Conference on Autonomous Agents and
  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.

\bibitem{mckinney2010data}
Wes McKinney et~al.
\newblock Data structures for statistical computing in python.
\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
  445, pages 51--56. van der Voort S, Millman J, 2010.

\bibitem{Mittal2009}
Shashi Mittal and Kalyanmoy Deb.
\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
  multiple conflicting objectives}.
\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
  2009.

\bibitem{Moran1957}
Patrick A~P Moran.
\newblock {Random Processes in Genetics}.
\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
  Society}, 54(1):60--71, 1957.

\bibitem{Nachbar1992}
John~H Nachbar.
\newblock {Evolution in the finitely repeated prisoner's dilemma}.
\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
  1992.

\bibitem{Nowak}
Martin~A Nowak.
\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
\newblock Cambridge: Harvard University Press.

\bibitem{Nowak1993}
Martin~A Nowak and Karl Sigmund.
\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
  the Prisoner's Dilemma game.}
\newblock {\em Nature}, 364(6432):56--58, 1993.

\bibitem{Press2012}
William~H Press and Freeman~J Dyson.
\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
  evolutionary opponent.}
\newblock {\em Proceedings of the National Academy of Sciences of the United
  States of America}, 109(26):10409--13, 2012.

\bibitem{Prlic2012}
Andreas Prlić and James~B Procter.
\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.

\bibitem{axelrodproject}
The~Axelrod project developers.
\newblock Axelrod: v2.9.0.
\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.

\bibitem{Robson1990}
Arthur~J Robson.
\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
  handshake}.
\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.

\bibitem{Sandve2013}
Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
\newblock {Ten Simple Rules for Reproducible Computational Research}.
\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.

\bibitem{Stewart2012}
Alexander~J Stewart and Joshua~B Plotkin.
\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
\newblock {\em Proceedings of the National Academy of Sciences},
  109(26):10134--10135, 2012.

\bibitem{stewart2013extortion}
Alexander~J Stewart and Joshua~B Plotkin.
\newblock {From extortion to generosity, evolution in the iterated prisoner’s
  dilemma}.
\newblock {\em Proceedings of the National Academy of Sciences},
  110(38):15348--15353, 2013.

\bibitem{Tzafestas2000}
Elpida Tzafestas.
\newblock {Toward adaptive cooperative behavior}.
\newblock {\em From Animals to animals: Proceedings of the 6th International
  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
  2000.

\bibitem{PD2017}
Unkwown.
\newblock www.prisoners-dilemma.com.
\newblock http://www.prisoners-dilemma.com/, 2017.

\bibitem{Berg2015}
Pieter Van~den Berg and Franz~J Weissing.
\newblock {The importance of mechanisms for the evolution of cooperation}.
\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
  Society, 2015.

\bibitem{walt2011numpy}
St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
\newblock {The NumPy array: a structure for efficient numerical computation}.
\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.

\bibitem{West2016}
Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
\newblock {The prisoner’s dilemma as a cancer model}.
\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.

\bibitem{Wilson2014}
Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
\newblock {Best Practices for Scientific Computing}.
\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.

\bibitem{Axelrod1995}
Jianzhong Wu and Robert Axelrod.
\newblock {How to cope with noise in the iterated prisoner's dilemma}.
\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.

\end{thebibliography}

\appendix

\section{Appendix A: List of players}\label{app:list_of_players}

\footnotesize
\begin{enumerate}
\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980a}
\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006}
\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006}
\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Banks1990, Beaufils1997, Berg2015, Li2011}
\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Stewart2012}
\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980a}
\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006}
\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980a, Tzafestas2000}
\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a}
\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980a}
\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
\end{enumerate}

\section{Appendix B: Supplementary figures}

\begin{itemize}
    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
for each strategy. The mean and error bars are shown against the collection of
all opponents.

    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
the collection of all opponents.

    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
ranks of each strategy according to mean absorption probability across all
population sizes.
\end{itemize}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
    \label{invasion-3}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
    \label{invasion-14}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
    \label{resistance-3}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
    \label{resistance-14}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
    \label{fig:ranks_v_size_invade}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
    population sizes.}
    \label{fig:ranks_v_size_resist}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
    population sizes.}
    \label{fig:ranks_v_size_coexist}
\end{figure}

\end{document}

### 2018-04-06 plos/main.tex
Include ranks v population size in main text.

@@
 probability of one individual of a given type successfully fixating in a
-population of \(N - 1\) other individuals, denoted by \(x_1\).
+population of \(N - 1\) other individuals, denoted by \(x_1\). The ranks of each
+strategy for all considered values of \(N\) according to mean \(x_1\) are shown
+in Fig~\ref{fig:ranks_v_size_invade}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
+    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
+    \label{fig:ranks_v_size_invade}
+\end{figure}
 
@@
 
-\subsubsection*{Strong resistors}
+\subsubsection*{Strong Resistors}
 
@@
 other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy.
+each strategy. The ranks of each strategy for all considered values of \(N\)
+according to mean \(x_{N-1}\) are shown in Fig~\ref{fig:ranks_v_size_resist}.
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
+    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
+    population sizes.}
+    \label{fig:ranks_v_size_resist}
+\end{figure}
 
@@
 \subsubsection*{The effect of population size}
+
+Fig~\ref{fig:ranks_v_size_coexist} complements
+Figs~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist} showing the
+ranks of each strategy for all considered even values of \(N\) according to mean
+\(x_{N/2}\).
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
+    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
+    population sizes.}
+    \label{fig:ranks_v_size_coexist}
+\end{figure}
 
@@
 
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
-    \label{fig:ranks_v_size_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
-    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_coexist}
-\end{figure}
-
 \end{document}

### 2018-04-13 main.tex
Make figure 1 bigger.

--- 2018-01-11 main.tex
@@
-\documentclass[10pt,journal]{IEEEtran}
-
-% Packages
-\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
+% Template for PLoS
+% Version 3.4 January 2017
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended
+% to minimize problems and delays during our production
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% Once your paper is accepted for publication,
+% PLEASE REMOVE ALL TRACKED CHANGES in this file
+% and leave only the final text of your manuscript.
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that
+% no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file.
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column.
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% Use Unicode characters when possible
+\usepackage[utf8x]{inputenc}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Leave date blank
+\date{}
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr}
+\usepackage{graphicx}
+\usepackage{epstopdf}
+\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+\setlength{\headheight}{27.023pt}
+\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\sf PLOS}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+
+%% END MACROS SECTION
+
+\usepackage{algorithm,algorithmic}
+\usepackage{amsmath}
+\usepackage{authblk}
+\usepackage{booktabs}
+\usepackage{booktabs}
+\usepackage{fancyvrb}
+\usepackage{graphicx}
 \usepackage{hyperref}
 \usepackage{multicol}
-\usepackage{booktabs}
+\usepackage{pdflscape}
+\usepackage{standalone}
+\usepackage{subcaption}
+\usepackage{tikz}
 \usepackage{xstring}
-\usepackage{subcaption}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{standalone}
-\usepackage{fancyvrb}
-\usepackage{algorithm,algorithmic}
-\usepackage{authblk}
-
-\usepackage{tikz}
+
 \usetikzlibrary{calc, shapes, patterns}
 
-% Title
-\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
-       Mechanisms: an Empirical Study of strategies in the Moran process for the
-       Iterated Prisoner's}
-\author[1]{Vincent Knight}
-\author[2]{Marc Harper}
-\author[1]{Nikoleta E. Glynatsi}
-\author[3]{Owen Campbell}
-
-\affil[1]{Cardiff University, School of Mathematics, UK}
-\affil[2]{Google Inc., Mountain View, CA, USA}
-\affil[3]{Not affiliated}
-
-\date{}
-
 \begin{document}
-
-\maketitle
-
-\begin{abstract}
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline
+{Evolution reinforces cooperation with the emergence of self-recognition
+ mechanisms: an empirical study of strategies in the Moran process for the
+ iterated prisoner's dilemma }
+% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Vincent Knight\textsuperscript{1*\Yinyang},
+Marc Harper\textsuperscript{2\Yinyang},
+Nikoleta E. Glynatsi\textsuperscript{2\ddag},
+Owen Campbell\textsuperscript{3\ddag},
+\\
+\bigskip
+\textbf{1} Cardiff University, School of Mathematics, Cardiff, UK
+\\
+\textbf{2} Google Inc., Mountain View, CA, USA
+\\
+\textbf{3} Independent Researcher, Chester, UK
+\\
+\bigskip
+
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+%
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+\Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+\ddag These authors also contributed equally to this work.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* knightva@cardiff.ac.uk
+
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
     We present insights and empirical results from an extensive numerical
@@
     evolutionarily stable as strategies employing handshake mechanisms.
-\end{abstract}
-
-\section{Introduction}\label{sec:introduction}
+\linenumbers
+
+\section*{Introduction}
 
@@
 evolutionary population dynamics that has been used to gain insights about the
-evolutionary stability in a number of settings (more details given in
-Section~\ref{sec:the_moran_process}).
+evolutionary stability in a number of settings.
 Several earlier
@@
 This manuscript provides a detailed numerical analysis of agent-based simulations
-of \textbf{\input{tex/num_strategies.tex}}complex and adaptive strategies for the
+of \textbf{164} complex and adaptive strategies for the
 IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
 effort to provide software for reproducible research for the IPD\@. The library
-now contains over \input{tex/num_strategies_axelrod.tex}parameterized
+now contains over 186 parameterized
 strategies including classics like TitForTat and WinStayLoseShift, as well as
@@
 strategies are finite state machines trained specifically for Moran processes
-(described further in Section~\ref{sec:strategies}).
+(described further in the Methods section).
 
@@
 
-\subsection{The Moran Process}\label{sec:the_moran_process}
+\section*{Materials and methods}
+\subsection*{The Moran Process}
 
@@
 population (a uniform random selection is used). This is shown diagrammatically
-in Figure~\ref{fig:moran_process}. In some settings mutation is
+in Fig~\ref{fig:moran_process}. In some settings mutation is
 also considered but without mutation (the case considered in this work) this
@@
 over a population is called the \textit{fixation probability}. A more detailed
-analytic description of this is given in Section~\ref{sec:validation}. In our
+analytic description of this is given later. In our
 simulations offspring do not inherit any knowledge or history from parent
@@
     \centering
-    \scalebox{.5}{ \input{tex/moran_process.tex}}
+    \scalebox{.7}{
+
+\begin{tikzpicture}[scale=.9]
+	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
+        color=blue!70, draw=blue] {};
+	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
+        color=blue!70, draw=blue] {};
+	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
+        color=blue!70, draw=blue] {};
+	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
+        color=blue!70, draw=blue] {};
+	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
+        color=blue!70, draw=blue] {};
+	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
+        color=red!70, draw=red] {};
+	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
+        color=red!70, draw=red] {};
+	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
+        color=red!70, draw=red] {};
+	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
+        color=red!70, draw=red] {};
+	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
+        color=red!70, draw=red] {};
+
+	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};
+
+	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+
+	\draw [dotted, very thick] (B4) circle (.25cm);
+
+	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};
+
+	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+
+	\draw [dotted, very thick] (B4) circle (.25cm);
+	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);
+
+	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};
+
+	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+
+	\draw [dotted, very thick] (A3) circle (.25cm);
+
+	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};
+
+	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (A3) at ($(A3) + (4.5, 0)$) {};
+	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
+        pattern color=blue!70, draw=blue] {};
+	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
+        pattern color=red!70, draw=red] {};
+
+	\draw [dotted, very thick] (A3) circle (.25cm);
+\end{tikzpicture}
+
+}
     \caption{A diagrammatic representation of a Moran process.}
@@
 
-\subsection{Strategies considered}\label{sec:strategies}
-
-To carry out this numerical experiment, \input{tex/num_strategies}
-strategies, listed (with their properties) in Appendix~\ref{app:list_of_players},
+\subsection*{Strategies considered}\label{sec:strategies}
+
+To carry out this numerical experiment, 164
+strategies, listed (with their properties) in the Appendix,
 are used from the Axelrod library. There are
-\input{tex/num_stochastic.tex}stochastic and
-\input{tex/num_deterministic.tex}deterministic strategies. Their memory depth,
+43 stochastic and
+121 deterministic strategies. Their memory depth,
 defined by the number of rounds of history used by the strategy each round, is
@@
 FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively. These are shown in Figures~\ref{fig:tf1},~\ref{fig:tf2}
+and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
 and~\ref{fig:tf3}), using the notation common in the literature where
@@
     \centering
-    \scalebox{.7}{\input{tex/fsm_one.tex}}
+    \scalebox{.7}{
+    \begin{tikzpicture}
+
+    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
+    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
+	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
+	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
+	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
+	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};
+
+	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
+	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};
+
+	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
+	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
+	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};
+
+	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
+	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
+	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
+	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};
+
+	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
+	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};
+
+    \coordinate[left of=0] (s);
+
+    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
+    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
+    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);
+
+    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
+    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);
+
+    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
+    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);
+
+    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
+    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);
+
+    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
+    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);
+
+    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
+    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);
+
+    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
+    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);
+
+    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
+    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);
+
+    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
+    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);
+
+    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
+    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);
+
+    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
+    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);
+
+    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
+    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);
+
+    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
+    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);
+
+    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
+    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);
+
+    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
+    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);
+
+    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
+    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);
+
+    \end{tikzpicture}
+    }
     \caption{TF1: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \scalebox{.7}{\input{tex/fsm_two.tex}}
+    \scalebox{.7}{
+
+    \begin{tikzpicture}
+
+    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
+    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
+	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};
+
+	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
+    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
+    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
+    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
+    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
+    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
+    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};
+
+    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
+    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
+    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
+    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
+    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
+    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
+    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};
+
+    \coordinate[below of=0] (s);
+
+    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);
+
+    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
+    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);
+
+    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
+    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);
+
+    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
+    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);
+
+    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
+    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/D$} (1);
+
+    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
+    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);
+
+    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
+    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);
+
+    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
+    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);
+
+    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
+    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);
+
+    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
+    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);
+
+    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
+    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);
+
+    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
+    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);
+
+    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
+    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);
+
+    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
+    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);
+
+    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
+    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);
+
+    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
+    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);
+
+    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
+    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);
+
+    \end{tikzpicture}
+    }
     \caption{TF2: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \input{tex/fsm_three.tex}
+    \begin{tikzpicture}
+
+    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];
+
+    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
+    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
+    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$}; 
+    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
+    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};  
+    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
+    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
+    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};
+
+    \coordinate[left of=0] (s);
+
+    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
+
+    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
+    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
+    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
+    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
+    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);
+
+    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
+    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
+    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);
+
+    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);
+
+    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
+    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
+    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
+    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
+    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
+    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
+    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
+    \end{tikzpicture}
     \caption{TF3: an 8 state finite state machine.}
@@
 players in the study, barring
-unusual cases arising from particular randomizations. Figure~\ref{fig:tf2} shows
+unusual cases arising from particular randomizations. Fig~\ref{fig:tf2} shows
 all 16 states of the strategy (states 6 and 7 are not reachable).
@@
 product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism. Figure~\ref{fig:tf3} shows
+in that it lacks a handshake mechanism. Fig~\ref{fig:tf3} shows
 all 8 states of the strategy produced by the training process (states 3 and 8
@@
     \centering
-        \scalebox{0.7}{\input{tex/memory_depth_count.tex}}
+        \scalebox{0.7}{
+            \begin{tabular}{lrrrrrrrrrrrrrrrr}
+            \toprule
+            Memory Depth &   0   &   1   &   2   &   3   &   4   &   5   &   6   &   9   &   10  &   11  &   12  &   16  &   20  &   40  &   200 &  \(\infty\)   \\
+            \midrule
+            Count &     3 &    29 &    12 &     8 &     2 &     6 &     1 &     1 &     5 &     1 &     1 &     2 &     2 &     2 &     1 &    88 \\
+            \bottomrule
+            \end{tabular}
+        }
         \caption{Memory depths}
@@
 
-\subsection{Data collection}\label{sec:data_collection}
+\subsection*{Data collection}
 
@@
         \label{alg:data_collection}
-        \input{tex/data_collection.tex}
+          \begin{algorithmic}[1]
+            \FOR{player\_one \textbf{in} players\_list}
+              \FOR{player\_two \textbf{in} (players\_list - player\_one)}
+                \STATE pair $\gets$ (player\_one, player\_two)
+                \FOR{starting\_population\_distributions \textbf{in} [$(1, N-1), (\frac{N}{2}, \frac{N}{2}), (N-1, 1)]$}
+                \WHILE {repetitions $\leq 1000$}
+                \STATE \textbf{simulate} moran process (pair, starting distribution)
+                \ENDWHILE
+                \STATE\textbf{yield} fixation probabilities
+                \ENDFOR
+              \ENDFOR
+            \ENDFOR
+          \end{algorithmic}
 \end{algorithm}
@@
         \label{alg:moran_process}
-        \input{tex/moran_process_simulation.tex}
+          \begin{algorithmic}[1]
+          \STATE initial population $\gets$ (pair, starting distribution) \
+          \STATE population $\gets$ initial population
+
+            \WHILE {population not uniform}
+              \FOR{player in population}
+              \FOR{opponent in (population - player)}
+                \STATE match $\gets$ (player, opponent) 
+                \STATE results $\gets$ stochastic\_cache (200 round match)
+                \ENDFOR
+              \ENDFOR
+              \STATE population $\gets$ sorted(results)
+              \STATE parent $\gets$ selected randomly in proportion to its total match payoffs
+              \STATE offspring $\gets$ parent
+              \STATE kill off $\gets$ uniformly random player from population
+              \STATE population $\gets$ offspring replaces kill off
+            \ENDWHILE
+          \end{algorithmic}
 \end{algorithm}
 
-Section~\ref{sec:validation} will further validate the methodology by comparing
+The next section will further validate the methodology by comparing
 simulated results to analytical results in a few selected cases. The main
 results of this
-manuscript are presented in Section~\ref{sec:empirical_results} which will
+manuscript are presented in which will
 present a detailed analysis of all the data generated. Finally,
-Section~\ref{sec:conclusion} will conclude and offer future avenues for the work
+a discussion and conclusion will offer future avenues for the work
 presented here.
 
-\section{Validation}\label{sec:validation}
+\section*{Results}
+
+\subsection*{Validation}
 
@@
 Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Figure~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
+Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
 confidence interval computed using an asymptotic normal approximation is also
@@
 
-Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
+Fig~\ref{fig:comparison_stochastic} shows the fixation probabilities for
 stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
@@
     \centering
-    \includegraphics[width=.95\columnwidth]{img/Alternator_v_WSLS.pdf}
+    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
     \caption{Comparison of theoretic and actual Moran Process fixation
@@
     \centering
-    \input{tex/t_test_results_alternator_v_wsls.tex}
+
+        \begin{tabular}{rrrr}
+        \toprule
+          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
+        \midrule
+          2 &          0.89942 &                0.89942 &                0.89942 \\
+          4 &          0.16344 &                0.74768 &                0.85877 \\
+          6 &          0.65406 &                0.84051 &                0.51992 \\
+          8 &          0.92617 &                0.45748 &                0.38604 \\
+         10 &          0.03505 &                0.37115 &                0.60635 \\
+         12 &          0.96697 &                0.20790 &                0.18124 \\
+         14 &          0.08126 &                0.63771 &                0.76246 \\
+         16 &          0.59434 &                0.07697 &                0.42520 \\
+         18 &          0.05339 &                0.47126 &                0.94814 \\
+         20 &          0.30805 &                0.79795 &                0.82381 \\
+        \bottomrule
+        \end{tabular}
+
     \caption{\(p\) values resulting from a $t$ test comparing the theoretic
@@
     \centering
-    \includegraphics[width=.95\columnwidth]{img/Calculator_v_Arrogant_QLearner.pdf}
+    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
     \caption{Comparison of theoretic and actual Moran Process
@@
     \centering
-    \input{tex/t_test_results_calculator_v_arrogant_q_learner.tex}
+        \begin{tabular}{rrrr}
+        \toprule
+          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
+        \midrule
+          2 &          0.05372 &                0.05372 &                0.05372 \\
+          4 &          0.34188 &                0.00940 &                0.00005 \\
+          6 &          0.16510 &                0.00000 &                0.00000 \\
+          8 &          0.03451 &                0.00000 &                0.00000 \\
+         10 &          0.00543 &                0.00000 &                0.00000 \\
+         12 &          0.19646 &                0.00000 &                0.00000 \\
+         14 &          0.00814 &                0.00000 &                0.00000 \\
+         16 &          0.01038 &                0.00000 &                0.00000 \\
+         18 &          0.39556 &                0.00000 &                0.00000 \\
+         20 &          0.00030 &                0.00000 &                0.00000 \\
+        \bottomrule
+        \end{tabular}
     \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
@@
 
-\section{Empirical results}\label{sec:empirical_results}
+\subsection*{Empirical results}
 
 This section outlines the data analysis carried out, all data for this study is
-available at~\cite{data}:
+available at~\cite{data}.
 
 \begin{itemize}
-    \item Section~\ref{sec:two_individuals} considers the specific case of
-        \(N=2\).
-    \item Section~\ref{sec:strong_invaders} investigates the effect of
+    \item First the specific case of
+        \(N=2\) is considered.
+    \item The effect of
         population size on the ability of a strategy to invade another
-        population. This will highlight how complex strategies with long
+        population is investigated. This will highlight how complex strategies with long
         memories outperform simpler strategies.
-    \item Section~\ref{sec:strong_resistors} similarly investigates the
-        ability to defend against an invasion.
-    \item Section~\ref{sec:population_size} investigates the relationship
+    \item Then a similar investigation of the
+        ability to defend against an invasion is given.
+    \item Finally the relationship
         between performance for differing population sizes as well as
-        taking a close look at zero determinant strategies \cite{Press2012}.
+        taking a close look at zero determinant strategies \cite{Press2012} is
+        analysed.
 \end{itemize}
 
-\subsection{The special case of \(N=2\)}\label{sec:two_individuals}
+\subsubsection*{The special case of \(N=2\)}
 
@@
 the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in sections~\ref{sec:strong_invaders}
-and~\ref{sec:strong_resistors}. The top 16 (10\%) strategies are
+considered separately for larger \(N\) in the following sections.
+The top 16 (10\%) strategies are
 shown in
+
 Table~\ref{tbl:summary_top_2} and figures showing the performance of all
-strategies are available in the supplementary materials.
+strategies are available in the appendix.
 The top five ranking strategies are:
@@
 strategies: ZD-extort-4. The performance of zero determinant strategies will be
-examined more closely in Section~\ref{sec:population_size}.
+examined more closely.
 
@@
     \centering
-    \scalebox{0.95}{\input{tex/summary_top_2_invade.tex}}
+    \scalebox{0.95}{
+        \begin{tabular}{llrrrrrrr}
+        \toprule
+        {} &                  Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
+        \midrule
+        1  &                      CS &  0.497 &  0.5020 &  0.6651 &   0.572 &  0.9908 &  0.993 &  0.1800 \\
+        2  &                Defector &  0.502 &  0.5020 &  0.6496 &   0.518 &  1.0000 &  1.000 &  0.1767 \\
+        3  &              Aggravater &  0.502 &  0.5020 &  0.6328 &   0.518 &  0.9790 &  0.999 &  0.1660 \\
+        4  &                Predator &  0.319 &  0.4980 &  0.6301 &   0.551 &  0.9870 &  0.993 &  0.1676 \\
+        5  &               Handshake &  0.006 &  0.4503 &  0.6240 &   0.524 &  0.9908 &  0.993 &  0.1889 \\
+        6  &                Prober 4 &  0.431 &  0.4620 &  0.6183 &   0.534 &  0.9579 &  0.958 &  0.1656 \\
+        7  &                     \textbf{TF1} &  0.430 &  0.4980 &  0.6171 &   0.544 &  0.9240 &  0.981 &  0.1345 \\
+        8  &                Prober 3 &  0.497 &  0.5011 &  0.6044 &   0.505 &  0.9930 &  0.993 &  0.1683 \\
+        9  &                     \textbf{TF2} &  0.324 &  0.5020 &  0.6026 &   0.565 &  0.8362 &  0.887 &  0.1092 \\
+        10 &                 Grudger &  0.497 &  0.5020 &  0.5996 &   0.502 &  0.9840 &  0.989 &  0.1695 \\
+        11 &       Better and Better &  0.388 &  0.3951 &  0.5980 &   0.514 &  0.9300 &  0.934 &  0.1865 \\
+        12 &                    MEM2 &  0.497 &  0.5001 &  0.5942 &   0.502 &  0.9840 &  0.987 &  0.1656 \\
+        13 &  Meta Hunter Aggressive &  0.247 &  0.2943 &  0.5933 &   0.517 &  0.9498 &  0.981 &  0.2013 \\
+        14 &                     \textbf{TF3} &  0.344 &  0.4971 &  0.5927 &   0.502 &  0.9790 &  0.982 &  0.1617 \\
+        15 &            Fool Me Once &  0.494 &  0.4980 &  0.5892 &   0.502 &  0.9790 &  0.982 &  0.1625 \\
+        16 &             ZD-Extort-4 &  0.497 &  0.5020 &  0.5867 &   0.584 &  0.6900 &  0.695 &  0.0724 \\
+        \bottomrule
+        \end{tabular}
+    }
     \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
@@
 
-As will be demonstrated in Section~\ref{sec:population_size} the results for
+As will be demonstrated the results for
 \(N=2\) differ from those of larger $N$. Hence these results do not concur with
@@
 
-\subsection{Strong Invaders}\label{sec:strong_invaders}
+\subsubsection*{Strong Invaders}
 
@@
 figures showing the performance of all strategies is available in the
-supplementary materials.
+appendix.
 
@@
         \centering
-        \input{tex/summary_top_3_invade.tex}
+            \begin{tabular}{llrrrrrrr}
+            \toprule
+            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
+            \midrule
+            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
+            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
+            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
+            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
+            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
+            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
+            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
+            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
+            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
+            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
+            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
+            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
+            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
+            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
+            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
+            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
+            \bottomrule
+            \end{tabular}
         \caption{\(N=3\)}
@@
         \centering
-        \input{tex/summary_top_7_invade.tex}
+            \begin{tabular}{llrrrrrrr}
+            \toprule
+            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
+            \midrule
+            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
+            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
+            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
+            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
+            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
+            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
+            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
+            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
+            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
+            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
+            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
+            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
+            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
+            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
+            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
+            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
+            \bottomrule
+            \end{tabular}
         \caption{\(N=7\)}
@@
         \centering
-        \input{tex/summary_top_14_invade.tex}
+            \begin{tabular}{llrrrrrrr}
+            \toprule
+            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
+            \midrule
+            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
+            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
+            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
+            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
+            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
+            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
+            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
+            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
+            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
+            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
+            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
+            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
+            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
+            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
+            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
+            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
+            \bottomrule
+            \end{tabular}
         \caption{\(N=14\)}
@@
     \item TF3, the finite state machine trained specifically for Moran processes
-        described in Section~\ref{sec:introduction}.
+        described.
     \item Prober 4, a strategy which starts with a specific 20 move sequence of
@@
 
-\subsection{Strong resistors}\label{sec:strong_resistors}
+\subsubsection*{Strong Resistors}
 
@@
 for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies from
-Section~\ref{sec:two_individuals} perform well for high \(N\).
+Once again none of the short memory strategies previously discussed perform well for high \(N\).
 
@@
         \centering
-        \input{tex/summary_top_3_resist.tex}
+            \begin{tabular}{llrrrrrrr}
+            \toprule
+            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
+            \midrule
+            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
+            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
+            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
+            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
+            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
+            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
+            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
+            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
+            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
+            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
+            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
+            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
+            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
+            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
+            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
+            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
+            \bottomrule
+            \end{tabular}
         \caption{\(N=3\)}
@@
         \centering
-        \input{tex/summary_top_7_resist.tex}
+            \begin{tabular}{llrrrrrrr}
+            \toprule
+            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
+            \midrule
+            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
+            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
+            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
+            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
+            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
+            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
+            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
+            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
+            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
+            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
+            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
+            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
+            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
+            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
+            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
+            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
+            \bottomrule
+            \end{tabular}
         \caption{\(N=7\)}
@@
         \centering
-        \input{tex/summary_top_14_resist.tex}
+        \begin{tabular}{llrrrrrrr}
+        \toprule
+        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
+        \midrule
+        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
+        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
+        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
+        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
+        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
+        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
+        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
+        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
+        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
+        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
+        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
+        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
+        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
+        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
+        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
+        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
+        \bottomrule
+        \end{tabular}
         \caption{\(N=14\)}
@@
 
-As described in Section~\ref{sec:strong_invaders} the strategies trained with
+As described previously the strategies trained with
 the payoff maximizing objective are among the best invaders in the library
@@
 It is evident through
-Sections~\ref{sec:two_individuals},~\ref{sec:strong_invaders}
-and~\ref{sec:strong_resistors} that performance of strategies not only depends
+the work presented that performance of strategies not only depends
 on the initial population distribution but also that there seems to be a
@@
 
-\subsection{The effect of population size}\label{sec:population_size}
+\subsubsection*{The effect of population size}
+
+Fig~\ref{fig:ranks_v_size_coexist} complements
+Figs~\ref{fig:ranks_v_size_invade} and~\ref{fig:ranks_v_size_resist} showing the
+ranks of each strategy for all considered even values of \(N\) according to mean
+\(x_{N/2}\).
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
+    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
+    population sizes.}
+    \label{fig:ranks_v_size_coexist}
+\end{figure}
 
@@
 in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
-expected since, as described in Section~\ref{sec:strategies} these strategies
+expected since, as described previously these strategies
 were trained in an initial population of \((N/2, N/2)\) individuals.
@@
     \scriptsize
-    \scalebox{0.7}{\input{tex/change_of_rank_invade.tex}}
+    \scalebox{0.7}{
+        \begin{tabular}{lrrrrrrrrrrrrr}
+        \toprule
+                         Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
+        \midrule
+                           CS &    1 &    1 &    2 &   11 &    9 &   11 &   13 &   21 &   16 &   22 &   17 &   25 &   23 \\
+                     Defector &    2 &   43 &   80 &   91 &   89 &   87 &   87 &  103 &   97 &  105 &   94 &  103 &  101 \\
+                   Aggravater &    3 &   50 &   89 &   99 &  102 &  103 &  108 &  113 &  114 &  115 &  115 &  116 &  117 \\
+                     Predator &    4 &    8 &   24 &   35 &   28 &   33 &   31 &   43 &   36 &   43 &   34 &   45 &   35 \\
+                    Handshake &    5 &   17 &   40 &   46 &   43 &   46 &   46 &   49 &   48 &   49 &   47 &   50 &   49 \\
+        \midrule
+               Evolved FSM 16 &   31 &   11 &    6 &    2 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
+            PSO Gambler 2\_2\_2 &   29 &   14 &   10 &    6 &    4 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
+         EvolvedLookerUp2\_2\_2 &   33 &   18 &   11 &    9 &   10 &    6 &    6 &    5 &    3 &    5 &    3 &    3 &    3 \\
+                  Evolved ANN &   20 &   10 &    8 &    7 &    8 &    5 &    3 &    3 &    4 &    3 &    4 &    4 &    4 \\
+                Evolved ANN 5 &   21 &    9 &    7 &    8 &    7 &    4 &    5 &    4 &    5 &    4 &    5 &    5 &    5 \\
+        \midrule
+                          \textbf{TF1} &    7 &   13 &   33 &   38 &   30 &   39 &   42 &   46 &   42 &   46 &   41 &   46 &   46 \\
+                          \textbf{TF2} &    9 &   19 &   29 &   33 &   19 &   28 &   29 &   38 &   27 &   34 &   26 &   32 &   30 \\
+                          \textbf{TF3} &   14 &    4 &    5 &    5 &    6 &    9 &   11 &   11 &   12 &   14 &   13 &   13 &   16 \\
+        \midrule
+                  ZD-Extort-4 &   16 &   81 &  107 &  120 &  135 &  136 &  142 &  140 &  142 &  142 &  144 &  144 &  145 \\
+               ZD-Extort-2 v2 &   41 &  105 &  126 &  140 &  152 &  152 &  153 &  152 &  153 &  153 &  153 &  152 &  153 \\
+                  ZD-Extort-2 &   43 &  107 &  125 &  139 &  151 &  151 &  152 &  153 &  152 &  152 &  152 &  153 &  152 \\
+                     ZD-SET-2 &  100 &  111 &  117 &  117 &  122 &  127 &  131 &  128 &  131 &  131 &  130 &  132 &  131 \\
+                    ZD-GTFT-2 &  112 &   92 &   82 &   80 &   81 &   82 &   84 &   72 &   81 &   71 &   78 &   72 &   70 \\
+                     ZD-GEN-2 &  113 &   96 &   87 &   83 &   85 &   88 &   90 &   82 &   87 &   82 &   86 &   83 &   91 \\
+        \bottomrule
+        \end{tabular}
+    }
     \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
@@
     \scriptsize
-    \scalebox{0.7}{\input{tex/change_of_rank_resist.tex}}
+    \scalebox{0.7}{
+        \begin{tabular}{lrrrrrrrrrrrrr}
+        \toprule
+                   Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
+        \midrule
+                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
+               Defector &    2 &   29 &   55 &   79 &   94 &   97 &   98 &   98 &  102 &  101 &  103 &  100 &  102 \\
+             Aggravater &    3 &   42 &   71 &   97 &  101 &  106 &  107 &  111 &  113 &  113 &  116 &  115 &  115 \\
+               Predator &    4 &    2 &    3 &    3 &    3 &    4 &    4 &    4 &    4 &    4 &    4 &    4 &    4 \\
+              Handshake &    5 &    4 &    5 &    5 &    5 &    5 &    5 &    6 &    6 &    6 &    6 &    6 &    6 \\
+        \midrule
+                    \textbf{TF1} &    7 &    3 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
+                    \textbf{TF2} &   10 &    5 &    4 &    4 &    4 &    3 &    3 &    3 &    3 &    3 &    3 &    3 &    3 \\
+               Prober 4 &    6 &    6 &    6 &    6 &    6 &    6 &    6 &    5 &    5 &    5 &    5 &    5 &    5 \\
+        \midrule
+                    \textbf{TF3} &   13 &    9 &   10 &   11 &   11 &   11 &   13 &   14 &   13 &   13 &   13 &   13 &   13 \\
+        \midrule
+            ZD-Extort-4 &   19 &   68 &   98 &  106 &  108 &  114 &  115 &  115 &  118 &  118 &  117 &  118 &  117 \\
+         ZD-Extort-2 v2 &   49 &   98 &  111 &  121 &  123 &  124 &  124 &  130 &  130 &  132 &  134 &  132 &  134 \\
+            ZD-Extort-2 &   50 &   97 &  112 &  123 &  124 &  125 &  123 &  126 &  131 &  131 &  132 &  133 &  133 \\
+               ZD-SET-2 &  108 &  105 &  104 &  104 &  103 &  103 &  100 &  100 &  101 &   99 &   98 &   98 &   98 \\
+              ZD-GTFT-2 &  112 &   95 &   88 &   84 &   75 &   72 &   71 &   73 &   71 &   71 &   67 &   68 &   68 \\
+               ZD-GEN-2 &  114 &   96 &   89 &   86 &   77 &   75 &   72 &   74 &   72 &   72 &   68 &   69 &   69 \\
+        \bottomrule
+        \end{tabular}
+    }
     \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
@@
     \scriptsize
-    \input{tex/change_of_rank_coexist.tex}
+        \begin{tabular}{lrrrrrrr}
+        \toprule
+                   Size &      2 &      4 &      6 &      8 &     10 &     12 &     14 \\
+        \midrule
+                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    2 \\
+               Defector &    2 &   78 &   99 &  106 &  110 &  113 &  120 \\
+             Aggravater &    3 &   91 &  105 &  111 &  122 &  125 &  128 \\
+               Predator &    4 &    2 &    4 &    4 &    4 &    4 &    4 \\
+              Handshake &    5 &    6 &    5 &    6 &    6 &    6 &    6 \\
+        \midrule
+                    \textbf{TF2} &    9 &    4 &    3 &    2 &    2 &    2 &    1 \\
+                    \textbf{TF1} &    7 &    3 &    2 &    3 &    3 &    3 &    3 \\
+               Prober 4 &    6 &    5 &    6 &    5 &    5 &    5 &    5 \\
+        \midrule
+                    \textbf{TF3} &   14 &    8 &    8 &    8 &    8 &    8 &    8 \\
+        \midrule
+            ZD-Extort-4 &   16 &  102 &  117 &  129 &  141 &  143 &  145 \\
+         ZD-Extort-2 v2 &   41 &  118 &  135 &  151 &  152 &  152 &  153 \\
+            ZD-Extort-2 &   43 &  117 &  136 &  149 &  151 &  151 &  152 \\
+               ZD-SET-2 &  100 &  110 &  110 &  108 &  106 &  106 &  108 \\
+              ZD-GTFT-2 &  112 &   82 &   80 &   77 &   75 &   75 &   74 \\
+               ZD-GEN-2 &  113 &   85 &   81 &   82 &   79 &   77 &   76 \\
+        \bottomrule
+        \end{tabular}
     \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
@@
 
-Figure~\ref{fig:correlation_coefficients} shows the correlation coefficients
+Fig~\ref{fig:correlation_coefficients} shows the correlation coefficients
 of the ranks of strategies in differing population size. How well a strategy
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/correlation_heatmap_invade.pdf}
+        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
         \caption{Rank based on \(x_1\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/correlation_heatmap_resist.pdf}
+        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
         \caption{Rank based on \(x_{N - 1}\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/correlation_heatmap_coexist.pdf}
+        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
         \caption{Rank based on \(x_{N/2}\)}
@@
 
-\section{Discussion}
+\section*{Discussion}
 
@@
 
-\section{Conclusion}\label{sec:conclusion}
+\section*{Conclusion}
 
@@
 results for \(N=2\) cannot be used to extrapolate performance in larger
-populations. This was shown both observationally in
-Sections~\ref{sec:strong_invaders} and~\ref{sec:strong_resistors} but also by
-considering the correlation of the ranks in different population sizes in
-Section~\ref{sec:population_size}.
+populations. This was shown both observationally
+ but also by
+considering the correlation of the ranks in different population sizes.
 
@@
 
-One of the major findings discussed in Section~\ref{sec:strong_resistors}, is
+One of the major findings discussed, is
 the ability of strategies with a handshake mechanism to resist invasion. This
@@
 process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. Figure~\ref{fig:cooperation_rates} shows the cooperation
+evolutionary process. Fig~\ref{fig:cooperation_rates} shows the cooperation
 rate of TF1, TF2, TF3 and CS
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF1_array.pdf}
+        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
         \caption{TF1}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF2_array.pdf}
+        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
         \caption{TF2}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_TF3_array.pdf}
+        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
         \caption{TF3}
@@
         \centering
-        \includegraphics[width=\columnwidth]{img/cooperation_0_0_10000_CS_array.pdf}
+        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
         \caption{CS}
@@
 
-\newpage
-\bibliographystyle{plain}
-\bibliography{tex/bibliography.bib}
+\nolinenumbers
+
+\begin{thebibliography}{10}
+
+\bibitem{Adami2013}
+Christoph Adami and Arend Hintze.
+\newblock {Evolutionary instability of zero-determinant strategies demonstrates
+  that winning is not everything.}
+\newblock {\em Nature communications}, 4(1):2193, 2013.
+
+\bibitem{adami2016evolutionary}
+Christoph Adami, Jory Schossau, and Arend Hintze.
+\newblock {Evolutionary game theory using agent-based methods}.
+\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
+
+\bibitem{affenzeller2009genetic}
+Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
+\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
+  Practical Applications}.
+\newblock Numerical Insights. CRC Press, 2009.
+
+\bibitem{Nowak2017}
+Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
+  Shing-Tung Yau, and Martin~A Nowak.
+\newblock {Evolutionary dynamics on any population structure}.
+\newblock 544:227--230, March 2017.
+
+\bibitem{Ashlock2015}
+Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
+\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
+  Agents}.
+\newblock {\em IEEE Transactions on Computational Intelligence and AI in
+  Games}, 7(1):53--65, 2015.
+
+\bibitem{Ashlock2008}
+Daniel Ashlock and Eun-Youn Kim.
+\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
+  dilemma strategies}.
+\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
+  2008.
+
+\bibitem{Ashlock2006}
+Wendy Ashlock and Daniel Ashlock.
+\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
+  with different population sizes}.
+\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
+  pages 297--304. IEEE, 2006.
+
+\bibitem{Ashlock2014}
+Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
+\newblock {The evolution of exploitation}.
+\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
+  Symposium on}, pages 135--142. IEEE, 2014.
+
+\bibitem{Axelrod1980a}
+Robert Axelrod.
+\newblock {Effective choice in the prisoner's dilemma}.
+\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
+
+\bibitem{Axelrod1980b}
+Robert Axelrod.
+\newblock {More Effective Choice in the Prisoner's Dilemma}.
+\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.
+
+\bibitem{Axelrod1984}
+Robert Axelrod.
+\newblock {\em The Evolution of Cooperation}.
+\newblock Basic books. Basic Books, 1984.
+
+\bibitem{Baek2016}
+{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
+  A}.
+\newblock {Comparing reactive and memory- one strategies of direct
+  reciprocity}.
+\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
+
+\bibitem{Banks1990}
+Jeffrey~S Banks and Rangarajan~K Sundaram.
+\newblock {Repeated games, finite automata, and complexity}.
+\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
+
+\bibitem{Beaufils1997}
+Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
+\newblock {Our meeting with gradual, a good strategy for the iterated
+  prisoner’s dilemma}.
+\newblock In {\em Proceedings of the Fifth International Workshop on the
+  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.
+
+\bibitem{brown2001interval}
+Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
+\newblock Interval estimation for a binomial proportion.
+\newblock {\em Statistical science}, pages 101--117, 2001.
+
+\bibitem{Andre2013}
+Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
+\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
+\newblock pages 1--6, 2013.
+
+\bibitem{Eckhart2015}
+Arnold Eckhart.
+\newblock Coopsim v0.9.9 beta 6.
+\newblock https://github.com/jecki/CoopSim/, 2015.
+
+\bibitem{Flood1958}
+Merrill~M Flood.
+\newblock {Some Experimental Games}, 1958.
+
+\bibitem{Frean1994}
+Marcus~R Frean.
+\newblock {The prisoner's dilemma without synchrony}.
+\newblock {\em Proceedings of the Royal Society of London B: Biological
+  Sciences}, 257(1348):75--79, 1994.
+
+\bibitem{Gaudesi2016}
+Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
+\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
+  dilemma tournaments}.
+\newblock {\em IEEE Transactions on Computational Intelligence and AI in
+  Games}, 8(3):288--300, 2016.
+
+\bibitem{marc_harper_2017_824264}
+Marc Harper, Vince Knight, and Martin Jones.
+\newblock Axelrod-python/axelrod-dojo: v0.0.1.
+\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
+
+\bibitem{Harper2017}
+Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
+  Glynatsi, and Owen Campbell.
+\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
+  Prisoner's Dilemma}.
+\newblock arXiv:1707.06307, 2017.
+
+\bibitem{Hilbe2017}
+Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
+  Nowak.
+\newblock {Memory-n strategies of direct reciprocity}.
+\newblock {\em Proceedings of the National Academy of Sciences}, page
+  201621239, 2017.
+
+\bibitem{Hilbe2013}
+Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
+\newblock {Adaptive dynamics of extortion and compliance}.
+\newblock {\em PloS one}, 8(11):e77886, 2013.
+
+\bibitem{hunter2007matplotlib}
+John~D Hunter.
+\newblock {Matplotlib: A 2D graphics environment}.
+\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
+
+\bibitem{kendall2007iterated}
+Graham Kendall, Xin Yao, and Siang~Y Chong.
+\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
+\newblock Advances in natural computation. World Scientific, 2007.
+
+\bibitem{Knight2016}
+Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
+  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
+  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
+  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
+  Timothy Standen, Luis Visintini, and Karl Molden.
+\newblock {An Open Framework for the Reproducible Study of the Iterated
+  Prisoner ' s Dilemma}.
+\newblock 2016.
+
+\bibitem{data}
+Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
+\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
+  Self-Recognition Mechanisms: an empirical study of the Moran process for the
+  iterated Prisoner's dilemma using reinforcement learning}.
+\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
+
+\bibitem{Kraines1989}
+David Kraines and Vivian Kraines.
+\newblock {Pavlov and the prisoner's dilemma}.
+\newblock {\em Theory and decision}, 26(1):47--79, 1989.
+
+\bibitem{Kuhn2017}
+Steven Kuhn.
+\newblock Prisoner's dilemma.
+\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
+  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
+  edition, 2017.
+
+\bibitem{Lee2015}
+Christopher Lee, Marc Harper, and Dashiell Fryer.
+\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
+\newblock {\em Plos One}, 10(3):e0120625, 2015.
+
+\bibitem{Li2011}
+Jiawei Li, Philip Hingston, and Graham Kendall.
+\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
+  Dilemma Competitions}.
+\newblock {\em IEEE Transactions on Computational Intelligence and AI in
+  Games}, 3(4):348--360, 2011.
+
+\bibitem{Li2009}
+Jiawei Li and Graham Kendall.
+\newblock {A strategy with novel evolutionary features for the iterated
+  prisoner's dilemma.}
+\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
+
+\bibitem{Li2014}
+Jiawei Li and Graham Kendall.
+\newblock {The effect of memory size on the evolutionary stability of
+  strategies in iterated prisoner's dilemma}.
+\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
+  2014.
+
+\bibitem{Prison1998}
+LIFL.
+\newblock Prison.
+\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
+
+\bibitem{Mathieu2015}
+Philippe Mathieu and Jean-Paul Delahaye.
+\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
+  Abstract)}.
+\newblock {\em 14th International Conference on Autonomous Agents and
+  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
+
+\bibitem{mckinney2010data}
+Wes McKinney et~al.
+\newblock Data structures for statistical computing in python.
+\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
+  445, pages 51--56. van der Voort S, Millman J, 2010.
+
+\bibitem{Mittal2009}
+Shashi Mittal and Kalyanmoy Deb.
+\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
+  multiple conflicting objectives}.
+\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
+  2009.
+
+\bibitem{Moran1957}
+Patrick A~P Moran.
+\newblock {Random Processes in Genetics}.
+\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
+  Society}, 54(1):60--71, 1957.
+
+\bibitem{Nachbar1992}
+John~H Nachbar.
+\newblock {Evolution in the finitely repeated prisoner's dilemma}.
+\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
+  1992.
+
+\bibitem{Nowak}
+Martin~A Nowak.
+\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
+\newblock Cambridge: Harvard University Press.
+
+\bibitem{Nowak1993}
+Martin~A Nowak and Karl Sigmund.
+\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
+  the Prisoner's Dilemma game.}
+\newblock {\em Nature}, 364(6432):56--58, 1993.
+
+\bibitem{Press2012}
+William~H Press and Freeman~J Dyson.
+\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
+  evolutionary opponent.}
+\newblock {\em Proceedings of the National Academy of Sciences of the United
+  States of America}, 109(26):10409--13, 2012.
+
+\bibitem{Prlic2012}
+Andreas Prlić and James~B Procter.
+\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
+\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
+
+\bibitem{axelrodproject}
+The~Axelrod project developers.
+\newblock Axelrod: v2.9.0.
+\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
+
+\bibitem{Robson1990}
+Arthur~J Robson.
+\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
+  handshake}.
+\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
+
+\bibitem{Sandve2013}
+Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
+\newblock {Ten Simple Rules for Reproducible Computational Research}.
+\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
+
+\bibitem{Stewart2012}
+Alexander~J Stewart and Joshua~B Plotkin.
+\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
+\newblock {\em Proceedings of the National Academy of Sciences},
+  109(26):10134--10135, 2012.
+
+\bibitem{stewart2013extortion}
+Alexander~J Stewart and Joshua~B Plotkin.
+\newblock {From extortion to generosity, evolution in the iterated prisoner’s
+  dilemma}.
+\newblock {\em Proceedings of the National Academy of Sciences},
+  110(38):15348--15353, 2013.
+
+\bibitem{Tzafestas2000}
+Elpida Tzafestas.
+\newblock {Toward adaptive cooperative behavior}.
+\newblock {\em From Animals to animals: Proceedings of the 6th International
+  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
+  2000.
+
+\bibitem{PD2017}
+Unkwown.
+\newblock www.prisoners-dilemma.com.
+\newblock http://www.prisoners-dilemma.com/, 2017.
+
+\bibitem{Berg2015}
+Pieter Van~den Berg and Franz~J Weissing.
+\newblock {The importance of mechanisms for the evolution of cooperation}.
+\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
+  Society, 2015.
+
+\bibitem{walt2011numpy}
+St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
+\newblock {The NumPy array: a structure for efficient numerical computation}.
+\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
+
+\bibitem{West2016}
+Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
+\newblock {The prisoner’s dilemma as a cancer model}.
+\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
+
+\bibitem{Wilson2014}
+Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
+  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
+  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
+\newblock {Best Practices for Scientific Computing}.
+\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
+
+\bibitem{Axelrod1995}
+Jianzhong Wu and Robert Axelrod.
+\newblock {How to cope with noise in the iterated prisoner's dilemma}.
+\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
+
+\end{thebibliography}
 
@@
 
-\section{List of players}\label{app:list_of_players}
+\section{Appendix A: List of players}\label{app:list_of_players}
 
@@
 \begin{enumerate}
-    \input{tex/list_of_players.tex}
+\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
+\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
+\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
+\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
+\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
+\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
+\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
+\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
+\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
+\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
+\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
+\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
+\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
+\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
+\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
+\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
+\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
+\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
+\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
+\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
+\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
+\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980a}
+\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
+\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006}
+\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006}
+\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
+\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
+\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
+\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Banks1990, Beaufils1997, Berg2015, Li2011}
+\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
+\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
+\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
+\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
+\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
+\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
+\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Stewart2012}
+\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
+\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
+\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
+\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
+\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980a}
+\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
+\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
+\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006}
+\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
+\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
+\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
+\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980a, Tzafestas2000}
+\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
+\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
+\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
+\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
+\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
+\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
+\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
+\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
+\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
+\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
+\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
+\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
+\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
+\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
+\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
+\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
+\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
+\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
+\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
+\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
+\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
+\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
+\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a}
+\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
+\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
+\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980a}
+\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
+\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
+\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
+\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
+\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
+\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
+\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
+\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
+\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
+\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
+\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
+\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
+\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
+\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
 \end{enumerate}
 
+\section{Appendix B: Supplementary figures}
+
+\begin{itemize}
+    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
+for each strategy. The mean and error bars are shown against the collection of
+all opponents.
+
+    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
+\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
+the collection of all opponents.
+
+    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
+ranks of each strategy according to mean absorption probability across all
+population sizes.
+\end{itemize}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
+    \label{invasion-3}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
+    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
+    \label{invasion-14}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
+    \label{resistance-3}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
+\end{figure}
+
+\begin{figure}[!hbtp]
+    \centering
+    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
+    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
+    \label{resistance-14}
+\end{figure}
+
 \end{document}

### 2018-04-18 main.tex

@@
 Marc Harper\textsuperscript{2\Yinyang},
-Nikoleta E. Glynatsi\textsuperscript{2\ddag},
+Nikoleta E. Glynatsi\textsuperscript{1\ddag},
 Owen Campbell\textsuperscript{3\ddag},
@@
 \begin{enumerate}
- \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
+ \item Zero determinant strategies are not effective invaders or defenders for $N > 2$.
  \item Complex strategies can be effective, and in fact can naturally evolve
@@
 software is (similarly to the Axelrod library) available on
-github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
+GitHub\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
 with documentation to
@@
 and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}), using the notation common in the literature where
+and~\ref{fig:tf3}, using the notation common in the literature where
 \(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
@@
 effective for larger population sizes, but these analyses consider stationary
-behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
+behaviour, while this work runs for a fixed number of rounds \cite{stewart2013extortion}.
 The stationarity assumption allows for a deterministic payoff matrix

### 2018-07-17 main.tex
Remove all images.
Add more details about the structured strategies.
Have added a general description of FSMs but also pointed (in various
places) at the ml paper.

@@
 \usepackage{lastpage,fancyhdr}
-\usepackage{graphicx}
+\usepackage[draft]{graphicx}
 \usepackage{epstopdf}
@@
 of \textbf{164} complex and adaptive strategies for the
-IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
+IPD\@. This is made possible by the Axelrod library~\cite{axelrodproject}, an
 effort to provide software for reproducible research for the IPD\@. The library
@@
 the open source nature of the project with over 50 contributors from around the
-world, made by programmers and researchers \cite{Knight2016}. Three of the considered
+world, made by programmers and researchers~\cite{Knight2016}. Three of the considered
 strategies are finite state machines trained specifically for Moran processes
@@
 
-A number of these strategies have been trained with reinforcement learning
-algorithms prior to this study and not specifically for the Moran process.
+Using families of strategies that depend on given parameters it is possible to
+find specific parameters through a training process called reinforcement
+learning. A detailed description of the various types considered is given
+in~\cite{Harper2017}.
+
+A number of these strategies have been trained this way (see~\cite{Harper2017})
+prior to this study and not specifically for the Moran process.
 
@@
 algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. They were trained to
+against all other opponents~\cite{affenzeller2009genetic}. They were trained to
 win IPD tournaments by maximizing their mean total payoffs against a variety
@@
 strategies are carried to the next generation along with new variants. Similar
-methods appear in the literature \cite{Ashlock2006}.
+methods appear in the literature~\cite{Ashlock2006}.
 There has also been some work on strategies using an evolutionary algorithm in real time:
@@
 
-All of the training code is archived at \cite{marc_harper_2017_824264}. This
+All of the training code is archived at~\cite{marc_harper_2017_824264}. This
 software is (similarly to the Axelrod library) available on
@@
 
-There are three further strategies trained specifically for this study; Trained
-FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}, using the notation common in the literature where
-\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
-\(A_2\) as well as arrows corresponding to changes of state.
+One particular family of strategies that has been studied in the literature are
+called finite state machines. These mathematical models consist of states and
+and responses to actions from one state to another. In the context of the IPD, a
+finite state machine, is a mapping from states and opponent actions to states
+and an action. For further details on this type of strategy, the reader is
+referred to~\cite{Ashlock2006, Harper2017}.
+
+There are three further strategies trained specifically for this
+study; Trained FSM 1, 2, and 3 (TF1 - TF3). These are finite state
+machines of 16, 16, and 8 states respectively.  These are shown in
+Fig~\ref{fig:tf1},~\ref{fig:tf2} and~\ref{fig:tf3}, using the notation common in
+the literature where \(A_1/A_2\) is the action of the opponent \(A_1\) and the
+response of the player \(A_2\) as well as arrows corresponding to changes of
+state.
 

### 2018-07-17 main.tex
Add extra comment about training criteria.
I'm not convinced it actually adds much but I think it's a
straightforward thing to add.

@@
 strategies, listed (with their properties) in the Appendix,
-are used from the Axelrod library. There are
+are used from the Axelrod library. The appendix includes citations to the
+original description of each strategy. There are
 43 stochastic and
@@
 of the same kind of training processes and is a better combined invader-resistor
-than the invaders that were trained previously to maximize payout.
+than the invaders that were trained previously to maximize payout. It is of
+interest to note that when trained in a payoff maximising criteria the finite
+state machines do not evolve to obtain a handshake, this highlights the
+importance of the evolutionary effect on this important mechanism.
 

### 2018-07-17 main.tex
Add further details about handshake mechanism.

@@
      through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or possess a handshake mechanism.
+ \item The strongest resistors specifically evolve or possess a handshake
+     mechanism.
  \item Strong invaders are generally cooperative strategies that do not defect
@@
 \end{enumerate}
+
+The notion of a handshake has been described previously in~\cite{Robson1990} and
+corresponds to idea that an individual exhibits behaviour that starts with a
+recognisable pattern. This in turn allows them to identify memers of their own
+type (who would exhibit the same pattern). This is analogous
+to the biological notion of `kin recognition' where individuals have the ability
+to recognise the phenotype of their own kin ~\cite{Mateo2003}.
 
@@
 a stochastic or error-correcting handshake that is an excellent resistor even in
-noisy environments \cite{Lee2015}.
+noisy environments~\cite{Lee2015}.
 
@@
   Prisoner's Dilemma}.
-\newblock arXiv:1707.06307, 2017.
+\newblock {\em PLOS ONE}, 12(12): 12 2017.
 
@@
 \newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
+
+\bibitem{Mateo2003}
+Jill M. Mateo.
+\newblock {Kin recognition in ground squirrels and other rodents}.
+\newblock In {\em Journal of Mammalogy}, 84 (4), 1163--1181
 

### 2018-07-17 main.tex
Fix a strange par indent.

@@
 
-When $N=2$ the fixation probabilities of the Moran process are effectively measures
-of the distribution of  relative
-mean payoffs over all possible matches between two players. The strategy
-that scores higher than the other more often will fixate more often. For \(N=2\)
-the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in the following sections.
-The top 16 (10\%) strategies are
-shown in
-
+When $N=2$ the fixation probabilities of the Moran process are effectively
+measures of the distribution of  relative mean payoffs over all possible matches
+between two players. The strategy that scores higher than the other more often
+will fixate more often. For \(N=2\) the two cases of \(x_1\) and \(x_{N-1}\)
+coincide, but will be considered separately for larger \(N\) in the following
+sections.  The top 16 (10\%) strategies are shown in
 Table~\ref{tbl:summary_top_2} and figures showing the performance of all
-strategies are available in the appendix.
-The top five ranking strategies are:
+strategies are available in the appendix.  The top five ranking strategies are:
 

### 2018-07-18 main.tex
Fix unclear sentences.
Also took the opportunity for minor fixes.

@@
 
-The notion of a handshake has been described previously in~\cite{Robson1990} and
-corresponds to idea that an individual exhibits behaviour that starts with a
-recognisable pattern. This in turn allows them to identify memers of their own
-type (who would exhibit the same pattern). This is analogous
-to the biological notion of `kin recognition' where individuals have the ability
-to recognise the phenotype of their own kin ~\cite{Mateo2003}.
+The notion of a \textbf{handshake} has been described previously
+in~\cite{Robson1990} and corresponds to the idea that an individual exhibits
+behaviour that starts with a recognisable pattern. This in turn allows them to
+identify individuals of their own type (who would exhibit the same pattern).
+This is analogous to the biological notion of `kin recognition' where
+individuals have the ability to recognise the phenotype of their own
+kin~\cite{Mateo2003}.
 
@@
 
-The Moran process was initially introduced in \cite{Moran1957}. It has since
+The Moran process was initially introduced in~\cite{Moran1957}. It has since
 been used in a variety of settings including the understanding of the spread of
-cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
-emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
+cooperative and non-cooperative behaviour such as cancer~\cite{West2016} and the
+emergence of cooperative behaviour in spatial topologies~\cite{Nowak2017}.
 However these works mainly consider relatively simple strategies. A few works
@@
 \cite{Li2014} but this is not done in the more widely used setting of the Moran
-process, rather in terms of infinite population stability. In \cite{Baek2016}
+process, rather in terms of infinite population stability. In~\cite{Baek2016}
 Moran processes are studied in a theoretical framework for a small subset of
@@
 Of particular interest are the zero determinant strategies introduced in
-\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
+\cite{Press2012}. It was argued in~\cite{stewart2013extortion} that generous
+ZD strategies are robust against invading strategies. However, in~\cite{Lee2015},
 a strategy using machine learning techniques was capable of resisting invasion
-and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
+and also able to invade any memory one strategy. In 2017,~\cite{Hilbe2017}
 has investigated the effect of memory length on strategy performance and the
 emergence of cooperation but this is not done in a Moran process context and only
-considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
+considers specific cases of memory 2 strategies. In~\cite{Adami2013} it was
 recognised that many zero determinant strategies do not fare well against
@@
 strategies, listed (with their properties) in the Appendix,
-are used from the Axelrod library. The appendix includes citations to the
+are used from the Axelrod library. The appendix also includes citations to the
 original description of each strategy. There are
@@
 A number of these strategies have been trained this way (see~\cite{Harper2017})
-prior to this study and not specifically for the Moran process.
+prior to this study and not specifically for the Moran process. For example:
 
@@
 called finite state machines. These mathematical models consist of states and
-and responses to actions from one state to another. In the context of the IPD, a
-finite state machine, is a mapping from states and opponent actions to states
-and an action. For further details on this type of strategy, the reader is
-referred to~\cite{Ashlock2006, Harper2017}.
+and responses to actions which indicate a next state given an action.  In the
+context of the IPD, a finite state machine, is a mapping from an arbitrary list
+of states and opponent actions (Cooperation or Defection) to states and an
+action (Cooperation or Defection). For further details,
+the reader is referred to~\cite{Ashlock2006, Harper2017}.
 
 There are three further strategies trained specifically for this
-study; Trained FSM 1, 2, and 3 (TF1 - TF3). These are finite state
+study; Trained FSM 1, 2, and 3 (TF1 \- TF3). These are finite state
 machines of 16, 16, and 8 states respectively.  These are shown in
@@
 
-As opposed to the previously described strategies, these strategies were trained
-with the objective function of \textit{mean fixation probabilities for Moran
-processes} starting at initial population states consisting of \(N/2\)
-individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the Axelrod library:
+As opposed to the previously described strategies~\cite{Harper2017}, these
+strategies were trained with the objective function of \textit{mean fixation
+probabilities for Moran processes} starting at initial population states
+consisting of \(N/2\) individuals of the training candidates and \(N/2\)
+individuals of an opponent strategy, taken from a selection of 150 opponents
+from the Axelrod library:
 
@@
 results of this
-manuscript are presented in which will
+manuscript will
 present a detailed analysis of all the data generated. Finally,
@@
 
-It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
-for which a zero determinant strategy does appear in the top 10\% ranking
-strategies: ZD-extort-4. The performance of zero determinant strategies will be
-examined more closely.
+It is also noted that TF1, TF2 and TF3 all perform well for this case of
+\(N=2\). This is also the value of \(N\) for which a zero determinant strategy
+does appear in the top 10\% ranking strategies: ZD-extort-4. The performance of
+zero determinant strategies will be examined more closely.
 
@@
 
-% In the next sections close attention to
-% strategies who are strong invaders/resistors is given.
-
 \subsubsection*{Strong Invaders}
@@
 for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies previously discussed perform well for high \(N\).
+Once again none of the short memory strategies previously discussed perform well
+for high \(N\).
 
@@
 Handshake (which ranks highly for the smaller values of \(N\)) were
-programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
-process without any priming.
+programmed, the handshakes of TF1 and TF2 evolved without any priming.
 
@@
 The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
+in particular TF1, TF2 and TF3 ranked one, third and eighth. This is to be
 expected since, as described previously these strategies
@@
 performs in any Moran process for \(N>2\) has
-little to do with the performance for \(N=2\). This illustrates why the strong
-performance of zero determinant strategies predicted in \cite{Press2012} does
+low correlation with the performance for \(N=2\). This illustrates why the strong
+performance of zero determinant strategies predicted in~\cite{Press2012} does
 not extend to larger populations. This was discussed theoretically in

### 2018-07-18 response_to_reviewers.tex
First draft of response to reviews.
Write response to reviews.

--- 2017-10-31 response_to_reviewers.tex
@@
 
-We would like to start our responses by stating that we feel that the reviews we
-have received are fair and detailed. It is clear that the reviewers are aiming
-to help us improve the manuscript and we are grateful for their time.
+Thank you for the review of our paper. We are delighted by the reviews: the
+second author feeling there are no modifications necessary and the second
+pointing out clarifications which have given us the opportunity to improve the
+manuscript.
 
-We were particularly happy to note that the reviewers not only felt the work was
-of interest but made a point to note that our open scientific approach was
-noteworthy (publishing of source code and data).
+\begin{quote}
+	1. Please ensure that your manuscript meets PLOS ONE's style requirements,
+	including those for file naming. The PLOS ONE style templates can be found at
+	\url{http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf}
+	and
+	\url{http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf}
+\end{quote}
 
-\begin{verbatim}
-    Remember that it is possible to put material into an on-line appendix which
-    is not page-limited if there are things you feel require more space to
-    display.
-\end{verbatim}
+\begin{quote}
+    2. Please remove your figures from within your manuscript file, leaving only
+    the individual TIFF/EPS image files, uploaded separately.  These will be
+    automatically included in the reviewers’ PDF.
+\end{quote}
 
-This is probably the most important change to the manuscript. We have moved most
-of the figures to a supplementary materials document which not only allows for
-them to be presented in a clearer way but also allows for all cases (variety of
-population sizes) to be included.
-
-We have referred to this throughout the text simply as `supplementary material',
-if there is a better way to do this we would be happy to change.
+All files have been renamed as requested and otherwise, the document follows the
+given LaTeX style template.
 
@@
 
-\begin{verbatim}
-   It's not easy to solve, so I can only point out the problems, and ask you to
-   do what is possible to fix them. One possibility would be to put all figures
-   in a downloadable Appendix, or some other online resource; and maybe remove
-   some of the figures from the paper, in order to make more room for the
-   others.
-\end{verbatim}
+\begin{quote}
+    1) The authors discussed about as many as 164 strategies, which were
+    trained/generated via different algorithms. Since understanding how the
+    strategies work plays an important role in understanding why some of them
+    succeed, I strongly suggest the authors to introduce the strategies in a more
+    detailed and clear way, especially those based on finite state machines as I
+    find no reference of them yet some of them perform well in the comparisons.
+\end{quote}
 
-Thank you for acknowledging the difficulty we're presented with. We feel that
-having opted to put most of the figures in supplementary materials we arrive at
-a more concise paper with much clearer plots (as they have more space).
+This is a well made point by the referee: ensuring the reader can understand
+these is vital to the paper.
+We have clarified the description of the strategies:
 
-We have also endeavoured to clear up the plots that have remained in the paper
-(for example by removing cluttering labelling).
+\begin{itemize}
+    \item Highlight that the appendix contains references for each strategy
+        including pointing to a recently published paper that goes in to details
+        about the structure of these strategies.
+    \item A more formal definition of a finite state machine explaining how they
+        fit in the framework of the IPD. We also have included another reference
+        which describes these.
+\end{itemize}
 
-\begin{verbatim}
-    font in the Appendix could be reduced (for example to the same size of the
-    font in the references)
-\end{verbatim}
+\begin{quote}
+  2) During the training/screening process, strategies generated via different
+  algorithms were trained according to different criteria to determine whether a
+  strategy was well trained or not. As examples, some were trained to maximize
+  their payoff while others were trained with the objective function of mean
+  fixation probabilities of Moran processes. So I am curious about how different
+  criteria influence the features of the strategies? Will the conclusion of this
+  work change if some strategies are trained in terms of other criteria?
+\end{quote}
 
-This has been done.
+The referee asks a good question here, indeed the conclusion would be different
+if strategies were trained in terms of other criteria. We have added a sentence
+to this effect at the conclusion section of the paper highlighting that training
+with evolutionary criteria seems to be fundamental to the appearance of a
+handshake mechanism.
 
-\begin{verbatim}
-    When you speak about evolutionary computation applied to the IPD, you could
-    add some words about reference [21], that is otherwise only cited for GTFT.
-    The basic idea of the publication was to create an EA able to adapt its
-    behavior by building a model of the opponent 'online', during the game, and
-    then exploiting the opponent's weaknesses. It's unpractical to use in your
-    experiments (reported computational time is considerable, the technique is
-    tailored for 1vs1 games as it can only model one opponent), but it could be
-    interesting for the reader.
-\end{verbatim}
+\begin{quote}
+  3) The concept `handshake mechanism' is essential to appreciate the results as
+  well as conclusion of this work but is not well defined, hence I suggest the
+  authors to explain this concept clearly.
+\end{quote}
 
-Thank you for pointing this out, we have included these details in our
-discussion.
+We have added a better description of the term handshake mechanism after it is
+first mentioned in the introduction. We have also included a reference to
+another paper that makes mention of this as well as briefly discussing the
+biological analogy of `kin recognition`.
 
-\begin{verbatim}
-- capitalization of words in the title is not consistent; why is "Emergence" with a capital "E", but "iterated" does not have a capital "I"?
-\end{verbatim}
+\begin{quote}
+  4) In line 241-242, it looks weird that there is a new paragraph starting in
+  the middle of the sentence `The top 16 (10\%) strategies are shown in Table 4
+  and figures...'
+\end{quote}
 
-We have fixed this.
+Thank you to the referee for pointing this out: it was an error and has been
+fixed.
 
-\begin{verbatim}
-- page 1
-	-- Recently, some strategies...can manipulate some... -> remove 'some'
-\end{verbatim}
+\begin{quote}
+  5) There are not a few phrases and sentences that may make the readers
+  confusing. One example is `This is also the N for which...' in line 256.
+\end{quote}
 
-\begin{verbatim}
-- page 2
-	-- The strongest resistors specifically evolve or have -> possess
-	-- Some work has looked -> A few works looked...
-	-- http link should be put in a footnote, and using \url{} (if you are writing in Latex)
-\end{verbatim}
-
-\begin{verbatim}
-- page 4
-	-- ...to analytical results in some cases -> a few selected cases
-\end{verbatim}
-
-\begin{verbatim}
-- page 5
-	-- The difference is that CS will
-defect after the handshake if the opponent defects while
-handshake will not. -> last Handshake should be capitalized, to separate the player from the strategy
-	-- Tables II -> Table II
-\end{verbatim}
-
-\begin{verbatim}
-- page 8
-	--  This will be explored
-further in the next section, looking not only at x 1 and x N −1
-but also consider x N/2 . -> considering...
-\end{verbatim}
-
-\begin{verbatim}
-- page 10
-	-- procceses -> processes
-	-- TABLE VI: replace 'some' with 'a few selected'
-\end{verbatim}
-
-All of these have been addressed.
-
-\begin{verbatim}
-- page 3
-	-- why did you present TF1, TF2, TF3 in reverse ordering?
-\end{verbatim}
-
-We were not too sure what happened here, looking at our version the ordering was
-correct. We will specifically inspect the proofs upon submission.
-
-\begin{verbatim}
-	-- Using this it is a known results -> I could not understand what you mean here
-\end{verbatim}
-
-\begin{verbatim}
-	-- These
-are no longer a good match which highlights the weakness of
-assuming a given interaction between two IPD strategies can be
-summarised with a set of utilities as shown in (1). -> this phrase is also not clear
-\end{verbatim}
-
-We have addressed both of these comment by rephrasing.
+Thank you for pointing this out. That particular sentence has been clarified and
+a thorough edit of the paper has been undertaken identifying and modifying
+further confusing sentences.
 
@@
 
-\begin{verbatim}
+\begin{quote}
+  Reviewer \#2: This manuscript provides a detailed numerical analysis of
+  agent-based simulations of 164 complex and adaptive strategies for the IPD,
+  using an online GitHub library. The authors presented a lot of insights and
+  empirical results. In my opinion, this paper is excellent, and worth publishing
+  in the present form.
+\end{quote}
 
-    1. Title -- I don't think your title represents your paper well. It isn't
-    really about cooperation and it uses the Moran process rather than studying
-    it. I suggest:
-
-    A Comprehensive Empirical Study Of Iterated Prisoner's Dilemma Strategies
-    Using The Moran Process
-
-    Or, if you prefer to focus on results:
-
-    Iterated Prisoner's Dilemma Strategies With Handshakes Are More
-    Evolutionarily Stable
-
-    Whatever you decide on, make sure all words in the title are capitalized.
-
-\end{verbatim}
-
-Many thanks for the suggestion, having reflected on this and as this wasn't
-raised by any of the other reviewers we have decided to keep with the original
-title. We feel that the self recognition mechanisms serve as a way to reinforce
-cooperation which we would prefer to keep in the title. If you feel particularly
-strongly about this we would re consider.
-
-\begin{verbatim}
-    On page 3 you give noise values for TF1, TF2, and TF3. Some explanation of
-    this would be nice. Also, how did you choose TF1, TF2, and TF3? Were they
-    chosen randomly from many runs or were they chosen based on some selection
-    principle?
-\end{verbatim}
-
-The paragraphs just before `There are three further strategies trained
-specifically for this
-study' describe the training mechanism used to obtain TF1, TF2 and TF3.  Given
-that the Moran processes used are not in a noisy environment we did not feel the
-need to discuss this further (2/3 of the trained strategies were not trained in
-noise).
-
-\begin{verbatim}
-
-    3. Figures 2, 3, 4 -- hard to see arrow heads, make them larger
-
-    4. Figures 5 and 6 -- These are too small. It would be better to show fewer
-    examples at a readable size.
-
-    5. Figure 13 -- text labeling axes and scale is too small.
-
-    6. Figure 14 -- Heat map labels should be larger as well as the x-axis label
-    "Rounds." Given space restrictions, it is not possible to make the strategy
-    names larger, but on your other figures it is possible to enlarge the image
-    to read the strategy names and on these figures it is not. Maybe change the
-    file format or the resolution.
-
-    7. Typos
-
-    Section IIIB: "given in Tables II" should be "Table II"
-
-    Section IIIC: "There are are only two new strategies" -- cut repeated "are"
-
-    Section IIID: "Figure 13 show" should be "shows"
-
-    Section V: "allowing the each strategy" -- cut the word "the"
-\end{verbatim}
-
-We have hopefully addressed all these points satisfactorily: making images
-larger and more readable as well as picking up the typos. 
-In particular for the heatmap, we have enlarged the text and simply removed the
-name labels (they are not important). The main point being to see the initial
-play handshake, and to this end we have chosen to only display 15 rounds (as
-opposed to 200).
-Thank you for bringing this to our attention.
-
-\section{Comments from third reviewer}
-
-\begin{verbatim}
-    The first overarching comment is on the density and unreadability of the
-    figures. Displaying as much data as possible is laudable, but to my eyes the
-    condition "as possible" no longer holds.
-\end{verbatim}
-
-We agree and have (as detailed in previous comments) hopefully addressed this.
-
-\begin{verbatim}
-    Particular examples: Fig. 5 is unreadably small, and without extreme
-    magnification it is impossible to read the titles/axes/any words in the
-    subfigure graphics. Note that this *can* be remedied by repeating such
-    information outside of the graphics, and explicitly writing that "the red
-    lines are x_n-1, x-axis is N from 2 to 14, y-axis is fixation probability
-    from 0 to 1" in the caption would allow those graphs to be understood.
-\end{verbatim}
-
-These pointers have been added to the caption but also the number of these
-specific plots have been reduced which also hopes with clarity.
-
-\begin{verbatim}
-For this, tables may well be more readable in conjunction with the figures. Fig.
-2-4 are on the edge of being uninterpretable, and a transition table would also
-help with implementing the strategy.
-\end{verbatim}
-
-We have improved the size of Fig 2-4. We have however chosen to stick with
-diagrams as this is often the way they are represented in the literature (for
-example in Ashlock's papers). Note that we've added a description of the
-interpretation of the figures. If you feel strongly about a table we will
-reconsider.
-
-\begin{verbatim}
-    Fig. 13,14 have unreadable axes. Additionally, Fig.7,9,11 are not only
-    unreadable, but nowhere is it described what the error bars are (I am
-    presuming you treat "fixation probability against opponent X" as one data
-    point and are displaying stats over X, but other possibilities abound). Same
-    goes for Fig 14: what is the cooperation rate per round? Is it fraction of C
-    played by that strategy (as opposed to payoff R) observed in round n (out of
-    how many?), over 10k trials of one single head-to-head match?
-\end{verbatim}
-
-Fig 13,14 have improved axes but also are now improved due to the fact that only
-15 rounds are presented. As well as this, the requested explanations have all
-been included.
-
-\begin{verbatim}
-    Another general observation is with the strategy listing. The "memory
-    depth", in number of rounds of history necessary, is given. This is one
-    particular way of considering strategies, but in my opinion a far more
-    important measure is minimal number of states in a FSM representation. An
-    example is given where GRIM(Grudger) would need infinite memory *as number
-    of rounds input to a lookup table*, but clearly GRIM needs just one bit of
-    memory: whether the opponent has ever defected, which obviously maps to its
-    2^1 states. Allowing the FSM to specify what information it stores is much
-    more flexible. I strongly suggest including the state size as well.
-\end{verbatim}
-
-We have added the number of states in all FSM strategies to this listing. Note
-that we have not attempted to quantify the minimal state representation of all
-strategies (this in itself would be an impressive piece of work outside of the
-scope of this paper).
-
-\begin{verbatim}
-    Several base details of the experiments which I would need to understand,
-    particularly in Algorithm 2:
-    * rounds per game in the actual IPD played
-    I cannot locate this fundamental number, which matters (see DOI
-    10.1109/CIG.2015.7317950)
-    * results <- cache(match)
-    There is a discussion that stochastic strategies exist, and the
-    interpretation of Fig. 6 implies the result of a matchoff remains stochastic
-    (as opposed to taking expected score). Does this mean the cache is a
-    probabilistic function? This is unexpected and should be noted as well in
-    the algorithm.
-    * parent <- selected randomly in proportion to total match payoffs
-    Each individual is selected randomly in proportion to *its* total match
-    payoffs against every other individual? This could be clearer
-    * kill off <- random player from population
-    Is this uniformly at random? This should be specified
-\end{verbatim}
-
-This have all been addressed, in particular we have added to the brief explanation
-of the sampling that occurs from the cached results but made this very explicit.
-
-\begin{verbatim}
-I must take particular issue with the last paragraph of Section II. This makes
-two significant claims with implications for future work:
-1. Sampled fixation probabilities for deterministic strategies are a "perfect
-match" with the theoretical probabilities computed above (the latter is strongly
-appreciated)
-2. Such sampled fixation probabilities for stochastic strategies are "no longer
-a good match" with the theoretical probabilities computed using (presumably)
-expected payoff between the pairs
-
-I cannot accept either statement given the current manuscript, nor accept the
-manuscript without them. To claim 1., a cursory glance at Fig. 5(a,b,e) belie a
-perfect match. To claim 2., Fig. 6(a,b,f) look better than the three
-aforementioned graphs. The issue is, of course, that these probabilities are
-(each) binomially-distributed samples. Wherever there is sampling, and matching
-to theoretical is mentioned, I expect a statistical test. Here, I request
-confidence intervals computed using Bonferroni- (or equivalent) corrected
-binomial models be at least displayed in Fig. 5-6. Claim 2., which seems true,
-requires a corrected exact test against H0.
-\end{verbatim}
-
-We feel that the reviewer has made an excellent point. To make things clearer we
-have chosen to only show one pair of strategies for both types (deterministic
-and stochastic) and have:
-
-\begin{itemize}
-    \item Added simulated confidence bars obtained using an asymptotic normal
-        approximation.
-    \item Carried out a t test over all values in the plots which show the level
-        of significance of the differences (for stochastic) and similarities
-        (for deterministic) of the results.
-\end{itemize}
-
-We contemplated including similar plots/tables that show similar outcomes to the
-supplementary materials but felt that this was perhaps not necessary and would
-be an overflow of information.
-
-\begin{verbatim}
-Firstly, the extremely wide error bars (many are basically 0-1) imply, as we all
-know, that the relation "X beats Y at a particular type of IPD competition" is
-not even close to transitive. Computing the mean fixation probability *against a
-particular set of opponents* is highly sensitive to the composition of the
-competition, in the instant case "wide selection across the literature" with
-unknown weighting. There is no reason to accept the authors' choice, indeed any
-choice, as authoritative.
-
-I strongly suggest that particular subgroups of strategies (ZD, simple FSM,
-handshakers, etc.) be evaluated in block fashion against other subgroups. This
-would allow statements of the form "ZD-type strategies fail (relative to
-neutral) to invade [group] at N=? pairwise", which is alluded to in the paper,
-with the bonus of readable data for each claim. Please ensure statistical
-analysis for these are multiple-testing corrected.
-\end{verbatim}
-
-We acknowledge the point made here by the referee: it is a good one. We would
-suggest that as well as the large number of strategies they also represent quite
-a diverse selection. However the point made by the referee stands. We have
-included this point in our discussion. Note however that in terms of carrying
-out a subgroup analysis, we feel that this would not fall within the scope of
-this work. To do it properly would constitute a fundamental rewrite of all the
-results. This has been noted in the discussion, including the important point
-that by making our data available anyone could do this (and we hope to do so
-ourselves).
-
-\begin{verbatim}
-Secondly, with the results as computed globally, reporting the mean is
-insufficient for these wide ranges; for each of Fig. 7(b) and Tables II-III
-other generic descriptive stats are necessary.
-\end{verbatim}
-
-A number of further statistics have been reported.
-
-\begin{verbatim}
-Minor detail: references [11] and [13] are the same work. Formatting of the
-references in general is also worth checking again.
-\end{verbatim}
-
-This has been done.
+Thank you for the confidence in our work and for the time taken to review.
 

### 2018-07-18 main.tex
Reformat files to eps (and write rename script).
Fix minor points that Nik caught.

@@
 One particular family of strategies that has been studied in the literature are
-called finite state machines. These mathematical models consist of states and
+called finite state machines. These mathematical models consist of states
 and responses to actions which indicate a next state given an action. In the
 context of the IPD, a finite state machine, is a mapping from an arbitrary list
-of states and opponent actions (Cooperation or Defection) to states and an
-action (Cooperation or Defection). For further details,
+of states and opponent actions (cooperation or defection) to states and an
+action (cooperation or defection). For further details,
 the reader is referred to~\cite{Ashlock2006, Harper2017}.
@@
     \centering
-    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
+    \includegraphics[width=.95\columnwidth]{./Fig1.eps}
     \caption{Comparison of theoretic and actual Moran Process fixation
@@
     \centering
-    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
+    \includegraphics[width=.95\columnwidth]{./Fig2.eps}
     \caption{Comparison of theoretic and actual Moran Process
@@
     \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
+    \includegraphics[width=\columnwidth]{./Fig3.eps}
     \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
+    \includegraphics[width=\columnwidth]{./Fig4.eps}
     \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
@@
     \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
+    \includegraphics[width=\columnwidth]{./Fig5.eps}
     \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
@@
 The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, third and eighth. This is to be
+in particular TF1, TF2 and TF3 ranked first, third and eighth. This is to be
 expected since, as described previously these strategies
@@
         \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
+        \includegraphics[width=\columnwidth]{./Fig6.eps}
         \caption{Rank based on \(x_1\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
+        \includegraphics[width=\columnwidth]{./Fig7.eps}
         \caption{Rank based on \(x_{N - 1}\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
+        \includegraphics[width=\columnwidth]{./Fig8.eps}
         \caption{Rank based on \(x_{N/2}\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
+        \includegraphics[width=\columnwidth]{./Fig9.eps}
         \caption{TF1}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
+        \includegraphics[width=\columnwidth]{./Fig10.eps}
         \caption{TF2}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
+        \includegraphics[width=\columnwidth]{./Fig11.eps}
         \caption{TF3}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
+        \includegraphics[width=\columnwidth]{./Fig12.eps}
         \caption{CS}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig13.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=3\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig14.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=4\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig15.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=5\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig16.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=6\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig17.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=7\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig18.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=8\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig19.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=9\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig20.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=10\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig21.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=11\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig22.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=12\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig23.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=13\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
+    \includegraphics[width=\textwidth]{./Fig24.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=14\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig25.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig26.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig27.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig28.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig29.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig30.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig31.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig32.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig33.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig34.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig35.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
+    \includegraphics[width=\textwidth]{./Fig36.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}

### 2018-07-19 main.tex

@@
 action (cooperation or defection). For further details,
-the reader is referred to~\cite{Ashlock2006, Harper2017}.
+the reader is referred to~\cite{Ashlock2006, AshlockBook, Ashlock2007, Harper2017}.
 
@@
 
+\bibitem{Ashlock2007}
+Wendy Ashlock
+\newblock {Why some representations are more cooperative than others for
+prisoner's dilemma}
+\newblock {\em Foundations of Computational Intelligence, 2007. FOCI 2007. IEEE
+symposium on}, 314--321,
+  2007.
+
 \bibitem{Ashlock2006}
@@
   pages 297--304. IEEE, 2006.
+
+\bibitem{AshlockBook}
+Daniel Ashlock.
+\newblock{Evolutionary computation for modeling and optimization},
+\newblock{Springer Science \& Business Media}
+2006
 

### 2018-08-08 response_to_reviewers.tex
Add references suggested by Marc.
Fix cover letter.

@@
 
+\begin{quote}
+In the cover letter, the authors said "We feel that it is an excellent fit for IEEE Transactions on Evolutionary Computation."
+
+If that so, we should not consider the publication of this paper here in this journal before the authors clarify this and confirm their decision.
+\end{quote}
+
+This was a mistake duration the preparation of the cover letter. This has been
+fixed: clearly stating our belief that PLOS one is a good fit.
+
 \section{Comments from first referee}
@@
     \item A more formal definition of a finite state machine explaining how they
-        fit in the framework of the IPD. We also have included another reference
+        fit in the framework of the IPD. We also have included numerous references
         which describes these.

### 2018-08-10 main.tex
Add the logo back in because PLOS's compiler breaks.
Re rename all images.

@@
 \usepackage{lastpage,fancyhdr}
-\usepackage[draft]{graphicx}
+\usepackage{graphicx}
 \usepackage{epstopdf}
@@
 \usepackage{subcaption}
+\usepackage{xstring}
+
 \usepackage{tikz}
-\usepackage{xstring}
-
 \usetikzlibrary{calc, shapes, patterns}
@@
     \centering
-    \scalebox{.7}{
-
-\begin{tikzpicture}[scale=.9]
-	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-
-	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-
-	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);
-
-	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-
-	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-\end{tikzpicture}
-
-}
+    \includegraphics[draft, width=\textwidth]{Fig1.eps}
     \caption{A diagrammatic representation of a Moran process.}
@@
     \centering
-    \scalebox{.7}{
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
-	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
-	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
-	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
-	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};
-
-	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
-	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};
-
-	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
-	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
-	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};
-
-	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
-	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
-	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};
-
-	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
-	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
-    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);
-
-    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
-    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);
-
-    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
-    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);
-
-    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
-    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);
-
-    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
-    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);
-
-    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
-    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);
-
-    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
-    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);
-
-    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
-    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);
-
-    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
-    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);
-
-    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
-    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);
-
-    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
-    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);
-
-    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
-    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);
-
-    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
-    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);
-
-    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
-    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);
-
-    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
-    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);
-
-    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
-    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);
-
-    \end{tikzpicture}
-    }
+    \includegraphics[draft, width=\textwidth]{Fig2.eps}
     \caption{TF1: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \scalebox{.7}{
-
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};
-
-	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
-    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
-    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
-    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
-    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
-    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
-    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};
-
-    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
-    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
-    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
-    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
-    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
-    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
-    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};
-
-    \coordinate[below of=0] (s);
-
-    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);
-
-    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
-    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);
-
-    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
-    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);
-
-    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
-    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);
-
-    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
-    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/D$} (1);
-
-    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
-    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);
-
-    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
-    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);
-
-    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
-    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);
-
-    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
-    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);
-
-    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
-    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);
-
-    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
-    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);
-
-    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
-    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);
-
-    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
-    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);
-
-    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
-    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);
-
-    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
-    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);
-
-    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
-    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);
-
-    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
-    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);
-
-    \end{tikzpicture}
-    }
+    \includegraphics[draft, width=\textwidth]{Fig3.eps}
     \caption{TF2: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];
-
-    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
-    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
-    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$};
-    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
-    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};
-    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
-    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
-    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-
-    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
-    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
-    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
-    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
-    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);
-
-    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
-    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
-    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);
-
-    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);
-
-    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
-    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
-    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
-    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
-    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
-    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
-    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
-    \end{tikzpicture}
+    \includegraphics[draft, width=\textwidth]{Fig4.eps}
     \caption{TF3: an 8 state finite state machine.}
@@
     \centering
-    \includegraphics[width=.95\columnwidth]{./Fig1.eps}
+    \includegraphics[draft, width=.95\columnwidth]{./Fig5.eps}
     \caption{Comparison of theoretic and actual Moran Process fixation
@@
     \centering
-    \includegraphics[width=.95\columnwidth]{./Fig2.eps}
+    \includegraphics[draft, width=.95\columnwidth]{./Fig6.eps}
     \caption{Comparison of theoretic and actual Moran Process
@@
     \centering
-    \includegraphics[width=\columnwidth]{./Fig3.eps}
+    \includegraphics[draft, width=\columnwidth]{./Fig7.eps}
     \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{./Fig4.eps}
+    \includegraphics[draft, width=\columnwidth]{./Fig8.eps}
     \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
@@
     \centering
-    \includegraphics[width=\columnwidth]{./Fig5.eps}
+    \includegraphics[draft, width=\columnwidth]{./Fig9.eps}
     \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig6.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig10.eps}
         \caption{Rank based on \(x_1\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig7.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig11.eps}
         \caption{Rank based on \(x_{N - 1}\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig8.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig12.eps}
         \caption{Rank based on \(x_{N/2}\)}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig9.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig13.eps}
         \caption{TF1}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig10.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig14.eps}
         \caption{TF2}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig11.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig15.eps}
         \caption{TF3}
@@
         \centering
-        \includegraphics[width=\columnwidth]{./Fig12.eps}
+        \includegraphics[draft, width=\columnwidth]{./Fig16.eps}
         \caption{CS}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig13.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig17.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=3\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig14.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig18.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=4\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig15.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig19.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=5\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig16.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig20.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=6\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig17.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig21.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=7\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig18.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig22.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=8\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig19.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig23.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=9\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig20.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig24.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=10\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig21.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig25.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=11\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig22.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig26.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=12\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig23.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig27.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=13\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig24.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig28.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=14\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig25.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig29.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig26.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig30.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig27.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig31.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig28.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig32.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig29.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig33.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig30.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig34.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig31.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig35.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig32.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig36.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig33.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig37.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig34.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig38.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig35.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig39.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
@@
     \centering
-    \includegraphics[width=\textwidth]{./Fig36.eps}
+    \includegraphics[draft, width=\textwidth]{./Fig40.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}

### 2018-08-10 moran_process.tex
Re rename all images.

--- 2018-04-05 plos/main.tex
@@
-% Template for PLoS
-% Version 3.4 January 2017
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
-\usepackage{algorithm,algorithmic}
-\usepackage{amsmath}
-\usepackage{authblk}
-\usepackage{booktabs}
-\usepackage{booktabs}
-\usepackage{fancyvrb}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{multicol}
-\usepackage{pdflscape}
-\usepackage{standalone}
-\usepackage{subcaption}
+\documentclass[crop,tikz]{standalone}
 \usepackage{tikz}
-\usepackage{xstring}
-
 \usetikzlibrary{calc, shapes, patterns}
-
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline
-{Evolution reinforces cooperation with the emergence of self-recognition
- mechanisms: an empirical study of strategies in the Moran process for the
- iterated prisoner's dilemma }
-% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Vincent Knight\textsuperscript{1*\Yinyang},
-Marc Harper\textsuperscript{2\Yinyang},
-Nikoleta E. Glynatsi\textsuperscript{2\ddag},
-Owen Campbell\textsuperscript{3\ddag},
-\\
-\bigskip
-\textbf{1} Cardiff University, School of Mathematics, Cardiff, UK
-\\
-\textbf{2} Google Inc., Mountain View, CA, USA
-\\
-\textbf{3} Independent Researcher, Chester, UK
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-%
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-\ddag These authors also contributed equally to this work.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* knightva@cardiff.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-    We present insights and empirical results from an extensive numerical
-    study of the evolutionary dynamics of the iterated prisoner's dilemma.
-    Fixation probabilities for Moran processes are obtained
-    for all pairs of 164 different strategies including classics such as TitForTat, zero
-    determinant strategies, and many more sophisticated strategies.
-    Players with long memories and sophisticated behaviours outperform
-    many strategies that perform well in a two player setting. Moreover we
-    introduce several strategies trained with evolutionary algorithms to
-    excel at the Moran process. These strategies are excellent invaders
-    and resistors of invasion and in some cases naturally evolve handshaking
-    mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake mechanisms.
-    This suggests that while maximizing individual payoff
-    can lead to the evolution of cooperation through invasion, the relatively
-    weak invasion resistance of payoff maximizing strategies are not as
-    evolutionarily stable as strategies employing handshake mechanisms.
-\linenumbers
-
-\section*{Introduction}
-
-The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
-used to model a variety of strategic interactions. Each player chooses
-simultaneously and independently
-between cooperation (C) or defection (D). The payoffs of
-the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
-\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one
-round game, but is commonly studied in a manner where the prior outcomes
-matter. This repeated form is called the Iterated Prisoner's
-Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
-number of strategies have been developed to take advantage of the history of
-play. Strategies referred to as zero determinant (ZD) strategies
-\cite{Press2012} can manipulate some players through extortionate mechanisms.
-
-The Moran Process \cite{Moran1957} is a model of
-evolutionary population dynamics that has been used to gain insights about the
-evolutionary stability in a number of settings.
-Several earlier
-works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
-or are limited to classes of strategies
-such as memory-one strategies that only use the previous round of play.
-
-This manuscript provides a detailed numerical analysis of agent-based simulations
-of \textbf{164} complex and adaptive strategies for the
-IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
-effort to provide software for reproducible research for the IPD\@. The library
-now contains over 186 parameterized
-strategies including classics like TitForTat and WinStayLoseShift, as well as
-recent variants such as OmegaTFT, zero determinant and other memory one
-strategies, strategies based on finite state machines, lookup tables, neural
-networks, and other machine learning based strategies, and a collection of novel
-strategies. Not all strategies have been considered for this study: excluded
-are those that make use of knowledge of the number of turns in a match
-and others that have a high
-computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 50 contributors from around the
-world, made by programmers and researchers \cite{Knight2016}. Three of the considered
-strategies are finite state machines trained specifically for Moran processes
-(described further in the Methods section).
-
-In addition to providing a large collection of strategies, the Axelrod library
-can conduct matches, tournaments and population
-dynamics with variations including noise and spatial structure.
-The strategies and simulation frameworks are
-automatically tested to an extraordinarily high degree of coverage in accordance
-with best research software practices.
-
-Using the Axelrod library and the many strategies it contains, we obtain the
-probability with which a given strategy takes over a population (referred to as
-fixation probability) for all pairs of strategies, identifying those that are
-effective invaders and those resistant to invasion, for population sizes $N=2$
-to $N=14$. Moreover we present a number (16) of strategies that were created via
-reinforcement algorithms (evolutionary and particle swarm algorithms) that are
-among the best invaders and resistors of invasion known to date, and show that
-handshaking mechanisms naturally arise from these processes as an
-invasion-resistance mechanism.
-
-In 2016, work has argued that agent-based
-simulations can provide insights in evolutionary game theory not available
-via direct mathematical analysis~\cite{adami2016evolutionary}. The results
-and insights contained in this paper would be difficult to derive analytically.
-
-In particular the following questions are addressed:
-\begin{enumerate}
-    \item What strategies are good invaders?
-    \item What strategies are good at resisting invasion?
-    \item How does the population size affect these findings?
-\end{enumerate}
-
-While the results agree with some of the published literature, it is found that:
-
-\begin{enumerate}
- \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
- \item Complex strategies can be effective, and in fact can naturally evolve
-     through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or possess a handshake mechanism.
- \item Strong invaders are generally cooperative strategies that do not defect
- first but retaliate to varying degrees of intensity against strategies that defect.
- \item Strategies evolved to maximize their total payoff can be strong invaders
- and achieve mutual cooperation with many other strategies.
-\end{enumerate}
-
-\section*{Materials and methods}
-\subsection*{The Moran Process}
-
-A Moran process is a stochastic birth death process on a finite population in which the
-population size stays constant over time. Individuals are \textit{selected}
-according to a given fitness landscape. The fitness landscape in this work is
-defined as the total utility against all other individuals in the population.
-Once selected, the individual
-is reproduced and similarly another individual is chosen to be removed from the
-population (a uniform random selection is used). This is shown diagrammatically
-in Fig~\ref{fig:moran_process}. In some settings mutation is
-also considered but without mutation (the case considered in this work) this
-process will arrive at an absorbing state where the population is entirely made
-up of players of one strategy. The probability with which a given strategy,
-starting from a single individual takes
-over a population is called the \textit{fixation probability}. A more detailed
-analytic description of this is given later. In our
-simulations offspring do not inherit any knowledge or history from parent
-replicants.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.5}{
-
 \begin{tikzpicture}[scale=.9]
@@
 \end{tikzpicture}
-
-}
-    \caption{A diagrammatic representation of a Moran process.}
-    \label{fig:moran_process}
-\end{figure}
-
-The Moran process was initially introduced in \cite{Moran1957}. It has since
-been used in a variety of settings including the understanding of the spread of
-cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
-emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider relatively simple strategies. A few works
-looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
-\cite{Li2014} but this is not done in the more widely used setting of the Moran
-process, rather in terms of infinite population stability. In \cite{Baek2016}
-Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies: strategies that recall
-the events of the previous round only.
-
-Of particular interest are the zero determinant strategies introduced in
-\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
-a strategy using machine learning techniques was capable of resisting invasion
-and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
-has investigated the effect of memory length on strategy performance and the
-emergence of cooperation but this is not done in a Moran process context and only
-considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
-recognised that many zero determinant strategies do not fare well against
-themselves. This is a disadvantage for the Moran process where the best
-strategies cooperate well with other players using the same strategy.
-
-This work uses pair-wise Moran processes in a similar way to matches in the many
-IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
-A population-based perspective is given which adds additional
-evolutionary components to the IPD, namely the evolutionary dynamics of invasion
-and resistance.
-
-\subsection*{Strategies considered}\label{sec:strategies}
-
-To carry out this numerical experiment, 164
-strategies, listed (with their properties) in the Appendix,
-are used from the Axelrod library. There are
-43 stochastic and
-121 deterministic strategies. Their memory depth,
-defined by the number of rounds of history used by the strategy each round, is
-shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
-strategy uses the entire history of play (whatever its length). For example, a
-strategy that utilizes a handshaking mechanism where the opponent's actions on
-the first few rounds of play determines the strategies subsequent behavior would
-have infinite memory depth.
-
-A number of these strategies have been trained with reinforcement learning
-algorithms prior to this study and not specifically for the Moran process.
-
-\begin{itemize}
-    \item Evolved ANN: a neural network based strategy;
-    \item Evolved LookerUp: a lookup table based strategy;
-    \item PSO Gambler: a stochastic version of the lookup table based strategy;
-    \item Evolved HMM: a hidden Markov model based strategy.
-\end{itemize}
-
-Apart from the PSO Gambler strategy, which was trained using a particle swarm
-optimisation algorithm, these strategies are trained with an evolutionary
-algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. They were trained to
-win IPD tournaments by maximizing their mean total payoffs against a variety
-of opponents. Variation is
-introduced via mutation and crossover of parameters, and the best performing
-strategies are carried to the next generation along with new variants. Similar
-methods appear in the literature \cite{Ashlock2006}.
-There has also been some work on strategies using an evolutionary algorithm in real time:
-in~\cite{Gaudesi2016}
-an evolutionary algorithm is used to build a model of the opponent and attempt
-to exploit any potential weakness. In this work all strategies resulting from
-evolutionary algorithms are pre-trained.
-
-More information about each player can be obtained in the documentation for
-\cite{axelrodproject} and a detailed description of the performance
-of these strategies in IPD tournaments is described in~\cite{Harper2017}.
-
-All of the training code is archived at \cite{marc_harper_2017_824264}. This
-software is (similarly to the Axelrod library) available on
-github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
-with documentation to
-train new strategies easily. Training
-typically takes less than 100 generations and can be completed within several
-hours on commodity hardware.
-
-There are three further strategies trained specifically for this study; Trained
-FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}), using the notation common in the literature where
-\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
-\(A_2\) as well as arrows corresponding to changes of state.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
-	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
-	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
-	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
-	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};
-
-	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
-	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};
-
-	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
-	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
-	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};
-
-	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
-	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
-	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};
-
-	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
-	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
-    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);
-
-    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
-    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);
-
-    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
-    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);
-
-    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
-    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);
-
-    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
-    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);
-
-    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
-    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);
-
-    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
-    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);
-
-    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
-    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);
-
-    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
-    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);
-
-    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
-    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);
-
-    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
-    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);
-
-    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
-    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);
-
-    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
-    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);
-
-    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
-    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);
-
-    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
-    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);
-
-    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
-    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);
-
-    \end{tikzpicture}
-    }
-    \caption{TF1: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 4.}
-    \label{fig:tf1}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};
-
-	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
-    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
-    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
-    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
-    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
-    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
-    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};
-
-    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
-    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
-    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
-    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
-    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
-    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
-    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};
-
-    \coordinate[below of=0] (s);
-
-    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);
-
-    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
-    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);
-
-    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
-    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);
-
-    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
-    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);
-
-    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
-    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/D$} (1);
-
-    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
-    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);
-
-    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
-    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);
-
-    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
-    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);
-
-    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
-    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);
-
-    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
-    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);
-
-    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
-    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);
-
-    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
-    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);
-
-    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
-    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);
-
-    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
-    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);
-
-    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
-    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);
-
-    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
-    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);
-
-    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
-    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);
-
-    \end{tikzpicture}
-    }
-    \caption{TF2: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 16.}
-    \label{fig:tf2}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];
-
-    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
-    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
-    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$}; 
-    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
-    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};  
-    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
-    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
-    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-
-    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
-    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
-    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
-    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
-    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);
-
-    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
-    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
-    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);
-
-    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);
-
-    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
-    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
-    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
-    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
-    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
-    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
-    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
-    \end{tikzpicture}
-    \caption{TF3: an 8 state finite state machine.}
-    \label{fig:tf3}
-\end{figure}
-
-As opposed to the previously described strategies, these strategies were trained
-with the objective function of \textit{mean fixation probabilities for Moran
-processes} starting at initial population states consisting of \(N/2\)
-individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the Axelrod library:
-
-\begin{itemize}
-	\item TF1 \(N=12\), 0\% noise.
-	\item TF2 \(N=10\), 0\% noise.
-	\item TF3 \(N=8\), 1\% noise.
-\end{itemize}
-
-The trained algorithms
-were run for fewer than 50 generations. Training data for this is available at
-\cite{data}.
-
-TF1 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
-achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
-very similar to a strategy known as ``Collective Strategy'', which has a
-handshake of CD and cooperates with opponents that matched the handshake
-until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
-Collective Strategy was specifically designed for evolutionary processes.
-
-TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
-Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
-can be rescued after a failed handshake by a complex sequence of plays
-which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
-GTFT, and a few others with low probability. TF2 defects against all other
-players in the study, barring
-unusual cases arising from particular randomizations. Fig~\ref{fig:tf2} shows
-all 16 states of the strategy (states 6 and 7 are not reachable).
-
-TF3 cooperates and defects with
-various cycles depending on the opponent's actions. TF3 will mutually
-cooperate with any strategy and only tolerates a few defections before
-defecting for the rest of match. It is similar to but not exactly the same as
-Fool Me Once, a strategy that cooperates until the opponent has defected twice
-(not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism. Fig~\ref{fig:tf3} shows
-all 8 states of the strategy produced by the training process (states 3 and 8
-are not reachable).
-
-For both TF1 and TF2 a handshake
-mechanism naturally emerges from the structure of the underlying finite state
-machine. This behavior is an outcome of the evolutionary process and is in no
-way hard-coded or included via an additional mechanism.
-
-\begin{table}[!hbtp]
-    \centering
-        \scalebox{0.7}{
-            \begin{tabular}{lrrrrrrrrrrrrrrrr}
-            \toprule
-            Memory Depth &   0   &   1   &   2   &   3   &   4   &   5   &   6   &   9   &   10  &   11  &   12  &   16  &   20  &   40  &   200 &  \(\infty\)   \\
-            \midrule
-            Count &     3 &    29 &    12 &     8 &     2 &     6 &     1 &     1 &     5 &     1 &     1 &     2 &     2 &     2 &     1 &    88 \\
-            \bottomrule
-            \end{tabular}
-        }
-        \caption{Memory depths}
-        \label{tbl:memory_depth_count}
-\end{table}
-
-\subsection*{Data collection}
-
-Each strategy pair is run for 1000 repetitions of the Moran process to fixation
-with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
-1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
-computed for each combination of starting distribution and value of \(N\).  The
-Axelrod library can carry out exact simulations of the Moran process. Since some
-of the strategies have a high computational cost or are stochastic, samples are
-taken from a large number of 200 turn match outcomes for the pairs of players
-for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
-matches is used). This approach was verified to agree with unsampled
-calculations to a high degree of accuracy in specific cases.  This is described
-in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.
-
-\begin{algorithm}[!hbtp]
-        \caption{Data Collection}
-        \label{alg:data_collection}
-          \begin{algorithmic}[1]
-            \FOR{player\_one \textbf{in} players\_list}
-              \FOR{player\_two \textbf{in} (players\_list - player\_one)}
-                \STATE pair $\gets$ (player\_one, player\_two)
-                \FOR{starting\_population\_distributions \textbf{in} [$(1, N-1), (\frac{N}{2}, \frac{N}{2}), (N-1, 1)]$}
-                \WHILE {repetitions $\leq 1000$}
-                \STATE \textbf{simulate} moran process (pair, starting distribution)
-                \ENDWHILE
-                \STATE\textbf{yield} fixation probabilities
-                \ENDFOR
-              \ENDFOR
-            \ENDFOR
-          \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[!hbtp]
-        \caption{Moran process}
-        \label{alg:moran_process}
-          \begin{algorithmic}[1]
-          \STATE initial population $\gets$ (pair, starting distribution) \
-          \STATE population $\gets$ initial population
-
-            \WHILE {population not uniform}
-              \FOR{player in population}
-              \FOR{opponent in (population - player)}
-                \STATE match $\gets$ (player, opponent) 
-                \STATE results $\gets$ stochastic\_cache (200 round match)
-                \ENDFOR
-              \ENDFOR
-              \STATE population $\gets$ sorted(results)
-              \STATE parent $\gets$ selected randomly in proportion to its total match payoffs
-              \STATE offspring $\gets$ parent
-              \STATE kill off $\gets$ uniformly random player from population
-              \STATE population $\gets$ offspring replaces kill off
-            \ENDWHILE
-          \end{algorithmic}
-\end{algorithm}
-
-The next section will further validate the methodology by comparing
-simulated results to analytical results in a few selected cases. The main
-results of this
-manuscript are presented in which will
-present a detailed analysis of all the data generated. Finally,
-a discussion and conclusion will offer future avenues for the work
-presented here.
-
-\section*{Results}
-
-\subsection*{Validation}
-
-As described in \cite{Nowak} consider the payoff matrix:
-
-\begin{equation}\label{equ:payoff_matrix}
-    M = \begin{pmatrix}
-        a, b\\
-        c, d
-        \end{pmatrix}
-\end{equation}
-
-The expected payoffs of \(i\) players of the first type in a population with \(N
-- i\) players of the second type are given by:
-
-\begin{equation}\label{equ:expected_payoff_one}
-    f_i = \frac{a(i - 1) + b(N - i)}{N - 1}
-\end{equation}
-
-\begin{equation}\label{equ:expected_payoff_two}
-    g_i = \frac{ci + d(N - i - 1)}{N - 1}
-\end{equation}
-
-The transitions within the birth death process that underpins the Moran process
-are then given by:
-
-\begin{align}
-    p_{i, i+1}&= \frac{if_i}{if_i+(N-i)g_i}\frac{N-i}{N}\label{equ:p_up}\\
-    p_{i, i-1}&= \frac{(N-i)g_i}{if_i+(N-i)g_i}\frac{i}{N}\label{equ:p_down}\\
-    p_{ii} &= 1 - p_{i, i+1} - p_{i, i-1}\label{equ:p_stay}
-\end{align}
-
-Using this the fixation probability
-of the first strategy in a population of \(i\) individuals of the first type
-and \(N-i\) individuals of the second, is given by \cite{Nowak2017}:
-
-\begin{equation}\label{equ:fixation_probability}
-x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}
-      \prod_{k=1}^{j}\gamma_j}
-\end{equation}
-
-where:
-
-\[
-\gamma_j = \frac{p_{j, j-1}}{p_{j, j+1}}
-\]
-
-A neutral strategy will have fixation probability $x_i = i/N$.
-
-Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
-confidence interval computed using an asymptotic normal approximation is also
-included \cite{brown2001interval}).
-The points represent the simulated
-values and the line shows the theoretical value. Note that these are
-deterministic strategies and show a good match between the expected value
-of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
-values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
-fact that the theoretic and simulated values are a good match.
-
-Fig~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
-good match (confirmed with a \(t\)-test in
-Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
-a given interaction between two IPD strategies can be summarised with a set of
-utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
-strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
-opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
-and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
-given pair and can be quite a complex endeavour for stochastic strategies with
-long memory: this is not necessary for the purposes of this work.  All data
-generated for this validation exercise can be found at~\cite{data}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
-    \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textit{deterministic} strategies: Alternator and
-         Cooperator. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.89942 &                0.89942 &                0.89942 \\
-          4 &          0.16344 &                0.74768 &                0.85877 \\
-          6 &          0.65406 &                0.84051 &                0.51992 \\
-          8 &          0.92617 &                0.45748 &                0.38604 \\
-         10 &          0.03505 &                0.37115 &                0.60635 \\
-         12 &          0.96697 &                0.20790 &                0.18124 \\
-         14 &          0.08126 &                0.63771 &                0.76246 \\
-         16 &          0.59434 &                0.07697 &                0.42520 \\
-         18 &          0.05339 &                0.47126 &                0.94814 \\
-         20 &          0.30805 &                0.79795 &                0.82381 \\
-        \bottomrule
-        \end{tabular}
-
-    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{deterministic} strategies: Alternator and
-    Cooperator.}
-    \label{tab:comparison_deterministic}
-\end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
-    \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textit{stochastic} strategies:
-             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_stochastic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.05372 &                0.05372 &                0.05372 \\
-          4 &          0.34188 &                0.00940 &                0.00005 \\
-          6 &          0.16510 &                0.00000 &                0.00000 \\
-          8 &          0.03451 &                0.00000 &                0.00000 \\
-         10 &          0.00543 &                0.00000 &                0.00000 \\
-         12 &          0.19646 &                0.00000 &                0.00000 \\
-         14 &          0.00814 &                0.00000 &                0.00000 \\
-         16 &          0.01038 &                0.00000 &                0.00000 \\
-         18 &          0.39556 &                0.00000 &                0.00000 \\
-         20 &          0.00030 &                0.00000 &                0.00000 \\
-        \bottomrule
-        \end{tabular}
-    \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{stochastic} strategies: Calculator and
-    Arrogant Q Learner.}
-    \label{tab:comparison_stochastic}
-\end{table}
-
-\subsection*{Empirical results}
-
-This section outlines the data analysis carried out, all data for this study is
-available at~\cite{data}.
-
-\begin{itemize}
-    \item First the specific case of
-        \(N=2\) is considered.
-    \item The effect of
-        population size on the ability of a strategy to invade another
-        population is investigated. This will highlight how complex strategies with long
-        memories outperform simpler strategies.
-    \item Then a similar investigation of the
-        ability to defend against an invasion is given.
-    \item Finally the relationship
-        between performance for differing population sizes as well as
-        taking a close look at zero determinant strategies \cite{Press2012} is
-        analysed.
-\end{itemize}
-
-\subsubsection*{The special case of \(N=2\)}
-
-When $N=2$ the fixation probabilities of the Moran process are effectively measures
-of the distribution of  relative
-mean payoffs over all possible matches between two players. The strategy
-that scores higher than the other more often will fixate more often. For \(N=2\)
-the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in the following sections.
-The top 16 (10\%) strategies are
-shown in
-
-Table~\ref{tbl:summary_top_2} and figures showing the performance of all
-strategies are available in the appendix.
-The top five ranking strategies are:
-
-\begin{enumerate}
-    \item The top strategy is the Collective Strategy (CS) which has a simple
-        handshake mechanism described above.
-    \item Defector: it always defects. Since it has no interactions with other
-        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
-    \item Aggravater, which plays like Grudger (responding to any
-        defections with unconditional defections throughout) however starts by
-        playing 3 defections.
-    \item Predator, a finite state machine described in \cite{Ashlock2006}.
-    \item Handshake, a slightly less aggressive version of the Collective
-        Strategy \cite{Robson1990}. As long as the initial sequence is played
-        then it cooperates. Thus it will do well in a population consisting of
-        many members of itself just as the Collective Strategy does. The
-        difference is that CS will defect after the handshake if the opponent
-        defects while Handshake will not.
-\end{enumerate}
-
-It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
-for which a zero determinant strategy does appear in the top 10\% ranking
-strategies: ZD-extort-4. The performance of zero determinant strategies will be
-examined more closely.
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \scalebox{0.95}{
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &                  Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-        \midrule
-        1  &                      CS &  0.497 &  0.5020 &  0.6651 &   0.572 &  0.9908 &  0.993 &  0.1800 \\
-        2  &                Defector &  0.502 &  0.5020 &  0.6496 &   0.518 &  1.0000 &  1.000 &  0.1767 \\
-        3  &              Aggravater &  0.502 &  0.5020 &  0.6328 &   0.518 &  0.9790 &  0.999 &  0.1660 \\
-        4  &                Predator &  0.319 &  0.4980 &  0.6301 &   0.551 &  0.9870 &  0.993 &  0.1676 \\
-        5  &               Handshake &  0.006 &  0.4503 &  0.6240 &   0.524 &  0.9908 &  0.993 &  0.1889 \\
-        6  &                Prober 4 &  0.431 &  0.4620 &  0.6183 &   0.534 &  0.9579 &  0.958 &  0.1656 \\
-        7  &                     \textbf{TF1} &  0.430 &  0.4980 &  0.6171 &   0.544 &  0.9240 &  0.981 &  0.1345 \\
-        8  &                Prober 3 &  0.497 &  0.5011 &  0.6044 &   0.505 &  0.9930 &  0.993 &  0.1683 \\
-        9  &                     \textbf{TF2} &  0.324 &  0.5020 &  0.6026 &   0.565 &  0.8362 &  0.887 &  0.1092 \\
-        10 &                 Grudger &  0.497 &  0.5020 &  0.5996 &   0.502 &  0.9840 &  0.989 &  0.1695 \\
-        11 &       Better and Better &  0.388 &  0.3951 &  0.5980 &   0.514 &  0.9300 &  0.934 &  0.1865 \\
-        12 &                    MEM2 &  0.497 &  0.5001 &  0.5942 &   0.502 &  0.9840 &  0.987 &  0.1656 \\
-        13 &  Meta Hunter Aggressive &  0.247 &  0.2943 &  0.5933 &   0.517 &  0.9498 &  0.981 &  0.2013 \\
-        14 &                     \textbf{TF3} &  0.344 &  0.4971 &  0.5927 &   0.502 &  0.9790 &  0.982 &  0.1617 \\
-        15 &            Fool Me Once &  0.494 &  0.4980 &  0.5892 &   0.502 &  0.9790 &  0.982 &  0.1625 \\
-        16 &             ZD-Extort-4 &  0.497 &  0.5020 &  0.5867 &   0.584 &  0.6900 &  0.695 &  0.0724 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
-    \label{tbl:summary_top_2}
-\end{table}
-
-As will be demonstrated the results for
-\(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that zero determinant strategies should be
-effective for larger population sizes, but these analyses consider stationary
-behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
-The stationarity assumption allows for a deterministic payoff matrix
-leading to the conclusions about zero determinant strategies in the space
-of memory-one strategies that do not generalize to this context.
-
-% In the next sections close attention to
-% strategies who are strong invaders/resistors is given.
-
-\subsubsection*{Strong Invaders}
-
-In this section the focus is on the ability of a mutant strategy to invade: the
-probability of one individual of a given type successfully fixating in a
-population of \(N - 1\) other individuals, denoted by \(x_1\).
-
-The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
-figures showing the performance of all strategies is available in the
-appendix.
-
-\begin{table}[!hbtp]
-    \centering
-    \tiny
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
-            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
-            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
-            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
-            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
-            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
-            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
-            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
-            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
-            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
-            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
-            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
-            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
-            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
-            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
-            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
-            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
-            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
-            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
-            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
-            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
-            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
-            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
-            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
-            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
-            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
-            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
-            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
-            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
-            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
-            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
-            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
-            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
-            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
-            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
-            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
-            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
-            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
-            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
-            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
-            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
-            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
-            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
-            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_invade}
-\end{table}
-
-It can be seen that apart from CS, none of the strategies for \(N=2\)
-of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
-top performing strategies are:
-
-\begin{itemize}
-    \item Grudger (which only performs well for \(N=3\)), starts by cooperating
-        but will defect if at any point the opponent has defected.
-    \item MEM2, an infinite memory strategy that switches between TFT, TF2T, and
-        Defector \cite{Li2014}.
-    \item TF3, the finite state machine trained specifically for Moran processes
-        described.
-    \item Prober 4, a strategy which starts with a specific 20 move sequence of
-        cooperations and defections \cite{Prison1998}. This initial sequence serves
-        as approximate handshake.
-    \item  PSO Gambler and Evolved Lookerup 2 2 2: strategies that make use
-        of a lookup table mapping the first 2 moves of the opponent as well as
-        the last 2 moves of both players to an action.  PSO gambler is a
-        stochastic version of  Lookerup which maps those states to probabilities
-       of cooperating. Lookerup was described in \cite{Knight2016}.
-    \item The Evolved ANN strategies are neural networks that map a number of
-	    attributes (first move, number of cooperations, last move, etc.) to
-	    an action. Both of these have been trained using an evolutionary
-	    algorithm.
-    \item Evolved FSM 16 is a 16 state finite state machine trained to
-        perform well in tournaments.
-\end{itemize}
-
-Only one of the above strategies is stochastic although close inspection of the
-source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin Evolved Looker Up.
-PSO Gambler Mem1 is a stochastic memory one strategy that has been trained to
-maximise its utility and does perform well.
-Apart from TF3, the finite state machines trained specifically for
-Moran processes do not appear in the top 5, while strategies trained for
-tournaments do. This is due to the nature of invasion: most of the opponents
-will initially be different strategies. The next section will consider the
-converse situation.
-
-\subsubsection*{Strong resistors}
-
-In addition to identifying good invaders, strategies resistant to invasion by
-other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy.
-
-Table~\ref{tbl:top_resist} shows the top strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
-for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies previously discussed perform well for high \(N\).
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
-            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
-            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
-            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
-            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
-            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
-            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
-            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
-            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
-            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
-            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
-            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
-            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
-            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
-            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
-            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
-            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
-            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
-            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
-            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
-            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
-            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
-            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
-            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
-            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
-            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
-            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
-            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
-            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
-            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
-            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
-        \midrule
-        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
-        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
-        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
-        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
-        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
-        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
-        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
-        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
-        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
-        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
-        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
-        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
-        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
-        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
-        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
-        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
-        \bottomrule
-        \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_resist}
-\end{table}
-
-Interestingly none of these strategies are stochastic: this is explained by the
-value of not provoking typically cooperative opponent strategies with
-speculative defections. This includes opponents using the same strategy.  Acting
-stochastically increases the chance of reducing the score of individuals of the
-same type in a Moran process.  However it is possible to design a strategy with
-a stochastic or error-correcting handshake that is an excellent resistor even in
-noisy environments \cite{Lee2015}.
-
-There are only two new strategies that appear in the top ranks for
-\(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
-resistors. They all have handshakes, and whilst the handshakes of CS and
-Handshake (which ranks highly for the smaller values of \(N\)) were
-programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
-process without any priming.
-
-As described previously the strategies trained with
-the payoff maximizing objective are among the best invaders in the library
-however they are not as resistant to invasion as the strategies trained using a
-Moran objective function. These strategies include trained finite state machine
-strategies, but they do not appear to have handshaking mechanisms. Therefore it
-is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
-handshakes for high invasion resistance. TF3 is a better total payoff maximizer
-which makes it a better invader along with the strategies
-trained to maximize total payoff since successful fitness proportionate selection
-is necessary for invasion. Training with an objective with initial population
-mix other than $(N/2, N/2)$ may favor invasion or resistance.
-
-The payoff maximizing strategies typically will not defect before the opponent's
-first defection, possibly because the training strategy collection contains some
-strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
-for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically for handshaking strategies
-it is advantageous to defect (as a signal)
-in order to achieve mutual cooperation with opponents using the same strategy
-but not with other opponents. Nevertheless an evolutionary process is able to
-tunnel through the costs and risks associated with early defections to find more
-optimal solutions, so it is not surprising in hindsight that handshaking
-strategies emerge from the evolutionary training process.
-
-A handshake requires at least one defection and there is
-selective pressure to defect as few times as possible to achieve the
-self-recognition mechanism. It is also unwise to defect on the first move as
-some strategies additionally retaliate in response to first round defections. So the
-handshakes used by TF1, TF2, and CS are in some sense optimal.
-
-It is evident through
-the work presented that performance of strategies not only depends
-on the initial population distribution but also that there seems to be a
-difference depending on whether or not \(N>2\). This will be explored further in
-the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also
-considering
-\(x_{N/2}\).
-
-\subsubsection*{The effect of population size}
-
-Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
-and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
-strategies:
-
-\begin{itemize}
-    \item The strategies that ranked highly for \(N=2\);
-    \item The strategies that ranked highly for \(N=14\);
-    \item The zero determinant strategies.
-\end{itemize}
-
-The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
-expected since, as described previously these strategies
-were trained in an initial population of \((N/2, N/2)\) individuals.
-
-For all starting populations
-\(i\in\{1, N/2, N-1\}\) the ranks of strategies are relatively stable across the
-different values of \(N>2\) however for \(N=2\) there is a distinct difference.
-This highlights that there is little that can be inferred about the evolutionary
-performance of a strategy in a large population from its performance in a small
-population. This is confirmed by the performance of the zero determinant strategies: while
-some do rank relatively highly for \(N=2\) (ZD-Extort-4 has rank 16) this rank
-does not translate to larger populations.
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                         Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                           CS &    1 &    1 &    2 &   11 &    9 &   11 &   13 &   21 &   16 &   22 &   17 &   25 &   23 \\
-                     Defector &    2 &   43 &   80 &   91 &   89 &   87 &   87 &  103 &   97 &  105 &   94 &  103 &  101 \\
-                   Aggravater &    3 &   50 &   89 &   99 &  102 &  103 &  108 &  113 &  114 &  115 &  115 &  116 &  117 \\
-                     Predator &    4 &    8 &   24 &   35 &   28 &   33 &   31 &   43 &   36 &   43 &   34 &   45 &   35 \\
-                    Handshake &    5 &   17 &   40 &   46 &   43 &   46 &   46 &   49 &   48 &   49 &   47 &   50 &   49 \\
-        \midrule
-               Evolved FSM 16 &   31 &   11 &    6 &    2 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-            PSO Gambler 2\_2\_2 &   29 &   14 &   10 &    6 &    4 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-         EvolvedLookerUp2\_2\_2 &   33 &   18 &   11 &    9 &   10 &    6 &    6 &    5 &    3 &    5 &    3 &    3 &    3 \\
-                  Evolved ANN &   20 &   10 &    8 &    7 &    8 &    5 &    3 &    3 &    4 &    3 &    4 &    4 &    4 \\
-                Evolved ANN 5 &   21 &    9 &    7 &    8 &    7 &    4 &    5 &    4 &    5 &    4 &    5 &    5 &    5 \\
-        \midrule
-                          \textbf{TF1} &    7 &   13 &   33 &   38 &   30 &   39 &   42 &   46 &   42 &   46 &   41 &   46 &   46 \\
-                          \textbf{TF2} &    9 &   19 &   29 &   33 &   19 &   28 &   29 &   38 &   27 &   34 &   26 &   32 &   30 \\
-                          \textbf{TF3} &   14 &    4 &    5 &    5 &    6 &    9 &   11 &   11 &   12 &   14 &   13 &   13 &   16 \\
-        \midrule
-                  ZD-Extort-4 &   16 &   81 &  107 &  120 &  135 &  136 &  142 &  140 &  142 &  142 &  144 &  144 &  145 \\
-               ZD-Extort-2 v2 &   41 &  105 &  126 &  140 &  152 &  152 &  153 &  152 &  153 &  153 &  153 &  152 &  153 \\
-                  ZD-Extort-2 &   43 &  107 &  125 &  139 &  151 &  151 &  152 &  153 &  152 &  152 &  152 &  153 &  152 \\
-                     ZD-SET-2 &  100 &  111 &  117 &  117 &  122 &  127 &  131 &  128 &  131 &  131 &  130 &  132 &  131 \\
-                    ZD-GTFT-2 &  112 &   92 &   82 &   80 &   81 &   82 &   84 &   72 &   81 &   71 &   78 &   72 &   70 \\
-                     ZD-GEN-2 &  113 &   96 &   87 &   83 &   85 &   88 &   90 &   82 &   87 &   82 &   86 &   83 &   91 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_invade}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                   Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-               Defector &    2 &   29 &   55 &   79 &   94 &   97 &   98 &   98 &  102 &  101 &  103 &  100 &  102 \\
-             Aggravater &    3 &   42 &   71 &   97 &  101 &  106 &  107 &  111 &  113 &  113 &  116 &  115 &  115 \\
-               Predator &    4 &    2 &    3 &    3 &    3 &    4 &    4 &    4 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    4 &    5 &    5 &    5 &    5 &    5 &    6 &    6 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF1} &    7 &    3 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-                    \textbf{TF2} &   10 &    5 &    4 &    4 &    4 &    3 &    3 &    3 &    3 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    6 &    6 &    6 &    6 &    6 &    6 &    5 &    5 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   13 &    9 &   10 &   11 &   11 &   11 &   13 &   14 &   13 &   13 &   13 &   13 &   13 \\
-        \midrule
-            ZD-Extort-4 &   19 &   68 &   98 &  106 &  108 &  114 &  115 &  115 &  118 &  118 &  117 &  118 &  117 \\
-         ZD-Extort-2 v2 &   49 &   98 &  111 &  121 &  123 &  124 &  124 &  130 &  130 &  132 &  134 &  132 &  134 \\
-            ZD-Extort-2 &   50 &   97 &  112 &  123 &  124 &  125 &  123 &  126 &  131 &  131 &  132 &  133 &  133 \\
-               ZD-SET-2 &  108 &  105 &  104 &  104 &  103 &  103 &  100 &  100 &  101 &   99 &   98 &   98 &   98 \\
-              ZD-GTFT-2 &  112 &   95 &   88 &   84 &   75 &   72 &   71 &   73 &   71 &   71 &   67 &   68 &   68 \\
-               ZD-GEN-2 &  114 &   96 &   89 &   86 &   77 &   75 &   72 &   74 &   72 &   72 &   68 &   69 &   69 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_resist}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-        \begin{tabular}{lrrrrrrr}
-        \toprule
-                   Size &      2 &      4 &      6 &      8 &     10 &     12 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    2 \\
-               Defector &    2 &   78 &   99 &  106 &  110 &  113 &  120 \\
-             Aggravater &    3 &   91 &  105 &  111 &  122 &  125 &  128 \\
-               Predator &    4 &    2 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    6 &    5 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF2} &    9 &    4 &    3 &    2 &    2 &    2 &    1 \\
-                    \textbf{TF1} &    7 &    3 &    2 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    5 &    6 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   14 &    8 &    8 &    8 &    8 &    8 &    8 \\
-        \midrule
-            ZD-Extort-4 &   16 &  102 &  117 &  129 &  141 &  143 &  145 \\
-         ZD-Extort-2 v2 &   41 &  118 &  135 &  151 &  152 &  152 &  153 \\
-            ZD-Extort-2 &   43 &  117 &  136 &  149 &  151 &  151 &  152 \\
-               ZD-SET-2 &  100 &  110 &  110 &  108 &  106 &  106 &  108 \\
-              ZD-GTFT-2 &  112 &   82 &   80 &   77 &   75 &   75 &   74 \\
-               ZD-GEN-2 &  113 &   85 &   81 &   82 &   79 &   77 &   76 \\
-        \bottomrule
-        \end{tabular}
-    \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_coexist}
-\end{table}
-
-Fig~\ref{fig:correlation_coefficients} shows the correlation coefficients
-of the ranks of strategies in differing population size. How well a strategy
-performs in any Moran process for \(N>2\) has
-little to do with the performance for \(N=2\). This illustrates why the strong
-performance of zero determinant strategies predicted in \cite{Press2012} does
-not extend to larger populations. This was discussed theoretically in
-\cite{Adami2013} and observed empirically in these simulations.
-
-\begin{figure}[!htbp]
-    \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
-        \caption{Rank based on \(x_1\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
-        \caption{Rank based on \(x_{N - 1}\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
-        \caption{Rank based on \(x_{N/2}\)}
-    \end{subfigure}
-    \caption{Heatmap of correlation coefficients of rankings by population size.}
-    \label{fig:correlation_coefficients}
-\end{figure}
-
-\section*{Discussion}
-
-Training strategies to excel
-at the Moran process leads to the evolution of cooperation, but only with like
-individuals in the case of TF1 and TF2. This may have significant implications
-for various biological and social phenomena such as
-human social interactions, particularly the evolution of ingroup/outgroup mechanisms
-and other sometimes costly rituals that reinforce group behavior.
-
-While TF1 and TF2 are competent invaders, the best invaders
-in the study do not appear to employ strict handshakes, and are generally
-cooperative strategies. TF3, which does not use a handshake, is a better invader
-than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
-of the same kind of training processes and is a better combined invader-resistor
-than the invaders that were trained previously to maximize payout.
-
-The strategies trained to maximize payoff in head-to-head matches are generally
-cooperative and are effective invaders.
-Combined with the fact that handshaking strategies are stronger resistors,
-this suggests that while maximizing individual payoff can lead to the evolution
-of cooperation, these strategies are not the most evolutionarily stable
-in the long run. A strategy with a handshaking mechanism is still capable of
-invading and is more resistant to subsequent invasions. Moreover, the
-best resistor of the payoff maximally trained strategies (Evolved Looker Up
-1\_1\_1),
-which always defects if the opponent defects in the first round, is effectively
-employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
-which emerged from training memory one strategies for the Moran process,
-also effectively employs a handshake of always cooperating, as it defects
-for the remainder of the match if the opponent ever defects.
-
-The insights that payoff maximizers are better invaders and that handshakers
-are better resistors suggests that a strategy
-aware of the population distribution could choose to become a handshaker at
-a critical threshold and use a strategy better for invasion when in the
-minority. Information about the population distribution was not available
-to our strategies. Previous work has showed that strategies able to retain
-memory across matches can infer the population distribution and act in such
-a manner, resulting in a strategy effective at invasion and resistance
-\cite{Lee2015}.
-
-We did not attempt other objective functions that may serve to select for both
-invasion and resistance better than training at a starting population of
-$(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
-improvement. Any handshake more sophisticated than always cooperate necessarily involves
-a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
-effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
-they need a longer or more strict handshake. But if this handshake involves
-a defection then likely the invasion ability is diminished for $N > 2$: the top
-invaders for larger $N$ are nice strategies that do not defect before their
-opponents. This is because good invaders need to maximize match payoff to benefit
-from fitness proportionate selection,
-and so in the absence of a handshake mechanism, knowledge of the population
-distribution, or some identifying label on the opponent,
-a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping dramatically in rank
-as the population size increases.
-
-We did, however, attempt to evolve CS using finite state machines and lookup table
-based players,
-which resulted in some very similar strategies. In particular we evolved a
-lookup strategy that had a handshake of DC and played TFT with other players
-after a correct handshake while defecting otherwise, which is quite close in
-function to CS (full grudging is not possible with a lookup table of limited
-depth).
-
-Finally we note that it may be possible to achieve similar results with smaller
-capacity finite state machine players.
-
-\section*{Conclusion}
-
-A detailed empirical analysis of 164 strategies of the IPD within a pairwise
-Moran process has been carried out. All \(\binom{164}{2}=13,366\) possible
-ordered pairs of strategies have been placed in a Moran process with different
-starting values allowing each strategy to attempt to invade the other.
-This is the largest such experiment carried out and has led to many insights.
-
-When studying evolutionary processes it is vital to consider \(N>2\) since
-results for \(N=2\) cannot be used to extrapolate performance in larger
-populations. This was shown both observationally
- but also by
-considering the correlation of the ranks in different population sizes.
-
-Memory one strategies do not perform as well as longer memory strategies in general
-in this study. Several longer memory strategies were high performers for invasion,
-particularly the strategies which have been trained using a number of reinforcement
-learning algorithms. Interestingly they have been trained to perform well in
-tournaments and not Moran processes specifically. In some cases these strategies
-utilize all the history of play (the neural network strategies and the lookup
-table strategies, the latter using the first round and some number of trailing rounds).
-
-There are no memory one strategies in the top 5 performing strategies
-for \(N>3\). Training memory-one strategies specifically for the Moran process
-typically led to Grudger / Grim, a memory-one strategy with
-four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
-The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
-training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
-For comparison, training for maximum score difference between the player and the
-opponent resulted in a strategy nearly the same as Grudger, with four-vector
-$(0.9459, 0, 0, 0)$ (not included in the study).
-
-One of the major findings discussed, is
-the ability of strategies with a handshake mechanism to resist invasion. This
-was not only revealed for CS (a human designed strategy) but also for
-two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
-process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. Fig~\ref{fig:cooperation_rates} shows the cooperation
-rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study.
-This corresponds to the fraction of cooperation played by that strategy observed
-in a given round (out of the first 15) where each matchup is repeated 10000 times to
-obtain the mean.
-
-While TF3
-does not have a strict handshake mechanism it is clear that all these strategies
-start a match by cooperating. It is then evident that TF3 cooperates more than
-the other strategies thus explaining the difference in performance. It is also
-clear that CS only cooperates with itself and Handshake: it is a very aggressive
-strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
-        \caption{TF1}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
-        \caption{TF2}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
-        \caption{TF3}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
-        \caption{CS}
-    \end{subfigure}
-    \caption{Cooperation rate per round (over 10000 repetitions). Rows
-        correspond to all the strategies considered in this work (ordered
-    alphabetically by name). Columns correspond to round of an IPD match.}
-    \label{fig:cooperation_rates}
-\end{figure}
-
-These findings are important for the ongoing understanding of
-population dynamics and offer evidence for some of the shortcomings of low
-memory which has started to be recognised by the community \cite{Hilbe2017}.
-
-All source code for this work has been written in a sustainable manner: it is
-open source, under version control and tested which ensures that all results can
-be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
-the processed data has also been properly archived and can be found
-at \cite{data}.
-
-There are many opportunities to build on this work. In particular, an analysis
-of the effect of noise should offer insights regarding the stability of the findings,
-particularly for the handshaking strategies. They may be less dominant for
-larger amounts of noise since the handshaking mechanisms may become brittle.
-There are many other variations to explore including populations with more
-than one type, spatial structure, and mutation.
-
-One final point to recognise: the large set of strategies used here does not in
-itself constitute an authoritative set. Whilst it is not only large but also very
-diverse, the results (and rankings) presented might change given a different set
-of strategies. A further piece of work could look at subgroups of strategies and
-how they fair against other subgroups. Note that because of the open nature of
-the work here (not only is the source code archived but so is the data) this and
-any other further analysis is possible to carry out.
-
-\section*{Acknowledgements}
-
-This work was performed using the computational facilities of the Advanced
-Research Computing @ Cardiff (ARCCA) Division, Cardiff University.
-
-A variety of software libraries have been used in this work:
-
-\begin{itemize}
-    \item The Axelrod library (IPD strategies and Moran processes)
-        \cite{axelrodproject}.
-    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
-    \item The pandas and numpy libraries (data manipulation)
-        \cite{mckinney2010data, walt2011numpy}.
-\end{itemize}
-
-\nolinenumbers
-
-\begin{thebibliography}{10}
-
-\bibitem{Adami2013}
-Christoph Adami and Arend Hintze.
-\newblock {Evolutionary instability of zero-determinant strategies demonstrates
-  that winning is not everything.}
-\newblock {\em Nature communications}, 4(1):2193, 2013.
-
-\bibitem{adami2016evolutionary}
-Christoph Adami, Jory Schossau, and Arend Hintze.
-\newblock {Evolutionary game theory using agent-based methods}.
-\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
-
-\bibitem{affenzeller2009genetic}
-Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
-\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
-  Practical Applications}.
-\newblock Numerical Insights. CRC Press, 2009.
-
-\bibitem{Nowak2017}
-Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
-  Shing-Tung Yau, and Martin~A Nowak.
-\newblock {Evolutionary dynamics on any population structure}.
-\newblock 544:227--230, March 2017.
-
-\bibitem{Ashlock2015}
-Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
-\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
-  Agents}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 7(1):53--65, 2015.
-
-\bibitem{Ashlock2008}
-Daniel Ashlock and Eun-Youn Kim.
-\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
-  dilemma strategies}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
-  2008.
-
-\bibitem{Ashlock2006}
-Wendy Ashlock and Daniel Ashlock.
-\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
-  with different population sizes}.
-\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
-  pages 297--304. IEEE, 2006.
-
-\bibitem{Ashlock2014}
-Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
-\newblock {The evolution of exploitation}.
-\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
-  Symposium on}, pages 135--142. IEEE, 2014.
-
-\bibitem{Axelrod1980a}
-Robert Axelrod.
-\newblock {Effective choice in the prisoner's dilemma}.
-\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
-
-\bibitem{Axelrod1980b}
-Robert Axelrod.
-\newblock {More Effective Choice in the Prisoner's Dilemma}.
-\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.
-
-\bibitem{Axelrod1984}
-Robert Axelrod.
-\newblock {\em The Evolution of Cooperation}.
-\newblock Basic books. Basic Books, 1984.
-
-\bibitem{Baek2016}
-{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
-  A}.
-\newblock {Comparing reactive and memory- one strategies of direct
-  reciprocity}.
-\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
-
-\bibitem{Banks1990}
-Jeffrey~S Banks and Rangarajan~K Sundaram.
-\newblock {Repeated games, finite automata, and complexity}.
-\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
-
-\bibitem{Beaufils1997}
-Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
-\newblock {Our meeting with gradual, a good strategy for the iterated
-  prisoner’s dilemma}.
-\newblock In {\em Proceedings of the Fifth International Workshop on the
-  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.
-
-\bibitem{brown2001interval}
-Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
-\newblock Interval estimation for a binomial proportion.
-\newblock {\em Statistical science}, pages 101--117, 2001.
-
-\bibitem{Andre2013}
-Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
-\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
-\newblock pages 1--6, 2013.
-
-\bibitem{Eckhart2015}
-Arnold Eckhart.
-\newblock Coopsim v0.9.9 beta 6.
-\newblock https://github.com/jecki/CoopSim/, 2015.
-
-\bibitem{Flood1958}
-Merrill~M Flood.
-\newblock {Some Experimental Games}, 1958.
-
-\bibitem{Frean1994}
-Marcus~R Frean.
-\newblock {The prisoner's dilemma without synchrony}.
-\newblock {\em Proceedings of the Royal Society of London B: Biological
-  Sciences}, 257(1348):75--79, 1994.
-
-\bibitem{Gaudesi2016}
-Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
-\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
-  dilemma tournaments}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 8(3):288--300, 2016.
-
-\bibitem{marc_harper_2017_824264}
-Marc Harper, Vince Knight, and Martin Jones.
-\newblock Axelrod-python/axelrod-dojo: v0.0.1.
-\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
-
-\bibitem{Harper2017}
-Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
-  Glynatsi, and Owen Campbell.
-\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
-  Prisoner's Dilemma}.
-\newblock arXiv:1707.06307, 2017.
-
-\bibitem{Hilbe2017}
-Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
-  Nowak.
-\newblock {Memory-n strategies of direct reciprocity}.
-\newblock {\em Proceedings of the National Academy of Sciences}, page
-  201621239, 2017.
-
-\bibitem{Hilbe2013}
-Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
-\newblock {Adaptive dynamics of extortion and compliance}.
-\newblock {\em PloS one}, 8(11):e77886, 2013.
-
-\bibitem{hunter2007matplotlib}
-John~D Hunter.
-\newblock {Matplotlib: A 2D graphics environment}.
-\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
-
-\bibitem{kendall2007iterated}
-Graham Kendall, Xin Yao, and Siang~Y Chong.
-\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
-\newblock Advances in natural computation. World Scientific, 2007.
-
-\bibitem{Knight2016}
-Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
-  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
-  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
-  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
-  Timothy Standen, Luis Visintini, and Karl Molden.
-\newblock {An Open Framework for the Reproducible Study of the Iterated
-  Prisoner ' s Dilemma}.
-\newblock 2016.
-
-\bibitem{data}
-Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
-\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
-  Self-Recognition Mechanisms: an empirical study of the Moran process for the
-  iterated Prisoner's dilemma using reinforcement learning}.
-\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
-
-\bibitem{Kraines1989}
-David Kraines and Vivian Kraines.
-\newblock {Pavlov and the prisoner's dilemma}.
-\newblock {\em Theory and decision}, 26(1):47--79, 1989.
-
-\bibitem{Kuhn2017}
-Steven Kuhn.
-\newblock Prisoner's dilemma.
-\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
-  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
-  edition, 2017.
-
-\bibitem{Lee2015}
-Christopher Lee, Marc Harper, and Dashiell Fryer.
-\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
-\newblock {\em Plos One}, 10(3):e0120625, 2015.
-
-\bibitem{Li2011}
-Jiawei Li, Philip Hingston, and Graham Kendall.
-\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
-  Dilemma Competitions}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 3(4):348--360, 2011.
-
-\bibitem{Li2009}
-Jiawei Li and Graham Kendall.
-\newblock {A strategy with novel evolutionary features for the iterated
-  prisoner's dilemma.}
-\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
-
-\bibitem{Li2014}
-Jiawei Li and Graham Kendall.
-\newblock {The effect of memory size on the evolutionary stability of
-  strategies in iterated prisoner's dilemma}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
-  2014.
-
-\bibitem{Prison1998}
-LIFL.
-\newblock Prison.
-\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
-
-\bibitem{Mathieu2015}
-Philippe Mathieu and Jean-Paul Delahaye.
-\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
-  Abstract)}.
-\newblock {\em 14th International Conference on Autonomous Agents and
-  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
-
-\bibitem{mckinney2010data}
-Wes McKinney et~al.
-\newblock Data structures for statistical computing in python.
-\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
-  445, pages 51--56. van der Voort S, Millman J, 2010.
-
-\bibitem{Mittal2009}
-Shashi Mittal and Kalyanmoy Deb.
-\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
-  multiple conflicting objectives}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
-  2009.
-
-\bibitem{Moran1957}
-Patrick A~P Moran.
-\newblock {Random Processes in Genetics}.
-\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
-  Society}, 54(1):60--71, 1957.
-
-\bibitem{Nachbar1992}
-John~H Nachbar.
-\newblock {Evolution in the finitely repeated prisoner's dilemma}.
-\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
-  1992.
-
-\bibitem{Nowak}
-Martin~A Nowak.
-\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
-\newblock Cambridge: Harvard University Press.
-
-\bibitem{Nowak1993}
-Martin~A Nowak and Karl Sigmund.
-\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
-  the Prisoner's Dilemma game.}
-\newblock {\em Nature}, 364(6432):56--58, 1993.
-
-\bibitem{Press2012}
-William~H Press and Freeman~J Dyson.
-\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
-  evolutionary opponent.}
-\newblock {\em Proceedings of the National Academy of Sciences of the United
-  States of America}, 109(26):10409--13, 2012.
-
-\bibitem{Prlic2012}
-Andreas Prlić and James~B Procter.
-\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
-\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
-
-\bibitem{axelrodproject}
-The~Axelrod project developers.
-\newblock Axelrod: v2.9.0.
-\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
-
-\bibitem{Robson1990}
-Arthur~J Robson.
-\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
-  handshake}.
-\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
-
-\bibitem{Sandve2013}
-Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
-\newblock {Ten Simple Rules for Reproducible Computational Research}.
-\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
-
-\bibitem{Stewart2012}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  109(26):10134--10135, 2012.
-
-\bibitem{stewart2013extortion}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {From extortion to generosity, evolution in the iterated prisoner’s
-  dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  110(38):15348--15353, 2013.
-
-\bibitem{Tzafestas2000}
-Elpida Tzafestas.
-\newblock {Toward adaptive cooperative behavior}.
-\newblock {\em From Animals to animals: Proceedings of the 6th International
-  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
-  2000.
-
-\bibitem{PD2017}
-Unkwown.
-\newblock www.prisoners-dilemma.com.
-\newblock http://www.prisoners-dilemma.com/, 2017.
-
-\bibitem{Berg2015}
-Pieter Van~den Berg and Franz~J Weissing.
-\newblock {The importance of mechanisms for the evolution of cooperation}.
-\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
-  Society, 2015.
-
-\bibitem{walt2011numpy}
-St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
-\newblock {The NumPy array: a structure for efficient numerical computation}.
-\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
-
-\bibitem{West2016}
-Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
-\newblock {The prisoner’s dilemma as a cancer model}.
-\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
-
-\bibitem{Wilson2014}
-Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
-  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
-  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
-\newblock {Best Practices for Scientific Computing}.
-\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
-
-\bibitem{Axelrod1995}
-Jianzhong Wu and Robert Axelrod.
-\newblock {How to cope with noise in the iterated prisoner's dilemma}.
-\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
-
-\end{thebibliography}
-
-\appendix
-
-\section{Appendix A: List of players}\label{app:list_of_players}
-
-\footnotesize
-\begin{enumerate}
-\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
-\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
-\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
-\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
-\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
-\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
-\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
-\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
-\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
-\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980a}
-\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
-\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006}
-\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006}
-\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
-\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
-\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Banks1990, Beaufils1997, Berg2015, Li2011}
-\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
-\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
-\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
-\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
-\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Stewart2012}
-\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
-\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
-\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
-\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980a}
-\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
-\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006}
-\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
-\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
-\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980a, Tzafestas2000}
-\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
-\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
-\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
-\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
-\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
-\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
-\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
-\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
-\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
-\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
-\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
-\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
-\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
-\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
-\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a}
-\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980a}
-\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
-\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\end{enumerate}
-
-\section{Appendix B: Supplementary figures}
-
-\begin{itemize}
-    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
-for each strategy. The mean and error bars are shown against the collection of
-all opponents.
-
-    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
-\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
-the collection of all opponents.
-
-    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
-ranks of each strategy according to mean absorption probability across all
-population sizes.
-\end{itemize}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
-    \label{invasion-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
-    \label{invasion-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
-    \label{resistance-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
-    \label{resistance-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
-    \label{fig:ranks_v_size_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
-    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_coexist}
-\end{figure}
-
 \end{document}

### 2018-08-10 tf1.tex
Re rename all images.

--- 2018-04-05 plos/main.tex
@@
-% Template for PLoS
-% Version 3.4 January 2017
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
-\usepackage{algorithm,algorithmic}
-\usepackage{amsmath}
-\usepackage{authblk}
-\usepackage{booktabs}
-\usepackage{booktabs}
-\usepackage{fancyvrb}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{multicol}
-\usepackage{pdflscape}
-\usepackage{standalone}
-\usepackage{subcaption}
+\documentclass[crop,tikz]{standalone}
 \usepackage{tikz}
-\usepackage{xstring}
-
 \usetikzlibrary{calc, shapes, patterns}
-
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline
-{Evolution reinforces cooperation with the emergence of self-recognition
- mechanisms: an empirical study of strategies in the Moran process for the
- iterated prisoner's dilemma }
-% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Vincent Knight\textsuperscript{1*\Yinyang},
-Marc Harper\textsuperscript{2\Yinyang},
-Nikoleta E. Glynatsi\textsuperscript{2\ddag},
-Owen Campbell\textsuperscript{3\ddag},
-\\
-\bigskip
-\textbf{1} Cardiff University, School of Mathematics, Cardiff, UK
-\\
-\textbf{2} Google Inc., Mountain View, CA, USA
-\\
-\textbf{3} Independent Researcher, Chester, UK
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-%
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-\ddag These authors also contributed equally to this work.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* knightva@cardiff.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-    We present insights and empirical results from an extensive numerical
-    study of the evolutionary dynamics of the iterated prisoner's dilemma.
-    Fixation probabilities for Moran processes are obtained
-    for all pairs of 164 different strategies including classics such as TitForTat, zero
-    determinant strategies, and many more sophisticated strategies.
-    Players with long memories and sophisticated behaviours outperform
-    many strategies that perform well in a two player setting. Moreover we
-    introduce several strategies trained with evolutionary algorithms to
-    excel at the Moran process. These strategies are excellent invaders
-    and resistors of invasion and in some cases naturally evolve handshaking
-    mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake mechanisms.
-    This suggests that while maximizing individual payoff
-    can lead to the evolution of cooperation through invasion, the relatively
-    weak invasion resistance of payoff maximizing strategies are not as
-    evolutionarily stable as strategies employing handshake mechanisms.
-\linenumbers
-
-\section*{Introduction}
-
-The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
-used to model a variety of strategic interactions. Each player chooses
-simultaneously and independently
-between cooperation (C) or defection (D). The payoffs of
-the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
-\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one
-round game, but is commonly studied in a manner where the prior outcomes
-matter. This repeated form is called the Iterated Prisoner's
-Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
-number of strategies have been developed to take advantage of the history of
-play. Strategies referred to as zero determinant (ZD) strategies
-\cite{Press2012} can manipulate some players through extortionate mechanisms.
-
-The Moran Process \cite{Moran1957} is a model of
-evolutionary population dynamics that has been used to gain insights about the
-evolutionary stability in a number of settings.
-Several earlier
-works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
-or are limited to classes of strategies
-such as memory-one strategies that only use the previous round of play.
-
-This manuscript provides a detailed numerical analysis of agent-based simulations
-of \textbf{164} complex and adaptive strategies for the
-IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
-effort to provide software for reproducible research for the IPD\@. The library
-now contains over 186 parameterized
-strategies including classics like TitForTat and WinStayLoseShift, as well as
-recent variants such as OmegaTFT, zero determinant and other memory one
-strategies, strategies based on finite state machines, lookup tables, neural
-networks, and other machine learning based strategies, and a collection of novel
-strategies. Not all strategies have been considered for this study: excluded
-are those that make use of knowledge of the number of turns in a match
-and others that have a high
-computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 50 contributors from around the
-world, made by programmers and researchers \cite{Knight2016}. Three of the considered
-strategies are finite state machines trained specifically for Moran processes
-(described further in the Methods section).
-
-In addition to providing a large collection of strategies, the Axelrod library
-can conduct matches, tournaments and population
-dynamics with variations including noise and spatial structure.
-The strategies and simulation frameworks are
-automatically tested to an extraordinarily high degree of coverage in accordance
-with best research software practices.
-
-Using the Axelrod library and the many strategies it contains, we obtain the
-probability with which a given strategy takes over a population (referred to as
-fixation probability) for all pairs of strategies, identifying those that are
-effective invaders and those resistant to invasion, for population sizes $N=2$
-to $N=14$. Moreover we present a number (16) of strategies that were created via
-reinforcement algorithms (evolutionary and particle swarm algorithms) that are
-among the best invaders and resistors of invasion known to date, and show that
-handshaking mechanisms naturally arise from these processes as an
-invasion-resistance mechanism.
-
-In 2016, work has argued that agent-based
-simulations can provide insights in evolutionary game theory not available
-via direct mathematical analysis~\cite{adami2016evolutionary}. The results
-and insights contained in this paper would be difficult to derive analytically.
-
-In particular the following questions are addressed:
-\begin{enumerate}
-    \item What strategies are good invaders?
-    \item What strategies are good at resisting invasion?
-    \item How does the population size affect these findings?
-\end{enumerate}
-
-While the results agree with some of the published literature, it is found that:
-
-\begin{enumerate}
- \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
- \item Complex strategies can be effective, and in fact can naturally evolve
-     through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or possess a handshake mechanism.
- \item Strong invaders are generally cooperative strategies that do not defect
- first but retaliate to varying degrees of intensity against strategies that defect.
- \item Strategies evolved to maximize their total payoff can be strong invaders
- and achieve mutual cooperation with many other strategies.
-\end{enumerate}
-
-\section*{Materials and methods}
-\subsection*{The Moran Process}
-
-A Moran process is a stochastic birth death process on a finite population in which the
-population size stays constant over time. Individuals are \textit{selected}
-according to a given fitness landscape. The fitness landscape in this work is
-defined as the total utility against all other individuals in the population.
-Once selected, the individual
-is reproduced and similarly another individual is chosen to be removed from the
-population (a uniform random selection is used). This is shown diagrammatically
-in Fig~\ref{fig:moran_process}. In some settings mutation is
-also considered but without mutation (the case considered in this work) this
-process will arrive at an absorbing state where the population is entirely made
-up of players of one strategy. The probability with which a given strategy,
-starting from a single individual takes
-over a population is called the \textit{fixation probability}. A more detailed
-analytic description of this is given later. In our
-simulations offspring do not inherit any knowledge or history from parent
-replicants.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.5}{
-
-\begin{tikzpicture}[scale=.9]
-	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-
-	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-
-	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);
-
-	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-
-	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-\end{tikzpicture}
-
-}
-    \caption{A diagrammatic representation of a Moran process.}
-    \label{fig:moran_process}
-\end{figure}
-
-The Moran process was initially introduced in \cite{Moran1957}. It has since
-been used in a variety of settings including the understanding of the spread of
-cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
-emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider relatively simple strategies. A few works
-looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
-\cite{Li2014} but this is not done in the more widely used setting of the Moran
-process, rather in terms of infinite population stability. In \cite{Baek2016}
-Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies: strategies that recall
-the events of the previous round only.
-
-Of particular interest are the zero determinant strategies introduced in
-\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
-a strategy using machine learning techniques was capable of resisting invasion
-and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
-has investigated the effect of memory length on strategy performance and the
-emergence of cooperation but this is not done in a Moran process context and only
-considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
-recognised that many zero determinant strategies do not fare well against
-themselves. This is a disadvantage for the Moran process where the best
-strategies cooperate well with other players using the same strategy.
-
-This work uses pair-wise Moran processes in a similar way to matches in the many
-IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
-A population-based perspective is given which adds additional
-evolutionary components to the IPD, namely the evolutionary dynamics of invasion
-and resistance.
-
-\subsection*{Strategies considered}\label{sec:strategies}
-
-To carry out this numerical experiment, 164
-strategies, listed (with their properties) in the Appendix,
-are used from the Axelrod library. There are
-43 stochastic and
-121 deterministic strategies. Their memory depth,
-defined by the number of rounds of history used by the strategy each round, is
-shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
-strategy uses the entire history of play (whatever its length). For example, a
-strategy that utilizes a handshaking mechanism where the opponent's actions on
-the first few rounds of play determines the strategies subsequent behavior would
-have infinite memory depth.
-
-A number of these strategies have been trained with reinforcement learning
-algorithms prior to this study and not specifically for the Moran process.
-
-\begin{itemize}
-    \item Evolved ANN: a neural network based strategy;
-    \item Evolved LookerUp: a lookup table based strategy;
-    \item PSO Gambler: a stochastic version of the lookup table based strategy;
-    \item Evolved HMM: a hidden Markov model based strategy.
-\end{itemize}
-
-Apart from the PSO Gambler strategy, which was trained using a particle swarm
-optimisation algorithm, these strategies are trained with an evolutionary
-algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. They were trained to
-win IPD tournaments by maximizing their mean total payoffs against a variety
-of opponents. Variation is
-introduced via mutation and crossover of parameters, and the best performing
-strategies are carried to the next generation along with new variants. Similar
-methods appear in the literature \cite{Ashlock2006}.
-There has also been some work on strategies using an evolutionary algorithm in real time:
-in~\cite{Gaudesi2016}
-an evolutionary algorithm is used to build a model of the opponent and attempt
-to exploit any potential weakness. In this work all strategies resulting from
-evolutionary algorithms are pre-trained.
-
-More information about each player can be obtained in the documentation for
-\cite{axelrodproject} and a detailed description of the performance
-of these strategies in IPD tournaments is described in~\cite{Harper2017}.
-
-All of the training code is archived at \cite{marc_harper_2017_824264}. This
-software is (similarly to the Axelrod library) available on
-github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
-with documentation to
-train new strategies easily. Training
-typically takes less than 100 generations and can be completed within several
-hours on commodity hardware.
-
-There are three further strategies trained specifically for this study; Trained
-FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}), using the notation common in the literature where
-\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
-\(A_2\) as well as arrows corresponding to changes of state.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
     \begin{tikzpicture}
@@
     \end{tikzpicture}
-    }
-    \caption{TF1: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 4.}
-    \label{fig:tf1}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};
-
-	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
-    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
-    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
-    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
-    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
-    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
-    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};
-
-    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
-    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
-    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
-    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
-    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
-    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
-    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};
-
-    \coordinate[below of=0] (s);
-
-    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);
-
-    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
-    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);
-
-    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
-    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);
-
-    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
-    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);
-
-    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
-    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/D$} (1);
-
-    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
-    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);
-
-    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
-    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);
-
-    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
-    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);
-
-    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
-    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);
-
-    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
-    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);
-
-    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
-    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);
-
-    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
-    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);
-
-    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
-    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);
-
-    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
-    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);
-
-    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
-    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);
-
-    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
-    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);
-
-    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
-    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);
-
-    \end{tikzpicture}
-    }
-    \caption{TF2: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 16.}
-    \label{fig:tf2}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];
-
-    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
-    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
-    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$}; 
-    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
-    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};  
-    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
-    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
-    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-
-    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
-    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
-    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
-    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
-    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);
-
-    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
-    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
-    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);
-
-    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);
-
-    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
-    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
-    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
-    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
-    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
-    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
-    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
-    \end{tikzpicture}
-    \caption{TF3: an 8 state finite state machine.}
-    \label{fig:tf3}
-\end{figure}
-
-As opposed to the previously described strategies, these strategies were trained
-with the objective function of \textit{mean fixation probabilities for Moran
-processes} starting at initial population states consisting of \(N/2\)
-individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the Axelrod library:
-
-\begin{itemize}
-	\item TF1 \(N=12\), 0\% noise.
-	\item TF2 \(N=10\), 0\% noise.
-	\item TF3 \(N=8\), 1\% noise.
-\end{itemize}
-
-The trained algorithms
-were run for fewer than 50 generations. Training data for this is available at
-\cite{data}.
-
-TF1 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
-achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
-very similar to a strategy known as ``Collective Strategy'', which has a
-handshake of CD and cooperates with opponents that matched the handshake
-until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
-Collective Strategy was specifically designed for evolutionary processes.
-
-TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
-Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
-can be rescued after a failed handshake by a complex sequence of plays
-which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
-GTFT, and a few others with low probability. TF2 defects against all other
-players in the study, barring
-unusual cases arising from particular randomizations. Fig~\ref{fig:tf2} shows
-all 16 states of the strategy (states 6 and 7 are not reachable).
-
-TF3 cooperates and defects with
-various cycles depending on the opponent's actions. TF3 will mutually
-cooperate with any strategy and only tolerates a few defections before
-defecting for the rest of match. It is similar to but not exactly the same as
-Fool Me Once, a strategy that cooperates until the opponent has defected twice
-(not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism. Fig~\ref{fig:tf3} shows
-all 8 states of the strategy produced by the training process (states 3 and 8
-are not reachable).
-
-For both TF1 and TF2 a handshake
-mechanism naturally emerges from the structure of the underlying finite state
-machine. This behavior is an outcome of the evolutionary process and is in no
-way hard-coded or included via an additional mechanism.
-
-\begin{table}[!hbtp]
-    \centering
-        \scalebox{0.7}{
-            \begin{tabular}{lrrrrrrrrrrrrrrrr}
-            \toprule
-            Memory Depth &   0   &   1   &   2   &   3   &   4   &   5   &   6   &   9   &   10  &   11  &   12  &   16  &   20  &   40  &   200 &  \(\infty\)   \\
-            \midrule
-            Count &     3 &    29 &    12 &     8 &     2 &     6 &     1 &     1 &     5 &     1 &     1 &     2 &     2 &     2 &     1 &    88 \\
-            \bottomrule
-            \end{tabular}
-        }
-        \caption{Memory depths}
-        \label{tbl:memory_depth_count}
-\end{table}
-
-\subsection*{Data collection}
-
-Each strategy pair is run for 1000 repetitions of the Moran process to fixation
-with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
-1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
-computed for each combination of starting distribution and value of \(N\).  The
-Axelrod library can carry out exact simulations of the Moran process. Since some
-of the strategies have a high computational cost or are stochastic, samples are
-taken from a large number of 200 turn match outcomes for the pairs of players
-for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
-matches is used). This approach was verified to agree with unsampled
-calculations to a high degree of accuracy in specific cases.  This is described
-in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.
-
-\begin{algorithm}[!hbtp]
-        \caption{Data Collection}
-        \label{alg:data_collection}
-          \begin{algorithmic}[1]
-            \FOR{player\_one \textbf{in} players\_list}
-              \FOR{player\_two \textbf{in} (players\_list - player\_one)}
-                \STATE pair $\gets$ (player\_one, player\_two)
-                \FOR{starting\_population\_distributions \textbf{in} [$(1, N-1), (\frac{N}{2}, \frac{N}{2}), (N-1, 1)]$}
-                \WHILE {repetitions $\leq 1000$}
-                \STATE \textbf{simulate} moran process (pair, starting distribution)
-                \ENDWHILE
-                \STATE\textbf{yield} fixation probabilities
-                \ENDFOR
-              \ENDFOR
-            \ENDFOR
-          \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[!hbtp]
-        \caption{Moran process}
-        \label{alg:moran_process}
-          \begin{algorithmic}[1]
-          \STATE initial population $\gets$ (pair, starting distribution) \
-          \STATE population $\gets$ initial population
-
-            \WHILE {population not uniform}
-              \FOR{player in population}
-              \FOR{opponent in (population - player)}
-                \STATE match $\gets$ (player, opponent) 
-                \STATE results $\gets$ stochastic\_cache (200 round match)
-                \ENDFOR
-              \ENDFOR
-              \STATE population $\gets$ sorted(results)
-              \STATE parent $\gets$ selected randomly in proportion to its total match payoffs
-              \STATE offspring $\gets$ parent
-              \STATE kill off $\gets$ uniformly random player from population
-              \STATE population $\gets$ offspring replaces kill off
-            \ENDWHILE
-          \end{algorithmic}
-\end{algorithm}
-
-The next section will further validate the methodology by comparing
-simulated results to analytical results in a few selected cases. The main
-results of this
-manuscript are presented in which will
-present a detailed analysis of all the data generated. Finally,
-a discussion and conclusion will offer future avenues for the work
-presented here.
-
-\section*{Results}
-
-\subsection*{Validation}
-
-As described in \cite{Nowak} consider the payoff matrix:
-
-\begin{equation}\label{equ:payoff_matrix}
-    M = \begin{pmatrix}
-        a, b\\
-        c, d
-        \end{pmatrix}
-\end{equation}
-
-The expected payoffs of \(i\) players of the first type in a population with \(N
-- i\) players of the second type are given by:
-
-\begin{equation}\label{equ:expected_payoff_one}
-    f_i = \frac{a(i - 1) + b(N - i)}{N - 1}
-\end{equation}
-
-\begin{equation}\label{equ:expected_payoff_two}
-    g_i = \frac{ci + d(N - i - 1)}{N - 1}
-\end{equation}
-
-The transitions within the birth death process that underpins the Moran process
-are then given by:
-
-\begin{align}
-    p_{i, i+1}&= \frac{if_i}{if_i+(N-i)g_i}\frac{N-i}{N}\label{equ:p_up}\\
-    p_{i, i-1}&= \frac{(N-i)g_i}{if_i+(N-i)g_i}\frac{i}{N}\label{equ:p_down}\\
-    p_{ii} &= 1 - p_{i, i+1} - p_{i, i-1}\label{equ:p_stay}
-\end{align}
-
-Using this the fixation probability
-of the first strategy in a population of \(i\) individuals of the first type
-and \(N-i\) individuals of the second, is given by \cite{Nowak2017}:
-
-\begin{equation}\label{equ:fixation_probability}
-x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}
-      \prod_{k=1}^{j}\gamma_j}
-\end{equation}
-
-where:
-
-\[
-\gamma_j = \frac{p_{j, j-1}}{p_{j, j+1}}
-\]
-
-A neutral strategy will have fixation probability $x_i = i/N$.
-
-Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
-confidence interval computed using an asymptotic normal approximation is also
-included \cite{brown2001interval}).
-The points represent the simulated
-values and the line shows the theoretical value. Note that these are
-deterministic strategies and show a good match between the expected value
-of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
-values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
-fact that the theoretic and simulated values are a good match.
-
-Fig~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
-good match (confirmed with a \(t\)-test in
-Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
-a given interaction between two IPD strategies can be summarised with a set of
-utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
-strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
-opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
-and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
-given pair and can be quite a complex endeavour for stochastic strategies with
-long memory: this is not necessary for the purposes of this work.  All data
-generated for this validation exercise can be found at~\cite{data}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
-    \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textit{deterministic} strategies: Alternator and
-         Cooperator. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.89942 &                0.89942 &                0.89942 \\
-          4 &          0.16344 &                0.74768 &                0.85877 \\
-          6 &          0.65406 &                0.84051 &                0.51992 \\
-          8 &          0.92617 &                0.45748 &                0.38604 \\
-         10 &          0.03505 &                0.37115 &                0.60635 \\
-         12 &          0.96697 &                0.20790 &                0.18124 \\
-         14 &          0.08126 &                0.63771 &                0.76246 \\
-         16 &          0.59434 &                0.07697 &                0.42520 \\
-         18 &          0.05339 &                0.47126 &                0.94814 \\
-         20 &          0.30805 &                0.79795 &                0.82381 \\
-        \bottomrule
-        \end{tabular}
-
-    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{deterministic} strategies: Alternator and
-    Cooperator.}
-    \label{tab:comparison_deterministic}
-\end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
-    \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textit{stochastic} strategies:
-             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_stochastic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.05372 &                0.05372 &                0.05372 \\
-          4 &          0.34188 &                0.00940 &                0.00005 \\
-          6 &          0.16510 &                0.00000 &                0.00000 \\
-          8 &          0.03451 &                0.00000 &                0.00000 \\
-         10 &          0.00543 &                0.00000 &                0.00000 \\
-         12 &          0.19646 &                0.00000 &                0.00000 \\
-         14 &          0.00814 &                0.00000 &                0.00000 \\
-         16 &          0.01038 &                0.00000 &                0.00000 \\
-         18 &          0.39556 &                0.00000 &                0.00000 \\
-         20 &          0.00030 &                0.00000 &                0.00000 \\
-        \bottomrule
-        \end{tabular}
-    \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{stochastic} strategies: Calculator and
-    Arrogant Q Learner.}
-    \label{tab:comparison_stochastic}
-\end{table}
-
-\subsection*{Empirical results}
-
-This section outlines the data analysis carried out, all data for this study is
-available at~\cite{data}.
-
-\begin{itemize}
-    \item First the specific case of
-        \(N=2\) is considered.
-    \item The effect of
-        population size on the ability of a strategy to invade another
-        population is investigated. This will highlight how complex strategies with long
-        memories outperform simpler strategies.
-    \item Then a similar investigation of the
-        ability to defend against an invasion is given.
-    \item Finally the relationship
-        between performance for differing population sizes as well as
-        taking a close look at zero determinant strategies \cite{Press2012} is
-        analysed.
-\end{itemize}
-
-\subsubsection*{The special case of \(N=2\)}
-
-When $N=2$ the fixation probabilities of the Moran process are effectively measures
-of the distribution of  relative
-mean payoffs over all possible matches between two players. The strategy
-that scores higher than the other more often will fixate more often. For \(N=2\)
-the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in the following sections.
-The top 16 (10\%) strategies are
-shown in
-
-Table~\ref{tbl:summary_top_2} and figures showing the performance of all
-strategies are available in the appendix.
-The top five ranking strategies are:
-
-\begin{enumerate}
-    \item The top strategy is the Collective Strategy (CS) which has a simple
-        handshake mechanism described above.
-    \item Defector: it always defects. Since it has no interactions with other
-        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
-    \item Aggravater, which plays like Grudger (responding to any
-        defections with unconditional defections throughout) however starts by
-        playing 3 defections.
-    \item Predator, a finite state machine described in \cite{Ashlock2006}.
-    \item Handshake, a slightly less aggressive version of the Collective
-        Strategy \cite{Robson1990}. As long as the initial sequence is played
-        then it cooperates. Thus it will do well in a population consisting of
-        many members of itself just as the Collective Strategy does. The
-        difference is that CS will defect after the handshake if the opponent
-        defects while Handshake will not.
-\end{enumerate}
-
-It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
-for which a zero determinant strategy does appear in the top 10\% ranking
-strategies: ZD-extort-4. The performance of zero determinant strategies will be
-examined more closely.
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \scalebox{0.95}{
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &                  Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-        \midrule
-        1  &                      CS &  0.497 &  0.5020 &  0.6651 &   0.572 &  0.9908 &  0.993 &  0.1800 \\
-        2  &                Defector &  0.502 &  0.5020 &  0.6496 &   0.518 &  1.0000 &  1.000 &  0.1767 \\
-        3  &              Aggravater &  0.502 &  0.5020 &  0.6328 &   0.518 &  0.9790 &  0.999 &  0.1660 \\
-        4  &                Predator &  0.319 &  0.4980 &  0.6301 &   0.551 &  0.9870 &  0.993 &  0.1676 \\
-        5  &               Handshake &  0.006 &  0.4503 &  0.6240 &   0.524 &  0.9908 &  0.993 &  0.1889 \\
-        6  &                Prober 4 &  0.431 &  0.4620 &  0.6183 &   0.534 &  0.9579 &  0.958 &  0.1656 \\
-        7  &                     \textbf{TF1} &  0.430 &  0.4980 &  0.6171 &   0.544 &  0.9240 &  0.981 &  0.1345 \\
-        8  &                Prober 3 &  0.497 &  0.5011 &  0.6044 &   0.505 &  0.9930 &  0.993 &  0.1683 \\
-        9  &                     \textbf{TF2} &  0.324 &  0.5020 &  0.6026 &   0.565 &  0.8362 &  0.887 &  0.1092 \\
-        10 &                 Grudger &  0.497 &  0.5020 &  0.5996 &   0.502 &  0.9840 &  0.989 &  0.1695 \\
-        11 &       Better and Better &  0.388 &  0.3951 &  0.5980 &   0.514 &  0.9300 &  0.934 &  0.1865 \\
-        12 &                    MEM2 &  0.497 &  0.5001 &  0.5942 &   0.502 &  0.9840 &  0.987 &  0.1656 \\
-        13 &  Meta Hunter Aggressive &  0.247 &  0.2943 &  0.5933 &   0.517 &  0.9498 &  0.981 &  0.2013 \\
-        14 &                     \textbf{TF3} &  0.344 &  0.4971 &  0.5927 &   0.502 &  0.9790 &  0.982 &  0.1617 \\
-        15 &            Fool Me Once &  0.494 &  0.4980 &  0.5892 &   0.502 &  0.9790 &  0.982 &  0.1625 \\
-        16 &             ZD-Extort-4 &  0.497 &  0.5020 &  0.5867 &   0.584 &  0.6900 &  0.695 &  0.0724 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
-    \label{tbl:summary_top_2}
-\end{table}
-
-As will be demonstrated the results for
-\(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that zero determinant strategies should be
-effective for larger population sizes, but these analyses consider stationary
-behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
-The stationarity assumption allows for a deterministic payoff matrix
-leading to the conclusions about zero determinant strategies in the space
-of memory-one strategies that do not generalize to this context.
-
-% In the next sections close attention to
-% strategies who are strong invaders/resistors is given.
-
-\subsubsection*{Strong Invaders}
-
-In this section the focus is on the ability of a mutant strategy to invade: the
-probability of one individual of a given type successfully fixating in a
-population of \(N - 1\) other individuals, denoted by \(x_1\).
-
-The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
-figures showing the performance of all strategies is available in the
-appendix.
-
-\begin{table}[!hbtp]
-    \centering
-    \tiny
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
-            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
-            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
-            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
-            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
-            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
-            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
-            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
-            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
-            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
-            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
-            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
-            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
-            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
-            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
-            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
-            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
-            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
-            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
-            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
-            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
-            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
-            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
-            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
-            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
-            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
-            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
-            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
-            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
-            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
-            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
-            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
-            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
-            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
-            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
-            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
-            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
-            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
-            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
-            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
-            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
-            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
-            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
-            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_invade}
-\end{table}
-
-It can be seen that apart from CS, none of the strategies for \(N=2\)
-of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
-top performing strategies are:
-
-\begin{itemize}
-    \item Grudger (which only performs well for \(N=3\)), starts by cooperating
-        but will defect if at any point the opponent has defected.
-    \item MEM2, an infinite memory strategy that switches between TFT, TF2T, and
-        Defector \cite{Li2014}.
-    \item TF3, the finite state machine trained specifically for Moran processes
-        described.
-    \item Prober 4, a strategy which starts with a specific 20 move sequence of
-        cooperations and defections \cite{Prison1998}. This initial sequence serves
-        as approximate handshake.
-    \item  PSO Gambler and Evolved Lookerup 2 2 2: strategies that make use
-        of a lookup table mapping the first 2 moves of the opponent as well as
-        the last 2 moves of both players to an action.  PSO gambler is a
-        stochastic version of  Lookerup which maps those states to probabilities
-       of cooperating. Lookerup was described in \cite{Knight2016}.
-    \item The Evolved ANN strategies are neural networks that map a number of
-	    attributes (first move, number of cooperations, last move, etc.) to
-	    an action. Both of these have been trained using an evolutionary
-	    algorithm.
-    \item Evolved FSM 16 is a 16 state finite state machine trained to
-        perform well in tournaments.
-\end{itemize}
-
-Only one of the above strategies is stochastic although close inspection of the
-source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin Evolved Looker Up.
-PSO Gambler Mem1 is a stochastic memory one strategy that has been trained to
-maximise its utility and does perform well.
-Apart from TF3, the finite state machines trained specifically for
-Moran processes do not appear in the top 5, while strategies trained for
-tournaments do. This is due to the nature of invasion: most of the opponents
-will initially be different strategies. The next section will consider the
-converse situation.
-
-\subsubsection*{Strong resistors}
-
-In addition to identifying good invaders, strategies resistant to invasion by
-other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy.
-
-Table~\ref{tbl:top_resist} shows the top strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
-for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies previously discussed perform well for high \(N\).
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
-            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
-            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
-            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
-            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
-            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
-            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
-            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
-            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
-            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
-            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
-            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
-            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
-            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
-            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
-            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
-            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
-            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
-            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
-            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
-            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
-            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
-            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
-            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
-            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
-            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
-            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
-            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
-            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
-            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
-            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
-        \midrule
-        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
-        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
-        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
-        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
-        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
-        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
-        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
-        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
-        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
-        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
-        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
-        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
-        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
-        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
-        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
-        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
-        \bottomrule
-        \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_resist}
-\end{table}
-
-Interestingly none of these strategies are stochastic: this is explained by the
-value of not provoking typically cooperative opponent strategies with
-speculative defections. This includes opponents using the same strategy.  Acting
-stochastically increases the chance of reducing the score of individuals of the
-same type in a Moran process.  However it is possible to design a strategy with
-a stochastic or error-correcting handshake that is an excellent resistor even in
-noisy environments \cite{Lee2015}.
-
-There are only two new strategies that appear in the top ranks for
-\(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
-resistors. They all have handshakes, and whilst the handshakes of CS and
-Handshake (which ranks highly for the smaller values of \(N\)) were
-programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
-process without any priming.
-
-As described previously the strategies trained with
-the payoff maximizing objective are among the best invaders in the library
-however they are not as resistant to invasion as the strategies trained using a
-Moran objective function. These strategies include trained finite state machine
-strategies, but they do not appear to have handshaking mechanisms. Therefore it
-is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
-handshakes for high invasion resistance. TF3 is a better total payoff maximizer
-which makes it a better invader along with the strategies
-trained to maximize total payoff since successful fitness proportionate selection
-is necessary for invasion. Training with an objective with initial population
-mix other than $(N/2, N/2)$ may favor invasion or resistance.
-
-The payoff maximizing strategies typically will not defect before the opponent's
-first defection, possibly because the training strategy collection contains some
-strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
-for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically for handshaking strategies
-it is advantageous to defect (as a signal)
-in order to achieve mutual cooperation with opponents using the same strategy
-but not with other opponents. Nevertheless an evolutionary process is able to
-tunnel through the costs and risks associated with early defections to find more
-optimal solutions, so it is not surprising in hindsight that handshaking
-strategies emerge from the evolutionary training process.
-
-A handshake requires at least one defection and there is
-selective pressure to defect as few times as possible to achieve the
-self-recognition mechanism. It is also unwise to defect on the first move as
-some strategies additionally retaliate in response to first round defections. So the
-handshakes used by TF1, TF2, and CS are in some sense optimal.
-
-It is evident through
-the work presented that performance of strategies not only depends
-on the initial population distribution but also that there seems to be a
-difference depending on whether or not \(N>2\). This will be explored further in
-the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also
-considering
-\(x_{N/2}\).
-
-\subsubsection*{The effect of population size}
-
-Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
-and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
-strategies:
-
-\begin{itemize}
-    \item The strategies that ranked highly for \(N=2\);
-    \item The strategies that ranked highly for \(N=14\);
-    \item The zero determinant strategies.
-\end{itemize}
-
-The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
-expected since, as described previously these strategies
-were trained in an initial population of \((N/2, N/2)\) individuals.
-
-For all starting populations
-\(i\in\{1, N/2, N-1\}\) the ranks of strategies are relatively stable across the
-different values of \(N>2\) however for \(N=2\) there is a distinct difference.
-This highlights that there is little that can be inferred about the evolutionary
-performance of a strategy in a large population from its performance in a small
-population. This is confirmed by the performance of the zero determinant strategies: while
-some do rank relatively highly for \(N=2\) (ZD-Extort-4 has rank 16) this rank
-does not translate to larger populations.
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                         Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                           CS &    1 &    1 &    2 &   11 &    9 &   11 &   13 &   21 &   16 &   22 &   17 &   25 &   23 \\
-                     Defector &    2 &   43 &   80 &   91 &   89 &   87 &   87 &  103 &   97 &  105 &   94 &  103 &  101 \\
-                   Aggravater &    3 &   50 &   89 &   99 &  102 &  103 &  108 &  113 &  114 &  115 &  115 &  116 &  117 \\
-                     Predator &    4 &    8 &   24 &   35 &   28 &   33 &   31 &   43 &   36 &   43 &   34 &   45 &   35 \\
-                    Handshake &    5 &   17 &   40 &   46 &   43 &   46 &   46 &   49 &   48 &   49 &   47 &   50 &   49 \\
-        \midrule
-               Evolved FSM 16 &   31 &   11 &    6 &    2 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-            PSO Gambler 2\_2\_2 &   29 &   14 &   10 &    6 &    4 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-         EvolvedLookerUp2\_2\_2 &   33 &   18 &   11 &    9 &   10 &    6 &    6 &    5 &    3 &    5 &    3 &    3 &    3 \\
-                  Evolved ANN &   20 &   10 &    8 &    7 &    8 &    5 &    3 &    3 &    4 &    3 &    4 &    4 &    4 \\
-                Evolved ANN 5 &   21 &    9 &    7 &    8 &    7 &    4 &    5 &    4 &    5 &    4 &    5 &    5 &    5 \\
-        \midrule
-                          \textbf{TF1} &    7 &   13 &   33 &   38 &   30 &   39 &   42 &   46 &   42 &   46 &   41 &   46 &   46 \\
-                          \textbf{TF2} &    9 &   19 &   29 &   33 &   19 &   28 &   29 &   38 &   27 &   34 &   26 &   32 &   30 \\
-                          \textbf{TF3} &   14 &    4 &    5 &    5 &    6 &    9 &   11 &   11 &   12 &   14 &   13 &   13 &   16 \\
-        \midrule
-                  ZD-Extort-4 &   16 &   81 &  107 &  120 &  135 &  136 &  142 &  140 &  142 &  142 &  144 &  144 &  145 \\
-               ZD-Extort-2 v2 &   41 &  105 &  126 &  140 &  152 &  152 &  153 &  152 &  153 &  153 &  153 &  152 &  153 \\
-                  ZD-Extort-2 &   43 &  107 &  125 &  139 &  151 &  151 &  152 &  153 &  152 &  152 &  152 &  153 &  152 \\
-                     ZD-SET-2 &  100 &  111 &  117 &  117 &  122 &  127 &  131 &  128 &  131 &  131 &  130 &  132 &  131 \\
-                    ZD-GTFT-2 &  112 &   92 &   82 &   80 &   81 &   82 &   84 &   72 &   81 &   71 &   78 &   72 &   70 \\
-                     ZD-GEN-2 &  113 &   96 &   87 &   83 &   85 &   88 &   90 &   82 &   87 &   82 &   86 &   83 &   91 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_invade}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                   Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-               Defector &    2 &   29 &   55 &   79 &   94 &   97 &   98 &   98 &  102 &  101 &  103 &  100 &  102 \\
-             Aggravater &    3 &   42 &   71 &   97 &  101 &  106 &  107 &  111 &  113 &  113 &  116 &  115 &  115 \\
-               Predator &    4 &    2 &    3 &    3 &    3 &    4 &    4 &    4 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    4 &    5 &    5 &    5 &    5 &    5 &    6 &    6 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF1} &    7 &    3 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-                    \textbf{TF2} &   10 &    5 &    4 &    4 &    4 &    3 &    3 &    3 &    3 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    6 &    6 &    6 &    6 &    6 &    6 &    5 &    5 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   13 &    9 &   10 &   11 &   11 &   11 &   13 &   14 &   13 &   13 &   13 &   13 &   13 \\
-        \midrule
-            ZD-Extort-4 &   19 &   68 &   98 &  106 &  108 &  114 &  115 &  115 &  118 &  118 &  117 &  118 &  117 \\
-         ZD-Extort-2 v2 &   49 &   98 &  111 &  121 &  123 &  124 &  124 &  130 &  130 &  132 &  134 &  132 &  134 \\
-            ZD-Extort-2 &   50 &   97 &  112 &  123 &  124 &  125 &  123 &  126 &  131 &  131 &  132 &  133 &  133 \\
-               ZD-SET-2 &  108 &  105 &  104 &  104 &  103 &  103 &  100 &  100 &  101 &   99 &   98 &   98 &   98 \\
-              ZD-GTFT-2 &  112 &   95 &   88 &   84 &   75 &   72 &   71 &   73 &   71 &   71 &   67 &   68 &   68 \\
-               ZD-GEN-2 &  114 &   96 &   89 &   86 &   77 &   75 &   72 &   74 &   72 &   72 &   68 &   69 &   69 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_resist}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-        \begin{tabular}{lrrrrrrr}
-        \toprule
-                   Size &      2 &      4 &      6 &      8 &     10 &     12 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    2 \\
-               Defector &    2 &   78 &   99 &  106 &  110 &  113 &  120 \\
-             Aggravater &    3 &   91 &  105 &  111 &  122 &  125 &  128 \\
-               Predator &    4 &    2 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    6 &    5 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF2} &    9 &    4 &    3 &    2 &    2 &    2 &    1 \\
-                    \textbf{TF1} &    7 &    3 &    2 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    5 &    6 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   14 &    8 &    8 &    8 &    8 &    8 &    8 \\
-        \midrule
-            ZD-Extort-4 &   16 &  102 &  117 &  129 &  141 &  143 &  145 \\
-         ZD-Extort-2 v2 &   41 &  118 &  135 &  151 &  152 &  152 &  153 \\
-            ZD-Extort-2 &   43 &  117 &  136 &  149 &  151 &  151 &  152 \\
-               ZD-SET-2 &  100 &  110 &  110 &  108 &  106 &  106 &  108 \\
-              ZD-GTFT-2 &  112 &   82 &   80 &   77 &   75 &   75 &   74 \\
-               ZD-GEN-2 &  113 &   85 &   81 &   82 &   79 &   77 &   76 \\
-        \bottomrule
-        \end{tabular}
-    \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_coexist}
-\end{table}
-
-Fig~\ref{fig:correlation_coefficients} shows the correlation coefficients
-of the ranks of strategies in differing population size. How well a strategy
-performs in any Moran process for \(N>2\) has
-little to do with the performance for \(N=2\). This illustrates why the strong
-performance of zero determinant strategies predicted in \cite{Press2012} does
-not extend to larger populations. This was discussed theoretically in
-\cite{Adami2013} and observed empirically in these simulations.
-
-\begin{figure}[!htbp]
-    \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
-        \caption{Rank based on \(x_1\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
-        \caption{Rank based on \(x_{N - 1}\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
-        \caption{Rank based on \(x_{N/2}\)}
-    \end{subfigure}
-    \caption{Heatmap of correlation coefficients of rankings by population size.}
-    \label{fig:correlation_coefficients}
-\end{figure}
-
-\section*{Discussion}
-
-Training strategies to excel
-at the Moran process leads to the evolution of cooperation, but only with like
-individuals in the case of TF1 and TF2. This may have significant implications
-for various biological and social phenomena such as
-human social interactions, particularly the evolution of ingroup/outgroup mechanisms
-and other sometimes costly rituals that reinforce group behavior.
-
-While TF1 and TF2 are competent invaders, the best invaders
-in the study do not appear to employ strict handshakes, and are generally
-cooperative strategies. TF3, which does not use a handshake, is a better invader
-than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
-of the same kind of training processes and is a better combined invader-resistor
-than the invaders that were trained previously to maximize payout.
-
-The strategies trained to maximize payoff in head-to-head matches are generally
-cooperative and are effective invaders.
-Combined with the fact that handshaking strategies are stronger resistors,
-this suggests that while maximizing individual payoff can lead to the evolution
-of cooperation, these strategies are not the most evolutionarily stable
-in the long run. A strategy with a handshaking mechanism is still capable of
-invading and is more resistant to subsequent invasions. Moreover, the
-best resistor of the payoff maximally trained strategies (Evolved Looker Up
-1\_1\_1),
-which always defects if the opponent defects in the first round, is effectively
-employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
-which emerged from training memory one strategies for the Moran process,
-also effectively employs a handshake of always cooperating, as it defects
-for the remainder of the match if the opponent ever defects.
-
-The insights that payoff maximizers are better invaders and that handshakers
-are better resistors suggests that a strategy
-aware of the population distribution could choose to become a handshaker at
-a critical threshold and use a strategy better for invasion when in the
-minority. Information about the population distribution was not available
-to our strategies. Previous work has showed that strategies able to retain
-memory across matches can infer the population distribution and act in such
-a manner, resulting in a strategy effective at invasion and resistance
-\cite{Lee2015}.
-
-We did not attempt other objective functions that may serve to select for both
-invasion and resistance better than training at a starting population of
-$(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
-improvement. Any handshake more sophisticated than always cooperate necessarily involves
-a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
-effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
-they need a longer or more strict handshake. But if this handshake involves
-a defection then likely the invasion ability is diminished for $N > 2$: the top
-invaders for larger $N$ are nice strategies that do not defect before their
-opponents. This is because good invaders need to maximize match payoff to benefit
-from fitness proportionate selection,
-and so in the absence of a handshake mechanism, knowledge of the population
-distribution, or some identifying label on the opponent,
-a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping dramatically in rank
-as the population size increases.
-
-We did, however, attempt to evolve CS using finite state machines and lookup table
-based players,
-which resulted in some very similar strategies. In particular we evolved a
-lookup strategy that had a handshake of DC and played TFT with other players
-after a correct handshake while defecting otherwise, which is quite close in
-function to CS (full grudging is not possible with a lookup table of limited
-depth).
-
-Finally we note that it may be possible to achieve similar results with smaller
-capacity finite state machine players.
-
-\section*{Conclusion}
-
-A detailed empirical analysis of 164 strategies of the IPD within a pairwise
-Moran process has been carried out. All \(\binom{164}{2}=13,366\) possible
-ordered pairs of strategies have been placed in a Moran process with different
-starting values allowing each strategy to attempt to invade the other.
-This is the largest such experiment carried out and has led to many insights.
-
-When studying evolutionary processes it is vital to consider \(N>2\) since
-results for \(N=2\) cannot be used to extrapolate performance in larger
-populations. This was shown both observationally
- but also by
-considering the correlation of the ranks in different population sizes.
-
-Memory one strategies do not perform as well as longer memory strategies in general
-in this study. Several longer memory strategies were high performers for invasion,
-particularly the strategies which have been trained using a number of reinforcement
-learning algorithms. Interestingly they have been trained to perform well in
-tournaments and not Moran processes specifically. In some cases these strategies
-utilize all the history of play (the neural network strategies and the lookup
-table strategies, the latter using the first round and some number of trailing rounds).
-
-There are no memory one strategies in the top 5 performing strategies
-for \(N>3\). Training memory-one strategies specifically for the Moran process
-typically led to Grudger / Grim, a memory-one strategy with
-four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
-The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
-training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
-For comparison, training for maximum score difference between the player and the
-opponent resulted in a strategy nearly the same as Grudger, with four-vector
-$(0.9459, 0, 0, 0)$ (not included in the study).
-
-One of the major findings discussed, is
-the ability of strategies with a handshake mechanism to resist invasion. This
-was not only revealed for CS (a human designed strategy) but also for
-two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
-process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. Fig~\ref{fig:cooperation_rates} shows the cooperation
-rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study.
-This corresponds to the fraction of cooperation played by that strategy observed
-in a given round (out of the first 15) where each matchup is repeated 10000 times to
-obtain the mean.
-
-While TF3
-does not have a strict handshake mechanism it is clear that all these strategies
-start a match by cooperating. It is then evident that TF3 cooperates more than
-the other strategies thus explaining the difference in performance. It is also
-clear that CS only cooperates with itself and Handshake: it is a very aggressive
-strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
-        \caption{TF1}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
-        \caption{TF2}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
-        \caption{TF3}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
-        \caption{CS}
-    \end{subfigure}
-    \caption{Cooperation rate per round (over 10000 repetitions). Rows
-        correspond to all the strategies considered in this work (ordered
-    alphabetically by name). Columns correspond to round of an IPD match.}
-    \label{fig:cooperation_rates}
-\end{figure}
-
-These findings are important for the ongoing understanding of
-population dynamics and offer evidence for some of the shortcomings of low
-memory which has started to be recognised by the community \cite{Hilbe2017}.
-
-All source code for this work has been written in a sustainable manner: it is
-open source, under version control and tested which ensures that all results can
-be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
-the processed data has also been properly archived and can be found
-at \cite{data}.
-
-There are many opportunities to build on this work. In particular, an analysis
-of the effect of noise should offer insights regarding the stability of the findings,
-particularly for the handshaking strategies. They may be less dominant for
-larger amounts of noise since the handshaking mechanisms may become brittle.
-There are many other variations to explore including populations with more
-than one type, spatial structure, and mutation.
-
-One final point to recognise: the large set of strategies used here does not in
-itself constitute an authoritative set. Whilst it is not only large but also very
-diverse, the results (and rankings) presented might change given a different set
-of strategies. A further piece of work could look at subgroups of strategies and
-how they fair against other subgroups. Note that because of the open nature of
-the work here (not only is the source code archived but so is the data) this and
-any other further analysis is possible to carry out.
-
-\section*{Acknowledgements}
-
-This work was performed using the computational facilities of the Advanced
-Research Computing @ Cardiff (ARCCA) Division, Cardiff University.
-
-A variety of software libraries have been used in this work:
-
-\begin{itemize}
-    \item The Axelrod library (IPD strategies and Moran processes)
-        \cite{axelrodproject}.
-    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
-    \item The pandas and numpy libraries (data manipulation)
-        \cite{mckinney2010data, walt2011numpy}.
-\end{itemize}
-
-\nolinenumbers
-
-\begin{thebibliography}{10}
-
-\bibitem{Adami2013}
-Christoph Adami and Arend Hintze.
-\newblock {Evolutionary instability of zero-determinant strategies demonstrates
-  that winning is not everything.}
-\newblock {\em Nature communications}, 4(1):2193, 2013.
-
-\bibitem{adami2016evolutionary}
-Christoph Adami, Jory Schossau, and Arend Hintze.
-\newblock {Evolutionary game theory using agent-based methods}.
-\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
-
-\bibitem{affenzeller2009genetic}
-Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
-\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
-  Practical Applications}.
-\newblock Numerical Insights. CRC Press, 2009.
-
-\bibitem{Nowak2017}
-Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
-  Shing-Tung Yau, and Martin~A Nowak.
-\newblock {Evolutionary dynamics on any population structure}.
-\newblock 544:227--230, March 2017.
-
-\bibitem{Ashlock2015}
-Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
-\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
-  Agents}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 7(1):53--65, 2015.
-
-\bibitem{Ashlock2008}
-Daniel Ashlock and Eun-Youn Kim.
-\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
-  dilemma strategies}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
-  2008.
-
-\bibitem{Ashlock2006}
-Wendy Ashlock and Daniel Ashlock.
-\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
-  with different population sizes}.
-\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
-  pages 297--304. IEEE, 2006.
-
-\bibitem{Ashlock2014}
-Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
-\newblock {The evolution of exploitation}.
-\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
-  Symposium on}, pages 135--142. IEEE, 2014.
-
-\bibitem{Axelrod1980a}
-Robert Axelrod.
-\newblock {Effective choice in the prisoner's dilemma}.
-\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
-
-\bibitem{Axelrod1980b}
-Robert Axelrod.
-\newblock {More Effective Choice in the Prisoner's Dilemma}.
-\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.
-
-\bibitem{Axelrod1984}
-Robert Axelrod.
-\newblock {\em The Evolution of Cooperation}.
-\newblock Basic books. Basic Books, 1984.
-
-\bibitem{Baek2016}
-{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
-  A}.
-\newblock {Comparing reactive and memory- one strategies of direct
-  reciprocity}.
-\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
-
-\bibitem{Banks1990}
-Jeffrey~S Banks and Rangarajan~K Sundaram.
-\newblock {Repeated games, finite automata, and complexity}.
-\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
-
-\bibitem{Beaufils1997}
-Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
-\newblock {Our meeting with gradual, a good strategy for the iterated
-  prisoner’s dilemma}.
-\newblock In {\em Proceedings of the Fifth International Workshop on the
-  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.
-
-\bibitem{brown2001interval}
-Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
-\newblock Interval estimation for a binomial proportion.
-\newblock {\em Statistical science}, pages 101--117, 2001.
-
-\bibitem{Andre2013}
-Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
-\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
-\newblock pages 1--6, 2013.
-
-\bibitem{Eckhart2015}
-Arnold Eckhart.
-\newblock Coopsim v0.9.9 beta 6.
-\newblock https://github.com/jecki/CoopSim/, 2015.
-
-\bibitem{Flood1958}
-Merrill~M Flood.
-\newblock {Some Experimental Games}, 1958.
-
-\bibitem{Frean1994}
-Marcus~R Frean.
-\newblock {The prisoner's dilemma without synchrony}.
-\newblock {\em Proceedings of the Royal Society of London B: Biological
-  Sciences}, 257(1348):75--79, 1994.
-
-\bibitem{Gaudesi2016}
-Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
-\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
-  dilemma tournaments}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 8(3):288--300, 2016.
-
-\bibitem{marc_harper_2017_824264}
-Marc Harper, Vince Knight, and Martin Jones.
-\newblock Axelrod-python/axelrod-dojo: v0.0.1.
-\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
-
-\bibitem{Harper2017}
-Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
-  Glynatsi, and Owen Campbell.
-\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
-  Prisoner's Dilemma}.
-\newblock arXiv:1707.06307, 2017.
-
-\bibitem{Hilbe2017}
-Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
-  Nowak.
-\newblock {Memory-n strategies of direct reciprocity}.
-\newblock {\em Proceedings of the National Academy of Sciences}, page
-  201621239, 2017.
-
-\bibitem{Hilbe2013}
-Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
-\newblock {Adaptive dynamics of extortion and compliance}.
-\newblock {\em PloS one}, 8(11):e77886, 2013.
-
-\bibitem{hunter2007matplotlib}
-John~D Hunter.
-\newblock {Matplotlib: A 2D graphics environment}.
-\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
-
-\bibitem{kendall2007iterated}
-Graham Kendall, Xin Yao, and Siang~Y Chong.
-\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
-\newblock Advances in natural computation. World Scientific, 2007.
-
-\bibitem{Knight2016}
-Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
-  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
-  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
-  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
-  Timothy Standen, Luis Visintini, and Karl Molden.
-\newblock {An Open Framework for the Reproducible Study of the Iterated
-  Prisoner ' s Dilemma}.
-\newblock 2016.
-
-\bibitem{data}
-Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
-\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
-  Self-Recognition Mechanisms: an empirical study of the Moran process for the
-  iterated Prisoner's dilemma using reinforcement learning}.
-\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
-
-\bibitem{Kraines1989}
-David Kraines and Vivian Kraines.
-\newblock {Pavlov and the prisoner's dilemma}.
-\newblock {\em Theory and decision}, 26(1):47--79, 1989.
-
-\bibitem{Kuhn2017}
-Steven Kuhn.
-\newblock Prisoner's dilemma.
-\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
-  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
-  edition, 2017.
-
-\bibitem{Lee2015}
-Christopher Lee, Marc Harper, and Dashiell Fryer.
-\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
-\newblock {\em Plos One}, 10(3):e0120625, 2015.
-
-\bibitem{Li2011}
-Jiawei Li, Philip Hingston, and Graham Kendall.
-\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
-  Dilemma Competitions}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 3(4):348--360, 2011.
-
-\bibitem{Li2009}
-Jiawei Li and Graham Kendall.
-\newblock {A strategy with novel evolutionary features for the iterated
-  prisoner's dilemma.}
-\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
-
-\bibitem{Li2014}
-Jiawei Li and Graham Kendall.
-\newblock {The effect of memory size on the evolutionary stability of
-  strategies in iterated prisoner's dilemma}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
-  2014.
-
-\bibitem{Prison1998}
-LIFL.
-\newblock Prison.
-\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
-
-\bibitem{Mathieu2015}
-Philippe Mathieu and Jean-Paul Delahaye.
-\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
-  Abstract)}.
-\newblock {\em 14th International Conference on Autonomous Agents and
-  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
-
-\bibitem{mckinney2010data}
-Wes McKinney et~al.
-\newblock Data structures for statistical computing in python.
-\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
-  445, pages 51--56. van der Voort S, Millman J, 2010.
-
-\bibitem{Mittal2009}
-Shashi Mittal and Kalyanmoy Deb.
-\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
-  multiple conflicting objectives}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
-  2009.
-
-\bibitem{Moran1957}
-Patrick A~P Moran.
-\newblock {Random Processes in Genetics}.
-\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
-  Society}, 54(1):60--71, 1957.
-
-\bibitem{Nachbar1992}
-John~H Nachbar.
-\newblock {Evolution in the finitely repeated prisoner's dilemma}.
-\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
-  1992.
-
-\bibitem{Nowak}
-Martin~A Nowak.
-\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
-\newblock Cambridge: Harvard University Press.
-
-\bibitem{Nowak1993}
-Martin~A Nowak and Karl Sigmund.
-\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
-  the Prisoner's Dilemma game.}
-\newblock {\em Nature}, 364(6432):56--58, 1993.
-
-\bibitem{Press2012}
-William~H Press and Freeman~J Dyson.
-\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
-  evolutionary opponent.}
-\newblock {\em Proceedings of the National Academy of Sciences of the United
-  States of America}, 109(26):10409--13, 2012.
-
-\bibitem{Prlic2012}
-Andreas Prlić and James~B Procter.
-\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
-\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
-
-\bibitem{axelrodproject}
-The~Axelrod project developers.
-\newblock Axelrod: v2.9.0.
-\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
-
-\bibitem{Robson1990}
-Arthur~J Robson.
-\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
-  handshake}.
-\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
-
-\bibitem{Sandve2013}
-Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
-\newblock {Ten Simple Rules for Reproducible Computational Research}.
-\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
-
-\bibitem{Stewart2012}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  109(26):10134--10135, 2012.
-
-\bibitem{stewart2013extortion}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {From extortion to generosity, evolution in the iterated prisoner’s
-  dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  110(38):15348--15353, 2013.
-
-\bibitem{Tzafestas2000}
-Elpida Tzafestas.
-\newblock {Toward adaptive cooperative behavior}.
-\newblock {\em From Animals to animals: Proceedings of the 6th International
-  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
-  2000.
-
-\bibitem{PD2017}
-Unkwown.
-\newblock www.prisoners-dilemma.com.
-\newblock http://www.prisoners-dilemma.com/, 2017.
-
-\bibitem{Berg2015}
-Pieter Van~den Berg and Franz~J Weissing.
-\newblock {The importance of mechanisms for the evolution of cooperation}.
-\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
-  Society, 2015.
-
-\bibitem{walt2011numpy}
-St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
-\newblock {The NumPy array: a structure for efficient numerical computation}.
-\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
-
-\bibitem{West2016}
-Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
-\newblock {The prisoner’s dilemma as a cancer model}.
-\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
-
-\bibitem{Wilson2014}
-Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
-  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
-  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
-\newblock {Best Practices for Scientific Computing}.
-\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
-
-\bibitem{Axelrod1995}
-Jianzhong Wu and Robert Axelrod.
-\newblock {How to cope with noise in the iterated prisoner's dilemma}.
-\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
-
-\end{thebibliography}
-
-\appendix
-
-\section{Appendix A: List of players}\label{app:list_of_players}
-
-\footnotesize
-\begin{enumerate}
-\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
-\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
-\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
-\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
-\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
-\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
-\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
-\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
-\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
-\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980a}
-\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
-\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006}
-\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006}
-\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
-\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
-\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Banks1990, Beaufils1997, Berg2015, Li2011}
-\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
-\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
-\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
-\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
-\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Stewart2012}
-\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
-\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
-\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
-\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980a}
-\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
-\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006}
-\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
-\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
-\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980a, Tzafestas2000}
-\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
-\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
-\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
-\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
-\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
-\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
-\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
-\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
-\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
-\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
-\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
-\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
-\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
-\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
-\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a}
-\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980a}
-\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
-\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\end{enumerate}
-
-\section{Appendix B: Supplementary figures}
-
-\begin{itemize}
-    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
-for each strategy. The mean and error bars are shown against the collection of
-all opponents.
-
-    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
-\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
-the collection of all opponents.
-
-    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
-ranks of each strategy according to mean absorption probability across all
-population sizes.
-\end{itemize}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
-    \label{invasion-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
-    \label{invasion-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
-    \label{resistance-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
-    \label{resistance-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
-    \label{fig:ranks_v_size_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
-    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_coexist}
-\end{figure}
-
 \end{document}

### 2018-08-10 tf2.tex
Re rename all images.

--- 2018-04-05 plos/main.tex
@@
-% Template for PLoS
-% Version 3.4 January 2017
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
-\usepackage{algorithm,algorithmic}
-\usepackage{amsmath}
-\usepackage{authblk}
-\usepackage{booktabs}
-\usepackage{booktabs}
-\usepackage{fancyvrb}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{multicol}
-\usepackage{pdflscape}
-\usepackage{standalone}
-\usepackage{subcaption}
+\documentclass[crop,tikz]{standalone}
 \usepackage{tikz}
-\usepackage{xstring}
-
 \usetikzlibrary{calc, shapes, patterns}
-
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline
-{Evolution reinforces cooperation with the emergence of self-recognition
- mechanisms: an empirical study of strategies in the Moran process for the
- iterated prisoner's dilemma }
-% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Vincent Knight\textsuperscript{1*\Yinyang},
-Marc Harper\textsuperscript{2\Yinyang},
-Nikoleta E. Glynatsi\textsuperscript{2\ddag},
-Owen Campbell\textsuperscript{3\ddag},
-\\
-\bigskip
-\textbf{1} Cardiff University, School of Mathematics, Cardiff, UK
-\\
-\textbf{2} Google Inc., Mountain View, CA, USA
-\\
-\textbf{3} Independent Researcher, Chester, UK
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-%
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-\ddag These authors also contributed equally to this work.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* knightva@cardiff.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-    We present insights and empirical results from an extensive numerical
-    study of the evolutionary dynamics of the iterated prisoner's dilemma.
-    Fixation probabilities for Moran processes are obtained
-    for all pairs of 164 different strategies including classics such as TitForTat, zero
-    determinant strategies, and many more sophisticated strategies.
-    Players with long memories and sophisticated behaviours outperform
-    many strategies that perform well in a two player setting. Moreover we
-    introduce several strategies trained with evolutionary algorithms to
-    excel at the Moran process. These strategies are excellent invaders
-    and resistors of invasion and in some cases naturally evolve handshaking
-    mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake mechanisms.
-    This suggests that while maximizing individual payoff
-    can lead to the evolution of cooperation through invasion, the relatively
-    weak invasion resistance of payoff maximizing strategies are not as
-    evolutionarily stable as strategies employing handshake mechanisms.
-\linenumbers
-
-\section*{Introduction}
-
-The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
-used to model a variety of strategic interactions. Each player chooses
-simultaneously and independently
-between cooperation (C) or defection (D). The payoffs of
-the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
-\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one
-round game, but is commonly studied in a manner where the prior outcomes
-matter. This repeated form is called the Iterated Prisoner's
-Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
-number of strategies have been developed to take advantage of the history of
-play. Strategies referred to as zero determinant (ZD) strategies
-\cite{Press2012} can manipulate some players through extortionate mechanisms.
-
-The Moran Process \cite{Moran1957} is a model of
-evolutionary population dynamics that has been used to gain insights about the
-evolutionary stability in a number of settings.
-Several earlier
-works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
-or are limited to classes of strategies
-such as memory-one strategies that only use the previous round of play.
-
-This manuscript provides a detailed numerical analysis of agent-based simulations
-of \textbf{164} complex and adaptive strategies for the
-IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
-effort to provide software for reproducible research for the IPD\@. The library
-now contains over 186 parameterized
-strategies including classics like TitForTat and WinStayLoseShift, as well as
-recent variants such as OmegaTFT, zero determinant and other memory one
-strategies, strategies based on finite state machines, lookup tables, neural
-networks, and other machine learning based strategies, and a collection of novel
-strategies. Not all strategies have been considered for this study: excluded
-are those that make use of knowledge of the number of turns in a match
-and others that have a high
-computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 50 contributors from around the
-world, made by programmers and researchers \cite{Knight2016}. Three of the considered
-strategies are finite state machines trained specifically for Moran processes
-(described further in the Methods section).
-
-In addition to providing a large collection of strategies, the Axelrod library
-can conduct matches, tournaments and population
-dynamics with variations including noise and spatial structure.
-The strategies and simulation frameworks are
-automatically tested to an extraordinarily high degree of coverage in accordance
-with best research software practices.
-
-Using the Axelrod library and the many strategies it contains, we obtain the
-probability with which a given strategy takes over a population (referred to as
-fixation probability) for all pairs of strategies, identifying those that are
-effective invaders and those resistant to invasion, for population sizes $N=2$
-to $N=14$. Moreover we present a number (16) of strategies that were created via
-reinforcement algorithms (evolutionary and particle swarm algorithms) that are
-among the best invaders and resistors of invasion known to date, and show that
-handshaking mechanisms naturally arise from these processes as an
-invasion-resistance mechanism.
-
-In 2016, work has argued that agent-based
-simulations can provide insights in evolutionary game theory not available
-via direct mathematical analysis~\cite{adami2016evolutionary}. The results
-and insights contained in this paper would be difficult to derive analytically.
-
-In particular the following questions are addressed:
-\begin{enumerate}
-    \item What strategies are good invaders?
-    \item What strategies are good at resisting invasion?
-    \item How does the population size affect these findings?
-\end{enumerate}
-
-While the results agree with some of the published literature, it is found that:
-
-\begin{enumerate}
- \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
- \item Complex strategies can be effective, and in fact can naturally evolve
-     through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or possess a handshake mechanism.
- \item Strong invaders are generally cooperative strategies that do not defect
- first but retaliate to varying degrees of intensity against strategies that defect.
- \item Strategies evolved to maximize their total payoff can be strong invaders
- and achieve mutual cooperation with many other strategies.
-\end{enumerate}
-
-\section*{Materials and methods}
-\subsection*{The Moran Process}
-
-A Moran process is a stochastic birth death process on a finite population in which the
-population size stays constant over time. Individuals are \textit{selected}
-according to a given fitness landscape. The fitness landscape in this work is
-defined as the total utility against all other individuals in the population.
-Once selected, the individual
-is reproduced and similarly another individual is chosen to be removed from the
-population (a uniform random selection is used). This is shown diagrammatically
-in Fig~\ref{fig:moran_process}. In some settings mutation is
-also considered but without mutation (the case considered in this work) this
-process will arrive at an absorbing state where the population is entirely made
-up of players of one strategy. The probability with which a given strategy,
-starting from a single individual takes
-over a population is called the \textit{fixation probability}. A more detailed
-analytic description of this is given later. In our
-simulations offspring do not inherit any knowledge or history from parent
-replicants.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.5}{
-
-\begin{tikzpicture}[scale=.9]
-	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-
-	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-
-	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);
-
-	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-
-	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-\end{tikzpicture}
-
-}
-    \caption{A diagrammatic representation of a Moran process.}
-    \label{fig:moran_process}
-\end{figure}
-
-The Moran process was initially introduced in \cite{Moran1957}. It has since
-been used in a variety of settings including the understanding of the spread of
-cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
-emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider relatively simple strategies. A few works
-looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
-\cite{Li2014} but this is not done in the more widely used setting of the Moran
-process, rather in terms of infinite population stability. In \cite{Baek2016}
-Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies: strategies that recall
-the events of the previous round only.
-
-Of particular interest are the zero determinant strategies introduced in
-\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
-a strategy using machine learning techniques was capable of resisting invasion
-and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
-has investigated the effect of memory length on strategy performance and the
-emergence of cooperation but this is not done in a Moran process context and only
-considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
-recognised that many zero determinant strategies do not fare well against
-themselves. This is a disadvantage for the Moran process where the best
-strategies cooperate well with other players using the same strategy.
-
-This work uses pair-wise Moran processes in a similar way to matches in the many
-IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
-A population-based perspective is given which adds additional
-evolutionary components to the IPD, namely the evolutionary dynamics of invasion
-and resistance.
-
-\subsection*{Strategies considered}\label{sec:strategies}
-
-To carry out this numerical experiment, 164
-strategies, listed (with their properties) in the Appendix,
-are used from the Axelrod library. There are
-43 stochastic and
-121 deterministic strategies. Their memory depth,
-defined by the number of rounds of history used by the strategy each round, is
-shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
-strategy uses the entire history of play (whatever its length). For example, a
-strategy that utilizes a handshaking mechanism where the opponent's actions on
-the first few rounds of play determines the strategies subsequent behavior would
-have infinite memory depth.
-
-A number of these strategies have been trained with reinforcement learning
-algorithms prior to this study and not specifically for the Moran process.
-
-\begin{itemize}
-    \item Evolved ANN: a neural network based strategy;
-    \item Evolved LookerUp: a lookup table based strategy;
-    \item PSO Gambler: a stochastic version of the lookup table based strategy;
-    \item Evolved HMM: a hidden Markov model based strategy.
-\end{itemize}
-
-Apart from the PSO Gambler strategy, which was trained using a particle swarm
-optimisation algorithm, these strategies are trained with an evolutionary
-algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. They were trained to
-win IPD tournaments by maximizing their mean total payoffs against a variety
-of opponents. Variation is
-introduced via mutation and crossover of parameters, and the best performing
-strategies are carried to the next generation along with new variants. Similar
-methods appear in the literature \cite{Ashlock2006}.
-There has also been some work on strategies using an evolutionary algorithm in real time:
-in~\cite{Gaudesi2016}
-an evolutionary algorithm is used to build a model of the opponent and attempt
-to exploit any potential weakness. In this work all strategies resulting from
-evolutionary algorithms are pre-trained.
-
-More information about each player can be obtained in the documentation for
-\cite{axelrodproject} and a detailed description of the performance
-of these strategies in IPD tournaments is described in~\cite{Harper2017}.
-
-All of the training code is archived at \cite{marc_harper_2017_824264}. This
-software is (similarly to the Axelrod library) available on
-github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
-with documentation to
-train new strategies easily. Training
-typically takes less than 100 generations and can be completed within several
-hours on commodity hardware.
-
-There are three further strategies trained specifically for this study; Trained
-FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}), using the notation common in the literature where
-\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
-\(A_2\) as well as arrows corresponding to changes of state.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
-	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
-	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
-	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
-	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};
-
-	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
-	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};
-
-	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
-	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
-	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};
-
-	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
-	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
-	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};
-
-	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
-	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
-    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);
-
-    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
-    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);
-
-    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
-    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);
-
-    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
-    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);
-
-    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
-    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);
-
-    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
-    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);
-
-    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
-    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);
-
-    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
-    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);
-
-    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
-    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);
-
-    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
-    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);
-
-    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
-    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);
-
-    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
-    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);
-
-    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
-    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);
-
-    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
-    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);
-
-    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
-    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);
-
-    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
-    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);
-
-    \end{tikzpicture}
-    }
-    \caption{TF1: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 4.}
-    \label{fig:tf1}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-
     \begin{tikzpicture}
@@
     \end{tikzpicture}
-    }
-    \caption{TF2: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 16.}
-    \label{fig:tf2}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.5cm, font=\boldmath];
-
-    \node[circle, draw=black, thick]  (0) at (0,0) [state] {$1$};
-    \node[circle, draw=black, thick]  (1) at ($(0)+(0,2)$) [state] {$2$};
-    \node[circle, draw=black, thick]  (2) at ($(1)+(2,1.5)$) [state] {$3$}; 
-    \node[circle, draw=black, thick]  (3) at ($(2)+(3,0)$) [state] {$4$};
-    \node[circle, draw=black, thick]  (4) at ($(1)+(8,0)$) [state] {$5$};  
-    \node[circle, draw=black, thick]  (5) at ($(0)+(8,0)$) [state] {$6$};
-    \node[circle, draw=black, thick]  (6) at ($(3)+(0,-4.5)$) [state] {$7$};
-    \node[circle, draw=black, thick]  (7) at ($(2)+(0,-4.5)$) [state] {$8$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-
-    \draw (0) edge[out=-45, in=-100, loop, thick] node [below] {$C/C$} (0);
-    \draw (6) edge[out=-45, in=-100, loop, thick] node [below] {$C/D$} (6);
-    \draw (6) edge[out=190, in=135, loop, thick] node [below, yshift=-0.5cm] {$D/D$} (6);
-    \draw (7) edge[out=190, in=135, loop, thick] node [above, xshift=1cm] {$C/D$} (7);
-    \draw (2) edge[out=190, in=135, loop, thick] node [left] {$D/D$} (2);
-
-    \draw (2) edge[out=0,in=180,->,thick] node [above] {$C/C$} (3);
-    \draw (3) edge[out=-35,in=170,->,thick] node [above right] {$C/D$} (4);
-    \draw (5) edge[out=-135,in=0,->,thick] node [below] {$C/C$} (6);
-
-    \draw (0) edge[out=45,in=-135,->,thick] node [above, rotate=45, xshift=2cm, yshift=-0.5cm] {$D/C$} (3);
-
-    \draw (1) edge[out=-45,in=180,->,thick] node [below right, xshift=2cm] {$C/D$} (5);
-    \draw (1) edge[out=-135,in=135,->,thick] node [left] {$D/C$} (0);
-    \draw (3) edge[out=-90,in=90,->,thick] node [above, rotate=90] {$D/D$} (6);
-    \draw (4) edge[out=90,in=0,->,thick] node [above] {$C/C$} (3);
-    \draw (4) edge[out=180,in=0,->,thick] node [above left, xshift=-2.5cm] {$D/D$} (1);
-    \draw (5) edge[out=135,in=-45,->,thick] node [below, rotate=-45] {$D/D$} (3);
-    \draw (7) edge[out=-90,in=-90,->,thick] node [below] {$D/C$} (5);
-    \end{tikzpicture}
-    \caption{TF3: an 8 state finite state machine.}
-    \label{fig:tf3}
-\end{figure}
-
-As opposed to the previously described strategies, these strategies were trained
-with the objective function of \textit{mean fixation probabilities for Moran
-processes} starting at initial population states consisting of \(N/2\)
-individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the Axelrod library:
-
-\begin{itemize}
-	\item TF1 \(N=12\), 0\% noise.
-	\item TF2 \(N=10\), 0\% noise.
-	\item TF3 \(N=8\), 1\% noise.
-\end{itemize}
-
-The trained algorithms
-were run for fewer than 50 generations. Training data for this is available at
-\cite{data}.
-
-TF1 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
-achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
-very similar to a strategy known as ``Collective Strategy'', which has a
-handshake of CD and cooperates with opponents that matched the handshake
-until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
-Collective Strategy was specifically designed for evolutionary processes.
-
-TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
-Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
-can be rescued after a failed handshake by a complex sequence of plays
-which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
-GTFT, and a few others with low probability. TF2 defects against all other
-players in the study, barring
-unusual cases arising from particular randomizations. Fig~\ref{fig:tf2} shows
-all 16 states of the strategy (states 6 and 7 are not reachable).
-
-TF3 cooperates and defects with
-various cycles depending on the opponent's actions. TF3 will mutually
-cooperate with any strategy and only tolerates a few defections before
-defecting for the rest of match. It is similar to but not exactly the same as
-Fool Me Once, a strategy that cooperates until the opponent has defected twice
-(not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism. Fig~\ref{fig:tf3} shows
-all 8 states of the strategy produced by the training process (states 3 and 8
-are not reachable).
-
-For both TF1 and TF2 a handshake
-mechanism naturally emerges from the structure of the underlying finite state
-machine. This behavior is an outcome of the evolutionary process and is in no
-way hard-coded or included via an additional mechanism.
-
-\begin{table}[!hbtp]
-    \centering
-        \scalebox{0.7}{
-            \begin{tabular}{lrrrrrrrrrrrrrrrr}
-            \toprule
-            Memory Depth &   0   &   1   &   2   &   3   &   4   &   5   &   6   &   9   &   10  &   11  &   12  &   16  &   20  &   40  &   200 &  \(\infty\)   \\
-            \midrule
-            Count &     3 &    29 &    12 &     8 &     2 &     6 &     1 &     1 &     5 &     1 &     1 &     2 &     2 &     2 &     1 &    88 \\
-            \bottomrule
-            \end{tabular}
-        }
-        \caption{Memory depths}
-        \label{tbl:memory_depth_count}
-\end{table}
-
-\subsection*{Data collection}
-
-Each strategy pair is run for 1000 repetitions of the Moran process to fixation
-with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
-1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
-computed for each combination of starting distribution and value of \(N\).  The
-Axelrod library can carry out exact simulations of the Moran process. Since some
-of the strategies have a high computational cost or are stochastic, samples are
-taken from a large number of 200 turn match outcomes for the pairs of players
-for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
-matches is used). This approach was verified to agree with unsampled
-calculations to a high degree of accuracy in specific cases.  This is described
-in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.
-
-\begin{algorithm}[!hbtp]
-        \caption{Data Collection}
-        \label{alg:data_collection}
-          \begin{algorithmic}[1]
-            \FOR{player\_one \textbf{in} players\_list}
-              \FOR{player\_two \textbf{in} (players\_list - player\_one)}
-                \STATE pair $\gets$ (player\_one, player\_two)
-                \FOR{starting\_population\_distributions \textbf{in} [$(1, N-1), (\frac{N}{2}, \frac{N}{2}), (N-1, 1)]$}
-                \WHILE {repetitions $\leq 1000$}
-                \STATE \textbf{simulate} moran process (pair, starting distribution)
-                \ENDWHILE
-                \STATE\textbf{yield} fixation probabilities
-                \ENDFOR
-              \ENDFOR
-            \ENDFOR
-          \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[!hbtp]
-        \caption{Moran process}
-        \label{alg:moran_process}
-          \begin{algorithmic}[1]
-          \STATE initial population $\gets$ (pair, starting distribution) \
-          \STATE population $\gets$ initial population
-
-            \WHILE {population not uniform}
-              \FOR{player in population}
-              \FOR{opponent in (population - player)}
-                \STATE match $\gets$ (player, opponent) 
-                \STATE results $\gets$ stochastic\_cache (200 round match)
-                \ENDFOR
-              \ENDFOR
-              \STATE population $\gets$ sorted(results)
-              \STATE parent $\gets$ selected randomly in proportion to its total match payoffs
-              \STATE offspring $\gets$ parent
-              \STATE kill off $\gets$ uniformly random player from population
-              \STATE population $\gets$ offspring replaces kill off
-            \ENDWHILE
-          \end{algorithmic}
-\end{algorithm}
-
-The next section will further validate the methodology by comparing
-simulated results to analytical results in a few selected cases. The main
-results of this
-manuscript are presented in which will
-present a detailed analysis of all the data generated. Finally,
-a discussion and conclusion will offer future avenues for the work
-presented here.
-
-\section*{Results}
-
-\subsection*{Validation}
-
-As described in \cite{Nowak} consider the payoff matrix:
-
-\begin{equation}\label{equ:payoff_matrix}
-    M = \begin{pmatrix}
-        a, b\\
-        c, d
-        \end{pmatrix}
-\end{equation}
-
-The expected payoffs of \(i\) players of the first type in a population with \(N
-- i\) players of the second type are given by:
-
-\begin{equation}\label{equ:expected_payoff_one}
-    f_i = \frac{a(i - 1) + b(N - i)}{N - 1}
-\end{equation}
-
-\begin{equation}\label{equ:expected_payoff_two}
-    g_i = \frac{ci + d(N - i - 1)}{N - 1}
-\end{equation}
-
-The transitions within the birth death process that underpins the Moran process
-are then given by:
-
-\begin{align}
-    p_{i, i+1}&= \frac{if_i}{if_i+(N-i)g_i}\frac{N-i}{N}\label{equ:p_up}\\
-    p_{i, i-1}&= \frac{(N-i)g_i}{if_i+(N-i)g_i}\frac{i}{N}\label{equ:p_down}\\
-    p_{ii} &= 1 - p_{i, i+1} - p_{i, i-1}\label{equ:p_stay}
-\end{align}
-
-Using this the fixation probability
-of the first strategy in a population of \(i\) individuals of the first type
-and \(N-i\) individuals of the second, is given by \cite{Nowak2017}:
-
-\begin{equation}\label{equ:fixation_probability}
-x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}
-      \prod_{k=1}^{j}\gamma_j}
-\end{equation}
-
-where:
-
-\[
-\gamma_j = \frac{p_{j, j-1}}{p_{j, j+1}}
-\]
-
-A neutral strategy will have fixation probability $x_i = i/N$.
-
-Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
-confidence interval computed using an asymptotic normal approximation is also
-included \cite{brown2001interval}).
-The points represent the simulated
-values and the line shows the theoretical value. Note that these are
-deterministic strategies and show a good match between the expected value
-of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
-values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
-fact that the theoretic and simulated values are a good match.
-
-Fig~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
-good match (confirmed with a \(t\)-test in
-Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
-a given interaction between two IPD strategies can be summarised with a set of
-utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
-strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
-opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
-and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
-given pair and can be quite a complex endeavour for stochastic strategies with
-long memory: this is not necessary for the purposes of this work.  All data
-generated for this validation exercise can be found at~\cite{data}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
-    \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textit{deterministic} strategies: Alternator and
-         Cooperator. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.89942 &                0.89942 &                0.89942 \\
-          4 &          0.16344 &                0.74768 &                0.85877 \\
-          6 &          0.65406 &                0.84051 &                0.51992 \\
-          8 &          0.92617 &                0.45748 &                0.38604 \\
-         10 &          0.03505 &                0.37115 &                0.60635 \\
-         12 &          0.96697 &                0.20790 &                0.18124 \\
-         14 &          0.08126 &                0.63771 &                0.76246 \\
-         16 &          0.59434 &                0.07697 &                0.42520 \\
-         18 &          0.05339 &                0.47126 &                0.94814 \\
-         20 &          0.30805 &                0.79795 &                0.82381 \\
-        \bottomrule
-        \end{tabular}
-
-    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{deterministic} strategies: Alternator and
-    Cooperator.}
-    \label{tab:comparison_deterministic}
-\end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
-    \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textit{stochastic} strategies:
-             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_stochastic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.05372 &                0.05372 &                0.05372 \\
-          4 &          0.34188 &                0.00940 &                0.00005 \\
-          6 &          0.16510 &                0.00000 &                0.00000 \\
-          8 &          0.03451 &                0.00000 &                0.00000 \\
-         10 &          0.00543 &                0.00000 &                0.00000 \\
-         12 &          0.19646 &                0.00000 &                0.00000 \\
-         14 &          0.00814 &                0.00000 &                0.00000 \\
-         16 &          0.01038 &                0.00000 &                0.00000 \\
-         18 &          0.39556 &                0.00000 &                0.00000 \\
-         20 &          0.00030 &                0.00000 &                0.00000 \\
-        \bottomrule
-        \end{tabular}
-    \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{stochastic} strategies: Calculator and
-    Arrogant Q Learner.}
-    \label{tab:comparison_stochastic}
-\end{table}
-
-\subsection*{Empirical results}
-
-This section outlines the data analysis carried out, all data for this study is
-available at~\cite{data}.
-
-\begin{itemize}
-    \item First the specific case of
-        \(N=2\) is considered.
-    \item The effect of
-        population size on the ability of a strategy to invade another
-        population is investigated. This will highlight how complex strategies with long
-        memories outperform simpler strategies.
-    \item Then a similar investigation of the
-        ability to defend against an invasion is given.
-    \item Finally the relationship
-        between performance for differing population sizes as well as
-        taking a close look at zero determinant strategies \cite{Press2012} is
-        analysed.
-\end{itemize}
-
-\subsubsection*{The special case of \(N=2\)}
-
-When $N=2$ the fixation probabilities of the Moran process are effectively measures
-of the distribution of  relative
-mean payoffs over all possible matches between two players. The strategy
-that scores higher than the other more often will fixate more often. For \(N=2\)
-the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in the following sections.
-The top 16 (10\%) strategies are
-shown in
-
-Table~\ref{tbl:summary_top_2} and figures showing the performance of all
-strategies are available in the appendix.
-The top five ranking strategies are:
-
-\begin{enumerate}
-    \item The top strategy is the Collective Strategy (CS) which has a simple
-        handshake mechanism described above.
-    \item Defector: it always defects. Since it has no interactions with other
-        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
-    \item Aggravater, which plays like Grudger (responding to any
-        defections with unconditional defections throughout) however starts by
-        playing 3 defections.
-    \item Predator, a finite state machine described in \cite{Ashlock2006}.
-    \item Handshake, a slightly less aggressive version of the Collective
-        Strategy \cite{Robson1990}. As long as the initial sequence is played
-        then it cooperates. Thus it will do well in a population consisting of
-        many members of itself just as the Collective Strategy does. The
-        difference is that CS will defect after the handshake if the opponent
-        defects while Handshake will not.
-\end{enumerate}
-
-It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
-for which a zero determinant strategy does appear in the top 10\% ranking
-strategies: ZD-extort-4. The performance of zero determinant strategies will be
-examined more closely.
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \scalebox{0.95}{
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &                  Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-        \midrule
-        1  &                      CS &  0.497 &  0.5020 &  0.6651 &   0.572 &  0.9908 &  0.993 &  0.1800 \\
-        2  &                Defector &  0.502 &  0.5020 &  0.6496 &   0.518 &  1.0000 &  1.000 &  0.1767 \\
-        3  &              Aggravater &  0.502 &  0.5020 &  0.6328 &   0.518 &  0.9790 &  0.999 &  0.1660 \\
-        4  &                Predator &  0.319 &  0.4980 &  0.6301 &   0.551 &  0.9870 &  0.993 &  0.1676 \\
-        5  &               Handshake &  0.006 &  0.4503 &  0.6240 &   0.524 &  0.9908 &  0.993 &  0.1889 \\
-        6  &                Prober 4 &  0.431 &  0.4620 &  0.6183 &   0.534 &  0.9579 &  0.958 &  0.1656 \\
-        7  &                     \textbf{TF1} &  0.430 &  0.4980 &  0.6171 &   0.544 &  0.9240 &  0.981 &  0.1345 \\
-        8  &                Prober 3 &  0.497 &  0.5011 &  0.6044 &   0.505 &  0.9930 &  0.993 &  0.1683 \\
-        9  &                     \textbf{TF2} &  0.324 &  0.5020 &  0.6026 &   0.565 &  0.8362 &  0.887 &  0.1092 \\
-        10 &                 Grudger &  0.497 &  0.5020 &  0.5996 &   0.502 &  0.9840 &  0.989 &  0.1695 \\
-        11 &       Better and Better &  0.388 &  0.3951 &  0.5980 &   0.514 &  0.9300 &  0.934 &  0.1865 \\
-        12 &                    MEM2 &  0.497 &  0.5001 &  0.5942 &   0.502 &  0.9840 &  0.987 &  0.1656 \\
-        13 &  Meta Hunter Aggressive &  0.247 &  0.2943 &  0.5933 &   0.517 &  0.9498 &  0.981 &  0.2013 \\
-        14 &                     \textbf{TF3} &  0.344 &  0.4971 &  0.5927 &   0.502 &  0.9790 &  0.982 &  0.1617 \\
-        15 &            Fool Me Once &  0.494 &  0.4980 &  0.5892 &   0.502 &  0.9790 &  0.982 &  0.1625 \\
-        16 &             ZD-Extort-4 &  0.497 &  0.5020 &  0.5867 &   0.584 &  0.6900 &  0.695 &  0.0724 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
-    \label{tbl:summary_top_2}
-\end{table}
-
-As will be demonstrated the results for
-\(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that zero determinant strategies should be
-effective for larger population sizes, but these analyses consider stationary
-behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
-The stationarity assumption allows for a deterministic payoff matrix
-leading to the conclusions about zero determinant strategies in the space
-of memory-one strategies that do not generalize to this context.
-
-% In the next sections close attention to
-% strategies who are strong invaders/resistors is given.
-
-\subsubsection*{Strong Invaders}
-
-In this section the focus is on the ability of a mutant strategy to invade: the
-probability of one individual of a given type successfully fixating in a
-population of \(N - 1\) other individuals, denoted by \(x_1\).
-
-The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
-figures showing the performance of all strategies is available in the
-appendix.
-
-\begin{table}[!hbtp]
-    \centering
-    \tiny
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
-            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
-            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
-            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
-            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
-            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
-            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
-            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
-            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
-            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
-            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
-            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
-            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
-            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
-            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
-            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
-            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
-            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
-            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
-            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
-            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
-            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
-            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
-            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
-            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
-            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
-            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
-            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
-            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
-            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
-            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
-            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
-            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
-            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
-            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
-            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
-            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
-            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
-            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
-            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
-            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
-            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
-            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
-            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_invade}
-\end{table}
-
-It can be seen that apart from CS, none of the strategies for \(N=2\)
-of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
-top performing strategies are:
-
-\begin{itemize}
-    \item Grudger (which only performs well for \(N=3\)), starts by cooperating
-        but will defect if at any point the opponent has defected.
-    \item MEM2, an infinite memory strategy that switches between TFT, TF2T, and
-        Defector \cite{Li2014}.
-    \item TF3, the finite state machine trained specifically for Moran processes
-        described.
-    \item Prober 4, a strategy which starts with a specific 20 move sequence of
-        cooperations and defections \cite{Prison1998}. This initial sequence serves
-        as approximate handshake.
-    \item  PSO Gambler and Evolved Lookerup 2 2 2: strategies that make use
-        of a lookup table mapping the first 2 moves of the opponent as well as
-        the last 2 moves of both players to an action.  PSO gambler is a
-        stochastic version of  Lookerup which maps those states to probabilities
-       of cooperating. Lookerup was described in \cite{Knight2016}.
-    \item The Evolved ANN strategies are neural networks that map a number of
-	    attributes (first move, number of cooperations, last move, etc.) to
-	    an action. Both of these have been trained using an evolutionary
-	    algorithm.
-    \item Evolved FSM 16 is a 16 state finite state machine trained to
-        perform well in tournaments.
-\end{itemize}
-
-Only one of the above strategies is stochastic although close inspection of the
-source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin Evolved Looker Up.
-PSO Gambler Mem1 is a stochastic memory one strategy that has been trained to
-maximise its utility and does perform well.
-Apart from TF3, the finite state machines trained specifically for
-Moran processes do not appear in the top 5, while strategies trained for
-tournaments do. This is due to the nature of invasion: most of the opponents
-will initially be different strategies. The next section will consider the
-converse situation.
-
-\subsubsection*{Strong resistors}
-
-In addition to identifying good invaders, strategies resistant to invasion by
-other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy.
-
-Table~\ref{tbl:top_resist} shows the top strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
-for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies previously discussed perform well for high \(N\).
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
-            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
-            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
-            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
-            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
-            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
-            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
-            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
-            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
-            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
-            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
-            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
-            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
-            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
-            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
-            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
-            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
-            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
-            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
-            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
-            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
-            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
-            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
-            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
-            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
-            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
-            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
-            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
-            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
-            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
-            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
-        \midrule
-        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
-        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
-        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
-        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
-        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
-        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
-        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
-        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
-        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
-        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
-        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
-        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
-        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
-        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
-        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
-        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
-        \bottomrule
-        \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_resist}
-\end{table}
-
-Interestingly none of these strategies are stochastic: this is explained by the
-value of not provoking typically cooperative opponent strategies with
-speculative defections. This includes opponents using the same strategy.  Acting
-stochastically increases the chance of reducing the score of individuals of the
-same type in a Moran process.  However it is possible to design a strategy with
-a stochastic or error-correcting handshake that is an excellent resistor even in
-noisy environments \cite{Lee2015}.
-
-There are only two new strategies that appear in the top ranks for
-\(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
-resistors. They all have handshakes, and whilst the handshakes of CS and
-Handshake (which ranks highly for the smaller values of \(N\)) were
-programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
-process without any priming.
-
-As described previously the strategies trained with
-the payoff maximizing objective are among the best invaders in the library
-however they are not as resistant to invasion as the strategies trained using a
-Moran objective function. These strategies include trained finite state machine
-strategies, but they do not appear to have handshaking mechanisms. Therefore it
-is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
-handshakes for high invasion resistance. TF3 is a better total payoff maximizer
-which makes it a better invader along with the strategies
-trained to maximize total payoff since successful fitness proportionate selection
-is necessary for invasion. Training with an objective with initial population
-mix other than $(N/2, N/2)$ may favor invasion or resistance.
-
-The payoff maximizing strategies typically will not defect before the opponent's
-first defection, possibly because the training strategy collection contains some
-strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
-for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically for handshaking strategies
-it is advantageous to defect (as a signal)
-in order to achieve mutual cooperation with opponents using the same strategy
-but not with other opponents. Nevertheless an evolutionary process is able to
-tunnel through the costs and risks associated with early defections to find more
-optimal solutions, so it is not surprising in hindsight that handshaking
-strategies emerge from the evolutionary training process.
-
-A handshake requires at least one defection and there is
-selective pressure to defect as few times as possible to achieve the
-self-recognition mechanism. It is also unwise to defect on the first move as
-some strategies additionally retaliate in response to first round defections. So the
-handshakes used by TF1, TF2, and CS are in some sense optimal.
-
-It is evident through
-the work presented that performance of strategies not only depends
-on the initial population distribution but also that there seems to be a
-difference depending on whether or not \(N>2\). This will be explored further in
-the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also
-considering
-\(x_{N/2}\).
-
-\subsubsection*{The effect of population size}
-
-Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
-and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
-strategies:
-
-\begin{itemize}
-    \item The strategies that ranked highly for \(N=2\);
-    \item The strategies that ranked highly for \(N=14\);
-    \item The zero determinant strategies.
-\end{itemize}
-
-The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
-expected since, as described previously these strategies
-were trained in an initial population of \((N/2, N/2)\) individuals.
-
-For all starting populations
-\(i\in\{1, N/2, N-1\}\) the ranks of strategies are relatively stable across the
-different values of \(N>2\) however for \(N=2\) there is a distinct difference.
-This highlights that there is little that can be inferred about the evolutionary
-performance of a strategy in a large population from its performance in a small
-population. This is confirmed by the performance of the zero determinant strategies: while
-some do rank relatively highly for \(N=2\) (ZD-Extort-4 has rank 16) this rank
-does not translate to larger populations.
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                         Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                           CS &    1 &    1 &    2 &   11 &    9 &   11 &   13 &   21 &   16 &   22 &   17 &   25 &   23 \\
-                     Defector &    2 &   43 &   80 &   91 &   89 &   87 &   87 &  103 &   97 &  105 &   94 &  103 &  101 \\
-                   Aggravater &    3 &   50 &   89 &   99 &  102 &  103 &  108 &  113 &  114 &  115 &  115 &  116 &  117 \\
-                     Predator &    4 &    8 &   24 &   35 &   28 &   33 &   31 &   43 &   36 &   43 &   34 &   45 &   35 \\
-                    Handshake &    5 &   17 &   40 &   46 &   43 &   46 &   46 &   49 &   48 &   49 &   47 &   50 &   49 \\
-        \midrule
-               Evolved FSM 16 &   31 &   11 &    6 &    2 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-            PSO Gambler 2\_2\_2 &   29 &   14 &   10 &    6 &    4 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-         EvolvedLookerUp2\_2\_2 &   33 &   18 &   11 &    9 &   10 &    6 &    6 &    5 &    3 &    5 &    3 &    3 &    3 \\
-                  Evolved ANN &   20 &   10 &    8 &    7 &    8 &    5 &    3 &    3 &    4 &    3 &    4 &    4 &    4 \\
-                Evolved ANN 5 &   21 &    9 &    7 &    8 &    7 &    4 &    5 &    4 &    5 &    4 &    5 &    5 &    5 \\
-        \midrule
-                          \textbf{TF1} &    7 &   13 &   33 &   38 &   30 &   39 &   42 &   46 &   42 &   46 &   41 &   46 &   46 \\
-                          \textbf{TF2} &    9 &   19 &   29 &   33 &   19 &   28 &   29 &   38 &   27 &   34 &   26 &   32 &   30 \\
-                          \textbf{TF3} &   14 &    4 &    5 &    5 &    6 &    9 &   11 &   11 &   12 &   14 &   13 &   13 &   16 \\
-        \midrule
-                  ZD-Extort-4 &   16 &   81 &  107 &  120 &  135 &  136 &  142 &  140 &  142 &  142 &  144 &  144 &  145 \\
-               ZD-Extort-2 v2 &   41 &  105 &  126 &  140 &  152 &  152 &  153 &  152 &  153 &  153 &  153 &  152 &  153 \\
-                  ZD-Extort-2 &   43 &  107 &  125 &  139 &  151 &  151 &  152 &  153 &  152 &  152 &  152 &  153 &  152 \\
-                     ZD-SET-2 &  100 &  111 &  117 &  117 &  122 &  127 &  131 &  128 &  131 &  131 &  130 &  132 &  131 \\
-                    ZD-GTFT-2 &  112 &   92 &   82 &   80 &   81 &   82 &   84 &   72 &   81 &   71 &   78 &   72 &   70 \\
-                     ZD-GEN-2 &  113 &   96 &   87 &   83 &   85 &   88 &   90 &   82 &   87 &   82 &   86 &   83 &   91 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_invade}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                   Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-               Defector &    2 &   29 &   55 &   79 &   94 &   97 &   98 &   98 &  102 &  101 &  103 &  100 &  102 \\
-             Aggravater &    3 &   42 &   71 &   97 &  101 &  106 &  107 &  111 &  113 &  113 &  116 &  115 &  115 \\
-               Predator &    4 &    2 &    3 &    3 &    3 &    4 &    4 &    4 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    4 &    5 &    5 &    5 &    5 &    5 &    6 &    6 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF1} &    7 &    3 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-                    \textbf{TF2} &   10 &    5 &    4 &    4 &    4 &    3 &    3 &    3 &    3 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    6 &    6 &    6 &    6 &    6 &    6 &    5 &    5 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   13 &    9 &   10 &   11 &   11 &   11 &   13 &   14 &   13 &   13 &   13 &   13 &   13 \\
-        \midrule
-            ZD-Extort-4 &   19 &   68 &   98 &  106 &  108 &  114 &  115 &  115 &  118 &  118 &  117 &  118 &  117 \\
-         ZD-Extort-2 v2 &   49 &   98 &  111 &  121 &  123 &  124 &  124 &  130 &  130 &  132 &  134 &  132 &  134 \\
-            ZD-Extort-2 &   50 &   97 &  112 &  123 &  124 &  125 &  123 &  126 &  131 &  131 &  132 &  133 &  133 \\
-               ZD-SET-2 &  108 &  105 &  104 &  104 &  103 &  103 &  100 &  100 &  101 &   99 &   98 &   98 &   98 \\
-              ZD-GTFT-2 &  112 &   95 &   88 &   84 &   75 &   72 &   71 &   73 &   71 &   71 &   67 &   68 &   68 \\
-               ZD-GEN-2 &  114 &   96 &   89 &   86 &   77 &   75 &   72 &   74 &   72 &   72 &   68 &   69 &   69 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_resist}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-        \begin{tabular}{lrrrrrrr}
-        \toprule
-                   Size &      2 &      4 &      6 &      8 &     10 &     12 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    2 \\
-               Defector &    2 &   78 &   99 &  106 &  110 &  113 &  120 \\
-             Aggravater &    3 &   91 &  105 &  111 &  122 &  125 &  128 \\
-               Predator &    4 &    2 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    6 &    5 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF2} &    9 &    4 &    3 &    2 &    2 &    2 &    1 \\
-                    \textbf{TF1} &    7 &    3 &    2 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    5 &    6 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   14 &    8 &    8 &    8 &    8 &    8 &    8 \\
-        \midrule
-            ZD-Extort-4 &   16 &  102 &  117 &  129 &  141 &  143 &  145 \\
-         ZD-Extort-2 v2 &   41 &  118 &  135 &  151 &  152 &  152 &  153 \\
-            ZD-Extort-2 &   43 &  117 &  136 &  149 &  151 &  151 &  152 \\
-               ZD-SET-2 &  100 &  110 &  110 &  108 &  106 &  106 &  108 \\
-              ZD-GTFT-2 &  112 &   82 &   80 &   77 &   75 &   75 &   74 \\
-               ZD-GEN-2 &  113 &   85 &   81 &   82 &   79 &   77 &   76 \\
-        \bottomrule
-        \end{tabular}
-    \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_coexist}
-\end{table}
-
-Fig~\ref{fig:correlation_coefficients} shows the correlation coefficients
-of the ranks of strategies in differing population size. How well a strategy
-performs in any Moran process for \(N>2\) has
-little to do with the performance for \(N=2\). This illustrates why the strong
-performance of zero determinant strategies predicted in \cite{Press2012} does
-not extend to larger populations. This was discussed theoretically in
-\cite{Adami2013} and observed empirically in these simulations.
-
-\begin{figure}[!htbp]
-    \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
-        \caption{Rank based on \(x_1\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
-        \caption{Rank based on \(x_{N - 1}\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
-        \caption{Rank based on \(x_{N/2}\)}
-    \end{subfigure}
-    \caption{Heatmap of correlation coefficients of rankings by population size.}
-    \label{fig:correlation_coefficients}
-\end{figure}
-
-\section*{Discussion}
-
-Training strategies to excel
-at the Moran process leads to the evolution of cooperation, but only with like
-individuals in the case of TF1 and TF2. This may have significant implications
-for various biological and social phenomena such as
-human social interactions, particularly the evolution of ingroup/outgroup mechanisms
-and other sometimes costly rituals that reinforce group behavior.
-
-While TF1 and TF2 are competent invaders, the best invaders
-in the study do not appear to employ strict handshakes, and are generally
-cooperative strategies. TF3, which does not use a handshake, is a better invader
-than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
-of the same kind of training processes and is a better combined invader-resistor
-than the invaders that were trained previously to maximize payout.
-
-The strategies trained to maximize payoff in head-to-head matches are generally
-cooperative and are effective invaders.
-Combined with the fact that handshaking strategies are stronger resistors,
-this suggests that while maximizing individual payoff can lead to the evolution
-of cooperation, these strategies are not the most evolutionarily stable
-in the long run. A strategy with a handshaking mechanism is still capable of
-invading and is more resistant to subsequent invasions. Moreover, the
-best resistor of the payoff maximally trained strategies (Evolved Looker Up
-1\_1\_1),
-which always defects if the opponent defects in the first round, is effectively
-employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
-which emerged from training memory one strategies for the Moran process,
-also effectively employs a handshake of always cooperating, as it defects
-for the remainder of the match if the opponent ever defects.
-
-The insights that payoff maximizers are better invaders and that handshakers
-are better resistors suggests that a strategy
-aware of the population distribution could choose to become a handshaker at
-a critical threshold and use a strategy better for invasion when in the
-minority. Information about the population distribution was not available
-to our strategies. Previous work has showed that strategies able to retain
-memory across matches can infer the population distribution and act in such
-a manner, resulting in a strategy effective at invasion and resistance
-\cite{Lee2015}.
-
-We did not attempt other objective functions that may serve to select for both
-invasion and resistance better than training at a starting population of
-$(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
-improvement. Any handshake more sophisticated than always cooperate necessarily involves
-a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
-effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
-they need a longer or more strict handshake. But if this handshake involves
-a defection then likely the invasion ability is diminished for $N > 2$: the top
-invaders for larger $N$ are nice strategies that do not defect before their
-opponents. This is because good invaders need to maximize match payoff to benefit
-from fitness proportionate selection,
-and so in the absence of a handshake mechanism, knowledge of the population
-distribution, or some identifying label on the opponent,
-a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping dramatically in rank
-as the population size increases.
-
-We did, however, attempt to evolve CS using finite state machines and lookup table
-based players,
-which resulted in some very similar strategies. In particular we evolved a
-lookup strategy that had a handshake of DC and played TFT with other players
-after a correct handshake while defecting otherwise, which is quite close in
-function to CS (full grudging is not possible with a lookup table of limited
-depth).
-
-Finally we note that it may be possible to achieve similar results with smaller
-capacity finite state machine players.
-
-\section*{Conclusion}
-
-A detailed empirical analysis of 164 strategies of the IPD within a pairwise
-Moran process has been carried out. All \(\binom{164}{2}=13,366\) possible
-ordered pairs of strategies have been placed in a Moran process with different
-starting values allowing each strategy to attempt to invade the other.
-This is the largest such experiment carried out and has led to many insights.
-
-When studying evolutionary processes it is vital to consider \(N>2\) since
-results for \(N=2\) cannot be used to extrapolate performance in larger
-populations. This was shown both observationally
- but also by
-considering the correlation of the ranks in different population sizes.
-
-Memory one strategies do not perform as well as longer memory strategies in general
-in this study. Several longer memory strategies were high performers for invasion,
-particularly the strategies which have been trained using a number of reinforcement
-learning algorithms. Interestingly they have been trained to perform well in
-tournaments and not Moran processes specifically. In some cases these strategies
-utilize all the history of play (the neural network strategies and the lookup
-table strategies, the latter using the first round and some number of trailing rounds).
-
-There are no memory one strategies in the top 5 performing strategies
-for \(N>3\). Training memory-one strategies specifically for the Moran process
-typically led to Grudger / Grim, a memory-one strategy with
-four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
-The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
-training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
-For comparison, training for maximum score difference between the player and the
-opponent resulted in a strategy nearly the same as Grudger, with four-vector
-$(0.9459, 0, 0, 0)$ (not included in the study).
-
-One of the major findings discussed, is
-the ability of strategies with a handshake mechanism to resist invasion. This
-was not only revealed for CS (a human designed strategy) but also for
-two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
-process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. Fig~\ref{fig:cooperation_rates} shows the cooperation
-rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study.
-This corresponds to the fraction of cooperation played by that strategy observed
-in a given round (out of the first 15) where each matchup is repeated 10000 times to
-obtain the mean.
-
-While TF3
-does not have a strict handshake mechanism it is clear that all these strategies
-start a match by cooperating. It is then evident that TF3 cooperates more than
-the other strategies thus explaining the difference in performance. It is also
-clear that CS only cooperates with itself and Handshake: it is a very aggressive
-strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
-        \caption{TF1}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
-        \caption{TF2}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
-        \caption{TF3}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
-        \caption{CS}
-    \end{subfigure}
-    \caption{Cooperation rate per round (over 10000 repetitions). Rows
-        correspond to all the strategies considered in this work (ordered
-    alphabetically by name). Columns correspond to round of an IPD match.}
-    \label{fig:cooperation_rates}
-\end{figure}
-
-These findings are important for the ongoing understanding of
-population dynamics and offer evidence for some of the shortcomings of low
-memory which has started to be recognised by the community \cite{Hilbe2017}.
-
-All source code for this work has been written in a sustainable manner: it is
-open source, under version control and tested which ensures that all results can
-be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
-the processed data has also been properly archived and can be found
-at \cite{data}.
-
-There are many opportunities to build on this work. In particular, an analysis
-of the effect of noise should offer insights regarding the stability of the findings,
-particularly for the handshaking strategies. They may be less dominant for
-larger amounts of noise since the handshaking mechanisms may become brittle.
-There are many other variations to explore including populations with more
-than one type, spatial structure, and mutation.
-
-One final point to recognise: the large set of strategies used here does not in
-itself constitute an authoritative set. Whilst it is not only large but also very
-diverse, the results (and rankings) presented might change given a different set
-of strategies. A further piece of work could look at subgroups of strategies and
-how they fair against other subgroups. Note that because of the open nature of
-the work here (not only is the source code archived but so is the data) this and
-any other further analysis is possible to carry out.
-
-\section*{Acknowledgements}
-
-This work was performed using the computational facilities of the Advanced
-Research Computing @ Cardiff (ARCCA) Division, Cardiff University.
-
-A variety of software libraries have been used in this work:
-
-\begin{itemize}
-    \item The Axelrod library (IPD strategies and Moran processes)
-        \cite{axelrodproject}.
-    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
-    \item The pandas and numpy libraries (data manipulation)
-        \cite{mckinney2010data, walt2011numpy}.
-\end{itemize}
-
-\nolinenumbers
-
-\begin{thebibliography}{10}
-
-\bibitem{Adami2013}
-Christoph Adami and Arend Hintze.
-\newblock {Evolutionary instability of zero-determinant strategies demonstrates
-  that winning is not everything.}
-\newblock {\em Nature communications}, 4(1):2193, 2013.
-
-\bibitem{adami2016evolutionary}
-Christoph Adami, Jory Schossau, and Arend Hintze.
-\newblock {Evolutionary game theory using agent-based methods}.
-\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
-
-\bibitem{affenzeller2009genetic}
-Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
-\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
-  Practical Applications}.
-\newblock Numerical Insights. CRC Press, 2009.
-
-\bibitem{Nowak2017}
-Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
-  Shing-Tung Yau, and Martin~A Nowak.
-\newblock {Evolutionary dynamics on any population structure}.
-\newblock 544:227--230, March 2017.
-
-\bibitem{Ashlock2015}
-Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
-\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
-  Agents}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 7(1):53--65, 2015.
-
-\bibitem{Ashlock2008}
-Daniel Ashlock and Eun-Youn Kim.
-\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
-  dilemma strategies}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
-  2008.
-
-\bibitem{Ashlock2006}
-Wendy Ashlock and Daniel Ashlock.
-\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
-  with different population sizes}.
-\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
-  pages 297--304. IEEE, 2006.
-
-\bibitem{Ashlock2014}
-Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
-\newblock {The evolution of exploitation}.
-\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
-  Symposium on}, pages 135--142. IEEE, 2014.
-
-\bibitem{Axelrod1980a}
-Robert Axelrod.
-\newblock {Effective choice in the prisoner's dilemma}.
-\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
-
-\bibitem{Axelrod1980b}
-Robert Axelrod.
-\newblock {More Effective Choice in the Prisoner's Dilemma}.
-\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.
-
-\bibitem{Axelrod1984}
-Robert Axelrod.
-\newblock {\em The Evolution of Cooperation}.
-\newblock Basic books. Basic Books, 1984.
-
-\bibitem{Baek2016}
-{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
-  A}.
-\newblock {Comparing reactive and memory- one strategies of direct
-  reciprocity}.
-\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
-
-\bibitem{Banks1990}
-Jeffrey~S Banks and Rangarajan~K Sundaram.
-\newblock {Repeated games, finite automata, and complexity}.
-\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
-
-\bibitem{Beaufils1997}
-Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
-\newblock {Our meeting with gradual, a good strategy for the iterated
-  prisoner’s dilemma}.
-\newblock In {\em Proceedings of the Fifth International Workshop on the
-  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.
-
-\bibitem{brown2001interval}
-Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
-\newblock Interval estimation for a binomial proportion.
-\newblock {\em Statistical science}, pages 101--117, 2001.
-
-\bibitem{Andre2013}
-Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
-\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
-\newblock pages 1--6, 2013.
-
-\bibitem{Eckhart2015}
-Arnold Eckhart.
-\newblock Coopsim v0.9.9 beta 6.
-\newblock https://github.com/jecki/CoopSim/, 2015.
-
-\bibitem{Flood1958}
-Merrill~M Flood.
-\newblock {Some Experimental Games}, 1958.
-
-\bibitem{Frean1994}
-Marcus~R Frean.
-\newblock {The prisoner's dilemma without synchrony}.
-\newblock {\em Proceedings of the Royal Society of London B: Biological
-  Sciences}, 257(1348):75--79, 1994.
-
-\bibitem{Gaudesi2016}
-Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
-\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
-  dilemma tournaments}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 8(3):288--300, 2016.
-
-\bibitem{marc_harper_2017_824264}
-Marc Harper, Vince Knight, and Martin Jones.
-\newblock Axelrod-python/axelrod-dojo: v0.0.1.
-\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
-
-\bibitem{Harper2017}
-Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
-  Glynatsi, and Owen Campbell.
-\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
-  Prisoner's Dilemma}.
-\newblock arXiv:1707.06307, 2017.
-
-\bibitem{Hilbe2017}
-Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
-  Nowak.
-\newblock {Memory-n strategies of direct reciprocity}.
-\newblock {\em Proceedings of the National Academy of Sciences}, page
-  201621239, 2017.
-
-\bibitem{Hilbe2013}
-Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
-\newblock {Adaptive dynamics of extortion and compliance}.
-\newblock {\em PloS one}, 8(11):e77886, 2013.
-
-\bibitem{hunter2007matplotlib}
-John~D Hunter.
-\newblock {Matplotlib: A 2D graphics environment}.
-\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
-
-\bibitem{kendall2007iterated}
-Graham Kendall, Xin Yao, and Siang~Y Chong.
-\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
-\newblock Advances in natural computation. World Scientific, 2007.
-
-\bibitem{Knight2016}
-Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
-  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
-  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
-  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
-  Timothy Standen, Luis Visintini, and Karl Molden.
-\newblock {An Open Framework for the Reproducible Study of the Iterated
-  Prisoner ' s Dilemma}.
-\newblock 2016.
-
-\bibitem{data}
-Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
-\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
-  Self-Recognition Mechanisms: an empirical study of the Moran process for the
-  iterated Prisoner's dilemma using reinforcement learning}.
-\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
-
-\bibitem{Kraines1989}
-David Kraines and Vivian Kraines.
-\newblock {Pavlov and the prisoner's dilemma}.
-\newblock {\em Theory and decision}, 26(1):47--79, 1989.
-
-\bibitem{Kuhn2017}
-Steven Kuhn.
-\newblock Prisoner's dilemma.
-\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
-  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
-  edition, 2017.
-
-\bibitem{Lee2015}
-Christopher Lee, Marc Harper, and Dashiell Fryer.
-\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
-\newblock {\em Plos One}, 10(3):e0120625, 2015.
-
-\bibitem{Li2011}
-Jiawei Li, Philip Hingston, and Graham Kendall.
-\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
-  Dilemma Competitions}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 3(4):348--360, 2011.
-
-\bibitem{Li2009}
-Jiawei Li and Graham Kendall.
-\newblock {A strategy with novel evolutionary features for the iterated
-  prisoner's dilemma.}
-\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
-
-\bibitem{Li2014}
-Jiawei Li and Graham Kendall.
-\newblock {The effect of memory size on the evolutionary stability of
-  strategies in iterated prisoner's dilemma}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
-  2014.
-
-\bibitem{Prison1998}
-LIFL.
-\newblock Prison.
-\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
-
-\bibitem{Mathieu2015}
-Philippe Mathieu and Jean-Paul Delahaye.
-\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
-  Abstract)}.
-\newblock {\em 14th International Conference on Autonomous Agents and
-  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
-
-\bibitem{mckinney2010data}
-Wes McKinney et~al.
-\newblock Data structures for statistical computing in python.
-\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
-  445, pages 51--56. van der Voort S, Millman J, 2010.
-
-\bibitem{Mittal2009}
-Shashi Mittal and Kalyanmoy Deb.
-\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
-  multiple conflicting objectives}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
-  2009.
-
-\bibitem{Moran1957}
-Patrick A~P Moran.
-\newblock {Random Processes in Genetics}.
-\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
-  Society}, 54(1):60--71, 1957.
-
-\bibitem{Nachbar1992}
-John~H Nachbar.
-\newblock {Evolution in the finitely repeated prisoner's dilemma}.
-\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
-  1992.
-
-\bibitem{Nowak}
-Martin~A Nowak.
-\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
-\newblock Cambridge: Harvard University Press.
-
-\bibitem{Nowak1993}
-Martin~A Nowak and Karl Sigmund.
-\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
-  the Prisoner's Dilemma game.}
-\newblock {\em Nature}, 364(6432):56--58, 1993.
-
-\bibitem{Press2012}
-William~H Press and Freeman~J Dyson.
-\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
-  evolutionary opponent.}
-\newblock {\em Proceedings of the National Academy of Sciences of the United
-  States of America}, 109(26):10409--13, 2012.
-
-\bibitem{Prlic2012}
-Andreas Prlić and James~B Procter.
-\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
-\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
-
-\bibitem{axelrodproject}
-The~Axelrod project developers.
-\newblock Axelrod: v2.9.0.
-\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
-
-\bibitem{Robson1990}
-Arthur~J Robson.
-\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
-  handshake}.
-\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
-
-\bibitem{Sandve2013}
-Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
-\newblock {Ten Simple Rules for Reproducible Computational Research}.
-\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
-
-\bibitem{Stewart2012}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  109(26):10134--10135, 2012.
-
-\bibitem{stewart2013extortion}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {From extortion to generosity, evolution in the iterated prisoner’s
-  dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  110(38):15348--15353, 2013.
-
-\bibitem{Tzafestas2000}
-Elpida Tzafestas.
-\newblock {Toward adaptive cooperative behavior}.
-\newblock {\em From Animals to animals: Proceedings of the 6th International
-  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
-  2000.
-
-\bibitem{PD2017}
-Unkwown.
-\newblock www.prisoners-dilemma.com.
-\newblock http://www.prisoners-dilemma.com/, 2017.
-
-\bibitem{Berg2015}
-Pieter Van~den Berg and Franz~J Weissing.
-\newblock {The importance of mechanisms for the evolution of cooperation}.
-\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
-  Society, 2015.
-
-\bibitem{walt2011numpy}
-St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
-\newblock {The NumPy array: a structure for efficient numerical computation}.
-\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
-
-\bibitem{West2016}
-Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
-\newblock {The prisoner’s dilemma as a cancer model}.
-\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
-
-\bibitem{Wilson2014}
-Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
-  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
-  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
-\newblock {Best Practices for Scientific Computing}.
-\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
-
-\bibitem{Axelrod1995}
-Jianzhong Wu and Robert Axelrod.
-\newblock {How to cope with noise in the iterated prisoner's dilemma}.
-\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
-
-\end{thebibliography}
-
-\appendix
-
-\section{Appendix A: List of players}\label{app:list_of_players}
-
-\footnotesize
-\begin{enumerate}
-\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
-\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
-\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
-\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
-\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
-\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
-\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
-\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
-\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
-\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980a}
-\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
-\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006}
-\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006}
-\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
-\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
-\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Banks1990, Beaufils1997, Berg2015, Li2011}
-\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
-\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
-\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
-\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
-\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Stewart2012}
-\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
-\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
-\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
-\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980a}
-\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
-\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006}
-\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
-\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
-\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980a, Tzafestas2000}
-\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
-\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
-\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
-\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
-\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
-\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
-\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
-\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
-\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
-\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
-\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
-\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
-\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
-\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
-\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a}
-\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980a}
-\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
-\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\end{enumerate}
-
-\section{Appendix B: Supplementary figures}
-
-\begin{itemize}
-    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
-for each strategy. The mean and error bars are shown against the collection of
-all opponents.
-
-    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
-\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
-the collection of all opponents.
-
-    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
-ranks of each strategy according to mean absorption probability across all
-population sizes.
-\end{itemize}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
-    \label{invasion-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
-    \label{invasion-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
-    \label{resistance-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
-    \label{resistance-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
-    \label{fig:ranks_v_size_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
-    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_coexist}
-\end{figure}
-
 \end{document}

### 2018-08-10 tf3.tex
Re rename all images.

--- 2018-04-05 plos/main.tex
@@
-% Template for PLoS
-% Version 3.4 January 2017
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended
-% to minimize problems and delays during our production
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% Once your paper is accepted for publication,
-% PLEASE REMOVE ALL TRACKED CHANGES in this file
-% and leave only the final text of your manuscript.
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file.
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column.
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8x]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% color can be used to apply background shading to table cells only
-\usepackage[table]{xcolor}
-
-% array package and thick rules for tables
-\usepackage{array}
-
-% create "+" rule type for thick vertical lines
-\newcolumntype{+}{!{\vrule width 2pt}}
-
-% create \thickcline for thick horizontal lines of variable length
-\newlength\savedwidth
-\newcommand\thickcline[1]{%
-  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-  \cline{#1}%
-  \noalign{\vskip\arrayrulewidth}%
-  \noalign{\global\arrayrulewidth\savedwidth}%
-}
-
-% \thickhline command for thick horizontal lines that span the table
-\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
-\hline
-\noalign{\global\arrayrulewidth\savedwidth}}
-
-% Remove comment for double spacing
-%\usepackage{setspace}
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-\renewcommand{\figurename}{Fig}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\setlength{\headheight}{27.023pt}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
-\usepackage{algorithm,algorithmic}
-\usepackage{amsmath}
-\usepackage{authblk}
-\usepackage{booktabs}
-\usepackage{booktabs}
-\usepackage{fancyvrb}
-\usepackage{graphicx}
-\usepackage{hyperref}
-\usepackage{multicol}
-\usepackage{pdflscape}
-\usepackage{standalone}
-\usepackage{subcaption}
+\documentclass[crop,tikz]{standalone}
 \usepackage{tikz}
-\usepackage{xstring}
-
 \usetikzlibrary{calc, shapes, patterns}
-
 \begin{document}
-\vspace*{0.2in}
-
-% Title must be 250 characters or less.
-\begin{flushleft}
-{\Large
-\textbf\newline
-{Evolution reinforces cooperation with the emergence of self-recognition
- mechanisms: an empirical study of strategies in the Moran process for the
- iterated prisoner's dilemma }
-% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Vincent Knight\textsuperscript{1*\Yinyang},
-Marc Harper\textsuperscript{2\Yinyang},
-Nikoleta E. Glynatsi\textsuperscript{2\ddag},
-Owen Campbell\textsuperscript{3\ddag},
-\\
-\bigskip
-\textbf{1} Cardiff University, School of Mathematics, Cardiff, UK
-\\
-\textbf{2} Google Inc., Mountain View, CA, USA
-\\
-\textbf{3} Independent Researcher, Chester, UK
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-%
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-\ddag These authors also contributed equally to this work.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* knightva@cardiff.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-    We present insights and empirical results from an extensive numerical
-    study of the evolutionary dynamics of the iterated prisoner's dilemma.
-    Fixation probabilities for Moran processes are obtained
-    for all pairs of 164 different strategies including classics such as TitForTat, zero
-    determinant strategies, and many more sophisticated strategies.
-    Players with long memories and sophisticated behaviours outperform
-    many strategies that perform well in a two player setting. Moreover we
-    introduce several strategies trained with evolutionary algorithms to
-    excel at the Moran process. These strategies are excellent invaders
-    and resistors of invasion and in some cases naturally evolve handshaking
-    mechanisms to resist invasion. The best invaders were those trained
-    to maximize total payoff while the best resistors invoke handshake mechanisms.
-    This suggests that while maximizing individual payoff
-    can lead to the evolution of cooperation through invasion, the relatively
-    weak invasion resistance of payoff maximizing strategies are not as
-    evolutionarily stable as strategies employing handshake mechanisms.
-\linenumbers
-
-\section*{Introduction}
-
-The Prisoner's Dilemma (PD) \cite{Flood1958} is a fundamental two player game
-used to model a variety of strategic interactions. Each player chooses
-simultaneously and independently
-between cooperation (C) or defection (D). The payoffs of
-the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
-\end{pmatrix}$, where $T > R > P > S$ and $2R > T + S$. The PD is a one
-round game, but is commonly studied in a manner where the prior outcomes
-matter. This repeated form is called the Iterated Prisoner's
-Dilemma (IPD). As described in \cite{Axelrod1980a, Knight2016, Press2012} a
-number of strategies have been developed to take advantage of the history of
-play. Strategies referred to as zero determinant (ZD) strategies
-\cite{Press2012} can manipulate some players through extortionate mechanisms.
-
-The Moran Process \cite{Moran1957} is a model of
-evolutionary population dynamics that has been used to gain insights about the
-evolutionary stability in a number of settings.
-Several earlier
-works have studied iterated games in the context of the prisoner's dilemma
-\cite{Nowak, stewart2013extortion}, however these often make simplifying assumptions
-or are limited to classes of strategies
-such as memory-one strategies that only use the previous round of play.
-
-This manuscript provides a detailed numerical analysis of agent-based simulations
-of \textbf{164} complex and adaptive strategies for the
-IPD\@. This is made possible by the Axelrod library \cite{axelrodproject}, an
-effort to provide software for reproducible research for the IPD\@. The library
-now contains over 186 parameterized
-strategies including classics like TitForTat and WinStayLoseShift, as well as
-recent variants such as OmegaTFT, zero determinant and other memory one
-strategies, strategies based on finite state machines, lookup tables, neural
-networks, and other machine learning based strategies, and a collection of novel
-strategies. Not all strategies have been considered for this study: excluded
-are those that make use of knowledge of the number of turns in a match
-and others that have a high
-computational run time. The large number of strategies are available thanks to
-the open source nature of the project with over 50 contributors from around the
-world, made by programmers and researchers \cite{Knight2016}. Three of the considered
-strategies are finite state machines trained specifically for Moran processes
-(described further in the Methods section).
-
-In addition to providing a large collection of strategies, the Axelrod library
-can conduct matches, tournaments and population
-dynamics with variations including noise and spatial structure.
-The strategies and simulation frameworks are
-automatically tested to an extraordinarily high degree of coverage in accordance
-with best research software practices.
-
-Using the Axelrod library and the many strategies it contains, we obtain the
-probability with which a given strategy takes over a population (referred to as
-fixation probability) for all pairs of strategies, identifying those that are
-effective invaders and those resistant to invasion, for population sizes $N=2$
-to $N=14$. Moreover we present a number (16) of strategies that were created via
-reinforcement algorithms (evolutionary and particle swarm algorithms) that are
-among the best invaders and resistors of invasion known to date, and show that
-handshaking mechanisms naturally arise from these processes as an
-invasion-resistance mechanism.
-
-In 2016, work has argued that agent-based
-simulations can provide insights in evolutionary game theory not available
-via direct mathematical analysis~\cite{adami2016evolutionary}. The results
-and insights contained in this paper would be difficult to derive analytically.
-
-In particular the following questions are addressed:
-\begin{enumerate}
-    \item What strategies are good invaders?
-    \item What strategies are good at resisting invasion?
-    \item How does the population size affect these findings?
-\end{enumerate}
-
-While the results agree with some of the published literature, it is found that:
-
-\begin{enumerate}
- \item Zero determinant strategies are not effective invaders or defenders for $N > 2$
- \item Complex strategies can be effective, and in fact can naturally evolve
-     through evolutionary processes to outperform designed strategies.
- \item The strongest resistors specifically evolve or possess a handshake mechanism.
- \item Strong invaders are generally cooperative strategies that do not defect
- first but retaliate to varying degrees of intensity against strategies that defect.
- \item Strategies evolved to maximize their total payoff can be strong invaders
- and achieve mutual cooperation with many other strategies.
-\end{enumerate}
-
-\section*{Materials and methods}
-\subsection*{The Moran Process}
-
-A Moran process is a stochastic birth death process on a finite population in which the
-population size stays constant over time. Individuals are \textit{selected}
-according to a given fitness landscape. The fitness landscape in this work is
-defined as the total utility against all other individuals in the population.
-Once selected, the individual
-is reproduced and similarly another individual is chosen to be removed from the
-population (a uniform random selection is used). This is shown diagrammatically
-in Fig~\ref{fig:moran_process}. In some settings mutation is
-also considered but without mutation (the case considered in this work) this
-process will arrive at an absorbing state where the population is entirely made
-up of players of one strategy. The probability with which a given strategy,
-starting from a single individual takes
-over a population is called the \textit{fixation probability}. A more detailed
-analytic description of this is given later. In our
-simulations offspring do not inherit any knowledge or history from parent
-replicants.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.5}{
-
-\begin{tikzpicture}[scale=.9]
-	\node (A1) at (-1, -1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A2) at (-1, 1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A3) at (0, .2) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A4) at (.2, -.6) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (A5) at (.5, -0.1) [circle, pattern=north west lines, pattern
-        color=blue!70, draw=blue] {};
-	\node (B1) at (-1, -.2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B2) at (1, -.5) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B3) at (.5, .8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B4) at (-.6, .2) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-	\node (B5) at (.6, -.8) [circle, pattern=north east lines, pattern
-        color=red!70, draw=red] {};
-
-	\draw [->] (1, 0) -- (3, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-
-	\draw [->] (5.5, 0) -- (7.5, 0) node [above, pos=0.5] {Birth};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (B4) circle (.25cm);
-	\node (B6) at ($(B4) + (0.5, 0.5)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\draw [->, dotted, very thick] (B4) [out=90, in=180] to (B6);
-
-	\draw [->] (10, 0) -- (12, 0) node [above, pos=0.5] {Selection};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-
-	\draw [->] (14.5, 0) -- (16.5, 0) node [above, pos=0.5] {Death};
-
-	\node (A1) at ($(A1) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A2) at ($(A2) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (A3) at ($(A3) + (4.5, 0)$) {};
-	\node (A4) at ($(A4) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-    \node (A5) at ($(A5) + (4.5, 0)$) [circle, pattern=north west lines,
-        pattern color=blue!70, draw=blue] {};
-	\node (B1) at ($(B1) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B2) at ($(B2) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B3) at ($(B3) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B4) at ($(B4) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B5) at ($(B5) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-	\node (B6) at ($(B6) + (4.5, 0)$) [circle, pattern=north east lines,
-        pattern color=red!70, draw=red] {};
-
-	\draw [dotted, very thick] (A3) circle (.25cm);
-\end{tikzpicture}
-
-}
-    \caption{A diagrammatic representation of a Moran process.}
-    \label{fig:moran_process}
-\end{figure}
-
-The Moran process was initially introduced in \cite{Moran1957}. It has since
-been used in a variety of settings including the understanding of the spread of
-cooperative and non-cooperative behaviour such as cancer \cite{West2016} and the
-emergence of cooperative behaviour in spatial topologies \cite{Nowak2017}.
-However these works mainly consider relatively simple strategies. A few works
-looked at evolutionary stability of agent-based strategies within the Prisoner's Dilemma
-\cite{Li2014} but this is not done in the more widely used setting of the Moran
-process, rather in terms of infinite population stability. In \cite{Baek2016}
-Moran processes are studied in a theoretical framework for a small subset of
-strategies. The subset included memory one strategies: strategies that recall
-the events of the previous round only.
-
-Of particular interest are the zero determinant strategies introduced in
-\cite{Press2012}. It was argued in \cite{stewart2013extortion} that generous
-ZD strategies are robust against invading strategies. However, in \cite{Lee2015},
-a strategy using machine learning techniques was capable of resisting invasion
-and also able to invade any memory one strategy. In 2017, \cite{Hilbe2017}
-has investigated the effect of memory length on strategy performance and the
-emergence of cooperation but this is not done in a Moran process context and only
-considers specific cases of memory 2 strategies. In \cite{Adami2013} it was
-recognised that many zero determinant strategies do not fare well against
-themselves. This is a disadvantage for the Moran process where the best
-strategies cooperate well with other players using the same strategy.
-
-This work uses pair-wise Moran processes in a similar way to matches in the many
-IPD tournaments published since Axelrod's original work~\cite{Axelrod1980a}.
-A population-based perspective is given which adds additional
-evolutionary components to the IPD, namely the evolutionary dynamics of invasion
-and resistance.
-
-\subsection*{Strategies considered}\label{sec:strategies}
-
-To carry out this numerical experiment, 164
-strategies, listed (with their properties) in the Appendix,
-are used from the Axelrod library. There are
-43 stochastic and
-121 deterministic strategies. Their memory depth,
-defined by the number of rounds of history used by the strategy each round, is
-shown in Table~\ref{tbl:memory_depth_count}. The memory depth is infinite if the
-strategy uses the entire history of play (whatever its length). For example, a
-strategy that utilizes a handshaking mechanism where the opponent's actions on
-the first few rounds of play determines the strategies subsequent behavior would
-have infinite memory depth.
-
-A number of these strategies have been trained with reinforcement learning
-algorithms prior to this study and not specifically for the Moran process.
-
-\begin{itemize}
-    \item Evolved ANN: a neural network based strategy;
-    \item Evolved LookerUp: a lookup table based strategy;
-    \item PSO Gambler: a stochastic version of the lookup table based strategy;
-    \item Evolved HMM: a hidden Markov model based strategy.
-\end{itemize}
-
-Apart from the PSO Gambler strategy, which was trained using a particle swarm
-optimisation algorithm, these strategies are trained with an evolutionary
-algorithm that perturbs strategy parameters and optimizes the mean total score
-against all other opponents \cite{affenzeller2009genetic}. They were trained to
-win IPD tournaments by maximizing their mean total payoffs against a variety
-of opponents. Variation is
-introduced via mutation and crossover of parameters, and the best performing
-strategies are carried to the next generation along with new variants. Similar
-methods appear in the literature \cite{Ashlock2006}.
-There has also been some work on strategies using an evolutionary algorithm in real time:
-in~\cite{Gaudesi2016}
-an evolutionary algorithm is used to build a model of the opponent and attempt
-to exploit any potential weakness. In this work all strategies resulting from
-evolutionary algorithms are pre-trained.
-
-More information about each player can be obtained in the documentation for
-\cite{axelrodproject} and a detailed description of the performance
-of these strategies in IPD tournaments is described in~\cite{Harper2017}.
-
-All of the training code is archived at \cite{marc_harper_2017_824264}. This
-software is (similarly to the Axelrod library) available on
-github\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
-with documentation to
-train new strategies easily. Training
-typically takes less than 100 generations and can be completed within several
-hours on commodity hardware.
-
-There are three further strategies trained specifically for this study; Trained
-FSM 1, 2, and 3 (TF1 - TF3). These are based on finite state machines of 16, 16,
-and 8 states respectively. These are shown in Fig~\ref{fig:tf1},~\ref{fig:tf2}
-and~\ref{fig:tf3}), using the notation common in the literature where
-\(A_1/A_2\) is the action of the opponent \(A_1\) and the response of the player
-\(A_2\) as well as arrows corresponding to changes of state.
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (5) at (0, 0) [state] {$6$};
-	\node[circle, draw=black, thick] (2) at (4, 0) [state] {$3$};
-	\node[circle, draw=black, thick] (15) at (-2, -2) [state] {$16$};
-	\node[circle, draw=black, thick] (8) at ($(2)+(2,-2)$) [state] {$9$};
-	\node[circle, draw=black, thick] (10) at ($(15)+(4, 0)$) [state] {$11$};
-
-	\node[circle, draw=black, thick] (7) at ($(5)+(-1,-4)$) [state] {$8$};
-	\node[circle, draw=black, thick] (11) at ($(7)+(2, 0)$) [state] {$12$};
-
-	\node[circle, draw=black, thick] (9) at ($(10)+(0,-4)$) [state] {$10$};
-	\node[circle, draw=black, thick] (0) at ($(9)+(-5,0)$) [state] {$1$};
-	\node[circle, draw=black, thick] (14) at ($(9)+(5,0)$) [state] {$15$};
-
-	\node[circle, draw=black, thick] (1) at ($(0)+(0,-2)$) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at ($(1)+(2,0)$) [state] {$5$};
-	\node[circle, draw=black, thick] (6) at ($(4)+(4,0)$) [state] {$7$};
-	\node[circle, draw=black, thick] (13) at ($(6)+(2,0)$) [state] {$14$};
-
-	\node[circle, draw=black, thick] (3) at ($(4)+(0,-2)$) [state] {$4$};
-	\node[circle, draw=black, thick] (12) at ($(6)+(0,-2)$) [state] {$13$};
-
-    \coordinate[left of=0] (s);
-
-    \draw (s) edge[out=0, in=180, ->, thick] node [above] {$C$} (0);
-    \draw (0) edge[out=90, in=135, ->, thick] node [above left] {$C/C$} (7);
-    \draw (0) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (1);
-
-    \draw (1) edge[out=45, in=-135, ->, thick] node [left] {$C/D$} (11);
-    \draw (1) edge[out=45, in=-135, ->, thick] node [right] {$D/D$} (11);
-
-    \draw (2) edge[out=-45, in=135, ->, thick] node [above right] {$C/D$} (8);
-    \draw (2) edge[out=-45, in=135, ->, thick] node [below left] {$D/C$} (8);
-
-    \draw (3) edge[out=180, in=135, ->, thick, loop] node [left] {$C/C$} (3);
-    \draw (3) edge[out=0, in=180, ->, thick] node [below] {$D/D$} (12);
-
-    \draw (4) edge[out=0, in=180, ->, thick] node [above] {$C/C$} (6);
-    \draw (4) edge[out=-90, in=90, ->, thick] node [left] {$D/C$} (3);
-
-    \draw (5) edge[out=0, in=180, ->, thick] node [below, yshift=-1cm, xshift=2cm] {$D/D$} (8);
-    \draw (5) edge[out=-45, in=90, ->, thick] node [left, yshift=-0.8cm, xshift=-0.3cm, rotate=90] {$C/C$} (11);
-
-    \draw (6) edge[out=0, in=180, ->, thick] node [below] {$C/D$} (13);
-    \draw (6) edge[out=45, in=180, ->, thick] node [above] {$D/C$} (14);
-
-    \draw (7) edge[out=-135, in=135, ->, thick] node [yshift=1.8cm] {$C/D$} (4);
-    \draw (7) edge[out=45, in=180, ->, thick] node [above, yshift=1.2cm, xshift=1.8cm] {$D/D$} (2);
-
-    \draw (8) edge[out=0, in=45, ->, thick, loop] node [above] {$D/D$} (8);
-    \draw (8) edge[out=-90, in=130, ->, thick] node [right] {$C/D$} (14);
-
-    \draw (9) edge[out=-135, in=-45, ->, thick] node [above] {$C/C$} (0);
-    \draw (9) edge[out=100, in=-100, ->, thick] node [above left, yshift=1.5cm, rotate=90] {$D/D$} (10);
-
-    \draw (10) edge[out=0, in=180, ->, thick] node [below left, xshift=-0.5cm] {$C/C$} (8);
-    \draw (10) edge[out=180, in=0, ->, thick] node [above left, xshift=-0.5cm] {$D/C$} (15);
-
-    \draw (11) edge[out=0, in=70, ->, thick] node [above right] {$C/D$} (6);
-    \draw (11) edge[out=155, in=-90, ->, thick] node [right, yshift=1cm] {$D/D$} (5);
-
-    \draw (12) edge[out=90, in=-90, ->, thick] node [above right] {$C/D$} (6);
-    \draw (12) edge[out=155, in=-90, ->, thick] node [left, yshift=-1cm] {$D/D$} (9);
-
-    \draw (13) edge[out=135, in=0, ->, thick] node [below left, xshift=-0.4cm, yshift=0.4cm] {$C/D$} (9);
-    \draw (13) edge[out=70, in=-135, ->, thick] node [right] {$D/D$} (8);
-
-    \draw (14) edge[out=70, in=-45, ->, thick] node [right] {$C/D$} (8);
-    \draw (14) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (13);
-
-    \draw (15) edge[out=-45, in=30, ->, thick] node [left, xshift=-1.8cm, yshift=2.5cm] {$C/C$} (4);
-    \draw (15) edge[out=90, in=180, ->, thick] node [above left] {$D/C$} (5);
-
-    \end{tikzpicture}
-    }
-    \caption{TF1: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 4.}
-    \label{fig:tf1}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \scalebox{.7}{
-
-    \begin{tikzpicture}
-
-    \tikzstyle{state}=[minimum width=0.8cm, font=\boldmath];
-    \node[circle, draw=black, thick] (1) at (0, 0) [state] {$2$};
-	\node[circle, draw=black, thick] (4) at (4, 0) [state] {$5$};
-
-	\node[circle, draw=black, thick] (5) at (-2, -1) [state] {$6$};
-    \node[circle, draw=black, thick] (6) at (2, -1) [state] {$7$};
-    \node[circle, draw=black, thick] (3) at ($(5)+(-1,-2)$) [state] {$4$};
-    \node[circle, draw=black, thick] (12) at ($(5)+(0,-4)$) [state] {$13$};
-    \node[circle, draw=black, thick] (8) at ($(12)+(0,-2)$) [state] {$9$};
-    \node[circle, draw=black, thick] (9) at ($(8)+(-2,0)$) [state] {$10$};
-    \node[circle, draw=black, thick] (0) at ($(8)+(0,-2)$) [state] {$1$};
-
-    \node[circle, draw=black, thick] (2) at ($(6)+(0,-2)$) [state] {$3$};
-    \node[circle, draw=black, thick] (14) at ($(2)+(2,0)$) [state] {$15$};
-    \node[circle, draw=black, thick] (7) at ($(2)+(0,-2)$) [state] {$8$};
-    \node[circle, draw=black, thick] (10) at ($(14)+(0,-2)$) [state] {$11$};
-    \node[circle, draw=black, thick] (13) at ($(7)+(0,-2)$) [state] {$14$};
-    \node[circle, draw=black, thick] (11) at ($(10)+(0,-2)$) [state] {$12$};
-    \node[circle, draw=black, thick] (15) at ($(11)+(0,-2)$) [state] {$16$};
-
-    \coordinate[below of=0] (s);
-
-    \draw (s) edge[out=90, in=-90, ->, thick] node [left] {$C$} (0);
-
-    \draw (0) edge[out=0, in=-90, ->, thick] node [below right] {$C/D$} (13);
-    \draw (0) edge[out=45, in=0, ->, thick] node [above, rotate=90] {$D/D$} (12);
-
-    \draw (1) edge[out=-90, in=0, ->, thick] node [above, yshift=1.3cm, xshift=0.3cm] {$C/D$} (3);
-    \draw (1) edge[out=0, in=180, ->, thick] node [above] {$D/D$} (4);
-
-    \draw (2) edge[out=-45, in=-135, ->, thick] node [above] {$C/D$} (14);
-    \draw (2) edge[out=180, in=90, ->, thick] node [above, yshift=0.8cm, xshift=3cm] {$D/D$} (9);
-
-    \draw (3) edge[out=180, in=-135, ->, thick] node [left, yshift=2cm, xshift=-0.1cm] {$C/C$} (0);
-    \draw (3) edge[out=135, in=180, ->, thick] node [above, yshift=0.2cm] {$D/D$} (1);
-
-    \draw (4) edge[out=90, in=90, ->, thick] node [above] {$C/D$} (1);
-    \draw (4) edge[out=-90, in=0, ->, thick] node [right] {$D/D$} (2);
-
-    \draw (5) edge[out=-90, in=90, ->, thick] node [right, yshift=1cm] {$C/C$} (12);
-    \draw (5) edge[out=0, in=180, ->, thick] node [below right] {$D/C$} (6);
-
-    \draw (6) edge[out=135, in=-45, ->, thick] node [right, xshift=1cm] {$C/C$} (1);
-    \draw (6) edge[out=-45, in=135, ->, thick] node [above left, yshift=-0.5cm] {$D/D$} (14);
-
-    \draw (7) edge[out=135, in=45, ->, thick] node [above] {$C/D$} (12);
-    \draw (7) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (2);
-
-    \draw (8) edge[out=90, in=-135, ->, thick] node [above right] {$C/D$} (7);
-    \draw (8) edge[out=180, in=0, ->, thick] node [above] {$D/D$} (9);
-
-    \draw (9) edge[out=-45, in=-135, ->, thick] node [below] {$C/D$} (8);
-    \draw (9) edge[out=-90, in=180, ->, thick] node [right] {$D/D$} (0);
-
-    \draw (10) edge[out=180, in=-60, ->, thick] node [below, yshift=-0.5cm, xshift=0.4cm] {$C/C$} (2);
-    \draw (10) edge[out=0, in=0, ->, thick] node [right] {$D/C$} (15);
-
-    \draw (11) edge[out=90, in=-45, ->, thick] node [below right, xshift=0.7cm] {$C/D$} (7);
-    \draw (11) edge[out=180, in=0, ->, thick] node [below] {$D/D$} (13);
-
-    \draw (12) edge[out=135, in=-45, ->, thick] node [above left] {$C/C$} (3);
-    \draw (12) edge[out=-90, in=135, ->, thick] node [left] {$D/D$} (8);
-
-    \draw (13) edge[out=90, in=-90, ->, thick] node [left] {$C/C$} (7);
-    \draw (13) edge[out=45, in=-135, ->, thick] node [below, yshift=-0.2cm, rotate=45] {$D/D$} (10);
-
-    \draw (14) edge[out=-90, in=90, ->, thick] node [right] {$C/D$} (10);
-    \draw (14) edge[out=-100, in=45, ->, thick] node [above] {$D/D$} (7);
-
-    \draw (15) edge[out=-135, in=180, ->, thick, loop] node [left] {$C/C$} (15);
-    \draw (15) edge[out=90, in=-90, ->, thick] node [left] {$D/D$} (11);
-
-    \end{tikzpicture}
-    }
-    \caption{TF2: a 16 state finite state machine with a handshake leading to
-    mutual cooperation at state 16.}
-    \label{fig:tf2}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
     \begin{tikzpicture}
@@
     \end{tikzpicture}
-    \caption{TF3: an 8 state finite state machine.}
-    \label{fig:tf3}
-\end{figure}
-
-As opposed to the previously described strategies, these strategies were trained
-with the objective function of \textit{mean fixation probabilities for Moran
-processes} starting at initial population states consisting of \(N/2\)
-individuals of the training candidates and \(N/2\) individuals of an opponent
-strategy, taken from a selection of 150 opponents from the Axelrod library:
-
-\begin{itemize}
-	\item TF1 \(N=12\), 0\% noise.
-	\item TF2 \(N=10\), 0\% noise.
-	\item TF3 \(N=8\), 1\% noise.
-\end{itemize}
-
-The trained algorithms
-were run for fewer than 50 generations. Training data for this is available at
-\cite{data}.
-
-TF1 has an initial handshake of CCD and cooperates if the opponent matches.
-However if the opponent later defects, TF1 will respond in kind, so the
-handshake is not permanent. Only one player (Prober 4 \cite{Prison1998}) manages to
-achieve cooperation with TF1 after about 20 rounds of play. TF1 is functionally
-very similar to a strategy known as ``Collective Strategy'', which has a
-handshake of CD and cooperates with opponents that matched the handshake
-until they defect, defecting thereafter if the opponent ever defects \cite{Li2009}.
-Collective Strategy was specifically designed for evolutionary processes.
-
-TF2 always starts with CD and will defect against opponents that start with
-DD\@. It plays CDD against itself and then cooperates thereafter; Fortress3 and
-Fortress4 also use a similar handshake and cooperate with TF2. Cooperation
-can be rescued after a failed handshake by a complex sequence of plays
-which sometimes results in mutual cooperation with Firm but Fair, Grofman, and
-GTFT, and a few others with low probability. TF2 defects against all other
-players in the study, barring
-unusual cases arising from particular randomizations. Fig~\ref{fig:tf2} shows
-all 16 states of the strategy (states 6 and 7 are not reachable).
-
-TF3 cooperates and defects with
-various cycles depending on the opponent's actions. TF3 will mutually
-cooperate with any strategy and only tolerates a few defections before
-defecting for the rest of match. It is similar to but not exactly the same as
-Fool Me Once, a strategy that cooperates until the opponent has defected twice
-(not necessarily consecutively), and defects indefinitely thereafter. Though a
-product of training with a Moran objective, it differs from TF1 and TF2
-in that it lacks a handshake mechanism. Fig~\ref{fig:tf3} shows
-all 8 states of the strategy produced by the training process (states 3 and 8
-are not reachable).
-
-For both TF1 and TF2 a handshake
-mechanism naturally emerges from the structure of the underlying finite state
-machine. This behavior is an outcome of the evolutionary process and is in no
-way hard-coded or included via an additional mechanism.
-
-\begin{table}[!hbtp]
-    \centering
-        \scalebox{0.7}{
-            \begin{tabular}{lrrrrrrrrrrrrrrrr}
-            \toprule
-            Memory Depth &   0   &   1   &   2   &   3   &   4   &   5   &   6   &   9   &   10  &   11  &   12  &   16  &   20  &   40  &   200 &  \(\infty\)   \\
-            \midrule
-            Count &     3 &    29 &    12 &     8 &     2 &     6 &     1 &     1 &     5 &     1 &     1 &     2 &     2 &     2 &     1 &    88 \\
-            \bottomrule
-            \end{tabular}
-        }
-        \caption{Memory depths}
-        \label{tbl:memory_depth_count}
-\end{table}
-
-\subsection*{Data collection}
-
-Each strategy pair is run for 1000 repetitions of the Moran process to fixation
-with starting population distributions of $(1, N-1)$, $(N/2, N/2)$ and $(N-1 ,
-1)$, for \(N\) from 2 through 14. The fixation probability is then empirically
-computed for each combination of starting distribution and value of \(N\).  The
-Axelrod library can carry out exact simulations of the Moran process. Since some
-of the strategies have a high computational cost or are stochastic, samples are
-taken from a large number of 200 turn match outcomes for the pairs of players
-for use in computing fitnesses in the Moran process (i.e. a stochastic cache of
-matches is used). This approach was verified to agree with unsampled
-calculations to a high degree of accuracy in specific cases.  This is described
-in Algorithms~\ref{alg:data_collection} and~\ref{alg:moran_process}.
-
-\begin{algorithm}[!hbtp]
-        \caption{Data Collection}
-        \label{alg:data_collection}
-          \begin{algorithmic}[1]
-            \FOR{player\_one \textbf{in} players\_list}
-              \FOR{player\_two \textbf{in} (players\_list - player\_one)}
-                \STATE pair $\gets$ (player\_one, player\_two)
-                \FOR{starting\_population\_distributions \textbf{in} [$(1, N-1), (\frac{N}{2}, \frac{N}{2}), (N-1, 1)]$}
-                \WHILE {repetitions $\leq 1000$}
-                \STATE \textbf{simulate} moran process (pair, starting distribution)
-                \ENDWHILE
-                \STATE\textbf{yield} fixation probabilities
-                \ENDFOR
-              \ENDFOR
-            \ENDFOR
-          \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[!hbtp]
-        \caption{Moran process}
-        \label{alg:moran_process}
-          \begin{algorithmic}[1]
-          \STATE initial population $\gets$ (pair, starting distribution) \
-          \STATE population $\gets$ initial population
-
-            \WHILE {population not uniform}
-              \FOR{player in population}
-              \FOR{opponent in (population - player)}
-                \STATE match $\gets$ (player, opponent) 
-                \STATE results $\gets$ stochastic\_cache (200 round match)
-                \ENDFOR
-              \ENDFOR
-              \STATE population $\gets$ sorted(results)
-              \STATE parent $\gets$ selected randomly in proportion to its total match payoffs
-              \STATE offspring $\gets$ parent
-              \STATE kill off $\gets$ uniformly random player from population
-              \STATE population $\gets$ offspring replaces kill off
-            \ENDWHILE
-          \end{algorithmic}
-\end{algorithm}
-
-The next section will further validate the methodology by comparing
-simulated results to analytical results in a few selected cases. The main
-results of this
-manuscript are presented in which will
-present a detailed analysis of all the data generated. Finally,
-a discussion and conclusion will offer future avenues for the work
-presented here.
-
-\section*{Results}
-
-\subsection*{Validation}
-
-As described in \cite{Nowak} consider the payoff matrix:
-
-\begin{equation}\label{equ:payoff_matrix}
-    M = \begin{pmatrix}
-        a, b\\
-        c, d
-        \end{pmatrix}
-\end{equation}
-
-The expected payoffs of \(i\) players of the first type in a population with \(N
-- i\) players of the second type are given by:
-
-\begin{equation}\label{equ:expected_payoff_one}
-    f_i = \frac{a(i - 1) + b(N - i)}{N - 1}
-\end{equation}
-
-\begin{equation}\label{equ:expected_payoff_two}
-    g_i = \frac{ci + d(N - i - 1)}{N - 1}
-\end{equation}
-
-The transitions within the birth death process that underpins the Moran process
-are then given by:
-
-\begin{align}
-    p_{i, i+1}&= \frac{if_i}{if_i+(N-i)g_i}\frac{N-i}{N}\label{equ:p_up}\\
-    p_{i, i-1}&= \frac{(N-i)g_i}{if_i+(N-i)g_i}\frac{i}{N}\label{equ:p_down}\\
-    p_{ii} &= 1 - p_{i, i+1} - p_{i, i-1}\label{equ:p_stay}
-\end{align}
-
-Using this the fixation probability
-of the first strategy in a population of \(i\) individuals of the first type
-and \(N-i\) individuals of the second, is given by \cite{Nowak2017}:
-
-\begin{equation}\label{equ:fixation_probability}
-x_i = \frac{1 + \sum_{j=1}^{i-1}\prod_{k=1}^{j}\gamma_j}{1 + \sum_{j=1}^{N-1}
-      \prod_{k=1}^{j}\gamma_j}
-\end{equation}
-
-where:
-
-\[
-\gamma_j = \frac{p_{j, j-1}}{p_{j, j+1}}
-\]
-
-A neutral strategy will have fixation probability $x_i = i/N$.
-
-Comparisons of \(x_1, x_{N/2}, x_{N-1}\) are shown in
-Fig~\ref{fig:comparison_deterministic} for Alternator and WSLS (a 5\%
-confidence interval computed using an asymptotic normal approximation is also
-included \cite{brown2001interval}).
-The points represent the simulated
-values and the line shows the theoretical value. Note that these are
-deterministic strategies and show a good match between the expected value
-of (\ref{equ:fixation_probability}) and the actual Moran process for all
-strategy pairs. These means have been compared using a \(t\)-test and the \(p\)
-values are shown in Table~\ref{tab:comparison_deterministic} which confirms the
-fact that the theoretic and simulated values are a good match.
-
-Fig~\ref{fig:comparison_stochastic} shows the fixation probabilities for
-stochastic strategies: Calculator and arrogant Q Learner. These are no longer a
-good match (confirmed with a \(t\)-test in
-Table~\ref{tab:comparison_stochastic}). This demonstrates that assuming
-a given interaction between two IPD strategies can be summarised with a set of
-utilities as shown in (\ref{equ:payoff_matrix}) is not correct. For any given pair of
-strategies it is possible to obtain \(p_{i,i-1}, p_{i,i+1}, p_{ii}\) exactly (as
-opposed to the approximations offered by (\ref{equ:p_up}), (\ref{equ:p_down})
-and (\ref{equ:p_stay})). Obtaining these requires particular analysis for a
-given pair and can be quite a complex endeavour for stochastic strategies with
-long memory: this is not necessary for the purposes of this work.  All data
-generated for this validation exercise can be found at~\cite{data}.
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Alternator_v_WSLS.pdf}
-    \caption{Comparison of theoretic and actual Moran Process fixation
-             probabilities for \textit{deterministic} strategies: Alternator and
-         Cooperator. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_deterministic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.89942 &                0.89942 &                0.89942 \\
-          4 &          0.16344 &                0.74768 &                0.85877 \\
-          6 &          0.65406 &                0.84051 &                0.51992 \\
-          8 &          0.92617 &                0.45748 &                0.38604 \\
-         10 &          0.03505 &                0.37115 &                0.60635 \\
-         12 &          0.96697 &                0.20790 &                0.18124 \\
-         14 &          0.08126 &                0.63771 &                0.76246 \\
-         16 &          0.59434 &                0.07697 &                0.42520 \\
-         18 &          0.05339 &                0.47126 &                0.94814 \\
-         20 &          0.30805 &                0.79795 &                0.82381 \\
-        \bottomrule
-        \end{tabular}
-
-    \caption{\(p\) values resulting from a $t$ test comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{deterministic} strategies: Alternator and
-    Cooperator.}
-    \label{tab:comparison_deterministic}
-\end{table}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=.95\columnwidth]{./Calculator_v_Arrogant_QLearner.pdf}
-    \caption{Comparison of theoretic and actual Moran Process
-             fixation probabilities for \textit{stochastic} strategies:
-             Calculator and Arrogant Q Learner. 5\% confidence intervals calculated using an asymptotic
-     normal approximation.
-The top most line on all figures (in red and using a circle) corresponds to
-\(x_{N-1}\), the middle line (in green and using a cross) corresponds to
-\(x_{N/2}\) and the bottom line (in blue and using an x) corresponds to
-\(x_{1}\).}
-    \label{fig:comparison_stochastic}
-\end{figure}
-
-\begin{table}[!hbtp]
-    \centering
-        \begin{tabular}{rrrr}
-        \toprule
-          N &  $p_1$ $p$ Value &  $p_{N / 2}$ $p$ Value &  $p_{N - 1}$ $p$ Value \\
-        \midrule
-          2 &          0.05372 &                0.05372 &                0.05372 \\
-          4 &          0.34188 &                0.00940 &                0.00005 \\
-          6 &          0.16510 &                0.00000 &                0.00000 \\
-          8 &          0.03451 &                0.00000 &                0.00000 \\
-         10 &          0.00543 &                0.00000 &                0.00000 \\
-         12 &          0.19646 &                0.00000 &                0.00000 \\
-         14 &          0.00814 &                0.00000 &                0.00000 \\
-         16 &          0.01038 &                0.00000 &                0.00000 \\
-         18 &          0.39556 &                0.00000 &                0.00000 \\
-         20 &          0.00030 &                0.00000 &                0.00000 \\
-        \bottomrule
-        \end{tabular}
-    \caption{\(p-\text{values}\) resulting from a \(t-\text{ test}\) comparing the theoretic
-        value with the simulated value of the Moran Process fixation
-        probabilities for \textit{stochastic} strategies: Calculator and
-    Arrogant Q Learner.}
-    \label{tab:comparison_stochastic}
-\end{table}
-
-\subsection*{Empirical results}
-
-This section outlines the data analysis carried out, all data for this study is
-available at~\cite{data}.
-
-\begin{itemize}
-    \item First the specific case of
-        \(N=2\) is considered.
-    \item The effect of
-        population size on the ability of a strategy to invade another
-        population is investigated. This will highlight how complex strategies with long
-        memories outperform simpler strategies.
-    \item Then a similar investigation of the
-        ability to defend against an invasion is given.
-    \item Finally the relationship
-        between performance for differing population sizes as well as
-        taking a close look at zero determinant strategies \cite{Press2012} is
-        analysed.
-\end{itemize}
-
-\subsubsection*{The special case of \(N=2\)}
-
-When $N=2$ the fixation probabilities of the Moran process are effectively measures
-of the distribution of  relative
-mean payoffs over all possible matches between two players. The strategy
-that scores higher than the other more often will fixate more often. For \(N=2\)
-the two cases of \(x_1\) and \(x_{N-1}\) coincide, but will be
-considered separately for larger \(N\) in the following sections.
-The top 16 (10\%) strategies are
-shown in
-
-Table~\ref{tbl:summary_top_2} and figures showing the performance of all
-strategies are available in the appendix.
-The top five ranking strategies are:
-
-\begin{enumerate}
-    \item The top strategy is the Collective Strategy (CS) which has a simple
-        handshake mechanism described above.
-    \item Defector: it always defects. Since it has no interactions with other
-        defectors (recall that \(N=2\)), its aggressiveness is rewarded.
-    \item Aggravater, which plays like Grudger (responding to any
-        defections with unconditional defections throughout) however starts by
-        playing 3 defections.
-    \item Predator, a finite state machine described in \cite{Ashlock2006}.
-    \item Handshake, a slightly less aggressive version of the Collective
-        Strategy \cite{Robson1990}. As long as the initial sequence is played
-        then it cooperates. Thus it will do well in a population consisting of
-        many members of itself just as the Collective Strategy does. The
-        difference is that CS will defect after the handshake if the opponent
-        defects while Handshake will not.
-\end{enumerate}
-
-It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
-for which a zero determinant strategy does appear in the top 10\% ranking
-strategies: ZD-extort-4. The performance of zero determinant strategies will be
-examined more closely.
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \scalebox{0.95}{
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &                  Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-        \midrule
-        1  &                      CS &  0.497 &  0.5020 &  0.6651 &   0.572 &  0.9908 &  0.993 &  0.1800 \\
-        2  &                Defector &  0.502 &  0.5020 &  0.6496 &   0.518 &  1.0000 &  1.000 &  0.1767 \\
-        3  &              Aggravater &  0.502 &  0.5020 &  0.6328 &   0.518 &  0.9790 &  0.999 &  0.1660 \\
-        4  &                Predator &  0.319 &  0.4980 &  0.6301 &   0.551 &  0.9870 &  0.993 &  0.1676 \\
-        5  &               Handshake &  0.006 &  0.4503 &  0.6240 &   0.524 &  0.9908 &  0.993 &  0.1889 \\
-        6  &                Prober 4 &  0.431 &  0.4620 &  0.6183 &   0.534 &  0.9579 &  0.958 &  0.1656 \\
-        7  &                     \textbf{TF1} &  0.430 &  0.4980 &  0.6171 &   0.544 &  0.9240 &  0.981 &  0.1345 \\
-        8  &                Prober 3 &  0.497 &  0.5011 &  0.6044 &   0.505 &  0.9930 &  0.993 &  0.1683 \\
-        9  &                     \textbf{TF2} &  0.324 &  0.5020 &  0.6026 &   0.565 &  0.8362 &  0.887 &  0.1092 \\
-        10 &                 Grudger &  0.497 &  0.5020 &  0.5996 &   0.502 &  0.9840 &  0.989 &  0.1695 \\
-        11 &       Better and Better &  0.388 &  0.3951 &  0.5980 &   0.514 &  0.9300 &  0.934 &  0.1865 \\
-        12 &                    MEM2 &  0.497 &  0.5001 &  0.5942 &   0.502 &  0.9840 &  0.987 &  0.1656 \\
-        13 &  Meta Hunter Aggressive &  0.247 &  0.2943 &  0.5933 &   0.517 &  0.9498 &  0.981 &  0.2013 \\
-        14 &                     \textbf{TF3} &  0.344 &  0.4971 &  0.5927 &   0.502 &  0.9790 &  0.982 &  0.1617 \\
-        15 &            Fool Me Once &  0.494 &  0.4980 &  0.5892 &   0.502 &  0.9790 &  0.982 &  0.1625 \\
-        16 &             ZD-Extort-4 &  0.497 &  0.5020 &  0.5867 &   0.584 &  0.6900 &  0.695 &  0.0724 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Top strategies for \(N=2\) (neutral fixation is \(p=0.5\))}
-    \label{tbl:summary_top_2}
-\end{table}
-
-As will be demonstrated the results for
-\(N=2\) differ from those of larger $N$. Hence these results do not concur with
-the literature which suggests that zero determinant strategies should be
-effective for larger population sizes, but these analyses consider stationary
-behaviour, while this work runs for a fixed number of rounds. \cite{stewart2013extortion}
-The stationarity assumption allows for a deterministic payoff matrix
-leading to the conclusions about zero determinant strategies in the space
-of memory-one strategies that do not generalize to this context.
-
-% In the next sections close attention to
-% strategies who are strong invaders/resistors is given.
-
-\subsubsection*{Strong Invaders}
-
-In this section the focus is on the ability of a mutant strategy to invade: the
-probability of one individual of a given type successfully fixating in a
-population of \(N - 1\) other individuals, denoted by \(x_1\).
-
-The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
-figures showing the performance of all strategies is available in the
-appendix.
-
-\begin{table}[!hbtp]
-    \centering
-    \tiny
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
-            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
-            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
-            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
-            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
-            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
-            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
-            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
-            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
-            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
-            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
-            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
-            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
-            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
-            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
-            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
-            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
-            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
-            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
-            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
-            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
-            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
-            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
-            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
-            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
-            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
-            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
-            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
-            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
-            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
-            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
-            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
-            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
-            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
-            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
-            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
-            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
-            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
-            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
-            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
-            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
-            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
-            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
-            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
-            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_invade}
-\end{table}
-
-It can be seen that apart from CS, none of the strategies for \(N=2\)
-of Table~\ref{tbl:summary_top_2} perform well for \(N\in\{3, 7, 14\}\). The new
-top performing strategies are:
-
-\begin{itemize}
-    \item Grudger (which only performs well for \(N=3\)), starts by cooperating
-        but will defect if at any point the opponent has defected.
-    \item MEM2, an infinite memory strategy that switches between TFT, TF2T, and
-        Defector \cite{Li2014}.
-    \item TF3, the finite state machine trained specifically for Moran processes
-        described.
-    \item Prober 4, a strategy which starts with a specific 20 move sequence of
-        cooperations and defections \cite{Prison1998}. This initial sequence serves
-        as approximate handshake.
-    \item  PSO Gambler and Evolved Lookerup 2 2 2: strategies that make use
-        of a lookup table mapping the first 2 moves of the opponent as well as
-        the last 2 moves of both players to an action.  PSO gambler is a
-        stochastic version of  Lookerup which maps those states to probabilities
-       of cooperating. Lookerup was described in \cite{Knight2016}.
-    \item The Evolved ANN strategies are neural networks that map a number of
-	    attributes (first move, number of cooperations, last move, etc.) to
-	    an action. Both of these have been trained using an evolutionary
-	    algorithm.
-    \item Evolved FSM 16 is a 16 state finite state machine trained to
-        perform well in tournaments.
-\end{itemize}
-
-Only one of the above strategies is stochastic although close inspection of the
-source code of PSO Gambler shows that it makes stochastic decisions rarely, and
-is functionally very similar to its deterministic cousin Evolved Looker Up.
-PSO Gambler Mem1 is a stochastic memory one strategy that has been trained to
-maximise its utility and does perform well.
-Apart from TF3, the finite state machines trained specifically for
-Moran processes do not appear in the top 5, while strategies trained for
-tournaments do. This is due to the nature of invasion: most of the opponents
-will initially be different strategies. The next section will consider the
-converse situation.
-
-\subsubsection*{Strong resistors}
-
-In addition to identifying good invaders, strategies resistant to invasion by
-other strategies are identified by examining the distribution of $x_{N-1}$ for
-each strategy.
-
-Table~\ref{tbl:top_resist} shows the top strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
-for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies previously discussed perform well for high \(N\).
-
-\begin{table}[!hbtp]
-    \tiny
-    \centering
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
-            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
-            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
-            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
-            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
-            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
-            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
-            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
-            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
-            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
-            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
-            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
-            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
-            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
-            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
-            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-            \begin{tabular}{llrrrrrrr}
-            \toprule
-            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
-            \midrule
-            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
-            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
-            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
-            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
-            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
-            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
-            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
-            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
-            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
-            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
-            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
-            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
-            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
-            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
-            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
-            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
-            \bottomrule
-            \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
-        \begin{tabular}{llrrrrrrr}
-        \toprule
-        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
-        \midrule
-        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
-        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
-        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
-        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
-        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
-        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
-        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
-        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
-        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
-        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
-        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
-        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
-        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
-        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
-        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
-        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
-        \bottomrule
-        \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_resist}
-\end{table}
-
-Interestingly none of these strategies are stochastic: this is explained by the
-value of not provoking typically cooperative opponent strategies with
-speculative defections. This includes opponents using the same strategy.  Acting
-stochastically increases the chance of reducing the score of individuals of the
-same type in a Moran process.  However it is possible to design a strategy with
-a stochastic or error-correcting handshake that is an excellent resistor even in
-noisy environments \cite{Lee2015}.
-
-There are only two new strategies that appear in the top ranks for
-\(x_{N-1}\): TF1 and TF2. These two strategies are with CS the strongest
-resistors. They all have handshakes, and whilst the handshakes of CS and
-Handshake (which ranks highly for the smaller values of \(N\)) were
-programmed, the handshakes of TF1 and TF2 evolved through an evolutionary
-process without any priming.
-
-As described previously the strategies trained with
-the payoff maximizing objective are among the best invaders in the library
-however they are not as resistant to invasion as the strategies trained using a
-Moran objective function. These strategies include trained finite state machine
-strategies, but they do not appear to have handshaking mechanisms. Therefore it
-is reasonable to conclude that the objective function is the cause of the
-emergence of handshaking mechanisms. More specifically, TF1 and TF2 evolved
-handshakes for high invasion resistance. TF3 is a better total payoff maximizer
-which makes it a better invader along with the strategies
-trained to maximize total payoff since successful fitness proportionate selection
-is necessary for invasion. Training with an objective with initial population
-mix other than $(N/2, N/2)$ may favor invasion or resistance.
-
-The payoff maximizing strategies typically will not defect before the opponent's
-first defection, possibly because the training strategy collection contains some
-strategies such as Grudger and Fool Me Once that retaliate harshly by defecting
-for the remainder of the match if the opponent has more than a small number of
-cumulative defections. Paradoxically for handshaking strategies
-it is advantageous to defect (as a signal)
-in order to achieve mutual cooperation with opponents using the same strategy
-but not with other opponents. Nevertheless an evolutionary process is able to
-tunnel through the costs and risks associated with early defections to find more
-optimal solutions, so it is not surprising in hindsight that handshaking
-strategies emerge from the evolutionary training process.
-
-A handshake requires at least one defection and there is
-selective pressure to defect as few times as possible to achieve the
-self-recognition mechanism. It is also unwise to defect on the first move as
-some strategies additionally retaliate in response to first round defections. So the
-handshakes used by TF1, TF2, and CS are in some sense optimal.
-
-It is evident through
-the work presented that performance of strategies not only depends
-on the initial population distribution but also that there seems to be a
-difference depending on whether or not \(N>2\). This will be explored further in
-the next section, looking not only at \(x_1\) and \(x_{N-1}\) but also
-considering
-\(x_{N/2}\).
-
-\subsubsection*{The effect of population size}
-
-Tables~\ref{tbl:ranks_v_size_invade},~\ref{tbl:ranks_v_size_resist}
-and~\ref{tbl:ranks_v_size_coexist} show the ranks for a selection of
-strategies:
-
-\begin{itemize}
-    \item The strategies that ranked highly for \(N=2\);
-    \item The strategies that ranked highly for \(N=14\);
-    \item The zero determinant strategies.
-\end{itemize}
-
-The results for \(x_{N/2}\) show similarities to the results for \(x_{N-1}\) and
-in particular TF1, TF2 and TF3 ranked one, three and eight. This is to be
-expected since, as described previously these strategies
-were trained in an initial population of \((N/2, N/2)\) individuals.
-
-For all starting populations
-\(i\in\{1, N/2, N-1\}\) the ranks of strategies are relatively stable across the
-different values of \(N>2\) however for \(N=2\) there is a distinct difference.
-This highlights that there is little that can be inferred about the evolutionary
-performance of a strategy in a large population from its performance in a small
-population. This is confirmed by the performance of the zero determinant strategies: while
-some do rank relatively highly for \(N=2\) (ZD-Extort-4 has rank 16) this rank
-does not translate to larger populations.
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                         Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                           CS &    1 &    1 &    2 &   11 &    9 &   11 &   13 &   21 &   16 &   22 &   17 &   25 &   23 \\
-                     Defector &    2 &   43 &   80 &   91 &   89 &   87 &   87 &  103 &   97 &  105 &   94 &  103 &  101 \\
-                   Aggravater &    3 &   50 &   89 &   99 &  102 &  103 &  108 &  113 &  114 &  115 &  115 &  116 &  117 \\
-                     Predator &    4 &    8 &   24 &   35 &   28 &   33 &   31 &   43 &   36 &   43 &   34 &   45 &   35 \\
-                    Handshake &    5 &   17 &   40 &   46 &   43 &   46 &   46 &   49 &   48 &   49 &   47 &   50 &   49 \\
-        \midrule
-               Evolved FSM 16 &   31 &   11 &    6 &    2 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-            PSO Gambler 2\_2\_2 &   29 &   14 &   10 &    6 &    4 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-         EvolvedLookerUp2\_2\_2 &   33 &   18 &   11 &    9 &   10 &    6 &    6 &    5 &    3 &    5 &    3 &    3 &    3 \\
-                  Evolved ANN &   20 &   10 &    8 &    7 &    8 &    5 &    3 &    3 &    4 &    3 &    4 &    4 &    4 \\
-                Evolved ANN 5 &   21 &    9 &    7 &    8 &    7 &    4 &    5 &    4 &    5 &    4 &    5 &    5 &    5 \\
-        \midrule
-                          \textbf{TF1} &    7 &   13 &   33 &   38 &   30 &   39 &   42 &   46 &   42 &   46 &   41 &   46 &   46 \\
-                          \textbf{TF2} &    9 &   19 &   29 &   33 &   19 &   28 &   29 &   38 &   27 &   34 &   26 &   32 &   30 \\
-                          \textbf{TF3} &   14 &    4 &    5 &    5 &    6 &    9 &   11 &   11 &   12 &   14 &   13 &   13 &   16 \\
-        \midrule
-                  ZD-Extort-4 &   16 &   81 &  107 &  120 &  135 &  136 &  142 &  140 &  142 &  142 &  144 &  144 &  145 \\
-               ZD-Extort-2 v2 &   41 &  105 &  126 &  140 &  152 &  152 &  153 &  152 &  153 &  153 &  153 &  152 &  153 \\
-                  ZD-Extort-2 &   43 &  107 &  125 &  139 &  151 &  151 &  152 &  153 &  152 &  152 &  152 &  153 &  152 \\
-                     ZD-SET-2 &  100 &  111 &  117 &  117 &  122 &  127 &  131 &  128 &  131 &  131 &  130 &  132 &  131 \\
-                    ZD-GTFT-2 &  112 &   92 &   82 &   80 &   81 &   82 &   84 &   72 &   81 &   71 &   78 &   72 &   70 \\
-                     ZD-GEN-2 &  113 &   96 &   87 &   83 &   85 &   88 &   90 &   82 &   87 &   82 &   86 &   83 &   91 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Invasion: Fixation ranks of a few selected strategies according to \(x_1\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_invade}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-    \scalebox{0.7}{
-        \begin{tabular}{lrrrrrrrrrrrrr}
-        \toprule
-                   Size &      2 &      3 &      4 &      5 &      6 &      7 &      8 &      9 &     10 &     11 &     12 &     13 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 &    1 \\
-               Defector &    2 &   29 &   55 &   79 &   94 &   97 &   98 &   98 &  102 &  101 &  103 &  100 &  102 \\
-             Aggravater &    3 &   42 &   71 &   97 &  101 &  106 &  107 &  111 &  113 &  113 &  116 &  115 &  115 \\
-               Predator &    4 &    2 &    3 &    3 &    3 &    4 &    4 &    4 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    4 &    5 &    5 &    5 &    5 &    5 &    6 &    6 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF1} &    7 &    3 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 &    2 \\
-                    \textbf{TF2} &   10 &    5 &    4 &    4 &    4 &    3 &    3 &    3 &    3 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    6 &    6 &    6 &    6 &    6 &    6 &    5 &    5 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   13 &    9 &   10 &   11 &   11 &   11 &   13 &   14 &   13 &   13 &   13 &   13 &   13 \\
-        \midrule
-            ZD-Extort-4 &   19 &   68 &   98 &  106 &  108 &  114 &  115 &  115 &  118 &  118 &  117 &  118 &  117 \\
-         ZD-Extort-2 v2 &   49 &   98 &  111 &  121 &  123 &  124 &  124 &  130 &  130 &  132 &  134 &  132 &  134 \\
-            ZD-Extort-2 &   50 &   97 &  112 &  123 &  124 &  125 &  123 &  126 &  131 &  131 &  132 &  133 &  133 \\
-               ZD-SET-2 &  108 &  105 &  104 &  104 &  103 &  103 &  100 &  100 &  101 &   99 &   98 &   98 &   98 \\
-              ZD-GTFT-2 &  112 &   95 &   88 &   84 &   75 &   72 &   71 &   73 &   71 &   71 &   67 &   68 &   68 \\
-               ZD-GEN-2 &  114 &   96 &   89 &   86 &   77 &   75 &   72 &   74 &   72 &   72 &   68 &   69 &   69 \\
-        \bottomrule
-        \end{tabular}
-    }
-    \caption{Resistance: Fixation ranks of a few selected strategies according to \(x_{N-1}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_resist}
-\end{table}
-
-\begin{table}[!hbtp]
-    \centering
-    \scriptsize
-        \begin{tabular}{lrrrrrrr}
-        \toprule
-                   Size &      2 &      4 &      6 &      8 &     10 &     12 &     14 \\
-        \midrule
-                     CS &    1 &    1 &    1 &    1 &    1 &    1 &    2 \\
-               Defector &    2 &   78 &   99 &  106 &  110 &  113 &  120 \\
-             Aggravater &    3 &   91 &  105 &  111 &  122 &  125 &  128 \\
-               Predator &    4 &    2 &    4 &    4 &    4 &    4 &    4 \\
-              Handshake &    5 &    6 &    5 &    6 &    6 &    6 &    6 \\
-        \midrule
-                    \textbf{TF2} &    9 &    4 &    3 &    2 &    2 &    2 &    1 \\
-                    \textbf{TF1} &    7 &    3 &    2 &    3 &    3 &    3 &    3 \\
-               Prober 4 &    6 &    5 &    6 &    5 &    5 &    5 &    5 \\
-        \midrule
-                    \textbf{TF3} &   14 &    8 &    8 &    8 &    8 &    8 &    8 \\
-        \midrule
-            ZD-Extort-4 &   16 &  102 &  117 &  129 &  141 &  143 &  145 \\
-         ZD-Extort-2 v2 &   41 &  118 &  135 &  151 &  152 &  152 &  153 \\
-            ZD-Extort-2 &   43 &  117 &  136 &  149 &  151 &  151 &  152 \\
-               ZD-SET-2 &  100 &  110 &  110 &  108 &  106 &  106 &  108 \\
-              ZD-GTFT-2 &  112 &   82 &   80 &   77 &   75 &   75 &   74 \\
-               ZD-GEN-2 &  113 &   85 &   81 &   82 &   79 &   77 &   76 \\
-        \bottomrule
-        \end{tabular}
-    \caption{Ranks of a few selected strategies according to \(x_{N/2}\) for different
-    population sizes}
-    \label{tbl:ranks_v_size_coexist}
-\end{table}
-
-Fig~\ref{fig:correlation_coefficients} shows the correlation coefficients
-of the ranks of strategies in differing population size. How well a strategy
-performs in any Moran process for \(N>2\) has
-little to do with the performance for \(N=2\). This illustrates why the strong
-performance of zero determinant strategies predicted in \cite{Press2012} does
-not extend to larger populations. This was discussed theoretically in
-\cite{Adami2013} and observed empirically in these simulations.
-
-\begin{figure}[!htbp]
-    \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_invade.pdf}
-        \caption{Rank based on \(x_1\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_resist.pdf}
-        \caption{Rank based on \(x_{N - 1}\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./correlation_heatmap_coexist.pdf}
-        \caption{Rank based on \(x_{N/2}\)}
-    \end{subfigure}
-    \caption{Heatmap of correlation coefficients of rankings by population size.}
-    \label{fig:correlation_coefficients}
-\end{figure}
-
-\section*{Discussion}
-
-Training strategies to excel
-at the Moran process leads to the evolution of cooperation, but only with like
-individuals in the case of TF1 and TF2. This may have significant implications
-for various biological and social phenomena such as
-human social interactions, particularly the evolution of ingroup/outgroup mechanisms
-and other sometimes costly rituals that reinforce group behavior.
-
-While TF1 and TF2 are competent invaders, the best invaders
-in the study do not appear to employ strict handshakes, and are generally
-cooperative strategies. TF3, which does not use a handshake, is a better invader
-than TF1 and TF2 but not as good a resistor. Nevertheless it was the result
-of the same kind of training processes and is a better combined invader-resistor
-than the invaders that were trained previously to maximize payout.
-
-The strategies trained to maximize payoff in head-to-head matches are generally
-cooperative and are effective invaders.
-Combined with the fact that handshaking strategies are stronger resistors,
-this suggests that while maximizing individual payoff can lead to the evolution
-of cooperation, these strategies are not the most evolutionarily stable
-in the long run. A strategy with a handshaking mechanism is still capable of
-invading and is more resistant to subsequent invasions. Moreover, the
-best resistor of the payoff maximally trained strategies (Evolved Looker Up
-1\_1\_1),
-which always defects if the opponent defects in the first round, is effectively
-employing a one-shot handshake of C. Similarly, Grudger (also known as Grim),
-which emerged from training memory one strategies for the Moran process,
-also effectively employs a handshake of always cooperating, as it defects
-for the remainder of the match if the opponent ever defects.
-
-The insights that payoff maximizers are better invaders and that handshakers
-are better resistors suggests that a strategy
-aware of the population distribution could choose to become a handshaker at
-a critical threshold and use a strategy better for invasion when in the
-minority. Information about the population distribution was not available
-to our strategies. Previous work has showed that strategies able to retain
-memory across matches can infer the population distribution and act in such
-a manner, resulting in a strategy effective at invasion and resistance
-\cite{Lee2015}.
-
-We did not attempt other objective functions that may serve to select for both
-invasion and resistance better than training at a starting population of
-$(N/2, N/2)$. Nevertheless our results suggest that there is not much room for
-improvement. Any handshake more sophisticated than always cooperate necessarily involves
-a defection. (A strategy with a handshake consisting of a long sequence of cooperations is
-effectively a grudger.) For TF3 or EvolvedLookerUp1\_1\_1 to become better resistors
-they need a longer or more strict handshake. But if this handshake involves
-a defection then likely the invasion ability is diminished for $N > 2$: the top
-invaders for larger $N$ are nice strategies that do not defect before their
-opponents. This is because good invaders need to maximize match payoff to benefit
-from fitness proportionate selection,
-and so in the absence of a handshake mechanism, knowledge of the population
-distribution, or some identifying label on the opponent,
-a strategy must be generally cooperative. Aggressive strategies
-are only effective invaders for the smallest $N$, dropping dramatically in rank
-as the population size increases.
-
-We did, however, attempt to evolve CS using finite state machines and lookup table
-based players,
-which resulted in some very similar strategies. In particular we evolved a
-lookup strategy that had a handshake of DC and played TFT with other players
-after a correct handshake while defecting otherwise, which is quite close in
-function to CS (full grudging is not possible with a lookup table of limited
-depth).
-
-Finally we note that it may be possible to achieve similar results with smaller
-capacity finite state machine players.
-
-\section*{Conclusion}
-
-A detailed empirical analysis of 164 strategies of the IPD within a pairwise
-Moran process has been carried out. All \(\binom{164}{2}=13,366\) possible
-ordered pairs of strategies have been placed in a Moran process with different
-starting values allowing each strategy to attempt to invade the other.
-This is the largest such experiment carried out and has led to many insights.
-
-When studying evolutionary processes it is vital to consider \(N>2\) since
-results for \(N=2\) cannot be used to extrapolate performance in larger
-populations. This was shown both observationally
- but also by
-considering the correlation of the ranks in different population sizes.
-
-Memory one strategies do not perform as well as longer memory strategies in general
-in this study. Several longer memory strategies were high performers for invasion,
-particularly the strategies which have been trained using a number of reinforcement
-learning algorithms. Interestingly they have been trained to perform well in
-tournaments and not Moran processes specifically. In some cases these strategies
-utilize all the history of play (the neural network strategies and the lookup
-table strategies, the latter using the first round and some number of trailing rounds).
-
-There are no memory one strategies in the top 5 performing strategies
-for \(N>3\). Training memory-one strategies specifically for the Moran process
-typically led to Grudger / Grim, a memory-one strategy with
-four-vector (1, 0, 0, 0). It appears to be the best resistor of the memory-one strategies.
-The highest performing memory-one strategy for invasion is PSO Gambler Mem 1,
-training to maximize total payout, which has four-vector $(1, 0.52173487, 0, 0.12050939)$.
-For comparison, training for maximum score difference between the player and the
-opponent resulted in a strategy nearly the same as Grudger, with four-vector
-$(0.9459, 0, 0, 0)$ (not included in the study).
-
-One of the major findings discussed, is
-the ability of strategies with a handshake mechanism to resist invasion. This
-was not only revealed for CS (a human designed strategy) but also for
-two FSM strategies (TF1 and TF2) specifically trained through an evolutionary
-process. In these two cases, the handshake mechanism was a product of the
-evolutionary process. Fig~\ref{fig:cooperation_rates} shows the cooperation
-rate of TF1, TF2, TF3 and CS
-for each round of a match against all the opponents in this study.
-This corresponds to the fraction of cooperation played by that strategy observed
-in a given round (out of the first 15) where each matchup is repeated 10000 times to
-obtain the mean.
-
-While TF3
-does not have a strict handshake mechanism it is clear that all these strategies
-start a match by cooperating. It is then evident that TF3 cooperates more than
-the other strategies thus explaining the difference in performance. It is also
-clear that CS only cooperates with itself and Handshake: it is a very aggressive
-strategy.
-
-\begin{figure}[!hbtp]
-    \centering
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF1_array.pdf}
-        \caption{TF1}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF2_array.pdf}
-        \caption{TF2}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_TF3_array.pdf}
-        \caption{TF3}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[width=\columnwidth]{./cooperation_0_0_10000_CS_array.pdf}
-        \caption{CS}
-    \end{subfigure}
-    \caption{Cooperation rate per round (over 10000 repetitions). Rows
-        correspond to all the strategies considered in this work (ordered
-    alphabetically by name). Columns correspond to round of an IPD match.}
-    \label{fig:cooperation_rates}
-\end{figure}
-
-These findings are important for the ongoing understanding of
-population dynamics and offer evidence for some of the shortcomings of low
-memory which has started to be recognised by the community \cite{Hilbe2017}.
-
-All source code for this work has been written in a sustainable manner: it is
-open source, under version control and tested which ensures that all results can
-be reproduced \cite{Prlic2012, Sandve2013, Wilson2014}. The raw data as well as
-the processed data has also been properly archived and can be found
-at \cite{data}.
-
-There are many opportunities to build on this work. In particular, an analysis
-of the effect of noise should offer insights regarding the stability of the findings,
-particularly for the handshaking strategies. They may be less dominant for
-larger amounts of noise since the handshaking mechanisms may become brittle.
-There are many other variations to explore including populations with more
-than one type, spatial structure, and mutation.
-
-One final point to recognise: the large set of strategies used here does not in
-itself constitute an authoritative set. Whilst it is not only large but also very
-diverse, the results (and rankings) presented might change given a different set
-of strategies. A further piece of work could look at subgroups of strategies and
-how they fair against other subgroups. Note that because of the open nature of
-the work here (not only is the source code archived but so is the data) this and
-any other further analysis is possible to carry out.
-
-\section*{Acknowledgements}
-
-This work was performed using the computational facilities of the Advanced
-Research Computing @ Cardiff (ARCCA) Division, Cardiff University.
-
-A variety of software libraries have been used in this work:
-
-\begin{itemize}
-    \item The Axelrod library (IPD strategies and Moran processes)
-        \cite{axelrodproject}.
-    \item The matplotlib library (visualisation) \cite{hunter2007matplotlib}.
-    \item The pandas and numpy libraries (data manipulation)
-        \cite{mckinney2010data, walt2011numpy}.
-\end{itemize}
-
-\nolinenumbers
-
-\begin{thebibliography}{10}
-
-\bibitem{Adami2013}
-Christoph Adami and Arend Hintze.
-\newblock {Evolutionary instability of zero-determinant strategies demonstrates
-  that winning is not everything.}
-\newblock {\em Nature communications}, 4(1):2193, 2013.
-
-\bibitem{adami2016evolutionary}
-Christoph Adami, Jory Schossau, and Arend Hintze.
-\newblock {Evolutionary game theory using agent-based methods}.
-\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
-
-\bibitem{affenzeller2009genetic}
-Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
-\newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
-  Practical Applications}.
-\newblock Numerical Insights. CRC Press, 2009.
-
-\bibitem{Nowak2017}
-Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
-  Shing-Tung Yau, and Martin~A Nowak.
-\newblock {Evolutionary dynamics on any population structure}.
-\newblock 544:227--230, March 2017.
-
-\bibitem{Ashlock2015}
-Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
-\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
-  Agents}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 7(1):53--65, 2015.
-
-\bibitem{Ashlock2008}
-Daniel Ashlock and Eun-Youn Kim.
-\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
-  dilemma strategies}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
-  2008.
-
-\bibitem{Ashlock2006}
-Wendy Ashlock and Daniel Ashlock.
-\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
-  with different population sizes}.
-\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
-  pages 297--304. IEEE, 2006.
-
-\bibitem{Ashlock2014}
-Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
-\newblock {The evolution of exploitation}.
-\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
-  Symposium on}, pages 135--142. IEEE, 2014.
-
-\bibitem{Axelrod1980a}
-Robert Axelrod.
-\newblock {Effective choice in the prisoner's dilemma}.
-\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
-
-\bibitem{Axelrod1980b}
-Robert Axelrod.
-\newblock {More Effective Choice in the Prisoner's Dilemma}.
-\newblock {\em Journal of Conflict Resolution}, 24(3):379--403, 1980.
-
-\bibitem{Axelrod1984}
-Robert Axelrod.
-\newblock {\em The Evolution of Cooperation}.
-\newblock Basic books. Basic Books, 1984.
-
-\bibitem{Baek2016}
-{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
-  A}.
-\newblock {Comparing reactive and memory- one strategies of direct
-  reciprocity}.
-\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
-
-\bibitem{Banks1990}
-Jeffrey~S Banks and Rangarajan~K Sundaram.
-\newblock {Repeated games, finite automata, and complexity}.
-\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
-
-\bibitem{Beaufils1997}
-Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
-\newblock {Our meeting with gradual, a good strategy for the iterated
-  prisoner’s dilemma}.
-\newblock In {\em Proceedings of the Fifth International Workshop on the
-  Synthesis and Simulation of Living Systems}, pages 202--209, 1997.
-
-\bibitem{brown2001interval}
-Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
-\newblock Interval estimation for a binomial proportion.
-\newblock {\em Statistical science}, pages 101--117, 2001.
-
-\bibitem{Andre2013}
-Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
-\newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
-\newblock pages 1--6, 2013.
-
-\bibitem{Eckhart2015}
-Arnold Eckhart.
-\newblock Coopsim v0.9.9 beta 6.
-\newblock https://github.com/jecki/CoopSim/, 2015.
-
-\bibitem{Flood1958}
-Merrill~M Flood.
-\newblock {Some Experimental Games}, 1958.
-
-\bibitem{Frean1994}
-Marcus~R Frean.
-\newblock {The prisoner's dilemma without synchrony}.
-\newblock {\em Proceedings of the Royal Society of London B: Biological
-  Sciences}, 257(1348):75--79, 1994.
-
-\bibitem{Gaudesi2016}
-Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
-\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
-  dilemma tournaments}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 8(3):288--300, 2016.
-
-\bibitem{marc_harper_2017_824264}
-Marc Harper, Vince Knight, and Martin Jones.
-\newblock Axelrod-python/axelrod-dojo: v0.0.1.
-\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
-
-\bibitem{Harper2017}
-Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
-  Glynatsi, and Owen Campbell.
-\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
-  Prisoner's Dilemma}.
-\newblock arXiv:1707.06307, 2017.
-
-\bibitem{Hilbe2017}
-Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
-  Nowak.
-\newblock {Memory-n strategies of direct reciprocity}.
-\newblock {\em Proceedings of the National Academy of Sciences}, page
-  201621239, 2017.
-
-\bibitem{Hilbe2013}
-Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
-\newblock {Adaptive dynamics of extortion and compliance}.
-\newblock {\em PloS one}, 8(11):e77886, 2013.
-
-\bibitem{hunter2007matplotlib}
-John~D Hunter.
-\newblock {Matplotlib: A 2D graphics environment}.
-\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
-
-\bibitem{kendall2007iterated}
-Graham Kendall, Xin Yao, and Siang~Y Chong.
-\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
-\newblock Advances in natural computation. World Scientific, 2007.
-
-\bibitem{Knight2016}
-Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
-  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
-  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
-  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
-  Timothy Standen, Luis Visintini, and Karl Molden.
-\newblock {An Open Framework for the Reproducible Study of the Iterated
-  Prisoner ' s Dilemma}.
-\newblock 2016.
-
-\bibitem{data}
-Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
-\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
-  Self-Recognition Mechanisms: an empirical study of the Moran process for the
-  iterated Prisoner's dilemma using reinforcement learning}.
-\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
-
-\bibitem{Kraines1989}
-David Kraines and Vivian Kraines.
-\newblock {Pavlov and the prisoner's dilemma}.
-\newblock {\em Theory and decision}, 26(1):47--79, 1989.
-
-\bibitem{Kuhn2017}
-Steven Kuhn.
-\newblock Prisoner's dilemma.
-\newblock In Edward~N. Zalta, editor, {\em The Stanford Encyclopedia of
-  Philosophy}. Metaphysics Research Lab, Stanford University, spring 2017
-  edition, 2017.
-
-\bibitem{Lee2015}
-Christopher Lee, Marc Harper, and Dashiell Fryer.
-\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
-\newblock {\em Plos One}, 10(3):e0120625, 2015.
-
-\bibitem{Li2011}
-Jiawei Li, Philip Hingston, and Graham Kendall.
-\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
-  Dilemma Competitions}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 3(4):348--360, 2011.
-
-\bibitem{Li2009}
-Jiawei Li and Graham Kendall.
-\newblock {A strategy with novel evolutionary features for the iterated
-  prisoner's dilemma.}
-\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
-
-\bibitem{Li2014}
-Jiawei Li and Graham Kendall.
-\newblock {The effect of memory size on the evolutionary stability of
-  strategies in iterated prisoner's dilemma}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
-  2014.
-
-\bibitem{Prison1998}
-LIFL.
-\newblock Prison.
-\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
-
-\bibitem{Mathieu2015}
-Philippe Mathieu and Jean-Paul Delahaye.
-\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
-  Abstract)}.
-\newblock {\em 14th International Conference on Autonomous Agents and
-  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
-
-\bibitem{mckinney2010data}
-Wes McKinney et~al.
-\newblock Data structures for statistical computing in python.
-\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
-  445, pages 51--56. van der Voort S, Millman J, 2010.
-
-\bibitem{Mittal2009}
-Shashi Mittal and Kalyanmoy Deb.
-\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
-  multiple conflicting objectives}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
-  2009.
-
-\bibitem{Moran1957}
-Patrick A~P Moran.
-\newblock {Random Processes in Genetics}.
-\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
-  Society}, 54(1):60--71, 1957.
-
-\bibitem{Nachbar1992}
-John~H Nachbar.
-\newblock {Evolution in the finitely repeated prisoner's dilemma}.
-\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
-  1992.
-
-\bibitem{Nowak}
-Martin~A Nowak.
-\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
-\newblock Cambridge: Harvard University Press.
-
-\bibitem{Nowak1993}
-Martin~A Nowak and Karl Sigmund.
-\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
-  the Prisoner's Dilemma game.}
-\newblock {\em Nature}, 364(6432):56--58, 1993.
-
-\bibitem{Press2012}
-William~H Press and Freeman~J Dyson.
-\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
-  evolutionary opponent.}
-\newblock {\em Proceedings of the National Academy of Sciences of the United
-  States of America}, 109(26):10409--13, 2012.
-
-\bibitem{Prlic2012}
-Andreas Prlić and James~B Procter.
-\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
-\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
-
-\bibitem{axelrodproject}
-The~Axelrod project developers.
-\newblock Axelrod: v2.9.0.
-\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
-
-\bibitem{Robson1990}
-Arthur~J Robson.
-\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
-  handshake}.
-\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
-
-\bibitem{Sandve2013}
-Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
-\newblock {Ten Simple Rules for Reproducible Computational Research}.
-\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
-
-\bibitem{Stewart2012}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  109(26):10134--10135, 2012.
-
-\bibitem{stewart2013extortion}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {From extortion to generosity, evolution in the iterated prisoner’s
-  dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  110(38):15348--15353, 2013.
-
-\bibitem{Tzafestas2000}
-Elpida Tzafestas.
-\newblock {Toward adaptive cooperative behavior}.
-\newblock {\em From Animals to animals: Proceedings of the 6th International
-  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
-  2000.
-
-\bibitem{PD2017}
-Unkwown.
-\newblock www.prisoners-dilemma.com.
-\newblock http://www.prisoners-dilemma.com/, 2017.
-
-\bibitem{Berg2015}
-Pieter Van~den Berg and Franz~J Weissing.
-\newblock {The importance of mechanisms for the evolution of cooperation}.
-\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
-  Society, 2015.
-
-\bibitem{walt2011numpy}
-St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
-\newblock {The NumPy array: a structure for efficient numerical computation}.
-\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
-
-\bibitem{West2016}
-Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
-\newblock {The prisoner’s dilemma as a cancer model}.
-\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
-
-\bibitem{Wilson2014}
-Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
-  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
-  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
-\newblock {Best Practices for Scientific Computing}.
-\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
-
-\bibitem{Axelrod1995}
-Jianzhong Wu and Robert Axelrod.
-\newblock {How to cope with noise in the iterated prisoner's dilemma}.
-\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
-
-\end{thebibliography}
-
-\appendix
-
-\section{Appendix A: List of players}\label{app:list_of_players}
-
-\footnotesize
-\begin{enumerate}
-\item $\phi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $\pi$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item $e$ - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ALLCorALLD - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Adaptive - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Pavlov 2006 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Adaptive Pavlov 2011 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Adaptive Tit For Tat: 0.5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Tzafestas2000}
-\item Aggravater - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Alternator - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1984, Mittal2009}
-\item Alternator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Anti Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Hilbe2013}
-\item AntiCycler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Appeaser - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Arrogant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Better and Better - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Bully - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Nachbar1992}
-\item Calculator - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Cautious QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item CollectiveStrategy(\textbf{CS}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2009}
-\item Contrite Tit For Tat(\textbf{CTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1995}
-\item Cooperator - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Cooperator Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Cycler CCCCCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCCD - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{axelrodproject}
-\item Cycler CCCDCD - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Cycler CCD - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Cycler DC - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Cycler DDC - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mittal2009}
-\item Davis: 10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Defector - \textit{Deterministic} - \textit{Memory depth}: 0. \cite{Axelrod1984, Mittal2009, Press2012}
-\item Defector Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Desperate - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Doubler - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item EasyGo - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011, Prison1998}
-\item Eatherley - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item Eventual Cycle Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved ANN 5 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Evolved FSM 16 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 16 Noise 05 - \textit{Deterministic} - \textit{Memory depth}: 16 - \textit{Number of states}: 14. \cite{axelrodproject}
-\item Evolved FSM 4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{axelrodproject}
-\item Evolved HMM 5 - \textit{Stochastic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item EvolvedLookerUp1\_1\_1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item EvolvedLookerUp2\_2\_2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item FSM Player: [(0, 'C', 0, 'C'), (0, 'D', 3, 'C'), (1, 'C', 5, 'D'), (1, 'D', 0, 'C'), (2, 'C', 3, 'C'), (2, 'D', 2, 'D'), (3, 'C', 4, 'D'), (3, 'D', 6, 'D'), (4, 'C', 3, 'C'), (4, 'D', 1, 'D'), (5, 'C', 6, 'C'), (5, 'D', 3, 'D'), (6, 'C', 6, 'D'), (6, 'D', 6, 'D'), (7, 'C', 7, 'D'), (7, 'D', 5, 'C')], 0, C(\textbf{TF3}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 8.
-\item FSM Player: [(0, 'C', 13, 'D'), (0, 'D', 12, 'D'), (1, 'C', 3, 'D'), (1, 'D', 4, 'D'), (2, 'C', 14, 'D'), (2, 'D', 9, 'D'), (3, 'C', 0, 'C'), (3, 'D', 1, 'D'), (4, 'C', 1, 'D'), (4, 'D', 2, 'D'), (5, 'C', 12, 'C'), (5, 'D', 6, 'C'), (6, 'C', 1, 'C'), (6, 'D', 14, 'D'), (7, 'C', 12, 'D'), (7, 'D', 2, 'D'), (8, 'C', 7, 'D'), (8, 'D', 9, 'D'), (9, 'C', 8, 'D'), (9, 'D', 0, 'D'), (10, 'C', 2, 'C'), (10, 'D', 15, 'C'), (11, 'C', 7, 'D'), (11, 'D', 13, 'D'), (12, 'C', 3, 'C'), (12, 'D', 8, 'D'), (13, 'C', 7, 'C'), (13, 'D', 10, 'D'), (14, 'C', 10, 'D'), (14, 'D', 7, 'D'), (15, 'C', 15, 'C'), (15, 'D', 11, 'D')], 0, C(\textbf{TF2}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item FSM Player: [(0, 'C', 7, 'C'), (0, 'D', 1, 'C'), (1, 'C', 11, 'D'), (1, 'D', 11, 'D'), (2, 'C', 8, 'D'), (2, 'D', 8, 'C'), (3, 'C', 3, 'C'), (3, 'D', 12, 'D'), (4, 'C', 6, 'C'), (4, 'D', 3, 'C'), (5, 'C', 11, 'C'), (5, 'D', 8, 'D'), (6, 'C', 13, 'D'), (6, 'D', 14, 'C'), (7, 'C', 4, 'D'), (7, 'D', 2, 'D'), (8, 'C', 14, 'D'), (8, 'D', 8, 'D'), (9, 'C', 0, 'C'), (9, 'D', 10, 'D'), (10, 'C', 8, 'C'), (10, 'D', 15, 'C'), (11, 'C', 6, 'D'), (11, 'D', 5, 'D'), (12, 'C', 6, 'D'), (12, 'D', 9, 'D'), (13, 'C', 9, 'D'), (13, 'D', 8, 'D'), (14, 'C', 8, 'D'), (14, 'D', 13, 'D'), (15, 'C', 4, 'C'), (15, 'D', 5, 'C')], 0, C(\textbf{TF1}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\) - \textit{Number of states}: 16.
-\item Feld: 1.0, 0.5, 200 - \textit{Stochastic} - \textit{Memory depth}: 200. \cite{Axelrod1980a}
-\item Firm But Fair - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Frean1994}
-\item Fool Me Forever - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fool Me Once - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Fool Me Once: 0.05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgetful Grudger - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Forgiver - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Forgiving Tit For Tat(\textbf{FTfT}) - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Fortress3 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2006}
-\item Fortress4 - \textit{Deterministic} - \textit{Memory depth}: 4 - \textit{Number of states}: 4. \cite{Ashlock2006}
-\item GTFT: 0.33 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Gaudesi2016, Nowak1993}
-\item General Soft Grudger: n=1,d=4,c=2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Gradual - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Beaufils1997}
-\item Gradual Killer: ('D', 'D', 'D', 'D', 'D', 'C', 'C') - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grofman - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Grudger - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Banks1990, Beaufils1997, Berg2015, Li2011}
-\item GrudgerAlternator - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Grumpy: Nice, 10, -10 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Handshake - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Robson1990}
-\item Hard Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Mittal2009}
-\item Hard Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Hard Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Hard Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Hard Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Hard Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Hard Tit For 2 Tats(\textbf{HTf2T}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Stewart2012}
-\item Hard Tit For Tat(\textbf{HTfT}) - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{PD2017}
-\item Hesitant QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Hopeless - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Inverse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Inverse Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Axelrod1980a, Stewart2012}
-\item Level Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Eckhart2015}
-\item Limited Retaliate 2: 0.08, 15 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate 3: 0.05, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Limited Retaliate: 0.1, 20 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item MEM2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2014}
-\item Math Constant Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter Aggressive: 7 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Meta Hunter: 6 players - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Naive Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Negation - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{PD2017}
-\item Nice Average Copier - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Nydegger - \textit{Deterministic} - \textit{Memory depth}: 3. \cite{Axelrod1980a}
-\item Omega TFT: 3, 8 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{kendall2007iterated}
-\item Once Bitten - \textit{Deterministic} - \textit{Memory depth}: 12. \cite{axelrodproject}
-\item Opposite Grudger - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 1\_1\_1 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler 2\_2\_2 Noise 05 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item PSO Gambler Mem1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Predator - \textit{Deterministic} - \textit{Memory depth}: 9 - \textit{Number of states}: 9. \cite{Ashlock2006}
-\item Prober - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Li2011}
-\item Prober 2 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 3 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Prober 4 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Pun1 - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2006}
-\item Punisher - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Raider - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 4. \cite{Ashlock2014}
-\item Random Hunter - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Random: 0.5 - \textit{Stochastic} - \textit{Memory depth}: 0. \cite{Axelrod1980a, Tzafestas2000}
-\item Remorseful Prober: 0.1 - \textit{Stochastic} - \textit{Memory depth}: 2. \cite{Li2011}
-\item Resurrection - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Eckhart2015}
-\item Retaliate 2: 0.08 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate 3: 0.05 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Retaliate: 0.1 - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Revised Downing: True - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Ripoff - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 3. \cite{Ashlock2008}
-\item Risky QLearner - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item SelfSteem - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item ShortMem - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{Andre2013}
-\item Shubik - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980a}
-\item Slow Tit For Two Tats - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{axelrodproject}
-\item Slow Tit For Two Tats 2 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Prison1998}
-\item Sneaky Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Soft Go By Majority - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1984, Mittal2009}
-\item Soft Go By Majority: 10 - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Soft Go By Majority: 20 - \textit{Deterministic} - \textit{Memory depth}: 20. \cite{axelrodproject}
-\item Soft Go By Majority: 40 - \textit{Deterministic} - \textit{Memory depth}: 40. \cite{axelrodproject}
-\item Soft Go By Majority: 5 - \textit{Deterministic} - \textit{Memory depth}: 5. \cite{axelrodproject}
-\item Soft Grudger - \textit{Deterministic} - \textit{Memory depth}: 6. \cite{Li2011}
-\item Soft Joss: 0.9 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Prison1998}
-\item SolutionB1 - \textit{Deterministic} - \textit{Memory depth}: 3 - \textit{Number of states}: 3. \cite{Ashlock2015}
-\item SolutionB5 - \textit{Deterministic} - \textit{Memory depth}: 5 - \textit{Number of states}: 6. \cite{Ashlock2015}
-\item Spiteful Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Stochastic Cooperator - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Adami2013}
-\item Stochastic WSLS: 0.05 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item Suspicious Tit For Tat - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Beaufils1997, Hilbe2013}
-\item Tester - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Axelrod1980b}
-\item ThueMorse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item ThueMorseInverse - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Thumper - \textit{Deterministic} - \textit{Memory depth}: 2 - \textit{Number of states}: 2. \cite{Ashlock2008}
-\item Tit For 2 Tats(\textbf{Tf2T}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item Tit For Tat(\textbf{TfT}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Axelrod1980a}
-\item Tricky Cooperator - \textit{Deterministic} - \textit{Memory depth}: 10. \cite{axelrodproject}
-\item Tricky Defector - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{axelrodproject}
-\item Tullock: 11 - \textit{Stochastic} - \textit{Memory depth}: 11. \cite{Axelrod1980a}
-\item Two Tits For Tat(\textbf{2TfT}) - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Axelrod1984}
-\item VeryBad - \textit{Deterministic} - \textit{Memory depth}: \(\infty\). \cite{Andre2013}
-\item Willing - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Berg2015}
-\item Win-Shift Lose-Stay: D(\textbf{WShLSt}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Li2011}
-\item Win-Stay Lose-Shift: C(\textbf{WSLS}) - \textit{Deterministic} - \textit{Memory depth}: 1. \cite{Kraines1989, Nowak1993, Stewart2012}
-\item Winner12 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Winner21 - \textit{Deterministic} - \textit{Memory depth}: 2. \cite{Mathieu2015}
-\item Worse and Worse - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 2 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item Worse and Worse 3 - \textit{Stochastic} - \textit{Memory depth}: \(\infty\). \cite{Prison1998}
-\item ZD-Extort-2 v2: 0.125, 0.5, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-Extort-2: 0.1111111111111111, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-Extort-4: 0.23529411764705882, 0.25, 1 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{axelrodproject}
-\item ZD-GEN-2: 0.125, 0.5, 3 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\item ZD-GTFT-2: 0.25, 0.5 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Stewart2012}
-\item ZD-SET-2: 0.25, 0.0, 2 - \textit{Stochastic} - \textit{Memory depth}: 1. \cite{Kuhn2017}
-\end{enumerate}
-
-\section{Appendix B: Supplementary figures}
-
-\begin{itemize}
-    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
-for each strategy. The mean and error bars are shown against the collection of
-all opponents.
-
-    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
-\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
-the collection of all opponents.
-
-    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
-ranks of each strategy according to mean absorption probability across all
-population sizes.
-\end{itemize}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
-    \label{invasion-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_invade.pdf}
-    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
-    \label{invasion-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_3_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
-    \label{resistance-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_4_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_5_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_6_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_7_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_8_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_9_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_10_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_11_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_12_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_13_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\textwidth]{./boxplot_14_resist.pdf}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
-    \label{resistance-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_invade.pdf}
-    \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
-    \label{fig:ranks_v_size_invade}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_resist.pdf}
-    \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_resist}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    \includegraphics[width=\columnwidth]{./average_rank_vs_population_size_coexist.pdf}
-    \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
-    population sizes.}
-    \label{fig:ranks_v_size_coexist}
-\end{figure}
-
 \end{document}

### 2018-08-10 rename-files-for-plos.sh

@@ -1,37 +1,42 @@
-# Script to rename all images files produced from running main.ipynb
-cp Alternator_v_WSLS.eps Fig1.eps
-cp Calculator_v_Arrogant_QLearner.eps Fig2.eps
-cp average_rank_vs_population_size_invade.eps Fig3.eps
-cp average_rank_vs_population_size_resist.eps Fig4.eps
-cp average_rank_vs_population_size_coexist.eps Fig5.eps
-cp correlation_heatmap_invade.eps Fig6.eps
-cp correlation_heatmap_resist.eps Fig7.eps
-cp correlation_heatmap_coexist.eps Fig8.eps
-cp cooperation_0_0_10000_TF1_array.eps Fig9.eps
-cp cooperation_0_0_10000_TF2_array.eps Fig10.eps
-cp cooperation_0_0_10000_TF3_array.eps Fig11.eps
-cp cooperation_0_0_10000_CS_array.eps Fig12.eps
-cp boxplot_3_invade.eps Fig13.eps
-cp boxplot_4_invade.eps Fig14.eps
-cp boxplot_5_invade.eps Fig15.eps
-cp boxplot_6_invade.eps Fig16.eps
-cp boxplot_7_invade.eps Fig17.eps
-cp boxplot_8_invade.eps Fig18.eps
-cp boxplot_9_invade.eps Fig19.eps
-cp boxplot_10_invade.eps Fig20.eps
-cp boxplot_11_invade.eps Fig21.eps
-cp boxplot_12_invade.eps Fig22.eps
-cp boxplot_13_invade.eps Fig23.eps
-cp boxplot_14_invade.eps Fig24.eps
-cp boxplot_3_resist.eps Fig25.eps
-cp boxplot_4_resist.eps Fig26.eps
-cp boxplot_5_resist.eps Fig27.eps
-cp boxplot_6_resist.eps Fig28.eps
-cp boxplot_7_resist.eps Fig29.eps
-cp boxplot_8_resist.eps Fig30.eps
-cp boxplot_9_resist.eps Fig31.eps
-cp boxplot_10_resist.eps Fig32.eps
-cp boxplot_11_resist.eps Fig33.eps
-cp boxplot_12_resist.eps Fig34.eps
-cp boxplot_13_resist.eps Fig35.eps
-cp boxplot_14_resist.eps Fig36.eps
+# Script to rename all images files produced from running main.ipynb and the
[…]

### 2018-10-05 main.tex
Final editorial requests:
- Remove footnote;
- Remove figures;
- Fix bibliographic style.
- Re order bibliographic items.
- Remove the subfigures.

@@
     \centering
-    \includegraphics[draft, width=\textwidth]{Fig1.eps}
+    %\includegraphics[ width=\textwidth]{Fig1.eps}
     \caption{A diagrammatic representation of a Moran process.}
@@
 software is (similarly to the Axelrod library) available on
-GitHub\footnote{\url{https://github.com/Axelrod-Python/axelrod-dojo}}
+GitHub~(\url{https://github.com/Axelrod-Python/axelrod-dojo})
 with documentation to
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{Fig2.eps}
+    %\includegraphics[ width=\textwidth]{Fig2.eps}
     \caption{TF1: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{Fig3.eps}
+    %\includegraphics[ width=\textwidth]{Fig3.eps}
     \caption{TF2: a 16 state finite state machine with a handshake leading to
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{Fig4.eps}
+    %\includegraphics[ width=\textwidth]{Fig4.eps}
     \caption{TF3: an 8 state finite state machine.}
@@
 confidence interval computed using an asymptotic normal approximation is also
-included \cite{brown2001interval}).
+included~\cite{brown2001interval}).
 The points represent the simulated
@@
     \centering
-    \includegraphics[draft, width=.95\columnwidth]{./Fig5.eps}
+    %\includegraphics[ width=.95\columnwidth]{./Fig5.eps}
     \caption{Comparison of theoretic and actual Moran Process fixation
@@
     \centering
-    \includegraphics[draft, width=.95\columnwidth]{./Fig6.eps}
+    %\includegraphics[ width=.95\columnwidth]{./Fig6.eps}
     \caption{Comparison of theoretic and actual Moran Process
@@
     \centering
-    \includegraphics[draft, width=\columnwidth]{./Fig7.eps}
+    %\includegraphics[ width=\columnwidth]{./Fig7.eps}
     \caption{\textbf{Invasion}: Ranks of all strategies according to \(x_1\) for different population sizes.}
@@
     \centering
-    \includegraphics[draft, width=\columnwidth]{./Fig8.eps}
+    %\includegraphics[ width=\columnwidth]{./Fig8.eps}
     \caption{\textbf{Resistance}: Ranks of all strategies according to \(x_{N-1}\) for different
@@
     \centering
-    \includegraphics[draft, width=\columnwidth]{./Fig9.eps}
+    %\includegraphics[ width=\columnwidth]{./Fig9.eps}
     \caption{Fixation ranks of all strategies according to \(x_{N/2}\) for different
@@
     \centering
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig10.eps}
-        \caption{Rank based on \(x_1\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig11.eps}
-        \caption{Rank based on \(x_{N - 1}\)}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[t]{.3\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig12.eps}
-        \caption{Rank based on \(x_{N/2}\)}
-    \end{subfigure}
+    %\includegraphics[ width=\columnwidth]{./Fig10.eps}
     \caption{Heatmap of correlation coefficients of rankings by population size.}
@@
     \centering
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig13.eps}
-        \caption{TF1}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig14.eps}
-        \caption{TF2}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig15.eps}
-        \caption{TF3}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{.5\columnwidth}
-        \centering
-        \includegraphics[draft, width=\columnwidth]{./Fig16.eps}
-        \caption{CS}
-    \end{subfigure}
+    %\includegraphics[ width=\columnwidth]{./Fig11.eps}
     \caption{Cooperation rate per round (over 10000 repetitions). Rows
@@
 
+\bibitem{Flood1958}
+Flood M.
+\newblock {Some Experimental Games}, 1958.
+
+\bibitem{Axelrod1980a}
+Axelrod R.
+\newblock {Effective choice in the prisoner's dilemma}.
+\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
+
+\bibitem{Knight2016}
+Knight V, Campbell O, Harper M, Langner K, Campbell J,
+  Campbell T, Carney A, Chorley M, Davidson-pilon C,
+  Glynatsi N, Ehrlich T, Jones M, Koutsovoulos G, Muller J, Palmer G, Petunov P, Slavin P,
+  Standen T, Visintini L, and Molden K.
+\newblock {An Open Framework for the Reproducible Study of the Iterated
+  Prisoner ' s Dilemma}.
+\newblock 2016.
+
+\bibitem{Press2012}
+Press W and Dyson F.
+\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
+  evolutionary opponent.}
+\newblock {\em Proceedings of the National Academy of Sciences of the United
+  States of America}, 109(26):10409--13, 2012.
+
+\bibitem{Moran1957}
+Moran P.
+\newblock {Random Processes in Genetics}.
+\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
+  Society}, 54(1):60--71, 1957.
+
+\bibitem{Nowak}
+Nowak M.
+\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
+\newblock Cambridge: Harvard University Press.
+
+\bibitem{stewart2013extortion}
+Stewart A and Plotkin J.
+\newblock {From extortion to generosity, evolution in the iterated prisoner’s
+  dilemma}.
+\newblock {\em Proceedings of the National Academy of Sciences},
+  110(38):15348--15353, 2013.
+
+\bibitem{axelrodproject}
+The~Axelrod project developers.
+\newblock Axelrod: v2.9.0.
+\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
+
+\bibitem{adami2016evolutionary}
+Adami C, Schossau J, and Hintze A.
+\newblock {Evolutionary game theory using agent-based methods}.
+\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
+
+\bibitem{Robson1990}
+Robson A.
+\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
+  handshake}.
+\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
+
+\bibitem{Mateo2003}
+Mateo J.
+\newblock {Kin recognition in ground squirrels and other rodents}.
+\newblock In {\em Journal of Mammalogy}, 84 (4), 1163--1181
+
+\bibitem{West2016}
+West J, Hasnain Z, Mason J, and Newton P.
+\newblock {The prisoner’s dilemma as a cancer model}.
+\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
+
+\bibitem{Nowak2017}
+Allen B, Lippner G, Chen Y, Fotouhi B, Momeni N,
+  Shing-Tung Yau, and Martin~A Nowak.
+\newblock {Evolutionary dynamics on any population structure}.
+\newblock 544:227--230, March 2017.
+
+\bibitem{Li2014}
+Li J and Kendall G.
+\newblock {The effect of memory size on the evolutionary stability of
+  strategies in iterated prisoner's dilemma}.
+\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
+  2014.
+
+\bibitem{Baek2016}
+{Seung Ki B, Hyeong-chai J, Christian H and Martin N}.
+\newblock {Comparing reactive and memory- one strategies of direct
+  reciprocity}.
+\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
+
+\bibitem{Lee2015}
+Lee C, Harper M, and Fryer D.
+\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
+\newblock {\em Plos One}, 10(3):e0120625, 2015.
+
+\bibitem{Hilbe2017}
+Hilbe C, Martinez-Vaquero L, Chatterjee K, and Nowak M.
+\newblock {Memory-n strategies of direct reciprocity}.
+\newblock {\em Proceedings of the National Academy of Sciences}, page
+  201621239, 2017.
+
 \bibitem{Adami2013}
-Christoph Adami and Arend Hintze.
+Adami C and Hintze A.
 \newblock {Evolutionary instability of zero-determinant strategies demonstrates
@@
 
-\bibitem{adami2016evolutionary}
-Christoph Adami, Jory Schossau, and Arend Hintze.
-\newblock {Evolutionary game theory using agent-based methods}.
-\newblock {\em Physics of Life Reviews}, 19(Supplement C):1 -- 26, 2016.
+\bibitem{Harper2017}
+Harper M, Knight V, Jones M, Koutsovoulos G, Glynatsi N , and Campbell O.
+\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
+  Prisoner's Dilemma}.
+\newblock {\em PLOS ONE}, 12(12): 12 2017.
 
 \bibitem{affenzeller2009genetic}
-Michael Affenzeller, Stefan Wagner, Stephan Winkler, and Andreas Beham.
+Affenzeller M, Wagner S, Winkler S, and Beham A.
 \newblock {\em Genetic Algorithms and Genetic Programming: Modern Concepts and
@@
 
-\bibitem{Nowak2017}
-Benjamin Allen, Gabor Lippner, Yu-Ting Chen, Babak Fotouhi, Naghmeh Momeni,
-  Shing-Tung Yau, and Martin~A Nowak.
-\newblock {Evolutionary dynamics on any population structure}.
-\newblock 544:227--230, March 2017.
-
-\bibitem{Ashlock2015}
-Daniel Ashlock, Joseph~Alexander Brown, and Philip Hingston.
-\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
-  Agents}.
+\bibitem{Ashlock2006}
+Ashlock W and Ashlock D.
+\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
+  with different population sizes}.
+\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
+  pages 297--304. IEEE, 2006.
+
+\bibitem{Gaudesi2016}
+Gaudesi M, Piccolo E, Squillero G, and Tonda A.
+\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
+  dilemma tournaments}.
 \newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 7(1):53--65, 2015.
-
-\bibitem{Ashlock2008}
-Daniel Ashlock and Eun-Youn Kim.
-\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
-  dilemma strategies}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
-  2008.
+  Games}, 8(3):288--300, 2016.
+
+\bibitem{marc_harper_2017_824264}
+Harper M, Knight V, and Jones M.
+\newblock Axelrod-python/axelrod-dojo: v0.0.1.
+\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
+
+\bibitem{AshlockBook}
+Ashlock D.
+\newblock{Evolutionary computation for modeling and optimization},
+\newblock{Springer Science \& Business Media}
+2006
 
 \bibitem{Ashlock2007}
-Wendy Ashlock
+Ashlock W
 \newblock {Why some representations are more cooperative than others for
@@
 
-\bibitem{Ashlock2006}
-Wendy Ashlock and Daniel Ashlock.
-\newblock {Changes in prisoner’s dilemma strategies over evolutionary time
-  with different population sizes}.
-\newblock In {\em Evolutionary Computation, 2006. CEC 2006. IEEE Congress on},
-  pages 297--304. IEEE, 2006.
-
-\bibitem{AshlockBook}
-Daniel Ashlock.
-\newblock{Evolutionary computation for modeling and optimization},
-\newblock{Springer Science \& Business Media}
-2006
-
-\bibitem{Ashlock2014}
-Wendy Ashlock, Jeffrey Tsang, and Daniel Ashlock.
-\newblock {The evolution of exploitation}.
-\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
-  Symposium on}, pages 135--142. IEEE, 2014.
-
-\bibitem{Axelrod1980a}
-Robert Axelrod.
-\newblock {Effective choice in the prisoner's dilemma}.
-\newblock {\em Journal of conflict resolution}, 24(1):3--25, 1980.
+\bibitem{data}
+Knight V, Harper M, and Glynatsi N.
+\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
+  Self-Recognition Mechanisms: an empirical study of the Moran process for the
+  iterated Prisoner's dilemma using reinforcement learning}.
+\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
+
+\bibitem{Prison1998}
+LIFL.
+\newblock Prison.
+\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
+
+\bibitem{Li2009}
+Li J and Kendall G.
+\newblock {A strategy with novel evolutionary features for the iterated
+  prisoner's dilemma.}
+\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
+
+\bibitem{brown2001interval}
+Brown L, Cai T, and DasGupta A.
+\newblock Interval estimation for a binomial proportion.
+\newblock {\em Statistical science}, pages 101--117, 2001.
+
+\bibitem{Prlic2012}
+Prlić A and Procter J.
+\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
+\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
+
+\bibitem{Sandve2013}
+Sandve G, Nekrutenko A, Taylor J, and Hovig E.
+\newblock {Ten Simple Rules for Reproducible Computational Research}.
+\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
+
+\bibitem{Wilson2014}
+Wilson G , Aruliah D, Brown T, Chue~Hong N, Davis M ,
+  Guy R , Haddock S , Huff K, Mitchell I , Plumbley M , 
+  Waugh B , White E , and Wilson P.
+\newblock {Best Practices for Scientific Computing}.
+\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
+
+\bibitem{hunter2007matplotlib}
+Hunter J.
+\newblock {Matplotlib: A 2D graphics environment}.
+\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
+
+\bibitem{mckinney2010data}
+McKinney W et~al.
+\newblock Data structures for statistical computing in python.
+\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
+  445, pages 51--56. van der Voort S, Millman J, 2010.
+
+\bibitem{walt2011numpy}
+van~der Walt S, Colbert C, and Varoquaux G.
+\newblock {The NumPy array: a structure for efficient numerical computation}.
+\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
+
+\bibitem{Li2011}
+Li J, Hingston P, and Kendall G.
+\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
+  Dilemma Competitions}.
+\newblock {\em IEEE Transactions on Computational Intelligence and AI in
+  Games}, 3(4):348--360, 2011.
+
+\bibitem{kendall2007iterated}
+Kendall G, Yao X, and Chong S.
+\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
+\newblock Advances in natural computation. World Scientific, 2007.
+
+\bibitem{Tzafestas2000}
+Tzafestas E.
+\newblock {Toward adaptive cooperative behavior}.
+\newblock {\em From Animals to animals: Proceedings of the 6th International
+  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
+  2000.
+
+\bibitem{Axelrod1984}
+Axelrod R.
+\newblock {\em The Evolution of Cooperation}.
+\newblock Basic books. Basic Books, 1984.
+
+\bibitem{Mittal2009}
+Mittal S and Deb K.
+\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
+  multiple conflicting objectives}.
+\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
+  2009.
+
+\bibitem{Hilbe2013}
+Hilbe C, Nowak M, and Traulsen A.
+\newblock {Adaptive dynamics of extortion and compliance}.
+\newblock {\em PloS one}, 8(11):e77886, 2013.
+
+\bibitem{Nachbar1992}
+Nachbar J.
+\newblock {Evolution in the finitely repeated prisoner's dilemma}.
+\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
+  1992.
+
+\bibitem{Axelrod1995}
+Wu J and Axelrod R .
+\newblock {How to cope with noise in the iterated prisoner's dilemma}.
+\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
+
+\bibitem{Berg2015}
+Van~den Berg P and Weissing F.
+\newblock {The importance of mechanisms for the evolution of cooperation}.
+\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
+  Society, 2015.
 
 \bibitem{Axelrod1980b}
-Robert Axelrod.
+Axelrod R.
 \newblock {More Effective Choice in the Prisoner's Dilemma}.
@@
 
-\bibitem{Axelrod1984}
-Robert Axelrod.
-\newblock {\em The Evolution of Cooperation}.
-\newblock Basic books. Basic Books, 1984.
-
-\bibitem{Baek2016}
-{Baek, Seung Ki and Jeong, Hyeong-chai and Hilbe, Christian and Nowak, Martin
-  A}.
-\newblock {Comparing reactive and memory- one strategies of direct
-  reciprocity}.
-\newblock {\em Nature Publishing Group}, pages 1--13, 2016.
-
-\bibitem{Banks1990}
-Jeffrey~S Banks and Rangarajan~K Sundaram.
-\newblock {Repeated games, finite automata, and complexity}.
-\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
+\bibitem{Frean1994}
+Frean M.
+\newblock {The prisoner's dilemma without synchrony}.
+\newblock {\em Proceedings of the Royal Society of London B: Biological
+  Sciences}, 257(1348):75--79, 1994.
+
+\bibitem{Nowak1993}
+Nowak M and Sigmund K.
+\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
+  the Prisoner's Dilemma game.}
+\newblock {\em Nature}, 364(6432):56--58, 1993.
 
 \bibitem{Beaufils1997}
-Bruno Beaufils, Jean-Paul Delahaye, and Philippe Mathieu.
+Beaufils B, Delahaye J, and Mathieu P.
 \newblock {Our meeting with gradual, a good strategy for the iterated
@@
 
-\bibitem{brown2001interval}
-Lawrence~D Brown, T~Tony Cai, and Anirban DasGupta.
-\newblock Interval estimation for a binomial proportion.
-\newblock {\em Statistical science}, pages 101--117, 2001.
+\bibitem{Banks1990}
+Banks J and Sundaram R.
+\newblock {Repeated games, finite automata, and complexity}.
+\newblock {\em Games and Economic Behavior}, 2(2):97--117, 1990.
+
+\bibitem{Stewart2012}
+Stewart A and Plotkin J.
+\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
+\newblock {\em Proceedings of the National Academy of Sciences},
+  109(26):10134--10135, 2012.
+
+\bibitem{PD2017}
+Unkwown.
+\newblock www.prisoners-dilemma.com.
+\newblock http://www.prisoners-dilemma.com/, 2017.
+
+\bibitem{Eckhart2015}
+Eckhart A.
+\newblock Coopsim v0.9.9 beta 6.
+\newblock https://github.com/jecki/CoopSim/, 2015.
+
+\bibitem{Ashlock2014}
+Ashlock W, Tsang J, and Ashlock D.
+\newblock {The evolution of exploitation}.
+\newblock In {\em Foundations of Computational Intelligence (FOCI), 2014 IEEE
+  Symposium on}, pages 135--142. IEEE, 2014.
+
+\bibitem{Ashlock2008}
+Ashlock D and Kim E.
+\newblock {Fingerprinting: Visualization and automatic analysis of prisoner's
+  dilemma strategies}.
+\newblock {\em IEEE Transactions on Evolutionary Computation}, 12(5):647--659,
+  2008.
 
 \bibitem{Andre2013}
-Andre~LC Carvalho, Honovan~P Rocha, Felipe~T Amaral, and Frederico~G Guimaraes.
+Carvalho A, Rocha H, Amaral F, and Guimaraes F.
 \newblock {Iterated Prisoner’s Dilemma-An extended analysis}.
@@
 
-\bibitem{Eckhart2015}
-Arnold Eckhart.
-\newblock Coopsim v0.9.9 beta 6.
-\newblock https://github.com/jecki/CoopSim/, 2015.
-
-\bibitem{Flood1958}
-Merrill~M Flood.
-\newblock {Some Experimental Games}, 1958.
-
-\bibitem{Frean1994}
-Marcus~R Frean.
-\newblock {The prisoner's dilemma without synchrony}.
-\newblock {\em Proceedings of the Royal Society of London B: Biological
-  Sciences}, 257(1348):75--79, 1994.
-
-\bibitem{Gaudesi2016}
-Marco Gaudesi, Elio Piccolo, Giovanni Squillero, and Alberto Tonda.
-\newblock {Exploiting evolutionary modeling to prevail in iterated prisoner’s
-  dilemma tournaments}.
+\bibitem{Ashlock2015}
+Ashlock D, Brown J, and Hingston P.
+\newblock {Multiple Opponent Optimization of Prisoner’s Dilemma Playing
+  Agents}.
 \newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 8(3):288--300, 2016.
-
-\bibitem{marc_harper_2017_824264}
-Marc Harper, Vince Knight, and Martin Jones.
-\newblock Axelrod-python/axelrod-dojo: v0.0.1.
-\newblock https://doi.org/10.5281/zenodo.824264, July 2017.
-
-\bibitem{Harper2017}
-Marc Harper, Vincent Knight, Martin Jones, Georgios Koutsovoulos, Nikoleta~E
-  Glynatsi, and Owen Campbell.
-\newblock {Reinforcement Learning Produces Dominant Strategies for the Iterated
-  Prisoner's Dilemma}.
-\newblock {\em PLOS ONE}, 12(12): 12 2017.
-
-\bibitem{Hilbe2017}
-Christian Hilbe, Luis~A Martinez-Vaquero, Krishnendu Chatterjee, and Martin~A
-  Nowak.
-\newblock {Memory-n strategies of direct reciprocity}.
-\newblock {\em Proceedings of the National Academy of Sciences}, page
-  201621239, 2017.
-
-\bibitem{Hilbe2013}
-Christian Hilbe, Martin~A Nowak, and Arne Traulsen.
-\newblock {Adaptive dynamics of extortion and compliance}.
-\newblock {\em PloS one}, 8(11):e77886, 2013.
-
-\bibitem{hunter2007matplotlib}
-John~D Hunter.
-\newblock {Matplotlib: A 2D graphics environment}.
-\newblock {\em Computing In Science \& Engineering}, 9(3):90--95, 2007.
-
-\bibitem{kendall2007iterated}
-Graham Kendall, Xin Yao, and Siang~Y Chong.
-\newblock {\em The Iterated Prisoners' Dilemma: 20 Years on}.
-\newblock Advances in natural computation. World Scientific, 2007.
-
-\bibitem{Knight2016}
-Vincent Knight, Owen Campbell, Marc Harper, Karol~M Langner, James Campbell,
-  Thomas Campbell, Alex Carney, Martin Chorley, Cameron Davidson-pilon,
-  Nikoleta Glynatsi, Tom{\'{a}}{\v{s}} Ehrlich, Martin Jones, Georgios
-  Koutsovoulos, Jochen Muller, Geraint Palmer, Piotr Petunov, Paul Slavin,
-  Timothy Standen, Luis Visintini, and Karl Molden.
-\newblock {An Open Framework for the Reproducible Study of the Iterated
-  Prisoner ' s Dilemma}.
-\newblock 2016.
-
-\bibitem{data}
-Vincent Knight, Marc Harper, and Nikoleta~E Glynatsi.
-\newblock {Data for: Evolution Reinforces Cooperation with the Emergence of
-  Self-Recognition Mechanisms: an empirical study of the Moran process for the
-  iterated Prisoner's dilemma using reinforcement learning}.
-\newblock https://doi.org/10.5281/zenodo.1040129, July 2017.
+  Games}, 7(1):53--65, 2015.
 
 \bibitem{Kraines1989}
-David Kraines and Vivian Kraines.
+Kraines D and Kraines V.
 \newblock {Pavlov and the prisoner's dilemma}.
@@
 
+\bibitem{Mathieu2015}
+Mathieu P and Delahaye J.
+\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
+  Abstract)}.
+\newblock {\em 14th International Conference on Autonomous Agents and
+  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
+
 \bibitem{Kuhn2017}
-Steven Kuhn.
+Kuhn S.
 \newblock Prisoner's dilemma.
@@
   edition, 2017.
-
-\bibitem{Lee2015}
-Christopher Lee, Marc Harper, and Dashiell Fryer.
-\newblock {The Art of War: Beyond Memory-one Strategies in Population Games}.
-\newblock {\em Plos One}, 10(3):e0120625, 2015.
-
-\bibitem{Li2011}
-Jiawei Li, Philip Hingston, and Graham Kendall.
-\newblock {Engineering Design of Strategies for Winning Iterated Prisoner's
-  Dilemma Competitions}.
-\newblock {\em IEEE Transactions on Computational Intelligence and AI in
-  Games}, 3(4):348--360, 2011.
-
-\bibitem{Li2009}
-Jiawei Li and Graham Kendall.
-\newblock {A strategy with novel evolutionary features for the iterated
-  prisoner's dilemma.}
-\newblock {\em Evolutionary Computation}, 17(2):257--274, 2009.
-
-\bibitem{Li2014}
-Jiawei Li and Graham Kendall.
-\newblock {The effect of memory size on the evolutionary stability of
-  strategies in iterated prisoner's dilemma}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 18(6):819--826,
-  2014.
-
-\bibitem{Prison1998}
-LIFL.
-\newblock Prison.
-\newblock http://www.lifl.fr/IPD/ipd.frame.html, 2008.
-
-\bibitem{Mateo2003}
-Jill M. Mateo.
-\newblock {Kin recognition in ground squirrels and other rodents}.
-\newblock In {\em Journal of Mammalogy}, 84 (4), 1163--1181
-
-\bibitem{Mathieu2015}
-Philippe Mathieu and Jean-Paul Delahaye.
-\newblock {New Winning Strategies for the Iterated Prisoner's Dilemma (Extended
-  Abstract)}.
-\newblock {\em 14th International Conference on Autonomous Agents and
-  Multiagent Systems (AAMAS 2015)}, pages 1665--1666, 2015.
-
-\bibitem{mckinney2010data}
-Wes McKinney et~al.
-\newblock Data structures for statistical computing in python.
-\newblock In {\em Proceedings of the 9th Python in Science Conference}, volume
-  445, pages 51--56. van der Voort S, Millman J, 2010.
-
-\bibitem{Mittal2009}
-Shashi Mittal and Kalyanmoy Deb.
-\newblock {Optimal strategies of the iterated prisoner's dilemma problem for
-  multiple conflicting objectives}.
-\newblock {\em IEEE Transactions on Evolutionary Computation}, 13(3):554--565,
-  2009.
-
-\bibitem{Moran1957}
-Patrick A~P Moran.
-\newblock {Random Processes in Genetics}.
-\newblock {\em Mathematical Proceedings of the Cambridge Philosophical
-  Society}, 54(1):60--71, 1957.
-
-\bibitem{Nachbar1992}
-John~H Nachbar.
-\newblock {Evolution in the finitely repeated prisoner's dilemma}.
-\newblock {\em Journal of Economic Behavior \& Organization}, 19(3):307--326,
-  1992.
-
-\bibitem{Nowak}
-Martin~A Nowak.
-\newblock {\em Evolutionary Dynamics: Exploring the Equations of Life}.
-\newblock Cambridge: Harvard University Press.
-
-\bibitem{Nowak1993}
-Martin~A Nowak and Karl Sigmund.
-\newblock {A strategy of win-stay, lose-shift that outperforms tit-for-tat in
-  the Prisoner's Dilemma game.}
-\newblock {\em Nature}, 364(6432):56--58, 1993.
-
-\bibitem{Press2012}
-William~H Press and Freeman~J Dyson.
-\newblock {Iterated Prisoner's Dilemma contains strategies that dominate any
-  evolutionary opponent.}
-\newblock {\em Proceedings of the National Academy of Sciences of the United
-  States of America}, 109(26):10409--13, 2012.
-
-\bibitem{Prlic2012}
-Andreas Prlić and James~B Procter.
-\newblock {Ten Simple Rules for the Open Development of Scientific Software}.
-\newblock {\em PLOS Computational Biology}, 8(12):1--3, 12 2012.
-
-\bibitem{axelrodproject}
-The~Axelrod project developers.
-\newblock Axelrod: v2.9.0.
-\newblock http://dx.doi.org/10.5281/zenodo.499122, April 2016.
-
-\bibitem{Robson1990}
-Arthur~J Robson.
-\newblock {Efficiency in evolutionary games: Darwin, Nash and the secret
-  handshake}.
-\newblock {\em Journal of theoretical Biology}, 144(3):379--396, 1990.
-
-\bibitem{Sandve2013}
-Geir~Kjetil Sandve, Anton Nekrutenko, James Taylor, and Eivind Hovig.
-\newblock {Ten Simple Rules for Reproducible Computational Research}.
-\newblock {\em PLoS Computational Biology}, 9(10):1--4, 2013.
-
-\bibitem{Stewart2012}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {Extortion and cooperation in the Prisoner’s Dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  109(26):10134--10135, 2012.
-
-\bibitem{stewart2013extortion}
-Alexander~J Stewart and Joshua~B Plotkin.
-\newblock {From extortion to generosity, evolution in the iterated prisoner’s
-  dilemma}.
-\newblock {\em Proceedings of the National Academy of Sciences},
-  110(38):15348--15353, 2013.
-
-\bibitem{Tzafestas2000}
-Elpida Tzafestas.
-\newblock {Toward adaptive cooperative behavior}.
-\newblock {\em From Animals to animals: Proceedings of the 6th International
-  Conference on the Simulation of Adaptive Behavior {(SAB-2000)}}, 2:334--340,
-  2000.
-
-\bibitem{PD2017}
-Unkwown.
-\newblock www.prisoners-dilemma.com.
-\newblock http://www.prisoners-dilemma.com/, 2017.
-
-\bibitem{Berg2015}
-Pieter Van~den Berg and Franz~J Weissing.
-\newblock {The importance of mechanisms for the evolution of cooperation}.
-\newblock In {\em Proc. R. Soc. B}, volume 282, page 20151382. The Royal
-  Society, 2015.
-
-\bibitem{walt2011numpy}
-St{\'e}fan van~der Walt, S~Chris Colbert, and Gael Varoquaux.
-\newblock {The NumPy array: a structure for efficient numerical computation}.
-\newblock {\em Computing in Science \& Engineering}, 13(2):22--30, 2011.
-
-\bibitem{West2016}
-Jeffrey West, Zaki Hasnain, Jeremy Mason, and Paul~K Newton.
-\newblock {The prisoner’s dilemma as a cancer model}.
-\newblock {\em Convergent Science Physical Oncology}, 2(3):035002, 2016.
-
-\bibitem{Wilson2014}
-Greg Wilson, D~A Aruliah, C~Titus Brown, Neil~P Chue~Hong, Matt Davis,
-  Richard~T Guy, Steven H~D Haddock, Kathryn~D Huff, Ian~M Mitchell, Mark~D
-  Plumbley, Ben Waugh, Ethan~P White, and Paul Wilson.
-\newblock {Best Practices for Scientific Computing}.
-\newblock {\em PLOS Biology}, 12(1):1--7, 01 2014.
-
-\bibitem{Axelrod1995}
-Jianzhong Wu and Robert Axelrod.
-\newblock {How to cope with noise in the iterated prisoner's dilemma}.
-\newblock {\em Journal of Conflict resolution}, 39(1):183--189, 1995.
 
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig17.eps}
+    %\includegraphics[ width=\textwidth]{./Fig12.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=3\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig18.eps}
+    %\includegraphics[ width=\textwidth]{./Fig13.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=4\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig19.eps}
+    %\includegraphics[ width=\textwidth]{./Fig14.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=5\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig20.eps}
+    %\includegraphics[ width=\textwidth]{./Fig15.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=6\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig21.eps}
+    %\includegraphics[ width=\textwidth]{./Fig16.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=7\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig22.eps}
+    %\includegraphics[ width=\textwidth]{./Fig17.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=8\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig23.eps}
+    %\includegraphics[ width=\textwidth]{./Fig18.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=9\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig24.eps}
+    %\includegraphics[ width=\textwidth]{./Fig19.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=10\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig25.eps}
+    %\includegraphics[ width=\textwidth]{./Fig20.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=11\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig26.eps}
+    %\includegraphics[ width=\textwidth]{./Fig21.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=12\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig27.eps}
+    %\includegraphics[ width=\textwidth]{./Fig22.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=13\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig28.eps}
+    %\includegraphics[ width=\textwidth]{./Fig23.eps}
     \caption{The fixation probabilities \(x_1\) for \(N=14\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig29.eps}
+    %\includegraphics[ width=\textwidth]{./Fig24.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig30.eps}
+    %\includegraphics[ width=\textwidth]{./Fig25.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig31.eps}
+    %\includegraphics[ width=\textwidth]{./Fig26.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig32.eps}
+    %\includegraphics[ width=\textwidth]{./Fig27.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig33.eps}
+    %\includegraphics[ width=\textwidth]{./Fig28.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig34.eps}
+    %\includegraphics[ width=\textwidth]{./Fig29.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig35.eps}
+    %\includegraphics[ width=\textwidth]{./Fig30.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig36.eps}
+    %\includegraphics[ width=\textwidth]{./Fig31.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig37.eps}
+    %\includegraphics[ width=\textwidth]{./Fig32.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig38.eps}
+    %\includegraphics[ width=\textwidth]{./Fig33.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig39.eps}
+    %\includegraphics[ width=\textwidth]{./Fig34.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
@@
     \centering
-    \includegraphics[draft, width=\textwidth]{./Fig40.eps}
+    %\includegraphics[ width=\textwidth]{./Fig35.eps}
     \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}

### 2018-10-05 rename-files-for-plos.sh

@@ -9,34 +9,29 @@ cp Calculator_v_Arrogant_QLearner.eps Fig6.eps
 cp average_rank_vs_population_size_invade.eps Fig7.eps
 cp average_rank_vs_population_size_resist.eps Fig8.eps
 cp average_rank_vs_population_size_coexist.eps Fig9.eps
-cp correlation_heatmap_invade.eps Fig10.eps
-cp correlation_heatmap_resist.eps Fig11.eps
-cp correlation_heatmap_coexist.eps Fig12.eps
-cp cooperation_0_0_10000_TF1_array.eps Fig13.eps
-cp cooperation_0_0_10000_TF2_array.eps Fig14.eps
-cp cooperation_0_0_10000_TF3_array.eps Fig15.eps
-cp cooperation_0_0_10000_CS_array.eps Fig16.eps
-cp boxplot_3_invade.eps Fig17.eps
-cp boxplot_4_invade.eps Fig18.eps
-cp boxplot_5_invade.eps Fig19.eps
-cp boxplot_6_invade.eps Fig20.eps
-cp boxplot_7_invade.eps Fig21.eps
-cp boxplot_8_invade.eps Fig22.eps
-cp boxplot_9_invade.eps Fig23.eps
-cp boxplot_10_invade.eps Fig24.eps
-cp boxplot_11_invade.eps Fig25.eps
-cp boxplot_12_invade.eps Fig26.eps
-cp boxplot_13_invade.eps Fig27.eps
-cp boxplot_14_invade.eps Fig28.eps
-cp boxplot_3_resist.eps Fig29.eps
-cp boxplot_4_resist.eps Fig30.eps
-cp boxplot_5_resist.eps Fig31.eps
-cp boxplot_6_resist.eps Fig32.eps
-cp boxplot_7_resist.eps Fig33.eps
-cp boxplot_8_resist.eps Fig34.eps
-cp boxplot_9_resist.eps Fig35.eps
-cp boxplot_10_resist.eps Fig36.eps
-cp boxplot_11_resist.eps Fig37.eps
-cp boxplot_12_resist.eps Fig38.eps
-cp boxplot_13_resist.eps Fig39.eps
-cp boxplot_14_resist.eps Fig40.eps
+cp correlation_heatmaps.eps Fig10.eps
+cp cooperation_heatmap.eps Fig11.eps
+cp boxplot_3_invade.eps Fig12.eps
[…]

### 2018-10-10 main.tex
Ensure a max of 6 authors are listed.

@@
 Knight V, Campbell O, Harper M, Langner K, Campbell J,
-  Campbell T, Carney A, Chorley M, Davidson-pilon C,
-  Glynatsi N, Ehrlich T, Jones M, Koutsovoulos G, Muller J, Palmer G, Petunov P, Slavin P,
-  Standen T, Visintini L, and Molden K.
+  Campbell T, et al.
   \newblock {An Open Framework for the Reproducible Study of the Iterated
@@
 Allen B, Lippner G, Chen Y, Fotouhi B, Momeni N,
-  Shing-Tung Yau, and Martin~A Nowak.
+  Shing-Tung Yau et al.
 \newblock {Evolutionary dynamics on any population structure}.
@@
 Wilson G , Aruliah D, Brown T, Chue~Hong N, Davis M ,
-  Guy R , Haddock S , Huff K, Mitchell I , Plumbley M , 
-  Waugh B , White E , and Wilson P.
+  Guy R , et al.
   \newblock {Best Practices for Scientific Computing}.

### 2018-10-12 main.tex
Relabel supporting information and separate tables

@@
 
-The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
-figures showing the performance of all strategies is available in the
-appendix.
+The top 16 strategies are given in
+Tables~\ref{tbl:top_invade_3},\ref{tbl:top_invade_7} and
+\ref{tbl:top_invade_14}. A variety of figures showing the performance of all
+strategies is available in the supporting information.
 
@@
     \tiny
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
             \begin{tabular}{llrrrrrrr}
@@
             \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
+    \caption{Top invaders for \(N=3\)}
+    \label{tbl:top_invade_3}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+    \tiny
             \begin{tabular}{llrrrrrrr}
@@
             \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
-        \centering
+    \caption{Top invaders for \(N=7\)}
+    \label{tbl:top_invade_7}
+\end{table}
+
+\begin{table}[!hbtp]
+    \centering
+    \tiny
             \begin{tabular}{llrrrrrrr}
@@
             \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_invade}
+    \caption{Top invaders for \(N=14\)}
+    \label{tbl:top_invade_14}
 \end{table}
@@
 
-Table~\ref{tbl:top_resist} shows the top strategies when ranked
-according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
-for all strategies are available in the supplementary materials.
-Once again none of the short memory strategies previously discussed perform well
-for high \(N\).
+Tables~\ref{tbl:top_resist_3},~\ref{tbl:top_resist_7} and
+\ref{tbl:top_resist_14} show the top strategies when ranked according to
+\(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results for all
+strategies are available in the supplementary materials.  Once again none of the
+short memory strategies previously discussed perform well for high \(N\).
 
@@
     \tiny
-    \centering
-    \begin{subfigure}[t]{\columnwidth}
     \centering
@@
         \end{tabular}
-        \caption{\(N=3\)}
-    \end{subfigure}%
-
-    \begin{subfigure}[t]{\columnwidth}
+        \caption{Top resistors for \(N=3\)}
+    \label{tbl:top_resist_3}
+\end{table}
+
+\begin{table}[!hbtp]
+    \tiny
     \centering
@@
             \end{tabular}
-        \caption{\(N=7\)}
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\columnwidth}
+    \caption{Top resistors for \(N=7\)}
+    \label{tbl:top_resist_7}
+\end{table}
+
+\begin{table}[!hbtp]
+    \tiny
     \centering
@@
         \end{tabular}
-        \caption{\(N=14\)}
-    \end{subfigure}
-    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
-    \label{tbl:top_resist}
+    \caption{Top resistors for \(N=14\)}
+    \label{tbl:top_resist_14}
 \end{table}
@@
 
-\section{Appendix A: List of players}\label{app:list_of_players}
+\section*{Appendix: List of players}\label{app:list_of_players}
 
@@
 
-\section{Appendix B: Supplementary figures}
-
-\begin{itemize}
-    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
-for each strategy. The mean and error bars are shown against the collection of
-all opponents.
-
-    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
-\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
-the collection of all opponents.
-
-    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
-ranks of each strategy according to mean absorption probability across all
-population sizes.
-\end{itemize}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig12.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
-    \label{invasion-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig13.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig14.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig15.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig16.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig17.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig18.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig19.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig20.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig21.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig22.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig23.eps}
-    \caption{The fixation probabilities \(x_1\) for \(N=14\)}
-    \label{invasion-14}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig24.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=3\)}
-    \label{resistance-3}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig25.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=4\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig26.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=5\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig27.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=6\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig28.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=7\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig29.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=8\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig30.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=9\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig31.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=10\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig32.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=11\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig33.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=12\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig34.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=13\)}
-\end{figure}
-
-\begin{figure}[!hbtp]
-    \centering
-    %\includegraphics[ width=\textwidth]{./Fig35.eps}
-    \caption{The fixation probabilities \(x_{N-1}\) for \(N=14\)}
-    \label{resistance-14}
+\section*{Supporting information}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S1_Fig.eps}
+    \textbf{S1 Fig.} The fixation probabilities \(x_1\) for \(N=3\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S2_Fig.eps}
+    \textbf{S2 Fig.} The fixation probabilities \(x_1\) for \(N=4\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S3_Fig.eps}
+    \textbf{S3 Fig.} The fixation probabilities \(x_1\) for \(N=5\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S4_Fig.eps}
+    \textbf{S4 Fig.} The fixation probabilities \(x_1\) for \(N=6\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S5_Fig.eps}
+    \textbf{S5 Fig.} The fixation probabilities \(x_1\) for \(N=7\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S6_Fig.eps}
+    \textbf{S6 Fig.} The fixation probabilities \(x_1\) for \(N=8\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S7_Fig.eps}
+    \textbf{S7 Fig.} The fixation probabilities \(x_1\) for \(N=9\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S8_Fig.eps}
+    \textbf{S8 Fig.} The fixation probabilities \(x_1\) for \(N=10\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S9_Fig.eps}
+    \textbf{S9 Fig.} The fixation probabilities \(x_1\) for \(N=11\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S10_Fig.eps}
+    \textbf{S10 Fig.} The fixation probabilities \(x_1\) for \(N=12\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S11_Fig.eps}
+    \textbf{S11 Fig.} The fixation probabilities \(x_1\) for \(N=13\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S12_Fig.eps}
+    \textbf{S12 Fig.} The fixation probabilities \(x_1\) for \(N=14\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S13_Fig.eps}
+    \textbf{S13 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=3\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S14_Fig.eps}
+    \textbf{S14 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=4\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S15_Fig.eps}
+    \textbf{S15 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=5\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S16_Fig.eps}
+    \textbf{S16 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=6\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S17_Fig.eps}
+    \textbf{S17 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=7\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S18_Fig.eps}
+    \textbf{S18 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=8\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S19_Fig.eps}
+    \textbf{S19 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=9\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S20_Fig.eps}
+    \textbf{S20 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=10\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S21_Fig.eps}
+    \textbf{S21 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=11\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S22_Fig.eps}
+    \textbf{S22 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=12\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S23_Fig.eps}
+    \textbf{S23 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=13\)
+\end{figure}
+
+\begin{figure}[!hbtp]
+    %\includegraphics[ width=\textwidth]{./S24_Fig.eps}
+    \textbf{S24 Fig.} The fixation probabilities \(x_{N-1}\) for \(N=14\)
 \end{figure}

### 2018-10-12 rename-files-for-plos.sh

@@ -11,27 +11,27 @@ cp average_rank_vs_population_size_resist.eps Fig8.eps
 cp average_rank_vs_population_size_coexist.eps Fig9.eps
 cp correlation_heatmaps.eps Fig10.eps
 cp cooperation_heatmap.eps Fig11.eps
-cp boxplot_3_invade.eps Fig12.eps
-cp boxplot_4_invade.eps Fig13.eps
-cp boxplot_5_invade.eps Fig14.eps
-cp boxplot_6_invade.eps Fig15.eps
-cp boxplot_7_invade.eps Fig16.eps
-cp boxplot_8_invade.eps Fig17.eps
-cp boxplot_9_invade.eps Fig18.eps
-cp boxplot_10_invade.eps Fig19.eps
-cp boxplot_11_invade.eps Fig20.eps
-cp boxplot_12_invade.eps Fig21.eps
-cp boxplot_13_invade.eps Fig22.eps
-cp boxplot_14_invade.eps Fig23.eps
-cp boxplot_3_resist.eps Fig24.eps
-cp boxplot_4_resist.eps Fig25.eps
-cp boxplot_5_resist.eps Fig26.eps
-cp boxplot_6_resist.eps Fig27.eps
-cp boxplot_7_resist.eps Fig28.eps
-cp boxplot_8_resist.eps Fig29.eps
-cp boxplot_9_resist.eps Fig30.eps
-cp boxplot_10_resist.eps Fig31.eps
-cp boxplot_11_resist.eps Fig32.eps
-cp boxplot_12_resist.eps Fig33.eps
-cp boxplot_13_resist.eps Fig34.eps
-cp boxplot_14_resist.eps Fig35.eps
+cp boxplot_3_invade.eps S1_Fig.eps
+cp boxplot_4_invade.eps S2_Fig.eps
+cp boxplot_5_invade.eps S3_Fig.eps
+cp boxplot_6_invade.eps S4_Fig.eps
+cp boxplot_7_invade.eps S5_Fig.eps
+cp boxplot_8_invade.eps S6_Fig.eps
+cp boxplot_9_invade.eps S7_Fig.eps
+cp boxplot_10_invade.eps S8_Fig.eps
+cp boxplot_11_invade.eps S9_Fig.eps
+cp boxplot_12_invade.eps S10_Fig.eps
+cp boxplot_13_invade.eps S11_Fig.eps
[…]
